### 2022-08-25 analysis.Rmd
move experiment inside experiment

---
title: "Face Attractiveness and the Sense of Reality"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr"
)

cache <- TRUE
runModels <- FALSE
bestModels <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/",
  fig.width = fig.width,
  fig.height = fig.height
)
```

# Introduction

The goal of this study was to...

# Methods

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggdist)
library(ggside)
library(easystats)
library(patchwork)
library(brms)

df <- read.csv("data/data.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
    Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
  )

# Fix precision
for(ill in unique(df$Illusion_Type)) {
  data <- df[df$Illusion_Type == ill, ] 
  i <- 10
  while (length(sort(unique(signif(data$Illusion_Difference, i)))) != 8) {
    i <- i - 1
  }
  df[df$Illusion_Type == ill, "Illusion_Difference"] <- signif(df[df$Illusion_Type == ill, "Illusion_Difference"], i)
  if (i != 10) {
    message(ill, ": Illusion_Difference values != 8. Rounded to ", i, ".")
  }
}

# Transformation
df <- df |> 
  mutate(    
    Illusion_Difference_log = log(1 + Illusion_Difference),
    Illusion_Difference_sqrt = sqrt(Illusion_Difference),
    Illusion_Difference_cbrt = Illusion_Difference**(1 / 3),
    Illusion_Strength_log = sign(Illusion_Strength) * log(1 + abs(Illusion_Strength)),
    Illusion_Strength_sqrt = sign(Illusion_Strength) * sqrt(abs(Illusion_Strength)),
    Illusion_Strength_cbrt = sign(Illusion_Strength) * (abs(Illusion_Strength)**(1 / 3))
    )
```

### 2022-08-25 experiment/stimuli/README.Rmd
move experiment inside experiment

---
title: "Stimuli Preprocessing"
output:
  github_document:
    toc: true
    fig_width: 10.08
    fig_height: 6
editor_options:
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
# options and parameters
options(digits = 3)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.path = "./figures/"
)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(easystats)
library(ggimage)
```

```{r, warning=FALSE, message=FALSE, fig.height=10, fig.width=10}
# 1. NEVER spaces or weird characters in paths/filenames etc
# 2. When possible, always work with relative paths and not absoltue (C://dom/) 
# so that it's reproducible
# Remove the comment above once it's read as a reading check
df <- read.csv("AMFD_norms.csv") |> 
  filter(FType == 0) |> 
  mutate(Gender = ifelse(Gender_cat == 2, "M", "F"),
         File = paste0("AMFD/N", Gender, "-", PhotoID, ".jpg"))

df_extremes <- df |> 
  filter(abs(standardize(Attract_mean)) > 1.5 | 
           abs(standardize(Trust_mean)) > 2)

ggplot(df, aes(x = Attract_mean, y=Trust_mean)) +
  geom_point(aes(color=Gender)) +
  geom_image(data=df_extremes, aes(image=File), size=0.1) + 
  geom_smooth(aes(color=Gender), method="lm", se=FALSE) +
  theme_modern() +
  labs(x = "Attractiveness", y = "Trust")
```

### 2022-08-25 preprocessing.R

@@ -1,6 +1,6 @@
 preprocess_raw <- function(file) {
   file <- read.csv(file)
-  
+
   # Internal Utilities
   unnest <- function(scale){
     data <- file |>
@@ -9,7 +9,7 @@ preprocess_raw <- function(file) {
       jsontools::json_unnest_longer(col='response', indices_to = 'index')
     data
   }
-  
+
   # Preprocess
   if (!"end_screen" %in% file$screen) {
     print(paste0("Warning: Incomplete data for ", file))
@@ -17,19 +17,19 @@ preprocess_raw <- function(file) {
   }
   # Demographics
   dem <- file[file$screen == "demographics" & !is.na(file$screen), "response"]
-  
+
   # Trials
   trials<-file[file$screen=='stimuli', ]
   response<- file[file$screen=='questionnaire',]
-  
+
   # Questionnaire
   questionnaire<- file |>
     filter(screen == 'questionnaire') |>
     select(participant_id, response) |>
     jsontools::json_unnest_wider(col='response')
   questionnaire<- questionnaire|>rename(Participant='participant_id')
-    
-  # Info 
+
+  # Info
   info <- file[file$screen == "browser_info" & !is.na(file$screen), ]
   data <- data.frame(
     Participant = trials$participant_id,
@@ -56,8 +56,8 @@ preprocess_raw <- function(file) {
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", trials$stimulus)),
     RT = as.numeric(response$rt)
   )
-  
-  # Psychometric Scales 
+
+  # Psychometric Scales
   # IPIP
   ipip6 <-unnest('IPIP6')|>
     pivot_wider(names_from='index', values_from='response')
@@ -68,24 +68,24 @@ preprocess_raw <- function(file) {
   data$Openness <- rowMeans(ipip6[grepl("Openness", names(ipip6))])
   data$HonestyHumility <- rowMeans(ipip6[grepl("HonestyHumility", names(ipip6))])
   data$Agreeableness <- rowMeans(ipip6[grepl("Agreeableness", names(ipip6))])
- 
+
   #SIAS
-  sias<-unnest('SIAS') 
+  sias<-unnest('SIAS')
   attention_check<- sias[sias$index=='Attention_Check_1',]
   attention_check<- attention_check |>
     pivot_wider(names_from='index', values_from='response')
   data$Attention_Check1<- attention_check$Attention_Check_1
-  
+
   sias <-sias|>
[…]

### 2022-08-25 preprocessing.R
preprocessing

@@ -2,11 +2,19 @@ preprocess_raw <- function(file) {
   file <- read.csv(file)
 
   # Internal Utilities
+  # unnest <- function(scale){
+  #   data <- file |>
+  #     filter(screen == scale) |>
+  #     select(participant_id, response) |>
+  #     jsontools::json_unnest_longer(col='response', indices_to = 'index')
+  #   data
+  # }
+  
   unnest <- function(scale){
     data <- file |>
       filter(screen == scale) |>
       select(participant_id, response) |>
-      jsontools::json_unnest_longer(col='response', indices_to = 'index')
+      jsontools::json_unnest_wider(col='response')
     data
   }
 
@@ -23,10 +31,7 @@ preprocess_raw <- function(file) {
   response<- file[file$screen=='questionnaire',]
 
   # Questionnaire
-  questionnaire<- file |>
-    filter(screen == 'questionnaire') |>
-    select(participant_id, response) |>
-    jsontools::json_unnest_wider(col='response')
+  questionnaire<- unnest('questionnaire')
   questionnaire<- questionnaire|>rename(Participant='participant_id')
 
   # Info
@@ -59,8 +64,7 @@ preprocess_raw <- function(file) {
 
   # Psychometric Scales
   # IPIP
-  ipip6 <-unnest('IPIP6')|>
-    pivot_wider(names_from='index', values_from='response')
+  ipip6 <-unnest('IPIP6')
   ipip6[grepl("_R", names(ipip6))] <- 100 - ipip6[grepl("_R", names(ipip6))]
   data$Extraversion <- rowMeans(ipip6[grepl("Extraversion", names(ipip6))])
   data$Conscientiousness <- rowMeans(ipip6[grepl("Conscientiousness", names(ipip6))])
@@ -69,39 +73,29 @@ preprocess_raw <- function(file) {
   data$HonestyHumility <- rowMeans(ipip6[grepl("HonestyHumility", names(ipip6))])
   data$Agreeableness <- rowMeans(ipip6[grepl("Agreeableness", names(ipip6))])
 
-  #SIAS
+  # SIAS + Attention Check 1
   sias<-unnest('SIAS')
-  attention_check<- sias[sias$index=='Attention_Check_1',]
-  attention_check<- attention_check |>
-    pivot_wider(names_from='index', values_from='response')
[…]

### 2022-08-25 analysis.Rmd
update preprocessing

@@
 
-df <- read.csv("data/data.csv") |>
-  mutate(
-    Date = lubridate::dmy(Date),
-    Participant = fct_reorder(Participant, Date),
-    Screen_Refresh = as.character(Screen_Refresh),
-    Illusion_Side = as.factor(Illusion_Side),
-    # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
-    Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
-    Block = as.factor(Block),
-    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
+df <- read.csv("data/data.csv") 
+# |>
+#   mutate(
+#     Date = lubridate::dmy(Date),
+#     Participant = fct_reorder(Participant, Date),
+#     Screen_Refresh = as.character(Screen_Refresh),
+#     Illusion_Side = as.factor(Illusion_Side),
+#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
+#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
+#     Block = as.factor(Block),
+#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
+#   )
+
+```
+
+## Exclusions {.tabset}
+
+```{r message=FALSE, warning=FALSE}
+outliers <- c()
+```
+
+We removed `r length(outliers)` participants upon inspection of...
+
+### Error Rate
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |>
+  group_by(Participant) |>
+  summarize(
+    # n = n(),
+    Error = sum(Error) / n(),
+    RT_Mean = mean(RT),
+    RT_SD = sd(RT),
+    IPIP6_SD = mean(IPIP6_SD),
+    PID5_SD = mean(PID5_SD),
+  ) |>
+  ungroup() |>
+  arrange(desc(Error))
+
+data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm=TRUE))) |> 
+  rbind(dfsub) |> 
+  knitr::kable() |>
+  kableExtra::row_spec(1, italic = TRUE) |> 
+  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
+  kableExtra::row_spec(which(dfsub$Participant %in% partial_outliers) + 1, background = "#FFECB3")
+```
+
+## Participants
+
+```{r message=FALSE, warning=FALSE}
+dfsub <- df |>
+  group_by(Participant) |>
+  select(Participant, Age, Sex, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
+  slice(1) |>
+  ungroup()
+```
+
+The final sample included `r report::report_participants(dfsub, age="Age", sex="Sex")`.
+
+```{r }
+plot_distribution <- function(dfsub, what = "Age", title = what, subtitle = "", fill = "orange") {
+  dfsub |>
+    ggplot(aes_string(x = what)) +
+    geom_density(fill = fill) +
+    geom_vline(xintercept = mean(dfsub[[what]]), color = "red", linetype = "dashed") +
+    scale_x_continuous(expand = c(0, 0)) +
+    scale_y_continuous(expand = c(0, 0)) +
+    ggtitle(title, subtitle = subtitle) +
+    theme_modern() +
+    theme(
+      plot.title = element_text(face = "bold", hjust = 0.5),
+      plot.subtitle = element_text(face = "italic", hjust = 0.5),
+      axis.title.x = element_blank(),
+      axis.title.y = element_blank(),
+      axis.text.y = element_blank()
     )
-
-# Fix precision
-for(ill in unique(df$Illusion_Type)) {
-  data <- df[df$Illusion_Type == ill, ] 
-  i <- 10
-  while (length(sort(unique(signif(data$Illusion_Difference, i)))) != 8) {
-    i <- i - 1
-  }
-  df[df$Illusion_Type == ill, "Illusion_Difference"] <- signif(df[df$Illusion_Type == ill, "Illusion_Difference"], i)
-  if (i != 10) {
-    message(ill, ": Illusion_Difference values != 8. Rounded to ", i, ".")
-  }
 }
 
-# Transformation
-df <- df |> 
-  mutate(    
-    Illusion_Difference_log = log(1 + Illusion_Difference),
-    Illusion_Difference_sqrt = sqrt(Illusion_Difference),
-    Illusion_Difference_cbrt = Illusion_Difference**(1 / 3),
-    Illusion_Strength_log = sign(Illusion_Strength) * log(1 + abs(Illusion_Strength)),
-    Illusion_Strength_sqrt = sign(Illusion_Strength) * sqrt(abs(Illusion_Strength)),
-    Illusion_Strength_cbrt = sign(Illusion_Strength) * (abs(Illusion_Strength)**(1 / 3))
-    )
+plot_waffle <- function(dfsub, what = "Nationality", title = what) {
+  ggwaffle::waffle_iron(dfsub, what) |>
+    # mutate(label = emojifont::fontawesome('fa-person')) |>
+    ggplot(aes(x, y, fill = group)) +
+    ggwaffle::geom_waffle() +
+    coord_equal() +
+    ggtitle(title) +
+    labs(fill = "") +
+    theme_void() +
+    theme(plot.title = element_text(face = "bold", hjust = 0.5))
+}
 ```
+
+```{r fig.width=20, fig.height=15}
+# p1 <- plot_distribution(dfsub, "Age", fill = "#FF9800")
+# p2 <- plot_distribution(dfsub, "Duration", title = "Total Duration", subtitle = "in minutes", fill = "#F44336")
+# p3 <- plot_distribution(dfsub, "Break_Duration", title = "Break Duration", subtitle = "in minutes", fill = "#3F51B5")
+
+p4 <- plot_waffle(dfsub, "Sex") +
+  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))
+
+p5 <- plot_waffle(dfsub, "Education") +
+  scale_fill_viridis_d()
+
+p6 <- plot_waffle(dfsub, "Nationality") +
+  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))
+
+p7 <- plot_waffle(dfsub, "Ethnicity") +
+  scale_fill_manual(values = c("Latino" = "#FF5722", "Asian" = "#FF9800", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Jewish" = "#9C27B0", "Mixed" = "#795548"))
+
+p8 <- plot_waffle(dfsub, "Screen_Resolution", title = "Screen Resolution") +
+  scale_fill_pizza_d() +
+  guides(fill = "none")
+
+p9 <- plot_waffle(dfsub, "Device_OS", title = "Device OS") +
+  scale_fill_bluebrown_d()
+
+# p10 <- plot_waffle(dfsub, "Screen_Refresh") +
+#   scale_fill_viridis_d()
+
+(p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
+```

### 2022-08-25 preprocessing.R

@@ -1,55 +1,45 @@
-preprocess_raw <- function(file) {
-  file <- read.csv(file)
+unnest <- function(file, scale) {
+  data <- file |>
+    filter(screen == scale) |>
+    select(participant_id, response) |>
+    jsontools::json_unnest_wider(col = "response")
+  data
+}
 
-  # Internal Utilities
-  # unnest <- function(scale){
-  #   data <- file |>
-  #     filter(screen == scale) |>
-  #     select(participant_id, response) |>
-  #     jsontools::json_unnest_longer(col='response', indices_to = 'index')
-  #   data
-  # }
-  
-  unnest <- function(scale){
-    data <- file |>
-      filter(screen == scale) |>
-      select(participant_id, response) |>
-      jsontools::json_unnest_wider(col='response')
-    data
-  }
+preprocess_raw <- function(file) {
+
+  data <- read.csv(file)
 
   # Preprocess
-  if (!"end_screen" %in% file$screen) {
+  if (!"end_screen" %in% data$screen) {
     print(paste0("Warning: Incomplete data for ", file))
     return(data.frame())
   }
+
   # Demographics
-  dem <- file[file$screen == "demographics" & !is.na(file$screen), "response"]
+  dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
 
   # Trials
-  trials<-file[file$screen=='stimuli', ]
-  response<- file[file$screen=='questionnaire',]
-
-  # Questionnaire
-  questionnaire<- unnest('questionnaire')
-  questionnaire<- questionnaire|>rename(Participant='participant_id')
+  trials <- data[data$screen == "stimuli", ]
+  answers <- unnest(data, "questionnaire")
 
   # Info
-  info <- file[file$screen == "browser_info" & !is.na(file$screen), ]
-  data <- data.frame(
+  info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
+
+  df <- data.frame(
     Participant = trials$participant_id,
     Age = as.numeric(jsonlite::fromJSON(dem[1])$age),
[…]

### 2022-08-25 analysis.Rmd
update

@@
 
-### Error Rate
+### Attention Checks
 
@@
   group_by(Participant) |>
-  summarize(
-    # n = n(),
-    Error = sum(Error) / n(),
-    RT_Mean = mean(RT),
-    RT_SD = sd(RT),
-    IPIP6_SD = mean(IPIP6_SD),
-    PID5_SD = mean(PID5_SD),
-  ) |>
+  select(Participant, starts_with("Attention")) |> 
+  slice(1) |> 
   ungroup() |>
-  arrange(desc(Error))
+  mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |> 
+  arrange(Attention_Check)
+```
 
+### Duration
+
+```{r message=FALSE, warning=FALSE}
+
+```
+
+### Ratings
+
+```{r message=FALSE, warning=FALSE}
+dfsub$Cor_Trustworthy <- NA
+dfsub$Cor_Attractive <- NA
+for(participant in dfsub$Participant) {
+  dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
+  dfsub[dfsub$Participant == participant, "Cor_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
+}
+```
+
+```{r message=FALSE, warning=FALSE}
 data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm=TRUE))) |> 
@@
   kableExtra::row_spec(1, italic = TRUE) |> 
-  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
-  kableExtra::row_spec(which(dfsub$Participant %in% partial_outliers) + 1, background = "#FFECB3")
+  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
 ```
@@
   group_by(Participant) |>
-  select(Participant, Age, Sex, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
+  select(Participant, Age, Sex, Sexual_Orientation, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
   slice(1) |>
@@
 
+p5 <- plot_waffle(dfsub, "Sexual_Orientation")
+
 p5 <- plot_waffle(dfsub, "Education") +
@@
 ```
+
+## Results
+
+### Manipulation Check
+
+```{r message=FALSE, warning=FALSE}
+df |> 
+  ggplot(aes(x = Real, y = Participant, fill=Participant)) +
+  ggdist::stat_slab(scale=2, slab_alpha = 0.9) + 
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  scale_y_discrete(expand = c(1, 1)) +
+  scale_x_continuous(limits = c(-100, 100), 
+                     expand = c(0.01, 0.01),
+                     breaks = c(-100, 0, 100),
+                     label = c("Fake", "0", "Real")) +
+  scale_fill_viridis_d() +
+  labs(x = "Simulation Monitoring", y = "Participants", title= "Distribution of Reality Judgments") +
+  guides(fill = "none") +
+  see::theme_modern() +
+  theme(axis.text.y = element_blank(),
+        plot.title = element_text(face = "bold", hjust = 0.5))
+```
+
+### Simulation Monitoring

### 2022-08-25 preprocessing.R

@@ -58,6 +58,9 @@ preprocess_raw <- function(file) {
     Similar = answers$Similarity
   )
 
+  # Format sexual orientation
+  df$Sexual_Orientation <- ifelse(df$Sexual_Orientation == "Other", jsonlite::fromJSON(dem[4])$sexual_orientation, df$Sexual_Orientation)
+
   # Format education
   df$Education <- gsub("University (", "", df$Education, fixed = TRUE)
   df$Education <- gsub(")", "", df$Education, fixed = TRUE)
@@ -142,7 +145,7 @@ preprocess_raw <- function(file) {
   # Attention checks
   df$Attention_Check1 <- sias$Attention_Check_1
   df$Attention_Check2 <- ffni$Attention_Check_2
-  df$Attention_Check3 <- scc$Attention_Check_3
+  df$Attention_Check3 <- 100 - scc$Attention_Check_3  # Reversed
 
   # Combine with Norms data
   norms <- read.csv("experiment/stimuli/AMFD_norms.csv")

### 2022-08-25 analysis.Rmd
update

@@
 #   )
-
 ```
@@
 dfsub$Cor_Attractive <- NA
-for(participant in dfsub$Participant) {
+for (participant in dfsub$Participant) {
   dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
@@
 ```{r message=FALSE, warning=FALSE}
-data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm=TRUE))) |> 
+data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
   rbind(dfsub) |>
@@
   kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
+```
+
+### Manipulation Check
+
+```{r message=FALSE, warning=FALSE}
+df |>
+  mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
+    summarize(Real = mean(Real)) |>
+    ungroup() |>
+    arrange(Real) |>
+    pull(Participant))) |>
+  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
+  ggdist::stat_slab(scale = 2, slab_alpha = 0.9) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  scale_y_discrete(expand = c(1, 1)) +
+  scale_x_continuous(
+    limits = c(-100, 100),
+    expand = c(0.01, 0.01),
+    breaks = c(-100, 0, 100),
+    label = c("Fake", "0", "Real")
+  ) +
+  scale_fill_viridis_d() +
+  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
+  guides(fill = "none") +
+  see::theme_modern() +
+  theme(
+    axis.text.y = element_blank(),
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  )
 ```
@@
 
-### Manipulation Check
+### Reality and Attractiveness
 
 ```{r message=FALSE, warning=FALSE}
-df |> 
-  ggplot(aes(x = Real, y = Participant, fill=Participant)) +
-  ggdist::stat_slab(scale=2, slab_alpha = 0.9) + 
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  scale_y_discrete(expand = c(1, 1)) +
-  scale_x_continuous(limits = c(-100, 100), 
-                     expand = c(0.01, 0.01),
-                     breaks = c(-100, 0, 100),
-                     label = c("Fake", "0", "Real")) +
-  scale_fill_viridis_d() +
-  labs(x = "Simulation Monitoring", y = "Participants", title= "Distribution of Reality Judgments") +
-  guides(fill = "none") +
-  see::theme_modern() +
-  theme(axis.text.y = element_blank(),
-        plot.title = element_text(face = "bold", hjust = 0.5))
+model <- glmmTMB::glmmTMB(Real ~ Attractive + (1|Participant), data = df)
 ```
 
-### Simulation Monitoring
+```{r message=FALSE, warning=FALSE}
+pred <- estimate_relation(model, at = c("Attractive"))
+
+df |> 
+  ggplot(aes(x = Attractive, y = Real)) +
+  geom_point() +
+  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
+  geom_line(data = pred, aes(y = Predicted))
+```

### 2022-08-25 preprocessing.R

@@ -50,12 +50,12 @@ preprocess_raw <- function(file) {
     Trial = as.numeric(trials$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", trials$stimulus)),
     RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
-    Real = datawizard::change_scale(answers$perceived_realness, to = c(-100, 100), range = c(0, 100)),
-    Attractive = answers$Attractiveness,
-    Approachable = answers$Approachability,
-    Trustworthy = answers$Trustworthiness,
-    Familiar = answers$Familiarity,
-    Similar = answers$Similarity
+    Real = datawizard::change_scale(answers$perceived_realness, to = c(-0.9999, 0.9999), range = c(0, 100)),
+    Attractive = datawizard::change_scale(answers$Attractiveness, to = c(0, 1), range = c(0, 100)),
+    Approachable = datawizard::change_scale(answers$Approachability, to = c(0, 1), range = c(0, 100)),
+    Trustworthy = datawizard::change_scale(answers$Trustworthiness, to = c(0, 1), range = c(0, 100)),
+    Familiar = datawizard::change_scale(answers$Familiarity, to = c(0, 1), range = c(0, 100)),
+    Similar = datawizard::change_scale(answers$Similarity, to = c(0, 1), range = c(0, 100))
   )
 
   # Format sexual orientation

### 2022-08-25 analysis.Rmd
remove rawdata

@@
   scale_x_continuous(
-    limits = c(-100, 100),
+    limits = c(-1, 1),
     expand = c(0.01, 0.01),
-    breaks = c(-100, 0, 100),
+    breaks = c(-1, 0, 1),
     label = c("Fake", "0", "Real")
@@
   ggplot(aes(x = Attractive, y = Real)) +
+  ggside::geom_xsidedensity(fill = "#F44336", color="white") +
+  ggside::geom_ysidedensity(fill = "#9C27B0", color="white") +
+  ggside::theme_ggside_void() +
+  geom_hline(yintercept = 0, linetype = "dotted") +
   geom_point() +

### 2022-08-25 preprocessing.R
add rt for scales

@@ -1,7 +1,7 @@
 unnest <- function(file, scale) {
   data <- file |>
-    filter(screen == scale) |>
-    select(participant_id, response) |>
+    dplyr::filter(screen == scale) |>
+    dplyr::select(participant_id, response) |>
     jsontools::json_unnest_wider(col = "response")
   data
 }
@@ -18,7 +18,7 @@ preprocess_raw <- function(file) {
 
   # Demographics
   dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
-
+  
   # Trials
   trials <- data[data$screen == "stimuli", ]
   answers <- unnest(data, "questionnaire")
@@ -80,14 +80,19 @@ preprocess_raw <- function(file) {
   df$IPIP6_Openness <- rowMeans(ipip6[grepl("Openness", names(ipip6))])
   df$IPIP6_HonestyHumility <- rowMeans(ipip6[grepl("HonestyHumility", names(ipip6))])
   df$IPIP6_Agreeableness <- rowMeans(ipip6[grepl("Agreeableness", names(ipip6))])
+  df$IPIP6_RT <- as.numeric(data[data$screen =='IPIP6', 'rt'])
+  
 
   # SIAS + Attention Check 1
   sias <- unnest(data, "SIAS")
   df$Social_Anxiety <- rowMeans(sias[grepl("SIAS", names(sias))])
-
+  df$SIAS_RT <- as.numeric(data[data$screen =='SIAS', 'rt'])
+  
   # SPS
   sps <- unnest(data, "SPS")
-  data$Social_Phobia <- rowMeans(sps[grepl("Social_Phobia", names(sps))])
+  df$Social_Phobia <- rowMeans(sps[grepl("Social_Phobia", names(sps))])
+  df$SocialPhobia_RT <- as.numeric(data[data$screen =='SPS', 'rt'])
+  
 
   # GAAIS
   gaais <- unnest(data, "GAAIS")
@@ -102,6 +107,8 @@ preprocess_raw <- function(file) {
   df$AI_8_Exciting <- gaais$GAAIS_8
   df$AI_9_Applications <- gaais$GAAIS_9
   df$AI_10_FaceErrors <- gaais$GAAIS_10
+  df$AI_RT <- as.numeric(data[data$screen =='GAAIS', 'rt'])
+  
 
 
 
@@ -122,12 +129,16 @@ preprocess_raw <- function(file) {
[…]

### 2022-08-29 analysis.Rmd
format duration

@@
   group_by(Participant) |>
-  select(Participant, starts_with("Attention")) |>
+  select(Participant, starts_with("Attention"), starts_with("Duration")) |>
   slice(1) |>
   ungroup() |>
+  rowwise() |> 
   mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |> 
+  ungroup() |> 
   arrange(Attention_Check)
@@
 ```{r message=FALSE, warning=FALSE}
-
+df 
 ```
@@
   rbind(dfsub) |>
+  mutate(Attention_Check = paste0(
+    insight::format_value(Attention_Check, 1), 
+    " (", insight::format_value(Attention_Check1, 0), 
+    ", ",
+    insight::format_value(Attention_Check2, 0), 
+    ", ",
+    insight::format_value(Attention_Check3, 0),
+    ")")) |> 
+  select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |> 
+  datawizard::data_relocate("Attention_Check", 2) |> 
   knitr::kable() |>

### 2022-08-29 preprocessing.R

@@ -18,7 +18,7 @@ preprocess_raw <- function(file) {
 
   # Demographics
   dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
-  
+
   # Trials
   trials <- data[data$screen == "stimuli", ]
   answers <- unnest(data, "questionnaire")
@@ -39,7 +39,8 @@ preprocess_raw <- function(file) {
     Ethnicity = tools::toTitleCase(jsonlite::fromJSON(dem[1])$ethnicity),
     Date = ifelse(is.null(info$date), NA, info$date),
     Time = ifelse(is.null(info$time), NA, info$time),
-    # Duration = as.numeric(file[file$screen == "end_screen", "time_elapsed"]) / 1000 / 60,
+    Duration_Questionnaire = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS', 'SCC'), 'rt'])) / 1000 / 60,
+    Duration_Task = sum(as.numeric(data[data$screen == "questionnaire", "rt"])) / 1000 / 60,
     Screen_Resolution = paste0(info$screen_width, "x", info$screen_height),
     Screen_Size = (as.numeric(info$screen_width) / 1000) * (as.numeric(info$screen_height) / 1000),
     Screen_Refresh = info$vsync_rate,
@@ -80,19 +81,16 @@ preprocess_raw <- function(file) {
   df$IPIP6_Openness <- rowMeans(ipip6[grepl("Openness", names(ipip6))])
   df$IPIP6_HonestyHumility <- rowMeans(ipip6[grepl("HonestyHumility", names(ipip6))])
   df$IPIP6_Agreeableness <- rowMeans(ipip6[grepl("Agreeableness", names(ipip6))])
-  df$IPIP6_RT <- as.numeric(data[data$screen =='IPIP6', 'rt'])
-  
+
 
   # SIAS + Attention Check 1
   sias <- unnest(data, "SIAS")
   df$Social_Anxiety <- rowMeans(sias[grepl("SIAS", names(sias))])
-  df$SIAS_RT <- as.numeric(data[data$screen =='SIAS', 'rt'])
-  
+
   # SPS
   sps <- unnest(data, "SPS")
[…]

### 2022-08-30 analysis.Rmd
edit

@@
 
-### Attention Checks
+### Attention Checks and Duration
 
@@
 
-### Duration
-
-```{r message=FALSE, warning=FALSE}
-df 
-```
-
 ### Ratings
@@
 ```
+
+### Summary
 
@@
 
-### Manipulation Check
+```{r message=FALSE, warning=FALSE}
+p_att <- dfsub |>
+  select(Participant, starts_with("Att")) |> 
+  pivot_longer(-Participant) |> 
+  # mutate(name = str_remove(name, "Cor_")) |> 
+  ggplot(aes(x = Participant, y = value)) +
+  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
+  scale_y_continuous(expand = c(0, 0)) +
+  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
+  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
+  see::theme_modern() +
+  theme(axis.text.x = element_text(angle = 45, hjust=1),
+        legend.position = "top") +
+  labs(y = "Score", fill="") +
+  guides(color = "none") +
+  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0))
 
-```{r message=FALSE, warning=FALSE}
-df |>
-  mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
-    summarize(Real = mean(Real)) |>
-    ungroup() |>
-    arrange(Real) |>
-    pull(Participant))) |>
-  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
-  ggdist::stat_slab(scale = 2, slab_alpha = 0.9) +
-  geom_vline(xintercept = 0, linetype = "dotted") +
-  scale_y_discrete(expand = c(1, 1)) +
-  scale_x_continuous(
-    limits = c(-1, 1),
-    expand = c(0.01, 0.01),
-    breaks = c(-1, 0, 1),
-    label = c("Fake", "0", "Real")
-  ) +
-  scale_fill_viridis_d() +
-  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
-  guides(fill = "none") +
+p_time <- dfsub |>
+  select(Participant, starts_with("Duration")) |> 
+  pivot_longer(-Participant) |> 
+  mutate(name = str_remove(name, "Duration_")) |> 
+  ggplot(aes(x = Participant, y = value)) +
+  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
+  scale_y_continuous(expand = c(0, 0)) +
+  scale_fill_manual(values = c("#4CAF50", "#FF9800")) +
+  scale_color_manual(values = c("#4CAF50", "#FF9800")) +
   see::theme_modern() +
-  theme(
-    axis.text.y = element_blank(),
-    plot.title = element_text(face = "bold", hjust = 0.5)
-  )
+  theme(axis.text.x = element_text(angle = 45, hjust=1),
+        legend.position = "top") +
+  labs(y = "Duration (min)", fill="") +
+  guides(color = "none") +
+  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0))
+
+p_cor <- dfsub |>
+  select(Participant, starts_with("Cor")) |> 
+  pivot_longer(-Participant) |> 
+  mutate(name = str_remove(name, "Cor_")) |> 
+  ggplot(aes(x = Participant, y = value)) +
+  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
+  scale_y_continuous(expand = c(0, 0)) +
+  scale_fill_manual(values = c("#F44336", "#9C27B0")) +
+  scale_color_manual(values = c("#F44336", "#9C27B0")) +
+  see::theme_modern() +
+  theme(axis.text.x = element_text(angle = 45, hjust=1),
+        legend.position = "top") +
+  labs(y = "Correlation", fill="") +
+  guides(color = "none") +
+  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0))
+
+(p_att + theme(axis.text.x = element_blank())) / 
+  (p_time + theme(axis.text.x = element_blank())) /
+  (p_cor)
 ```
@@
     geom_density(fill = fill) +
-    geom_vline(xintercept = mean(dfsub[[what]]), color = "red", linetype = "dashed") +
     scale_x_continuous(expand = c(0, 0)) +
@@
 
-plot_waffle <- function(dfsub, what = "Nationality", title = what) {
-  ggwaffle::waffle_iron(dfsub, what) |>
-    # mutate(label = emojifont::fontawesome('fa-person')) |>
-    ggplot(aes(x, y, fill = group)) +
-    ggwaffle::geom_waffle() +
+plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
+  library(emojifont)
+  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
+    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
+    # mutate(label = emojifont::emoji('smiley')) |>
+    ggplot(aes(x, y)) +
+    geom_point(aes(color = group), shape = "square", size=size) +
+    # ggwaffle::geom_waffle(color = "white") +
+    # geom_point() +
+    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
+    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
     coord_equal() +
     ggtitle(title) +
-    labs(fill = "") +
+    labs(fill = "", color = "") +
+    # scale_x_continuous(expand = c(0, 0)) +
+    # scale_y_continuous(expand = c(0, 0)) +
     theme_void() +
+    # ggwaffle::theme_waffle() +
     theme(plot.title = element_text(face = "bold", hjust = 0.5))
@@
 p4 <- plot_waffle(dfsub, "Sex") +
-  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))
+  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))
 
@@
 
-(p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
+# (p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
 ```
@@
 
+### Manipulation Check
+
+```{r message=FALSE, warning=FALSE}
+df |>
+  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
+  #   summarize(Real = mean(Real)) |>
+  #   ungroup() |>
+  #   arrange(Real) |>
+  #   pull(Participant))) |>
+  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
+  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
+  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
+  geom_vline(xintercept = 0.5, linetype = "dotted") +
+  scale_y_discrete(expand = c(1, 1)) +
+  scale_x_continuous(
+    limits = c(0, 1),
+    expand = c(0, 0),
+    breaks = c(0, 0.5, 1),
+    label = c("Fake", "0", "Real")
+  ) +
+  scale_fill_viridis_d() +
+  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
+  guides(fill = "none") +
+  see::theme_modern() +
+  theme(
+    # axis.text.y = element_blank(),
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  )
+```
+
+### Colinearity
+
+```{r message=FALSE, warning=FALSE}
+IVs <- c("Attractive", "Trustworthy", "Approachable", "Familiar", "Similar")
+
+preds <- data.frame()
+dats <- data.frame()
+for(x in IVs) {
+  for(y in IVs) {
+    if(x == y) next
+    print(paste(y, "~", x))
+    model <- glmmTMB::glmmTMB(as.formula(
+      paste(y, "~", x, " * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")), 
+      data = df, 
+      family=glmmTMB::beta_family()
+      )
+
+    # model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, 
+    #                     random = list(Participant=~1, Stimulus=~1), 
+    #                     data = df, 
+    #                     family=mgcv::betar())
+
+    pred <- estimate_relation(model, at=c(x, "Stimulus_SameSex"), length=20)
+    pred$y <- y
+    pred <- data_rename(pred, x, "Score")
+    pred$x <- x
+    preds <- rbind(preds, pred)
+
+    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x=x, y=y))
+  }
+}
+
+dats <- mutate(dats, x = fct_relevel(x, IVs), y = fct_relevel(y, IVs))
+preds <- mutate(preds, x = fct_relevel(x, IVs), y = fct_relevel(y, IVs))
+```
+
+```{r message=FALSE, warning=FALSE}
+dats |> 
+  ggplot(aes(x = Score, y = Predicted)) +
+  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  geom_ribbon(data=preds, aes(ymin = CI_low, ymax = CI_high, group=Stimulus_SameSex), alpha = 0.3) +
+  geom_line(data=preds, aes(color=Stimulus_SameSex)) +
+  scale_fill_gradientn(colors=c("white", "#FF9800", "#F44336"), guide="none") +
+  scale_x_continuous(expand=c(0, 0)) +
+  scale_y_continuous(expand=c(0, 0)) +
+  facet_grid(y~x, switch = "both") +
+  theme_modern() +
+  labs(title = "Collinearity in the Stimuli Ratings") +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_blank(),
+    strip.placement = "outside",
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    plot.title = element_text(face="bold", hjust=0.5)
+  ) +
+  ggside::geom_xsidedensity(fill = "grey", color="white") +
+  ggside::geom_ysidedensity(fill = "grey", color="white") +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  ggside::ggside(collapse = "all") 
+```
+
 ### Reality and Attractiveness
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB::glmmTMB(Real ~ Attractive + (1|Participant), data = df)
+model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) + poly(Trustworthy, 2) +
+                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
+model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())
+
+parameters::parameters(model)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-pred <- estimate_relation(model, at = c("Attractive"))
+pred <- estimate_relation(model, at = c("Attractive"), length=20)
 
@@
   ggplot(aes(x = Attractive, y = Real)) +
-  ggside::geom_xsidedensity(fill = "#F44336", color="white") +
-  ggside::geom_ysidedensity(fill = "#9C27B0", color="white") +
+  ggside::geom_xsidedensity(fill = "grey", color="white") +
+  ggside::geom_ysidedensity(fill = "grey", color="white") +
   ggside::theme_ggside_void() +
-  geom_hline(yintercept = 0, linetype = "dotted") +
-  geom_point() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  geom_hline(yintercept = 0.5, linetype = "dotted") +
+  geom_point2(alpha=0.25, size=4, color="white") +
   geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
-  geom_line(data = pred, aes(y = Predicted))
+  geom_line(data = pred, aes(y = Predicted)) +
+  scale_fill_viridis_c(guide="none") +
+  scale_x_continuous(expand=c(0, 0)) +
+  scale_y_continuous(expand=c(0, 0))
+
+pred <- estimate_relation(model, at = c("Trustworthy"), length=20)
+
+df |> 
+  ggplot(aes(x = Trustworthy, y = Real)) +
+  ggside::geom_xsidedensity(fill = "grey", color="white") +
+  ggside::geom_ysidedensity(fill = "grey", color="white") +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  geom_hline(yintercept = 0.5, linetype = "dotted") +
+  geom_point2(alpha=0.25, size=4, color="white") +
+  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
+  geom_line(data = pred, aes(y = Predicted)) +
+  scale_fill_viridis_c(guide="none") +
+  scale_x_continuous(expand=c(0, 0)) +
+  scale_y_continuous(expand=c(0, 0))
 ```

### 2022-08-30 preprocessing.R

@@ -39,7 +39,7 @@ preprocess_raw <- function(file) {
     Ethnicity = tools::toTitleCase(jsonlite::fromJSON(dem[1])$ethnicity),
     Date = ifelse(is.null(info$date), NA, info$date),
     Time = ifelse(is.null(info$time), NA, info$time),
-    Duration_Questionnaire = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS', 'SCC'), 'rt'])) / 1000 / 60,
+    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS', 'SCC'), 'rt'])) / 1000 / 60,
     Duration_Task = sum(as.numeric(data[data$screen == "questionnaire", "rt"])) / 1000 / 60,
     Screen_Resolution = paste0(info$screen_width, "x", info$screen_height),
     Screen_Size = (as.numeric(info$screen_width) / 1000) * (as.numeric(info$screen_height) / 1000),
@@ -51,12 +51,12 @@ preprocess_raw <- function(file) {
     Trial = as.numeric(trials$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", trials$stimulus)),
     RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
-    Real = datawizard::change_scale(answers$perceived_realness, to = c(-0.9999, 0.9999), range = c(0, 100)),
-    Attractive = datawizard::change_scale(answers$Attractiveness, to = c(0, 1), range = c(0, 100)),
-    Approachable = datawizard::change_scale(answers$Approachability, to = c(0, 1), range = c(0, 100)),
-    Trustworthy = datawizard::change_scale(answers$Trustworthiness, to = c(0, 1), range = c(0, 100)),
-    Familiar = datawizard::change_scale(answers$Familiarity, to = c(0, 1), range = c(0, 100)),
-    Similar = datawizard::change_scale(answers$Similarity, to = c(0, 1), range = c(0, 100))
+    Real = datawizard::change_scale(answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 100)),
[…]

### 2022-08-30 preprocessing.R
add ISI

@@ -50,7 +50,8 @@ preprocess_raw <- function(file) {
     Device_OS = info$os,
     Trial = as.numeric(trials$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", trials$stimulus)),
-    RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
+    RT = as.numeric(data[data$screen == "questionnaire", "rt"]) / 1000,
+    ISI = as.numeric(data[data$screen == "fixation", "trial_duration"]) /1000,
     Real = datawizard::change_scale(answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 100)),
     Attractive = datawizard::change_scale(answers$Attractiveness, to = c(0.0001, 0.9999), range = c(0, 100)),
     Approachable = datawizard::change_scale(answers$Approachability, to = c(0.0001, 0.9999), range = c(0, 100)),

### 2022-08-30 experiment/study2/parameters.js
updates for study2

@@ -1,0 +1,631 @@
+/* Measures */ //===============================================================
+// Scale Labels
+var scale1 = ["Not at All", "Extremely"]
+var scale2 = ["Strongly Disagree", "Strongly Agree"]
+
+// Oosterhof and Todorov (2008) - 9 point scale (Not at all to Extremely)
+var items = [
+    //"The face looked real to me",
+    "<b>Assuming the person you saw was real...</b> <br><br>Would you find this person attractive?",
+    // "Would you find this person approachable?",
+    "Would you find this person trustworthy?",
+    "How much does this person remind you of someone you know?",
+    // "How much does this face look like yours?",
+    // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
+    // "How dominant is the face you saw?",
+    //"How musculine/feminine is the face you saw?",
+    // "How emotionally stable is the face you saw?",
+    // "How mean is the face you saw?",
+    // "How boring is the face you saw?",
+    // "How intelligent is the face you saw?",
+    // "How caring is the face you saw?",
+    // "How egoistic is the face you saw?",
+    // "How responsible is the face you saw?",
+]
+
+var dimensions = [
+    //"Real",
+    "Attractiveness",
+    // "Approachability",
+    "Trustworthiness",
+    "Familiarity",   // Familiarity (van vugt et al., 2010)
+    // "Similarity"
+]
+
+// var items2 = [
+//     "<b>Approachable</b>",
+//     "<b>Familiar</b>",
+//     "<b>Trustworthy</b>",
+//     "<b>Sociable</b>",
+//     "<b>Similar</b>"
+// ]
+
+// var dimensions2 = [
+//     "Approachability",
+//     "Familiarity",   // Familiarity (van vugt et al., 2010)
+//     "Trustworthiness",
+//     "Sociability",
+//     "Similarity"  //Similarity (Van Vugt et al., 2006)
+// ]
+
+// Mini IPIP scale
+var IPIP = [
+    "<b>I am the life of the party</b><br>",
+    "<b>I sympathize with others' feelings</b><br>",
+    "<b>I get chores done right away</b><br>",
+    "<b>I have frequent mood swings</b><br>",
+    "<b>I have a vivid imagination</b><br>",
+    "<b>I feel entitled to more of everything</b><br>",
+    "<b>I do not talk a lot</b><br>",
[…]

### 2022-08-30 analysis.Rmd
minor

@@
 
-df <- read.csv("data/data.csv")
-# |>
-#   mutate(
-#     Date = lubridate::dmy(Date),
-#     Participant = fct_reorder(Participant, Date),
-#     Screen_Refresh = as.character(Screen_Refresh),
-#     Illusion_Side = as.factor(Illusion_Side),
-#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
-#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
-#     Block = as.factor(Block),
+df <- read.csv("data/data.csv") |>
+  mutate(
+    Date = lubridate::dmy(Date),
+    Participant = fct_reorder(Participant, Date),
+    Screen_Refresh = as.character(Screen_Refresh)
 #     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
-#   )
+  )
+
+# Create individual scores for Simulation Moniroting
+df <- df |> 
+  mutate(Belief = ifelse(SimulationMonitoring >= 0, "Real", "Fake")) |> 
+  group_by(Participant, Belief) |> 
+  summarise(Confidence = mean(abs(SimulationMonitoring))) |> 
+  pivot_wider(names_from = "Belief", values_from = "Confidence") |> 
+  transmute(Participant, ConfidenceReality=Real, ConfidenceSimulation=Fake) |> 
+  merge(df, by="Participant")
 ```
@@
 
+#### Real / Fake
+
 ```{r message=FALSE, warning=FALSE}
@@
     breaks = c(0, 0.5, 1),
-    label = c("Fake", "0", "Real")
+    label = c("Fake", "", "Real")
   ) +
@@
 
-### Colinearity
+#### Colinearity
 
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) + poly(Trustworthy, 2) +
+model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) +
                             (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
@@
   scale_y_continuous(expand=c(0, 0))
+```
 
+### Reality and Trustworthiness
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB::glmmTMB(Real ~ poly(Trustworthy, 2) +
+                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
+
+parameters::parameters(model)
+```
+
+```{r message=FALSE, warning=FALSE}
 pred <- estimate_relation(model, at = c("Trustworthy"), length=20)
@@
 ```
+
+### Reality and Familiarity
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB::glmmTMB(Real ~ poly(Familiar, 2) +
+                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
+model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())
+
+parameters::parameters(model)
+```
+
+```{r message=FALSE, warning=FALSE}
+pred <- estimate_relation(model, at = c("Familiar"), length=20)
+
+df |> 
+  ggplot(aes(x = Familiar, y = Real)) +
+  ggside::geom_xsidedensity(fill = "grey", color="white") +
+  ggside::geom_ysidedensity(fill = "grey", color="white") +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  geom_hline(yintercept = 0.5, linetype = "dotted") +
+  geom_point2(alpha=0.25, size=4, color="white") +
+  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
+  geom_line(data = pred, aes(y = Predicted)) +
+  scale_fill_viridis_c(guide="none") +
+  scale_x_continuous(expand=c(0, 0)) +
+  scale_y_continuous(expand=c(0, 0))
+```

### 2022-08-30 preprocessing.R

@@ -51,6 +51,7 @@ preprocess_raw <- function(file) {
     Trial = as.numeric(trials$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", trials$stimulus)),
     RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
+    SimulationMonitoring = datawizard::change_scale(answers$perceived_realness, to = c(-1, 1), range = c(0, 100)),
     Real = datawizard::change_scale(answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 100)),
     Attractive = datawizard::change_scale(answers$Attractiveness, to = c(0.0001, 0.9999), range = c(0, 100)),
     Approachable = datawizard::change_scale(answers$Approachability, to = c(0.0001, 0.9999), range = c(0, 100)),

### 2022-08-31 experiment/parameters.js
put old expe in pilot folder

@@ -7,10 +7,10 @@ var scale2 = ["Strongly Disagree", "Strongly Agree"]
 var items = [
     //"The face looked real to me",
     "<b>Assuming the person you saw was real...</b> <br><br>Would you find this person attractive?",
-    "Would you find this person approachable?",
+    // "Would you find this person approachable?",
     "Would you find this person trustworthy?",
     "How much does this person remind you of someone you know?",
-    "How much does this face look like yours?",
+    // "How much does this face look like yours?",
     // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
     // "How dominant is the face you saw?",
     //"How musculine/feminine is the face you saw?",
@@ -26,10 +26,10 @@ var items = [
 var dimensions = [
     //"Real",
     "Attractiveness",
-    "Approachability",
+    // "Approachability",
     "Trustworthiness",
     "Familiarity",   // Familiarity (van vugt et al., 2010)
-    "Similarity"
+    // "Similarity"
 ]
 
 // var items2 = [
@@ -112,12 +112,12 @@ var SIAS_SF = [
     "<b>I feel tense if I am alone with just one person </b><br>",
     "<b>I have difficulty talking with other people </b><br>",
     "<b>I find it difficult to disagree with another's point of view </b><br>"
-    ]
+]
 
 var SIAS_dim = [
     "SIAS_1",
     "SIAS_2",
-   // "Attention_Check_1",
+    // "Attention_Check_1",
     "SIAS_3",
     "SIAS_4",
     "SIAS_5",
@@ -125,7 +125,7 @@ var SIAS_dim = [
 ]
 
 // Social Phobia Scale (SPS)
-var SPS_SF =[
+var SPS_SF = [
     "<b>I get nervous that people are staring at me as I walk down the street </b><br>",
     "<b>I worry about shaking or trembling when I'm watched by other people </b><br>",
     "<b>I would get tense if I had to sit facing other people on a bus or a train </b><br>",
@@ -156,7 +156,7 @@ var FFNI_BF = [
     "<b>I tend to take charge of most situations</b><br>",
     "<b>I often think that others aren't telling me the whole truth</b><br>",
     "<b>I believe I am entitled to special accommodations</b><br>",
-//    "<b>Please select 'Strongly Agree' to demonstrate your attention</b><br>",
[…]

### 2022-08-31 experiment/pilot/parameters.js

@@ -7,10 +7,10 @@ var scale2 = ["Strongly Disagree", "Strongly Agree"]
 var items = [
     //"The face looked real to me",
     "<b>Assuming the person you saw was real...</b> <br><br>Would you find this person attractive?",
-    // "Would you find this person approachable?",
+    "Would you find this person approachable?",
     "Would you find this person trustworthy?",
     "How much does this person remind you of someone you know?",
-    // "How much does this face look like yours?",
+    "How much does this face look like yours?",
     // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
     // "How dominant is the face you saw?",
     //"How musculine/feminine is the face you saw?",
@@ -26,10 +26,10 @@ var items = [
 var dimensions = [
     //"Real",
     "Attractiveness",
-    // "Approachability",
+    "Approachability",
     "Trustworthiness",
     "Familiarity",   // Familiarity (van vugt et al., 2010)
-    // "Similarity"
+    "Similarity"
 ]
 
 // var items2 = [
@@ -112,12 +112,12 @@ var SIAS_SF = [
     "<b>I feel tense if I am alone with just one person </b><br>",
     "<b>I have difficulty talking with other people </b><br>",
     "<b>I find it difficult to disagree with another's point of view </b><br>"
-]
+    ]
 
 var SIAS_dim = [
     "SIAS_1",
     "SIAS_2",
-    // "Attention_Check_1",
+   // "Attention_Check_1",
     "SIAS_3",
     "SIAS_4",
     "SIAS_5",
@@ -125,7 +125,7 @@ var SIAS_dim = [
 ]
 
 // Social Phobia Scale (SPS)
-var SPS_SF = [
+var SPS_SF =[
     "<b>I get nervous that people are staring at me as I walk down the street </b><br>",
     "<b>I worry about shaking or trembling when I'm watched by other people </b><br>",
     "<b>I would get tense if I had to sit facing other people on a bus or a train </b><br>",
@@ -156,7 +156,7 @@ var FFNI_BF = [
     "<b>I tend to take charge of most situations</b><br>",
     "<b>I often think that others aren't telling me the whole truth</b><br>",
     "<b>I believe I am entitled to special accommodations</b><br>",
-    //    "<b>Please select 'Strongly Agree' to demonstrate your attention</b><br>",
[…]

### 2022-08-31 experiment/parameters.js
update questions

@@ -6,9 +6,9 @@ var scale2 = ["Strongly Disagree", "Strongly Agree"]
 // Oosterhof and Todorov (2008) - 9 point scale (Not at all to Extremely)
 var items = [
     //"The face looked real to me",
-    "<b>Assuming the person you saw was real...</b> <br><br>Would you find this person attractive?",
+    "How attractive do you find this person?",
     // "Would you find this person approachable?",
-    "Would you find this person trustworthy?",
+    "How much would you trust this person?",
     "How much does this person remind you of someone you know?",
     // "How much does this face look like yours?",
     // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)

### 2022-08-31 experiment/pilot/old_preprocessing.R
update preprocessing

@@ -7,26 +7,25 @@ unnest <- function(file, scale) {
 }
 
 preprocess_raw <- function(file) {
-  
+
   data <- read.csv(file)
-  
+
   # Preprocess
   if (!"end_screen" %in% data$screen) {
     print(paste0("Warning: Incomplete data for ", file))
     return(data.frame())
   }
-  
+
   # Demographics
   dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
-  
+
   # Trials
   trials <- data[data$screen == "stimuli", ]
   answers <- unnest(data, "questionnaire")
-  realness_answers <- unnest(data, "perceived_realness")
-  
+
   # Info
   info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
-  
+
   df <- data.frame(
     Participant = trials$participant_id,
     Age = as.numeric(jsonlite::fromJSON(dem[1])$age),
@@ -40,9 +39,8 @@ preprocess_raw <- function(file) {
     Ethnicity = tools::toTitleCase(jsonlite::fromJSON(dem[1])$ethnicity),
     Date = ifelse(is.null(info$date), NA, info$date),
     Time = ifelse(is.null(info$time), NA, info$time),
-    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS'), 'rt'])) / 1000 / 60,
-    Duration_Task = sum(as.numeric(data[data$screen =="questionnaire", "rt"])) /1000 /60,
-    Duration_Realness = sum(as.numeric(data[data$screen == "perceived_realness", "rt"])) / 1000 / 60,
+    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS', 'SCC'), 'rt'])) / 1000 / 60,
+    Duration_Task = sum(as.numeric(data[data$screen == "questionnaire", "rt"])) / 1000 / 60,
     Screen_Resolution = paste0(info$screen_width, "x", info$screen_height),
     Screen_Size = (as.numeric(info$screen_width) / 1000) * (as.numeric(info$screen_height) / 1000),
     Screen_Refresh = info$vsync_rate,
[…]

### 2022-08-31 experiment/pilot/old_preprocessing.R
Initial commit

@@ -1,191 +1,0 @@
-unnest <- function(file, scale) {
-  data <- file |>
-    dplyr::filter(screen == scale) |>
-    dplyr::select(participant_id, response) |>
-    jsontools::json_unnest_wider(col = "response")
-  data
-}
-
-preprocess_raw <- function(file) {
-
-  data <- read.csv(file)
-
-  # Preprocess
-  if (!"end_screen" %in% data$screen) {
-    print(paste0("Warning: Incomplete data for ", file))
-    return(data.frame())
-  }
-
-  # Demographics
-  dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
-
-  # Trials
-  trials <- data[data$screen == "stimuli", ]
-  answers <- unnest(data, "questionnaire")
-
-  # Info
-  info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
-
-  df <- data.frame(
-    Participant = trials$participant_id,
-    Age = as.numeric(jsonlite::fromJSON(dem[1])$age),
-    Sex = jsonlite::fromJSON(dem[2])$sex,
-    Sexual_Orientation = jsonlite::fromJSON(dem[3])$sexual_orientation,
-    Religion = jsonlite::fromJSON(dem[5])$religion,
-    Religion_Spirituality = as.numeric(jsonlite::fromJSON(dem[7])$religiosity),
-    Religion_Activity = as.numeric(jsonlite::fromJSON(dem[7])$religious_activity),
-    Education = jsonlite::fromJSON(dem[2])$education,
-    Nationality = tools::toTitleCase(jsonlite::fromJSON(dem[1])$nationality),
-    Ethnicity = tools::toTitleCase(jsonlite::fromJSON(dem[1])$ethnicity),
-    Date = ifelse(is.null(info$date), NA, info$date),
-    Time = ifelse(is.null(info$time), NA, info$time),
-    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS', 'SCC'), 'rt'])) / 1000 / 60,
-    Duration_Task = sum(as.numeric(data[data$screen == "questionnaire", "rt"])) / 1000 / 60,
[…]

### 2022-08-31 experiment/pilot/parameters.js

@@ -1,631 +1,0 @@
-/* Measures */ //===============================================================
-// Scale Labels
-var scale1 = ["Not at All", "Extremely"]
-var scale2 = ["Strongly Disagree", "Strongly Agree"]
-
-// Oosterhof and Todorov (2008) - 9 point scale (Not at all to Extremely)
-var items = [
-    //"The face looked real to me",
-    "<b>Assuming the person you saw was real...</b> <br><br>Would you find this person attractive?",
-    "Would you find this person approachable?",
-    "Would you find this person trustworthy?",
-    "How much does this person remind you of someone you know?",
-    "How much does this face look like yours?",
-    // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
-    // "How dominant is the face you saw?",
-    //"How musculine/feminine is the face you saw?",
-    // "How emotionally stable is the face you saw?",
-    // "How mean is the face you saw?",
-    // "How boring is the face you saw?",
-    // "How intelligent is the face you saw?",
-    // "How caring is the face you saw?",
-    // "How egoistic is the face you saw?",
-    // "How responsible is the face you saw?",
-]
-
-var dimensions = [
-    //"Real",
-    "Attractiveness",
-    "Approachability",
-    "Trustworthiness",
-    "Familiarity",   // Familiarity (van vugt et al., 2010)
-    "Similarity"
-]
-
-// var items2 = [
-//     "<b>Approachable</b>",
-//     "<b>Familiar</b>",
-//     "<b>Trustworthy</b>",
-//     "<b>Sociable</b>",
-//     "<b>Similar</b>"
-// ]
-
-// var dimensions2 = [
-//     "Approachability",
-//     "Familiarity",   // Familiarity (van vugt et al., 2010)
-//     "Trustworthiness",
-//     "Sociability",
-//     "Similarity"  //Similarity (Van Vugt et al., 2006)
-// ]
-
-// Mini IPIP scale
-var IPIP = [
-    "<b>I am the life of the party</b><br>",
-    "<b>I sympathize with others' feelings</b><br>",
-    "<b>I get chores done right away</b><br>",
-    "<b>I have frequent mood swings</b><br>",
-    "<b>I have a vivid imagination</b><br>",
-    "<b>I feel entitled to more of everything</b><br>",
-    "<b>I do not talk a lot</b><br>",
[…]

### 2022-08-31 experiment/pilot/old_preprocessing.R
Revert "Initial commit"
This reverts commit 1daa2d4fb11e42094fea4de83c05b377c9faece7.

@@ -1,0 +1,191 @@
+unnest <- function(file, scale) {
+  data <- file |>
+    dplyr::filter(screen == scale) |>
+    dplyr::select(participant_id, response) |>
+    jsontools::json_unnest_wider(col = "response")
+  data
+}
+
+preprocess_raw <- function(file) {
+
+  data <- read.csv(file)
+
+  # Preprocess
+  if (!"end_screen" %in% data$screen) {
+    print(paste0("Warning: Incomplete data for ", file))
+    return(data.frame())
+  }
+
+  # Demographics
+  dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
+
+  # Trials
+  trials <- data[data$screen == "stimuli", ]
+  answers <- unnest(data, "questionnaire")
+
+  # Info
+  info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
+
+  df <- data.frame(
+    Participant = trials$participant_id,
+    Age = as.numeric(jsonlite::fromJSON(dem[1])$age),
+    Sex = jsonlite::fromJSON(dem[2])$sex,
+    Sexual_Orientation = jsonlite::fromJSON(dem[3])$sexual_orientation,
+    Religion = jsonlite::fromJSON(dem[5])$religion,
+    Religion_Spirituality = as.numeric(jsonlite::fromJSON(dem[7])$religiosity),
+    Religion_Activity = as.numeric(jsonlite::fromJSON(dem[7])$religious_activity),
+    Education = jsonlite::fromJSON(dem[2])$education,
+    Nationality = tools::toTitleCase(jsonlite::fromJSON(dem[1])$nationality),
+    Ethnicity = tools::toTitleCase(jsonlite::fromJSON(dem[1])$ethnicity),
+    Date = ifelse(is.null(info$date), NA, info$date),
+    Time = ifelse(is.null(info$time), NA, info$time),
+    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS', 'SCC'), 'rt'])) / 1000 / 60,
+    Duration_Task = sum(as.numeric(data[data$screen == "questionnaire", "rt"])) / 1000 / 60,
[…]

### 2022-08-31 experiment/pilot/parameters.js

@@ -1,0 +1,631 @@
+/* Measures */ //===============================================================
+// Scale Labels
+var scale1 = ["Not at All", "Extremely"]
+var scale2 = ["Strongly Disagree", "Strongly Agree"]
+
+// Oosterhof and Todorov (2008) - 9 point scale (Not at all to Extremely)
+var items = [
+    //"The face looked real to me",
+    "<b>Assuming the person you saw was real...</b> <br><br>Would you find this person attractive?",
+    "Would you find this person approachable?",
+    "Would you find this person trustworthy?",
+    "How much does this person remind you of someone you know?",
+    "How much does this face look like yours?",
+    // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
+    // "How dominant is the face you saw?",
+    //"How musculine/feminine is the face you saw?",
+    // "How emotionally stable is the face you saw?",
+    // "How mean is the face you saw?",
+    // "How boring is the face you saw?",
+    // "How intelligent is the face you saw?",
+    // "How caring is the face you saw?",
+    // "How egoistic is the face you saw?",
+    // "How responsible is the face you saw?",
+]
+
+var dimensions = [
+    //"Real",
+    "Attractiveness",
+    "Approachability",
+    "Trustworthiness",
+    "Familiarity",   // Familiarity (van vugt et al., 2010)
+    "Similarity"
+]
+
+// var items2 = [
+//     "<b>Approachable</b>",
+//     "<b>Familiar</b>",
+//     "<b>Trustworthy</b>",
+//     "<b>Sociable</b>",
+//     "<b>Similar</b>"
+// ]
+
+// var dimensions2 = [
+//     "Approachability",
+//     "Familiarity",   // Familiarity (van vugt et al., 2010)
+//     "Trustworthiness",
+//     "Sociability",
+//     "Similarity"  //Similarity (Van Vugt et al., 2006)
+// ]
+
+// Mini IPIP scale
+var IPIP = [
+    "<b>I am the life of the party</b><br>",
+    "<b>I sympathize with others' feelings</b><br>",
+    "<b>I get chores done right away</b><br>",
+    "<b>I have frequent mood swings</b><br>",
+    "<b>I have a vivid imagination</b><br>",
+    "<b>I feel entitled to more of everything</b><br>",
+    "<b>I do not talk a lot</b><br>",
[…]

### 2022-09-01 experiment/parameters.js
updates

@@ -7,8 +7,9 @@ var scale2 = ["Strongly Disagree", "Strongly Agree"]
 var items = [
     //"The face looked real to me",
     "How attractive do you find this person?",
+    "To what extent do you find this person good-looking?",
     // "Would you find this person approachable?",
-    "How much would you trust this person?",
+    "To what extent do you trust this person?",
     "How much does this person remind you of someone you know?",
     // "How much does this face look like yours?",
     // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
@@ -25,7 +26,8 @@ var items = [
 
 var dimensions = [
     //"Real",
-    "Attractiveness",
+    "General_Attractiveness",
+    "Physical_Attractiveness",
     // "Approachability",
     "Trustworthiness",
     "Familiarity",   // Familiarity (van vugt et al., 2010)

### 2022-09-01 experiment/parameters.js
updates

@@ -6,11 +6,11 @@ var scale2 = ["Strongly Disagree", "Strongly Agree"]
 // Oosterhof and Todorov (2008) - 9 point scale (Not at all to Extremely)
 var items = [
     //"The face looked real to me",
-    "How attractive do you find this person?",
-    "To what extent do you find this person good-looking?",
+    "This person is good-looking.",
+    "I find this person attractive.",
     // "Would you find this person approachable?",
-    "To what extent do you trust this person?",
-    "How much does this person remind you of someone you know?",
+    "I find this person trustworthy.",
+    "This person reminds me of someone I know.",
     // "How much does this face look like yours?",
     // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
     // "How dominant is the face you saw?",
@@ -26,8 +26,8 @@ var items = [
 
 var dimensions = [
     //"Real",
-    "General_Attractiveness",
     "Physical_Attractiveness",
+    "General_Attractiveness",
     // "Approachability",
     "Trustworthiness",
     "Familiarity",   // Familiarity (van vugt et al., 2010)

### 2022-09-01 experiment/parameters.js
comment out more

@@ -6,11 +6,11 @@ var scale2 = ["Strongly Disagree", "Strongly Agree"]
 // Oosterhof and Todorov (2008) - 9 point scale (Not at all to Extremely)
 var items = [
     //"The face looked real to me",
-    "This person is good-looking.",
-    "I find this person attractive.",
+    "This face is good-looking",
+    "I find this person attractive",
     // "Would you find this person approachable?",
-    "I find this person trustworthy.",
-    "This person reminds me of someone I know.",
+    "I find this person trustworthy",
+    "This person reminds me of someone I know",
     // "How much does this face look like yours?",
     // "How weird is the face you saw?",   // include eeriness as well? (cf uncanny valley effect)
     // "How dominant is the face you saw?",

### 2022-09-01 preprocessing.R
update preprocessing

@@ -20,15 +20,25 @@ preprocess_raw <- function(file) {
   dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
   
   # Trials
-  trials <- data[data$screen == "stimuli", ]
+  block1 <- data[data$screen == "stimuli" & data$block_number=='1', ]
+  block2<- data[data$screen == "stimuli" & data$block_number=='2', ]
   answers <- unnest(data, "questionnaire")
   realness_answers <- unnest(data, "perceived_realness")
+  
+  # Realness Block
+  realness_df <- data.frame(
+    Block2_Trial = as.numeric(block2$trial_number),
+    Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block2$stimulus)),
+    Real = datawizard::change_scale(realness_answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 1)),
+    Realness_RT = as.numeric(data[data$screen =="perceived_realness", "rt"]),
+    SimulationMonitoring = datawizard::change_scale(realness_answers$perceived_realness, to = c(-1, 1), range = c(0, 1))
+  )
   
   # Info
   info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
   
   df <- data.frame(
-    Participant = trials$participant_id,
+    Participant = block1$participant_id,
     Age = as.numeric(jsonlite::fromJSON(dem[1])$age),
     Sex = jsonlite::fromJSON(dem[2])$sex,
     Sexual_Orientation = jsonlite::fromJSON(dem[3])$sexual_orientation,
@@ -41,8 +51,7 @@ preprocess_raw <- function(file) {
     Date = ifelse(is.null(info$date), NA, info$date),
     Time = ifelse(is.null(info$time), NA, info$time),
     Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS'), 'rt'])) / 1000 / 60,
-    Duration_Task = sum(as.numeric(data[data$screen =="questionnaire", "rt"])) /1000 /60,
-    Duration_Realness = sum(as.numeric(data[data$screen == "perceived_realness", "rt"])) / 1000 / 60,
[…]

### 2022-09-08 analysis.Rmd
update

@@
 ```{r message=FALSE, warning=FALSE}
-dfsub$Cor_Trustworthy <- NA
-dfsub$Cor_Attractive <- NA
+dfsub$r_Trustworthy <- NA
+dfsub$r_Attractive <- NA
+dfsub$r_Goodlooking <- NA
 for (participant in dfsub$Participant) {
-  dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
-  dfsub[dfsub$Participant == participant, "Cor_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
+  dfsub[dfsub$Participant == participant, "r_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
+  dfsub[dfsub$Participant == participant, "r_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
+  dfsub[dfsub$Participant == participant, "r_Goodlooking"] <- cor(df[df$Participant == participant, "Goodlooking"], df[df$Participant == participant, "Norms_Attractive"])
 }
@@
 p_cor <- dfsub |>
-  select(Participant, starts_with("Cor")) |> 
+  select(Participant, starts_with("r_")) |> 
   pivot_longer(-Participant) |> 
-  mutate(name = str_remove(name, "Cor_")) |> 
+  mutate(name = str_remove(name, "r_")) |> 
   ggplot(aes(x = Participant, y = value)) +
@@
   scale_y_continuous(expand = c(0, 0)) +
-  scale_fill_manual(values = c("#F44336", "#9C27B0")) +
-  scale_color_manual(values = c("#F44336", "#9C27B0")) +
+  scale_fill_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
+  scale_color_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
   see::theme_modern() +
@@
 plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
-  library(emojifont)
+  # library(emojifont)
   ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
@@
   #   pull(Participant))) |>
-  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
+  mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |> 
   ggplot(aes(x = Real, y = Participant, fill = Participant)) +
@@
 ```
+
+#### Effect of Delay
 

### 2022-09-08 preprocessing.R

@@ -7,24 +7,24 @@ unnest <- function(file, scale) {
 }
 
 preprocess_raw <- function(file) {
-  
+
   data <- read.csv(file)
-  
+
   # Preprocess
   if (!"end_screen" %in% data$screen) {
     print(paste0("Warning: Incomplete data for ", file))
     return(data.frame())
   }
-  
+
   # Demographics
   dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
-  
+
   # Trials
   block1 <- data[data$screen == "stimuli" & data$block_number=='1', ]
-  block2<- data[data$screen == "stimuli" & data$block_number=='2', ]
+  block2 <- data[data$screen == "stimuli" & data$block_number=='2', ]
   answers <- unnest(data, "questionnaire")
   realness_answers <- unnest(data, "perceived_realness")
-  
+
   # Realness Block
   realness_df <- data.frame(
     Block2_Trial = as.numeric(block2$trial_number),
@@ -33,10 +33,10 @@ preprocess_raw <- function(file) {
     Realness_RT = as.numeric(data[data$screen =="perceived_realness", "rt"]),
     SimulationMonitoring = datawizard::change_scale(realness_answers$perceived_realness, to = c(-1, 1), range = c(0, 1))
   )
-  
+
   # Info
   info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
-  
+
   df <- data.frame(
     Participant = block1$participant_id,
     Age = as.numeric(jsonlite::fromJSON(dem[1])$age),
@@ -62,8 +62,8 @@ preprocess_raw <- function(file) {
     Block1_Trial = as.numeric(block1$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block1$stimulus)),
     Questionnaire_RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
-    PhysicalAttractiveness = datawizard::change_scale(answers$Physical_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
-    GeneralAttractiveness = datawizard::change_scale(answers$General_Attractiveness, to =c(0.0001, 0.9999), range = c(0, 1)),
[…]

### 2022-09-08 preprocessing.R
Update preprocessing.R

@@ -7,7 +7,6 @@ unnest <- function(file, scale) {
 }
 
 preprocess_raw <- function(file) {
-
   data <- read.csv(file)
 
   # Preprocess
@@ -20,8 +19,8 @@ preprocess_raw <- function(file) {
   dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
 
   # Trials
-  block1 <- data[data$screen == "stimuli" & data$block_number=='1', ]
-  block2 <- data[data$screen == "stimuli" & data$block_number=='2', ]
+  block1 <- data[data$screen == "stimuli" & data$block_number == "1", ]
+  block2 <- data[data$screen == "stimuli" & data$block_number == "2", ]
   answers <- unnest(data, "questionnaire")
   realness_answers <- unnest(data, "perceived_realness")
 
@@ -30,7 +29,7 @@ preprocess_raw <- function(file) {
     Block2_Trial = as.numeric(block2$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block2$stimulus)),
     Real = datawizard::change_scale(realness_answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 1)),
-    Realness_RT = as.numeric(data[data$screen =="perceived_realness", "rt"]),
+    Realness_RT = as.numeric(data[data$screen == "perceived_realness", "rt"]),
     SimulationMonitoring = datawizard::change_scale(realness_answers$perceived_realness, to = c(-1, 1), range = c(0, 1))
   )
 
@@ -50,8 +49,8 @@ preprocess_raw <- function(file) {
     Ethnicity = tools::toTitleCase(jsonlite::fromJSON(dem[1])$ethnicity),
     Date = ifelse(is.null(info$date), NA, info$date),
     Time = ifelse(is.null(info$time), NA, info$time),
-    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c('IUS', 'IPIP6', 'SIAS', 'SPS', 'GAAIS', 'FFNI-BF', 'GPTS'), 'rt'])) / 1000 / 60,
-    Duration_Task = sum(as.numeric(data[data$screen %in% c("questionnaire", "perceived_realness"), "rt"])) /1000 /60,
+    Duration_Questionnaires = sum(as.numeric(data[data$screen %in% c("IUS", "IPIP6", "SIAS", "SPS", "GAAIS", "FFNI-BF", "GPTS"), "rt"])) / 1000 / 60,
[…]

### 2022-09-08 preprocessing.R
add time diff to preprocessing

@@ -21,6 +21,7 @@ preprocess_raw <- function(file) {
   # Trials
   block1 <- data[data$screen == "stimuli" & data$block_number == "1", ]
   block2 <- data[data$screen == "stimuli" & data$block_number == "2", ]
+
   answers <- unnest(data, "questionnaire")
   realness_answers <- unnest(data, "perceived_realness")
 
@@ -28,6 +29,7 @@ preprocess_raw <- function(file) {
   realness_df <- data.frame(
     Block2_Trial = as.numeric(block2$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block2$stimulus)),
+    Stim_Time_2 = as.numeric(block2$time_elapsed),
     Real = datawizard::change_scale(realness_answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 1)),
     Realness_RT = as.numeric(data[data$screen == "perceived_realness", "rt"]),
     SimulationMonitoring = datawizard::change_scale(realness_answers$perceived_realness, to = c(-1, 1), range = c(0, 1))
@@ -60,6 +62,7 @@ preprocess_raw <- function(file) {
     Device_OS = info$os,
     Block1_Trial = as.numeric(block1$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block1$stimulus)),
+    Stim_Time_1 = as.numeric(block1$time_elapsed),
     Questionnaire_RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
     Goodlooking = datawizard::change_scale(answers$Physical_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
     Attractive = datawizard::change_scale(answers$General_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
@@ -69,6 +72,7 @@ preprocess_raw <- function(file) {
 
   # Merge data from both task blocks
   df <- merge(df, realness_df, on = "Stimulus")
+  df$Stim_TimeDiff <- df$Stim_Time_2 - df$Stim_Time_1
 
   # Format sexual orientation
   df$Sexual_Orientation <- ifelse(df$Sexual_Orientation == "Other", jsonlite::fromJSON(dem[4])$sexual_orientation, df$Sexual_Orientation)

### 2022-09-08 analysis.Rmd
script

--- 2022-08-30 analysis.Rmd
@@
 
-df <- read.csv("data/data.csv")
-# |>
-#   mutate(
-#     Date = lubridate::dmy(Date),
-#     Participant = fct_reorder(Participant, Date),
-#     Screen_Refresh = as.character(Screen_Refresh),
-#     Illusion_Side = as.factor(Illusion_Side),
-#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
-#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
-#     Block = as.factor(Block),
-#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
-#   )
+df <- read.csv("data/data.csv") |>
+  mutate(
+    Date = lubridate::dmy(Date),
+    Participant = fct_reorder(Participant, Date),
+    Screen_Refresh = as.character(Screen_Refresh),
+    # Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other"),
+    Belief = fct_relevel(Belief, "Fake", "Real"),
+    Stimulus_Interest = case_when(
+      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Opposite" ~ TRUE,
+      Sexual_Orientation == "Heterosexual" & Stimulus_SameSex == "Same" ~ FALSE,
+      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Opposite" ~ FALSE,
+      Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Same" ~ TRUE,
+      Sexual_Orientation == "Bisexual" ~ TRUE,
+      TRUE ~ NA
+    )
+  )
+
+# head(df[is.na(df$Stimulus_Attract), ])
+
+# Create individual scores for Simulation Monitoring
+df <- df |>
+  group_by(Participant, Belief) |>
+  summarise(Confidence = mean(abs(Belief_Confidence)),
+            n = n() / 109) |> 
+  pivot_wider(names_from = "Belief", values_from = c("Confidence", "n")) |>
+  ungroup() |> 
+  merge(df, by = "Participant")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-outliers <- c()
+outliers <- c(
+  # Very short duration for questionnaire in particular + low rating correlations
+  "5eaef8702b68455d6e130595_ptsga"
+  )
+outliers_partial <- c(
+  "5c6414540821d30001046198_x9q7r",
+  "60dd7b03f1e72d38230df476_9yh9n")
 ```
@@
   group_by(Participant) |>
-  select(Participant, starts_with("Attention"), starts_with("Duration")) |>
+  select(Participant, starts_with("Attention"), starts_with("Duration"), n_Fake) |>
   slice(1) |>
@@
     insight::format_value(Attention_Check, 1),
-    " (", insight::format_value(Attention_Check1, 0), 
+    " (", insight::format_value(Attention_Check1, 1),
     ", ",
-    insight::format_value(Attention_Check2, 0), 
+    insight::format_value(Attention_Check2, 1),
     ", ",
-    insight::format_value(Attention_Check3, 0),
-    ")")) |> 
+    insight::format_value(Attention_Check3, 1),
+    ")"
+  )) |>
   select(-Attention_Check1, -Attention_Check2, -Attention_Check3) |>
@@
   kableExtra::row_spec(1, italic = TRUE) |>
-  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
+  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
+  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
 ```
@@
   see::theme_modern() +
-  theme(axis.text.x = element_text(angle = 45, hjust=1),
-        legend.position = "top") +
-  labs(y = "Score", fill="") +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = "top"
+  ) +
+  labs(y = "Score", fill = "") +
   guides(color = "none") +
-  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
+  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
   ggside::theme_ggside_void() +
@@
   see::theme_modern() +
-  theme(axis.text.x = element_text(angle = 45, hjust=1),
-        legend.position = "top") +
-  labs(y = "Duration (min)", fill="") +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = "top"
+  ) +
+  labs(y = "Duration (min)", fill = "") +
   guides(color = "none") +
-  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
+  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
   ggside::theme_ggside_void() +
@@
 p_cor <- dfsub |>
-  select(Participant, starts_with("Cor")) |> 
+  select(Participant, starts_with("r_")) |>
   pivot_longer(-Participant) |>
-  mutate(name = str_remove(name, "Cor_")) |> 
+  mutate(name = str_remove(name, "r_")) |>
   ggplot(aes(x = Participant, y = value)) +
@@
   scale_y_continuous(expand = c(0, 0)) +
-  scale_fill_manual(values = c("#F44336", "#9C27B0")) +
-  scale_color_manual(values = c("#F44336", "#9C27B0")) +
+  scale_fill_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
+  scale_color_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
   see::theme_modern() +
-  theme(axis.text.x = element_text(angle = 45, hjust=1),
-        legend.position = "top") +
-  labs(y = "Correlation", fill="") +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, 
+                               color = ifelse(levels(dfsub$Participant) %in% outliers, "red", ifelse(levels(dfsub$Participant) %in% outliers_partial, "orange", "black"))),
+    legend.position = "top"
+  ) +
+  labs(y = "Correlation", fill = "") +
   guides(color = "none") +
-  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
+  ggside::geom_ysidedensity(aes(x = after_stat(scaled), color = name)) +
   ggside::theme_ggside_void() +
@@
   (p_cor)
+
+df <- df |> 
+  filter(!Participant %in% outliers)
 ```
@@
   group_by(Participant) |>
-  select(Participant, Age, Sex, Sexual_Orientation, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
+  select(Participant, Age, Sex, Sexual_Orientation, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen"), starts_with("IPIP"), starts_with("Social_"), starts_with("FFNI_"), starts_with("GPTS_"), starts_with("IUS_"), starts_with("SelfAttractiveness"), starts_with("AI"), n_Real, Confidence_Fake, Confidence_Real) |>
   slice(1) |>
@@
 
-plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
-  library(emojifont)
+plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size = 3) {
+  # library(emojifont)
   ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
@@
     ggplot(aes(x, y)) +
-    geom_point(aes(color = group), shape = "square", size=size) +
+    geom_point(aes(color = group), shape = "square", size = size) +
     # ggwaffle::geom_waffle(color = "white") +
@@
 ```{r fig.width=20, fig.height=15}
-# p1 <- plot_distribution(dfsub, "Age", fill = "#FF9800")
-# p2 <- plot_distribution(dfsub, "Duration", title = "Total Duration", subtitle = "in minutes", fill = "#F44336")
-# p3 <- plot_distribution(dfsub, "Break_Duration", title = "Break Duration", subtitle = "in minutes", fill = "#3F51B5")
+p1 <- estimate_density(dfsub$Age) |>
+  ggplot(aes(x = x, y = y)) +
+  geom_area(fill = "#FF9800")
 
-p4 <- plot_waffle(dfsub, "Sex") +
+p2 <- plot_waffle(dfsub, "Sex") +
   scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63", "Other" = "#FF9800"))
 
-p5 <- plot_waffle(dfsub, "Sexual_Orientation")
+p3 <- plot_waffle(dfsub, "Sexual_Orientation")
 
-p5 <- plot_waffle(dfsub, "Education") +
+p4 <- plot_waffle(dfsub, "Education") +
   scale_fill_viridis_d()
 
-p6 <- plot_waffle(dfsub, "Nationality") +
+p5 <- plot_waffle(dfsub, "Nationality") +
   scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))
 
-p7 <- plot_waffle(dfsub, "Ethnicity") +
+p6 <- plot_waffle(dfsub, "Ethnicity") +
   scale_fill_manual(values = c("Latino" = "#FF5722", "Asian" = "#FF9800", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Jewish" = "#9C27B0", "Mixed" = "#795548"))
 
-p8 <- plot_waffle(dfsub, "Screen_Resolution", title = "Screen Resolution") +
+p7 <- plot_waffle(dfsub, "Screen_Resolution", title = "Screen Resolution") +
   scale_fill_pizza_d() +
@@
 
-p9 <- plot_waffle(dfsub, "Device_OS", title = "Device OS") +
+p8 <- plot_waffle(dfsub, "Device_OS", title = "Device OS") +
   scale_fill_bluebrown_d()
@@
 
-# (p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
+patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p7, p8))
 ```
 
-## Results
+# Results
 
-### Manipulation Check
+## Manipulation Check
+
+### Real / Fake
 
 ```{r message=FALSE, warning=FALSE}
+# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
+
 df |>
-  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
-  #   summarize(Real = mean(Real)) |>
-  #   ungroup() |>
-  #   arrange(Real) |>
-  #   pull(Participant))) |>
-  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
-  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
+  mutate(Participant = fct_relevel(Participant, df |> 
+    group_by(Participant) |>
+    summarize(Belief_Answer = mean(Belief_Answer)) |>
+    ungroup() |>
+    arrange(Belief_Answer) |>
+    pull(Participant) |>
+    as.character())) |>
+  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
+  ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
   ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
-  geom_vline(xintercept = 0.5, linetype = "dotted") +
-  scale_y_discrete(expand = c(1, 1)) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  scale_y_discrete(expand = c(0.5, 0.5)) +
   scale_x_continuous(
-    limits = c(0, 1),
+    limits = c(-1, 1),
     expand = c(0, 0),
-    breaks = c(0, 0.5, 1),
-    label = c("Fake", "0", "Real")
+    breaks = c(-1, 0, 1),
+    label = c("Fake", "", "Real")
   ) +
@@
 ```{r message=FALSE, warning=FALSE}
-IVs <- c("Attractive", "Trustworthy", "Approachable", "Familiar", "Similar")
+IVs <- c("Attractive", "Goodlooking", "Trustworthy", "Familiar")
 
@@
 dats <- data.frame()
-for(x in IVs) {
-  for(y in IVs) {
-    if(x == y) next
+for (x in IVs) {
+  for (y in IVs) {
+    if (x == y) next
     print(paste(y, "~", x))
     model <- glmmTMB::glmmTMB(as.formula(
-      paste(y, "~", x, " * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")), 
+      paste(y, "~", x, "* Sex * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")
+    ),
     data = df,
-      family=glmmTMB::beta_family()
+    family = glmmTMB::beta_family()
     )
@@
 
-    pred <- estimate_relation(model, at=c(x, "Stimulus_SameSex"), length=20)
+    pred <- estimate_relation(model, at = c(x, "Stimulus_SameSex", "Sex"), length = 20)
     pred$y <- y
@@
 
-    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x=x, y=y))
+    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x = x, y = y))
   }
@@
   stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
-  geom_ribbon(data=preds, aes(ymin = CI_low, ymax = CI_high, group=Stimulus_SameSex), alpha = 0.3) +
-  geom_line(data=preds, aes(color=Stimulus_SameSex)) +
-  scale_fill_gradientn(colors=c("white", "#FF9800", "#F44336"), guide="none") +
-  scale_x_continuous(expand=c(0, 0)) +
-  scale_y_continuous(expand=c(0, 0)) +
-  facet_grid(y~x, switch = "both") +
+  # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
+  geom_line(data = preds, aes(color = Sex, linetype=Stimulus_SameSex)) +
+  scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
+  scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  facet_grid(y ~ x, switch = "both") +
   theme_modern() +
@@
     axis.title.y = element_blank(),
-    plot.title = element_text(face="bold", hjust=0.5)
+    plot.title = element_text(face = "bold", hjust = 0.5)
   ) +
-  ggside::geom_xsidedensity(fill = "grey", color="white") +
-  ggside::geom_ysidedensity(fill = "grey", color="white") +
+  ggside::geom_xsidedensity(fill = "grey", color = "white") +
+  ggside::geom_ysidedensity(fill = "grey", color = "white") +
   ggside::theme_ggside_void() +
@@
 
-### Reality and Attractiveness
+### Effect of Delay
 
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB::glmmTMB(Real ~ poly(Attractive, 2) + poly(Trustworthy, 2) +
-                            (1|Participant) + (1|Stimulus), data = df, family=glmmTMB::beta_family())
-model <- mgcv::gamm(Real ~ s(Attractive) + Trustworthy, random = list(Participant=~1, Stimulus=~1), data = df, family=mgcv::betar())
+model <- glmmTMB::glmmTMB(Belief ~ poly(Delay, 2) + (1|Participant) + (1|Stimulus),
+      data = df,
+      family = "binomial"
+    )
+pred <- estimate_relation(model, at = "Delay", length = 20)
 
-parameters::parameters(model)
+m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / poly(Delay, 2) + (1|Participant) + (1|Stimulus),
+      data = df,
+      family = glmmTMB::beta_family()
+    )
+y_conf <- estimate_relation(m_conf, at = c("Delay", "Belief"), length = 20)
+y_conf <- y_conf |> 
+  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))
+
+df |>
+  ggplot(aes(x = Delay, y = Real)) +
+  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  geom_hline(yintercept = 0.5, linetype = "dotted") +
+  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
+  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed") +
+  geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
+  geom_line(data=pred, aes(y=Predicted), color="red") +
+  scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  theme_modern() +
+  labs(title = "Effect of Re-exposure Delay", x = "Minutes") +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_blank(),
+    strip.placement = "outside",
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  ) +
+  ggside::geom_xsidedensity(fill = "#795548", color = "white") +
+  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  ggside::ggside(collapse = "all")
+```
+
+## Determinants of Reality
+
+```{r message=FALSE, warning=FALSE}
+make_model <- function(df, var = "Attractive", formula=var, fill = "#2196F3") {
+  m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", formula)),
+                             data = df,
+                             family = "binomial")
+  y_real <- estimate_relation(m_real, at = c(var, "Sex"), length = 20)
+
+  m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief /", formula)),
+        data = df,
+        family = glmmTMB::beta_family()
+      )
+  y_conf <- estimate_relation(m_conf, at = c(var, "Belief", "Sex"), length = 20)
+  y_conf <- y_conf |> 
+    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))
+
+  p <- df |>
+    ggplot(aes_string(x = var, y = "Real")) +
+    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+    scale_fill_gradientn(colors = c("white", fill), guide = "none") +
+    ggnewscale::new_scale_fill() +
+    geom_hline(yintercept = 0.5, linetype = "dotted") +
+    # geom_point2(alpha = 0.25, size = 4, color = "black") +
+    geom_line(data=y_conf, aes(y=Predicted, group=interaction(Belief, Sex), color=Sex), linetype="dashed") +
+    geom_ribbon(data = y_real, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
+    geom_line(data = y_real, aes(y = Predicted, color=Sex)) +
+
+    scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
+    scale_fill_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
+    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
+    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
+    theme_modern(axis.title.space=0) + 
+    ggside::geom_xsidedensity(fill = fill, color = "white") +
+    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
+    ggside::theme_ggside_void() +
+    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+    ggside::scale_xsidey_continuous(expand = c(0, 0))
+
+  list(p=p)
+}
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-pred <- estimate_relation(model, at = c("Attractive"), length=20)
+rez_at <- make_model(filter(df, Stimulus_Interest == TRUE), 
+                     formula = "poly(Attractive, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
+                     var="Attractive", fill = "#F44336")
+rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE), 
+                     formula = "poly(Goodlooking, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
+                     var="Goodlooking", fill = "#E91E63")
+rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE), 
+                     formula = "poly(Trustworthy, 2) * Sex + Goodlooking + (1|Participant) + (1|Stimulus)", 
+                     var="Trustworthy", fill = "#4CAF50")
+rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE), 
+                     formula = "poly(Familiar, 2) * Sex + (1|Participant) + (1|Stimulus)", 
+                     var="Familiar", fill = "#2196F3")
 
-df |> 
-  ggplot(aes(x = Attractive, y = Real)) +
-  ggside::geom_xsidedensity(fill = "grey", color="white") +
-  ggside::geom_ysidedensity(fill = "grey", color="white") +
-  ggside::theme_ggside_void() +
-  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
-  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
-  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
-  geom_hline(yintercept = 0.5, linetype = "dotted") +
-  geom_point2(alpha=0.25, size=4, color="white") +
-  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
-  geom_line(data = pred, aes(y = Predicted)) +
-  scale_fill_viridis_c(guide="none") +
-  scale_x_continuous(expand=c(0, 0)) +
-  scale_y_continuous(expand=c(0, 0))
+(rez_at$p +
+  theme(axis.text.x = element_blank()) +
+  labs(x = "Attractiveness") |
+rez_gl$p +
+  labs(x = "Beauty") +
+  theme(axis.text.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank())
+) / 
+(rez_tr$p +
+  labs(x = "Trustworthiness") |
+rez_fa$p +
+  labs(x = "Familiarity") +
+  theme(axis.text.y = element_blank(),
+        axis.title.y = element_blank())
+) + 
+  plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
+  plot_layout(guides = "collect")
+```
 
-pred <- estimate_relation(model, at = c("Trustworthy"), length=20)
+## Interaction
 
-df |> 
-  ggplot(aes(x = Trustworthy, y = Real)) +
-  ggside::geom_xsidedensity(fill = "grey", color="white") +
-  ggside::geom_ysidedensity(fill = "grey", color="white") +
-  ggside::theme_ggside_void() +
-  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
-  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
-  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
-  geom_hline(yintercept = 0.5, linetype = "dotted") +
-  geom_point2(alpha=0.25, size=4, color="white") +
-  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
-  geom_line(data = pred, aes(y = Predicted)) +
-  scale_fill_viridis_c(guide="none") +
-  scale_x_continuous(expand=c(0, 0)) +
-  scale_y_continuous(expand=c(0, 0))
+```{r message=FALSE, warning=FALSE}
+cor_test(dfsub, "SelfAttractiveness1", "SelfAttractiveness2")
+
+df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])
+
 ```
+
+## Inter-Individual Correlates
+
+```{r message=FALSE, warning=FALSE}
+model <- glmmTMB::glmmTMB(Belief ~ 1 + (1|Participant) + (1|Stimulus), data=df, family="binomial")
+dfsub <- modelbased::estimate_grouplevel(model) |> 
+  filter(Group == "Participant") |> 
+  transmute(Participant = Level, Simulation_Monitoring=Coefficient) |> 
+  merge(dfsub, by="Participant")
+
+model <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief + (Belief|Participant) + (1|Stimulus), data=df, family=glmmTMB::beta_family())
+dfsub <- modelbased::estimate_grouplevel(model) |> 
+  filter(Group == "Participant") |> 
+  transmute(Participant = Level, Parameter, Coefficient) |> 
+  pivot_wider(names_from = "Parameter", values_from = "Coefficient") |> 
+  transmute(Participant, Confidence_Real_Model = BeliefReal, Confidence_Fake_Model = `(Intercept)`) |> 
+  merge(dfsub, by="Participant")
+```
+```{r message=FALSE, warning=FALSE}
+correlation::correlation(dfsub[c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model")], 
+                         dfsub[c("Confidence_Fake", "Confidence_Real", "n_Real")],
+                         )
+```
+
+### IPIP-6
+
+```{r message=FALSE, warning=FALSE}
+make_correlation <- function(x, y) {
+  cor <- correlation::correlation(x,
+    y,
+    bayesian = TRUE,
+    bayesian_prior = "medium.narrow",
+    sort = TRUE
+  ) |>
+    datawizard::data_remove(c("ROPE_Percentage"))
+  cor$`BF (Spearman)` <- format_bf(
+    correlation::correlation(
+      x, y,
+      bayesian = TRUE,
+      ranktransform = TRUE,
+      bayesian_prior = "medium.narrow"
+    )$BF,
+    name = NULL, stars = TRUE
+  )
+  cor |>
+    arrange(desc(BF))
+}
+
+sr <- c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model", "Confidence_Fake", "Confidence_Real", "n_Real")
+
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IPIP")))
+filter(r, BF > 1)
+```
+
+### AI
+
+```{r message=FALSE, warning=FALSE}
+rez <- parameters::n_factors(select(dfsub, starts_with("AI")))
+plot(rez)
+
+efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n=3, rotation="varimax", sort=TRUE)
+
+dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |> 
+  cbind(dfsub)
+```
+```{r message=FALSE, warning=FALSE}
+r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
+filter(r, BF > 1)
+```

### 2022-09-08 preprocessing.R

@@ -29,10 +29,20 @@ preprocess_raw <- function(file) {
   realness_df <- data.frame(
     Block2_Trial = as.numeric(block2$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block2$stimulus)),
-    Stim_Time_2 = as.numeric(block2$time_elapsed),
-    Real = datawizard::change_scale(realness_answers$perceived_realness, to = c(0.0001, 0.9999), range = c(0, 1)),
-    Realness_RT = as.numeric(data[data$screen == "perceived_realness", "rt"]),
-    SimulationMonitoring = datawizard::change_scale(realness_answers$perceived_realness, to = c(-1, 1), range = c(0, 1))
+    Delay2 = as.numeric(block2$time_elapsed),
+    Real_RT = as.numeric(data[data$screen == "perceived_realness", "rt"]),
+    Real = datawizard::change_scale(realness_answers$perceived_realness,
+                                    to = c(0.0001, 0.9999), range = c(0, 1)
+    ),
+    Belief_Answer = datawizard::change_scale(realness_answers$perceived_realness,
+      to = c(-1, 1), range = c(0, 1)
+    ),
+    Belief = ifelse(realness_answers$perceived_realness >= 0.5, "Real", "Fake"),
+    Belief_Confidence = datawizard::change_scale(abs(datawizard::change_scale(realness_answers$perceived_realness,
+      to = c(-1, 1), range = c(0, 1)
+    )),
+    to = c(0.0001, 0.9999), range = c(0, 1)
+    )
   )
 
   # Info
@@ -62,8 +72,8 @@ preprocess_raw <- function(file) {
     Device_OS = info$os,
     Block1_Trial = as.numeric(block1$trial_number),
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block1$stimulus)),
-    Stim_Time_1 = as.numeric(block1$time_elapsed),
-    Questionnaire_RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
+    Delay1 = as.numeric(block1$time_elapsed),
+    RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
     Goodlooking = datawizard::change_scale(answers$Physical_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
[…]

### 2022-09-08 preprocessing.R
update

@@ -95,11 +95,16 @@ preprocess_raw <- function(file) {
 
   # Standardize demographics
   # unique(df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Latin", "Hisapanic"), "Latino", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Latin", "Hisapanic", "Latino/Hispanic"), "Hispanic", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Europe", "White"), "Caucasian", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("South African Coloured"), "African", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Mestiza", "Mixed Race", "Mixed Race "), "Mixed", df$Ethnicity)
+
+  # unique(df$Nationality)
 
   # Add info related to stimulus
   df$Stimulus_Sex <- ifelse(stringr::str_detect(df$Stimulus, "NF"), "Female", "Male")
-  df$Stimulus_SameSex <- ifelse(df$Sex == df$Stimulus_Sex, "Same", "Opposite")
+  df$Stimulus_SameSex <- ifelse(df$Sex == df$Stimulus_Sex, "Same", "Different")
 
   # Psychometric Scales
   # IPIP

### 2022-09-09 analysis.Rmd

@@
 ```
-
-# Introduction
-
-The goal of this study was to...
 
@@
 outliers_partial <- c(
+  "5dc3485219ca0326027ce91f_37ho9",
   "5c6414540821d30001046198_x9q7r",
@@
 We removed `r length(outliers)` participants upon inspection of...
+
+### Extreme Items
+
+```{r message=FALSE, warning=FALSE}
+extreme_items <- df |> 
+  group_by(Stimulus, Belief) |>
+  summarize(n = n() / nrow(dfsub)) |>
+  pivot_wider(values_from = "n", names_from = "Belief") |> 
+  mutate(File = paste0("experiment/stimuli/AMFD/", Stimulus)) |> 
+  arrange(Real) |> 
+  filter(Real < 0.2 | Real > 0.8)
+
+p_item <- df |>
+  filter(Stimulus %in% extreme_items$Stimulus) |> 
+  mutate(Stimulus = fct_relevel(Stimulus, as.character(extreme_items$Stimulus))) |>
+  ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
+  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  ggimage::geom_image(data=extreme_items, aes(image=File, x = 0, y=Stimulus), size=0.1, by="height") +
+  # scale_y_discrete(expand = c(0.5, 0.5)) +
+  scale_x_continuous(
+    limits = c(-1, 1),
+    expand = c(0, 0),
+    breaks = c(-1, 0, 1),
+    label = c("Fake", "", "Real")
+  ) +
+  scale_fill_viridis_d(option = "inferno") +
+  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
+  guides(fill = "none") +
+  see::theme_modern() +
+  theme(
+    # axis.text.y = element_blank(),
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  )
+# p_item
+
+df <- df |> 
+  filter(!Stimulus %in% extreme_items$Stimulus)
+```
+
+We removed `r nrow(extreme_items)` trials per participant.
 
@@
 ```{r message=FALSE, warning=FALSE}
-data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
+data.frame(Participant = c(paste0("Total (n=", nrow(dfsub), ")")), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
   rbind(dfsub) |>
@@
   # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed") +
+  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed", color="red") +
   geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
@@
     scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
-    theme_modern(axis.title.space=0) + 
+    theme_modern(axis.title.space=5) + 
     ggside::geom_xsidedensity(fill = fill, color = "white") +
@@
 
-  list(p=p)
+  list(p=p, model_belief=m_real)
 }
@@
 rez_at <- make_model(filter(df, Stimulus_Interest == TRUE), 
-                     formula = "poly(Attractive, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
+                     formula = "Sex / poly(Attractive, 2) + Trustworthy + (1|Participant) + (1|Stimulus)", 
                      var="Attractive", fill = "#F44336")
 rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE), 
-                     formula = "poly(Goodlooking, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
+                     formula = "Sex / poly(Goodlooking, 2) + Trustworthy + (1|Participant) + (1|Stimulus)", 
                      var="Goodlooking", fill = "#E91E63")
 rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE), 
-                     formula = "poly(Trustworthy, 2) * Sex + Goodlooking + (1|Participant) + (1|Stimulus)", 
+                     formula = "Sex / poly(Trustworthy, 2) + Goodlooking + (1|Participant) + (1|Stimulus)", 
                      var="Trustworthy", fill = "#4CAF50")
 rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE), 
-                     formula = "poly(Familiar, 2) * Sex + (1|Participant) + (1|Stimulus)", 
+                     formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)", 
                      var="Familiar", fill = "#2196F3")
+
+parameters::parameters(rez_at$model_belief)
+parameters::parameters(rez_gl$model_belief)
+parameters::parameters(rez_tr$model_belief)
+parameters::parameters(rez_fa$model_belief)
 
@@
 df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])
-
 ```
@@
 efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n=3, rotation="varimax", sort=TRUE)
-
+efa
 dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |> 
@@
 ```
+
+### Social Anxiety
+
+```{r message=FALSE, warning=FALSE}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("Social_")))
+filter(r, BF > 1)
+```
+
+### Intolerance to Uncertainty
+
+```{r message=FALSE, warning=FALSE}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IUS_")))
+filter(r, BF > 1)
+```
+
+### Narcissism
+
+```{r message=FALSE, warning=FALSE}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("FFNI_")))
+filter(r, BF > 1)
+```
+
+### Paranoid Beliefs
+
+```{r message=FALSE, warning=FALSE}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("GPTS_")))
+filter(r, BF > 1)
+```

### 2022-09-12 analysis.Rmd
update

--- 2022-09-08 analysis.Rmd
@@
 
-# Introduction
-
-The goal of this study was to...
-
 # Methods
@@
     Screen_Refresh = as.character(Screen_Refresh),
-    # Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other"),
+    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other", "Prefer not to Say"),
     Belief = fct_relevel(Belief, "Fake", "Real"),
@@
       Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Same" ~ TRUE,
-      Sexual_Orientation == "Bisexual" ~ TRUE,
+      Sexual_Orientation %in% c("Bisexual", "Queer") ~ TRUE,
       TRUE ~ NA
@@
   group_by(Participant, Belief) |>
-  summarise(Confidence = mean(abs(Belief_Confidence)),
-            n = n() / 109) |> 
+  summarise(
+    Confidence = mean(abs(Belief_Confidence)),
+    n = n() / 109
+  ) |>
   pivot_wider(names_from = "Belief", values_from = c("Confidence", "n")) |>
@@
   # Very short duration for questionnaire in particular + low rating correlations
-  "5eaef8702b68455d6e130595_ptsga"
+  "5eaef8702b68455d6e130595_ptsga",
+  "5f0f0a2a8b2a480447f31b21_lqgpz",
+  "611d03b822d4c8e041ea0c32_m0knb"
 )
 outliers_partial <- c(
+  "5dc3485219ca0326027ce91f_37ho9",
   "5c6414540821d30001046198_x9q7r",
-  "60dd7b03f1e72d38230df476_9yh9n")
+  "60dd7b03f1e72d38230df476_9yh9n",
+  "5962799cb752840001ca478b_jh4sl",
+  "5f44c23fbf2ddb80bcdf0edc_dnbny",
+  "5e80370d48b5f47170e30e5c_5w2gf"
+)
 ```
@@
 We removed `r length(outliers)` participants upon inspection of...
+
+### Extreme Items
+
+```{r message=FALSE, warning=FALSE}
+extreme_items <- df |>
+  group_by(Stimulus, Belief) |>
+  summarize(n = n() / length(unique(df$Participant))) |>
+  pivot_wider(values_from = "n", names_from = "Belief") |>
+  mutate(File = paste0("experiment/stimuli/AMFD/", Stimulus)) |>
+  arrange(Real) |>
+  filter(Real < 0.15 | Real > 0.85)
+
+p_item <- df |>
+  filter(Stimulus %in% extreme_items$Stimulus) |>
+  mutate(Stimulus = fct_relevel(Stimulus, as.character(extreme_items$Stimulus))) |>
+  ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
+  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  ggimage::geom_image(data = extreme_items, aes(image = File, x = 0, y = Stimulus), size = 0.1, by = "height") +
+  # scale_y_discrete(expand = c(0.5, 0.5)) +
+  scale_x_continuous(
+    limits = c(-1, 1),
+    expand = c(0, 0),
+    breaks = c(-1, 0, 1),
+    label = c("Fake", "", "Real")
+  ) +
+  scale_fill_viridis_d(option = "inferno") +
+  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
+  guides(fill = "none") +
+  see::theme_modern() +
+  theme(
+    # axis.text.y = element_blank(),
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  )
+# p_item
+
+df <- df |>
+  filter(!Stimulus %in% extreme_items$Stimulus)
+```
+
+We removed `r nrow(extreme_items)` trials per participant.
 
@@
 dfsub$r_Attractive <- NA
-dfsub$r_Goodlooking <- NA
+dfsub$r_Beauty <- NA
 for (participant in dfsub$Participant) {
@@
   dfsub[dfsub$Participant == participant, "r_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
-  dfsub[dfsub$Participant == participant, "r_Goodlooking"] <- cor(df[df$Participant == participant, "Goodlooking"], df[df$Participant == participant, "Norms_Attractive"])
+  dfsub[dfsub$Participant == participant, "r_Beauty"] <- cor(df[df$Participant == participant, "Beauty"], df[df$Participant == participant, "Norms_Attractive"])
 }
@@
   kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
+# kableExtra::row_spec(which(str_detect(dfsub$Participant, "613a972033d79df11a6570de")) + 1, background = "green")
 ```
@@
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, 
-                               color = ifelse(levels(dfsub$Participant) %in% outliers, "red", ifelse(levels(dfsub$Participant) %in% outliers_partial, "orange", "black"))),
+    axis.text.x = element_text(
+      angle = 45, hjust = 1,
+      color = ifelse(levels(dfsub$Participant) %in% outliers, "red", ifelse(levels(dfsub$Participant) %in% outliers_partial, "orange", "black"))
+    ),
     legend.position = "top"
@@
 
-p5 <- plot_waffle(dfsub, "Nationality") +
-  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "Eastern" = "#673AB7", "African" = "#4CAF50", "South African" = "#009688"))
+p5 <- dfsub |>
+  group_by(Nationality) |>
+  mutate(n = n()) |>
+  ungroup() |>
+  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
+  ggplot(aes(Nationality)) +
+  geom_bar(aes(fill = Nationality)) +
+  scale_fill_viridis_d(guide = "none") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 
@@
 
-patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p7, p8))
+patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p8))
 ```
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, fig.height=fig.width*1.5}
 # plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
-
 df |>
@@
   ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
-  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
+  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups", color = "black", size = 0.1) +
   geom_vline(xintercept = 0, linetype = "dotted") +
-  scale_y_discrete(expand = c(0.5, 0.5)) +
+  scale_y_discrete(expand = c(0.02, 0)) +
   scale_x_continuous(
@@
     expand = c(0, 0),
-    breaks = c(-1, 0, 1),
+    breaks = c(-0.95, 0, 0.95),
     label = c("Fake", "", "Real")
@@
   theme(
-    # axis.text.y = element_blank(),
+    axis.text.y = element_blank(),
     plot.title = element_text(face = "bold", hjust = 0.5)
-  )
+  ) +
+  ggside::geom_xsidedensity(fill = "grey", color = "white") +
+  ggside::scale_xsidey_continuous(expand = c(0, 0))
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-IVs <- c("Attractive", "Goodlooking", "Trustworthy", "Familiar")
+IVs <- c("Attractive", "Beauty", "Trustworthy", "Familiar")
 
@@
     model <- glmmTMB::glmmTMB(as.formula(
-      paste(y, "~", x, "* Sex * Stimulus_SameSex + (1|Participant) + (1|Stimulus)")
+      paste(y, "~", x, "* Sex * Stimulus_Interest + (1|Participant) + (1|Stimulus)")
     ),
@@
 
-    pred <- estimate_relation(model, at = c(x, "Stimulus_SameSex", "Sex"), length = 20)
+    pred <- estimate_relation(model, at = c(x, "Stimulus_Interest", "Sex"), length = 20)
     pred$y <- y
@@
 
-    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x = x, y = y))
+    dats <- rbind(dats, data.frame(Score = df[[x]], Predicted = df[[y]], x = x, y = y, Sex = df$Sex))
   }
@@
   # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
-  geom_line(data = preds, aes(color = Sex, linetype=Stimulus_SameSex)) +
+  geom_line(data = preds, aes(color = Sex, linetype = Stimulus_Interest)) +
   scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
-  scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
+  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
+  scale_linetype_manual(values = c("TRUE" = "solid", "FALSE" = "dashed")) +
+  scale_x_continuous(expand = c(0, 0), labels = scales::percent()) +
+  scale_y_continuous(expand = c(0, 0), labels = scales::percent()) +
   facet_grid(y ~ x, switch = "both") +
@@
   ) +
-  ggside::geom_xsidedensity(fill = "grey", color = "white") +
-  ggside::geom_ysidedensity(fill = "grey", color = "white") +
+  ggnewscale::new_scale_fill() +
+  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
+  ggside::geom_xsidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
+  ggside::geom_ysidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
   ggside::theme_ggside_void() +
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB::glmmTMB(Belief ~ poly(Delay, 2) + (1|Participant) + (1|Stimulus),
+model <- glmmTMB::glmmTMB(Belief ~ Delay + (1 | Participant) + (1 | Stimulus),
   data = df,
@@
 
-m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / poly(Delay, 2) + (1|Participant) + (1|Stimulus),
+m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / Delay + ((Belief / Delay) | Participant) + (1 | Stimulus),
   data = df,
@@
 y_conf <- y_conf |>
-  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))
+  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(x, range = c(1, 0), to = c(0, 0.5))))
 
@@
   # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-  geom_line(data=y_conf, aes(y=Predicted, group=Belief), linetype = "dashed") +
-  geom_ribbon(data=pred, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
-  geom_line(data=pred, aes(y=Predicted), color="red") +
+  geom_line(data = y_conf, aes(y = Predicted, group = Belief), linetype = "dashed", color = "red") +
+  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
+  geom_line(data = pred, aes(y = Predicted), color = "red") +
   scale_fill_gradientn(colors = c("white", "#795548"), guide = "none") +
   scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
   theme_modern() +
@@
   ggside::ggside(collapse = "all")
+
+parameters::parameters(model)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-make_model <- function(df, var = "Attractive", formula=var, fill = "#2196F3") {
+make_model <- function(df, var = "Attractive", formula = var, fill = "#2196F3") {
+  # Models
   m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", formula)),
     data = df,
-                             family = "binomial")
-  y_real <- estimate_relation(m_real, at = c(var, "Sex"), length = 20)
+    family = "binomial"
+  )
+  y_real <- estimate_relation(m_real, at = c(var, "Sex"), length = 21)
+  # gam <- brms::brm(paste0("Belief ~ s(", var, ", by=Sex) + (1|Participant) + (1|Stimulus)"),
+  #                  data=df,
+  #                  algorithm="sampling",
+  #                  family = "bernoulli")
+  # trend <- estimate_relation(gam, at = c(var, "Sex"), length = 81, preserve_range=FALSE)
+  # slope <- estimate_slopes(gam, trend=var, at = c(var, "Sex"), length = 81)
+  # trend$Trend <- interpret_pd(slope$pd)
+  # trend$group <- 0
+  # trend$group[2:nrow(trend)] <- as.character(cumsum(ifelse(trend$Trend[2:nrow(trend)] == trend$Trend[1:nrow(trend)-1], 0, 1)))
 
@@
   )
-  y_conf <- estimate_relation(m_conf, at = c(var, "Belief", "Sex"), length = 20)
+  y_conf <- estimate_relation(m_conf, at = c(var, "Belief", "Sex"), length = 21)
   y_conf <- y_conf |>
-    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range=c(0, 1), to=c(0.5, 1)), datawizard::rescale(x, range=c(1, 0), to=c(0, 0.5))))
+    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(x, range = c(1, 0), to = c(0, 0.5))))
 
+  # Significance
+  param <- parameters::parameters(m_real, effects = "fixed", keep = var)
+  sig <- data.frame(
+    x = 0.5,
+    y = y_real[c(11, 32), "Predicted"] + c(0.05, -0.05),
+    p = c(min(param$p[c(1, 3)]), min(param$p[c(2, 4)])),
+    Sex = c("Female", "Male")
+  )
+  sig$label <- format_p(sig$p, stars_only = TRUE)
+
+  # Plot
   p <- df |>
@@
     # geom_point2(alpha = 0.25, size = 4, color = "black") +
-    geom_line(data=y_conf, aes(y=Predicted, group=interaction(Belief, Sex), color=Sex), linetype="dashed") +
-    geom_ribbon(data = y_real, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
-    geom_line(data = y_real, aes(y = Predicted, color=Sex)) +
-
-    scale_color_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
-    scale_fill_manual(values=c("Male" = "#2196F3", "Female" = "#E91E63")) +
+    geom_line(data = y_conf, aes(y = Predicted, group = interaction(Belief, Sex), color = Sex), linetype = "dashed") +
+    geom_ribbon(data = y_real, aes(y = Predicted, group = Sex, fill = Sex, ymin = CI_low, ymax = CI_high), alpha = 1 / 3) +
+    geom_line(data = y_real, aes(y = Predicted, color = Sex), size=1) +
+    # geom_ribbon(data = trend, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 1/6) +
+    # geom_line(data = trend, aes(y = Predicted, color=Sex, linetype=Trend, group=interaction(Sex, group)), size=0.6) +
+    geom_text(data = sig, aes(y = y, x = x, label = label, color = Sex), size = 8) +
+    scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
+    scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
     scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
     scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
-    theme_modern(axis.title.space=0) + 
+    guides(fill = guide_legend(override.aes = list(alpha = 1))) +
+    theme_modern(axis.title.space = 5) +
     ggside::geom_xsidedensity(fill = fill, color = "white") +
@@
 
-  list(p=p)
+  list(p = p, model_belief = m_real, model_confidence = m_conf)
 }
@@
 rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
-                     formula = "poly(Attractive, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
-                     var="Attractive", fill = "#F44336")
+  formula = "Sex / poly(Attractive, 2) + (1|Participant) + (1|Stimulus)",
+  var = "Attractive", fill = "#F44336"
+)
 rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
-                     formula = "poly(Goodlooking, 2) * Sex + Trustworthy + (1|Participant) + (1|Stimulus)", 
-                     var="Goodlooking", fill = "#E91E63")
+  formula = "Sex / poly(Beauty, 2) + Trustworthy + (1|Participant) + (1|Stimulus)",
+  var = "Beauty", fill = "#E91E63"
+)
 rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
-                     formula = "poly(Trustworthy, 2) * Sex + Goodlooking + (1|Participant) + (1|Stimulus)", 
-                     var="Trustworthy", fill = "#4CAF50")
+  formula = "Sex / poly(Trustworthy, 2) + Beauty + (1|Participant) + (1|Stimulus)",
+  var = "Trustworthy", fill = "#4CAF50"
+)
 rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
-                     formula = "poly(Familiar, 2) * Sex + (1|Participant) + (1|Stimulus)", 
-                     var="Familiar", fill = "#2196F3")
+  formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)",
+  var = "Familiar", fill = "#2196F3"
+)
 
@@
     labs(x = "Beauty") +
-  theme(axis.text.x = element_blank(),
+    theme(
+      axis.text.x = element_blank(),
       axis.title.y = element_blank(),
-        axis.text.y = element_blank())
+      axis.text.y = element_blank()
+    )
 ) /
@@
       labs(x = "Familiarity") +
-  theme(axis.text.y = element_blank(),
-        axis.title.y = element_blank())
+      theme(
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()
+      )
   ) +
@@
   plot_layout(guides = "collect")
+```
+
+```{r message=FALSE, warning=FALSE}
+parameters::parameters(rez_at$model_belief, effects = "fixed", keep = "Attractive")
+performance::r2(rez_at$model_belief)
+performance::icc(rez_at$model_belief, by_group = TRUE)
+parameters::parameters(rez_at$model_confidence, effects = "fixed", keep = "Attractive")
+
+parameters::parameters(rez_gl$model_belief, effects = "fixed", keep = "Beauty")
+performance::r2(rez_gl$model_belief)
+performance::icc(rez_gl$model_belief, by_group = TRUE)
+parameters::parameters(rez_gl$model_confidence, effects = "fixed", keep = "Beauty")
+
+parameters::parameters(rez_tr$model_belief, effects = "fixed", keep = "Trustworthy")
+performance::r2(rez_tr$model_belief)
+performance::icc(rez_tr$model_belief, by_group = TRUE)
+parameters::parameters(rez_tr$model_confidence, effects = "fixed", keep = "Trustworthy")
+
+parameters::parameters(rez_fa$model_belief, effects = "fixed", keep = "Familiar")
+performance::r2(rez_fa$model_belief)
+performance::icc(rez_fa$model_belief, by_group = TRUE)
+parameters::parameters(rez_fa$model_confidence, effects = "fixed", keep = "Familiar")
 ```
@@
 df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])
+```
 
+```{r message=FALSE, warning=FALSE}
+m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Attractive, 2) * Self_Attractiveness) + (1 | Participant) + (1 | Stimulus),
+  data = filter(df, Stimulus_Interest == TRUE),
+  family = "binomial"
+)
+
+parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness")
+
+m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Beauty, 2) * Self_Attractiveness) + Trustworthy + (1 | Participant) + (1 | Stimulus),
+  data = filter(df, Stimulus_Interest == TRUE),
+  family = "binomial"
+)
+
+parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness")
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-model <- glmmTMB::glmmTMB(Belief ~ 1 + (1|Participant) + (1|Stimulus), data=df, family="binomial")
+model <- glmmTMB::glmmTMB(Belief ~ 1 + (1 | Participant) + (1 | Stimulus), data = df, family = "binomial")
 dfsub <- modelbased::estimate_grouplevel(model) |>
   filter(Group == "Participant") |>
-  transmute(Participant = Level, Simulation_Monitoring=Coefficient) |> 
-  merge(dfsub, by="Participant")
+  transmute(Participant = Level, Simulation_Monitoring = Coefficient) |>
+  merge(dfsub, by = "Participant")
 
-model <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief + (Belief|Participant) + (1|Stimulus), data=df, family=glmmTMB::beta_family())
+model <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief + (Belief | Participant) + (1 | Stimulus), data = df, family = glmmTMB::beta_family())
 dfsub <- modelbased::estimate_grouplevel(model) |>
@@
   transmute(Participant, Confidence_Real_Model = BeliefReal, Confidence_Fake_Model = `(Intercept)`) |>
-  merge(dfsub, by="Participant")
+  merge(dfsub, by = "Participant")
 ```
 ```{r message=FALSE, warning=FALSE}
-correlation::correlation(dfsub[c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model")], 
+correlation::correlation(
+  dfsub[c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model")],
   dfsub[c("Confidence_Fake", "Confidence_Real", "n_Real")],
@@
 
+plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey") {
+  param <- cor_test(dfsub, x, y, bayesian = TRUE)
+
+  # Format stat output
+  r <- str_replace(str_remove(insight::format_value(param$rho), "^0+"), "^-0+", "-")
+  CI_low <- str_replace(str_remove(insight::format_value(param$CI_low), "^0+"), "^-0+", "-")
+  CI_high <- str_replace(str_remove(insight::format_value(param$CI_high), "^0+"), "^-0+", "-")
+
+  stat <- paste0("italic(r)~'= ", r, ", 95% CI [", CI_low, ", ", CI_high, "], BF'['10']~'", paste0(insight::format_bf(param$BF, name = "")), "'")
+
+  label <- data.frame(
+    x = min(dfsub[[x]], na.rm = TRUE),
+    y = max(dfsub[[y]], na.rm = TRUE),
+    label = stat
+  )
+
+  # Plot
+  dfsub |>
+    ggplot(aes_string(x = x, y = y)) +
+    geom_point2(
+      size = 3,
+      color = fill,
+      # color = DVs[x],
+      alpha = 2 / 3
+    ) +
+    geom_smooth(method = "lm", color = "black", formula = "y ~ x", alpha = 0.3) +
+    labs(y = ylab, x = xlab) +
+    geom_label(data = label, aes(x = x, y = y), label = str2expression(label$label), hjust = 0, vjust = 1) +
+    theme_modern() +
+    ggside::geom_xsidedensity(fill = "grey", color = "white") +
+    ggside::geom_ysidedensity(fill = fill, color = "white") +
+    ggside::theme_ggside_void() +
+    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+    ggside::scale_xsidey_continuous(expand = c(0, 0))
+}
+```
+```{r message=FALSE, warning=FALSE}
 sr <- c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model", "Confidence_Fake", "Confidence_Real", "n_Real")
@@
 filter(r, BF > 1)
+
+plot_correlation(dfsub,
+  x = "Confidence_Real",
+  y = "IPIP6_HonestyHumility",
+  xlab = "Confidence_Real",
+  ylab = "IPIP6_HonestyHumility",
+  fill = "grey"
+)
 ```
@@
 
-efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n=3, rotation="varimax", sort=TRUE)
-
+efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n = 3, rotation = "varimax", sort = TRUE)
+efa
 dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |>

### 2022-09-12 submission/manuscript.Rmd
update

---
title             : "**Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated**"
shorttitle        : "Illusion Game Validation"
author:

  - name          : "Dominique Makowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dom.makowski@gmail.com"
    orcid         : 0000-0001-5375-9967
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Funding acquisition"
      - "Investigation"
      - "Methodology"
      - "Project administration"
      - "Resources"
      - "Software"
      - "Supervision"
      - "Validation"
      - "Visualization"
      - "Writing – original draft"
  - name          : "An Shu Te"
    affiliation   : "1"
    orcid         : 0000-0001-8008-2824
    role:
      - "Project administration"
      - "Resources"
      - "Investigation"
      - "Writing – original draft"
  - name          : "Stephanie Kirk"
    affiliation   : "1"
    orcid         : 0000-0002-9312-5552
    role:
      - "Project administration"
      - "Resources"
      - "Writing – original draft"
  - name          : "Ngoi Zi Liang"
    affiliation   : "1"
    role:
      - "Project administration"
      - "Resources"
      - "Writing – review & editing"
  - name          : "S.H. Annabel Chen"
    affiliation   : "1, 2, 3, 4"
    orcid         : 0000-0002-1540-5516
    role:
      - "Project administration"
      - "Supervision"
      - "Writing – review & editing"
affiliation:

  - id            : "1"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "2"
    institution   : "LKC Medicine, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "National Institute of Education, Singapore"
  - id            : "4"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
authornote: |
  Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (dom.makowski@gmail.com).
abstract: |
  Abstract abstract abstract.
keywords          : "visual illusions, illusion game, Pyllusion, personality, general factor"
wordcount         : "5114"
bibliography      : references.bib
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : yes
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
csl: utils/apa.csl
header-includes:
  - \usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
editor_options:
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
# options and parameters
options(digits = 3)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 450,
  fig.width = see::golden_ratio(9),
  fig.height = 9,
  fig.path = "figures/"
)

cache <- TRUE
```

<!-- Objective features -->
Technology allows already to create near-perfect simulations indistinguishable from reality. If real and fake stimuli are identical based on their objective characteristics, how can we make - hopefully accurate - judgments regarding their nature?

<!-- Context -->
Literatue shows that context surrounding stimuli plays an important role. But in the absence of context, what drives the beliefs of reality?

<!-- Internal features -->
Psychological factors. Stable dispositional traits. Reactive characteristics.

# Acknowledgments

We would like to thank STUDENT NAME for his contribution.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-09-12 preprocessing.R

@@ -74,7 +74,7 @@ preprocess_raw <- function(file) {
     Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block1$stimulus)),
     Delay1 = as.numeric(block1$time_elapsed),
     RT = as.numeric(data[data$screen == "questionnaire", "rt"]),
-    Goodlooking = datawizard::change_scale(answers$Physical_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
+    Beauty = datawizard::change_scale(answers$Physical_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
     Attractive = datawizard::change_scale(answers$General_Attractiveness, to = c(0.0001, 0.9999), range = c(0, 1)),
     Trustworthy = datawizard::change_scale(answers$Trustworthiness, to = c(0.0001, 0.9999), range = c(0, 1)),
     Familiar = datawizard::change_scale(answers$Familiarity, to = c(0.0001, 0.9999), range = c(0, 1))
@@ -87,6 +87,9 @@ preprocess_raw <- function(file) {
 
   # Format sexual orientation
   df$Sexual_Orientation <- ifelse(df$Sexual_Orientation == "Other", jsonlite::fromJSON(dem[4])$sexual_orientation, df$Sexual_Orientation)
+  df$Sexual_Orientation <- ifelse(df$Sexual_Orientation %in% c("I identify as poly-romantic and sexually attracted primarily to females"), "Homosexual", df$Sexual_Orientation)  # Because that person is female
+  df[grepl("a74bc_q0ukp", df$Participant), "Sex"] <- "Male"
+
 
   # Format education
   df$Education <- gsub("University (", "", df$Education, fixed = TRUE)
@@ -95,16 +98,20 @@ preprocess_raw <- function(file) {
 
   # Standardize demographics
   # unique(df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Latin", "Hisapanic", "Latino/Hispanic"), "Hispanic", df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Europe", "White"), "Caucasian", df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("South African Coloured"), "African", df$Ethnicity)
[…]

### 2022-09-13 analysis.Rmd
ms

@@
 
-plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size = 3) {
+plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 10, size = 4) {
   # library(emojifont)
@@
   ggplot(aes(x = x, y = y)) +
-  geom_area(fill = "#FF9800")
+  geom_area(fill = "#FF9800") +
+  labs(x = "Age", y = "") +
+  theme_modern()
 
@@
   scale_fill_viridis_d(guide = "none") + 
+  theme_modern() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
@@
 
-patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p8))
+patchwork::wrap_plots(list(p1, p2, p3, p5, p4, p6))
 ```
@@
   scale_linetype_manual(values = c("TRUE" = "solid", "FALSE" = "dashed")) +
-  scale_x_continuous(expand = c(0, 0), labels = scales::percent()) +
-  scale_y_continuous(expand = c(0, 0), labels = scales::percent()) +
+  scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
+  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
   facet_grid(y ~ x, switch = "both") +
@@
     scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
-    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
+    scale_y_continuous(expand = c(0, 0), breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c("Fake", "25%", "50%", "75%", "Real")) +
+    labs(y = "Simulation Monitoring") +
     guides(fill = guide_legend(override.aes = list(alpha = 1))) +
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width}
 rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
@@
 
-(rez_at$p +
+fig1a <- (rez_at$p +
   theme(axis.text.x = element_blank()) +
@@
   plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
-  plot_layout(guides = "collect")
+  plot_layout(guides = "collect") &
+  theme(legend.position='top', legend.title = element_blank())
+fig1a
 ```
@@
 
-## Interaction
+## Interaction with Self-Attractiveness
 
@@
 
-```{r message=FALSE, warning=FALSE}
-model <- glmmTMB::glmmTMB(Belief ~ 1 + (1 | Participant) + (1 | Stimulus), data = df, family = "binomial")
-dfsub <- modelbased::estimate_grouplevel(model) |>
-  filter(Group == "Participant") |>
-  transmute(Participant = Level, Simulation_Monitoring = Coefficient) |>
-  merge(dfsub, by = "Participant")
-
-model <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief + (Belief | Participant) + (1 | Stimulus), data = df, family = glmmTMB::beta_family())
-dfsub <- modelbased::estimate_grouplevel(model) |>
-  filter(Group == "Participant") |>
-  transmute(Participant = Level, Parameter, Coefficient) |>
-  pivot_wider(names_from = "Parameter", values_from = "Coefficient") |>
-  transmute(Participant, Confidence_Real_Model = BeliefReal, Confidence_Fake_Model = `(Intercept)`) |>
-  merge(dfsub, by = "Participant")
-```
-```{r message=FALSE, warning=FALSE}
-correlation::correlation(
-  dfsub[c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model")],
-  dfsub[c("Confidence_Fake", "Confidence_Real", "n_Real")],
-)
-```
-
 ### IPIP-6
@@
 
-plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey") {
+plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey", fillx = "purple") {
   param <- cor_test(dfsub, x, y, bayesian = TRUE)
@@
       size = 3,
-      color = fill,
+      color = fillx,
       # color = DVs[x],
@@
     labs(y = ylab, x = xlab) +
-    geom_label(data = label, aes(x = x, y = y), label = str2expression(label$label), hjust = 0, vjust = 1) +
-    theme_modern() +
-    ggside::geom_xsidedensity(fill = "grey", color = "white") +
+    geom_label(data = label, aes(x = x, y = y), label = str2expression(label$label), hjust = 0, vjust = 1, size=rel(3.5)) +
+    theme_modern(axis.title.space = 5) +
+    ggside::geom_xsidedensity(fill = fillx, color = "white") +
     ggside::geom_ysidedensity(fill = fill, color = "white") +
@@
 ```{r message=FALSE, warning=FALSE}
-sr <- c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model", "Confidence_Fake", "Confidence_Real", "n_Real")
+sr <- c("Confidence_Fake", "Confidence_Real", "n_Real")
 
@@
 filter(r, BF > 1)
-
-plot_correlation(dfsub,
-  x = "Confidence_Real",
-  y = "IPIP6_HonestyHumility",
-  xlab = "Confidence_Real",
-  ylab = "IPIP6_HonestyHumility",
-  fill = "grey"
-)
 ```
@@
 ```
+
+```{r message=FALSE, warning=FALSE}
+p1 <- plot_correlation(dfsub,
+  x = "IPIP6_HonestyHumility",
+  y = "Confidence_Real",
+  ylab = "Confidence that the stimulus is real",
+  xlab = "Honesty-Humility",
+  fillx = "#00BCD4",
+  fill = "#D81B60"
+) + 
+  scale_y_continuous(labels=scales::percent)
+
+p2 <- plot_correlation(dfsub,
+  y = "Confidence_Fake",
+  x = "AI_Enthusiasm",
+  ylab = "Confidence that the stimulus is fake",
+  xlab = "Enthusiasm about AI technology",
+  fillx = "#607D8B",
+  fill = "#3F51B5"
+) + 
+  scale_y_continuous(labels=scales::percent)
+
+p3 <- plot_correlation(dfsub,
+  y = "Confidence_Real",
+  x = "AI_Enthusiasm",
+  ylab = "Confidence that the stimulus is real",
+  xlab = "Enthusiasm about AI technology",
+  fillx = "#607D8B",
+  fill = "#D81B60"
+) + 
+  scale_y_continuous(labels=scales::percent)
+
+p4 <- plot_correlation(dfsub,
+  y = "Confidence_Real",
+  x = "FFNI_AcclaimSeeking",
+  ylab = "Confidence that the stimulus is real",
+  xlab = "Narcissism (Acclaim Seeking)",
+  fillx = "#FF9800",
+  fill = "#D81B60"
+) + 
+  scale_y_continuous(labels=scales::percent)
+
+p5 <- plot_correlation(dfsub,
+  y = "Confidence_Fake",
+  x = "FFNI_AcclaimSeeking",
+  ylab = "Confidence that the stimulus is fake",
+  xlab = "Narcissism (Acclaim Seeking)",
+  fillx = "#FF9800",
+  fill = "#3F51B5"
+) + 
+  scale_y_continuous(labels=scales::percent)
+
+p6 <- plot_correlation(dfsub,
+  y = "Confidence_Real",
+  x = "FFNI_GrandioseFantasies",
+  ylab = "Confidence that the stimulus is real",
+  xlab = "Narcissism (Grandiose Fantasies)",
+  fillx = "#FFC107",
+  fill = "#D81B60"
+) + 
+  scale_y_continuous(labels=scales::percent)
+
+fig <- wrap_elements(fig1a) /
+  wrap_elements(
+    ((p3 / p2) | (p1 / p6) | (p4 / p5)) + 
+  plot_annotation(title = "Personality Correlates of Simulation Monitoring Tendencies", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
+  ) +
+  plot_layout(heights = c(1.1, 0.9))
+
+ggsave("figures/Figure2.png", width=fig.height * 1.8, height=fig.width * 1.5)
+```

### 2022-09-13 submission/manuscript.Rmd
ms

@@
 
-<!-- Objective features -->
-Technology allows already to create near-perfect simulations indistinguishable from reality.
-If real and fake stimuli are identical based on their objective characteristics, how can we make - hopefully accurate - judgments regarding their nature?
+<!-- stakes and Post-truth era -->
+For the first time in Humanity's history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
+These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives which ground truth is often hard to access.
+They carry important consequences for the technological and entertainment sector, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination.
+This challenge is central to what has been coined as the "post-truth era" (**REF Lewandowsky et al., 2017**), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
+
+<!-- Ambiguous stimuli and irrelevance of objective features -->
+While there are still some fields in which simulations are not perfectly realistic (e.g., Computer Generated Images - CGI in movies often lack the details and appearance of reality), it is fair to assume that these technical limitations will become negligible in the near future.
+This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
 <!-- Context -->
-Literatue shows that context surrounding stimuli plays an important role. But in the absence of context, what drives the beliefs of reality?
+Literature shows that context surrounding stimuli plays an important role in the assessment of its reality (a process henceforth referred to as *simulation monitoring*, **REF makowski2019phenomenal and makowski 2018 thesis**).
+*Blabla some literature and references on how we use the context (source of information, author of information, knowledge about credibility and things like that)*.
+What drives the beliefs of reality in the absence of contextual cues (**Figure 1**).
+
+```{r message=FALSE, warning=FALSE, fig.cap="The decision to believe that an imbiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.", out.width="100%"}
+knitr::include_graphics("../figures/Figure1.png")
+```
 
 <!-- Internal features -->
-Psychological factors. Stable dispositional traits. Reactive characteristics.
+Psychological factors. Stable dispositional traits. Cognitive styles and the like
+
+<!-- Reactive features -->
+Aside from stimulus- and individual-realted characteristics, it is possible that simulation monitoring is driven by the interaction between the two, i.e., by the reaction associated with the experience of a given stimulus.
+For instance, emotions.
+Lines of evidence found in the link between presence and emotion (see *makowski2017avengers* and more) and fiction and emotion regulation (fictional reappraisal papers from makowski and more).
+Other include familiarity and self-relevance (can cite sperduti fiction 1 here).
+
+<!-- Attractiveness -->
+Images of faces, one of the most comon artificial inteligence (AI) target, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF).
+Talk about possible links between attractiveness and simulation monitoring
+
+<!-- Goals and hypotheses -->
+
+```{r message=FALSE, warning=FALSE, fig.cap="Top part shows blabla.", out.width="100%"}
+knitr::include_graphics("../figures/Figure2.png")
+```
+
+## Methods
+
+### Procedure
+
+### Participants
+
+## Results
+
+## Discussion
 

### 2022-09-13 submission/manuscript.tex
ms

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{visual illusions, illusion game, Pyllusion, personality, general factor\newline\indent Word count: 5114}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, \& S.H. Annabel Chen1, 2, 3, 4},
  pdflang={en-EN},
  pdfkeywords={visual illusions, illusion game, Pyllusion, personality, general factor},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}}
\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{1}, Stephanie Kirk\textsuperscript{1}, Ngoi Zi Liang\textsuperscript{1}, \& S.H. Annabel Chen\textsuperscript{1, 2, 3, 4}}
\date{}

\shorttitle{Illusion Game Validation}

\authornote{

Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (\href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}).

The authors made the following contributions. Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Ngoi Zi Liang: Project administration, Resources, Writing -- review \& editing; S.H. Annabel Chen: Project administration, Supervision, Writing -- review \& editing.

Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore. E-mail: \href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{2} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{3} National Institute of Education, Singapore\\\textsuperscript{4} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}

\abstract{%
Abstract abstract abstract.
}

\begin{document}
\maketitle

For the first time in Humanity's history, technology has enabled the creation of near-perfect simulations indistinguishable from reality. These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives which ground truth is often hard to access. They carry important consequences for the technological and entertainment sector, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination. This challenge is central to what has been coined as the ``post-truth era'' (\textbf{REF Lewandowsky et al., 2017}), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.

While there are still some fields in which simulations are not perfectly realistic (e.g., Computer Generated Images - CGI in movies often lack the details and appearance of reality), it is fair to assume that these technical limitations will become negligible in the near future. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?

Literature shows that context surrounding stimuli plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, \textbf{REF makowski2019phenomenal and makowski 2018 thesis}). \emph{Blabla some literature and references on how we use the context (source of information, author of information, knowledge about credibility and things like that)}. What drives the beliefs of reality in the absence of contextual cues (\textbf{Figure 1}).

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/Figure1} \caption{The decision to believe that an imbiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.}\label{fig:unnamed-chunk-2}
\end{figure}

Psychological factors. Stable dispositional traits. Cognitive styles and the like

Aside from stimulus- and individual-realted characteristics, it is possible that simulation monitoring is driven by the interaction between the two, i.e., by the reaction associated with the experience of a given stimulus. For instance, emotions. Lines of evidence found in the link between presence and emotion (see \emph{makowski2017avengers} and more) and fiction and emotion regulation (fictional reappraisal papers from makowski and more). Other include familiarity and self-relevance (can cite sperduti fiction 1 here).

Images of faces, one of the most comon artificial inteligence (AI) target, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF). Talk about possible links between attractiveness and simulation monitoring

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows blabla.}\label{fig:unnamed-chunk-3}
\end{figure}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

We would like to thank STUDENT NAME for his contribution.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

\clearpage
\renewcommand{\listfigurename}{Figure captions}

\end{document}

### 2022-09-13 analysis.Rmd
start results

@@
   filter(!Stimulus %in% extreme_items$Stimulus)
+
+extreme_items
 ```
@@
   ggside::scale_xsidey_continuous(expand = c(0, 0))
+
+df |> 
+  group_by(Participant, Belief) |> 
+  summarize(n = n() / 108, 
+            Confidence = mean(Belief_Confidence)) |> 
+  pivot_wider(values_from=c("n", "Confidence"), names_from="Belief") |> 
+  ungroup() |> 
+  describe_posterior(centrality = "mean", test=FALSE)
 ```
@@
 
-parameters::parameters(model)
+hdi(df$Delay)
+estimate_relation(model, at="Delay=c(0, 60)")
+
+parameters::parameters(model, effects="fixed", exponentiate=TRUE)
+parameters::parameters(m_conf, effects="fixed")
 ```

### 2022-09-13 submission/manuscript.Rmd
start results

@@
 
+### Data Analysis
+
+The real-fake ratings were converted into two scores.
+
 ## Results
 
+The analysis was carried out using *R 4.2* [**REF**], the *tidyverse* [**REF**], and the *easystats* collection of packages [**REFs for insight, parameters, performance, see**].
+
+### Manipulation Check
+
+Only one image file, classified as fake in 87.4\% of trials, yielded a strong simulation monitoring bias (> 85\%).
+This image was removed from further analysis (leaving 108 trials per participant).
+On average, across participants, 44\% of trials (95\% CI [0.11, 0.64]) was considered fake and 56\% of trials (95\% CI [0.36, 0.89]) was considered real.
+
+There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$ $z = -2.27$, $p = 0.023$).
+There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).
+
+### Determinants of Simualtion Monitoring
+
 ## Discussion
+
+Although expected, the first striking result is that despite all items being real photos from the same database, all people easily believe (to high degrees of confidence) that a significant proportion of them was fake.
+This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
 

### 2022-09-13 submission/manuscript.Rmd
update intro

--- 2022-09-12 submission/manuscript.Rmd
@@
   chunk_output_type: console
+bibliography: references.bib
 ---
@@
 
-<!-- Objective features -->
-Technology allows already to create near-perfect simulations indistinguishable from reality.
-If real and fake stimuli are identical based on their objective characteristics, how can we make - hopefully accurate - judgments regarding their nature?
+<!-- stakes and Post-truth era -->
+For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations  indistinguishable from reality.
+These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
+Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
+This challenge is  thus central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack  thereof) between authentic and simulated objects will play a critical role.
+
+<!-- Ambiguous stimuli and irrelevance of objective features -->
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain  key details and an overall appearance of reality), it is fair to assume that these technical limitations will become  negligible in the near future.
+In fact, in the field of face perception and recognition, recent research found images of  artificially-generated faces to be perceived as more real than real faces [@nightingale2022; @tucciarelli2020; @moshel2022].
+This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective  characteristics (for instance, facial features in the perception of real relative to fake faces; [@holmes2016; @moshel2022]), how can we make judgments regarding their nature?
 
 <!-- Context -->
-Literatue shows that context surrounding stimuli plays an important role. But in the absence of context, what drives the beliefs of reality?
+Literature shows that the context surrounding a stimulus often plays an important  role in the assessment of its reality (a process henceforth referred to as *simulation monitoring* [@makowski2019phenomenal; @makowski2018cognitive]).
+Whereas individuals could rely on the content of the stimulus, making a reality judgement based solely on this information could be too cognitively effortful, especially if the stimulus is imbued with ambiguity [@michael2021source; @susmann2021persuasion].
+As such, the Elaboration Likelihood Model(ELM) posits that people tend to draw on peripheral contextual cues, such as the source of the stimulus, credibility, authority and expertise of the source etc., to help facilitate their evaluation [petty1986elaboration].
+Accordingly, such reliance on peripheral cues has been consistently reported across multiple studies, most recently with regards to people's trust in news articles reporting on the COVID-19 pandemic [@susmann2021persuasion;@michael2021source].
+In the absence of these contextual information, however, what then  drives our beliefs of reality?
+(**Figure 1**).
+
+```{r message=FALSE, warning=FALSE, fig.cap="The decision to believe that an ambiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.", out.width="100%"}
+knitr::include_graphics("../figures/Figure1.png")
+```
 
 <!-- Internal features -->
-Psychological factors. Stable dispositional traits. Reactive characteristics.
+Similar to contextual cues, the inter-individual characteristics of the assessor also impacts whether a stimulus is ultimately perceived to be real (or fake).
+Factors such as the individual's cognitive style, prior beliefs, as well as personality traits have been shown to significantly impact people's belief in ambiguous stimuli [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
+Specifically, individuals with higher levels of analytical reasoning have been found to be better at distinguishing real from fake stimuli, possibly since detection of false information requires careful scrutinization and deliberation [@pehlivanoglu2021role; @pennycook2019lazy].
+Unsurprisingly, possessing prior knowledge or beliefs about the stimulus at hand also influences one's perception of it; biasing us to attend only to information in line with our predispositions (what is known as **confirmation bias**) [@britt2019reasoned].
+For instance, in a study conducted by [@tucciarelli2020], participants who were told about the presence of social agents reported lower levels of trust relative to those who were not relayed any information.
+Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
+
+<!-- Reactive features -->
+Aside from stimulus- and individual-related characteristics, it is possible that simulation monitoring is driven by an interaction between the two, i.e., by the reaction associated with the experience of a given stimulus.
+One way in which this is exemplified is via emotions.
+For instance, in the field of virtual reality (VR), emotional features have been shown to increase the virtual domain's presence, i.e., the extent to which the the system is able to deliver a convincing (real-like) environment with which an agent can interact [@sanchez2005presence; @makowski2017being].
+This hence implies that the inclusion of emotional features could increase people's belief in simulations.
+Indeed, several studies have suggested that heightened stimulus emotionality is associated with greater belief in fake, but not real, information [@martel2020reliance].
+On the contrary, research relating emotional works of fiction to simulation monitoring have instead found emotionality to be associated with reduced perceptions of realness [@makowski2019phenomenal], i.e., emotional stimuli were more likely perceived to be fake as opposed to real.
+However, since participants were told the descriptions corresponding to some of the stimuli were fake, the latter finding could be understood as a result of the participants engaging in spontaneous fictional appraisal, an emotion regulation mechanism in which individuals lower their perception of realness of the given stimulus by endowing it with a fictional context [@sperduti2017distinctive; @sperduti2016paradox].
+Moreover, when the stimuli was self-relevant, studies show that the experienced intensity of emotions was enhanced [@sperduti2016paradox; @goldstein2009pleasure].
+This hence implies that self-relevance could modulate the relationship between the emotionality of a stimulus and our perceptions of it's realness.
+Additionally, other features that drive individuals' evaluation of a stimulus, such as familiarity, have also been shown to correlate positively with the perception of it as truth [@begg1992dissociation]
+
+<!-- Attractiveness -->
+Images of faces, one of the most common artificial intelligence (AI) targets, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF).
+Talk about possible links between attractiveness and simulation monitoring
+
+<!-- Goals and hypotheses -->
+
+```{r message=FALSE, warning=FALSE, fig.cap="Top part shows blabla.", out.width="100%"}
+knitr::include_graphics("../figures/Figure2.png")
+```
+
+## Methods
+
+### Procedure
+
+### Participants
+
+### Data Analysis
+
+The real-fake ratings were converted into two scores.
+
+## Results
+
+The analysis was carried out using *R 4.2* [**REF**], the *tidyverse* [**REF**], and the *easystats* collection of packages [**REFs for insight, parameters, performance, see**].
+
+### Manipulation Check
+
+Only one image file, classified as fake in 87.4\% of trials, yielded a strong simulation monitoring bias (> 85\%).
+This image was removed from further analysis (leaving 108 trials per participant).
+On average, across participants, 44\% of trials (95\% CI [0.11, 0.64]) was considered fake and 56\% of trials (95\% CI [0.36, 0.89]) was considered real.
+
+There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$ $z = -2.27$, $p = 0.023$).
+There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).
+
+### Determinants of Simualtion Monitoring
+
+## Discussion
+
+Although expected, the first striking result is that despite all items being real photos from the same database, all people easily believe (to high degrees of confidence) that a significant proportion of them was fake.
+This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
 

### 2022-09-14 submission/manuscript.Rmd
update

@@
 For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
-Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
+These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
+Such advancements not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
 This challenge is thus central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack  thereof) between authentic and simulated objects will play a critical role.
@@
 <!-- Ambiguous stimuli and irrelevance of objective features -->
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain  key details and an overall appearance of reality), it is fair to assume that these technical limitations will become  negligible in the near future.
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details and an overall appearance of reality; cf "the uncanny valley effect"; [@mcdonnell2010face]), it is fair to assume that these technical limitations will become  negligible in the near future.
 In fact, in the field of face perception and recognition, recent research found images of  artificially-generated faces to be perceived as more real than real faces [@nightingale2022; @tucciarelli2020; @moshel2022].
@@
 <!-- Attractiveness -->
-Images of faces, one of the most common artificial intelligence (AI) targets, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF).
+Images of faces, one of the most common artificial intelligence (AI) targets, integrate components of emotional reaction, salience, self-relevance via attractiveness (REF).
 Talk about possible links between attractiveness and simulation monitoring

### 2022-09-14 submission/manuscript.Rmd
Update manuscript.Rmd

--- 2022-09-13 submission/manuscript.Rmd
@@
 Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
-This challenge is  thus central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack  thereof) between authentic and simulated objects will play a critical role.
+This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
 
 <!-- Ambiguous stimuli and irrelevance of objective features -->
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain  key details and an overall appearance of reality), it is fair to assume that these technical limitations will become  negligible in the near future.
-In fact, in the field of face perception and recognition, recent research found images of  artificially-generated faces to be perceived as more real than real faces [@nightingale2022; @tucciarelli2020; @moshel2022].
-This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective  characteristics (for instance, facial features in the perception of real relative to fake faces; [@holmes2016; @moshel2022]), how can we make judgments regarding their nature?
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images), it is fair to assume that these technical limitations will become negligible in the near future, in  particular in the field of faces generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
+This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
 <!-- Context -->
-Literature shows that the context surrounding a stimulus often plays an important  role in the assessment of its reality (a process henceforth referred to as *simulation monitoring* [@makowski2019phenomenal; @makowski2018cognitive]).
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
+The extensive search and processing of cues within ambiguous stimuli being and cognitively effortful [@michael2021source; @susmann2021persuasion].
 Whereas individuals could rely on the content of the stimulus, making a reality judgement based solely on this information could be too cognitively effortful, especially if the stimulus is imbued with ambiguity [@michael2021source; @susmann2021persuasion].
-As such, the Elaboration Likelihood Model(ELM) posits that people tend to draw on peripheral contextual cues, such as the source of the stimulus, credibility, authority and expertise of the source etc., to help facilitate their evaluation [petty1986elaboration].
+As such, the Elaboration Likelihood Model (ELM) posits that people tend to draw on peripheral contextual cues, such as the source of the stimulus, credibility, authority and expertise of the source etc., to help facilitate their evaluation [petty1986elaboration].
 Accordingly, such reliance on peripheral cues has been consistently reported across multiple studies, most recently with regards to people's trust in news articles reporting on the COVID-19 pandemic [@susmann2021persuasion;@michael2021source].

### 2022-09-14 submission/manuscript.Rmd

@@
 For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations  indistinguishable from reality.
-These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
+These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
 Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and  disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
@@
 <!-- Ambiguous stimuli and irrelevance of objective features -->
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images), it is fair to assume that these technical limitations will become negligible in the near future, in  particular in the field of faces generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
+While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, in  particular in the field of faces generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
 This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?

### 2022-09-14 submission/manuscript.Rmd
Update manuscript.Rmd

@@
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
-The extensive search and processing of cues within ambiguous stimuli being and cognitively effortful [@michael2021source; @susmann2021persuasion].
-Whereas individuals could rely on the content of the stimulus, making a reality judgement based solely on this information could be too cognitively effortful, especially if the stimulus is imbued with ambiguity [@michael2021source; @susmann2021persuasion].
-As such, the Elaboration Likelihood Model (ELM) posits that people tend to draw on peripheral contextual cues, such as the source of the stimulus, credibility, authority and expertise of the source etc., to help facilitate their evaluation [petty1986elaboration].
-Accordingly, such reliance on peripheral cues has been consistently reported across multiple studies, most recently with regards to people's trust in news articles reporting on the COVID-19 pandemic [@susmann2021persuasion;@michael2021source].
-In the absence of these contextual information, however, what then  drives our beliefs of reality?
-(**Figure 1**).
+The extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation [petty1986elaboration; @susmann2021persuasion; @michael2021source].
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult.
+In the absence of contextual information, what drives our beliefs of reality?
 
@@
 <!-- Internal features -->
-Similar to contextual cues, the inter-individual characteristics of the assessor also impacts whether a stimulus is ultimately perceived to be real (or fake).
-Factors such as the individual's cognitive style, prior beliefs, as well as personality traits have been shown to significantly impact people's belief in ambiguous stimuli [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
-Specifically, individuals with higher levels of analytical reasoning have been found to be better at distinguishing real from fake stimuli, possibly since detection of false information requires careful scrutinization and deliberation [@pehlivanoglu2021role; @pennycook2019lazy].
-Unsurprisingly, possessing prior knowledge or beliefs about the stimulus at hand also influences one's perception of it; biasing us to attend only to information in line with our predispositions (what is known as **confirmation bias**) [@britt2019reasoned].
-For instance, in a study conducted by [@tucciarelli2020], participants who were told about the presence of social agents reported lower levels of trust relative to those who were not relayed any information.
-Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
+The evidence shows that inter-individual characteristics play a role in the formation of beliefs of reality, with factors such as cognitive style, prior beliefs, and personality traits significantly impacting simulation monitoring [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
+For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy].
+Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information in line with our expectations [@britt2019reasoned], and dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
 
 <!-- Reactive features -->
-Aside from stimulus- and individual-related characteristics, it is possible that simulation monitoring is driven by an interaction between the two, i.e., by the reaction associated with the experience of a given stimulus.
-One way in which this is exemplified is via emotions.
-For instance, in the field of virtual reality (VR), emotional features have been shown to increase the virtual domain's presence, i.e., the extent to which the the system is able to deliver a convincing (real-like) environment with which an agent can interact [@sanchez2005presence; @makowski2017being].
-This hence implies that the inclusion of emotional features could increase people's belief in simulations.
-Indeed, several studies have suggested that heightened stimulus emotionality is associated with greater belief in fake, but not real, information [@martel2020reliance].
-On the contrary, research relating emotional works of fiction to simulation monitoring have instead found emotionality to be associated with reduced perceptions of realness [@makowski2019phenomenal], i.e., emotional stimuli were more likely perceived to be fake as opposed to real.
-However, since participants were told the descriptions corresponding to some of the stimuli were fake, the latter finding could be understood as a result of the participants engaging in spontaneous fictional appraisal, an emotion regulation mechanism in which individuals lower their perception of realness of the given stimulus by endowing it with a fictional context [@sperduti2017distinctive; @sperduti2016paradox].
-Moreover, when the stimuli was self-relevant, studies show that the experienced intensity of emotions was enhanced [@sperduti2016paradox; @goldstein2009pleasure].
-This hence implies that self-relevance could modulate the relationship between the emotionality of a stimulus and our perceptions of it's realness.
-Additionally, other features that drive individuals' evaluation of a stimulus, such as familiarity, have also been shown to correlate positively with the perception of it as truth [@begg1992dissociation]
+Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two, i.e., the subjective reaction associated with the experience of a given stimulus, contributes to simulation monitoring decisions.
+For instance, the intensity of experienced emotions have been shown to increase the sense of presence, i.e., the extent to which one feels like "being there", as if the movie or the VR environment was real [@sanchez2005presence; @makowski2017being], and beliefs that the stimuli were fake led to emotion down-regulation [@makowski2019phenomenal; sperduti2017distinctive].
+However, @martel2020reliance reported that heightened stimulus emotionality was associated with greater belief in fake, but not real, information.
+Other factors, such as the stimulus' perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity  [@begg1992dissociation], could also play a role in our processing and reaction to real vs.
+non-real material.
 

### 2022-09-14 submission/manuscript.Rmd
manu

@@
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
-The extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation [petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult.
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation [petty1986elaboration; @susmann2021persuasion; @michael2021source].
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult [*REF*].
 In the absence of contextual information, what drives our beliefs of reality?
@@
 <!-- Internal features -->
-The evidence shows that inter-individual characteristics play a role in the formation of beliefs of reality, with factors such as cognitive style, prior beliefs, and personality traits significantly impacting simulation monitoring [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
+Moreover, evidence from research indicates that inter-individual characteristics also play a crucial role in the formation of beliefs of reality, with factors such as cognitive style, prior beliefs, and personality traits significantly impacting simulation monitoring [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
 For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy].
@@
 Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two, i.e., the subjective reaction associated with the experience of a given stimulus, contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase the sense of presence, i.e., the extent to which one feels like "being there", as if the movie or the VR environment was real [@sanchez2005presence; @makowski2017being], and beliefs that the stimuli were fake led to emotion down-regulation [@makowski2019phenomenal; sperduti2017distinctive].
-However, @martel2020reliance reported that heightened stimulus emotionality was associated with greater belief in fake, but not real, information.
-Other factors, such as the stimulus' perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity  [@begg1992dissociation], could also play a role in our processing and reaction to real vs.
-non-real material.
+For instance, the intensity of experienced emotions have been shown to increase one's sense of presence in a simulated reality, i.e., the extent to which one feels like "being there", as if the movie or the VR environment was real [@sanchez2005presence; @makowski2017being], and beliefs that the stimuli were fake were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
+In line with these findings, other studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated  with greater belief [@martel2020reliance; @bago2022emotion].
+Additionally, other factors, such as the stimulus' perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
 
 <!-- Attractiveness -->
-Images of faces, one of the most common artificial intelligence (AI) targets, integrate components of emotional reaction, salience, self-relevance via attractiveness (REF).
-Talk about possible links between attractiveness and simulation monitoring
+With the advancement of technology, AI-generated images of faces have increasingly been used to study various cognitive mechanisms and processes, such as that underlying emotion processing [@dyck2008recognition; @dyck2010virtual].
+Notably, the ability to manipulate the degree of emotionality and salience of virtual faces, by changing its facial dimensions, make them ideal targets for simulation monitoring research [@fuentes2018evolutionary; @ferstl2018perceptual].
+To this effect, the attractiveness of AI-generated faces, which integrates both components of emotional intensity and saliency [@o2003beauty; @debruine2007dissociating; sobieraj2014beautiful], have indeed been associated with its perceived realness.
+To be specific, research findings suggest that artificially created faces were judged to be less attractive as compared to real faces [@liefooghe2022faces; tsikandilakis2019beauty; @diel2022familiarity].
+Interestingly, @liefooghe2022faces further reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
+Whereas such studies posit that lower perceived realness of a given stimulus leads to lower ratings of attractiveness, little is known about the impacts of attractiveness on simulation monitoring.
 
 <!-- Goals and hypotheses -->
+The goal of this study is therefore to determine whether the attractiveness of artificially-generated faces affects our reality judgement of it.
+Based on the Embodied Reality Theory [@makowski2018cognitive; @makowski2019phenomenal], which suggests that highly salient stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness of a given virtual stimulus, i.e., faces rated as highly attractive or unattractive will be judged to be more real.
+Additionally, we further postulate that inter-individual characteristics, such as personality traits and predisposed attitudes, will interact with the relationship between perceived realness and attractiveness.
+Moreover, given the well-established positive correlation between attractiveness and perceived trustworthiness as well as familiarity often reported in previous studies, we posit that virtual faces judged to be real will also be rated as more trustworthy and familiar [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial].
+
+In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
 
@@
 
+109 photos of neutral-expression faces of real individuals were retrieved from the American Multiracial Face Database (AMFD, [@chen2021broadening]).
+In the first part of the study, participants answered a series of personality questionnaires.
+This includes the *Mini-IPIP6* [24 items, @sibley2011], to measure 6 "normal" personality traits (Extraversion, Openness, Conscientiousness, Agreeableness, Neuroticism and Honesty-Humility); the *FFNI-BF* [30 items, @jauk2022validation] to measure 9 facets of narcissism (acclaim-seeking, distrust, entitlement, exploitativeness, indifference, lack of empathy, manipulativeness, need for admiration and thrill-seeking); the *R-GPTS* [18 items, @freeman2021revised], to measure 2 sub-scales of paranoid thinking (persecution and reference ideation); the *IUS-12* [12 items, @carleton2007fearing], to assess beliefs about uncertainty and the future; the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development], to assess social anxiety levels as well as a 10-item scale that measures participants general attitudes towards artificial intelligence (of which 5 items were adapted from the *GAAIS* [@schepman2020initial]).
+
+In the second part of this study, the set of facial images retrieved from the AMFD were presented to the participants for 500ms each, in a randomized order.
+Following each facial display, participants were asked to rate each face on its **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") using a visual analog scale.
+
+In the last part of the study, participants were informed that half of the facial images previously seen were AI-generated.
+The same set of facial images displayed before were then presented for a second set of trials in a new randomized order.
+As per the first set, each facial stimuli was presented for 500ms.
+After each display, participants were asked to judge whether they thought the face they saw was real (or fake) using a visual analog scale.
+
+This experiment was implemented using *jsPsych* [@de2015jspsych], and the full set of instructions is available in the experiment code.
+
 ### Participants
+
+103 participants were recruited via *Prolific* ([www.prolificacademic.co.uk](www.prolificacademic.co.uk)), a crowd-sourcing platform providing high data quality [@peer2022].
+The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
+Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 50 minutes to finish.
+Demographic variables (age, gender, and ethnicity) were self-reported on a voluntary basis.
+
+Upon inspection of stimuli ratings, attention check responses and total duration spent to complete the personality questionnaires, 3 participants were removed for spending an implausibly short time to finish the questionnaires and having very low correlations between their stimuli ratings and that of the normative distribution.
+
+The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48.0% females, 52.0% males, 0.0% other).
 
@@
 
-The analysis was carried out using *R 4.2* [**REF**], the *tidyverse* [**REF**], and the *easystats* collection of packages [**REFs for insight, parameters, performance, see**].
+The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
 

### 2022-09-15 analysis.Rmd
more stats

@@
   describe_posterior(centrality = "mean", test=FALSE)
+
+m <- glmmTMB::glmmTMB(Belief ~ 1 + (1|Participant) + (1|Stimulus), data=df, family="binomial")
+icc(m, by_group = TRUE)
 ```
@@
 
+correlation::correlation(df[IVs], partial=TRUE)
+```
+
+```{r message=FALSE, warning=FALSE}
 preds <- data.frame()
@@
 rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
-  formula = "Sex / poly(Beauty, 2) + Trustworthy + (1|Participant) + (1|Stimulus)",
+  formula = "Sex / poly(Beauty, 2) + Trustworthy + Familiar + (1|Participant) + (1|Stimulus)",
   var = "Beauty", fill = "#E91E63"
@@
 rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
-  formula = "Sex / poly(Trustworthy, 2) + Beauty + (1|Participant) + (1|Stimulus)",
+  formula = "Sex / poly(Trustworthy, 2) + Beauty + Familiar + (1|Participant) + (1|Stimulus)",
   var = "Trustworthy", fill = "#4CAF50"
@@
 rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
-  formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)",
+  formula = "Sex / poly(Familiar, 2) + Beauty + Trustworthy + (1|Participant) + (1|Stimulus)",
   var = "Familiar", fill = "#2196F3"

### 2022-09-15 submission/manuscript.Rmd
Update manuscript.Rmd
more stats

@@
 
-```{r message=FALSE, warning=FALSE, fig.cap="Top part shows blabla.", out.width="100%"}
-knitr::include_graphics("../figures/Figure2.png")
-```
-
 ## Methods
@@
 
-The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48.0% females, 52.0% males, 0.0% other).
+The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48% females, 52% males).
 
@@
 
-The real-fake ratings were converted into two scores.
+The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
+Models predicting the former were set as logistic mixed models (with the participants and images entered as random factors), and models modeling the latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) were modeled using beta regression models (suited for an outcome variable expressed in percentages).
+
+We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real pictures of faces) were indeed judged as fake in a sufficient proportion to warrant their analysis.
+Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).
+
+The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**.
+Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*.
+We took into account the gender of participants and stimuli by retaining the pictures that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+
+```{r message=FALSE, warning=FALSE, fig.cap="Top part shows blabla.", out.width="100%"}
+knitr::include_graphics("../figures/Figure2.png")
+```
+
+The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
+As all the details, scripts and complimentary analyses are available in open-access, the manuscript will focus on significant results.
 
@@
 
-The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
-
 ### Manipulation Check
 
-Only one image file, classified as fake in 87.4\% of trials, yielded a strong simulation monitoring bias (> 85\%).
-This image was removed from further analysis (leaving 108 trials per participant).
-On average, across participants, 44\% of trials (95\% CI [0.11, 0.64]) was considered fake and 56\% of trials (95\% CI [0.36, 0.89]) was considered real.
+Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials.
+This image was removed from further analysis, leaving 108 trials per participant.
+On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the pictures.
 
-There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$ $z = -2.27$, $p = 0.023$).
+There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$ $z = -2.27$, $p = .023$).
 There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).
 
-### Determinants of Simualtion Monitoring
+### Determinants of Simulation Monitoring
+
+Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.8%) with the belief that a stimulus was real ($\beta_{poly1} = 16.37$, $95\% CI = [7.76, 24.98]$ $z = 3.73$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.77$, $95\% CI = [1.41, 14.13]$ $z = 2.40$, $p = .017$), with both non-attractive and attractive faces being judged as more real.
+No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real ($\beta_{poly2} = 4.38$, $95\% CI = [0.96, 7.79]$ $z = 2.51$, $p = .012$).
+
+Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.5%) with the belief that a stimulus was real ($\beta_{poly1} = 9.54$, $95\% CI = [1.43, 17.65]$ $z = 2.31$, $p = .021$) for males only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 6.61$, $95\% CI = [1.98, 11.24]$ $z = 2.80$, $p = .005$).
+
+Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.60$, $95\% CI = [4.15, 19.06]$ $z = 3.05$, $p = .002$) for females only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces ($\beta_{poly2} = 6.47$, $95\% CI = [1.73, 11.21]$ $z = 2.68$, $p = .007$).
+
+We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%).
+However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$ $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$ $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$ $z = 1.96$, $p = .05$), for males only, suggesting that faces judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
 
@@
 This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
+In fact, stimuli-related and participant-related characteristics accounted for about only less than 20% of the variance in the beliefs, suggesting that a large part of it is related to other subjective processes.
+
+Though attractiveness does not seem to be the primary drive underlying simulation monitoring of face images, it does nonetheless display an association.
 

### 2022-09-15 analysis.Rmd
results

@@
 )
-
 parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness")
 
-m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Beauty, 2) * Self_Attractiveness) + Trustworthy + (1 | Participant) + (1 | Stimulus),
+m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Beauty, 2) * Self_Attractiveness) + Trustworthy + Familiar + (1 | Participant) + (1 | Stimulus),
   data = filter(df, Stimulus_Interest == TRUE),
@@
 )
-
 parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness")
@@
 
-### AI
+### Narcissism
 
 ```{r message=FALSE, warning=FALSE}
-rez <- parameters::n_factors(select(dfsub, starts_with("AI")))
-plot(rez)
-
-efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n = 3, rotation = "varimax", sort = TRUE)
-efa
-dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |>
-  cbind(dfsub)
-```
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("FFNI_")))
 filter(r, BF > 1)
@@
 
-### Narcissism
-
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, starts_with("FFNI_")))
-filter(r, BF > 1)
-```
-
 ### Paranoid Beliefs
@@
 r <- make_correlation(dfsub[sr], select(dfsub, starts_with("GPTS_")))
+filter(r, BF > 1)
+```
+
+### AI
+
+```{r message=FALSE, warning=FALSE}
+rez <- parameters::n_factors(select(dfsub, starts_with("AI")))
+plot(rez)
+
+efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n = 3, rotation = "varimax", sort = TRUE)
+efa
+dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |>
+  cbind(dfsub)
+```
+```{r message=FALSE, warning=FALSE}
+r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
 filter(r, BF > 1)

### 2022-09-15 submission/manuscript.Rmd
results

@@
   chunk_output_type: console
-bibliography: references.bib
 ---
@@
 We took into account the gender of participants and stimuli by retaining the pictures that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
 
@@
 
-The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@bayestestRArticle; @correlationArticle; @performanceArticle; @insightArticle].
+Finally, we investigated the inter-individual correlates of simulation monitoring by computing, for each participant, the proportion of faces judged as real (i.e., the overall bias towards one or the other belief), as well as the average confidence for faces judged as real, and fake.
+We assessed the link between these scores and dispositional traits using Bayesian correlation analysis [@makowski2019indices@; @correlationArticle].
+
+The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle].
 As all the details, scripts and complimentary analyses are available in open-access, the manuscript will focus on significant results.
@@
 
-There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$ $z = -2.27$, $p = .023$).
+There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
 There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).
@@
 
-Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.8%) with the belief that a stimulus was real ($\beta_{poly1} = 16.37$, $95\% CI = [7.76, 24.98]$ $z = 3.73$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.77$, $95\% CI = [1.41, 14.13]$ $z = 2.40$, $p = .017$), with both non-attractive and attractive faces being judged as more real.
-No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real ($\beta_{poly2} = 4.38$, $95\% CI = [0.96, 7.79]$ $z = 2.51$, $p = .012$).
+Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.8%) with the belief that a stimulus was real ($\beta_{poly1} = 16.37$, $95\% CI = [7.76, 24.98]$, $z = 3.73$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.77$, $95\% CI = [1.41, 14.13]$, $z = 2.40$, $p = .017$), with both non-attractive and attractive faces being judged as more real.
+No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real ($\beta_{poly2} = 4.38$, $95\% CI = [0.96, 7.79]$, $z = 2.51$, $p = .012$).
+There was no interaction with reported self-attractiveness.
 
-Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.5%) with the belief that a stimulus was real ($\beta_{poly1} = 9.54$, $95\% CI = [1.43, 17.65]$ $z = 2.31$, $p = .021$) for males only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 6.61$, $95\% CI = [1.98, 11.24]$ $z = 2.80$, $p = .005$).
+Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.5%) with the belief that a stimulus was real ($\beta_{poly1} = 9.54$, $95\% CI = [1.43, 17.65]$, $z = 2.31$, $p = .021$) for males only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 6.61$, $95\% CI = [1.98, 11.24]$, $z = 2.80$, $p = .005$).
+There was no interaction with reported self-attractiveness.
 
-Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.60$, $95\% CI = [4.15, 19.06]$ $z = 3.05$, $p = .002$) for females only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces ($\beta_{poly2} = 6.47$, $95\% CI = [1.73, 11.21]$ $z = 2.68$, $p = .007$).
+Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.60$, $95\% CI = [4.15, 19.06]$, $z = 3.05$, $p = .002$) for females only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces ($\beta_{poly2} = 6.47$, $95\% CI = [1.73, 11.21]$, $z = 2.68$, $p = .007$).
 
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$ $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$ $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$ $z = 1.96$, $p = .05$), for males only, suggesting that faces judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+
+### Inter-Individual Correlates of Simulation Monitoring
+
+Bayesian correlations with personality traits suggested that Honesty-Humility was negatively associated with the confidence in reality ($r = -0.21$, $95\% CI = [-0.38, -0.03]$, $BF_{10} = 3.57$), and positively associated with the Narcissism trait of Acclaim Seeking ($r = 0.26$, $95\% CI = [0.08, 0.43]$, $BF_{10} = 14.38$) and Grandiose Fantasies ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.18$).
+Acclaim Seeking was also positively related with the confidence in fake judgments ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.52$).
+No significant correlations was found for social anxiety, intolerance to uncertainty, or paranoid beliefs.
+
+Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
+Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real ($r = 0.24$, $95\% CI = [0.06, 0.41]$, $BF_{10} = 8.00$) and fake ($r = 0.28$, $95\% CI = [0.11, 0.44]$, $BF_{10} = 23.04$) judgments.
 

### 2022-09-15 submission/manuscript.tex
results

@@
 
-For the first time in Humanity's history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives which ground truth is often hard to access.
-They carry important consequences for the technological and entertainment sector, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination.
-This challenge is central to what has been coined as the ``post-truth era'' (\textbf{REF Lewandowsky et al., 2017}), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
+For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
+These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
+Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
+This issue is central to what has been coined the ``post-truth era'' (Lewandowsky et al., 2017), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
 
-While there are still some fields in which simulations are not perfectly realistic (e.g., Computer Generated Images - CGI in movies often lack the details and appearance of reality), it is fair to assume that these technical limitations will become negligible in the near future.
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of faces generation and replacement (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
 This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
-Literature shows that context surrounding stimuli plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, \textbf{REF makowski2019phenomenal and makowski 2018 thesis}).
-\emph{Blabla some literature and references on how we use the context (source of information, author of information, knowledge about credibility and things like that)}.
-What drives the beliefs of reality in the absence of contextual cues (\textbf{Figure 1}).
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (Makowski, 2018; a process henceforth referred to as \emph{simulation monitoring}, Makowski, Sperduti, et al., 2019).
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation {[}petty1986elaboration; Susmann et al.
+(2021); Michael and Sanson (2021){]}.
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult {[}\emph{REF}{]}.
+In the absence of contextual information, what drives our beliefs of reality?
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figures/Figure1} \caption{The decision to believe that an imbiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.}\label{fig:unnamed-chunk-2}
+\includegraphics[width=1\linewidth]{../figures/Figure1} \caption{The decision to believe that an ambiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.}\label{fig:unnamed-chunk-2}
 \end{figure}
 
-Psychological factors. Stable dispositional traits. Cognitive styles and the like
+Moreover, evidence from research indicates that inter-individual characteristics also play a crucial role in the formation of beliefs of reality, with factors such as cognitive style, prior beliefs, and personality traits significantly impacting simulation monitoring (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
+For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019).
+Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information in line with our expectations (Britt et al., 2019), and dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
 
-Aside from stimulus- and individual-realted characteristics, it is possible that simulation monitoring is driven by the interaction between the two, i.e., by the reaction associated with the experience of a given stimulus.
-For instance, emotions.
-Lines of evidence found in the link between presence and emotion (see \emph{makowski2017avengers} and more) and fiction and emotion regulation (fictional reappraisal papers from makowski and more).
-Other include familiarity and self-relevance (can cite sperduti fiction 1 here).
+Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two, i.e., the subjective reaction associated with the experience of a given stimulus, contributes to simulation monitoring decisions.
+For instance, the intensity of experienced emotions have been shown to increase one's sense of presence in a simulated reality, i.e., the extent to which one feels like ``being there'', as if the movie or the VR environment was real (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005), and beliefs that the stimuli were fake were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
+In line with these findings, other studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
+Additionally, other factors, such as the stimulus' perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in our processing and reaction to real as opposed to non-real material.
 
-Images of faces, one of the most comon artificial inteligence (AI) target, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF).
-Talk about possible links between attractiveness and simulation monitoring
+With the advancement of technology, AI-generated images of faces have increasingly been used to study various cognitive mechanisms and processes, such as that underlying emotion processing (Dyck et al., 2008, 2010).
+Notably, the ability to manipulate the degree of emotionality and salience of virtual faces, by changing its facial dimensions, make them ideal targets for simulation monitoring research (Ferstl \& McDonnell, 2018; Fuentes-Hurtado et al., 2018).
+To this effect, the attractiveness of AI-generated faces, which integrates both components of emotional intensity and saliency {[}O'Doherty et al.
+(2003); DeBruine et al.
+(2007); sobieraj2014beautiful{]}, have indeed been associated with its perceived realness.
+To be specific, research findings suggest that artificially created faces were judged to be less attractive as compared to real faces {[}Liefooghe et al.
+(2022); tsikandilakis2019beauty; Diel and Lewis (2022){]}.
+Interestingly, Liefooghe et al.
+(2022) further reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
+Whereas such studies posit that lower perceived realness of a given stimulus leads to lower ratings of attractiveness, little is known about the impacts of attractiveness on simulation monitoring.
 
-\begin{figure}
-\includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows blabla.}\label{fig:unnamed-chunk-3}
-\end{figure}
+The goal of this study is therefore to determine whether the attractiveness of artificially-generated faces affects our reality judgement of it.
+Based on the Embodied Reality Theory (Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that highly salient stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness of a given virtual stimulus, i.e., faces rated as highly attractive or unattractive will be judged to be more real.
+Additionally, we further postulate that inter-individual characteristics, such as personality traits and predisposed attitudes, will interact with the relationship between perceived realness and attractiveness.
+Moreover, given the well-established positive correlation between attractiveness and perceived trustworthiness as well as familiarity often reported in previous studies, we posit that virtual faces judged to be real will also be rated as more trustworthy and familiar (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011).
+
+In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
 
@@
 
+109 photos of neutral-expression faces of real individuals were retrieved from the American Multiracial Face Database (AMFD, (Chen et al., 2021)).
+In the first part of the study, participants answered a series of personality questionnaires.
+This includes the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011), to measure 6 ``normal'' personality traits (Extraversion, Openness, Conscientiousness, Agreeableness, Neuroticism and Honesty-Humility); the \emph{FFNI-BF} (30 items, Jauk et al., 2022) to measure 9 facets of narcissism (acclaim-seeking, distrust, entitlement, exploitativeness, indifference, lack of empathy, manipulativeness, need for admiration and thrill-seeking); the \emph{R-GPTS} (18 items, Freeman et al., 2021), to measure 2 sub-scales of paranoid thinking (persecution and reference ideation); the \emph{IUS-12} (12 items, Carleton et al., 2007), to assess beliefs about uncertainty and the future; the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012), to assess social anxiety levels as well as a 10-item scale that measures participants general attitudes towards artificial intelligence (of which 5 items were adapted from the \emph{GAAIS} (Schepman \& Rodway, 2020)).
+
+In the second part of this study, the set of facial images retrieved from the AMFD were presented to the participants for 500ms each, in a randomized order.
+Following each facial display, participants were asked to rate each face on its \textbf{Attractiveness} (``I find this person attractive''), \textbf{Beauty} (``This face is good-looking''), \textbf{Trustworthiness} (``I find this person trustworthy'') and \textbf{Familiarity} (``This person reminds me of someone I know'') using a visual analog scale.
+
+In the last part of the study, participants were informed that half of the facial images previously seen were AI-generated.
+The same set of facial images displayed before were then presented for a second set of trials in a new randomized order.
+As per the first set, each facial stimuli was presented for 500ms.
+After each display, participants were asked to judge whether they thought the face they saw was real (or fake) using a visual analog scale.
+
+This experiment was implemented using \emph{jsPsych} (De Leeuw, 2015), and the full set of instructions is available in the experiment code.
+
 \hypertarget{participants}{%
 \subsubsection{Participants}\label{participants}}
+
+103 participants were recruited via \emph{Prolific} (\url{www.prolificacademic.co.uk}), a crowd-sourcing platform providing high data quality (Peer et al., 2022).
+The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
+Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 50 minutes to finish.
+Demographic variables (age, gender, and ethnicity) were self-reported on a voluntary basis.
+
+Upon inspection of stimuli ratings, attention check responses and total duration spent to complete the personality questionnaires, 3 participants were removed for spending an implausibly short time to finish the questionnaires and having very low correlations between their stimuli ratings and that of the normative distribution.
+
+The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: {[}19, 66{]}; Sex: 48\% females, 52\% males).
+
+\hypertarget{data-analysis}{%
+\subsubsection{Data Analysis}\label{data-analysis}}
+
+The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two distinct mechanisms: the dichotomous \emph{belief} (real or fake, derived based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
+Models predicting the former were set as logistic mixed models (with the participants and images entered as random factors), and models modeling the latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) were modeled using beta regression models (suited for an outcome variable expressed in percentages).
+
+We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real pictures of faces) were indeed judged as fake in a sufficient proportion to warrant their analysis.
+Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).
+
+The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (\textbf{Figure 2}.
+Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables \emph{mutatis mutandis}.
+We took into account the gender of participants and stimuli by retaining the pictures that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows blabla.}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+Finally, we investigated the inter-individual correlates of simulation monitoring by computing, for each participant, the proportion of faces judged as real (i.e., the overall bias towards one or the other belief), as well as the average confidence for faces judged as real, and fake.
+We assessed the link between these scores and dispositional traits using Bayesian correlation analysis (Makowski, Ben-Shachar, Chen, et al., 2019@; Makowski et al., 2020).
+
+The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski, Ben-Shachar, \& Lüdecke, 2019).
+As all the details, scripts and complimentary analyses are available in open-access, the manuscript will focus on significant results.
 
@@
 
+\hypertarget{manipulation-check}{%
+\subsubsection{Manipulation Check}\label{manipulation-check}}
+
+Only one image file yielded a strong simulation monitoring bias (\textgreater{} 85\%), being classified as fake in 87.4\% of trials.
+This image was removed from further analysis, leaving 108 trials per participant.
+On average, across participants, 44\% of images (95\% CI {[}0.11, 0.64{]}) were judged as fake and 56\% of images (95\% CI {[}0.36, 0.89{]}) as real.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5\% for the participants and 8.7\% for the pictures.
+
+There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min (\(OR = 0.99\), \(95\% CI = [0.99, 1.00]\), \(z = -2.27\), \(p = .023\)).
+There was also a significant negative effect on judgment confidence, but only in the real condition (\(\beta = -0.005\), \(95\% CI = [-0.1, 0.0]\), \(p = .023\)).
+
+\hypertarget{determinants-of-simulation-monitoring}{%
+\subsubsection{Determinants of Simulation Monitoring}\label{determinants-of-simulation-monitoring}}
+
+Attractiveness had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.8\%) with the belief that a stimulus was real (\(\beta_{poly1} = 16.37\), \(95\% CI = [7.76, 24.98]\), \(z = 3.73\), \(p < .001\)) for males, and a quadratic relationship for females (\(\beta_{poly2} = 7.77\), \(95\% CI = [1.41, 14.13]\), \(z = 2.40\), \(p = .017\)), with both non-attractive and attractive faces being judged as more real.
+No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real (\(\beta_{poly2} = 4.38\), \(95\% CI = [0.96, 7.79]\), \(z = 2.51\), \(p = .012\)).
+There was no interaction with reported self-attractiveness.
+
+Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 3.5\%) with the belief that a stimulus was real (\(\beta_{poly1} = 9.54\), \(95\% CI = [1.43, 17.65]\), \(z = 2.31\), \(p = .021\)) for males only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces (\(\beta_{poly2} = 6.61\), \(95\% CI = [1.98, 11.24]\), \(z = 2.80\), \(p = .005\)).
+There was no interaction with reported self-attractiveness.
+
+Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 3.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 11.60\), \(95\% CI = [4.15, 19.06]\), \(z = 3.05\), \(p = .002\)) for females only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces (\(\beta_{poly2} = 6.47\), \(95\% CI = [1.73, 11.21]\), \(z = 2.68\), \(p = .007\)).
+
+We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness (\(R^2_{marginal}\) = 3.0\%).
+However, a significant positive and linear relationship was found with the confidence in faces judged as real (\(\beta_{poly1} = 9.31\), \(95\% CI = [3.45, 15.17]\), \(z = -3.11\), \(p = .002\)), and a quadratic relationship for faces judged as fake (\(\beta_{poly1} = -12.67\), \(95\% CI = [-19.87, -5.47]\), \(z = -3.45\), \(p < .001\); \(\beta_{poly2} = 8.14\), \(95\% CI = [0.01, 16.28]\), \(z = 1.96\), \(p = .05\)), for males only, suggesting that faces judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+
+\hypertarget{inter-individual-correlates-of-simulation-monitoring}{%
+\subsubsection{Inter-Individual Correlates of Simulation Monitoring}\label{inter-individual-correlates-of-simulation-monitoring}}
+
+Bayesian correlations with personality traits suggested that Honesty-Humility was negatively associated with the confidence in reality (\(r = -0.21\), \(95\% CI = [-0.38, -0.03]\), \(BF_{10} = 3.57\)), and positively associated with the Narcissism trait of Acclaim Seeking (\(r = 0.26\), \(95\% CI = [0.08, 0.43]\), \(BF_{10} = 14.38\)) and Grandiose Fantasies (\(r = 0.22\), \(95\% CI = [0.04, 0.40]\), \(BF_{10} = 4.18\)).
+Acclaim Seeking was also positively related with the confidence in fake judgments (\(r = 0.22\), \(95\% CI = [0.04, 0.40]\), \(BF_{10} = 4.52\)).
+No significant correlations was found for social anxiety, intolerance to uncertainty, or paranoid beliefs.
+
+Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
+Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real (\(r = 0.24\), \(95\% CI = [0.06, 0.41]\), \(BF_{10} = 8.00\)) and fake (\(r = 0.28\), \(95\% CI = [0.11, 0.44]\), \(BF_{10} = 23.04\)) judgments.
+
 \hypertarget{discussion}{%
 \subsection{Discussion}\label{discussion}}
+
+Although expected, the first striking result is that despite all items being real photos from the same database, all people easily believe (to high degrees of confidence) that a significant proportion of them was fake.
+This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
+In fact, stimuli-related and participant-related characteristics accounted for about only less than 20\% of the variance in the beliefs, suggesting that a large part of it is related to other subjective processes.
+
+Though attractiveness does not seem to be the primary drive underlying simulation monitoring of face images, it does nonetheless display an association.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
+Bago, B., Rosenzweig, L. R., Berinsky, A. J., \& Rand, D. G. (2022). Emotion may predict susceptibility to fake news but emotion regulation does not seem to help. \emph{Cognition and Emotion}, 1--15.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
+Bartosik, B., Wojcik, G.
+M., Brzezicka, A., \& Kawiak, A.
+(2021).
+Are you able to trust me?
+Analysis of the relationships between personality traits and the assessment of attractiveness and trust.
+\emph{Frontiers in Human Neuroscience}, \emph{15}, 685530.
+
+\leavevmode\vadjust pre{\hypertarget{ref-begg1992dissociation}{}}%
+Begg, I.
+M., Anas, A., \& Farinacci, S.
+(1992).
+Dissociation of processes in belief: Source recollection, statement familiarity, and the illusion of truth.
+\emph{Journal of Experimental Psychology: General}, \emph{121}(4), 446.
+
+\leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
+Britt, M. A., Rouet, J.-F., Blaum, D., \& Millis, K. (2019). A reasoned approach to dealing with fake news. \emph{Policy Insights from the Behavioral and Brain Sciences}, \emph{6}(1), 94--101.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
+Bryanov, K., \& Vziatysheva, V. (2021). Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS One}, \emph{16}(6), e0253717.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
+Carleton, R.
+N., Norton, M.
+P.
+J., \& Asmundson, G.
+J.
+(2007).
+Fearing the unknown: A short version of the intolerance of uncertainty scale.
+\emph{Journal of Anxiety Disorders}, \emph{21}(1), 105--117.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021broadening}{}}%
+Chen, J. M., Norman, J. B., \& Nam, Y. (2021). Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods}, \emph{53}(1), 371--389.
+
+\leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
+De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-debruine2007dissociating}{}}%
+DeBruine, L.
+M., Jones, B.
+C., Unger, L., Little, A.
+C., \& Feinberg, D.
+R.
+(2007).
+Dissociating averageness and attractiveness: Attractive faces are not always average.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{33}(6), 1420.
+
+\leavevmode\vadjust pre{\hypertarget{ref-diel2022familiarity}{}}%
+Diel, A., \& Lewis, M. (2022). Familiarity, orientation, and realism increase face uncanniness by sensitizing to facial distortions. \emph{Journal of Vision}, \emph{22}(4), 14--14.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dyck2008recognition}{}}%
+Dyck, M., Winbeck, M., Leiberg, S., Chen, Y., Gur, R. C., \& Mathiak, K. (2008). Recognition profile of emotions in natural and virtual faces. \emph{PloS One}, \emph{3}(11), e3628.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dyck2010virtual}{}}%
+Dyck, M., Winbeck, M., Leiberg, S., Chen, Y., \& Mathiak, K.
+(2010).
+Virtual faces as a tool to study emotion recognition deficits in schizophrenia.
+\emph{Psychiatry Research}, \emph{179}(3), 247--252.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ecker2022psychological}{}}%
+Ecker, U.
+K., Lewandowsky, S., Cook, J., Schmid, P., Fazio, L.
+K., Brashier, N., Kendeou, P., Vraga, E.
+K., \& Amazeen, M.
+A.
+(2022).
+The psychological drivers of misinformation belief and its resistance to correction.
+\emph{Nature Reviews Psychology}, \emph{1}(1), 13--29.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ferstl2018perceptual}{}}%
+Ferstl, Y., \& McDonnell, R.
+(2018).
+A perceptual study on the manipulation of facial features for trait portrayal in virtual agents.
+\emph{Proceedings of the 18th International Conference on Intelligent Virtual Agents}, 281--288.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2021revised}{}}%
+Freeman, D., Loe, B.
+S., Kingdon, D., Startup, H., Molodynski, A., Rosebrock, L., Brown, P., Sheaves, B., Waite, F., \& Bird, J.
+C.
+(2021).
+The revised green et al., Paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
+\emph{Psychological Medicine}, \emph{51}(2), 244--253.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fuentes2018evolutionary}{}}%
+Fuentes-Hurtado, F., Diego-Mas, J. A., Naranjo, V., \& Alcañiz, M. (2018). Evolutionary computation for modelling social traits in realistic looking synthetic faces. \emph{Complexity}, \emph{2018}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
+Garrido, M. V., \& Prada, M. (2017). KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces. \emph{Frontiers in Psychology}, \emph{8}, 2181.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
+Goldstein, T.
+R.
+(2009).
+The pleasure of unadulterated sadness: Experiencing sorrow in fiction, nonfiction, and" in person.".
+\emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4), 232.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
+Jauk, E., Olaru, G., Schürch, E., Back, M.
+D., \& Morf, C.
+C.
+(2022).
+Validation of the german five-factor narcissism inventory and construction of a brief form using ant colony optimization.
+\emph{Assessment}, 10731911221075761.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2017beyond}{}}%
+Lewandowsky, S., Ecker, U.
+K., \& Cook, J.
+(2017).
+Beyond misinformation: Understanding and coping with the {``post-truth''} era.
+\emph{Journal of Applied Research in Memory and Cognition}, \emph{6}(4), 353--369.
+
+\leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
+Liefooghe, B., Oliveira, M., Leisten, L. M., Hoogers, E., Aarts, H., \& Hortensius, R. (2022). \emph{Faces merely labelled as artificial are trusted less}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-little2011facial}{}}%
+Little, A.
+C., Jones, B.
+C., \& DeBruine, L.
+M.
+(2011).
+Facial attractiveness: Evolutionary based research.
+\emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{366}(1571), 1638--1659.
+
+\leavevmode\vadjust pre{\hypertarget{ref-parametersArticle}{}}%
+Lüdecke, D., Ben-Shachar, M., Patil, I., \& Makowski, D.
+(2020).
+Extracting, computing and exploring the parameters of statistical models using {R}.
+\emph{Journal of Open Source Software}, \emph{5}(53), 2445.
+\url{https://doi.org/10.21105/joss.02445}
+
+\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
+Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., \& Makowski, D.
+(2021).
+{performance}: An {R} package for assessment, comparison and testing of statistical models.
+\emph{Journal of Open Source Software}, \emph{6}(60), 3139.
+\url{https://doi.org/10.21105/joss.03139}
+
+\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
+Lüdecke, D., Waggoner, P., \& Makowski, D.
+(2019).
+Insight: A unified interface to access information from model objects in {R}.
+\emph{Journal of Open Source Software}, \emph{4}(38), 1412.
+\url{https://doi.org/10.21105/joss.01412}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2018cognitive}{}}%
+Makowski, D. (2018). \emph{Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal} {[}PhD thesis{]}. Sorbonne Paris Cit{é}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2019indices}{}}%
+Makowski, D., Ben-Shachar, M. S., Chen, S. A., \& Lüdecke, D. (2019). Indices of effect existence and significance in the bayesian framework. \emph{Frontiers in Psychology}, \emph{10}, 2767.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%
+Makowski, D., Ben-Shachar, M., \& Lüdecke, D.
+(2019).
+{bayestestR}: Describing effects and their uncertainty, existence and significance within the {Bayesian} framework.
+\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
+\url{https://doi.org/10.21105/joss.01541}
+
+\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
+Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D.
+(2020).
+Methods and algorithms for correlation analysis in {R}.
+\emph{Journal of Open Source Software}, \emph{5}(51), 2306.
+\url{https://doi.org/10.21105/joss.02306}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2017being}{}}%
+Makowski, D., Sperduti, M., Nicolas, S., \& Piolino, P. (2017). {``Being there''} and remembering it: Presence improves memory encoding. \emph{Consciousness and Cognition}, \emph{53}, 194--202.
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
+Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
+(2019).
+Phenomenal, bodily and brain correlates of fictional reappraisal as an implicit emotion regulation strategy.
+\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 877--897.
+
+\leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
+Martel, C., Pennycook, G., \& Rand, D. G. (2020). Reliance on emotion promotes belief in fake news. \emph{Cognitive Research: Principles and Implications}, \emph{5}(1), 1--20.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcdonnell2010face}{}}%
+McDonnell, R., \& Breidt, M. (2010). Face reality: Investigating the uncanny valley for virtual faces. In \emph{ACM SIGGRAPH ASIA 2010 sketches} (pp. 1--2).
+
+\leavevmode\vadjust pre{\hypertarget{ref-michael2021source}{}}%
+Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moshel2022}{}}%
+Moshel, M.
+L., Robinson, A.
+K., Carlson, T.
+A., \& Grootswagers, T.
+(2022).
+Are you for real?
+Decoding realistic AI-generated faces from neural activity.
+\emph{Vision Research}, \emph{199}, 108079.
+\url{https://doi.org/10.1016/j.visres.2022.108079}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nightingale2022}{}}%
+Nightingale, S.
+J., \& Farid, H.
+(2022).
+AI-synthesized faces are indistinguishable from real faces and more trustworthy.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(8), e2120481119.
+\url{https://doi.org/10.1073/pnas.2120481119}
+
+\leavevmode\vadjust pre{\hypertarget{ref-o2003beauty}{}}%
+O'Doherty, J., Winston, J., Critchley, H., Perrett, D., Burt, D.
+M., \& Dolan, R.
+J.
+(2003).
+Beauty in a smile: The role of medial orbitofrontal cortex in facial attractiveness.
+\emph{Neuropsychologia}, \emph{41}(2), 147--155.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
+Pantserev, K.
+(2020).
+\emph{The malicious use of AI-based deepfake technology as the new threat to psychological security and political stability} (pp.
+37--55).
+\url{https://doi.org/10.1007/978-3-030-35746-7_3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peer2022}{}}%
+Peer, E., Rothschild, D., Gordon, A., Evernden, Z., \& Damer, E.
+(2022).
+Data quality of platforms and panels for online behavioral research.
+\emph{Behavior Research Methods}, \emph{54}(4), 1643--1662.
+\url{https://doi.org/10.3758/s13428-021-01694-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pehlivanoglu2021role}{}}%
+Pehlivanoglu, D., Lin, T., Deceus, F., Heemskerk, A., Ebner, N.
+C., \& Cahill, B.
+S.
+(2021).
+The role of analytical reasoning and source credibility on the evaluation of real and fake full-length news articles.
+\emph{Cognitive Research: Principles and Implications}, \emph{6}(1), 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pennycook2019lazy}{}}%
+Pennycook, G., \& Rand, D. G. (2019). Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning. \emph{Cognition}, \emph{188}, 39--50.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
+Peters, L., Sunderland, M., Andrews, G., Rapee, R.
+M., \& Mattick, R.
+P.
+(2012).
+Development of a short form social interaction anxiety (SIAS) and social phobia scale (SPS) using nonparametric item response theory: The SIAS-6 and the SPS-6.
+\emph{Psychological Assessment}, \emph{24}(1), 66.
+
+\leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
+Piksa, M., Noworyta, K., Piasecki, J., Gwiazdzinski, P., Gundersen, A.
+B., Kunst, J., \& Rygula, R.
+(2022).
+Cognitive processes and personality traits underlying four phenotypes of susceptibility to (mis) information.
+\emph{Frontiers in Psychiatry}, 1142.
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
+R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
+Sanchez-Vives, M. V., \& Slater, M. (2005). From presence to consciousness through virtual reality. \emph{Nature Reviews Neuroscience}, \emph{6}(4), 332--339.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schepman2020initial}{}}%
+Schepman, A., \& Rodway, P. (2020). Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in Human Behavior Reports}, \emph{1}, 100014.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
+Sibley, C., Luyten, N., Wolfman, M., Mobberley, A., Wootton, L.
+W., Hammond, M., Sengupta, N., Perry, R., West-Newman, T., Wilson, M., McLellan, L., Hoverd, W.
+J., \& Robertson, A.
+(2011).
+The mini-IPIP6: Validation and extension of a short measure of the big-six factors of personality in new zealand.
+\emph{New Zealand Journal of Psychology}, \emph{40}, 142--159.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sindermann2020short}{}}%
+Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology}, \emph{36}, 44--48.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperduti2016paradox}{}}%
+Sperduti, M., Arcangeli, M., Makowski, D., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
+(2016).
+The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance.
+\emph{Acta Psychologica}, \emph{165}, 53--59.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperduti2017distinctive}{}}%
+Sperduti, M., Makowski, D., Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
+(2017).
+The distinctive role of executive functions in implicit emotion regulation.
+\emph{Acta Psychologica}, \emph{173}, 13--20.
+
+\leavevmode\vadjust pre{\hypertarget{ref-susmann2021persuasion}{}}%
+Susmann, M.
+W., Xu, M., Clark, J.
+K., Wallace, L.
+E., Blankenship, K.
+L., Philipp-Muller, A.
+Z., Luttrell, A., Wegener, D.
+T., \& Petty, R.
+E.
+(2021).
+Persuasion amidst a pandemic: Insights from the elaboration likelihood model.
+\emph{European Review of Social Psychology}, 1--37.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
+Tucciarelli, R., Vehar, N., \& Tsakiris, M. (2020). \emph{On the realness of people who do not exist: the social processing of artificial faces}. \url{https://doi.org/10.31234/osf.io/dnk9x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
+L., Miller, E., Bache, S.
+M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
+P., Spinu, V., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
 \end{CSLReferences}

### 2022-09-15 submission/manuscript.Rmd
intro

@@
 <!-- Attractiveness -->
-With the advancement of technology, AI-generated images of faces have increasingly been used to study various cognitive mechanisms and processes, such as that underlying emotion processing [@dyck2008recognition; @dyck2010virtual].
-Notably, the ability to manipulate the degree of emotionality and salience of virtual faces, by changing its facial dimensions, make them ideal targets for simulation monitoring research [@fuentes2018evolutionary; @ferstl2018perceptual].
-To this effect, the attractiveness of AI-generated faces, which integrates both components of emotional intensity and saliency [@o2003beauty; @debruine2007dissociating; sobieraj2014beautiful], have indeed been associated with its perceived realness.
-To be specific, research findings suggest that artificially created faces were judged to be less attractive as compared to real faces [@liefooghe2022faces; tsikandilakis2019beauty; @diel2022familiarity].
-Interestingly, @liefooghe2022faces further reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas such studies posit that lower perceived realness of a given stimulus leads to lower ratings of attractiveness, little is known about the impacts of attractiveness on simulation monitoring.
+AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of faces evaluation, such as trustworthiness or attractiveness (**REF**).
+Interestingly, several studies report that artificially created faces were judged to be less attractive (**QUESTION: was their nature known to the participant?**) as compared to real faces [@tsikandilakis2019beauty; @diel2022familiarity], and @liefooghe2022faces further reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
+Whereas this line of evidence suggests that beliefs of reality have an effect on attractiveness ratings of faces, the opposite question, whether attractiveness could drive beliefs of reality, has received no attention to date.
 
 <!-- Goals and hypotheses -->
-The goal of this study is therefore to determine whether the attractiveness of artificially-generated faces affects our reality judgement of it.
-Based on the Embodied Reality Theory [@makowski2018cognitive; @makowski2019phenomenal], which suggests that highly salient stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness of a given virtual stimulus, i.e., faces rated as highly attractive or unattractive will be judged to be more real.
-Additionally, we further postulate that inter-individual characteristics, such as personality traits and predisposed attitudes, will interact with the relationship between perceived realness and attractiveness.
-Moreover, given the well-established positive correlation between attractiveness and perceived trustworthiness as well as familiarity often reported in previous studies, we posit that virtual faces judged to be real will also be rated as more trustworthy and familiar [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial].
+This study aims primarily at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the embodied reality theory [outlined in @makowski2018cognitive; @makowski2019phenomenal], which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
+Moreover, we expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
+Additionally, we will further explore the role of dispositional traits, such as personality and attitude towards AI, characteristics on inter-individual simulation monitoring tendencies.
+
+## Methods
 
 In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
-
-## Methods
 

### 2022-09-15 submission/manuscript.Rmd
discussion

@@
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation [petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult [*REF*].
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult [@berghel2018weaponizing; @chen2015news].
 In the absence of contextual information, what drives our beliefs of reality?
@@
 <!-- Attractiveness -->
-AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of faces evaluation, such as trustworthiness or attractiveness (**REF**).
-Interestingly, several studies report that artificially created faces were judged to be less attractive (**QUESTION: was their nature known to the participant?**) as compared to real faces [@tsikandilakis2019beauty; @diel2022familiarity], and @liefooghe2022faces further reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas this line of evidence suggests that beliefs of reality have an effect on attractiveness ratings of faces, the opposite question, whether attractiveness could drive beliefs of reality, has received no attention to date.
+AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of faces evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
+Interestingly, some studies report that when the nature of the faces was ambiguous, artificially created faces that were previously rated as more attractive were judged by subjects to be less real [@tucciarelli2020].
+However, as the attractiveness ratings were given by independent raters instead of the participants, the direction of the relationship between perceived realness and attractiveness cannot be concluded.
+To this end, @liefooghe2022faces reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
+Whereas this line of evidence suggests that beliefs of reality have an effect on attractiveness ratings of faces, the opposite question, whether attractiveness could drive beliefs of reality, has received little attention to date.
 
@@
 Moreover, we expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
-Additionally, we will further explore the role of dispositional traits, such as personality and attitude towards AI, characteristics on inter-individual simulation monitoring tendencies.
+Additionally, we will further explore the role of dispositional traits, such as personality and attitude towards AI, as well as characteristics of inter-individual simulation monitoring tendencies.
 
@@
 
-Although expected, the first striking result is that despite all items being real photos from the same database, all people easily believe (to high degrees of confidence) that a significant proportion of them was fake.
-This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
-In fact, stimuli-related and participant-related characteristics accounted for about only less than 20% of the variance in the beliefs, suggesting that a large part of it is related to other subjective processes.
+Notably, despite all the facial images being of real individuals retrieved from the same database, our results found every participant easily believed (to high degrees of confidence) that a significant proportion of them were fake.
+While this result is unsurprising, it is nevertheless a testimony to the existing expectations regarding CGI technology, as well as to the volatility of our sense of reality.
+In fact, stimuli-related and participant-related characteristics accounted for less than 20% of the variance in beliefs, suggesting that a large part of it is associated with other subjective processes.
 
-Though attractiveness does not seem to be the primary drive underlying simulation monitoring of face images, it does nonetheless display an association.
+### Attractiveness and Beauty (males -positive linear; females -quadratic(u-shape); judgement confidence positive quadratic relationship for females only in the real condition)
+
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of facial images in the present study, it does nonetheless display an association.
+Furthermore, the positive quadratic relationship found between beliefs of realness and attractiveness for female participants is aligned with our hypothesis, that faces which are highly salient (i.e., perceived to be very attractive or very unattractive) are judged to be more real.
+Alternatively, the positive linear relationship between beauty and attractiveness, and beliefs of realness observed for males could have an evolutionary basis.
+In particular, males are widely postulated to place more importance toward facial attractiveness as a sign of reproductive potential, relative to females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender].
+As such, males could have perceived highly attractive and beautiful faces to be more real since such attractiveness act as salient cues of biological quality [@fink2006facial].
+Therefore, our study suggests a more complex relationship between stimulus attractiveness, demographic variables and perceptions of reality that has not been examined in the literature.
+
+Moreover, beyond its impacts on individuals' beliefs about realness, attractiveness was found to significantly affect the confidence in judgements for females.
+
+### trustworthiness
+
+In contrast to the findings for attractiveness, trustworthiness only positively predicted beliefs in realness for females.
+While we had expected a positive relationship between the two variables across both genders, this observation is also consistent with the evolutionary perspective, which suggests that females, relative to males, are more averse to risk-taking because it may compromise their reproductive potential [@van2020sex].
+As such, given that low facial trustworthiness may signal greater risk, perceived trustworthiness may confer greater importance in predicting the perception of reality for females than males [@hou2019survival].
+Interestingly, while several studies have found both possessing prior knowledge that faces were artificial and the perceived realness of virtual faces to be predictive of trustworthiness ratings (i.e., faces judged as real were rated as more trustworthy) [@liefooghe2022faces; @hoogers2021effect; @balas2017], the same cannot easily be said of the opposite direction; that is, trustworthiness does not seem to be a primary driver underlying the processes of simulation monitoring.
+
+### familiarity (confidence judgement; positive linear -real; quadratic -fake)
+Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.
+
+### inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake)
+
+### AI attitudes (enthusiam - positive with confidence in both real and fake judgements)
+
+### Re-exposure Delay
+
+Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, with shorter delays being associated with faces being rated as more real.
+Interestingly, while it could be posited that shorter delays led to the faces appearing more familiar and thereby increased people's belief in its realness, this seems unlikely considering perceived familiarity did not significantly affect simulation monitoring decisions made, even after controlling for attractiveness and trustworthiness.
+Alternatively, shorter re-exposure delays could have led to the faces being better remembered, thus triggering autobiographical memory processes [@gobbini2013prioritized] and evoking a sense of personal relevance during the repeated display.
+Indeed, fictional stimuli that were associated with more personal memories have been shown to up-regulate emotions [@sperduti2016paradox; @makowski2017being], thus biasing the realness of the given stimulus
 

### 2022-09-15 submission/manuscript.Rmd
Update manuscript.Rmd

--- 2022-09-15 submission/manuscript.Rmd
@@
 Additionally, we will further explore the role of dispositional traits, such as personality and attitude towards AI, characteristics on inter-individual simulation monitoring tendencies.
+Note that the discriminative accuracy between "true" photos and "true" artificially-generated images is not relevant for this study, which focuses on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 
-109 photos of neutral-expression faces of real individuals were retrieved from the American Multiracial Face Database (AMFD, [@chen2021broadening]).
-In the first part of the study, participants answered a series of personality questionnaires.
-This includes the *Mini-IPIP6* [24 items, @sibley2011], to measure 6 "normal" personality traits (Extraversion, Openness, Conscientiousness, Agreeableness, Neuroticism and Honesty-Humility); the *FFNI-BF* [30 items, @jauk2022validation] to measure 9 facets of narcissism (acclaim-seeking, distrust, entitlement, exploitativeness, indifference, lack of empathy, manipulativeness, need for admiration and thrill-seeking); the *R-GPTS* [18 items, @freeman2021revised], to measure 2 sub-scales of paranoid thinking (persecution and reference ideation); the *IUS-12* [12 items, @carleton2007fearing], to assess beliefs about uncertainty and the future; the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development], to assess social anxiety levels as well as a 10-item scale that measures participants general attitudes towards artificial intelligence (of which 5 items were adapted from the *GAAIS* [@schepman2020initial]).
+In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development], assessing social anxiety levels.
+Finally, we created 5 items pertaining to expectations about AI-generated images technology (**TODO: write here some of the questions**).
+To lower their saliency and possibly prime the subjects about the task, we mixed these items with 5 items of the attitudes towards AI scale [*GAAIS*, @schepman2020initial].
+3 attention check questions were embedded in the questionnaires.
 
-In the second part of this study, the set of facial images retrieved from the AMFD were presented to the participants for 500ms each, in a randomized order.
-Following each facial display, participants were asked to rate each face on its **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") using a visual analog scale.
+In the second part of this study, 109 photos of neutral-expression faces of real individuals from the American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order.
+Following each stimulus, ratings of **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") were collected using visual analog scales.
 
-In the last part of the study, participants were informed that half of the facial images previously seen were AI-generated.
-The same set of facial images displayed before were then presented for a second set of trials in a new randomized order.
-As per the first set, each facial stimuli was presented for 500ms.
-After each display, participants were asked to judge whether they thought the face they saw was real (or fake) using a visual analog scale.
-
-This experiment was implemented using *jsPsych* [@de2015jspsych], and the full set of instructions is available in the experiment code.
+In the last part of the study, participants were informed that about half of the face images previously seen were AI-generated (the instructions used a cover story mentioning that the research was aimed at validating a new face generation algorithm).
+The same set of stimuli was displayed again for 500 ms in a new randomized order.
+This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scales (with *Fake* and *Real* as the two extremes).
+The study was implemented using *jsPsych* [@de2015jspsych], and the full set of instructions is available in the experiment code.
 
@@
 
-103 participants were recruited via *Prolific* ([www.prolificacademic.co.uk](www.prolificacademic.co.uk)), a crowd-sourcing platform providing high data quality [@peer2022].
+One hundred and three participants were recruited via *Prolific*, the the crowd-sourcing platform providing the best data quality [@peer2022].
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
-Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 50 minutes to finish.
-Demographic variables (age, gender, and ethnicity) were self-reported on a voluntary basis.
+Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish.
+Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.
 
-Upon inspection of stimuli ratings, attention check responses and total duration spent to complete the personality questionnaires, 3 participants were removed for spending an implausibly short time to finish the questionnaires and having very low correlations between their stimuli ratings and that of the normative distribution.
-
+We excluded 3 participants that failed 2 (out of 3) or more attention check questions.
 The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48% females, 52% males).

### 2022-09-15 submission/manuscript.Rmd

--- 2022-09-15 submission/manuscript.Rmd
@@
 Moreover, we expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
-Additionally, we will further explore the role of dispositional traits, such as personality and attitude towards AI, as well as characteristics of inter-individual simulation monitoring tendencies.
+Additionally, we will further explore the link of dispositional traits, such as personality and attitude towards AI, with inter-individual simulation monitoring tendencies.
+Note that the discriminative accuracy between "true" photos and "true" artificially-generated images is not relevant for this study, which focuses on the beliefs that a stimulus is real or fake, independently of its true nature.
 

### 2022-09-15 submission/manuscript.Rmd
Update manuscript.Rmd

@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development], assessing social anxiety levels.
+In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty.
 Finally, we created 5 items pertaining to expectations about AI-generated images technology (**TODO: write here some of the questions**).
 To lower their saliency and possibly prime the subjects about the task, we mixed these items with 5 items of the attitudes towards AI scale [*GAAIS*, @schepman2020initial].
-3 attention check questions were embedded in the questionnaires.
+This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the questionnaires.
 

### 2022-09-15 submission/manuscript.Rmd
format comments

@@
 
-### Attractiveness and Beauty (males -positive linear; females -quadratic(u-shape); judgement confidence positive quadratic relationship for females only in the real condition)
+<!-- Attractiveness and Beauty (males -positive linear; females -quadratic(u-shape); judgement confidence positive quadratic relationship for females only in the real condition) -->
 
@@
 
-### trustworthiness
+<!-- trustworthiness -->
 
@@
 
-### familiarity (confidence judgement; positive linear -real; quadratic -fake)
+<!-- familiarity (confidence judgement; positive linear -real; quadratic -fake) -->
 Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.
 
-### inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake)
+<!-- inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake) -->
 
-### AI attitudes (enthusiam - positive with confidence in both real and fake judgements)
+<!-- AI attitudes (enthusiam - positive with confidence in both real and fake judgements) -->
 
-### Re-exposure Delay
+<!-- Re-exposure Delay -->
 

### 2022-09-16 submission/manuscript.tex
pdf

@@
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (Makowski, 2018; a process henceforth referred to as \emph{simulation monitoring}, Makowski, Sperduti, et al., 2019).
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation {[}petty1986elaboration; Susmann et al.
-(2021); Michael and Sanson (2021){]}.
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult {[}\emph{REF}{]}.
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult (Berghel, 2018; Y.
+Chen et al., 2015).
 In the absence of contextual information, what drives our beliefs of reality?
@@
 
-With the advancement of technology, AI-generated images of faces have increasingly been used to study various cognitive mechanisms and processes, such as that underlying emotion processing (Dyck et al., 2008, 2010).
-Notably, the ability to manipulate the degree of emotionality and salience of virtual faces, by changing its facial dimensions, make them ideal targets for simulation monitoring research (Ferstl \& McDonnell, 2018; Fuentes-Hurtado et al., 2018).
-To this effect, the attractiveness of AI-generated faces, which integrates both components of emotional intensity and saliency {[}O'Doherty et al.
-(2003); DeBruine et al.
-(2007); sobieraj2014beautiful{]}, have indeed been associated with its perceived realness.
-To be specific, research findings suggest that artificially created faces were judged to be less attractive as compared to real faces {[}Liefooghe et al.
-(2022); tsikandilakis2019beauty; Diel and Lewis (2022){]}.
-Interestingly, Liefooghe et al.
-(2022) further reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas such studies posit that lower perceived realness of a given stimulus leads to lower ratings of attractiveness, little is known about the impacts of attractiveness on simulation monitoring.
+AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of faces evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
+Interestingly, some studies report that when the nature of the faces was ambiguous, artificially created faces that were previously rated as more attractive were judged by subjects to be less real (Tucciarelli et al., 2020).
+However, as the attractiveness ratings were given by independent raters instead of the participants, the direction of the relationship between perceived realness and attractiveness cannot be concluded.
+To this end, Liefooghe et al.
+(2022) reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
+Whereas this line of evidence suggests that beliefs of reality have an effect on attractiveness ratings of faces, the opposite question, whether attractiveness could drive beliefs of reality, has received little attention to date.
 
-The goal of this study is therefore to determine whether the attractiveness of artificially-generated faces affects our reality judgement of it.
-Based on the Embodied Reality Theory (Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that highly salient stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness of a given virtual stimulus, i.e., faces rated as highly attractive or unattractive will be judged to be more real.
-Additionally, we further postulate that inter-individual characteristics, such as personality traits and predisposed attitudes, will interact with the relationship between perceived realness and attractiveness.
-Moreover, given the well-established positive correlation between attractiveness and perceived trustworthiness as well as familiarity often reported in previous studies, we posit that virtual faces judged to be real will also be rated as more trustworthy and familiar (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011).
-
-In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
+This study aims primarily at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the embodied reality theory (outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
+Moreover, we expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
+Additionally, we will further explore the link of dispositional traits, such as personality and attitude towards AI, with inter-individual simulation monitoring tendencies.
+Note that the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images is not relevant for this study, which focuses on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 
+In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
+
 \hypertarget{procedure}{%
@@
 
-109 photos of neutral-expression faces of real individuals were retrieved from the American Multiracial Face Database (AMFD, (Chen et al., 2021)).
-In the first part of the study, participants answered a series of personality questionnaires.
-This includes the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011), to measure 6 ``normal'' personality traits (Extraversion, Openness, Conscientiousness, Agreeableness, Neuroticism and Honesty-Humility); the \emph{FFNI-BF} (30 items, Jauk et al., 2022) to measure 9 facets of narcissism (acclaim-seeking, distrust, entitlement, exploitativeness, indifference, lack of empathy, manipulativeness, need for admiration and thrill-seeking); the \emph{R-GPTS} (18 items, Freeman et al., 2021), to measure 2 sub-scales of paranoid thinking (persecution and reference ideation); the \emph{IUS-12} (12 items, Carleton et al., 2007), to assess beliefs about uncertainty and the future; the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012), to assess social anxiety levels as well as a 10-item scale that measures participants general attitudes towards artificial intelligence (of which 5 items were adapted from the \emph{GAAIS} (Schepman \& Rodway, 2020)).
+In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011) measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012) assessing social anxiety levels, the \emph{FFNI-BF} (30 items, Jauk et al., 2022) measuring 9 facets of narcissism; the \emph{R-GPTS} (18 items, Freeman et al., 2021) measuring 2 dimensions related to paranoid thinking; the \emph{IUS-12} (12 items, Carleton et al., 2007) measuring intolerance to uncertainty.
+Finally, we created 5 items pertaining to expectations about AI-generated images technology (\textbf{TODO: write here some of the questions}).
+To lower their saliency and possibly prime the subjects about the task, we mixed these items with 5 items of the attitudes towards AI scale (\emph{GAAIS}, Schepman \& Rodway, 2020).
+This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the questionnaires.
 
-In the second part of this study, the set of facial images retrieved from the AMFD were presented to the participants for 500ms each, in a randomized order.
-Following each facial display, participants were asked to rate each face on its \textbf{Attractiveness} (``I find this person attractive''), \textbf{Beauty} (``This face is good-looking''), \textbf{Trustworthiness} (``I find this person trustworthy'') and \textbf{Familiarity} (``This person reminds me of someone I know'') using a visual analog scale.
+In the second part of this study, 109 photos of neutral-expression faces of real individuals from the American Multiracial Face Database (AMFD, (J.
+M.
+Chen et al., 2021)) were presented to the participants for 500ms each, in a randomized order.
+Following each stimulus, ratings of \textbf{Attractiveness} (``I find this person attractive''), \textbf{Beauty} (``This face is good-looking''), \textbf{Trustworthiness} (``I find this person trustworthy'') and \textbf{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
 
-In the last part of the study, participants were informed that half of the facial images previously seen were AI-generated.
-The same set of facial images displayed before were then presented for a second set of trials in a new randomized order.
-As per the first set, each facial stimuli was presented for 500ms.
-After each display, participants were asked to judge whether they thought the face they saw was real (or fake) using a visual analog scale.
-
-This experiment was implemented using \emph{jsPsych} (De Leeuw, 2015), and the full set of instructions is available in the experiment code.
+In the last part of the study, participants were informed that about half of the face images previously seen were AI-generated (the instructions used a cover story mentioning that the research was aimed at validating a new face generation algorithm).
+The same set of stimuli was displayed again for 500 ms in a new randomized order.
+This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scales (with \emph{Fake} and \emph{Real} as the two extremes).
+The study was implemented using \emph{jsPsych} (De Leeuw, 2015), and the full set of instructions is available in the experiment code.
 
@@
 
-103 participants were recruited via \emph{Prolific} (\url{www.prolificacademic.co.uk}), a crowd-sourcing platform providing high data quality (Peer et al., 2022).
+One hundred and three participants were recruited via \emph{Prolific}, the the crowd-sourcing platform providing the best data quality (Peer et al., 2022).
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
-Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 50 minutes to finish.
-Demographic variables (age, gender, and ethnicity) were self-reported on a voluntary basis.
+Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish.
+Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.
 
-Upon inspection of stimuli ratings, attention check responses and total duration spent to complete the personality questionnaires, 3 participants were removed for spending an implausibly short time to finish the questionnaires and having very low correlations between their stimuli ratings and that of the normative distribution.
-
+We excluded 3 participants that failed 2 (out of 3) or more attention check questions.
 The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: {[}19, 66{]}; Sex: 48\% females, 52\% males).
@@
 
-Although expected, the first striking result is that despite all items being real photos from the same database, all people easily believe (to high degrees of confidence) that a significant proportion of them was fake.
-This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
-In fact, stimuli-related and participant-related characteristics accounted for about only less than 20\% of the variance in the beliefs, suggesting that a large part of it is related to other subjective processes.
+Notably, despite all the facial images being of real individuals retrieved from the same database, our results found every participant easily believed (to high degrees of confidence) that a significant proportion of them were fake.
+While this result is unsurprising, it is nevertheless a testimony to the existing expectations regarding CGI technology, as well as to the volatility of our sense of reality.
+In fact, stimuli-related and participant-related characteristics accounted for less than 20\% of the variance in beliefs, suggesting that a large part of it is associated with other subjective processes.
 
-Though attractiveness does not seem to be the primary drive underlying simulation monitoring of face images, it does nonetheless display an association.
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of facial images in the present study, it does nonetheless display an association.
+Furthermore, the positive quadratic relationship found between beliefs of realness and attractiveness for female participants is aligned with our hypothesis, that faces which are highly salient (i.e., perceived to be very attractive or very unattractive) are judged to be more real.
+Alternatively, the positive linear relationship between beauty and attractiveness, and beliefs of realness observed for males could have an evolutionary basis.
+In particular, males are widely postulated to place more importance toward facial attractiveness as a sign of reproductive potential, relative to females, who tend to value characteristics signaling resource acquisition capabilities (Qi \& Ying, 2022).
+As such, males could have perceived highly attractive and beautiful faces to be more real since such attractiveness act as salient cues of biological quality (Fink et al., 2006).
+Therefore, our study suggests a more complex relationship between stimulus attractiveness, demographic variables and perceptions of reality that has not been examined in the literature.
+
+Moreover, beyond its impacts on individuals' beliefs about realness, attractiveness was found to significantly affect the confidence in judgements for females.
+
+In contrast to the findings for attractiveness, trustworthiness only positively predicted beliefs in realness for females.
+While we had expected a positive relationship between the two variables across both genders, this observation is also consistent with the evolutionary perspective, which suggests that females, relative to males, are more averse to risk-taking because it may compromise their reproductive potential (Van Den Akker et al., 2020).
+As such, given that low facial trustworthiness may signal greater risk, perceived trustworthiness may confer greater importance in predicting the perception of reality for females than males (Hou \& Liu, 2019).
+Interestingly, while several studies have found both possessing prior knowledge that faces were artificial and the perceived realness of virtual faces to be predictive of trustworthiness ratings (i.e., faces judged as real were rated as more trustworthy) (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), the same cannot easily be said of the opposite direction; that is, trustworthiness does not seem to be a primary driver underlying the processes of simulation monitoring.
+
+Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.
+
+Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, with shorter delays being associated with faces being rated as more real.
+Interestingly, while it could be posited that shorter delays led to the faces appearing more familiar and thereby increased people's belief in its realness, this seems unlikely considering perceived familiarity did not significantly affect simulation monitoring decisions made, even after controlling for attractiveness and trustworthiness.
+Alternatively, shorter re-exposure delays could have led to the faces being better remembered, thus triggering autobiographical memory processes (Gobbini et al., 2013) and evoking a sense of personal relevance during the repeated display.
+Indeed, fictional stimuli that were associated with more personal memories have been shown to up-regulate emotions (Makowski et al., 2017; Sperduti et al., 2016), thus biasing the realness of the given stimulus
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-balas2017}{}}%
+Balas, B., \& Pacella, J. (2017). Trustworthiness perception is disrupted in artificial faces. \emph{Computers in Human Behavior}, \emph{77}. \url{https://doi.org/10.1016/j.chb.2017.08.045}
+
 \leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-berghel2018weaponizing}{}}%
+Berghel, H. (2018). Weaponizing twitter litter: Abuse-forming networks and social media. \emph{Computer}, \emph{51}(4), 70--73.
+
 \leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
@@
 Bryanov, K., \& Vziatysheva, V. (2021). Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS One}, \emph{16}(6), e0253717.
+
+\leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
+Calbi, M., Heimann, K., Barratt, D., Siri, F., Umiltà, M.
+A., \& Gallese, V.
+(2017).
+How context influences our perception of emotional faces: A behavioral study on the kuleshov effect.
+\emph{Frontiers in Psychology}, \emph{8}.
+\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2017.01684}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
+Chen, Y., Conroy, N.
+K., \& Rubin, V.
+L.
+(2015).
+News in an online world: The need for an {``automatic crap detector.''} \emph{Proceedings of the Association for Information Science and Technology}, \emph{52}(1), 1--4.
+
 \leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
 De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-debruine2007dissociating}{}}%
-DeBruine, L.
-M., Jones, B.
-C., Unger, L., Little, A.
-C., \& Feinberg, D.
-R.
-(2007).
-Dissociating averageness and attractiveness: Attractive faces are not always average.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{33}(6), 1420.
-
-\leavevmode\vadjust pre{\hypertarget{ref-diel2022familiarity}{}}%
-Diel, A., \& Lewis, M. (2022). Familiarity, orientation, and realism increase face uncanniness by sensitizing to facial distortions. \emph{Journal of Vision}, \emph{22}(4), 14--14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dyck2008recognition}{}}%
-Dyck, M., Winbeck, M., Leiberg, S., Chen, Y., Gur, R. C., \& Mathiak, K. (2008). Recognition profile of emotions in natural and virtual faces. \emph{PloS One}, \emph{3}(11), e3628.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dyck2010virtual}{}}%
-Dyck, M., Winbeck, M., Leiberg, S., Chen, Y., \& Mathiak, K.
-(2010).
-Virtual faces as a tool to study emotion recognition deficits in schizophrenia.
-\emph{Psychiatry Research}, \emph{179}(3), 247--252.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ferstl2018perceptual}{}}%
-Ferstl, Y., \& McDonnell, R.
-(2018).
-A perceptual study on the manipulation of facial features for trait portrayal in virtual agents.
-\emph{Proceedings of the 18th International Conference on Intelligent Virtual Agents}, 281--288.
+\leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
+Fink, B., Neave, N., Manning, J.
+T., \& Grammer, K.
+(2006).
+Facial symmetry and judgements of attractiveness, health and personality.
+\emph{Personality and Individual Differences}, \emph{41}(3), 491--499.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-fuentes2018evolutionary}{}}%
-Fuentes-Hurtado, F., Diego-Mas, J. A., Naranjo, V., \& Alcañiz, M. (2018). Evolutionary computation for modelling social traits in realistic looking synthetic faces. \emph{Complexity}, \emph{2018}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
 Garrido, M. V., \& Prada, M. (2017). KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces. \emph{Frontiers in Psychology}, \emph{8}, 2181.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gobbini2013prioritized}{}}%
+Gobbini, M.
+I., Gors, J.
+D., Halchenko, Y.
+O., Rogers, C., Guntupalli, J.
+S., Hughes, H., \& Cipolli, C.
+(2013).
+Prioritized detection of personally familiar faces.
+\emph{PloS One}, \emph{8}(6), e66620.
 
@@
 \emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4), 232.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hoogers2021effect}{}}%
+Hoogers, E. (2021). \emph{The effect of attitude towards computer generated faces on face perception} {[}\{B.S.\} thesis{]}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hou2019survival}{}}%
+Hou, C., \& Liu, Z.
+(2019).
+The survival processing advantage of face: The memorization of the (un) trustworthy face contributes more to survival adaptation.
+\emph{Evolutionary Psychology}, \emph{17}(2), 1474704919839726.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-o2003beauty}{}}%
-O'Doherty, J., Winston, J., Critchley, H., Perrett, D., Burt, D.
-M., \& Dolan, R.
-J.
-(2003).
-Beauty in a smile: The role of medial orbitofrontal cortex in facial attractiveness.
-\emph{Neuropsychologia}, \emph{41}(2), 147--155.
-
 \leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-petty1986elaboration}{}}%
+Petty, R. E., \& Cacioppo, J. T. (1986). The elaboration likelihood model of persuasion. In \emph{Communication and persuasion} (pp. 1--24). Springer.
+
 \leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
@@
 \emph{Frontiers in Psychiatry}, 1142.
+
+\leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
+Qi, Y., \& Ying, J. (2022). Gender biases in the accuracy of facial judgments: Facial attractiveness and perceived socioeconomic status. \emph{Frontiers in Psychology}, \emph{13}.
 
@@
 Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology}, \emph{36}, 44--48.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
+Sobieraj, S., \& Krämer, N. C. (2014). What is beautiful in cyberspace? Communication with attractive avatars. \emph{International Conference on Social Computing and Social Media}, 125--136.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-tsikandilakis2019beauty}{}}%
+Tsikandilakis, M., Bali, P., \& Chapman, P.
+(2019).
+Beauty is in the eye of the beholder: The appraisal of facial attractiveness and its relation to conscious awareness.
+\emph{Perception}, \emph{48}(1), 72--92.
+
 \leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
 Tucciarelli, R., Vehar, N., \& Tsakiris, M. (2020). \emph{On the realness of people who do not exist: the social processing of artificial faces}. \url{https://doi.org/10.31234/osf.io/dnk9x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2020sex}{}}%
+Van Den Akker, O.
+R., Assen, M.
+A.
+van, Van Vugt, M., \& Wicherts, J.
+M.
+(2020).
+Sex differences in trust and trustworthiness: A meta-analysis of the trust game and the gift-exchange game.
+\emph{Journal of Economic Psychology}, \emph{81}, 102329.
 

### 2022-09-17 submission/manuscript.Rmd
address stephanie's points

@@
       - "Writing – review & editing"
+  - name          : "Panagiotis Mavros"
+    affiliation   : "2"
+    orcid         : 0000-0002-1540-5516
+    role:
+      - "Supervision"
+      - "Writing – review & editing"
   - name          : "S.H. Annabel Chen"
-    affiliation   : "1, 2, 3, 4"
+    affiliation   : "1, 3, 4, 5"
     orcid         : 0000-0002-1540-5516
@@
 <!-- stakes and Post-truth era -->
-For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
-Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
+For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
+These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
+Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
 This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
@@
 <!-- Ambiguous stimuli and irrelevance of objective features -->
-While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of faces generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
+While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of face generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
 This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
@@
 For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy].
-Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information in line with our expectations [@britt2019reasoned], and dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
+Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with our expectations [@britt2019reasoned].
+Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
 
 <!-- Reactive features -->
-Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two, i.e., the subjective reaction associated with the experience of a given stimulus, contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase one's sense of presence in a simulated reality, i.e., the extent to which one feels like "being there", as if the movie or the VR environment was real [@sanchez2005presence; @makowski2017being], and beliefs that the stimuli were fake were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
-In line with these findings, other studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated  with greater belief [@martel2020reliance; @bago2022emotion].
+Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
+For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like "being there", as if the object of experience was real - when engaged in a fictional movie or a VR environment [@sanchez2005presence; @makowski2017being].
+Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated  with greater belief [@martel2020reliance; @bago2022emotion].
 Additionally, other factors, such as the stimulus' perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
@@
 To this end, @liefooghe2022faces reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas this line of evidence suggests that beliefs of reality have an effect on attractiveness ratings of faces, the opposite question, whether attractiveness could drive beliefs of reality, has received little attention to date.
+Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question, whether attractiveness could drive simulation monitoring, has received little attention to date.
 
 <!-- Goals and hypotheses -->
-This study aims primarily at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory [outlined in @makowski2018cognitive; @makowski2019phenomenal], which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
-Moreover, we expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
+This study primarily aims at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the embodied reality theory [outlined in @makowski2018cognitive; @makowski2019phenomenal], which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
+We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link of dispositional traits, such as personality and attitude towards AI, with inter-individual simulation monitoring tendencies.
@@
 Following each stimulus, ratings of **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") were collected using visual analog scales.
+(**TODO: add details and justifications**)
 
@@
 
-We excluded 3 participants that failed 2 (out of 3) or more attention check questions.
+We excluded 3 participants that failed 2 (>= 66%) or more attention check questions.
 The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48% females, 52% males).
@@
 Finally, we investigated the inter-individual correlates of simulation monitoring by computing, for each participant, the proportion of faces judged as real (i.e., the overall bias towards one or the other belief), as well as the average confidence for faces judged as real, and fake.
-We assessed the link between these scores and dispositional traits using Bayesian correlation analysis [@makowski2019indices@; @correlationArticle].
+We assessed the link between these scores and dispositional traits using Bayesian correlation analysis [@makowski2019indices; @correlationArticle].
 
 The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle].
-As all the details, scripts and complimentary analyses are available in open-access, the manuscript will focus on significant results.
+As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
 
@@
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
 
@@
 
-Notably, despite all the facial images being of real individuals retrieved from the same database, our results found every participant easily believed (to high degrees of confidence) that a significant proportion of them were fake.
-While this result is unsurprising, it is nevertheless a testimony to the existing expectations regarding CGI technology, as well as to the volatility of our sense of reality.
-In fact, stimuli-related and participant-related characteristics accounted for less than 20% of the variance in beliefs, suggesting that a large part of it is associated with other subjective processes.
+This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that the stimulus is artificially generated.
+The most striking result is that despite all the images being real faces retrieved from the same validated database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
+This result is a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+It underlines the strong impact of prior expectations and information on reality beliefs.
+In fact, stimuli-related and participant-related characteristics accounted for less than 20% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
 
@@
 
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of facial images in the present study, it does nonetheless display an association.
-Furthermore, the positive quadratic relationship found between beliefs of realness and attractiveness for female participants is aligned with our hypothesis, that faces which are highly salient (i.e., perceived to be very attractive or very unattractive) are judged to be more real.
-Alternatively, the positive linear relationship between beauty and attractiveness, and beliefs of realness observed for males could have an evolutionary basis.
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern depending on the participant's gender.
+The quadratic relationship found for female participants is aligned with our hypothesis that faces which are highly salient (i.e., perceived to be very attractive or very unattractive) are judged to be more real.
+Alternatively, we could interpret the mostly positive linear relationship for males under an evolutionary lens.
+
 In particular, males are widely postulated to place more importance toward facial attractiveness as a sign of reproductive potential, relative to females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender].

### 2022-09-17 submission/manuscript.Rmd
Update manuscript.Rmd

@@
 
-In the second part of this study, 109 photos of neutral-expression faces of real individuals from the American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order.
+In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order.
 Following each stimulus, ratings of **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") were collected using visual analog scales.
@@
 This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that the stimulus is artificially generated.
-The most striking result is that despite all the images being real faces retrieved from the same validated database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
-This result is a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
+This finding is a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
@@
 Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern depending on the participant's gender.
-The quadratic relationship found for female participants is aligned with our hypothesis that faces which are highly salient (i.e., perceived to be very attractive or very unattractive) are judged to be more real.
+The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
 Alternatively, we could interpret the mostly positive linear relationship for males under an evolutionary lens.
+In particular, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial].
+As such, it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces are significantly more salient than unattractive ones, in turn distorting the relationship with simulation monitoring.
+Future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (**ref on saliency in EEG or fMRI**) or physiological markers [in particular, heart rate deceleration, **include refs**].
 
-In particular, males are widely postulated to place more importance toward facial attractiveness as a sign of reproductive potential, relative to females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender].
-As such, males could have perceived highly attractive and beautiful faces to be more real since such attractiveness act as salient cues of biological quality [@fink2006facial].
-Therefore, our study suggests a more complex relationship between stimulus attractiveness, demographic variables and perceptions of reality that has not been examined in the literature.
-
-Moreover, beyond its impacts on individuals' beliefs about realness, attractiveness was found to significantly affect the confidence in judgements for females.
+<!-- Beauty -->
+discuss why the link with beauty is slightly different.
 

### 2022-09-17 submission/manuscript.Rmd
Update manuscript.Rmd

@@
 discuss why the link with beauty is slightly different.
+Note that for models for beauty we adjusted the models for trustowrthiness and familiarity, hence possibly masking the multidimensionality of attractiveness.
 
 <!-- trustworthiness -->
-
-In contrast to the findings for attractiveness, trustworthiness only positively predicted beliefs in realness for females.
-While we had expected a positive relationship between the two variables across both genders, this observation is also consistent with the evolutionary perspective, which suggests that females, relative to males, are more averse to risk-taking because it may compromise their reproductive potential [@van2020sex].
-As such, given that low facial trustworthiness may signal greater risk, perceived trustworthiness may confer greater importance in predicting the perception of reality for females than males [@hou2019survival].
-Interestingly, while several studies have found both possessing prior knowledge that faces were artificial and the perceived realness of virtual faces to be predictive of trustworthiness ratings (i.e., faces judged as real were rated as more trustworthy) [@liefooghe2022faces; @hoogers2021effect; @balas2017], the same cannot easily be said of the opposite direction; that is, trustworthiness does not seem to be a primary driver underlying the processes of simulation monitoring.
+In contrast to the findings for attractiveness, trustworthiness linearly increased beliefs in realness for females only.
+Given the evidence for the effect in the opposite direction, suggesting that faces presented as were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders.
+One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionary as a compromise their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+However, faces judged as highly untrustworthy should have appear as even more salient (representing an evolutionary threat), and hence be judged as more real.
+As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
 
 <!-- familiarity (confidence judgement; positive linear -real; quadratic -fake) -->
-Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.
+Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
+It is to note that the distribution of familiarity ratings was strongly skewed, and that a low number of pictures was rated as highly familiar.
+Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposures of items before the simulation monitoring ratings.
 
@@
 
-We would like to thank STUDENT NAME for his contribution.
+We would like to thank **TODO: add STUDENT NAME** for his contribution to the selection of the materials.
 

### 2022-09-17 submission/manuscript.Rmd
minor

@@
 These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
-Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
+Such developments not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
 This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
@@
 
-We excluded 3 participants that failed 2 (>= 66%) or more attention check questions.
-The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48% females, 52% males).
+We excluded 3 participants that failed 2 (>= 66\%) or more attention check questions.
+The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48\% females, 52\% males).
 
@@
 It underlines the strong impact of prior expectations and information on reality beliefs.
-In fact, stimuli-related and participant-related characteristics accounted for less than 20% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
+In fact, stimuli-related and participant-related characteristics accounted for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
 
-<!-- Attractiveness and Beauty (males -positive linear; females -quadratic(u-shape); judgement confidence positive quadratic relationship for females only in the real condition) -->
+<!-- Attractiveness and Beauty -->
 
@@
 
-<!-- familiarity (confidence judgement; positive linear -real; quadratic -fake) -->
+<!-- familiarity -->
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.

### 2022-09-17 submission/manuscript.tex
minor

@@
   pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
-  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, \& S.H. Annabel Chen1, 2, 3, 4},
+  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
   pdflang={en-EN},
@@
 \title{\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}}
-\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{1}, Stephanie Kirk\textsuperscript{1}, Ngoi Zi Liang\textsuperscript{1}, \& S.H. Annabel Chen\textsuperscript{1, 2, 3, 4}}
+\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{1}, Stephanie Kirk\textsuperscript{1}, Ngoi Zi Liang\textsuperscript{1}, Panagiotis Mavros\textsuperscript{2}, \& S.H.
+Annabel Chen\textsuperscript{1, 3, 4, 5}}
 \date{}
@@
 The authors made the following contributions.
-Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Ngoi Zi Liang: Project administration, Resources, Writing -- review \& editing; S.H.
+Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Ngoi Zi Liang: Project administration, Resources, Writing -- review \& editing; Panagiotis Mavros: Supervision, Writing -- review \& editing; S.H.
 Annabel Chen: Project administration, Supervision, Writing -- review \& editing.
@@
 
-For the first time in the history of humanity, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
-Such progress not only carries important consequences for the technological and entertainment sectors, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
+For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
+These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
+Such developments not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
 This issue is central to what has been coined the ``post-truth era'' (Lewandowsky et al., 2017), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
 
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of faces generation and replacement (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of face generation and replacement (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
 This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
@@
 For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019).
-Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information in line with our expectations (Britt et al., 2019), and dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
+Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with our expectations (Britt et al., 2019).
+Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
 
-Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two, i.e., the subjective reaction associated with the experience of a given stimulus, contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase one's sense of presence in a simulated reality, i.e., the extent to which one feels like ``being there'', as if the movie or the VR environment was real (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005), and beliefs that the stimuli were fake were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
-In line with these findings, other studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
+Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
+For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005).
+Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
 Additionally, other factors, such as the stimulus' perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in our processing and reaction to real as opposed to non-real material.
@@
 (2022) reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas this line of evidence suggests that beliefs of reality have an effect on attractiveness ratings of faces, the opposite question, whether attractiveness could drive beliefs of reality, has received little attention to date.
+Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question, whether attractiveness could drive simulation monitoring, has received little attention to date.
 
-This study aims primarily at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory (outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between the perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
-Moreover, we expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
+This study primarily aims at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the embodied reality theory (outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
+We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link of dispositional traits, such as personality and attitude towards AI, with inter-individual simulation monitoring tendencies.
@@
 
-In the second part of this study, 109 photos of neutral-expression faces of real individuals from the American Multiracial Face Database (AMFD, (J.
+In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, (J.
 M.
@@
 Following each stimulus, ratings of \textbf{Attractiveness} (``I find this person attractive''), \textbf{Beauty} (``This face is good-looking''), \textbf{Trustworthiness} (``I find this person trustworthy'') and \textbf{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
+(\textbf{TODO: add details and justifications})
 
@@
 
-We excluded 3 participants that failed 2 (out of 3) or more attention check questions.
+We excluded 3 participants that failed 2 (\textgreater= 66\%) or more attention check questions.
 The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: {[}19, 66{]}; Sex: 48\% females, 52\% males).
@@
 Finally, we investigated the inter-individual correlates of simulation monitoring by computing, for each participant, the proportion of faces judged as real (i.e., the overall bias towards one or the other belief), as well as the average confidence for faces judged as real, and fake.
-We assessed the link between these scores and dispositional traits using Bayesian correlation analysis (Makowski, Ben-Shachar, Chen, et al., 2019@; Makowski et al., 2020).
+We assessed the link between these scores and dispositional traits using Bayesian correlation analysis (Makowski et al., 2020; Makowski, Ben-Shachar, Chen, et al., 2019).
 
 The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski, Ben-Shachar, \& Lüdecke, 2019).
-As all the details, scripts and complimentary analyses are available in open-access, the manuscript will focus on significant results.
+As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
 
@@
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness (\(R^2_{marginal}\) = 3.0\%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real (\(\beta_{poly1} = 9.31\), \(95\% CI = [3.45, 15.17]\), \(z = -3.11\), \(p = .002\)), and a quadratic relationship for faces judged as fake (\(\beta_{poly1} = -12.67\), \(95\% CI = [-19.87, -5.47]\), \(z = -3.45\), \(p < .001\); \(\beta_{poly2} = 8.14\), \(95\% CI = [0.01, 16.28]\), \(z = 1.96\), \(p = .05\)), for males only, suggesting that faces judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+However, a significant positive and linear relationship was found with the confidence in faces judged as real (\(\beta_{poly1} = 9.31\), \(95\% CI = [3.45, 15.17]\), \(z = -3.11\), \(p = .002\)), and a quadratic relationship for faces judged as fake (\(\beta_{poly1} = -12.67\), \(95\% CI = [-19.87, -5.47]\), \(z = -3.45\), \(p < .001\); \(\beta_{poly2} = 8.14\), \(95\% CI = [0.01, 16.28]\), \(z = 1.96\), \(p = .05\)), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
 
@@
 
-Notably, despite all the facial images being of real individuals retrieved from the same database, our results found every participant easily believed (to high degrees of confidence) that a significant proportion of them were fake.
-While this result is unsurprising, it is nevertheless a testimony to the existing expectations regarding CGI technology, as well as to the volatility of our sense of reality.
-In fact, stimuli-related and participant-related characteristics accounted for less than 20\% of the variance in beliefs, suggesting that a large part of it is associated with other subjective processes.
+This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that the stimulus is artificially generated.
+The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
+This finding is a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+It underlines the strong impact of prior expectations and information on reality beliefs.
+In fact, stimuli-related and participant-related characteristics accounted for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
 
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of facial images in the present study, it does nonetheless display an association.
-Furthermore, the positive quadratic relationship found between beliefs of realness and attractiveness for female participants is aligned with our hypothesis, that faces which are highly salient (i.e., perceived to be very attractive or very unattractive) are judged to be more real.
-Alternatively, the positive linear relationship between beauty and attractiveness, and beliefs of realness observed for males could have an evolutionary basis.
-In particular, males are widely postulated to place more importance toward facial attractiveness as a sign of reproductive potential, relative to females, who tend to value characteristics signaling resource acquisition capabilities (Qi \& Ying, 2022).
-As such, males could have perceived highly attractive and beautiful faces to be more real since such attractiveness act as salient cues of biological quality (Fink et al., 2006).
-Therefore, our study suggests a more complex relationship between stimulus attractiveness, demographic variables and perceptions of reality that has not been examined in the literature.
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern depending on the participant's gender.
+The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
+Alternatively, we could interpret the mostly positive linear relationship for males under an evolutionary lens.
+In particular, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Fink et al., 2006; Qi \& Ying, 2022).
+As such, it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces are significantly more salient than unattractive ones, in turn distorting the relationship with simulation monitoring.
+Future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (\textbf{ref on saliency in EEG or fMRI}) or physiological markers {[}in particular, heart rate deceleration, \textbf{include refs}{]}.
 
-Moreover, beyond its impacts on individuals' beliefs about realness, attractiveness was found to significantly affect the confidence in judgements for females.
+discuss why the link with beauty is slightly different.
+Note that for models for beauty we adjusted the models for trustowrthiness and familiarity, hence possibly masking the multidimensionality of attractiveness.
 
-In contrast to the findings for attractiveness, trustworthiness only positively predicted beliefs in realness for females.
-While we had expected a positive relationship between the two variables across both genders, this observation is also consistent with the evolutionary perspective, which suggests that females, relative to males, are more averse to risk-taking because it may compromise their reproductive potential (Van Den Akker et al., 2020).
-As such, given that low facial trustworthiness may signal greater risk, perceived trustworthiness may confer greater importance in predicting the perception of reality for females than males (Hou \& Liu, 2019).
-Interestingly, while several studies have found both possessing prior knowledge that faces were artificial and the perceived realness of virtual faces to be predictive of trustworthiness ratings (i.e., faces judged as real were rated as more trustworthy) (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), the same cannot easily be said of the opposite direction; that is, trustworthiness does not seem to be a primary driver underlying the processes of simulation monitoring.
+In contrast to the findings for attractiveness, trustworthiness linearly increased beliefs in realness for females only.
+Given the evidence for the effect in the opposite direction, suggesting that faces presented as were rated as more trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such link to be present for both genders.
+One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females (explained evolutionary as a compromise their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
+However, faces judged as highly untrustworthy should have appear as even more salient (representing an evolutionary threat), and hence be judged as more real.
+As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
 
-Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.
+Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
+It is to note that the distribution of familiarity ratings was strongly skewed, and that a low number of pictures was rated as highly familiar.
+Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposures of items before the simulation monitoring ratings.
 
@@
 
-We would like to thank STUDENT NAME for his contribution.
+We would like to thank \textbf{TODO: add STUDENT NAME} for his contribution to the selection of the materials.
 

### 2022-09-19 submission/manuscript.Rmd
update manu

@@
 In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated  with greater belief [@martel2020reliance; @bago2022emotion].
-Additionally, other factors, such as the stimulus' perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
+Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
 
@@
 In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty.
-Finally, we created 5 items pertaining to expectations about AI-generated images technology (**TODO: write here some of the questions**).
-To lower their saliency and possibly prime the subjects about the task, we mixed these items with 5 items of the attitudes towards AI scale [*GAAIS*, @schepman2020initial].
+Finally, we created 5 items pertaining to expectations about AI-generated images technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
+To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items of the general attitudes towards AI scale [*GAAIS*, @schepman2020initial].
 This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the questionnaires.
@@
 In particular, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial].
-As such, it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces are significantly more salient than unattractive ones, in turn distorting the relationship with simulation monitoring.
-Future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (**ref on saliency in EEG or fMRI**) or physiological markers [in particular, heart rate deceleration, **include refs**].
+As such, it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces as significantly more salient than unattractive ones, in turn distorting the relationship with simulation monitoring.
+Future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @goldstein2002influence].
 
@@
 discuss why the link with beauty is slightly different.
-Note that for models for beauty we adjusted the models for trustowrthiness and familiarity, hence possibly masking the multidimensionality of attractiveness.
+Note that for models for beauty we adjusted the models for trustworthiness and familiarity, hence possibly masking the multidimensionality of attractiveness.
 
@@
 Given the evidence for the effect in the opposite direction, suggesting that faces presented as were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders.
-One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionary as a compromise their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-However, faces judged as highly untrustworthy should have appear as even more salient (representing an evolutionary threat), and hence be judged as more real.
+One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionary as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+That being the case, however, faces judged as highly untrustworthy should have appear as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 
-<!-- inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake) -->
+<!-- inter-indiv correlates -->
 
-<!-- AI attitudes (enthusiam - positive with confidence in both real and fake judgements) -->
+Unsurprisingly, participants with higher scores in Narcissism traits of Acclaim Seeking and Grandiose Fantasies were generally more confident in their simulation monitoring decisions.
+While early researchers had proposed narcissism to be a unitary construct [@raskin1988principal; @sedikides2004normal], recent studies view narcissism as encompassing 2 different dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and an insatiable need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness [@pincus2011narcissistic].
+Whereas narcissism has long been linked to over-confidence in decision-making [@campbell2004narcissism], a growing body of research indicates that this relationship is likely mostly driven by facets of narcissistic grandiosity (such as Acclaim Seeking), which drives individuals to see themselves as more superior than others and to externalize blame for poor decision-making consequences [@o2021grandiose].
+Indeed, the evidence shows that attributes of narcissistic grandiosity predict individuals' overconfidence in cognitive decision-making as well as a willingness to ignore expert feedback [@chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+
+Conversely, the literature on the correlation between honesty-humility and perceptual confidence judgements remain comparatively scarce, besides some research linking higher levels of honesty-humility to increased perceptions of risk and risk aversion [@levidi2022understanding; @weller2012honest].
+As such, it could be argued that individuals with higher levels of honesty-humility could inherently possess a greater simulation monitoring sensitivity, perceiving a higher risk in deciding the realness of the given stimulus and therefore be less confident of their reality judgements.
+This is further supported by convergent evidence finding a negative link between honesty humility and narcissism [@hodson2018dark].
+Therefore, further research examining the relationship between simulation monitoring decisions, personality traits, particularly that related to the dark triad and honesty-humility, and the perceived risks involved, is warranted.
+
+<!-- AI attitudes -->
+
+Interestingly, despite the ubiquity of AI, there is a lack of research pertaining to the influence of people's AI attitudes on their confidence in their discriminative ability to distinguish between output that is "true" (i.e., images of real faces) from those that is artificially-generated.
+One possible explanation for the positive association observed between AI-Enthusiasm and confidence in reality judgements is that individuals with highly positive AI attitudes could perceive themselves as having greater knowledge about AI and its capabilities, hence allowing them to be more confident in their simulation monitoring decisions.
+This is in line with previous research findings which indicate that having greater enthusiasm about AI is related to having a higher confidence in one's knowledge regarding AI competencies [@said2022artificial].
+Moreover, @said2022artificial further reports that AI attitudes interacts with people's perceived AI knowledge to influence their perception of the opportunities and risks accorded by AI applications.
+Specifically, people with AI attitudes that were highly positive and that were more confident in their AI knowledge tended to over-estimate the advantages of AI and under-estimate the risks involved in their application.
+As such, the positive association between individuals' confidence in their simulation monitoring decisions and their attitude towards AI could have been driven by their perception of their knowledge of AI.
 

### 2022-09-20 submission/manuscript.Rmd
update manu

--- 2022-09-17 submission/manuscript.Rmd
@@
 In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated  with greater belief [@martel2020reliance; @bago2022emotion].
-Additionally, other factors, such as the stimulus' perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
+Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
 
 <!-- Attractiveness -->
-AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of faces evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
+AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
 Interestingly, some studies report that when the nature of the faces was ambiguous, artificially created faces that were previously rated as more attractive were judged by subjects to be less real [@tucciarelli2020].
@@
 <!-- Goals and hypotheses -->
-This study primarily aims at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory [outlined in @makowski2018cognitive; @makowski2019phenomenal], which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
+This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the embodied reality theory [outlined in @makowski2018cognitive; @makowski2019phenomenal], which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty.
-Finally, we created 5 items pertaining to expectations about AI-generated images technology (**TODO: write here some of the questions**).
-To lower their saliency and possibly prime the subjects about the task, we mixed these items with 5 items of the attitudes towards AI scale [*GAAIS*, @schepman2020initial].
-This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the questionnaires.
+In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; and the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty.
+Finally, we devised 5 items pertaining to expectations about AI-generated images technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
+To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale [*GAAIS*, @schepman2020initial].
+This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the set of scales.
 
-In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order.
-Following each stimulus, ratings of **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") were collected using visual analog scales.
-(**TODO: add details and justifications**)
+In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display for 750ms.
+After each stimulus presentation, ratings of **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") were collected using visual analog scales.
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 scales, measuring general attractiveness (**Attractiveness**) and physical attractiveness (**Beauty**), to determine whether the effects on simulation monitoring are driven by physical features.
 
@@
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
-This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scales (with *Fake* and *Real* as the two extremes).
+This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with *Fake* and *Real* as the two extremes).
 The study was implemented using *jsPsych* [@de2015jspsych], and the full set of instructions is available in the experiment code.
@@
 
-<!-- Attractiveness and Beauty -->
-
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern depending on the participant's gender.
-The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
+<!-- Attractiveness -->
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender.
+In particular, the quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
 Alternatively, we could interpret the mostly positive linear relationship for males under an evolutionary lens.
-In particular, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial].
-As such, it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces are significantly more salient than unattractive ones, in turn distorting the relationship with simulation monitoring.
-Future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (**ref on saliency in EEG or fMRI**) or physiological markers [in particular, heart rate deceleration, **include refs**].
-
-<!-- Beauty -->
-discuss why the link with beauty is slightly different.
-Note that for models for beauty we adjusted the models for trustowrthiness and familiarity, hence possibly masking the multidimensionality of attractiveness.
+Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial].
+However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces as significantly more salient than unattractive ones and in turn distorting the relationship with simulation monitoring, beauty, operationalized as physical attractiveness, was found to have a significant positive linear relationship with simulation monitoring decisions for males even after adjusting for the effects of trustworthiness and familiarity; both characteristics that are evolutionarily advantageous [@hou2019survival; @little2011facial].
+As such, future studies are warranted to test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @goldstein2002influence].
 
@@
 In contrast to the findings for attractiveness, trustworthiness linearly increased beliefs in realness for females only.
-Given the evidence for the effect in the opposite direction, suggesting that faces presented as were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders.
-One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionary as a compromise their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-However, faces judged as highly untrustworthy should have appear as even more salient (representing an evolutionary threat), and hence be judged as more real.
+Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders.
+One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+That being the case, however, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-It is to note that the distribution of familiarity ratings was strongly skewed, and that a low number of pictures was rated as highly familiar.
+However, it is to note that the distribution of familiarity ratings was strongly skewed, and that a low number of pictures was rated as highly familiar.
 Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposures of items before the simulation monitoring ratings.
 
-<!-- inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake) -->
+<!-- inter-indiv correlates -->
+Unsurprisingly, participants with higher scores in Narcissism traits of Acclaim Seeking and Grandiose Fantasies were generally more confident in their simulation monitoring decisions.
+While early researchers had proposed narcissism to be a unitary construct [@raskin1988principal; @sedikides2004normal], recent studies cast narcissism as encompassing 2 unique dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and a need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness [@pincus2011narcissistic].
+Whereas narcissism has long been linked to over-confidence in decision-making [@campbell2004narcissism], a growing body of research indicates that this relationship is likely mostly driven by facets of narcissistic grandiosity (such as Acclaim Seeking), which drives individuals to see themselves as more superior than others and to externalize blame for poor decision-making consequences [@o2021grandiose].
+Indeed, the evidence alludes that attributes specific to narcissistic grandiosity predict individuals' overconfidence in cognitive decision-making [@chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
 
-<!-- AI attitudes (enthusiam - positive with confidence in both real and fake judgements) -->
+Conversely, the literature on the correlation between honesty-humility and perceptual confidence judgements remain comparatively scarce, albeit some existing research links higher levels of honesty-humility to increased perceptions of risk and greater risk aversion [@levidi2022understanding; @weller2012honest].
+As such, it could be argued that individuals with higher levels of honesty-humility could inherently possess a greater simulation monitoring sensitivity, perceiving a higher risk involved in making decisions on realness and therefore be less confident of their beliefs of reality.
+This is further supported by convergent evidence finding a negative link between honesty-humility and narcissism [@hodson2018dark].
+Therefore, further research examining the relationship between simulation monitoring decisions, personality traits, particularly that related to the dark triad and honesty-humility, and the perceived risks involved in making such evaluations, is warranted.
+
+<!-- AI attitudes -->
+Interestingly, despite the ubiquity of AI, there is a lack of research pertaining to the influence of people's AI attitudes on their confidence in their discriminative ability to distinguish between output that is "true" (i.e., images of real faces) from those that is artificially-generated.
+One possible explanation for the positive relationship observed between AI-Enthusiasm and confidence in reality judgements could be that individuals with highly positive AI attitudes may perceive themselves as having greater knowledge about AI and its capabilities, hence permitting them to be more confident in their simulation monitoring decisions.
+This is in line with previous research findings, which indicate that greater enthusiasm about AI is related to having a higher confidence in one's knowledge regarding AI competencies [@said2022artificial].
+Moreover, @said2022artificial further reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications.
+Specifically, people with AI attitudes that were highly positive and that were more confident in their AI knowledge were more likely to over-estimate the advantages of AI and under-estimate the risks involved in their application.
+As such, it is plausible that individuals' perceived self-knowledge about AI could have modulated the relationship between their attitudes towards AI and their confidence in their reality judgements.
 
 <!-- Re-exposure Delay -->
+Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real.
+This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
+Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces [@wiese2021familiarity].
+Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
+Future studies could hence further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
 
-Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, with shorter delays being associated with faces being rated as more real.
-Interestingly, while it could be posited that shorter delays led to the faces appearing more familiar and thereby increased people's belief in its realness, this seems unlikely considering perceived familiarity did not significantly affect simulation monitoring decisions made, even after controlling for attractiveness and trustworthiness.
-Alternatively, shorter re-exposure delays could have led to the faces being better remembered, thus triggering autobiographical memory processes [@gobbini2013prioritized] and evoking a sense of personal relevance during the repeated display.
-Indeed, fictional stimuli that were associated with more personal memories have been shown to up-regulate emotions [@sperduti2016paradox; @makowski2017being], thus biasing the realness of the given stimulus
+In conclusion, research on our ability to discriminate between what is real from what is not is increasingly relevant given the current expansion on technologies related to virtual and augmented realities.
+The aim of the present study was to examine whether facial attractiveness can significantly influence our simulation monitoring decisions.
+In line with our hypothesis, we found faces rated as attractive and unattractive to be perceived as more real for females as a result of an increased salience.
+However, for males, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized.
+As such, future studies could further investigate the role of attractiveness in simulation monitoring, taking greater consideration of the former's multidimensionality.
 

### 2022-09-21 analysis.Rmd
update results

--- 2022-09-15 analysis.Rmd
@@
 title: "Face Attractiveness and the Sense of Reality"
-output: html_document
+author: "Dominique Makowski et al."
+output:
+  html_document:
+    toc: true
+    toc_depth: 2
+    theme: paper
+    code_folding: hide
 date: "`r Sys.Date()`"
@@
 
-We removed `r length(outliers)` participants upon inspection of...
+We removed `r length(outliers)` participants based on failed attention checks.
 
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, cache=cache}
 extreme_items <- df |>
@@
   kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |>
-  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")
+  kableExtra::row_spec(which(dfsub$Participant %in% outliers_partial) + 1, background = "#FFCC80")  |> 
+  kableExtra::kable_styling(full_width = TRUE) |> 
+  kableExtra::scroll_box(width = "100%", height = "500px")
 # kableExtra::row_spec(which(str_detect(dfsub$Participant, "613a972033d79df11a6570de")) + 1, background = "green")
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, cache=cache}
 p_att <- dfsub |>
@@
 
-plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 10, size = 4) {
+plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 10, size = 6) {
   # library(emojifont)
@@
 
-```{r message=FALSE, warning=FALSE, fig.height=fig.width*1.5}
+```{r message=FALSE, warning=FALSE, fig.height=fig.width*1.5, cache=cache}
 # plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, cache=cache}
 preds <- data.frame()
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, cache=cache}
 dats |>
@@
 
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, cache=cache}
 model <- glmmTMB::glmmTMB(Belief ~ Delay + (1 | Participant) + (1 | Stimulus),
@@
 
-parameters::parameters(model, effects="fixed", exponentiate=TRUE)
-parameters::parameters(m_conf, effects="fixed")
+parameters::parameters(model, effects="fixed", exponentiate=TRUE) |> 
+  display()
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
 ```
 
-## Determinants of Reality
+## Determinants of Reality {.tabset}
 
@@
   param <- parameters::parameters(m_real, effects = "fixed", keep = var)
-  sig <- data.frame(
-    x = 0.5,
-    y = y_real[c(11, 32), "Predicted"] + c(0.05, -0.05),
+  sig1 <- data.frame(x = 0.5, 
+                     y = y_real[c(11, 31), "Predicted"] + c(0.04, -0.05),
                      p = c(min(param$p[c(1, 3)]), min(param$p[c(2, 4)])),
-    Sex = c("Female", "Male")
-  )
-  sig$label <- format_p(sig$p, stars_only = TRUE)
+                     Sex = y_real[c(11, 31), "Sex"])
+  sig1$label <- ifelse(sig1$p > .05 & sig1$p < .099, format_p(sig1$p), format_p(sig1$p, stars_only = TRUE))
+  param <- parameters::parameters(m_conf, effects = "fixed", keep = var)
+  sig2 <- data.frame(x = 0.5,
+                     y = y_conf[c(11, 31, 51, 71), "Predicted"] + c(0.04, -0.04, -0.04, 0.04),
+                     p = c(min(param$p[c(1, 5)]), min(param$p[c(2, 6)]), min(param$p[c(3, 7)]), min(param$p[c(4, 8)])),
+                     Belief = y_conf[c(11, 31, 51, 71), "Belief"],
+                     Sex = y_conf[c(11, 32, 51, 72), "Sex"])
+  sig2$label <- ifelse(sig2$p > .05 & sig2$p < .099, format_p(sig2$p), format_p(sig2$p, stars_only = TRUE))
 
@@
     # geom_line(data = trend, aes(y = Predicted, color=Sex, linetype=Trend, group=interaction(Sex, group)), size=0.6) +
-    geom_text(data = sig, aes(y = y, x = x, label = label, color = Sex), size = 8) +
+    geom_text(data = sig1, aes(y = y, x = x, label = label, color = Sex), size = ifelse(sig1$p < .05, 8.5, 3.5)) +
+    geom_text(data = sig2, aes(y = y, x = x, label = label, color = Sex), size = ifelse(sig2$p < .05, 5, 3)) +
     scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
@@
 
-```{r message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width}
+```{r make_models, message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width, cache=cache}
 rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
@@
 )
+```
 
+### Attractiveness
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+parameters::parameters(rez_at$model_belief, effects = "fixed", keep = "Attractive") |> 
+  display()
+performance::performance(rez_at$model_belief, metrics = c("R2")) |> 
+  display()
+performance::icc(rez_at$model_belief, by_group = TRUE)  |> 
+  display()
+parameters::parameters(rez_at$model_confidence, effects = "fixed", keep = "Attractive")  |> 
+  display()
+
+rez_at$p
+```
+
+### Beauty
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+parameters::parameters(rez_gl$model_belief, effects = "fixed", keep = "Beauty")|> 
+  display()
+performance::performance(rez_gl$model_belief, metrics = c("R2")) |> 
+  display()
+performance::icc(rez_gl$model_belief, by_group = TRUE)|> 
+  display()
+parameters::parameters(rez_gl$model_confidence, effects = "fixed", keep = "Beauty") |> 
+  display()
+
+rez_gl$p
+```
+
+### Trustworthiness
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+parameters::parameters(rez_tr$model_belief, effects = "fixed", keep = "Trustworthy") |> 
+  display()
+performance::performance(rez_tr$model_belief, metrics = c("R2")) |> 
+  display()
+performance::icc(rez_tr$model_belief, by_group = TRUE) |> 
+  display()
+parameters::parameters(rez_tr$model_confidence, effects = "fixed", keep = "Trustworthy") |> 
+  display()
+
+rez_tr$p
+```
+
+### Familiarity
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+parameters::parameters(rez_fa$model_belief, effects = "fixed", keep = "Familiar") |> 
+  display()
+performance::performance(rez_fa$model_belief, metrics = c("R2")) |> 
+  display()
+performance::icc(rez_fa$model_belief, by_group = TRUE) |> 
+  display()
+parameters::parameters(rez_fa$model_confidence, effects = "fixed", keep = "Familiar") |> 
+  display()
+
+rez_fa$p
+```
+
+## Interaction with Self-Attractiveness
+
+```{r message=FALSE, warning=FALSE}
+cor_test(dfsub, "SelfAttractiveness1", "SelfAttractiveness2")
+
+df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Attractive, 2) * Self_Attractiveness) + (1 | Participant) + (1 | Stimulus),
+  data = filter(df, Stimulus_Interest == TRUE),
+  family = "binomial"
+)
+parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness") |> 
+  display()
+
+m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Beauty, 2) * Self_Attractiveness) + Trustworthy + Familiar + (1 | Participant) + (1 | Stimulus),
+  data = filter(df, Stimulus_Interest == TRUE),
+  family = "binomial"
+)
+parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness") |> 
+  display()
+```
+
+## Inter-Individual Correlates {.tabset}
+
+```{r message=FALSE, warning=FALSE}
+plot_interindividual <- function(m_real, m_conf, var = "IPIP6_HonestyHumility", fill = "#D81B60") {
+  y_real <- estimate_relation(m_real, at = c(var), length = 21)
+  y_conf <- estimate_relation(m_conf, at = c(var, "Belief"), length = 21)
+
+  y_conf <- y_conf |>
+    mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(x, range = c(1, 0), to = c(0, 0.5))))
+
+  # Significance
+  mid <- max(y_conf[[var]])-diff(range(y_conf[[var]])) / 2
+  sig1 <- data.frame(x = mid, y = y_real[c(11), "Predicted"] + 0.065,
+                     p = parameters::parameters(m_real, effects = "fixed", keep = var)$p)
+  sig1$label <- ifelse(sig1$p > .05 & sig1$p < .1, format_p(sig1$p), format_p(sig1$p, stars_only = TRUE))
+  sig2 <- data.frame(x = mid, y = y_conf[c(11, 31), "Predicted"] + c(-0.065, 0.065),
+                     p = parameters::parameters(m_conf, effects = "fixed", keep = var)$p,
+                     Belief = y_conf[c(11, 31), "Belief"])
+  sig2$label <- ifelse(sig2$p > .05 & sig2$p < .1, format_p(sig2$p), format_p(sig2$p, stars_only = TRUE))
+
+  # Data
+  dat <- insight::get_data(m_conf) |> 
+                  group_by(Participant, Belief) |> 
+                  data_select(c("Participant", "Belief", var, "Belief_Confidence")) |> 
+                  mean_qi(.width = 0.5) |> 
+    mutate(Belief_Confidence = ifelse(Belief == "Real", datawizard::rescale(Belief_Confidence, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(Belief_Confidence, range = c(1, 0), to = c(0, 0.5))))
+
+  # Plot
+  p <- df |>
+    ggplot(aes_string(x = var, y = "Real")) +
+    stat_density_2d(data=filter(df, Belief=="Real"), aes(fill = ..density..), geom = "raster", contour = FALSE, alpha=0.5) +
+    scale_fill_gradientn(colors = c("white", "#4CAF50"), guide = "none") +
+    ggnewscale::new_scale_fill() +
+    stat_density_2d(data=filter(df, Belief=="Fake"), aes(fill = ..density..), geom = "raster", contour = FALSE, alpha=0.5) +
+    scale_fill_gradientn(colors = c("white", "#F44336"), guide = "none") +
+    ggnewscale::new_scale_fill() +
+    geom_hline(yintercept = 0.5, linetype = "dotted") +
+    geom_point2(data=dat, aes(y = Belief_Confidence, color = Belief), alpha = 0.25, size = 4) +
+    geom_ribbon(data = y_conf, aes(y = Predicted, ymin = CI_low, ymax = CI_high, fill = Belief), alpha = 1 / 6) +
+    geom_line(data = y_conf, aes(y = Predicted, group = Belief, color = Belief)) +
+    geom_ribbon(data = y_real, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 1 / 6) +
+    geom_line(data = y_real, aes(y = Predicted), size=1) +
+    geom_text(data = sig1, aes(y = y, x = x, label = label), size = ifelse(sig1$p < .05, 8, 3.5)) +
+    geom_text(data = sig2, aes(y = y, x = x, label = label), size = ifelse(sig2$p < .05, 8, 3.5)) +
+    scale_color_manual(values = c("Real" = "#4CAF50", "Fake" = "#F44336")) +
+    scale_fill_manual(values = c("Real" = "#4CAF50", "Fake" = "#F44336")) +
+    scale_x_continuous(expand = c(0, 0)) +
+    scale_y_continuous(expand = c(0, 0), breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c("Fake", "25%", "50%", "75%", "Real")) +
+    labs(y = "Simulation Monitoring") +
+    guides(fill = guide_legend(override.aes = list(alpha = 1))) +
+    theme_modern(axis.title.space = 5) +
+    ggside::geom_xsidedensity(data=dat, fill = fill, color = NA) +
+    ggside::geom_ysidedensity(data=dat, aes(fill = Belief, y=Belief_Confidence), color = NA) +
+    ggside::theme_ggside_void() +
+    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+    ggside::scale_xsidey_continuous(expand = c(0, 0))
+
+  p
+}
+```
+
+```{r message=FALSE, warning=FALSE}
+make_correlation <- function(x, y) {
+  cor <- correlation::correlation(x,
+    y,
+    bayesian = TRUE,
+    bayesian_prior = "medium.narrow",
+    sort = TRUE
+  ) |>
+    datawizard::data_remove(c("ROPE_Percentage"))
+  cor$`BF (Spearman)` <- format_bf(
+    correlation::correlation(
+      x, y,
+      bayesian = TRUE,
+      ranktransform = TRUE,
+      bayesian_prior = "medium.narrow"
+    )$BF,
+    name = NULL, stars = TRUE
+  )
+  cor |>
+    arrange(desc(BF))
+}
+```
+
+### IPIP-6
+
+```{r ipip, message=FALSE, warning=FALSE, cache=cache}
+f <- paste0("(",paste(names(select(df, starts_with("IPIP"))), collapse = " + "), 
+            ") + (1|Participant) + (1|Stimulus)")
+
+m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", f)), data=df, family = "binomial")
+
+parameters::parameters(m_real, effects="fixed") |> 
+  display()
+
+m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", f)), 
+                           data=df, 
+                           family = glmmTMB::beta_family())
+
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
+
+p_ipip <- plot_interindividual(m_real, m_conf, var = "IPIP6_HonestyHumility", fill = "#00BCD4") + labs(x = "Honesty-Humility")
+p_ipip
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+sr <- c("Confidence_Fake", "Confidence_Real", "n_Real")
+
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IPIP")))
+filter(r, BF > 1)
+```
+
+### Narcissism
+
+```{r narcissism, message=FALSE, warning=FALSE, cache=cache}
+f <- paste0("(",paste(names(select(df, starts_with("FFNI"))), collapse = " + "), 
+            ") + (1|Participant) + (1|Stimulus)")
+
+m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", f)), data=df, family = "binomial")
+
+parameters::parameters(m_real, effects="fixed") |> 
+  display()
+
+m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", f)), 
+                           data=df, 
+                           family = glmmTMB::beta_family())
+
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
+
+p_ffni1 <- plot_interindividual(m_real, m_conf, var = "FFNI_AcclaimSeeking", fill = "#FFC107") + labs(x = "Narcissism (Acclaim Seeking)")
+p_ffni1
+
+p_ffni2 <- plot_interindividual(m_real, m_conf, var = "FFNI_Authoritativeness", fill = "#FF9800") + labs(x = "Narcissism (Authoritativeness)")
+p_ffni2
+
+p_ffni3 <- plot_interindividual(m_real, m_conf, var = "FFNI_ThrillSeeking", fill = "#FF5722") + labs(x = "Narcissism (Thrill Seeking)")
+p_ffni3 
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("FFNI_")))
+filter(r, BF > 1)
+```
+
+### Social Anxiety
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+f <- paste0("(",paste(names(select(df, starts_with("Social_"))), collapse = " + "), 
+            ") + (1|Participant) + (1|Stimulus)")
+
+m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", f)), data=df, family = "binomial")
+
+parameters::parameters(m_real, effects="fixed") |> 
+  display()
+
+m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", f)), 
+                           data=df, 
+                           family = glmmTMB::beta_family())
+
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
+
+p_social <- plot_interindividual(m_real, m_conf, var = "Social_Phobia", fill = "#E040FB") + labs(x = "Social Phobia")
+p_social 
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("Social_")))
+filter(r, BF > 1)
+```
+
+### Intolerance to Uncertainty
+
+```{r ius, message=FALSE, warning=FALSE, cache=cache}
+f <- paste0("(",paste(names(select(df, starts_with("IUS_"))), collapse = " + "), 
+            ") + (1|Participant) + (1|Stimulus)")
+
+m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", f)), data=df, family = "binomial")
+
+parameters::parameters(m_real, effects="fixed") |> 
+  display()
+
+m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", f)), 
+                           data=df, 
+                           family = glmmTMB::beta_family())
+
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IUS_")))
+filter(r, BF > 1)
+```
+
+### Paranoid Beliefs
+
+```{r gpts, message=FALSE, warning=FALSE, cache=cache}
+f <- paste0("(",paste(names(select(df, starts_with("GPTS_"))), collapse = " + "), 
+            ") + (1|Participant) + (1|Stimulus)")
+
+m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", f)), data=df, family = "binomial")
+
+parameters::parameters(m_real, effects="fixed") |> 
+  display()
+
+m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", f)), 
+                           data=df, 
+                           family = glmmTMB::beta_family())
+
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+r <- make_correlation(dfsub[sr], select(dfsub, starts_with("GPTS_")))
+filter(r, BF > 1)
+```
+
+### AI
+
+```{r ai, message=FALSE, warning=FALSE, cache=cache}
+rez <- parameters::n_factors(select(dfsub, starts_with("AI")))
+plot(rez)
+
+efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n = 3, rotation = "varimax", sort = TRUE)
+efa
+dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |>
+  cbind(dfsub)
+df <- predict(efa, newdata=df, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |> 
+  cbind(df)
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+f <- paste0("(AI_Enthusiasm + AI_Realness + AI_Danger) + (1|Participant) + (1|Stimulus)")
+
+m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", f)), data=df, family = "binomial")
+
+parameters::parameters(m_real, effects="fixed") |> 
+  display()
+
+m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", f)), 
+                           data=df, 
+                           family = glmmTMB::beta_family())
+
+parameters::parameters(m_conf, effects="fixed") |> 
+  display()
+
+p_ai <- plot_interindividual(m_real, m_conf, var = "AI_Enthusiasm", fill = "#607D8B") + 
+  labs(x = "Enthusiasm about AI technology")
+p_ai 
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
+filter(r, BF > 1)
+```
+
+## Figures
+
+```{r message=FALSE, warning=FALSE}
 fig1a <- (rez_at$p +
@@
   theme(legend.position='top', legend.title = element_blank())
-fig1a
+
+fig <- wrap_elements(fig1a) /
+  wrap_elements(
+    ((p_ffni1 / p_ipip) | (p_ffni2 / p_social) | (p_ffni3 / p_ai)) + 
+  plot_layout(guides = "collect") +
+  plot_annotation(title = "Personality Correlates of Simulation Monitoring Tendencies", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
+  ) +
+  plot_layout(heights = c(1.1, 0.9))
+
+ggsave("figures/Figure2.png", width=fig.height * 1.8, height=fig.width * 1.5)
 ```
 
-```{r message=FALSE, warning=FALSE}
-parameters::parameters(rez_at$model_belief, effects = "fixed", keep = "Attractive")
-performance::r2(rez_at$model_belief)
-performance::icc(rez_at$model_belief, by_group = TRUE)
-parameters::parameters(rez_at$model_confidence, effects = "fixed", keep = "Attractive")
-
-parameters::parameters(rez_gl$model_belief, effects = "fixed", keep = "Beauty")
-performance::r2(rez_gl$model_belief)
-performance::icc(rez_gl$model_belief, by_group = TRUE)
-parameters::parameters(rez_gl$model_confidence, effects = "fixed", keep = "Beauty")
-
-parameters::parameters(rez_tr$model_belief, effects = "fixed", keep = "Trustworthy")
-performance::r2(rez_tr$model_belief)
-performance::icc(rez_tr$model_belief, by_group = TRUE)
-parameters::parameters(rez_tr$model_confidence, effects = "fixed", keep = "Trustworthy")
-
-parameters::parameters(rez_fa$model_belief, effects = "fixed", keep = "Familiar")
-performance::r2(rez_fa$model_belief)
-performance::icc(rez_fa$model_belief, by_group = TRUE)
-parameters::parameters(rez_fa$model_confidence, effects = "fixed", keep = "Familiar")
-```
-
-## Interaction with Self-Attractiveness
-
-```{r message=FALSE, warning=FALSE}
-cor_test(dfsub, "SelfAttractiveness1", "SelfAttractiveness2")
-
-df$Self_Attractiveness <- rowMeans(df[c("SelfAttractiveness1", "SelfAttractiveness2")])
-```
-
-```{r message=FALSE, warning=FALSE}
-m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Attractive, 2) * Self_Attractiveness) + (1 | Participant) + (1 | Stimulus),
-  data = filter(df, Stimulus_Interest == TRUE),
-  family = "binomial"
-)
-
-parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness")
-
-m_real <- glmmTMB::glmmTMB(Belief ~ Sex / (poly(Beauty, 2) * Self_Attractiveness) + Trustworthy + (1 | Participant) + (1 | Stimulus),
-  data = filter(df, Stimulus_Interest == TRUE),
-  family = "binomial"
-)
-
-parameters::parameters(m_real, effects = "fixed", keep = "Self_Attractiveness")
-```
-
-## Inter-Individual Correlates
-
-### IPIP-6
-
-```{r message=FALSE, warning=FALSE}
-make_correlation <- function(x, y) {
-  cor <- correlation::correlation(x,
-    y,
-    bayesian = TRUE,
-    bayesian_prior = "medium.narrow",
-    sort = TRUE
-  ) |>
-    datawizard::data_remove(c("ROPE_Percentage"))
-  cor$`BF (Spearman)` <- format_bf(
-    correlation::correlation(
-      x, y,
-      bayesian = TRUE,
-      ranktransform = TRUE,
-      bayesian_prior = "medium.narrow"
-    )$BF,
-    name = NULL, stars = TRUE
-  )
-  cor |>
-    arrange(desc(BF))
-}
-
+```{r message=FALSE, warning=FALSE, eval=FALSE}
 plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey", fillx = "purple") {
@@
 }
-```
-```{r message=FALSE, warning=FALSE}
-sr <- c("Confidence_Fake", "Confidence_Real", "n_Real")
 
-r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IPIP")))
-filter(r, BF > 1)
-```
-
-### AI
-
-```{r message=FALSE, warning=FALSE}
-rez <- parameters::n_factors(select(dfsub, starts_with("AI")))
-plot(rez)
-
-efa <- parameters::factor_analysis(select(dfsub, starts_with("AI")), n = 3, rotation = "varimax", sort = TRUE)
-efa
-dfsub <- predict(efa, names = c("AI_Enthusiasm", "AI_Realness", "AI_Danger")) |>
-  cbind(dfsub)
-```
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, AI_Enthusiasm, AI_Realness, AI_Danger))
-filter(r, BF > 1)
-```
-
-### Social Anxiety
-
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, starts_with("Social_")))
-filter(r, BF > 1)
-```
-
-### Intolerance to Uncertainty
-
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IUS_")))
-filter(r, BF > 1)
-```
-
-### Narcissism
-
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, starts_with("FFNI_")))
-filter(r, BF > 1)
-```
-
-### Paranoid Beliefs
-
-```{r message=FALSE, warning=FALSE}
-r <- make_correlation(dfsub[sr], select(dfsub, starts_with("GPTS_")))
-filter(r, BF > 1)
-```
-
-```{r message=FALSE, warning=FALSE}
 p1 <- plot_correlation(dfsub,
@@
     ((p3 / p2) | (p1 / p6) | (p4 / p5)) + 
-  plot_annotation(title = "Personality Correlates of Simulation Monitoring Tendencies", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
+  plot_annotation(title = "Personality Correlates of Simulation Monitoring", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
   ) +
@@
 ```
+
+# References

### 2022-09-21 submission/manuscript.Rmd
Update manuscript.Rmd
update results

@@
   Abstract abstract abstract.
-keywords          : "visual illusions, illusion game, Pyllusion, personality, general factor"
+keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
 wordcount         : "5114"
@@
 To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale [*GAAIS*, @schepman2020initial].
-This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the set of scales.
+This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the surveys.
 
-In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display for 750ms.
-After each stimulus presentation, ratings of **Attractiveness** ("I find this person attractive"), **Beauty** ("This face is good-looking"), **Trustworthiness** ("I find this person trustworthy") and **Familiarity** ("This person reminds me of someone I know") were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 scales, measuring general attractiveness (**Attractiveness**) and physical attractiveness (**Beauty**), to determine whether the effects on simulation monitoring are driven by physical features.
+In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 50 0ms each, in a randomized order, following a fixation cross display (750 ms).
+After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales.
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").
 
@@
 This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with *Fake* and *Real* as the two extremes).
-The study was implemented using *jsPsych* [@de2015jspsych], and the full set of instructions is available in the experiment code.
+The study was implemented using *jsPsych* [@de2015jspsych], and the exact instructions are available in the experiment code.
 
@@
 
-One hundred and three participants were recruited via *Prolific*, the the crowd-sourcing platform providing the best data quality [@peer2022].
+One hundred and three participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
-Models predicting the former were set as logistic mixed models (with the participants and images entered as random factors), and models modeling the latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) were modeled using beta regression models (suited for an outcome variable expressed in percentages).
+The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
+The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which models probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).
 
@@
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
+Finally, we investigated the inter-individual correlates of simulation monitoring with similar models (but this time, for all items regardless of the participant's gender or sexual orientation) for each questionnaire, with all of the subscales as orthogonal predictors.
 
-```{r message=FALSE, warning=FALSE, fig.cap="Top part shows blabla.", out.width="100%"}
+```{r message=FALSE, warning=FALSE, fig.cap="Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
+fake (solid line) and 2) on the confidence associated with that judgment (dashed lines) depending on the sex.
+Bottom part shows the effect of personality traits on the belief (black line) and the confidence associated with it (colored lines).
+The points are the average per participant confidence for both types of judgments.
+Stars indicate significance (p < .001***, p < .01**, p < .05*)", out.width="100%"}
 knitr::include_graphics("../figures/Figure2.png")
@@
 
-Finally, we investigated the inter-individual correlates of simulation monitoring by computing, for each participant, the proportion of faces judged as real (i.e., the overall bias towards one or the other belief), as well as the average confidence for faces judged as real, and fake.
-We assessed the link between these scores and dispositional traits using Bayesian correlation analysis [@makowski2019indices; @correlationArticle].
-
-The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle].
+The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle].
 As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
@@
 
-Bayesian correlations with personality traits suggested that Honesty-Humility was negatively associated with the confidence in reality ($r = -0.21$, $95\% CI = [-0.38, -0.03]$, $BF_{10} = 3.57$), and positively associated with the Narcissism trait of Acclaim Seeking ($r = 0.26$, $95\% CI = [0.08, 0.43]$, $BF_{10} = 14.38$) and Grandiose Fantasies ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.18$).
+The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship predominantly with the confidence associated with faces judged as real ($\beta_{real} = -1.69$, $95\% CI = [-2.74, -0.63]$, $z = -3.14$, $p < .01$; $\beta_{fake} = -1.02$, $95\% CI = [-2.07, 0.03]$, $z = -1.90$, $p = 0.058$).
+Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and *Acclaim Seeking* ($\beta_{real} = 2.08$, $95\% CI = [0.79, 3.37]$, $z = 3.16$, $p < .01$; $\beta_{fake} = 1.60$, $95\% CI = [0.30, 2.90]$, $z = 2.42$, $p < .05$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.38$, $95\% CI = [-2.50, -0.27]$, $z = -2.43$, $p < .05$; $\beta_{fake} = -1.23$, $95\% CI = [-2.35, -0.11]$, $z = -2.15$, $p < .05$) and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$).
+Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found.
+No significant relationships was found for intolerance to uncertainty or paranoid beliefs.
+
+<!-- Bayesian correlations with personality traits suggested that Honesty-Humility was negatively associated with the confidence in reality ($r = -0.21$, $95\% CI = [-0.38, -0.03]$, $BF_{10} = 3.57$), and positively associated with the Narcissism trait of Acclaim Seeking ($r = 0.26$, $95\% CI = [0.08, 0.43]$, $BF_{10} = 14.38$) and Grandiose Fantasies ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.18$).
 Acclaim Seeking was also positively related with the confidence in fake judgments ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.52$).
 No significant correlations was found for social anxiety, intolerance to uncertainty, or paranoid beliefs.
+-->
 
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real ($r = 0.24$, $95\% CI = [0.06, 0.41]$, $BF_{10} = 8.00$) and fake ($r = 0.28$, $95\% CI = [0.11, 0.44]$, $BF_{10} = 23.04$) judgments.
+Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.29$, $95\% CI = [0.08, 0.50]$, $z = 2.74$, $p < .01$; $\beta_{fake} = 0.38$, $95\% CI = [0.18, 0.59]$, $z = 3.60$, $p < 0.001$).
+
+<!-- Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real ($r = 0.24$, $95\% CI = [0.06, 0.41]$, $BF_{10} = 8.00$) and fake ($r = 0.28$, $95\% CI = [0.11, 0.44]$, $BF_{10} = 23.04$) judgments.
+-->
 
@@
 
-<!-- Attractiveness -->
+<!-- Attractiveness: females -->
 Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender.
-In particular, the quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-Alternatively, we could interpret the mostly positive linear relationship for males under an evolutionary lens.
+The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgments, and its role in simulation monitoring, are a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women **[REF?]**.
+
+<!-- Attractiveness: males -->
+Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial].
-However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces as significantly more salient than unattractive ones and in turn distorting the relationship with simulation monitoring, beauty, operationalized as physical attractiveness, was found to have a significant positive linear relationship with simulation monitoring decisions for males even after adjusting for the effects of trustworthiness and familiarity; both characteristics that are evolutionarily advantageous [@hou2019survival; @little2011facial].
-As such, future studies are warranted to test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @goldstein2002influence].
+However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces, in turn distorting the relationship with simulation monitoring.
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @goldstein2002influence].
+
+<!-- even after adjusting for the effects of trustworthiness and familiarity; both characteristics that are evolutionarily advantageous [@hou2019survival; @little2011facial]. A -->
 
 <!-- trustworthiness -->
-In contrast to the findings for attractiveness, trustworthiness linearly increased beliefs in realness for females only.
+Our results suggested that trustworthiness ratings linearly increased beliefs in realness, for females only.
 Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders.
 One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-That being the case, however, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
+However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-However, it is to note that the distribution of familiarity ratings was strongly skewed, and that a low number of pictures was rated as highly familiar.
-Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposures of items before the simulation monitoring ratings.
+However, the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before the simulation monitoring judgments.
 
 <!-- inter-indiv correlates -->
-Unsurprisingly, participants with higher scores in Narcissism traits of Acclaim Seeking and Grandiose Fantasies were generally more confident in their simulation monitoring decisions.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with stronger narcissism (in particular the acclaim seeking and grandiose fantasies dimensions) displayed a stronger confidence in their simulation monitoring judgments.
+This is in line with the literature
+
 While early researchers had proposed narcissism to be a unitary construct [@raskin1988principal; @sedikides2004normal], recent studies cast narcissism as encompassing 2 unique dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and a need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness [@pincus2011narcissistic].
@@
 
-We would like to thank **TODO: add STUDENT NAME** for his contribution to the selection of the materials.
+We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
 

### 2022-09-21 submission/manuscript.tex
update results

@@
 {}{\PatchFailed}
-\keywords{visual illusions, illusion game, Pyllusion, personality, general factor\newline\indent Word count: 5114}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 5114}
 \usepackage{lineno}
@@
   pdflang={en-EN},
-  pdfkeywords={visual illusions, illusion game, Pyllusion, personality, general factor},
+  pdfkeywords={attractiveness, simulation monitoring, fiction, deep fakes, sense of reality},
   hidelinks,
@@
 In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
-Additionally, other factors, such as the stimulus' perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in our processing and reaction to real as opposed to non-real material.
+Additionally, other factors, such as the stimuli's perceived self-relevance (T.
+R.
+Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in our processing and reaction to real as opposed to non-real material.
 
-AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of faces evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
+AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
 Interestingly, some studies report that when the nature of the faces was ambiguous, artificially created faces that were previously rated as more attractive were judged by subjects to be less real (Tucciarelli et al., 2020).
@@
 
-This study primarily aims at exploring the effect of face attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory (outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely believed to be real.
+This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the embodied reality theory (outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011) measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012) assessing social anxiety levels, the \emph{FFNI-BF} (30 items, Jauk et al., 2022) measuring 9 facets of narcissism; the \emph{R-GPTS} (18 items, Freeman et al., 2021) measuring 2 dimensions related to paranoid thinking; the \emph{IUS-12} (12 items, Carleton et al., 2007) measuring intolerance to uncertainty.
-Finally, we created 5 items pertaining to expectations about AI-generated images technology (\textbf{TODO: write here some of the questions}).
-To lower their saliency and possibly prime the subjects about the task, we mixed these items with 5 items of the attitudes towards AI scale (\emph{GAAIS}, Schepman \& Rodway, 2020).
-This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the questionnaires.
+In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011) measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012) assessing social anxiety levels, the \emph{FFNI-BF} (30 items, Jauk et al., 2022) measuring 9 facets of narcissism; the \emph{R-GPTS} (18 items, Freeman et al., 2021) measuring 2 dimensions related to paranoid thinking; and the \emph{IUS-12} (12 items, Carleton et al., 2007) measuring intolerance to uncertainty.
+Finally, we devised 5 items pertaining to expectations about AI-generated images technology (``I think current Artificial Intelligence algorithms can generate very realistic images'').
+To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale (\emph{GAAIS}, Schepman \& Rodway, 2020).
+This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the surveys.
 
@@
 M.
-Chen et al., 2021)) were presented to the participants for 500ms each, in a randomized order.
-Following each stimulus, ratings of \textbf{Attractiveness} (``I find this person attractive''), \textbf{Beauty} (``This face is good-looking''), \textbf{Trustworthiness} (``I find this person trustworthy'') and \textbf{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
-(\textbf{TODO: add details and justifications})
+Chen et al., 2021)) were presented to the participants for 50 0ms each, in a randomized order, following a fixation cross display (750 ms).
+After each stimulus presentation, ratings of \emph{Trustworthiness} (``I find this person trustworthy'') and \emph{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we assessed attractiveness using 2 scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
 
@@
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
-This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scales (with \emph{Fake} and \emph{Real} as the two extremes).
-The study was implemented using \emph{jsPsych} (De Leeuw, 2015), and the full set of instructions is available in the experiment code.
+This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with \emph{Fake} and \emph{Real} as the two extremes).
+The study was implemented using \emph{jsPsych} (De Leeuw, 2015), and the exact instructions are available in the experiment code.
 
@@
 
-One hundred and three participants were recruited via \emph{Prolific}, the the crowd-sourcing platform providing the best data quality (Peer et al., 2022).
+One hundred and three participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data (Peer et al., 2022).
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two distinct mechanisms: the dichotomous \emph{belief} (real or fake, derived based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
-Models predicting the former were set as logistic mixed models (with the participants and images entered as random factors), and models modeling the latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) were modeled using beta regression models (suited for an outcome variable expressed in percentages).
+The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, derived based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
+The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which models probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).
 
@@
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
+Finally, we investigated the inter-individual correlates of simulation monitoring with similar models (but this time, for all items regardless of the participant's gender or sexual orientation) for each questionnaire, with all of the subscales as orthogonal predictors.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows blabla.}\label{fig:unnamed-chunk-3}
+\includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
+fake (solid line) and 2) on the confidence associated with that judgment (dashed lines) depending on the sex.
+Bottom part shows the effect of personality traits on the belief (black line) and the confidence associated with it (colored lines).
+The points are the average per participant confidence for both types of judgments.
+Stars indicate significance (p < .001***, p < .01**, p < .05*)}\label{fig:unnamed-chunk-3}
 \end{figure}
 
-Finally, we investigated the inter-individual correlates of simulation monitoring by computing, for each participant, the proportion of faces judged as real (i.e., the overall bias towards one or the other belief), as well as the average confidence for faces judged as real, and fake.
-We assessed the link between these scores and dispositional traits using Bayesian correlation analysis (Makowski et al., 2020; Makowski, Ben-Shachar, Chen, et al., 2019).
-
-The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski, Ben-Shachar, \& Lüdecke, 2019).
+The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski et al., 2020; Makowski, Ben-Shachar, et al., 2019).
 As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
@@
 
-Bayesian correlations with personality traits suggested that Honesty-Humility was negatively associated with the confidence in reality (\(r = -0.21\), \(95\% CI = [-0.38, -0.03]\), \(BF_{10} = 3.57\)), and positively associated with the Narcissism trait of Acclaim Seeking (\(r = 0.26\), \(95\% CI = [0.08, 0.43]\), \(BF_{10} = 14.38\)) and Grandiose Fantasies (\(r = 0.22\), \(95\% CI = [0.04, 0.40]\), \(BF_{10} = 4.18\)).
-Acclaim Seeking was also positively related with the confidence in fake judgments (\(r = 0.22\), \(95\% CI = [0.04, 0.40]\), \(BF_{10} = 4.52\)).
-No significant correlations was found for social anxiety, intolerance to uncertainty, or paranoid beliefs.
+The models including the personality traits suggested that \emph{Honesty-Humility} had a significant negative relationship predominantly with the confidence associated with faces judged as real (\(\beta_{real} = -1.69\), \(95\% CI = [-2.74, -0.63]\), \(z = -3.14\), \(p < .01\); \(\beta_{fake} = -1.02\), \(95\% CI = [-2.07, 0.03]\), \(z = -1.90\), \(p = 0.058\)).
+Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and \emph{Acclaim Seeking} (\(\beta_{real} = 2.08\), \(95\% CI = [0.79, 3.37]\), \(z = 3.16\), \(p < .01\); \(\beta_{fake} = 1.60\), \(95\% CI = [0.30, 2.90]\), \(z = 2.42\), \(p < .05\)), and a negative relationship with \emph{Authoritativeness} (\(\beta_{real} = -1.38\), \(95\% CI = [-2.50, -0.27]\), \(z = -2.43\), \(p < .05\); \(\beta_{fake} = -1.23\), \(95\% CI = [-2.35, -0.11]\), \(z = -2.15\), \(p < .05\)) and \emph{Thrill Seeking} (\(\beta_{real} = -0.93\), \(95\% CI = [-1.75, -0.10]\), \(z = -2.20\), \(p < .05\); \(\beta_{fake} = -1.03\), \(95\% CI = [-1.87, -0.20]\), \(z = -2.44\), \(p < .05\)).
+Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake (\(\beta = -0.97\), \(95\% CI = [-1.86, -0.08]\), \(z = -2.14\), \(p < .05\)), but no effect on the confidence judgments was found.
+No significant relationships was found for intolerance to uncertainty or paranoid beliefs.
 
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real (\(r = 0.24\), \(95\% CI = [0.06, 0.41]\), \(BF_{10} = 8.00\)) and fake (\(r = 0.28\), \(95\% CI = [0.11, 0.44]\), \(BF_{10} = 23.04\)) judgments.
+Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments (\(\beta_{real} = 0.29\), \(95\% CI = [0.08, 0.50]\), \(z = 2.74\), \(p < .01\); \(\beta_{fake} = 0.38\), \(95\% CI = [0.18, 0.59]\), \(z = 3.60\), \(p < 0.001\)).
 
@@
 
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern depending on the participant's gender.
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender.
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-Alternatively, we could interpret the mostly positive linear relationship for males under an evolutionary lens.
-In particular, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Fink et al., 2006; Qi \& Ying, 2022).
-As such, it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering attractive faces are significantly more salient than unattractive ones, in turn distorting the relationship with simulation monitoring.
-Future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (\textbf{ref on saliency in EEG or fMRI}) or physiological markers {[}in particular, heart rate deceleration, \textbf{include refs}{]}.
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgments, and its role in simulation monitoring, are a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women \textbf{{[}REF?{]}}.
 
-discuss why the link with beauty is slightly different.
-Note that for models for beauty we adjusted the models for trustowrthiness and familiarity, hence possibly masking the multidimensionality of attractiveness.
+Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
+Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Fink et al., 2006; Qi \& Ying, 2022).
+However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces, in turn distorting the relationship with simulation monitoring.
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers (in particular, heart rate deceleration, A.
+Goldstein et al., 2002).
 
-In contrast to the findings for attractiveness, trustworthiness linearly increased beliefs in realness for females only.
-Given the evidence for the effect in the opposite direction, suggesting that faces presented as were rated as more trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such link to be present for both genders.
-One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females (explained evolutionary as a compromise their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
-However, faces judged as highly untrustworthy should have appear as even more salient (representing an evolutionary threat), and hence be judged as more real.
+Our results suggested that trustworthiness ratings linearly increased beliefs in realness, for females only.
+Given the evidence suggesting that faces presented as real were rated as more trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such link to be present for both genders.
+One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females (explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
+However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-It is to note that the distribution of familiarity ratings was strongly skewed, and that a low number of pictures was rated as highly familiar.
-Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposures of items before the simulation monitoring ratings.
+However, the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before the simulation monitoring judgments.
 
-Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, with shorter delays being associated with faces being rated as more real.
-Interestingly, while it could be posited that shorter delays led to the faces appearing more familiar and thereby increased people's belief in its realness, this seems unlikely considering perceived familiarity did not significantly affect simulation monitoring decisions made, even after controlling for attractiveness and trustworthiness.
-Alternatively, shorter re-exposure delays could have led to the faces being better remembered, thus triggering autobiographical memory processes (Gobbini et al., 2013) and evoking a sense of personal relevance during the repeated display.
-Indeed, fictional stimuli that were associated with more personal memories have been shown to up-regulate emotions (Makowski et al., 2017; Sperduti et al., 2016), thus biasing the realness of the given stimulus
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with stronger narcissism (in particular the acclaim seeking and grandiose fantasies dimensions) displayed a stronger confidence in their simulation monitoring judgments.
+This is in line with the literature
+
+While early researchers had proposed narcissism to be a unitary construct (Raskin \& Terry, 1988; Sedikides et al., 2004), recent studies cast narcissism as encompassing 2 unique dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and a need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness (Pincus \& Roche, 2011).
+Whereas narcissism has long been linked to over-confidence in decision-making (Campbell et al., 2004), a growing body of research indicates that this relationship is likely mostly driven by facets of narcissistic grandiosity (such as Acclaim Seeking), which drives individuals to see themselves as more superior than others and to externalize blame for poor decision-making consequences (O'Reilly \& Hall, 2021).
+Indeed, the evidence alludes that attributes specific to narcissistic grandiosity predict individuals' overconfidence in cognitive decision-making (Brunell \& Buelow, 2017; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
+
+Conversely, the literature on the correlation between honesty-humility and perceptual confidence judgements remain comparatively scarce, albeit some existing research links higher levels of honesty-humility to increased perceptions of risk and greater risk aversion (Levidi et al., 2022; Weller \& Thulin, 2012).
+As such, it could be argued that individuals with higher levels of honesty-humility could inherently possess a greater simulation monitoring sensitivity, perceiving a higher risk involved in making decisions on realness and therefore be less confident of their beliefs of reality.
+This is further supported by convergent evidence finding a negative link between honesty-humility and narcissism (Hodson et al., 2018).
+Therefore, further research examining the relationship between simulation monitoring decisions, personality traits, particularly that related to the dark triad and honesty-humility, and the perceived risks involved in making such evaluations, is warranted.
+
+Interestingly, despite the ubiquity of AI, there is a lack of research pertaining to the influence of people's AI attitudes on their confidence in their discriminative ability to distinguish between output that is ``true'' (i.e., images of real faces) from those that is artificially-generated.
+One possible explanation for the positive relationship observed between AI-Enthusiasm and confidence in reality judgements could be that individuals with highly positive AI attitudes may perceive themselves as having greater knowledge about AI and its capabilities, hence permitting them to be more confident in their simulation monitoring decisions.
+This is in line with previous research findings, which indicate that greater enthusiasm about AI is related to having a higher confidence in one's knowledge regarding AI competencies (Said et al., 2022).
+Moreover, Said et al.
+(2022) further reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications.
+Specifically, people with AI attitudes that were highly positive and that were more confident in their AI knowledge were more likely to over-estimate the advantages of AI and under-estimate the risks involved in their application.
+As such, it is plausible that individuals' perceived self-knowledge about AI could have modulated the relationship between their attitudes towards AI and their confidence in their reality judgements.
+
+Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real.
+This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
+Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces (Wiese et al., 2021).
+Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity (Makowski et al., 2017; Sperduti et al., 2016), thus biasing its salience and perceived realness.
+Future studies could hence further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+
+In conclusion, research on our ability to discriminate between what is real from what is not is increasingly relevant given the current expansion on technologies related to virtual and augmented realities.
+The aim of the present study was to examine whether facial attractiveness can significantly influence our simulation monitoring decisions.
+In line with our hypothesis, we found faces rated as attractive and unattractive to be perceived as more real for females as a result of an increased salience.
+However, for males, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized.
+As such, future studies could further investigate the role of attractiveness in simulation monitoring, taking greater consideration of the former's multidimensionality.
 
@@
 
-We would like to thank \textbf{TODO: add STUDENT NAME} for his contribution to the selection of the materials.
+We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abraham2009reality}{}}%
+Abraham, A., \& Von Cramon, D.
+Y.
+(2009).
+Reality= relevance?
+Insights from spontaneous modulations of the brain's default network when telling apart reality from fiction.
+\emph{PloS One}, \emph{4}(3), e4741.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-brunell2017narcissism}{}}%
+Brunell, A. B., \& Buelow, M. T. (2017). Narcissism and performance on behavioral decision-making tasks. \emph{Journal of Behavioral Decision Making}, \emph{30}(1), 3--14.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-campbell2004narcissism}{}}%
+Campbell, W. K., Goodie, A. S., \& Foster, J. D. (2004). Narcissism, confidence, and risk attitude. \emph{Journal of Behavioral Decision Making}, \emph{17}(4), 297--311.
+
 \leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
@@
 \emph{Journal of Anxiety Disorders}, \emph{21}(1), 105--117.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
+Chatterjee, A., \& Pollock, T. G. (2017). Master of puppets: How narcissistic CEOs construct their professional worlds. \emph{Academy of Management Review}, \emph{42}(4), 703--725.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein2002influence}{}}%
+Goldstein, A., Spencer, K. M., \& Donchin, E. (2002). The influence of stimulus deviance and novelty on the P300 and novelty P3. \emph{Psychophysiology}, \emph{39}(6), 781--790.
+
 \leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
@@
 \emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4), 232.
+
+\leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
+Han, S., Li, Y., Liu, S., Xu, Q., Tan, Q., \& Zhang, L.
+(2018).
+Beauty is in the eye of the beholder: The halo effect and generalization effect in the facial attractiveness evaluation.
+\emph{Acta Psychologica Sinica}, \emph{50}(4), 363.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hodson2018dark}{}}%
+Hodson, G., Book, A., Visser, B.
+A., Volk, A.
+A., Ashton, M.
+C., \& Lee, K.
+(2018).
+Is the dark triad common factor distinct from low honesty-humility?
+\emph{Journal of Research in Personality}, \emph{73}, 123--129.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-indovina2007dissociation}{}}%
+Indovina, I., \& Macaluso, E. (2007). Dissociation of stimulus relevance and saliency factors during shifts of visuospatial attention. \emph{Cerebral Cortex}, \emph{17}(7), 1701--1711.
+
 \leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
@@
 \emph{Assessment}, 10731911221075761.
+
+\leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
+Levidi, M.
+D.
+C., McGrath, A., Kyriakoulis, P., \& Sulikowski, D.
+(2022).
+Understanding criminal decision-making: Links between honesty-humility, perceived risk and negative affect: Psychology, crime \& law.
+\emph{Psychology, Crime and Law}, 1--29.
 
@@
 \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{366}(1571), 1638--1659.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lou2015perceptual}{}}%
+Lou, B., Hsu, W.-Y., \& Sajda, P.
+(2015).
+Perceptual salience and reward both influence feedback-related neural activity arising from choice.
+\emph{Journal of Neuroscience}, \emph{35}(38), 13064--13075.
 
@@
 Makowski, D. (2018). \emph{Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal} {[}PhD thesis{]}. Sorbonne Paris Cit{é}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2019indices}{}}%
-Makowski, D., Ben-Shachar, M. S., Chen, S. A., \& Lüdecke, D. (2019). Indices of effect existence and significance in the bayesian framework. \emph{Frontiers in Psychology}, \emph{10}, 2767.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-o2021grandiose}{}}%
+O'Reilly, C.
+A., \& Hall, N.
+(2021).
+Grandiose narcissists and decision making: Impulsive, overconfident, and skeptical of experts--but seldom in doubt.
+\emph{Personality and Individual Differences}, \emph{168}, 110280.
+
 \leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pincus2011narcissistic}{}}%
+Pincus, A.
+L., \& Roche, M.
+J.
+(2011).
+Narcissistic grandiosity and narcissistic vulnerability.
+\emph{The Handbook of Narcissism and Narcissistic Personality Disorder: Theoretical Approaches, Empirical Findings, and Treatments}, 31--40.
+
 \leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-raskin1988principal}{}}%
+Raskin, R., \& Terry, H.
+(1988).
+A principal-components analysis of the narcissistic personality inventory and further evidence of its construct validity.
+\emph{Journal of Personality and Social Psychology}, \emph{54}(5), 890.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
+Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
+
+\leavevmode\vadjust pre{\hypertarget{ref-said2022artificial}{}}%
+Said, N., Potinteu, A.-E., Brich, I., Buder, J., Schumm, H., \& Huff, M. (2022). \emph{An artificial intelligence perspective: How knowledge and confidence shape risk and opportunity perception}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
@@
 Schepman, A., \& Rodway, P. (2020). Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in Human Behavior Reports}, \emph{1}, 100014.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sedikides2004normal}{}}%
+Sedikides, C., Rudich, E.
+A., Gregg, A.
+P., Kumashiro, M., \& Rusbult, C.
+(2004).
+Are normal narcissists psychologically healthy?: Self-esteem matters.
+\emph{Journal of Personality and Social Psychology}, \emph{87}(3), 400.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-taylor2009neural}{}}%
+Taylor, M.
+J., Arsalidou, M., Bayless, S.
+J., Morris, D., Evans, J.
+W., \& Barbeau, E.
+J.
+(2009).
+Neural correlates of personally familiar faces: Parents, partner and own faces.
+\emph{Human Brain Mapping}, \emph{30}(7), 2008--2020.
+
 \leavevmode\vadjust pre{\hypertarget{ref-tsikandilakis2019beauty}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
+Weller, J.
+A., \& Thulin, E.
+W.
+(2012).
+Do honest people take fewer risks?
+Personality correlates of risk-taking to achieve gains and avoid losses in HEXACO space.
+\emph{Personality and Individual Differences}, \emph{53}(7), 923--926.
+
 \leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wiese2021familiarity}{}}%
+Wiese, H., Hobden, G., Siilbek, E., Martignac, V., Flack, T.
+R., Ritchie, K.
+L., Young, A.
+W., \& Burton, A.
+M.
+(2021).
+Familiarity is familiarity is familiarity: Event-related brain potentials reveal qualitatively similar representations of personally familiar and famous faces.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}.
+
 \end{CSLReferences}

### 2022-09-21 submission/manuscript.Rmd
discussion

@@
 <!-- inter-indiv correlates -->
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with stronger narcissism (in particular the acclaim seeking and grandiose fantasies dimensions) displayed a stronger confidence in their simulation monitoring judgments.
-This is in line with the literature
-
-While early researchers had proposed narcissism to be a unitary construct [@raskin1988principal; @sedikides2004normal], recent studies cast narcissism as encompassing 2 unique dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and a need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness [@pincus2011narcissistic].
-Whereas narcissism has long been linked to over-confidence in decision-making [@campbell2004narcissism], a growing body of research indicates that this relationship is likely mostly driven by facets of narcissistic grandiosity (such as Acclaim Seeking), which drives individuals to see themselves as more superior than others and to externalize blame for poor decision-making consequences [@o2021grandiose].
-Indeed, the evidence alludes that attributes specific to narcissistic grandiosity predict individuals' overconfidence in cognitive decision-making [@chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-
-Conversely, the literature on the correlation between honesty-humility and perceptual confidence judgements remain comparatively scarce, albeit some existing research links higher levels of honesty-humility to increased perceptions of risk and greater risk aversion [@levidi2022understanding; @weller2012honest].
-As such, it could be argued that individuals with higher levels of honesty-humility could inherently possess a greater simulation monitoring sensitivity, perceiving a higher risk involved in making decisions on realness and therefore be less confident of their beliefs of reality.
-This is further supported by convergent evidence finding a negative link between honesty-humility and narcissism [@hodson2018dark].
-Therefore, further research examining the relationship between simulation monitoring decisions, personality traits, particularly that related to the dark triad and honesty-humility, and the perceived risks involved in making such evaluations, is warranted.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
+Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+However, an inverse effect was found for other facets of narcissism, such as authoritativeness and thrill seeking.
+We interpret these effects as related to a higher response assertiveness and, for thrill seeking, tolerance of cognitive uncertainty (note that the tolerance to uncertainty scale, which mostly measures the anxiety associated with uncertain events, did not show any link).
+Taken together, these results suggest that participants with low humility, high recognition desires, and high excitement-seeking traits are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
+Participants with opposite traits might perceive a higher risk in the decision process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
 
 <!-- AI attitudes -->
-Interestingly, despite the ubiquity of AI, there is a lack of research pertaining to the influence of people's AI attitudes on their confidence in their discriminative ability to distinguish between output that is "true" (i.e., images of real faces) from those that is artificially-generated.
-One possible explanation for the positive relationship observed between AI-Enthusiasm and confidence in reality judgements could be that individuals with highly positive AI attitudes may perceive themselves as having greater knowledge about AI and its capabilities, hence permitting them to be more confident in their simulation monitoring decisions.
-This is in line with previous research findings, which indicate that greater enthusiasm about AI is related to having a higher confidence in one's knowledge regarding AI competencies [@said2022artificial].
-Moreover, @said2022artificial further reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications.
-Specifically, people with AI attitudes that were highly positive and that were more confident in their AI knowledge were more likely to over-estimate the advantages of AI and under-estimate the risks involved in their application.
-As such, it is plausible that individuals' perceived self-knowledge about AI could have modulated the relationship between their attitudes towards AI and their confidence in their reality judgements.
+Despite the ubiquity of AI, the literature pertaining on the influence of people's AI attitudes on simulation monitoring is scarce.
+Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
+Instead, we found that one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings.
+It is possible that participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
+This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].
+
+<!-- Social phobia -->
+However, it is to important note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
+In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, which low values were associated with an increased tendency of rating faces as real.
+**TODO: a bit of discussion, mostly on the fact taht the stimuli used were faces**.
 
 <!-- Re-exposure Delay -->
-Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real.
+On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real.
 This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].

### 2022-09-22 submission/manuscript.Rmd
updatess

@@
 These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
-Such developments not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
+Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
 This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
@@
 In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; and the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty.
-Finally, we devised 5 items pertaining to expectations about AI-generated images technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
+Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness ("How attractive would you say you are?", @marcinkowska2021self) and the other measuring physical attractiveness ("How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive).
+Finally, we devised 5 items pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
 To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale [*GAAIS*, @schepman2020initial].
-This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the surveys.
+This scale was presented after the social anxiety questionnaires.
+3 attention check questions were also embedded in the surveys.
 
-In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 50 0ms each, in a randomized order, following a fixation cross display (750 ms).
+In the second part of this study, 109 neutral-expression facial images of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 visual analog scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").
 
-In the last part of the study, participants were informed that about half of the face images previously seen were AI-generated (the instructions used a cover story mentioning that the research was aimed at validating a new face generation algorithm).
+In the last part of the study, participants were informed that about half of the facial images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 
-One hundred and three participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
+103 participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which models probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
+The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modeled the probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
 The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).
 
-We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real pictures of faces) were indeed judged as fake in a sufficient proportion to warrant their analysis.
+We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real images of faces) were indeed judged as fake in sufficient proportion to warrant their analysis.
 Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).
 
-The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**.
+The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**).
 Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*.
-We took into account the gender of participants and stimuli by retaining the pictures that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+We took into account the gender of participants and stimuli by retaining the images of faces that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
@@
 On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the pictures.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the images.
 
@@
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are not familiar or highly familiar.
 
@@
 Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found.
-No significant relationships was found for intolerance to uncertainty or paranoid beliefs.
+No significant relationships were found for intolerance to uncertainty or paranoid beliefs.
 
@@
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgments, and its role in simulation monitoring, are a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women **[REF?]**.
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
 
@@
 Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
-Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial].
-However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces, in turn distorting the relationship with simulation monitoring.
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @goldstein2002influence].
+Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
+However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].
 
@@
 <!-- trustworthiness -->
-Our results suggested that trustworthiness ratings linearly increased beliefs in realness, for females only.
-Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such link to be present for both genders.
-One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+Our results suggested that trustworthiness ratings linearly increased beliefs in realness for females only.
+Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be present for both genders.
+One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
 However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-However, the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before the simulation monitoring judgments.
+However, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Hence, future studies could re-examine this link (or lack thereof) by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items participants are subjected to before making simulation monitoring judgments.
 
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
-Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
 However, an inverse effect was found for other facets of narcissism, such as authoritativeness and thrill seeking.
-We interpret these effects as related to a higher response assertiveness and, for thrill seeking, tolerance of cognitive uncertainty (note that the tolerance to uncertainty scale, which mostly measures the anxiety associated with uncertain events, did not show any link).
+We interpret the effects of the former as related to a higher response assertiveness and, for thrill-seeking, a tolerance of cognitive uncertainty (note that the intolerance to uncertainty scale, which largely measures the anxiety associated with uncertain events, did not show any link).
 Taken together, these results suggest that participants with low humility, high recognition desires, and high excitement-seeking traits are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
@@
 <!-- AI attitudes -->
-Despite the ubiquity of AI, the literature pertaining on the influence of people's AI attitudes on simulation monitoring is scarce.
+Despite the ubiquity of AI, the literature pertaining the influence of people's AI attitudes on simulation monitoring is scarce.
 Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
@@
 <!-- Social phobia -->
-However, it is to important note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
-In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, which low values were associated with an increased tendency of rating faces as real.
-**TODO: a bit of discussion, mostly on the fact taht the stimuli used were faces**.
+However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
+In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency of rating faces as real.
+This association could be put into perspective considering that the stimuli used were images of real faces, and social phobia is characterized as an abnormally extreme fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact].
+Specifically, previous studies have found social phobia to be related to neutral faces being perceived as more threatening [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation].
+Whereas such reports indicate that individuals with greater social anxiety will perceive faces as more salient, hence suggesting that simulation monitoring decisions will be positively related to social phobia, we found opposing evidence that high social phobia scores were associated with increased ratings of faces being fake instead.
+This apparent contradiction could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which people change their mental representations of the realness of a stimulus to manage their own emotional reactions [@sperduti2017distinctive; @sperduti2016paradox].
+As the images of faces could have been perceived very negatively by individuals that are socially anxious, they may have spontaneously applied fictional reappraisal in processing the facial stimuli, thereby leading to an increased tendency to judge them as fake.
+Indeed, this is aligned with a previous study which reported that rates of belief in realness significantly decreased when pictures presented as real were emotional as compared to when they were neutral [@makowski2016phenomenal].
+Given the implication of cognitive control abilities with fictional reappraisal [@hofmann2012executive; @schmeichel2010working], this hypothesis could hence be tested by assessing executive functions in relation to their simulation monitoring decisions in future studies.
 

### 2022-09-25 analysis.Rmd
discussion
update

@@
       Sexual_Orientation == "Homosexual" & Stimulus_SameSex == "Same" ~ TRUE,
-      Sexual_Orientation %in% c("Bisexual", "Queer") ~ TRUE,
+      Sexual_Orientation %in% c("Bisexual", "Queer", "Pansexual") ~ TRUE,
       TRUE ~ NA
@@
   "5f0f0a2a8b2a480447f31b21_lqgpz",
-  "611d03b822d4c8e041ea0c32_m0knb"
+  "611d03b822d4c8e041ea0c32_m0knb",
+  # Prefered not answering to sexual orientation: further analysis impossible
+  "60eb34f117838a34a29a69d3_rxv85"
 )
@@
 
-plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 10, size = 6) {
+plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 7, size = 6) {
   # library(emojifont)
@@
   # Significance
+  sig1 <- data.frame(x = 0.5, 
+                     y = y_real[c(11, 31), "Predicted"],
+                     Sex = y_real[c(11, 31), "Sex"])
   param <- parameters::parameters(m_real, effects = "fixed", keep = var)
-  sig1 <- data.frame(x = 0.5, 
-                     y = y_real[c(11, 31), "Predicted"] + c(0.04, -0.05),
-                     p = c(min(param$p[c(1, 3)]), min(param$p[c(2, 4)])),
-                     Sex = y_real[c(11, 31), "Sex"])
+  sig1$p <- c(min(param[str_detect(param$Parameter, sig1$Sex[1]), "p"]), min(param[str_detect(param$Parameter, sig1$Sex[2]), "p"]))
+  sig1$y <- sig1$y + ifelse(sig1$Sex == "Male", 0.03, -0.03)
   sig1$label <- ifelse(sig1$p > .05 & sig1$p < .099, format_p(sig1$p), format_p(sig1$p, stars_only = TRUE))
-  param <- parameters::parameters(m_conf, effects = "fixed", keep = var)
+
   sig2 <- data.frame(x = 0.5, 
-                     y = y_conf[c(11, 31, 51, 71), "Predicted"] + c(0.04, -0.04, -0.04, 0.04),
-                     p = c(min(param$p[c(1, 5)]), min(param$p[c(2, 6)]), min(param$p[c(3, 7)]), min(param$p[c(4, 8)])),
-                     Belief = y_conf[c(11, 31, 51, 71), "Belief"],
-                     Sex = y_conf[c(11, 32, 51, 72), "Sex"])
+                     y =  y_conf[c(11, 31, 51, 71), "Predicted"],
+                     Sex = y_conf[c(11, 31, 51, 71), "Sex"],
+                     Belief = y_conf[c(11, 31, 51, 71), "Belief"]) |> 
+    arrange(Sex, Belief)
+  param <- parameters::parameters(m_conf, effects = "fixed", keep = var) |> 
+    arrange(Parameter)
+  sig2$p <- c(min(param$p[c(1, 2)]), min(param$p[c(5, 6)]), min(param$p[c(3, 4)]), min(param$p[c(7, 8)]))
+  sig2$y <- sig2$y + ifelse(sig2$Belief == "Real", 0.02, -0.02)
   sig2$label <- ifelse(sig2$p > .05 & sig2$p < .099, format_p(sig2$p), format_p(sig2$p, stars_only = TRUE))
@@
 
-p_ffni3 <- plot_interindividual(m_real, m_conf, var = "FFNI_ThrillSeeking", fill = "#FF5722") + labs(x = "Narcissism (Thrill Seeking)")
-p_ffni3 
+# p_ffni3 <- plot_interindividual(m_real, m_conf, var = "FFNI_ThrillSeeking", fill = "#FF5722") + labs(x = "Narcissism (Thrill Seeking)")
+# p_ffni3 
 ```
@@
 filter(r, BF > 1)
+```
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+cor_test(dfsub, "FFNI_Authoritativeness", "IPIP6_HonestyHumility")
+# cor_test(dfsub, "FFNI_ThrillSeeking", "IPIP6_HonestyHumility")
 ```
@@
 
-p_social <- plot_interindividual(m_real, m_conf, var = "Social_Phobia", fill = "#E040FB") + labs(x = "Social Phobia")
-p_social 
+# p_social <- plot_interindividual(m_real, m_conf, var = "Social_Phobia", fill = "#E040FB") + labs(x = "Social Phobia")
+# p_social 
 ```
@@
   wrap_elements(
-    ((p_ffni1 / p_ipip) | (p_ffni2 / p_social) | (p_ffni3 / p_ai)) + 
+    # ((p_ffni1 / p_ipip) | (p_ffni2 / p_social) | (p_ffni3 / p_ai)) + 
+    ((p_ffni1 / p_ipip) | (p_ffni2 / p_ai)) + 
   plot_layout(guides = "collect") +

### 2022-09-25 analysis2.Rmd
update

--- 2022-09-25 analysis.Rmd
@@
 
-cache <- TRUE
+cache <- FALSE
 runModels <- FALSE
@@
 df <- df |>
-  filter(!Participant %in% outliers)
+  filter(!Participant %in% c(outliers, outliers_partial))
 ```

### 2022-09-25 submission/manuscript.Rmd
update

@@
 
-In the second part of this study, 109 neutral-expression facial images of real individuals from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
+In the second part of this study, 109 pictures of neutral-expression faces from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales.
@@
 
-In the last part of the study, participants were informed that about half of the facial images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
+In the last part of the study, participants were informed that about half of images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 
-103 participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
+One hundred and three participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modeled the probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modeled using beta regressions (suited for outcome variables expressed in percentages).
 
-We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real images of faces) were indeed judged as fake in sufficient proportion to warrant their analysis.
+We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were all images of real faces) were judged as fake in sufficient proportion to warrant their analysis.
 Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).
@@
 Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*.
-We took into account the gender of participants and stimuli by retaining the images of faces that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+We took into account the gender of participants and stimuli by retaining the stimuli that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
@@
 On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the images.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the stimuli.
 
@@
 However, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-Hence, future studies could re-examine this link (or lack thereof) by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items participants are subjected to before making simulation monitoring judgments.
+Future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
 
@@
 <!-- AI attitudes -->
-Despite the ubiquity of AI, the literature pertaining the influence of people's AI attitudes on simulation monitoring is scarce.
+Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
 Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
@@
 However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
-In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency of rating faces as real.
-This association could be put into perspective considering that the stimuli used were images of real faces, and social phobia is characterized as an abnormally extreme fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact].
-Specifically, previous studies have found social phobia to be related to neutral faces being perceived as more threatening [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation].
-Whereas such reports indicate that individuals with greater social anxiety will perceive faces as more salient, hence suggesting that simulation monitoring decisions will be positively related to social phobia, we found opposing evidence that high social phobia scores were associated with increased ratings of faces being fake instead.
-This apparent contradiction could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which people change their mental representations of the realness of a stimulus to manage their own emotional reactions [@sperduti2017distinctive; @sperduti2016paradox].
-As the images of faces could have been perceived very negatively by individuals that are socially anxious, they may have spontaneously applied fictional reappraisal in processing the facial stimuli, thereby leading to an increased tendency to judge them as fake.
-Indeed, this is aligned with a previous study which reported that rates of belief in realness significantly decreased when pictures presented as real were emotional as compared to when they were neutral [@makowski2016phenomenal].
-Given the implication of cognitive control abilities with fictional reappraisal [@hofmann2012executive; @schmeichel2010working], this hypothesis could hence be tested by assessing executive functions in relation to their simulation monitoring decisions in future studies.
+In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
+Social phobia being characterized as a heightened fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact], the nature of the stimuli - pictures of faces - could play a role in this association.
+However, given the fact that neutral faces are perceived as more threatening by participants with high social phobia [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation], and thus likely more salient, we would have expected high social phobia tendencies to be associated with a bias towards reality judgment.
+This apparent contradiction could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
+Moreover, this result is in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
+**TODO: can you double check that this last statement is correct?**.
+Future studies should clarify the role of emotions and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
 
 <!-- Re-exposure Delay -->
-On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real.
+On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, a shorter re-exposure delay was associated with an increased likelihood of judging the faces as real.
 This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].

### 2022-09-25 preprocessing.R

@@ -98,9 +98,10 @@ preprocess_raw <- function(file) {
 
   # Standardize demographics
   # unique(df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Latin", "Hisapanic", "Latino/Hispanic", "Latino", "Latino Hispanic"), "Hispanic", df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Europe", "White", "European/White", "Polish", "White Caucasian"), "Caucasian", df$Ethnicity)
-  df$Ethnicity <- ifelse(df$Ethnicity %in% c("South African Coloured", "Black/African", "Black", "Black ", "Black (African)"), "African", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Latin", "Hisapanic", "Latino/Hispanic", "Latino", "Latino Hispanic", "Latinoamerican", "Latinamerican", "HIspanic", "Hispanic/ Latino", "Latinx"), "Hispanic", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Europe", "White", "European/White", "Polish", "White Caucasian", "White, European", "Albanian"), "Caucasian", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("South African Coloured", "Black/African", "Black", "Black ", "Black (African)", "Black African", "Africa"), "African", df$Ethnicity)
+  df$Ethnicity <- ifelse(df$Ethnicity %in% c("Chinese", "South Asian", "Indian"), "Asian", df$Ethnicity)
   df$Ethnicity <- ifelse(df$Ethnicity %in% c("Mestiza", "Mixed Race", "Mixed Race ", "Coloured/Mixed"), "Mixed", df$Ethnicity)
 
   # unique(df$Nationality)

### 2022-09-27 analysis.Rmd
update

@@
 outliers <- c(
-  # Very short duration for questionnaire in particular + low rating correlations
+  # More than 2 attention check fails
+  "611d03b822d4c8e041ea0c32_m0knb",
+  "5f0f0a2a8b2a480447f31b21_lqgpz",
+  # Very short duration for questionnaire + low rating correlations (< 0.1)
   "5eaef8702b68455d6e130595_ptsga",
-  "5f0f0a2a8b2a480447f31b21_lqgpz",
-  "611d03b822d4c8e041ea0c32_m0knb",
+  "61356174c090b0083f131e01_asm81",
   # Prefered not answering to sexual orientation: further analysis impossible
@@
 outliers_partial <- c(
+  # 1 attention check failed
   "5dc3485219ca0326027ce91f_37ho9",
@@
 
-```{r message=FALSE, warning=FALSE, cache=cache}
+```{r message=FALSE, warning=FALSE, cache=cache, fig.width=20, fig.height=20}
 p_att <- dfsub |>
@@
 df <- df |>
-  filter(!Participant %in% outliers)
+  filter(!Participant %in% c(outliers))
 ```
@@
   sig1$p <- c(min(param[str_detect(param$Parameter, sig1$Sex[1]), "p"]), min(param[str_detect(param$Parameter, sig1$Sex[2]), "p"]))
-  sig1$y <- sig1$y + ifelse(sig1$Sex == "Male", 0.03, -0.03)
+  sig1$y <- sig1$y + ifelse(sig1$Sex == "Male", -0.03, 0.03)
   sig1$label <- ifelse(sig1$p > .05 & sig1$p < .099, format_p(sig1$p), format_p(sig1$p, stars_only = TRUE))
@@
   sig2$p <- c(min(param$p[c(1, 2)]), min(param$p[c(5, 6)]), min(param$p[c(3, 4)]), min(param$p[c(7, 8)]))
-  sig2$y <- sig2$y + ifelse(sig2$Belief == "Real", 0.02, -0.02)
+  sig2$y <- sig2$y + ifelse(sig2$Belief == "Real", 0.03, -0.03)
   sig2$label <- ifelse(sig2$p > .05 & sig2$p < .099, format_p(sig2$p), format_p(sig2$p, stars_only = TRUE))
@@
 
+```{r message=FALSE, warning=FALSE, cache=cache}
+analyze_interindividual <- function(df, questionnaire = "IPIP6_") {
+  param_real <- data.frame()
+  param_conf <- data.frame()
+  for(var in names(select(df, starts_with(questionnaire)))) {
+    m_real <- glmmTMB::glmmTMB(as.formula(paste0("Belief ~ ", var)), 
+                               data=datawizard::standardise(df, select=var), family = "binomial")
+    param_real <- rbind(param_real, parameters::parameters(m_real, effects="fixed")[2, ])
+
+    m_conf <- glmmTMB::glmmTMB(as.formula(paste0("Belief_Confidence ~ Belief / ", var)),
+
+                               data=datawizard::standardise(df, select=var), 
+                             family = glmmTMB::beta_family())
+
+    param_conf <- rbind(param_conf, parameters::parameters(m_conf, effects="fixed")[3:4, ])
+  }
+
+  param_real <- param_real |> 
+    mutate(Parameter = str_remove(Parameter, questionnaire)) |> 
+    select(-SE)
+  param_conf <- param_conf |> 
+    tidyr::separate("Parameter", into = c("Belief", "Dimension"), sep = ":") |> 
+    mutate(Belief = str_remove(Belief, "Belief"),
+           Dimension = str_remove(Dimension, questionnaire)) |> 
+    select(-SE)
+  list(param_real, param_conf)
+}
+```
+
 ### IPIP-6
@@
 
-parameters::parameters(m_real, effects="fixed") |> 
+parameters::parameters(m_real, effects="fixed", exponentiate = TRUE) |> 
   display()

### 2022-09-27 submission/manuscript.Rmd
update results

@@
 This image was removed from further analysis, leaving 108 trials per participant.
-On average, across participants, 44\% of images (95\% CI [0.11, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.89]) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5% for the participants and 8.7% for the stimuli.
+On average, across participants, 44\% of images (95\% CI [0.12, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.84]) as real.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.
 
-There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
+While the delay of re-exposure of the stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay, but only when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)
+
+<!-- There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
 There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).
+-->
 
@@
 
-Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.8%) with the belief that a stimulus was real ($\beta_{poly1} = 16.37$, $95\% CI = [7.76, 24.98]$, $z = 3.73$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.77$, $95\% CI = [1.41, 14.13]$, $z = 2.40$, $p = .017$), with both non-attractive and attractive faces being judged as more real.
-No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real ($\beta_{poly2} = 4.38$, $95\% CI = [0.96, 7.79]$, $z = 2.51$, $p = .012$).
+Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\% CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\% CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
+Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\% CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\% CI = [0.86, 9.60]$, $z = 2.35$, $p = .019$) for females.
+For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92, $, $95\% CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
 There was no interaction with reported self-attractiveness.
 
-Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.5%) with the belief that a stimulus was real ($\beta_{poly1} = 9.54$, $95\% CI = [1.43, 17.65]$, $z = 2.31$, $p = .021$) for males only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 6.61$, $95\% CI = [1.98, 11.24]$, $z = 2.80$, $p = .005$).
+Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.82$, $95\% CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\% CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$).
 There was no interaction with reported self-attractiveness.
 
-Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 3.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.60$, $95\% CI = [4.15, 19.06]$, $z = 3.05$, $p = .002$) for females only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces ($\beta_{poly2} = 6.47$, $95\% CI = [1.73, 11.21]$, $z = 2.68$, $p = .007$).
+Trustworthiness, adjusted for beauty and familiarity, had a predominantly significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for $p\approx .05$ for females only.
+No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence as real or fake than average faces.
 
-We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 3.0%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.31$, $95\% CI = [3.45, 15.17]$, $z = -3.11$, $p = .002$), and a quadratic relationship for faces judged as fake ($\beta_{poly1} = -12.67$, $95\% CI = [-19.87, -5.47]$, $z = -3.45$, $p < .001$; $\beta_{poly2} = 8.14$, $95\% CI = [0.01, 16.28]$, $z = 1.96$, $p = .05$), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are not familiar or highly familiar.
+We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%).
+However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) and a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with more confidence when they are unfamiliar.
 
@@
 
-The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship predominantly with the confidence associated with faces judged as real ($\beta_{real} = -1.69$, $95\% CI = [-2.74, -0.63]$, $z = -3.14$, $p < .01$; $\beta_{fake} = -1.02$, $95\% CI = [-2.07, 0.03]$, $z = -1.90$, $p = 0.058$).
-Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and *Acclaim Seeking* ($\beta_{real} = 2.08$, $95\% CI = [0.79, 3.37]$, $z = 3.16$, $p < .01$; $\beta_{fake} = 1.60$, $95\% CI = [0.30, 2.90]$, $z = 2.42$, $p < .05$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.38$, $95\% CI = [-2.50, -0.27]$, $z = -2.43$, $p < .05$; $\beta_{fake} = -1.23$, $95\% CI = [-2.35, -0.11]$, $z = -2.15$, $p < .05$) and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$).
-Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found.
+The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\% CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\% CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
+For trait narcissism, significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\% CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\% CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
+Confidence judgements also shared links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
+
+Overall social anxiety levels (obtained from aggregating the 2 anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly associated with the confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$).
+Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$).
+In particular, confidence in real judgements was found to share predominantly significant positive links with the *Prospective Anxiety* dimension ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$), although there was a negative association found with the *Inhibitory Anxiety* dimension ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$).
+There was also a largely significant positive relationship between the *Persecutory Ideation* dimension of *Paranoid Beliefs* with the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$) for $p\approx .05$.
+However, the negative relationship between confidence judgements and *Paranoid Beliefs* was only found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
+
+<!-- and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$).     -->
+
+<!--Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found.
 No significant relationships were found for intolerance to uncertainty or paranoid beliefs.
+-->
 
@@
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.29$, $95\% CI = [0.08, 0.50]$, $z = 2.74$, $p < .01$; $\beta_{fake} = 0.38$, $95\% CI = [0.18, 0.59]$, $z = 3.60$, $p < 0.001$).
+Whereas overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
 
@@
 
+<!--TO-DO: Uncertainty Intolerance and Paranoid Thinking -->
+
 <!-- Re-exposure Delay -->

### 2022-09-29 submission/manuscript.Rmd
update more

@@
 As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
+In particular, given the statistical volatility of the findings, which itself could have been a testament to the shifting nature and inter-individuality of our sense of reality, the present study will concentrate on results that provide very strong evidence against the null hypothesis ($p <.01$).
 
@@
 Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\% CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\% CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
-Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\% CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\% CI = [0.86, 9.60]$, $z = 2.35$, $p = .019$) for females.
+Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\% CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\% CI = [0.
+86, 9.60]$, $z = 2.35$, $p = .019$) for females.
 For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92, $, $95\% CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
@@
 
-Trustworthiness, adjusted for beauty and familiarity, had a predominantly significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for $p\approx .05$ for females only.
+Trustworthiness, adjusted for beauty and familiarity, had a predominantly significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
 No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence as real or fake than average faces.
@@
 In particular, confidence in real judgements was found to share predominantly significant positive links with the *Prospective Anxiety* dimension ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$), although there was a negative association found with the *Inhibitory Anxiety* dimension ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$).
-There was also a largely significant positive relationship between the *Persecutory Ideation* dimension of *Paranoid Beliefs* with the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$) for $p\approx .05$.
+There was also a largely significant positive relationship between the *Persecutory Ideation* dimension of *Paranoid Beliefs* with the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
 However, the negative relationship between confidence judgements and *Paranoid Beliefs* was only found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
@@
 The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
+This is further evidenced by the observation that female participants were more confident in their judgement of fake faces when they rated the given stimulus very high or low on beauty.
 
@@
 <!-- trustworthiness -->
-Our results suggested that trustworthiness ratings linearly increased beliefs in realness for females only.
-Given the evidence suggesting that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be present for both genders.
+Our results suggested that trustworthiness ratings linearly increased beliefs in realness for females only (for p-values around .05).
+Given the evidence positing that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be more strongly present for both genders.
 One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
+While this hypothesis seems justified, given that female participants' confidence judgements for both fake and real faces were highest when these faces were rated highly trustworthy and untrustworthy, for the hypothesis to hold true, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-However, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-Future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
+Interestingly, however, there was a significant relationship between familiarity and confidence judegments only for males, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence.
+It is possible that the confidence judgements of females are less malleable, and thus less likely to be influenced by the variability in face familiarity.
+In fact, this observation is consistent with that of @kaplan2012effect, whose study showed female participants exhibited greater metacognitive awareness in a facial recall task.
+However, this has not been corroborated by recent research, which found gender differences in the opposite direction instead (males were significantly overconfident regardless of their performance accuracy and the experimental conditions) [@bailey2021gender; @herbst2020gender].
+Furthermore, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
 
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
-Given the negative correlation between honesty-humility and narcissism [@hodson2018dark], we put this result in perspective with the positive link observed with narcissistic acclaim seeking, confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-However, an inverse effect was found for other facets of narcissism, such as authoritativeness and thrill seeking.
-We interpret the effects of the former as related to a higher response assertiveness and, for thrill-seeking, a tolerance of cognitive uncertainty (note that the intolerance to uncertainty scale, which largely measures the anxiety associated with uncertain events, did not show any link).
-Taken together, these results suggest that participants with low humility, high recognition desires, and high excitement-seeking traits are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
-Participants with opposite traits might perceive a higher risk in the decision process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
+
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher probability of judging the face stimuli as real.
+Indeed, this finding is in line with recent research suggesting that narcissists are less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant of their environment [@carolan2017searching; @grapsas2020and; @eddy2021self].
+For instance, @de2019facial reports that participants with higher scores in narcissism were faster at accurately recognizing faces with neutral and low-intensity emotional expressions.
+This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less thoughtful information-processing, thereby leading to their increased perceptions of the displayed stimulus being real.
+
+Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+However, an inverse effect was found for other facets of narcissism, such as authoritativeness.
+We interpret this correlation as related to a higher response assertiveness.
+Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
+Participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
+
+<!-- for thrill-seeking, a tolerance of cognitive uncertainty (note that the intolerance to uncertainty scale, which largely measures the anxiety associated with uncertain events, did not show any link) -->
 
@@
 Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
-Instead, we found that one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings.
-It is possible that participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
+Instead, we found that having a generally positive attitude towards AI was related to a decrease in confidence in real judgements.
+However, it should be noted that our data analyses found the attitudes towards AI scale was better explained as 3 latent dimensions rather than an aggregated score.
+Indeed, analysing the extracted factors separately revealed that only one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings.
+This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
 This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].
 
-<!-- Social phobia -->
-However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
-In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
+<!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
+Unsurprisingly, individuals with more persecutory ideations (a form of paranoia where one believes they will be harmed by others, @buck2019capturing) were more likely to rate the faces presented as real relative to fake.
+Consistent with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment [@freeman2005psychology], it is likely that people with higher levels of paranoia are more sensitive to social threat and thus perceive the face stimuli presented with greater salience and emotionality, hence increasing their beliefs of its realness [@fornells2015people; @freeman2003can].
+However, higher levels of persecutory ideation, social anxiety and intolerance of uncertainty were related to lower confidence in real judgements.
+While this observation appears contradictory, it could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
+Indeed, previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
+This result is also in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
+As such, given the positive correlation between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia], it is possible that individuals high in such traits have greater interpersonal sensitivity and perceived the ambiguous face images with greater emotional reactivity, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
+
+<!-- In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
 Social phobia being characterized as a heightened fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact], the nature of the stimuli - pictures of faces - could play a role in this association.
 However, given the fact that neutral faces are perceived as more threatening by participants with high social phobia [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation], and thus likely more salient, we would have expected high social phobia tendencies to be associated with a bias towards reality judgment.
-This apparent contradiction could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
-Moreover, this result is in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
-**TODO: can you double check that this last statement is correct?**.
+This apparent contradiction could be explained through the lens of fictional reappraisal,  **TODO: can you double check that this last statement is correct?**.
 Future studies should clarify the role of emotions and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
-
-<!--TO-DO: Uncertainty Intolerance and Paranoid Thinking -->
+-->
+<!-- However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*. -->
 
 <!-- Re-exposure Delay -->
-On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, a shorter re-exposure delay was associated with an increased likelihood of judging the faces as real.
-This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
+On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
+This may be because shorter re-exposure delays led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
+In fact, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
+However, that being the case, we would have expected shorter re-exposure delays to be related to a higher probability of the faces being rated as real.
+As such, future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+
+<!--a shorter re-exposure delay was associated with an increased likelihood of judging the faces as real.
 Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces [@wiese2021familiarity].
-Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
-Future studies could hence further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity [@sperduti2016paradox; @makowski2017being].
+-->
 

### 2022-09-30 submission/manuscript.Rmd
update

@@
 <!-- Ambiguous stimuli and irrelevance of objective features -->
-While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of face generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
-This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
+While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
+Such circumstance, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
@@
 
-One hundred and three participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
+One hundred and fifty participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-We excluded 3 participants that failed 2 (>= 66\%) or more attention check questions.
-The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48\% females, 52\% males).
+We excluded 5 participants that either failed 2 (>= 66\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
+The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3\% females, 51.0\% males, 0.7\% others).
 
@@
 As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
-In particular, given the statistical volatility of the findings, which itself could have been a testament to the shifting nature and inter-individuality of our sense of reality, the present study will concentrate on results that provide very strong evidence against the null hypothesis ($p <.01$).
+In particular, given the statistical volatility of some of the findings, which itself could have been a testament to the shifting nature and inter-individuality of our sense of reality, the present study will concentrate on results that provide very strong evidence against the null hypothesis ($p <.01$).
 
@@
 
-Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials.
+Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 88.7\% of trials.
 This image was removed from further analysis, leaving 108 trials per participant.
@@
 
-While the delay of re-exposure of the stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay, but only when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)
 
@@
 
-Trustworthiness, adjusted for beauty and familiarity, had a predominantly significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
-No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence as real or fake than average faces.
+Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
+No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.
 
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) and a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with more confidence when they are unfamiliar.
+However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
+This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
 
@@
 For trait narcissism, significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\% CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\% CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
-Confidence judgements also shared links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
+Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
 
-Overall social anxiety levels (obtained from aggregating the 2 anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly associated with the confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$).
+The *Paranoid Thinking* dimension of *Persecutory Ideation* was positively related to the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
+However, a negative relationship between confidence judgements and having paranoid beliefs was found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
+Social anxiety levels (obtained from aggregating the 2 social anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly negatively related to confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$).
 Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$).
-In particular, confidence in real judgements was found to share predominantly significant positive links with the *Prospective Anxiety* dimension ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$), although there was a negative association found with the *Inhibitory Anxiety* dimension ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$).
-There was also a largely significant positive relationship between the *Persecutory Ideation* dimension of *Paranoid Beliefs* with the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
-However, the negative relationship between confidence judgements and *Paranoid Beliefs* was only found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
+Specifically, although a negative association was observed between confidence in real judgements and the uncertainty intolerance dimension of *Inhibitory Anxiety* ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$), predominantly positive links were observed with its dimension of *Prospective Anxiety* ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$).
 
@@
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-Whereas overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
+As such, although overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, the extracted latent factor of AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
 
@@
 The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
-This is further evidenced by the observation that female participants were more confident in their judgement of fake faces when they rated the given stimulus very high or low on beauty.
+In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that external beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
 
 <!-- Attractiveness: males -->
-Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
+Alternatively, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
@@
 <!-- trustworthiness -->
-Our results suggested that trustworthiness ratings linearly increased beliefs in realness for females only (for p-values around .05).
-Given the evidence positing that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be more strongly present for both genders.
+Our results found a positive linear trend between trustworthiness and simulation monitoring for females only; suggesting trustworthiness ratings linearly increased their beliefs in realness.
+Given the evidence positing that faces presented as real were rated more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be more clearly present for both genders.
 One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-While this hypothesis seems justified, given that female participants' confidence judgements for both fake and real faces were highest when these faces were rated highly trustworthy and untrustworthy, for the hypothesis to hold true, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
+While this hypothesis justifies much of our findings, particularly considering female participants' confidence judgements for both fake and real faces were also highest when these faces were rated very trustworthy and untrustworthy, for the hypothesis to hold true, faces deemed untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-Interestingly, however, there was a significant relationship between familiarity and confidence judegments only for males, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence.
-It is possible that the confidence judgements of females are less malleable, and thus less likely to be influenced by the variability in face familiarity.
-In fact, this observation is consistent with that of @kaplan2012effect, whose study showed female participants exhibited greater metacognitive awareness in a facial recall task.
+Interestingly, however, there was a significant relationship between familiarity and confidence judgements for males only, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence.
+Previous studies have typically shown females to be superior at face recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect].
+As such, it is possible that the confidence judgements of females are less malleable to variability in face familiarity.
+Indeed, metacognitive awareness has been associated with greater cognitive inflexibility [@mishra2019gender].
 However, this has not been corroborated by recent research, which found gender differences in the opposite direction instead (males were significantly overconfident regardless of their performance accuracy and the experimental conditions) [@bailey2021gender; @herbst2020gender].
-Furthermore, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Furthermore, it is to be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
@@
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher probability of judging the face stimuli as real.
-Indeed, this finding is in line with recent research suggesting that narcissists are less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant of their environment [@carolan2017searching; @grapsas2020and; @eddy2021self].
-For instance, @de2019facial reports that participants with higher scores in narcissism were faster at accurately recognizing faces with neutral and low-intensity emotional expressions.
-This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less thoughtful information-processing, thereby leading to their increased perceptions of the displayed stimulus being real.
+Indeed, this finding is in line with recent research suggesting that narcissists were more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly due to the fact that they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant of their environment [@carolan2017searching; @grapsas2020and; @eddy2021self].
+This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less thoughtful information-processing, leading to their increased perceptions of the displayed stimulus being real.
 
@@
 Instead, we found that having a generally positive attitude towards AI was related to a decrease in confidence in real judgements.
-However, it should be noted that our data analyses found the attitudes towards AI scale was better explained as 3 latent dimensions rather than an aggregated score.
-Indeed, analysing the extracted factors separately revealed that only one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings.
+However, it should be noted that we found attitudes towards AI to be better understood via 3 latent dimensions rather than encompassed within an aggregated score.
+Indeed, examining the extracted factors separately revealed only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
 This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
@@
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
-Unsurprisingly, individuals with more persecutory ideations (a form of paranoia where one believes they will be harmed by others, @buck2019capturing) were more likely to rate the faces presented as real relative to fake.
+Unsurprisingly, individuals with more persecutory ideations (a form of paranoia where one believes others intend to cause them harm, @buck2019capturing) were more likely to rate the faces presented as real relative to fake.
 Consistent with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment [@freeman2005psychology], it is likely that people with higher levels of paranoia are more sensitive to social threat and thus perceive the face stimuli presented with greater salience and emotionality, hence increasing their beliefs of its realness [@fornells2015people; @freeman2003can].
 However, higher levels of persecutory ideation, social anxiety and intolerance of uncertainty were related to lower confidence in real judgements.
-While this observation appears contradictory, it could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
+While such results appear contradictory, it could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
 Indeed, previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
 This result is also in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
-As such, given the positive correlation between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia], it is possible that individuals high in such traits have greater interpersonal sensitivity and perceived the ambiguous face images with greater emotional reactivity, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
+As such, given the positive correlation between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia], it is possible that individuals high in such traits have greater interpersonal sensitivity and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
 

### 2022-10-03 submission/manuscript.Rmd
minor updates

@@
 
-In the second part of this study, 109 pictures of neutral-expression faces from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
+In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales.
@@
 
-In the last part of the study, participants were informed that about half of images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
+In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle].
-As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
-In particular, given the statistical volatility of some of the findings, which itself could have been a testament to the shifting nature and inter-individuality of our sense of reality, the present study will concentrate on results that provide very strong evidence against the null hypothesis ($p <.01$).
+As all the details, scripts and complimentary analyses are open-access, and given that some of the results were statistically volatile, possibly due to the shifting nature and subjectivity of our sense of reality, this manuscript will concentrate on findings that are highly statistically significant ($p <.01$).
 
@@
 
-The *Paranoid Thinking* dimension of *Persecutory Ideation* was positively related to the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
-However, a negative relationship between confidence judgements and having paranoid beliefs was found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
-Social anxiety levels (obtained from aggregating the 2 social anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly negatively related to confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$).
+A negative correlation was found between *Paranoid Thinking* and confidence judgements for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
+Additionally, its dimension of *Persecutory Ideation* was positively related to the belief of the faces being real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
+Alternatively, overall social anxiety levels (obtained from aggregating the 2 social anxiety scales - *SIAS-6* and *SPS-6*) was significantly negatively related to confidence judgements, but only for faces judged as real ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$).
 Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$).
-Specifically, although a negative association was observed between confidence in real judgements and the uncertainty intolerance dimension of *Inhibitory Anxiety* ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$), predominantly positive links were observed with its dimension of *Prospective Anxiety* ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$).
+In contrast, although a negative association was observed between confidence in real judgements and the uncertainty intolerance dimension of *Inhibitory Anxiety* ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$), predominantly positive links were observed with the dimension of *Prospective Anxiety* ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$).
 
@@
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-As such, although overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, the extracted latent factor of AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
+As such, although overall attitudes towards AI was significantly and negatively associated with the judgement confidence for real faces ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, the extracted factor of AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
 
@@
 The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding is a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+This finding could thus be seen as a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
@@
 <!-- Attractiveness: males -->
-Alternatively, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
+Alternatively, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
@@
 One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-While this hypothesis justifies much of our findings, particularly considering female participants' confidence judgements for both fake and real faces were also highest when these faces were rated very trustworthy and untrustworthy, for the hypothesis to hold true, faces deemed untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
+While this hypothesis justifies much of our findings, particularly considering female participants' confidence judgements for both fake and real faces were also higher when these faces were rated very trustworthy and untrustworthy, for the hypothesis to hold true, faces deemed untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-Interestingly, however, there was a significant relationship between familiarity and confidence judgements for males only, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence.
-Previous studies have typically shown females to be superior at face recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect].
-As such, it is possible that the confidence judgements of females are less malleable to variability in face familiarity.
-Indeed, metacognitive awareness has been associated with greater cognitive inflexibility [@mishra2019gender].
-However, this has not been corroborated by recent research, which found gender differences in the opposite direction instead (males were significantly overconfident regardless of their performance accuracy and the experimental conditions) [@bailey2021gender; @herbst2020gender].
-Furthermore, it is to be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Interestingly, there was a significant relationship between familiarity and confidence judgements for males only, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence.
+However, taking into perspective that previous studies report females to be superior at face recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect], it is possible that the confidence judgements of females are less malleable to variability in face familiarity.
+Indeed, metacognitive awareness has been associated with overconfidence in making judgements [@mata2013metacognitive; @klein2018metacognitive].
+However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident regardless of their performance accuracy and the experimental conditions [@bailey2021gender; @herbst2020gender].
+Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
-
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher probability of judging the face stimuli as real.
-Indeed, this finding is in line with recent research suggesting that narcissists were more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly due to the fact that they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant of their environment [@carolan2017searching; @grapsas2020and; @eddy2021self].
-This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less thoughtful information-processing, leading to their increased perceptions of the displayed stimulus being real.
+Indeed, this finding is in line with recent research suggesting that narcissists were more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly due to the fact that they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
+This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytic-processing, leading to their increased perceptions of the displayed stimulus being real.
 
@@
 However, higher levels of persecutory ideation, social anxiety and intolerance of uncertainty were related to lower confidence in real judgements.
-While such results appear contradictory, it could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
-Indeed, previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
-This result is also in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
-As such, given the positive correlation between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia], it is possible that individuals high in such traits have greater interpersonal sensitivity and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
+While these results appear contradictory, such findings could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
+Previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
+This result is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
+As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
 
+<!-- given the known positive correlations between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia] -->
 <!-- In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
@@
 In fact, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
-However, that being the case, we would have expected shorter re-exposure delays to be related to a higher probability of the faces being rated as real.
+However, that being the case, we would have expected shorter re-exposure delays to be related to a greater belief of the faces being real.
 As such, future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
@@
 In conclusion, research on our ability to discriminate between what is real from what is not is increasingly relevant given the current expansion on technologies related to virtual and augmented realities.
-The aim of the present study was to examine whether facial attractiveness can significantly influence our simulation monitoring decisions.
+The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions.
 In line with our hypothesis, we found faces rated as attractive and unattractive to be perceived as more real for females as a result of an increased salience.
 However, for males, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized.
-As such, future studies could further investigate the role of attractiveness in simulation monitoring, taking greater consideration of the former's multidimensionality.
+As such, future studies could take greater consideration of the multidimensionality of facial attractiveness in investigating its role in simulation monitoring decisions.
 

### 2022-10-06 submission/manuscript.Rmd
results

@@
 <!-- Ambiguous stimuli and irrelevance of objective features -->
-While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022].
-Such circumstance, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
+While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
+Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
@@
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult [@berghel2018weaponizing; @chen2015news].
-In the absence of contextual information, what drives our beliefs of reality?
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has been an information published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
+In the absence of clear contextual information, what drives our beliefs of reality?
 
@@
 <!-- Internal features -->
-Moreover, evidence from research indicates that inter-individual characteristics also play a crucial role in the formation of beliefs of reality, with factors such as cognitive style, prior beliefs, and personality traits significantly impacting simulation monitoring [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
-For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy].
-Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with our expectations [@britt2019reasoned].
+Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
+For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy], and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations [@britt2019reasoned].
 Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
@@
 In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated  with greater belief [@martel2020reliance; @bago2022emotion].
-Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in our processing and reaction to real as opposed to non-real material.
+Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in guiding our appraisal of a stimulus.
 
 <!-- Attractiveness -->
-AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
-Interestingly, some studies report that when the nature of the faces was ambiguous, artificially created faces that were previously rated as more attractive were judged by subjects to be less real [@tucciarelli2020].
-However, as the attractiveness ratings were given by independent raters instead of the participants, the direction of the relationship between perceived realness and attractiveness cannot be concluded.
-To this end, @liefooghe2022faces reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question, whether attractiveness could drive simulation monitoring, has received little attention to date.
+AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
+Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were as less real [@tucciarelli2020].
+**Converserly, [or in line with that]**, @liefooghe2022faces reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge [**TODO: in what direction?**.
+Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
 
@@
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
-Additionally, we will further explore the link of dispositional traits, such as personality and attitude towards AI, with inter-individual simulation monitoring tendencies.
-Note that the discriminative accuracy between "true" photos and "true" artificially-generated images is not relevant for this study, which focuses on the beliefs that a stimulus is real or fake, independently of its true nature.
+Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
+This study aims beyond the investigation of the discriminative accuracy between "true" photos and "true" artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modeled the probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modeled using beta regressions (suited for outcome variables expressed in percentages).
+The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modelled the probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using beta regressions (suited for outcome variables expressed in percentages).
 
@@
 
-The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**).
+The determinants of reality beliefs were modelled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**).
 Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*.
@@
 The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle].
-As all the details, scripts and complimentary analyses are open-access, and given that some of the results were statistically volatile, possibly due to the shifting nature and subjectivity of our sense of reality, this manuscript will concentrate on findings that are highly statistically significant ($p <.01$).
+As all the details, scripts and complimentary analyses are open-access, we will focus in hte manuscript on findings that are highly statistically significant ($p <.01$).
 
@@
 
-Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 88.7\% of trials.
+Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake by 88.7\% of participants.
 This image was removed from further analysis, leaving 108 trials per participant.
-On average, across participants, 44\% of images (95\% CI [0.12, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.84]) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.
+On average, across participants, 44\% of images (95\%~CI [0.12, 0.64]) were judged as fake and 56\% of images (95\%~CI [0.36, 0.84]) as real.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0\% for the participants and 9.6\% for the stimuli.
 
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$)
 
-<!-- There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
-There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).
+<!-- There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\%~CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
+There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\%~CI = [-0.1, 0.0]$, $p = .023$).
 -->
@@
 
-Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\% CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\% CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
-Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\% CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\% CI = [0.
+Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0\%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
+Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\%~CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\%~CI = [0.
 86, 9.60]$, $z = 2.35$, $p = .019$) for females.
-For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92, $, $95\% CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
+For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92, $, $95\%~CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
 There was no interaction with reported self-attractiveness.
 
-Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.82$, $95\% CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\% CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$).
+Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.82$, $95\%~CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\%~CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$).
 There was no interaction with reported self-attractiveness.
 
-Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
-No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.
+Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\%~CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
+No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\%~CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\%~CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.
 
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%).
-However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
+However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
 This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
@@
 
-The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\% CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\% CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
-For trait narcissism, significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\% CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\% CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
-Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
+The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\%~CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\%~CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
 
-A negative correlation was found between *Paranoid Thinking* and confidence judgements for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
-Additionally, its dimension of *Persecutory Ideation* was positively related to the belief of the faces being real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
-Alternatively, overall social anxiety levels (obtained from aggregating the 2 social anxiety scales - *SIAS-6* and *SPS-6*) was significantly negatively related to confidence judgements, but only for faces judged as real ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$).
-Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$).
-In contrast, although a negative association was observed between confidence in real judgements and the uncertainty intolerance dimension of *Inhibitory Anxiety* ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$), predominantly positive links were observed with the dimension of *Prospective Anxiety* ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$).
+Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\%~CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\%~CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
+Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
 
-<!-- and *Thrill Seeking* ($\beta_{real} = -0.93$, $95\% CI = [-1.75, -0.10]$, $z = -2.20$, $p < .05$; $\beta_{fake} = -1.03$, $95\% CI = [-1.87, -0.20]$, $z = -2.44$, $p < .05$).     -->
+A negative relationship was found between *Paranoid Thinking* and confidence judgements for faces judged as real ($\beta_{real} = -0.21$, $95\%~CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
 
-<!--Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake ($\beta = -0.97$, $95\% CI = [-1.86, -0.08]$, $z = -2.14$, $p < .05$), but no effect on the confidence judgments was found.
-No significant relationships were found for intolerance to uncertainty or paranoid beliefs.
--->
-
-<!-- Bayesian correlations with personality traits suggested that Honesty-Humility was negatively associated with the confidence in reality ($r = -0.21$, $95\% CI = [-0.38, -0.03]$, $BF_{10} = 3.57$), and positively associated with the Narcissism trait of Acclaim Seeking ($r = 0.26$, $95\% CI = [0.08, 0.43]$, $BF_{10} = 14.38$) and Grandiose Fantasies ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.18$).
-Acclaim Seeking was also positively related with the confidence in fake judgments ($r = 0.22$, $95\% CI = [0.04, 0.40]$, $BF_{10} = 4.52$).
-No significant correlations was found for social anxiety, intolerance to uncertainty, or paranoid beliefs.
--->
+The *Prospective Anxiety* aspect of intolerance to uncertainty shared a negative trend in its associatin with confidence ratings ($\beta_{real} = 1.43$, $95\%~CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$; $\beta_{fake} = -0.91$, $95\%~CI = [-1.93, 0.11]$, $z = -1.75$, $p = .081$).
+No significant effect was found for social anxiety.
 
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-As such, although overall attitudes towards AI was significantly and negatively associated with the judgement confidence for real faces ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, the extracted factor of AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
-
-<!-- Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real ($r = 0.24$, $95\% CI = [0.06, 0.41]$, $BF_{10} = 8.00$) and fake ($r = 0.28$, $95\% CI = [0.11, 0.44]$, $BF_{10} = 23.04$) judgments.
--->
+Only AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
 

### 2022-10-06 submission/manuscript.Rmd
update discussion

@@
 AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
-Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were as less real [@tucciarelli2020].
-**Converserly, [or in line with that]**, @liefooghe2022faces reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge [**TODO: in what direction?**.
+Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real [@tucciarelli2020].
+Conversely, @liefooghe2022faces reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
 Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
@@
 The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle].
-As all the details, scripts and complimentary analyses are open-access, we will focus in hte manuscript on findings that are highly statistically significant ($p <.01$).
+As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant ($p <.01$).
 
@@
 
-A negative relationship was found between *Paranoid Thinking* and confidence judgements for faces judged as real ($\beta_{real} = -0.21$, $95\%~CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).
+A positive trend was found in the relationship between the *Persecutory Ideation* dimension of paranoid thinking and the belief that the faces were real ($\beta = 1.87$, $95\%~CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
 
-The *Prospective Anxiety* aspect of intolerance to uncertainty shared a negative trend in its associatin with confidence ratings ($\beta_{real} = 1.43$, $95\%~CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$; $\beta_{fake} = -0.91$, $95\%~CI = [-1.93, 0.11]$, $z = -1.75$, $p = .081$).
+The *Prospective Anxiety* aspect of intolerance to uncertainty shared a negative trend in its association with confidence ratings ($\beta_{real} = 1.43$, $95\%~CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$; $\beta_{fake} = -0.91$, $95\%~CI = [-1.93, 0.11]$, $z = -1.75$, $p = .081$).
 No significant effect was found for social anxiety.
@@
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-Only AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
+However,  only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
 
@@
 The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
-In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that external beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
+In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
 
 <!-- Attractiveness: males -->
-Alternatively, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
+Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
-However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].
+However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces for males, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].
 
@@
 <!-- trustworthiness -->
-Our results found a positive linear trend between trustworthiness and simulation monitoring for females only; suggesting trustworthiness ratings linearly increased their beliefs in realness.
-Given the evidence positing that faces presented as real were rated more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be more clearly present for both genders.
+Our results found a positive linear trend between trustworthiness and simulation monitoring for females only; suggesting trustworthiness ratings increased their beliefs in realness.
+Given prior evidence that faces presented as computer-generated were rated less trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a linear association to be more clearly present for both genders.
 One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-While this hypothesis justifies much of our findings, particularly considering female participants' confidence judgements for both fake and real faces were also higher when these faces were rated very trustworthy and untrustworthy, for the hypothesis to hold true, faces deemed untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
+However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
 As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-Interestingly, there was a significant relationship between familiarity and confidence judgements for males only, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence.
-However, taking into perspective that previous studies report females to be superior at face recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect], it is possible that the confidence judgements of females are less malleable to variability in face familiarity.
+Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where highly familiar faces were rated as real and unfamiliar faces as fake with greater confidence.
+This could be taken into perspective with previous studies, which report females to be relatively superior at face recall and recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect].
+Hence, it is possible that the confidence in evaluating faces are less malleable to external factors such as face familiarity for females.
 Indeed, metacognitive awareness has been associated with overconfidence in making judgements [@mata2013metacognitive; @klein2018metacognitive].
-However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident regardless of their performance accuracy and the experimental conditions [@bailey2021gender; @herbst2020gender].
+However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident in face recall, regardless of their performance accuracy [@bailey2021gender; @herbst2020gender].
 Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher probability of judging the face stimuli as real.
-Indeed, this finding is in line with recent research suggesting that narcissists were more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly due to the fact that they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
-This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytic-processing, leading to their increased perceptions of the displayed stimulus being real.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a greater belief that the faces presented were real.
+Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly because they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant when attending to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
+As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
 
 Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-However, an inverse effect was found for other facets of narcissism, such as authoritativeness.
-We interpret this correlation as related to a higher response assertiveness.
+Although an inverse effect was found for the authoritativeness facet of narcissism, we interpret this correlation as related to a higher response assertiveness.
 Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
@@
 Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
-Instead, we found that having a generally positive attitude towards AI was related to a decrease in confidence in real judgements.
-However, it should be noted that we found attitudes towards AI to be better understood via 3 latent dimensions rather than encompassed within an aggregated score.
-Indeed, examining the extracted factors separately revealed only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
+Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
 This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
@@
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
-Unsurprisingly, individuals with more persecutory ideations (a form of paranoia where one believes others intend to cause them harm, @buck2019capturing) were more likely to rate the faces presented as real relative to fake.
-Consistent with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment [@freeman2005psychology], it is likely that people with higher levels of paranoia are more sensitive to social threat and thus perceive the face stimuli presented with greater salience and emotionality, hence increasing their beliefs of its realness [@fornells2015people; @freeman2003can].
-However, higher levels of persecutory ideation, social anxiety and intolerance of uncertainty were related to lower confidence in real judgements.
-While these results appear contradictory, such findings could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
-Previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
-This result is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
-As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
+Unsurprisingly, we found that individuals with more persecutory ideations (a form of paranoia where one believes others intend to cause them harm, @buck2019capturing) tend to rate the faces presented as real relative to fake.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that people with more persecutory ideations perceived the faces with greater salience and emotionality, hence increasing their beliefs of its realness.
+Indeed, this is in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
+
+In contrast, however, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
+This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
+While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
+In fact, previous studies report that individuals with greater paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
+This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
+As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that attenuated their confidence in real judgements.
+Future studies should clarify the role of emotions, particularly those related to anxiety, and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
 
@@
 This apparent contradiction could be explained through the lens of fictional reappraisal,  **TODO: can you double check that this last statement is correct?**.
-Future studies should clarify the role of emotions and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
 -->
@@
 This may be because shorter re-exposure delays led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
-In fact, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
-However, that being the case, we would have expected shorter re-exposure delays to be related to a greater belief of the faces being real.
-As such, future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+Indeed, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
+However, that being the case, we expect shorter re-exposure delays to be significantly related to a greater belief of the faces being real.
+Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
 
@@
 
-In conclusion, research on our ability to discriminate between what is real from what is not is increasingly relevant given the current expansion on technologies related to virtual and augmented realities.
+In conclusion, research on our ability to discriminate between what is real from what is not is increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.
 The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions.
 In line with our hypothesis, we found faces rated as attractive and unattractive to be perceived as more real for females as a result of an increased salience.
-However, for males, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized.
+In contrast, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized for males.
 As such, future studies could take greater consideration of the multidimensionality of facial attractiveness in investigating its role in simulation monitoring decisions.
+Furthermore, it is important to note that besides the traits of narcissistic acclaim-seeking and manipulativeness, and the persecutory ideation dimension of paranoid thinking, all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
+Hence, future studies could expand upon the present study to further investigate the types of and degree to which different inter-individual variables influence our beliefs of reality.
 

### 2022-10-07 submission/manuscript.Rmd
update

@@
 
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$)
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\%~CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$)
 
@@
 Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0\%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
-Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30, $, $95\%~CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23, $, $95\%~CI = [0.
+Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30$, $95\%~CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23$, $95\%~CI = [0.
 86, 9.60]$, $z = 2.35$, $p = .019$) for females.
-For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92, $, $95\%~CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
+For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92$, $95\%~CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
 There was no interaction with reported self-attractiveness.
@@
 
-This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that the stimulus is artificially generated.
-The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding could thus be seen as a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that a stimulus was artificially generated.
+The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
+This finding can be seen as a testimony not only to the effectiveness of our instructions, nut also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
-In fact, stimuli-related and participant-related characteristics accounted for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
+In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
 
@@
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
-However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces for males, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].
+It is thus possible that the evolutionary weight associated with attractiveness skewed men's perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring.
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [e.g., heart rate deceleration, @skora2022functional].
 
@@
 <!-- trustworthiness -->
-Our results found a positive linear trend between trustworthiness and simulation monitoring for females only; suggesting trustworthiness ratings increased their beliefs in realness.
+Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
 Given prior evidence that faces presented as computer-generated were rated less trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a linear association to be more clearly present for both genders.
-One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
 However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
-As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
+Further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
 
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where highly familiar faces were rated as real and unfamiliar faces as fake with greater confidence.
+Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
 This could be taken into perspective with previous studies, which report females to be relatively superior at face recall and recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect].
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a greater belief that the faces presented were real.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were found to be associated with a higher number of faces judged as real.
 Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly because they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant when attending to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
@@
 Participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
-
-<!-- for thrill-seeking, a tolerance of cognitive uncertainty (note that the intolerance to uncertainty scale, which largely measures the anxiety associated with uncertain events, did not show any link) -->
 
@@
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
-Unsurprisingly, we found that individuals with more persecutory ideations (a form of paranoia where one believes others intend to cause them harm, @buck2019capturing) tend to rate the faces presented as real relative to fake.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that people with more persecutory ideations perceived the faces with greater salience and emotionality, hence increasing their beliefs of its realness.
-Indeed, this is in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
+Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
 
-In contrast, however, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
+In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
 This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
-While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
+**WHY IS THIS CONTRADICTORY?
+the next part seems to be about emotion regulation.
+While interesting, it's a bit of a non-sequitur no?
+And the previous explanation could almost be enough.** While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
 In fact, previous studies report that individuals with greater paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
-This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal].
+This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2019phenomenal].
 As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that attenuated their confidence in real judgements.
@@
 Indeed, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
-However, that being the case, we expect shorter re-exposure delays to be significantly related to a greater belief of the faces being real.
+If that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
 Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
 
-<!--a shorter re-exposure delay was associated with an increased likelihood of judging the faces as real.
-Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces [@wiese2021familiarity].
-Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity [@sperduti2016paradox; @makowski2017being].
--->
-
-In conclusion, research on our ability to discriminate between what is real from what is not is increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.
+<!-- Conclusion -->
+In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.
 The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions.
-In line with our hypothesis, we found faces rated as attractive and unattractive to be perceived as more real for females as a result of an increased salience.
-In contrast, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized for males.
-As such, future studies could take greater consideration of the multidimensionality of facial attractiveness in investigating its role in simulation monitoring decisions.
-Furthermore, it is important to note that besides the traits of narcissistic acclaim-seeking and manipulativeness, and the persecutory ideation dimension of paranoid thinking, all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*.
-Hence, future studies could expand upon the present study to further investigate the types of and degree to which different inter-individual variables influence our beliefs of reality.
+We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
+We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
+Limitations include [**TO ADD**].
 

### 2022-10-07 submission/manuscript.tex
update

@@
 These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
-Such developments not only carries important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
+Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
 This issue is central to what has been coined the ``post-truth era'' (Lewandowsky et al., 2017), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
 
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of face generation and replacement (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
-This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
+Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (Makowski, 2018; a process henceforth referred to as \emph{simulation monitoring}, Makowski, Sperduti, et al., 2019).
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus, and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) can render this task difficult (Berghel, 2018; Y.
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has been an information published), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
 Chen et al., 2015).
-In the absence of contextual information, what drives our beliefs of reality?
+In the absence of clear contextual information, what drives our beliefs of reality?
 
@@
 
-Moreover, evidence from research indicates that inter-individual characteristics also play a crucial role in the formation of beliefs of reality, with factors such as cognitive style, prior beliefs, and personality traits significantly impacting simulation monitoring (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
-For instance, individuals with higher levels of analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019).
-Prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with our expectations (Britt et al., 2019).
+Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
+For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019), and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations (Britt et al., 2019).
 Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
@@
 In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
-Additionally, other factors, such as the stimuli's perceived self-relevance (T.
-R.
-Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in our processing and reaction to real as opposed to non-real material.
+Additionally, other factors, such as the stimuli's perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in guiding our appraisal of a stimulus.
 
-AI-generated images of faces, due to their popularity as a target of CGI technology and the possibility of experimentally manipulating facial features, are increasingly used to study face processing as related to saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
-Interestingly, some studies report that when the nature of the faces was ambiguous, artificially created faces that were previously rated as more attractive were judged by subjects to be less real (Tucciarelli et al., 2020).
-However, as the attractiveness ratings were given by independent raters instead of the participants, the direction of the relationship between perceived realness and attractiveness cannot be concluded.
-To this end, Liefooghe et al.
-(2022) reports that attractiveness ratings differed significantly between participants who were told that the faces were AI-generated from those who had no prior knowledge.
-Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question, whether attractiveness could drive simulation monitoring, has received little attention to date.
+AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
+Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real (Tucciarelli et al., 2020).
+Conversely, Liefooghe et al.
+(2022) reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
+Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
 
@@
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
-Additionally, we will further explore the link of dispositional traits, such as personality and attitude towards AI, with inter-individual simulation monitoring tendencies.
-Note that the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images is not relevant for this study, which focuses on the beliefs that a stimulus is real or fake, independently of its true nature.
+Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
+This study aims beyond the investigation of the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011) measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012) assessing social anxiety levels, the \emph{FFNI-BF} (30 items, Jauk et al., 2022) measuring 9 facets of narcissism; the \emph{R-GPTS} (18 items, Freeman et al., 2021) measuring 2 dimensions related to paranoid thinking; and the \emph{IUS-12} (12 items, Carleton et al., 2007) measuring intolerance to uncertainty.
-Finally, we devised 5 items pertaining to expectations about AI-generated images technology (``I think current Artificial Intelligence algorithms can generate very realistic images'').
+Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness (``How attractive would you say you are?'', Marcinkowska et al.
+(2021)) and the other measuring physical attractiveness (``How would you rate your own physical attractiveness relative to the average'', Spielmann et al.
+(2020)).
+Finally, we devised 5 items pertaining to expectations about AI-generated image technology (``I think current Artificial Intelligence algorithms can generate very realistic images'').
 To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale (\emph{GAAIS}, Schepman \& Rodway, 2020).
-This scale was presented after the social anxiety questionnaires, and 3 attention check questions were embedded in the surveys.
+This scale was presented after the social anxiety questionnaires.
+3 attention check questions were also embedded in the surveys.
 
-In the second part of this study, 109 photos of neutral-expression faces of real individuals from the validated American Multiracial Face Database (AMFD, (J.
+In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database (AMFD, (J.
 M.
-Chen et al., 2021)) were presented to the participants for 50 0ms each, in a randomized order, following a fixation cross display (750 ms).
+Chen et al., 2021)) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of \emph{Trustworthiness} (``I find this person trustworthy'') and \emph{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we assessed attractiveness using 2 scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we assessed attractiveness using 2 visual analog scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
 
-In the last part of the study, participants were informed that about half of the face images previously seen were AI-generated (the instructions used a cover story mentioning that the research was aimed at validating a new face generation algorithm).
+In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 
-One hundred and three participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data (Peer et al., 2022).
+One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data (Peer et al., 2022).
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-We excluded 3 participants that failed 2 (\textgreater= 66\%) or more attention check questions.
-The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: {[}19, 66{]}; Sex: 48\% females, 52\% males).
+We excluded 5 participants that either failed 2 (\textgreater= 66\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
+The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: {[}19, 66{]}; Sex: 48.3\% females, 51.0\% males, 0.7\% others).
 
@@
 The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, derived based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which models probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity) was modeled using beta regression models (suited for outcome variables expressed in percentages).
+The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modelled the probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using beta regressions (suited for outcome variables expressed in percentages).
 
-We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were real pictures of faces) were indeed judged as fake in a sufficient proportion to warrant their analysis.
+We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were all images of real faces) were judged as fake in sufficient proportion to warrant their analysis.
 Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).
 
-The determinants of reality beliefs were modeled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (\textbf{Figure 2}.
+The determinants of reality beliefs were modelled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (\textbf{Figure 2}).
 Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables \emph{mutatis mutandis}.
-We took into account the gender of participants and stimuli by retaining the pictures that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+We took into account the gender of participants and stimuli by retaining the stimuli that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
@@
 The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski et al., 2020; Makowski, Ben-Shachar, et al., 2019).
-As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results.
+As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant (\(p <.01\)).
 
@@
 
-Only one image file yielded a strong simulation monitoring bias (\textgreater{} 85\%), being classified as fake in 87.4\% of trials.
+Only one image file yielded a strong simulation monitoring bias (\textgreater{} 85\%), being classified as fake by 88.7\% of participants.
 This image was removed from further analysis, leaving 108 trials per participant.
-On average, across participants, 44\% of images (95\% CI {[}0.11, 0.64{]}) were judged as fake and 56\% of images (95\% CI {[}0.36, 0.89{]}) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 10.5\% for the participants and 8.7\% for the pictures.
+On average, across participants, 44\% of images (95\%\textasciitilde CI {[}0.12, 0.64{]}) were judged as fake and 56\% of images (95\%\textasciitilde CI {[}0.36, 0.84{]}) as real.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0\% for the participants and 9.6\% for the stimuli.
 
-There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min (\(OR = 0.99\), \(95\% CI = [0.99, 1.00]\), \(z = -2.27\), \(p = .023\)).
-There was also a significant negative effect on judgment confidence, but only in the real condition (\(\beta = -0.005\), \(95\% CI = [-0.1, 0.0]\), \(p = .023\)).
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality (\(OR = 1.00\), \(95\%~CI = [0.99, 1.00]\) ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real (\(\beta = -0.006\), \(95\%~CI = [-0.1, 0.002]\), \(p = .004\))
 
@@
 
-Attractiveness had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.8\%) with the belief that a stimulus was real (\(\beta_{poly1} = 16.37\), \(95\% CI = [7.76, 24.98]\), \(z = 3.73\), \(p < .001\)) for males, and a quadratic relationship for females (\(\beta_{poly2} = 7.77\), \(95\% CI = [1.41, 14.13]\), \(z = 2.40\), \(p = .017\)), with both non-attractive and attractive faces being judged as more real.
-No significant relationship was found between attractiveness ratings and belief confidence, aside of a similar trend for females only, for faces judged as real (\(\beta_{poly2} = 4.38\), \(95\% CI = [0.96, 7.79]\), \(z = 2.51\), \(p = .012\)).
+Attractiveness had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 16.57\), \(95\%~CI = [7.33, 25.82]\), \(z = 3.51\), \(p < .001\)) for males, and a quadratic relationship for females (\(\beta_{poly2} = 7.82\), \(95\%~CI = [1.81, 13.84]\), \(z = 2.55\), \(p = .011\)), with both non-attractive and attractive faces being judged as more real.
+Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real (\(\beta_{poly2} = 4.30\), \(95\%~CI = [0.97, 7.64]\), \(z = 2.53\), \(p = .011\)) and as fake (\(\beta_{poly2} = 5.23\), \(95\%~CI = [0.
+86, 9.60]\), \(z = 2.35\), \(p = .019\)) for females.
+For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake (\(\beta_{poly2} = -9.92\), \(95\%~CI = [-18.99, -0.86]\), \(z = -2.15\), \(p = .032\)).
 There was no interaction with reported self-attractiveness.
 
-Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 3.5\%) with the belief that a stimulus was real (\(\beta_{poly1} = 9.54\), \(95\% CI = [1.43, 17.65]\), \(z = 2.31\), \(p = .021\)) for males only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces (\(\beta_{poly2} = 6.61\), \(95\% CI = [1.98, 11.24]\), \(z = 2.80\), \(p = .005\)).
+Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 11.82\), \(95\%~CI = [4.28, 20.21]\), \(z = 2.76\), \(p = .006\)) for males only.
+No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces (\(\beta_{poly2} = 7.84\), \(95\%~CI = [3.39, 12.29]\), \(z = 3.46\), \(p < .001\)).
 There was no interaction with reported self-attractiveness.
 
-Trustworthiness, adjusted for beauty and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 3.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 11.60\), \(95\% CI = [4.15, 19.06]\), \(z = 3.05\), \(p = .002\)) for females only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as real, suggesting that non-trustworthy and highly trustworthy faces were rated as real with more confidence than average faces (\(\beta_{poly2} = 6.47\), \(95\% CI = [1.73, 11.21]\), \(z = 2.68\), \(p = .007\)).
+Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 6.44\), \(95\%~CI = [-0.11, 13.00]\), \(z = 1.93\), \(p = .0054\)) for females only.
+No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real (\(\beta_{poly2} = 6.14\), \(95\%~CI = [2.13, 10.14]\), \(z = 3.00\), \(p = .003\)) as well as fake (\(\beta_{poly2} =6.12\), \(95\%~CI = [1.49, 10.75]\), \(z = 2.59\), \(p = .001\)), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.
 
-We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness (\(R^2_{marginal}\) = 3.0\%).
-However, a significant positive and linear relationship was found with the confidence in faces judged as real (\(\beta_{poly1} = 9.31\), \(95\% CI = [3.45, 15.17]\), \(z = -3.11\), \(p = .002\)), and a quadratic relationship for faces judged as fake (\(\beta_{poly1} = -12.67\), \(95\% CI = [-19.87, -5.47]\), \(z = -3.45\), \(p < .001\); \(\beta_{poly2} = 8.14\), \(95\% CI = [0.01, 16.28]\), \(z = 1.96\), \(p = .05\)), for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with less confidence when they are of not familiar or highly familiar.
+We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness (\(R^2_{marginal}\) = 2.0\%).
+However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real (\(\beta_{poly1} = 9.98\), \(95\%~CI = [3.83, 16.13]\), \(z = 3.18\), \(p = .001\)) whereas a negative linear relationship was found with those judged as fake (\(\beta_{poly1} = -12.41\), \(95\%~CI = [-20.27, -4.54]\), \(z = -3.09\), \(p = .002\)) for males only.
+This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
 
@@
 
-The models including the personality traits suggested that \emph{Honesty-Humility} had a significant negative relationship predominantly with the confidence associated with faces judged as real (\(\beta_{real} = -1.69\), \(95\% CI = [-2.74, -0.63]\), \(z = -3.14\), \(p < .01\); \(\beta_{fake} = -1.02\), \(95\% CI = [-2.07, 0.03]\), \(z = -1.90\), \(p = 0.058\)).
-Narcissism shared significant links through various dimensions, such as positive relationship between the confidence for both real and fake judgments and \emph{Acclaim Seeking} (\(\beta_{real} = 2.08\), \(95\% CI = [0.79, 3.37]\), \(z = 3.16\), \(p < .01\); \(\beta_{fake} = 1.60\), \(95\% CI = [0.30, 2.90]\), \(z = 2.42\), \(p < .05\)), and a negative relationship with \emph{Authoritativeness} (\(\beta_{real} = -1.38\), \(95\% CI = [-2.50, -0.27]\), \(z = -2.43\), \(p < .05\); \(\beta_{fake} = -1.23\), \(95\% CI = [-2.35, -0.11]\), \(z = -2.15\), \(p < .05\)) and \emph{Thrill Seeking} (\(\beta_{real} = -0.93\), \(95\% CI = [-1.75, -0.10]\), \(z = -2.20\), \(p < .05\); \(\beta_{fake} = -1.03\), \(95\% CI = [-1.87, -0.20]\), \(z = -2.44\), \(p < .05\)).
-Finally, the social phobia dimension was significantly associated with a decreased probability of judging faces as fake (\(\beta = -0.97\), \(95\% CI = [-1.86, -0.08]\), \(z = -2.14\), \(p < .05\)), but no effect on the confidence judgments was found.
-No significant relationships was found for intolerance to uncertainty or paranoid beliefs.
+The models including the personality traits suggested that \emph{Honesty-Humility} had a significant negative relationship with the confidence associated with real as well as fake judgements (\(\beta_{real} = -1.62\), \(95\%~CI = [-2.55, -0.70]\), \(z = -3.43\), \(p < .001\); \(\beta_{fake} = -1.16\), \(95\%~CI = [-2.09, -0.23]\), \(z = -2.45\), \(p = 0.014\)).
+
+Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as \emph{Acclaim Seeking} (\(\beta = 2.24\), \(95\%~CI = [1.17, 4.27]\), \(z = 2.44\), \(p = .015\)), and \emph{Manipulativeness} (\(\beta = 0.47\), \(95\%~CI = [0.25, 0.87]\), \(z = -2.4\), \(p = 0.017\)).
+Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with \emph{Acclaim Seeking} (\(\beta_{real} = 1.65\), \(95\%~CI = [0.59, 2.70]\), \(z = 3.07\), \(p =.002\); \(\beta_{fake} = 1.62\), \(95\%~CI = [0.56, 2.68]\), \(z = 3.00\), \(p = .003\)), and a negative relationship with \emph{Authoritativeness} (\(\beta_{real} = -1.57\), \(95\%~CI = [-2.58, -0.57]\), \(z = -3.08\), \(p = .002\); \(\beta_{fake} = -1.49\), \(95\%~CI = [-2.50, -0.48]\), \(z = -2.89\), \(p = .004\)).
+
+A positive trend was found in the relationship between the \emph{Persecutory Ideation} dimension of paranoid thinking and the belief that the faces were real (\(\beta = 1.87\), \(95\%~CI = [0.99, 3.54]\), \(z = 1.93\), \(p = .054\)).
+
+The \emph{Prospective Anxiety} aspect of intolerance to uncertainty shared a negative trend in its association with confidence ratings (\(\beta_{real} = 1.43\), \(95\%~CI = [0.10, 2.76]\), \(z = 2.10\), \(p = .036\); \(\beta_{fake} = -0.91\), \(95\%~CI = [-1.93, 0.11]\), \(z = -1.75\), \(p = .081\)).
+No significant effect was found for social anxiety.
 
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-Only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments (\(\beta_{real} = 0.29\), \(95\% CI = [0.08, 0.50]\), \(z = 2.74\), \(p < .01\); \(\beta_{fake} = 0.38\), \(95\% CI = [0.18, 0.59]\), \(z = 3.60\), \(p < 0.001\)).
+However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments (\(\beta_{real} = 0.21\), \(95\%~CI = [0.02, 0.40]\), \(z = 2.20\), \(p = .028\); \(\beta_{fake} = 0.31\), \(95\%~CI = [0.12, 0.50]\), \(z = -8.90\), \(p < 0.001\)).
 
@@
 
-This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that the stimulus is artificially generated.
-The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants, when given the information, believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding is a testimony to both the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that a stimulus was artificially generated.
+The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
+This finding can be seen as a testimony not only to the effectiveness of our instructions, nut also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
-In fact, stimuli-related and participant-related characteristics accounted for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
+In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
 
@@
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgments, and its role in simulation monitoring, are a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women \textbf{{[}REF?{]}}.
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
+In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
 
-Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens.
-Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Fink et al., 2006; Qi \& Ying, 2022).
-However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces, in turn distorting the relationship with simulation monitoring.
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers (in particular, heart rate deceleration, A.
-Goldstein et al., 2002).
+Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
+Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \& Ying, 2022).
+It is thus possible that the evolutionary weight associated with attractiveness skewed men's perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring.
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers (e.g., heart rate deceleration, Skora et al., 2022).
 
-Our results suggested that trustworthiness ratings linearly increased beliefs in realness, for females only.
-Given the evidence suggesting that faces presented as real were rated as more trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such link to be present for both genders.
-One of the contributing mechanism to this dimorphism could have been the increased risk-taking aversion reported in females (explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
-However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real.
-As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
+Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
+Given prior evidence that faces presented as computer-generated were rated less trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such a linear association to be more clearly present for both genders.
+One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females (explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
+However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
+Further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
 
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-However, the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-Future studies could re-examine this aspect by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before the simulation monitoring judgments.
+Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
+This could be taken into perspective with previous studies, which report females to be relatively superior at face recall and recognition (Lewin \& Herlitz, 2002; Mishra et al., 2019), displaying higher levels of facial memory (Sommer et al., 2013) and exhibiting greater metacognitive awareness (Kaplan, 2012).
+Hence, it is possible that the confidence in evaluating faces are less malleable to external factors such as face familiarity for females.
+Indeed, metacognitive awareness has been associated with overconfidence in making judgements (Klein et al., 2018; Mata et al., 2013).
+However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident in face recall, regardless of their performance accuracy (Bailey, 2021; Herbst, 2020).
+Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with stronger narcissism (in particular the acclaim seeking and grandiose fantasies dimensions) displayed a stronger confidence in their simulation monitoring judgments.
-This is in line with the literature
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012), displayed a lower confidence in their simulation monitoring judgments.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were found to be associated with a higher number of faces judged as real.
+Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news (Piksa et al., 2022; Sindermann et al., 2020), possibly because they were less likely to engage in cognitive strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020) and are more vigilant when attending to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
+As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
 
-While early researchers had proposed narcissism to be a unitary construct (Raskin \& Terry, 1988; Sedikides et al., 2004), recent studies cast narcissism as encompassing 2 unique dimensions - namely narcissistic vulnerability, which is characterized by low self-esteem and a need for admiration, and narcissistic grandiosity, which encompasses high self-esteem, arrogance and aggressive self-assertiveness (Pincus \& Roche, 2011).
-Whereas narcissism has long been linked to over-confidence in decision-making (Campbell et al., 2004), a growing body of research indicates that this relationship is likely mostly driven by facets of narcissistic grandiosity (such as Acclaim Seeking), which drives individuals to see themselves as more superior than others and to externalize blame for poor decision-making consequences (O'Reilly \& Hall, 2021).
-Indeed, the evidence alludes that attributes specific to narcissistic grandiosity predict individuals' overconfidence in cognitive decision-making (Brunell \& Buelow, 2017; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
+Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
+Although an inverse effect was found for the authoritativeness facet of narcissism, we interpret this correlation as related to a higher response assertiveness.
+Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
+Participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
 
-Conversely, the literature on the correlation between honesty-humility and perceptual confidence judgements remain comparatively scarce, albeit some existing research links higher levels of honesty-humility to increased perceptions of risk and greater risk aversion (Levidi et al., 2022; Weller \& Thulin, 2012).
-As such, it could be argued that individuals with higher levels of honesty-humility could inherently possess a greater simulation monitoring sensitivity, perceiving a higher risk involved in making decisions on realness and therefore be less confident of their beliefs of reality.
-This is further supported by convergent evidence finding a negative link between honesty-humility and narcissism (Hodson et al., 2018).
-Therefore, further research examining the relationship between simulation monitoring decisions, personality traits, particularly that related to the dark triad and honesty-humility, and the perceived risks involved in making such evaluations, is warranted.
+Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
+Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
+Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
+This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities (Said et al., 2022), hence permitting themselves to be more confident in their simulation monitoring decisions.
+This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (@ Said et al., 2022).
 
-Interestingly, despite the ubiquity of AI, there is a lack of research pertaining to the influence of people's AI attitudes on their confidence in their discriminative ability to distinguish between output that is ``true'' (i.e., images of real faces) from those that is artificially-generated.
-One possible explanation for the positive relationship observed between AI-Enthusiasm and confidence in reality judgements could be that individuals with highly positive AI attitudes may perceive themselves as having greater knowledge about AI and its capabilities, hence permitting them to be more confident in their simulation monitoring decisions.
-This is in line with previous research findings, which indicate that greater enthusiasm about AI is related to having a higher confidence in one's knowledge regarding AI competencies (Said et al., 2022).
-Moreover, Said et al.
-(2022) further reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications.
-Specifically, people with AI attitudes that were highly positive and that were more confident in their AI knowledge were more likely to over-estimate the advantages of AI and under-estimate the risks involved in their application.
-As such, it is plausible that individuals' perceived self-knowledge about AI could have modulated the relationship between their attitudes towards AI and their confidence in their reality judgements.
+Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003), it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters (Freeman et al., 2005).
 
-Although the order of presentation of the facial images was randomized to reduce effects of adaptation, re-exposure delay was found to have a significant negative effect on simulation monitoring decisions, i.e., shorter delays were associated with faces being rated as more real.
-This may be because shorter re-exposure delays could have led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
-Although the distribution variance in re-exposure delay is small, recent research using event-related brain potentials report representations of faces to be qualitatively similar regardless of the degree and type of familiarity (e.g., personal or media-based), only distinguishing between familiar and unfamiliar faces (Wiese et al., 2021).
-Moreover, fictional stimuli has been shown to up-regulate emotions when associated with familiarity (Makowski et al., 2017; Sperduti et al., 2016), thus biasing its salience and perceived realness.
-Future studies could hence further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements (J.
+T.-H.
+Chen \& Lovibond, 2016; Jensen et al., 2014).
+This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios (Jensen et al., 2014; Wei, 2021).
+\textbf{WHY IS THIS CONTRADICTORY?
+the next part seems to be about emotion regulation.
+While interesting, it's a bit of a non-sequitur no?
+And the previous explanation could almost be enough.} While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions (Singer-Landau \& Meiran, 2021; Sperduti et al., 2016, 2017).
+In fact, previous studies report that individuals with greater paranoia and anxiety engaged in more affective processing of external ambiguous stimuli (Fornells-Ambrojo et al., 2015).
+This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral (Makowski, Sperduti, et al., 2019).
+As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that attenuated their confidence in real judgements.
+Future studies should clarify the role of emotions, particularly those related to anxiety, and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
 
-In conclusion, research on our ability to discriminate between what is real from what is not is increasingly relevant given the current expansion on technologies related to virtual and augmented realities.
-The aim of the present study was to examine whether facial attractiveness can significantly influence our simulation monitoring decisions.
-In line with our hypothesis, we found faces rated as attractive and unattractive to be perceived as more real for females as a result of an increased salience.
-However, for males, the observation of a positive linear relationship between attractiveness and beauty with simulation monitoring decisions, adjusted for evolutionarily advantageous features such as trustworthiness, suggest a more complex relationship than hypothesized.
-As such, future studies could further investigate the role of attractiveness in simulation monitoring, taking greater consideration of the former's multidimensionality.
+On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
+This may be because shorter re-exposure delays led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
+Indeed, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity (Makowski et al., 2017; Sperduti et al., 2016), thus biasing its salience and perceived realness.
+If that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
+Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+
+In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.
+The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions.
+We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
+We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
+Limitations include {[}\textbf{TO ADD}{]}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ahadzadeh2021social}{}}%
+Ahadzadeh, A. S., Ong, F. S., \& Wu, S. L. (2021). Social media skepticism and belief in conspiracy theories about COVID-19: The moderating role of the dark triad. \emph{Current Psychology}, 1--13.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
 Bago, B., Rosenzweig, L. R., Berinsky, A. J., \& Rand, D. G. (2022). Emotion may predict susceptibility to fake news but emotion regulation does not seem to help. \emph{Cognition and Emotion}, 1--15.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bailey2021gender}{}}%
+Bailey, A. (2021). \emph{A gender in-group effect on facial recall} {[}PhD thesis{]}. University of Tasmania.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-buunk2002age}{}}%
+Buunk, B.
+P., Dijkstra, P., Fetchenhauer, D., \& Kenrick, D.
+T.
+(2002).
+Age and gender differences in mate selection criteria for various involvement levels.
+\emph{Personal Relationships}, \emph{9}(3), 271--278.
+
 \leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-carolan2017searching}{}}%
+Carolan, P.
+L.
+(2017).
+\emph{Searching {``inaffectively''}: A behavioral, psychometric, and electroencephalographic investigation of psychopathic personality and visual-spatial attention} {[}PhD thesis{]}.
+Arts \& Social Sciences: Department of Psychology.
+
 \leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
@@
 Chen, J. M., Norman, J. B., \& Nam, Y. (2021). Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods}, \emph{53}(1), 371--389.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2016intolerance}{}}%
+Chen, J.
+T.-H., \& Lovibond, P.
+F.
+(2016).
+Intolerance of uncertainty is associated with increased threat appraisal and negative affect under ambiguity but not uncertainty.
+\emph{Behavior Therapy}, \emph{47}(1), 42--53.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-eddy2021self}{}}%
+Eddy, C. M. (2021). Self-serving social strategies: A systematic review of social cognition in narcissism. \emph{Current Psychology}, 1--19.
+
 \leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
@@
 \emph{Personality and Individual Differences}, \emph{41}(3), 491--499.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fornells2015people}{}}%
+Fornells-Ambrojo, M., Freeman, D., Slater, M., Swapp, D., Antley, A., \& Barker, C.
+(2015).
+How do people with persecutory delusions evaluate threat in a controlled social environment?
+A qualitative study using virtual reality.
+\emph{Behavioural and Cognitive Psychotherapy}, \emph{43}(1), 89--107.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2005psychology}{}}%
+Freeman, D., Garety, P.
+A., Bebbington, P., Slater, M., Kuipers, E., Fowler, D., Green, C., Jordan, J., Ray, K., \& Dunn, G.
+(2005).
+The psychology of persecutory ideation II: A virtual reality experimental study.
+\emph{The Journal of Nervous and Mental Disease}, \emph{193}(5), 309--315.
 
@@
 \emph{Psychological Medicine}, \emph{51}(2), 244--253.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2003can}{}}%
+Freeman, D., Slater, M., Bebbington, P.
+E., Garety, P.
+A., Kuipers, E., Fowler, D., Met, A., Read, C.
+M., Jordan, J., \& Vinayagamoorthy, V.
+(2003).
+Can virtual reality be used to investigate persecutory ideation?
+\emph{The Journal of Nervous and Mental Disease}, \emph{191}(8), 509--514.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein2002influence}{}}%
-Goldstein, A., Spencer, K. M., \& Donchin, E. (2002). The influence of stimulus deviance and novelty on the P300 and novelty P3. \emph{Psychophysiology}, \emph{39}(6), 781--790.
-
 \leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-grapsas2020and}{}}%
+Grapsas, S., Brummelman, E., Back, M.
+D., \& Denissen, J.
+J.
+(2020).
+The {``why''} and {``how''} of narcissism: A process model of narcissistic status pursuit.
+\emph{Perspectives on Psychological Science}, \emph{15}(1), 150--172.
+
 \leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
@@
 \emph{Acta Psychologica Sinica}, \emph{50}(4), 363.
+
+\leavevmode\vadjust pre{\hypertarget{ref-herbst2020gender}{}}%
+Herbst, T.
+H.
+(2020).
+Gender differences in self-perception accuracy: The confidence gap and women leaders' underrepresentation in academia.
+\emph{SA Journal of Industrial Psychology}, \emph{46}(1), 1--8.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-jensen2014intolerance}{}}%
+Jensen, D., Kind, A.
+J., Morrison, A.
+S., \& Heimberg, R.
+G.
+(2014).
+Intolerance of uncertainty and immediate decision-making in high-risk situations.
+\emph{Journal of Experimental Psychopathology}, \emph{5}(2), 178--190.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaplan2012effect}{}}%
+Kaplan, S. (2012). \emph{The effect of gender on recalling facial features: Does our gender determine which features are encoded at first glance?}
+
+\leavevmode\vadjust pre{\hypertarget{ref-klein2018metacognitive}{}}%
+Klein, D., Cunningham, A., \& Buchanan, E.
+M.
+(2018).
+How metacognitive awareness relates to overconfidence in interval judgments.
+\emph{International Journal of Undergraduate Research and Creative Activities}, \emph{10}(1).
+
 \leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lewin2002sex}{}}%
+Lewin, C., \& Herlitz, A. (2002). Sex differences in face recognition---women's faces make the difference. \emph{Brain and Cognition}, \emph{50}(1), 121--128.
+
 \leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
@@
 \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{366}(1571), 1638--1659.
+
+\leavevmode\vadjust pre{\hypertarget{ref-littrell2020overconfidently}{}}%
+Littrell, S., Fugelsang, J., \& Risko, E. F. (2020). Overconfidently underthinking: Narcissism negatively predicts cognitive reflection. \emph{Thinking \& Reasoning}, \emph{26}(3), 352--380.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-marcinkowska2021self}{}}%
+Marcinkowska, U.
+M., Jones, B.
+C., \& Lee, A.
+J.
+(2021).
+Self-rated attractiveness predicts preferences for sexually dimorphic facial characteristics in a culturally diverse sample.
+\emph{Scientific Reports}, \emph{11}(1), 1--8.
+
 \leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
 Martel, C., Pennycook, G., \& Rand, D. G. (2020). Reliance on emotion promotes belief in fake news. \emph{Cognitive Research: Principles and Implications}, \emph{5}(1), 1--20.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mata2013metacognitive}{}}%
+Mata, A., Ferreira, M.
+B., \& Sherman, S.
+J.
+(2013).
+The metacognitive advantage of deliberative thinkers: A dual-process perspective on overconfidence.
+\emph{Journal of Personality and Social Psychology}, \emph{105}(3), 353.
 
@@
 Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mishra2019gender}{}}%
+Mishra, M.
+V., Likitlersuang, J., B Wilmer, J., Cohan, S., Germine, L., \& DeGutis, J.
+M.
+(2019).
+Gender differences in familiar face recognition and the influence of sociocultural gender inequality.
+\emph{Scientific Reports}, \emph{9}(1), 1--12.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pincus2011narcissistic}{}}%
-Pincus, A.
-L., \& Roche, M.
-J.
-(2011).
-Narcissistic grandiosity and narcissistic vulnerability.
-\emph{The Handbook of Narcissism and Narcissistic Personality Disorder: Theoretical Approaches, Empirical Findings, and Treatments}, 31--40.
-
 \leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
@@
 R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-raskin1988principal}{}}%
-Raskin, R., \& Terry, H.
-(1988).
-A principal-components analysis of the narcissistic personality inventory and further evidence of its construct validity.
-\emph{Journal of Personality and Social Psychology}, \emph{54}(5), 890.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sedikides2004normal}{}}%
-Sedikides, C., Rudich, E.
-A., Gregg, A.
-P., Kumashiro, M., \& Rusbult, C.
-(2004).
-Are normal narcissists psychologically healthy?: Self-esteem matters.
-\emph{Journal of Personality and Social Psychology}, \emph{87}(3), 400.
-
 \leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-singer2021cognitive}{}}%
+Singer-Landau, E., \& Meiran, N.
+(2021).
+Cognitive appraisal contributes to feeling generation through emotional evidence accumulation rate: Evidence from instructed fictional reappraisal.
+\emph{Emotion}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-skora2022functional}{}}%
+Skora, L., Livermore, J., \& Roelofs, K. (2022). The functional role of cardiac activity in perception and action. \emph{Neuroscience \& Biobehavioral Reviews}, 104655.
+
 \leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
 Sobieraj, S., \& Krämer, N. C. (2014). What is beautiful in cyberspace? Communication with attractive avatars. \emph{International Conference on Social Computing and Social Media}, 125--136.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sommer2013sex}{}}%
+Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A., \& Wilhelm, O. (2013). Sex differences in face cognition. \emph{Acta Psychologica}, \emph{142}(1), 62--73.
 
@@
 \emph{Acta Psychologica}, \emph{173}, 13--20.
+
+\leavevmode\vadjust pre{\hypertarget{ref-spielmann2020predictive}{}}%
+Spielmann, S.
+S., Maxwell, J.
+A., MacDonald, G., Peragine, D., \& Impett, E.
+A.
+(2020).
+The predictive effects of fear of being single on physical attractiveness and less selective partner selection strategies.
+\emph{Journal of Social and Personal Relationships}, \emph{37}(1), 100--123.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-wei2021confidence}{}}%
+Wei, L. (2021). \emph{Confidence and information seeking in decision making under uncertainty} {[}PhD thesis{]}. University of Oxford.
+
 \leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wiese2021familiarity}{}}%
-Wiese, H., Hobden, G., Siilbek, E., Martignac, V., Flack, T.
-R., Ritchie, K.
-L., Young, A.
-W., \& Burton, A.
-M.
-(2021).
-Familiarity is familiarity is familiarity: Event-related brain potentials reveal qualitatively similar representations of personally familiar and famous faces.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}.
-
 \end{CSLReferences}

### 2022-10-07 submission/manuscript.Rmd
update manu

@@
 abstract: |
+
   Abstract abstract abstract.
@@
 <!-- stakes and Post-truth era -->
+
 For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
@@
 <!-- Ambiguous stimuli and irrelevance of objective features -->
+
 While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
@@
 <!-- Context -->
+
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has been an information published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
+However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
 In the absence of clear contextual information, what drives our beliefs of reality?
@@
 <!-- Internal features -->
+
 Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
@@
 <!-- Reactive features -->
+
 Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
@@
 <!-- Attractiveness -->
+
 AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
@@
 <!-- Goals and hypotheses -->
+
 This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
@@
 
-We excluded 5 participants that either failed 2 (>= 66\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
-The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3\% females, 51.0\% males, 0.7\% others).
+We excluded 5 participants that either failed 2 (\>= 66%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
+The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3% females, 51.0% males, 0.7% others).
 
@@
 The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modelled the probability of assigning a face to the real (>= 0) as opposed to fake (< 0).
+The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modelled the probability of assigning a face to the real (\>= 0) as opposed to fake (\< 0).
 The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using beta regressions (suited for outcome variables expressed in percentages).
@@
 
-Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake by 88.7\% of participants.
+Only one image file yielded a strong simulation monitoring bias (\> 85%), being classified as fake by 88.7% of participants.
 This image was removed from further analysis, leaving 108 trials per participant.
-On average, across participants, 44\% of images (95\%~CI [0.12, 0.64]) were judged as fake and 56\% of images (95\%~CI [0.36, 0.84]) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0\% for the participants and 9.6\% for the stimuli.
+On average, across participants, 44% of images (95%\~CI [0.12, 0.64]) were judged as fake and 56% of images (95%\~CI [0.36, 0.84]) as real.
+An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.
 
@@
 
-Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0\%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
+Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
 Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30$, $95\%~CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23$, $95\%~CI = [0.
@@
 Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.82$, $95\%~CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\%~CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$).
+No effect on confidence was found, aside from a quadratic relationship in females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\%~CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$).
 There was no interaction with reported self-attractiveness.
@@
 The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding can be seen as a testimony not only to the effectiveness of our instructions, nut also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+This finding can be seen as a testimony not only to the effectiveness of our instructions, but also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
-In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
+In fact, stimuli-related and participant-related characteristics accounted together for less than 20% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
 
 <!-- Attractiveness: females -->
+
 Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender.
@@
 <!-- Attractiveness: males -->
+
 Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
@@
 <!-- trustworthiness -->
+
 Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
@@
 <!-- familiarity -->
+
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
@@
 <!-- inter-indiv correlates -->
+
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were found to be associated with a higher number of faces judged as real.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher number of faces judged as real.
 Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly because they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant when attending to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
@@
 <!-- AI attitudes -->
+
 Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
@@
 This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
-This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].
+This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [\@ @said2022artificial].
 
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
+
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits were associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
@@
 <!-- given the known positive correlations between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia] -->
+
 <!-- In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
@@
 -->
+
 <!-- However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*. -->
@@
 <!-- Re-exposure Delay -->
+
 On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
@@
 <!-- Conclusion -->
+
 In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.

### 2022-10-09 submission/manuscript.Rmd
update

--- 2022-10-07 submission/manuscript.Rmd
@@
 This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
-**WHY IS THIS CONTRADICTORY?
-the next part seems to be about emotion regulation.
-While interesting, it's a bit of a non-sequitur no?
-And the previous explanation could almost be enough.** While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive].
-In fact, previous studies report that individuals with greater paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people].
-This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2019phenomenal].
-As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that attenuated their confidence in real judgements.
-Future studies should clarify the role of emotions, particularly those related to anxiety, and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
+Interestingly, no significant effect on individuals' perceptions of realness was observed despite the shared positive links between uncertainty intolerance and paranoia [@zheng2022worry].
+This suggests that being predisposed to view ambiguous scenarios negatively and having an enhanced sensitivity to social threats only partially explains the influence of paranoid traits on people's beliefs of realness.
+Given the lack of clear dissociation between the domains and mechanisms of paranoia and uncertainty intolerance [@king2017paranoia; @zheng2022worry], future studies should clarify the role of paranoid thinking on simulation monitoring processes, and attempt to delineate the specific emotional mechanisms involved.
 
@@
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-Limitations include [**TO ADD**].
+A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to, when they rated the face images on characteristics such as attractiveness.
+Hence, despite only a low number of faces being rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness.
+As such, future studies could modulate the extent to which facial memory affects realness judgements by incorporating novel face images during the re-exposure trial and examining if any significant difference is observed between the new and old images presented.
 

### 2022-10-09 submission/manuscript.Rmd

--- 2022-10-07 submission/manuscript.Rmd
@@
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
-
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits were associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
@@
 <!-- Conclusion -->
-
 In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.

### 2022-10-10 submission/manuscript.Rmd
update

@@
 
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\%~CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$)
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\%~CI = [0.99, 1.00]$ ), judgment confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$)
 
@@
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%).
-However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
+However, a significant positive and linear relationship was found between familiarity and the confidence judgments of rating faces as real ($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
 This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
@@
 
-The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\%~CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\%~CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
+The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgments ($\beta_{real} = -1.62$, $95\%~CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\%~CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
 
 Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\%~CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\%~CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
-Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
+Confidence judgments also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
 
@@
 The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
-In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
+In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgment of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
 
@@
 Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
-Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
+Interestingly, there were significant linear relationships between familiarity and confidence judgments for males only, where familiarity increased the confidence of reality beliefs.
 This could be taken into perspective with previous studies, which report females to be relatively superior at face recall and recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect].
 Hence, it is possible that the confidence in evaluating faces are less malleable to external factors such as face familiarity for females.
-Indeed, metacognitive awareness has been associated with overconfidence in making judgements [@mata2013metacognitive; @klein2018metacognitive].
+Indeed, metacognitive awareness has been associated with overconfidence in making judgments [@mata2013metacognitive; @klein2018metacognitive].
 However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident in face recall, regardless of their performance accuracy [@bailey2021gender; @herbst2020gender].
@@
 Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly because they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant when attending to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
-As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
+As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient, and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
 
-Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-Although an inverse effect was found for the authoritativeness facet of narcissism, we interpret this correlation as related to a higher response assertiveness.
+Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgments in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this correlation as related to a higher response assertiveness.
 Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
@@
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
 
-In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
+In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgments [@chen2016intolerance; @jensen2014intolerance].
 This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
-Interestingly, no significant effect on individuals' perceptions of realness was observed despite the shared positive links between uncertainty intolerance and paranoia [@zheng2022worry].
-This suggests that being predisposed to view ambiguous scenarios negatively and having an enhanced sensitivity to social threats only partially explains the influence of paranoid traits on people's beliefs of realness.
-Given the lack of clear dissociation between the domains and mechanisms of paranoia and uncertainty intolerance [@king2017paranoia; @zheng2022worry], future studies should clarify the role of paranoid thinking on simulation monitoring processes, and attempt to delineate the specific emotional mechanisms involved.
+Interestingly, no significant effect on individuals' perceptions of realness was observed despite uncertainty intolerance being commonly associated with enhanced threat appraisal [@zheng2022worry; @chen2016intolerance; @jensen2014intolerance].
+To this end, recent studies have attempted to disentangle the perception of threat from the experience of negative affect in ambiguous situations, conceptualising uncertainty intolerance as a response to unpredictability independent of threat altogether [@pepperdine2018disentangling; @milne2019review].
+Taking this into perspective with the positive relations found between paranoid traits and beliefs of reality, future studies could clarify the role of threat appraisal on simulation monitoring processes, and attempt to delineate the specific mechanisms involved.
 
@@
 
-On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
+On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgments for faces perceived as real following a shorter re-exposure delay.
 This may be because shorter re-exposure delays led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
@@
 If that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
-Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgments.
 
@@
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to, when they rated the face images on characteristics such as attractiveness.
-Hence, despite only a low number of faces being rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness.
-As such, future studies could modulate the extent to which facial memory affects realness judgements by incorporating novel face images during the re-exposure trial and examining if any significant difference is observed between the new and old images presented.
+A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to (when they rated the face images on characteristics such as attractiveness).
+Although only a small subset of faces was rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness.
+As such, future studies could modulate and examine the extent to which facial memory affects realness judgments by incorporating novel face images during the re-exposure trial or varying the duration of the re-exposure delay.
 

### 2022-10-11 submission/manuscript.Rmd
update manu

--- 2022-10-09 submission/manuscript.Rmd
@@
 abstract: |
-
-  Abstract abstract abstract.
+  Distinguishing between artificial, computer-generated images and reality has become an increasingly difficult and complex task, and the role of stimuli characteristics that may be involved in driving simulation monitoring remains unclear.
+In this study, participants (n=150) were presented with real facial images and rated stimuli characteristics (attractiveness, beauty, trustworthiness, familiarity) before making reality judgments.
+We applied Bayesian mixed models to investigate the relationship between participants’ reality judgments, inter-individual traits and characteristic of facial images.
+Our results suggest a gender-dependent relationship between attractiveness, beauty and reality judgments.
+We report a quadratic relationship for female participants between attractiveness and reality, versus a significant positive linear relationship for males between attractiveness, beauty and reality.
+Furthermore, we found that the dispositional traits: narcissistic acclaim-seeking and manipulativeness, and persecutory ideation, were positively associated with real-fake judgements.
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
@@
 While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
-Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
+Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
 
@@
 ```{r message=FALSE, warning=FALSE, fig.cap="Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
-fake (solid line) and 2) on the confidence associated with that judgment (dashed lines) depending on the sex.
+fake (solid line) and 2) on the confidence associated with that judgement (dashed lines) depending on the sex.
 Bottom part shows the effect of personality traits on the belief (black line) and the confidence associated with it (colored lines).
-The points are the average per participant confidence for both types of judgments.
+The points are the average per participant confidence for both types of judgements.
 Stars indicate significance (p < .001***, p < .01**, p < .05*)", out.width="100%"}
@@
 <!-- There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\%~CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
-There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\%~CI = [-0.1, 0.0]$, $p = .023$).
+There was also a significant negative effect on judgement confidence, but only in the real condition ($\beta = -0.005$, $95\%~CI = [-0.1, 0.0]$, $p = .023$).
 -->
@@
 Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\%~CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\%~CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
-Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
+Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgements with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
 
@@
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
+However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgements ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
 
@@
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
 In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
@@
 Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
+As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
 
@@
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgments.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgements.
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher number of faces judged as real.
 Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly because they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant when attending to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
-As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
+As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient, and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
 
 Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-Although an inverse effect was found for the authoritativeness facet of narcissism, we interpret this correlation as related to a higher response assertiveness.
-Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
+Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this correlation as related to a higher response assertiveness.
+Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
 Participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
@@
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
+
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
 
-In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
+In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
 This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
-Interestingly, no significant effect on individuals' perceptions of realness was observed despite the shared positive links between uncertainty intolerance and paranoia [@zheng2022worry].
-This suggests that being predisposed to view ambiguous scenarios negatively and having an enhanced sensitivity to social threats only partially explains the influence of paranoid traits on people's beliefs of realness.
-Given the lack of clear dissociation between the domains and mechanisms of paranoia and uncertainty intolerance [@king2017paranoia; @zheng2022worry], future studies should clarify the role of paranoid thinking on simulation monitoring processes, and attempt to delineate the specific emotional mechanisms involved.
+Interestingly, no significant effect on individuals' perceptions of realness was observed despite uncertainty intolerance being commonly associated with enhanced threat appraisal [@zheng2022worry; @chen2016intolerance; @jensen2014intolerance].
+To this end, recent studies have attempted to disentangle the perception of threat from the experience of negative affect in ambiguous situations, conceptualising uncertainty intolerance as a response to unpredictability independent of threat altogether [@pepperdine2018disentangling; @milne2019review].
+Taking this into perspective with the positive relations found between paranoid traits and beliefs of reality, future studies could clarify the role of threat appraisal on simulation monitoring processes, and attempt to delineate the specific mechanisms involved.
 
@@
 Social phobia being characterized as a heightened fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact], the nature of the stimuli - pictures of faces - could play a role in this association.
-However, given the fact that neutral faces are perceived as more threatening by participants with high social phobia [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation], and thus likely more salient, we would have expected high social phobia tendencies to be associated with a bias towards reality judgment.
+However, given the fact that neutral faces are perceived as more threatening by participants with high social phobia [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation], and thus likely more salient, we would have expected high social phobia tendencies to be associated with a bias towards reality judgement.
 This apparent contradiction could be explained through the lens of fictional reappraisal,  **TODO: can you double check that this last statement is correct?**.
@@
 
-<!-- However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgments, but not the simulation monitoring bias *per se*. -->
+<!-- However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgements, but not the simulation monitoring bias *per se*. -->
 
@@
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to, when they rated the face images on characteristics such as attractiveness.
-Hence, despite only a low number of faces being rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness.
-As such, future studies could modulate the extent to which facial memory affects realness judgements by incorporating novel face images during the re-exposure trial and examining if any significant difference is observed between the new and old images presented.
+A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to (when they rated the face images on characteristics such as attractiveness).
+Although only a small subset of faces was rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness.
+As such, future studies could modulate and examine the extent to which facial memory affects realness judgements by incorporating novel face images during the re-exposure trial or varying the duration of the re-exposure delay.
 

### 2022-10-11 submission/manuscript.Rmd
update

@@
 abstract: |
-  Distinguishing between artificial, computer-generated images and reality has become an increasingly difficult and complex task, and the role of stimuli characteristics that may be involved in driving simulation monitoring remains unclear.
-In this study, participants (n=150) were presented with real facial images and rated stimuli characteristics (attractiveness, beauty, trustworthiness, familiarity) before making reality judgments.
-We applied Bayesian mixed models to investigate the relationship between participants’ reality judgments, inter-individual traits and characteristic of facial images.
-Our results suggest a gender-dependent relationship between attractiveness, beauty and reality judgments.
-We report a quadratic relationship for female participants between attractiveness and reality, versus a significant positive linear relationship for males between attractiveness, beauty and reality.
-Furthermore, we found that the dispositional traits: narcissistic acclaim-seeking and manipulativeness, and persecutory ideation, were positively associated with real-fake judgements.
+  Distinguishing between artificial stimuli (e.g., computer-generated faces) and reality has become increasingly difficult given technological advances.
+However, the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
+The stimuli were then presented again with the new information that a number of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
+Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large amount of them as "fake".
+Moreover, our results suggest a gender-dependent role of attractiveness on reality judgments, with faces rated as more attractive being classified as more real.
+We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "5114"
+wordcount         : "4697"
 bibliography      : references.bib
@@
 
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2019phenomenal; @makowski2018cognitive].
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2018cognitive; @makowski2019phenomenal].
 With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
 However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
-In the absence of clear contextual information, what drives our beliefs of reality?
+Thus, in the absence of clear contextual information, what drives our beliefs of reality?
 
@@
 
-In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.
-The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions.
+Understanding the factors driving the reality beliefs pertaining to ambiguous stimuli is becoming increasingly pertinent given the rapid technological advances.
+The aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
 We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-A limitation of the current paradigm includes requiring participants to judge the realness of faces they had prior exposure to (when they rated the face images on characteristics such as attractiveness).
-Although only a small subset of faces was rated as highly familiar, subconscious recall of the face stimuli during re-exposure could have confounded perceptions of its realness.
-As such, future studies could modulate and examine the extent to which facial memory affects realness judgements by incorporating novel face images during the re-exposure trial or varying the duration of the re-exposure delay.
+
+Regarding the possible study limitations, the current paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements to influence the other ratings).
+Although the effect of re-exposure delay was negligible, the potential bias induced by face familiarity (as compared to judging completely new items) cannot be discarded.
+Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
+It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimuli - like hair or eyes in the case of faces, or based on a gut feeling).
 

### 2022-10-11 submission/manuscript.tex
update

@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 5114}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4697}
 \usepackage{lineno}
@@
 \abstract{%
-Abstract abstract abstract.
+Distinguishing between artificial stimuli (e.g., computer-generated faces) and reality has become increasingly difficult given technological advances.
+However, the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
+The stimuli were then presented again with the new information that a number of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
+Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large amount of them as ``fake''.
+Moreover, our results suggest a gender-dependent role of attractiveness on reality judgments, with faces rated as more attractive being classified as more real.
+We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
 }
@@
 While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
-Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
-
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (Makowski, 2018; a process henceforth referred to as \emph{simulation monitoring}, Makowski, Sperduti, et al., 2019).
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has been an information published), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
+Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
+
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, Makowski, 2018; Makowski, Sperduti, et al., 2019).
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
+However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
 Chen et al., 2015).
@@
 \includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
-fake (solid line) and 2) on the confidence associated with that judgment (dashed lines) depending on the sex.
+fake (solid line) and 2) on the confidence associated with that judgement (dashed lines) depending on the sex.
 Bottom part shows the effect of personality traits on the belief (black line) and the confidence associated with it (colored lines).
-The points are the average per participant confidence for both types of judgments.
+The points are the average per participant confidence for both types of judgements.
 Stars indicate significance (p < .001***, p < .01**, p < .05*)}\label{fig:unnamed-chunk-3}
@@
 Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 11.82\), \(95\%~CI = [4.28, 20.21]\), \(z = 2.76\), \(p = .006\)) for males only.
-No effect on confidence was found, aside from a quadratic relationship for females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces (\(\beta_{poly2} = 7.84\), \(95\%~CI = [3.39, 12.29]\), \(z = 3.46\), \(p < .001\)).
+No effect on confidence was found, aside from a quadratic relationship in females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces (\(\beta_{poly2} = 7.84\), \(95\%~CI = [3.39, 12.29]\), \(z = 3.46\), \(p < .001\)).
 There was no interaction with reported self-attractiveness.
@@
 Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as \emph{Acclaim Seeking} (\(\beta = 2.24\), \(95\%~CI = [1.17, 4.27]\), \(z = 2.44\), \(p = .015\)), and \emph{Manipulativeness} (\(\beta = 0.47\), \(95\%~CI = [0.25, 0.87]\), \(z = -2.4\), \(p = 0.017\)).
-Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with \emph{Acclaim Seeking} (\(\beta_{real} = 1.65\), \(95\%~CI = [0.59, 2.70]\), \(z = 3.07\), \(p =.002\); \(\beta_{fake} = 1.62\), \(95\%~CI = [0.56, 2.68]\), \(z = 3.00\), \(p = .003\)), and a negative relationship with \emph{Authoritativeness} (\(\beta_{real} = -1.57\), \(95\%~CI = [-2.58, -0.57]\), \(z = -3.08\), \(p = .002\); \(\beta_{fake} = -1.49\), \(95\%~CI = [-2.50, -0.48]\), \(z = -2.89\), \(p = .004\)).
+Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgements with \emph{Acclaim Seeking} (\(\beta_{real} = 1.65\), \(95\%~CI = [0.59, 2.70]\), \(z = 3.07\), \(p =.002\); \(\beta_{fake} = 1.62\), \(95\%~CI = [0.56, 2.68]\), \(z = 3.00\), \(p = .003\)), and a negative relationship with \emph{Authoritativeness} (\(\beta_{real} = -1.57\), \(95\%~CI = [-2.58, -0.57]\), \(z = -3.08\), \(p = .002\); \(\beta_{fake} = -1.49\), \(95\%~CI = [-2.50, -0.48]\), \(z = -2.89\), \(p = .004\)).
 
@@
 Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments (\(\beta_{real} = 0.21\), \(95\%~CI = [0.02, 0.40]\), \(z = 2.20\), \(p = .028\); \(\beta_{fake} = 0.31\), \(95\%~CI = [0.12, 0.50]\), \(z = -8.90\), \(p < 0.001\)).
+However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgements (\(\beta_{real} = 0.21\), \(95\%~CI = [0.02, 0.40]\), \(z = 2.20\), \(p = .028\); \(\beta_{fake} = 0.31\), \(95\%~CI = [0.12, 0.50]\), \(z = -8.90\), \(p < 0.001\)).
 
@@
 The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding can be seen as a testimony not only to the effectiveness of our instructions, nut also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+This finding can be seen as a testimony not only to the effectiveness of our instructions, but also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
@@
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
 In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
@@
 Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.
-
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012), displayed a lower confidence in their simulation monitoring judgments.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were found to be associated with a higher number of faces judged as real.
+As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
+
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012), displayed a lower confidence in their simulation monitoring judgements.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher number of faces judged as real.
 Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news (Piksa et al., 2022; Sindermann et al., 2020), possibly because they were less likely to engage in cognitive strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020) and are more vigilant when attending to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
-As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
+As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient, and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
 
 Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
-Although an inverse effect was found for the authoritativeness facet of narcissism, we interpret this correlation as related to a higher response assertiveness.
-Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgment regarding the real or fake nature of ambiguous stimuli.
+Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this correlation as related to a higher response assertiveness.
+Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
 Participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
@@
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003), it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters (Freeman et al., 2005).
 
-In contrast, intolerance to uncertainty, a trait related to enhanced threat appraisal, was found to be negatively associated with the confidence in real judgements (J.
+In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgements (J.
 T.-H.
@@
 This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios (Jensen et al., 2014; Wei, 2021).
-\textbf{WHY IS THIS CONTRADICTORY?
-the next part seems to be about emotion regulation.
-While interesting, it's a bit of a non-sequitur no?
-And the previous explanation could almost be enough.} While the findings seem contradictory, they could possibly be interpreted through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a means to down-regulate the associated emotional reactions (Singer-Landau \& Meiran, 2021; Sperduti et al., 2016, 2017).
-In fact, previous studies report that individuals with greater paranoia and anxiety engaged in more affective processing of external ambiguous stimuli (Fornells-Ambrojo et al., 2015).
-This is also in line with prior findings which suggest that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral (Makowski, Sperduti, et al., 2019).
-As such, it is possible that individuals high in such anxiety-related traits are more sensitive to social cues and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that attenuated their confidence in real judgements.
-Future studies should clarify the role of emotions, particularly those related to anxiety, and attempt at delineating processes related to emotion perception and reaction from emotion regulation.
+Interestingly, no significant effect on individuals' perceptions of realness was observed despite uncertainty intolerance being commonly associated with enhanced threat appraisal (J.
+T.-H.
+Chen \& Lovibond, 2016; Jensen et al., 2014; Zheng et al., 2022).
+To this end, recent studies have attempted to disentangle the perception of threat from the experience of negative affect in ambiguous situations, conceptualising uncertainty intolerance as a response to unpredictability independent of threat altogether (Milne et al., 2019; Pepperdine et al., 2018).
+Taking this into perspective with the positive relations found between paranoid traits and beliefs of reality, future studies could clarify the role of threat appraisal on simulation monitoring processes, and attempt to delineate the specific mechanisms involved.
 
@@
 
-In conclusion, understanding the factors driving our beliefs that ambiguous stimuli are real or not is becoming increasingly pertinent, given the current expansion on technologies related to virtual and augmented realities.
-The aim of the present study was to examine whether facial attractiveness significantly influences our simulation monitoring decisions.
+Understanding the factors driving the reality beliefs pertaining to ambiguous stimuli is becoming increasingly pertinent given the rapid technological advances.
+The aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
 We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-Limitations include {[}\textbf{TO ADD}{]}.
+
+Regarding the possible study limitations, the current paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements to influence the other ratings).
+Although the effect of re-exposure delay was negligible, the potential bias induced by face familiarity (as compared to judging completely new items) cannot be discarded.
+Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
+It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimuli - like hair or eyes in the case of faces, or based on a gut feeling).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
+King, A., \& Dudley, R.
+(2017).
+Paranoia, worry, cognitive avoidance and intolerance of uncertainty in a student population.
+\emph{Journal of Applied Psychology and Social Science}, \emph{3}(2), 70--89.
+
 \leavevmode\vadjust pre{\hypertarget{ref-klein2018metacognitive}{}}%
@@
 Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
+
+\leavevmode\vadjust pre{\hypertarget{ref-milne2019review}{}}%
+Milne, S., Lomax, C., \& Freeston, M. (2019). A review of the relationship between intolerance of uncertainty and threat appraisal in anxiety. \emph{The Cognitive Behaviour Therapist}, \emph{12}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pepperdine2018disentangling}{}}%
+Pepperdine, E., Lomax, C., \& Freeston, M. (2018). Disentangling intolerance of uncertainty and threat appraisal in everyday situations. \emph{Journal of Anxiety Disorders}, \emph{57}, 31--38.
+
 \leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
@@
 Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology}, \emph{36}, 44--48.
-
-\leavevmode\vadjust pre{\hypertarget{ref-singer2021cognitive}{}}%
-Singer-Landau, E., \& Meiran, N.
-(2021).
-Cognitive appraisal contributes to feeling generation through emotional evidence accumulation rate: Evidence from instructed fictional reappraisal.
-\emph{Emotion}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-zheng2022worry}{}}%
+Zheng, S., Marcos, M., Stewart, K.
+E., Szabo, J., Pawluk, E., Girard, T.
+A., \& Koerner, N.
+(2022).
+Worry, intolerance of uncertainty, negative urgency, and their associations to paranoid thinking.
+\emph{Personality and Individual Differences}, \emph{186}, 111382.
+
 \end{CSLReferences}

### 2022-10-11 submission/manuscript.Rmd
update againnn

@@
 The stimuli were then presented again with the new information that a number of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
-Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large amount of them as "fake".
+Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as "fake".
 Moreover, our results suggest a gender-dependent role of attractiveness on reality judgments, with faces rated as more attractive being classified as more real.
@@
 While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
-Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
+Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?
 
@@
 
-In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
+In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which prefaced that the aim of the research was to validate a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
-It is thus possible that the evolutionary weight associated with attractiveness skewed men's perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring.
+It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
 However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [e.g., heart rate deceleration, @skora2022functional].
@@
 Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
-Participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
+Alternatively, participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
 
@@
 This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
-This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [\@ @said2022artificial].
+This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@said2022artificial].
 
@@
 It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimuli - like hair or eyes in the case of faces, or based on a gut feeling).
+On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used in evaluating the realness of the perceived stimuli (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling).
 

### 2022-10-12 submission/manuscript.Rmd
update

@@
 abstract: |
-  Distinguishing between artificial stimuli (e.g., computer-generated faces) and reality has become increasingly difficult given technological advances.
-However, the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+  Technological advances make the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, and the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
 In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
@@
 Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as "fake".
-Moreover, our results suggest a gender-dependent role of attractiveness on reality judgments, with faces rated as more attractive being classified as more real.
+Moreover, our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "4697"
+wordcount         : "4707"
 bibliography      : references.bib
@@
 
-In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which prefaced that the aim of the research was to validate a new face generation algorithm).
+In the last part of the study, participants were informed that "about half" of the image"s previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%).
-However, a significant positive and linear relationship was found between familiarity and the confidence judgments of rating faces as real ($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
+However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
 This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
@@
 It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used in evaluating the realness of the perceived stimuli (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling).
+On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling) to guide their reality beliefs.
 

### 2022-10-12 submission/manuscript.tex
update

@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4697}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4707}
 \usepackage{lineno}
@@
 \abstract{%
-Distinguishing between artificial stimuli (e.g., computer-generated faces) and reality has become increasingly difficult given technological advances.
-However, the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+Technological advances make the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, and the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
 In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
 The stimuli were then presented again with the new information that a number of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
-Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large amount of them as ``fake''.
-Moreover, our results suggest a gender-dependent role of attractiveness on reality judgments, with faces rated as more attractive being classified as more real.
+Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as ``fake''.
+Moreover, our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
@@
 Chen et al., 2015).
-In the absence of clear contextual information, what drives our beliefs of reality?
+Thus, in the absence of clear contextual information, what drives our beliefs of reality?
 
@@
 
-In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which mentioned that the research was aimed at validating a new face generation algorithm).
+In the last part of the study, participants were informed that ``about half'' of the image''s previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \& Ying, 2022).
-It is thus possible that the evolutionary weight associated with attractiveness skewed men's perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring.
+It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
 However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers (e.g., heart rate deceleration, Skora et al., 2022).
@@
 This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities (Said et al., 2022), hence permitting themselves to be more confident in their simulation monitoring decisions.
-This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (@ Said et al., 2022).
+This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (Said et al., 2022).
 
@@
 It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimuli - like hair or eyes in the case of faces, or based on a gut feeling).
+On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling) to guide their reality beliefs.
 

### 2022-10-12 submission/manuscript.Rmd
update
@anshu-97 can you add something in the funding section to include PPF and NICE

@@
 title             : "**Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated**"
-shorttitle        : "Illusion Game Validation"
+shorttitle        : "Attractiveness and Reality"
 author:
@@
   - id            : "2"
+    institution   : "Singapore-ETH Centre, Future Cities Laboratory, Singapore"
+  - id            : "3"
     institution   : "LKC Medicine, Nanyang Technological University, Singapore"
-  - id            : "3"
+  - id            : "4"
     institution   : "National Institute of Education, Singapore"
-  - id            : "4"
+  - id            : "5"
     institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
@@
 
-In the last part of the study, participants were informed that "about half" of the image"s previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
+In the last part of the study, participants were informed that "about half" of the images previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 
-The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, derived based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modelled the probability of assigning a face to the real (\>= 0) as opposed to fake (\< 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using beta regressions (suited for outcome variables expressed in percentages).
+The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
+The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\>= 0) as opposed to fake (\< 0).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using mixed beta regressions (suited for outcome variables expressed in percentages).
+The models included the participants and stimuli as random factors.
 
@@
 
+# Funding
+
 # Acknowledgments

### 2022-10-13 submission/manuscript.Rmd

@@
   Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (dom.makowski@gmail.com).
+This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme.
 abstract: |

### 2022-10-13 analysis.Rmd
Revert "Merge branch 'main' of https://github.com/RealityBending/FakeFace"
This reverts commit b3560a45cd81079ffd21d0a0c004e66fabe8cf14, reversing
changes made to 1b92eb7cb78b582b0068e6afac202a92671c582e.

@@
 
-p_ffni2 <- plot_interindividual(m_real, m_conf, var = "FFNI_Authoritativeness", fill = "#FF9800") + labs(x = "Narcissism (Authoritativeness)")
+p_ffni2 <- plot_interindividual(m_real, m_conf, var = "FFNI_Authoritativeness", fill = "#FF5722") + labs(x = "Narcissism (Authoritativeness)")
 p_ffni2
 
-# p_ffni3 <- plot_interindividual(m_real, m_conf, var = "FFNI_ThrillSeeking", fill = "#FF5722") + labs(x = "Narcissism (Thrill Seeking)")
-# p_ffni3 
+p_ffni3 <- plot_interindividual(m_real, m_conf, var = "FFNI_Manipulativeness", fill = "#FF9800") + labs(x = "Narcissism (Manipulativeness)")
+p_ffni3
 ```
@@
   display()
+
+p_gpts1 <- plot_interindividual(m_real, m_conf, var = "GPTS_Persecution", fill = "#673AB7") + labs(x = "Paranoid Thoughts (Persecution)")
+p_gpts1
 ```
@@
   plot_layout(guides = "collect") &
-  theme(legend.position='top', legend.title = element_blank())
+  theme(legend.title = element_text(face = "bold"))
 
@@
     # ((p_ffni1 / p_ipip) | (p_ffni2 / p_social) | (p_ffni3 / p_ai)) + 
-    ((p_ffni1 / p_ipip) | (p_ffni2 / p_ai)) + 
+    ((p_ffni1 / p_ipip) | (p_ffni3 / p_gpts1) | (p_ffni2 / p_ai)) +
   plot_layout(guides = "collect") +
-  plot_annotation(title = "Personality Correlates of Simulation Monitoring Tendencies", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
+  plot_annotation(title = "Personality Correlates of Simulation Monitoring Tendencies", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) &
+  theme(legend.title = element_text(face = "bold")) 
   ) +

### 2022-10-13 submission/manuscript.Rmd
Revert "Merge branch 'main' of https://github.com/RealityBending/FakeFace"
This reverts commit b3560a45cd81079ffd21d0a0c004e66fabe8cf14, reversing
changes made to 1b92eb7cb78b582b0068e6afac202a92671c582e.

--- 2022-10-12 submission/manuscript.Rmd
@@
   Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (dom.makowski@gmail.com).
+This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme.
 abstract: |
-  Technological advances make the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, and the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+  Distinguishing between artificial stimuli (e.g., computer-generated faces) and reality has become increasingly difficult given technological advances.
+However, the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
 In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
@@
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "4707"
+wordcount         : "4697"
 bibliography      : references.bib
@@
 
-In the last part of the study, participants were informed that "about half" of the image"s previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
+In the last part of the study, participants were informed that about half of the images previously seen were AI-generated (the instructions used a cover story which prefaced that the aim of the research was to validate a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling) to guide their reality beliefs.
+On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used in evaluating the realness of the perceived stimuli (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling).
 

### 2022-10-13 submission/manuscript.Rmd
Revert "add funding info"
This reverts commit 1b92eb7cb78b582b0068e6afac202a92671c582e.

@@
   Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (dom.makowski@gmail.com).
-This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme.
 abstract: |

### 2022-10-13 analysis.Rmd
update

@@
     theme_modern(axis.title.space = 5) +
-    ggside::geom_xsidedensity(fill = fill, color = "white") +
-    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
+    ggside::geom_xsidedensity(aes(fill = Sex), alpha=2/3, color = NA) +
+    ggside::geom_ysidedensity(aes(fill = Sex), alpha=2/3, color = NA) +
     ggside::theme_ggside_void() +

### 2022-10-13 submission/manuscript.Rmd
update

--- 2022-10-13 submission/manuscript.Rmd
@@
 
+This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
+
 # Acknowledgments

### 2022-10-13 submission/manuscript.tex
update

@@
 
-\shorttitle{Illusion Game Validation}
+\shorttitle{Attractiveness and Reality}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{2} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{3} National Institute of Education, Singapore\\\textsuperscript{4} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{2} Singapore-ETH Centre, Future Cities Laboratory, Singapore\\\textsuperscript{3} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{4} National Institute of Education, Singapore\\\textsuperscript{5} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}
 
@@
 
-In the last part of the study, participants were informed that ``about half'' of the image''s previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
+In the last part of the study, participants were informed that ``about half'' of the images previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
 The same set of stimuli was displayed again for 500 ms in a new randomized order.
@@
 
-The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, derived based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models (with the participants and images entered as random factors), which modelled the probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using beta regressions (suited for outcome variables expressed in percentages).
+The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
+The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
+The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using mixed beta regressions (suited for outcome variables expressed in percentages).
+The models included the participants and stimuli as random factors.
 
@@
 On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling) to guide their reality beliefs.
+
+\hypertarget{funding}{%
+\section{Funding}\label{funding}}
+
+This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister's Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
 

### 2022-10-20 submission/manuscript.Rmd
update manu

@@
 This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that a stimulus was artificially generated.
-The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding can be seen as a testimony not only to the effectiveness of our instructions, but also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
+Most strikingly, despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
+This finding hence attests to the effectiveness of our instructions, highlighting the current expectations regarding CGI technology, as well as the volatility of our sense of reality.
 It underlines the strong impact of prior expectations and information on reality beliefs.
@@
 The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
-In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
+In fact, female participants were more confident in judging faces as fake only when they were rated very high or low on beauty, suggesting that physical beauty and attractiveness are not analogous in their effects on simulation monitoring decisions.
 
@@
 
-Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
+Contrary to our hypothesis, we did not find familiarity to be significantly related to simulation monitoring decisions.
 Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-This could be taken into perspective with previous studies, which report females to be relatively superior at face recall and recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect].
-Hence, it is possible that the confidence in evaluating faces are less malleable to external factors such as face familiarity for females.
-Indeed, metacognitive awareness has been associated with overconfidence in making judgements [@mata2013metacognitive; @klein2018metacognitive].
-However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident in face recall, regardless of their performance accuracy [@bailey2021gender; @herbst2020gender].
-Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+While this alludes to confidence judgements in face simulation monitoring decisions being more stable in females [@mata2013metacognitive; @klein2018metacognitive], the present literature regarding gender differences in face recognition confidence has been mixed.
+Namely, previous reports of females demonstrating superior facial memory [@mishra2019gender; @lewin2002sex; @sommer2013sex] and higher metacognitve awareness [@kaplan2012effect], have been contested by recent findings of males' overconfidence in face recall [@bailey2021gender; @herbst2020gender].
+Furthermore, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
@@
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], displayed a lower confidence in their simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher number of faces judged as real.
-Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly because they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant when attending to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
-As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient, and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], to be related to a lower confidence in simulation monitoring judgements.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was associated with a higher number of faces judged as real.
+This is in line with recent research which found narcissists were less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and are more cognizant of external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
 
-Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], we confirm previous evidence of the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
 Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this correlation as related to a higher response assertiveness.
@@
 
-<!-- AI attitudes -->
-
-Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
-Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
-Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
-This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
-This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@said2022artificial].
-
 <!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
 
-Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
+Our findings suggest - though with weak significance - a positive link between paranoid ideation and the belief that the stimuli were real.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it could be that individuals with paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
 
-In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
+<!-- In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
 This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
@@
 Taking this into perspective with the positive relations found between paranoid traits and beliefs of reality, future studies could clarify the role of threat appraisal on simulation monitoring processes, and attempt to delineate the specific mechanisms involved.
+-->
 
@@
 
+<!-- AI attitudes -->
+
+Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
+Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
+Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
+This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
+In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@said2022artificial].
+
 <!-- Re-exposure Delay -->
@@
 On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-This may be because shorter re-exposure delays led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
-Indeed, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity [@sperduti2016paradox; @makowski2017being], thus biasing its salience and perceived realness.
-If that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
+This may be because shorter re-exposure delays, as opposed to longer delays, led to the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
+Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness [@sperduti2016paradox; @makowski2017being].
+However, if that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
 Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
@@
 Understanding the factors driving the reality beliefs pertaining to ambiguous stimuli is becoming increasingly pertinent given the rapid technological advances.
-The aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
-We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
-We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-
-Regarding the possible study limitations, the current paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements to influence the other ratings).
+The current experimental paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements from influencing the other ratings).
 Although the effect of re-exposure delay was negligible, the potential bias induced by face familiarity (as compared to judging completely new items) cannot be discarded.
 Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
-It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling) to guide their reality beliefs.
+
+The aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
+Notably, we found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
+We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
+However, it has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
 

### 2022-10-22 submission/manuscript.Rmd
discussion

@@
 Most strikingly, despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding hence attests to the effectiveness of our instructions, highlighting the current expectations regarding CGI technology, as well as the volatility of our sense of reality.
-It underlines the strong impact of prior expectations and information on reality beliefs.
-In fact, stimuli-related and participant-related characteristics accounted together for less than 20% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
+This finding not only attests to the effectiveness of our instructions, but highlights the current levels of expectation regarding CGI technology.
+The strong impact of prior expectations and information on reality beliefs demonstrated here underlines the volatility of our sense of reality.
+In fact, stimuli-related and participant-related characteristics accounted together for less than 20% of the beliefs variance, suggesting a large contribution of other subjective processes.
 
@@
 Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-While this alludes to confidence judgements in face simulation monitoring decisions being more stable in females [@mata2013metacognitive; @klein2018metacognitive], the present literature regarding gender differences in face recognition confidence has been mixed.
-Namely, previous reports of females demonstrating superior facial memory [@mishra2019gender; @lewin2002sex; @sommer2013sex] and higher metacognitve awareness [@kaplan2012effect], have been contested by recent findings of males' overconfidence in face recall [@bailey2021gender; @herbst2020gender].
-Furthermore, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Although the familiarity measure was not a "recognition" measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females [@mishra2019gender; @lewin2002sex; @sommer2013sex], as well as an overconfidence in face recall for males [@bailey2021gender; @herbst2020gender].
+However, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
@@
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility, a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest], to be related to a lower confidence in simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was associated with a higher number of faces judged as real.
-This is in line with recent research which found narcissists were less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and are more cognizant of external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest] - to be related to a lower confidence in simulation monitoring judgements.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
+This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and to be more vigilant and attentive to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
 
-Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], we confirm previous evidence of the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this correlation as related to a higher response assertiveness.
+Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
+Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this relationship as related to a higher response assertiveness.
 Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
@@
 
-Our findings suggest - though with weak significance - a positive link between paranoid ideation and the belief that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it could be that individuals with paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
-This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters [@freeman2005psychology].
+Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
+This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters [@freeman2005psychology].
 
@@
 
-<!-- given the known positive correlations between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia] -->
-
 <!-- In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
@@
 -->
-
-<!-- However, it is important to note that all of the aforementioned dispositional traits did only influence the confidence judgements, but not the simulation monitoring bias *per se*. -->
 
@@
 On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-This may be because shorter re-exposure delays, as opposed to longer delays, led to the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
+Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
 Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness [@sperduti2016paradox; @makowski2017being].
@@
 
-<!-- Conclusion -->
+<!-- Limitations -->
 
-Understanding the factors driving the reality beliefs pertaining to ambiguous stimuli is becoming increasingly pertinent given the rapid technological advances.
+Several limitations have to be noted.
 The current experimental paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements from influencing the other ratings).
@@
 Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
+Moreover, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
 
-The aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
+<!-- Conclusion -->
+
+In summary, the aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
 Notably, we found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-However, it has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
+We hope subsequent works to further our understanding of the factors driving the reality beliefs pertaining to ambiguous stimuli, an question becoming increasingly pertinent given the rapid technological advances.
 

### 2022-10-22 submission/manuscript.Rmd
knit

@@
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "4707"
+wordcount         : "4436"
 bibliography      : references.bib

### 2022-10-22 submission/manuscript.tex
knit

@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4707}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4436}
 \usepackage{lineno}
@@
 This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that a stimulus was artificially generated.
-The most striking result, in our opinion, is that despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding can be seen as a testimony not only to the effectiveness of our instructions, but also to the current expectations regarding CGI technology in the population, as well as to the volatility of our sense of reality.
-It underlines the strong impact of prior expectations and information on reality beliefs.
-In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting that a large part of it is associated with other subjective processes.
+Most strikingly, despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
+This finding not only attests to the effectiveness of our instructions, but highlights the current levels of expectation regarding CGI technology.
+The strong impact of prior expectations and information on reality beliefs demonstrated here underlines the volatility of our sense of reality.
+In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting a large contribution of other subjective processes.
 
@@
 The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
-In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that physical beauty only partially explains the role attractiveness plays in simulation monitoring decisions.
+In fact, female participants were more confident in judging faces as fake only when they were rated very high or low on beauty, suggesting that physical beauty and attractiveness are not analogous in their effects on simulation monitoring decisions.
 
@@
 
-Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions.
+Contrary to our hypothesis, we did not find familiarity to be significantly related to simulation monitoring decisions.
 Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-This could be taken into perspective with previous studies, which report females to be relatively superior at face recall and recognition (Lewin \& Herlitz, 2002; Mishra et al., 2019), displaying higher levels of facial memory (Sommer et al., 2013) and exhibiting greater metacognitive awareness (Kaplan, 2012).
-Hence, it is possible that the confidence in evaluating faces are less malleable to external factors such as face familiarity for females.
-Indeed, metacognitive awareness has been associated with overconfidence in making judgements (Klein et al., 2018; Mata et al., 2013).
-However, it should be noted that this has not been corroborated by recent research, which found males were significantly overconfident in face recall, regardless of their performance accuracy (Bailey, 2021; Herbst, 2020).
-Furthermore, the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females (Lewin \& Herlitz, 2002; Mishra et al., 2019; Sommer et al., 2013), as well as an overconfidence in face recall for males (Bailey, 2021; Herbst, 2020).
+However, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found that participants with higher scores of honesty-humility, a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012), displayed a lower confidence in their simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher number of faces judged as real.
-Indeed, this finding is in line with recent research suggesting that narcissists are more susceptible to fake news (Piksa et al., 2022; Sindermann et al., 2020), possibly because they were less likely to engage in cognitive strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020) and are more vigilant when attending to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
-As such, individuals with greater narcissistic tendencies could have perceived the face images as more salient, and engaged in less analytical reasoning, leading to their increased perceptions of the faces being real.
-
-Moreover, we put the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), thus confirming the evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
-Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this correlation as related to a higher response assertiveness.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012) - to be related to a lower confidence in simulation monitoring judgements.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
+This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
+
+Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
+Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this relationship as related to a higher response assertiveness.
 Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
 Alternatively, participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
+
+Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
+This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters (Freeman et al., 2005).
 
@@
 This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities (Said et al., 2022), hence permitting themselves to be more confident in their simulation monitoring decisions.
-This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (Said et al., 2022).
-
-Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it could thus be possible that stronger paranoid traits was associated with a greater perception of faces as salient and emotional, hence increasing their beliefs of its realness.
-This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment populated with virtual characters (Freeman et al., 2005).
-
-In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgements (J.
-T.-H.
-Chen \& Lovibond, 2016; Jensen et al., 2014).
-This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios (Jensen et al., 2014; Wei, 2021).
-Interestingly, no significant effect on individuals' perceptions of realness was observed despite uncertainty intolerance being commonly associated with enhanced threat appraisal (J.
-T.-H.
-Chen \& Lovibond, 2016; Jensen et al., 2014; Zheng et al., 2022).
-To this end, recent studies have attempted to disentangle the perception of threat from the experience of negative affect in ambiguous situations, conceptualising uncertainty intolerance as a response to unpredictability independent of threat altogether (Milne et al., 2019; Pepperdine et al., 2018).
-Taking this into perspective with the positive relations found between paranoid traits and beliefs of reality, future studies could clarify the role of threat appraisal on simulation monitoring processes, and attempt to delineate the specific mechanisms involved.
+In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (Said et al., 2022).
 
 On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-This may be because shorter re-exposure delays led to the faces being better remembered and appearing more familiar than faces that were displayed after a longer delay, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
-Indeed, this finding is in line with studies that show an up-regulation of emotions when fictional stimuli were associated with familiarity (Makowski et al., 2017; Sperduti et al., 2016), thus biasing its salience and perceived realness.
-If that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
+Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
+Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness (Makowski et al., 2017; Sperduti et al., 2016).
+However, if that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
 Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
 
-Understanding the factors driving the reality beliefs pertaining to ambiguous stimuli is becoming increasingly pertinent given the rapid technological advances.
-The aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
-We found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
-We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-
-Regarding the possible study limitations, the current paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements to influence the other ratings).
+Several limitations have to be noted.
+The current experimental paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements from influencing the other ratings).
 Although the effect of re-exposure delay was negligible, the potential bias induced by face familiarity (as compared to judging completely new items) cannot be discarded.
 Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
-It has to be noted that the magnitude of the effects found was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
-On top of exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces, or based on a gut feeling) to guide their reality beliefs.
+Moreover, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
+
+In summary, the aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
+Notably, we found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
+We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
+We hope subsequent works to further our understanding of the factors driving the reality beliefs pertaining to ambiguous stimuli, an question becoming increasingly pertinent given the rapid technological advances.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2016intolerance}{}}%
-Chen, J.
-T.-H., \& Lovibond, P.
-F.
-(2016).
-Intolerance of uncertainty is associated with increased threat appraisal and negative affect under ambiguity but not uncertainty.
-\emph{Behavior Therapy}, \emph{47}(1), 42--53.
-
 \leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-jensen2014intolerance}{}}%
-Jensen, D., Kind, A.
-J., Morrison, A.
-S., \& Heimberg, R.
-G.
-(2014).
-Intolerance of uncertainty and immediate decision-making in high-risk situations.
-\emph{Journal of Experimental Psychopathology}, \emph{5}(2), 178--190.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kaplan2012effect}{}}%
-Kaplan, S. (2012). \emph{The effect of gender on recalling facial features: Does our gender determine which features are encoded at first glance?}
-
 \leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
@@
 \emph{Journal of Applied Psychology and Social Science}, \emph{3}(2), 70--89.
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2018metacognitive}{}}%
-Klein, D., Cunningham, A., \& Buchanan, E.
-M.
-(2018).
-How metacognitive awareness relates to overconfidence in interval judgments.
-\emph{International Journal of Undergraduate Research and Creative Activities}, \emph{10}(1).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mata2013metacognitive}{}}%
-Mata, A., Ferreira, M.
-B., \& Sherman, S.
-J.
-(2013).
-The metacognitive advantage of deliberative thinkers: A dual-process perspective on overconfidence.
-\emph{Journal of Personality and Social Psychology}, \emph{105}(3), 353.
-
 \leavevmode\vadjust pre{\hypertarget{ref-mcdonnell2010face}{}}%
@@
 Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
-
-\leavevmode\vadjust pre{\hypertarget{ref-milne2019review}{}}%
-Milne, S., Lomax, C., \& Freeston, M. (2019). A review of the relationship between intolerance of uncertainty and threat appraisal in anxiety. \emph{The Cognitive Behaviour Therapist}, \emph{12}.
 
@@
 Pennycook, G., \& Rand, D. G. (2019). Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning. \emph{Cognition}, \emph{188}, 39--50.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pepperdine2018disentangling}{}}%
-Pepperdine, E., Lomax, C., \& Freeston, M. (2018). Disentangling intolerance of uncertainty and threat appraisal in everyday situations. \emph{Journal of Anxiety Disorders}, \emph{57}, 31--38.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-wei2021confidence}{}}%
-Wei, L. (2021). \emph{Confidence and information seeking in decision making under uncertainty} {[}PhD thesis{]}. University of Oxford.
-
 \leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zheng2022worry}{}}%
-Zheng, S., Marcos, M., Stewart, K.
-E., Szabo, J., Pawluk, E., Girard, T.
-A., \& Koerner, N.
-(2022).
-Worry, intolerance of uncertainty, negative urgency, and their associations to paranoid thinking.
-\emph{Personality and Individual Differences}, \emph{186}, 111382.
-
 \end{CSLReferences}

### 2022-11-07 submission/manuscript.Rmd
psych science

@@
 abstract: |
-  Technological advances make the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, and the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+  Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
 In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
-The stimuli were then presented again with the new information that a number of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
+The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
 Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as "fake".
@@
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
+
+  **Statement of relevance.** Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
+Given the evolutionary importance of perceived attractiveness, we investigated if faces rated as more attractive would be more likely judged as real (vs "fake", i.e., artificially generated).
+We indeed found a gender-dependent role of attractiveness on reality judgements, as well as a global influence of personality traits such as narcissism.
+These results are discussed in the light of consciousness psychology and evolutionary science, and are relevant to AI-researchers and misinformation management agencies.
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "4436"
+wordcount         : "4428"
 bibliography      : references.bib
@@
 draft             : no
-mask              : no
+mask              : yes
 figurelist        : yes
@@
 
-In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
+In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/MaskedForReview**](https://github.com/RealityBending/FakeFace){.uri}.
 
@@
 The points are the average per participant confidence for both types of judgements.
-Stars indicate significance (p < .001***, p < .01**, p < .05*)", out.width="100%"}
+Stars indicate significance (p < .001***, p < .01**, p < .05*).", out.width="100%"}
 knitr::include_graphics("../figures/Figure2.png")
@@
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-We hope subsequent works to further our understanding of the factors driving the reality beliefs pertaining to ambiguous stimuli, an question becoming increasingly pertinent given the rapid technological advances.
+We believe that these findings provide the foundations to help us understand what drives reality beliefs in an increasingly reality-ambiguous world.
 
@@
 
-This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
+This work was supported by **[masked for review]**
+<!-- This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
+-->
 
@@
 
-We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
+**[masked for review]**
+<!-- We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials. -->
 

### 2022-11-07 submission/manuscript.tex
psych science

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,mask,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4436}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4428}
 \usepackage{lineno}
@@
   pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
-  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
   pdflang={en-EN},
@@
 \abstract{%
-Technological advances make the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, and the factors that drive our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
 In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
-The stimuli were then presented again with the new information that a number of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
+The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
 Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as ``fake''.
@@
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
+
+\textbf{Statement of relevance.} Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
+Given the evolutionary importance of perceived attractiveness, we investigated if faces rated as more attractive would be more likely judged as real (vs ``fake'', i.e., artificially generated).
+We indeed found a gender-dependent role of attractiveness on reality judgements, as well as a global influence of personality traits such as narcissism.
+These results are discussed in the light of consciousness psychology and evolutionary science, and are relevant to AI-researchers and misinformation management agencies.
 }
@@
 
-In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
+In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/MaskedForReview}}.
 
@@
 The points are the average per participant confidence for both types of judgements.
-Stars indicate significance (p < .001***, p < .01**, p < .05*)}\label{fig:unnamed-chunk-3}
+Stars indicate significance (p < .001***, p < .01**, p < .05*).}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister's Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
+This work was supported by \textbf{{[}masked for review{]}}
 
@@
 
-We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
+\textbf{{[}masked for review{]}}
 

### 2022-11-10 submission/manuscript.Rmd
scirep

@@
     role:
+      - "Data curation"
       - "Project administration"
@@
 
-  **Statement of relevance.** Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
+  **Significance Statement.** Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
 Given the evolutionary importance of perceived attractiveness, we investigated if faces rated as more attractive would be more likely judged as real (vs "fake", i.e., artificially generated).
@@
 These results are discussed in the light of consciousness psychology and evolutionary science, and are relevant to AI-researchers and misinformation management agencies.
+
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
@@
 draft             : no
-mask              : yes
+mask              : no
 figurelist        : yes
@@
 output            : papaja::apa6_pdf
-csl: utils/apa.csl
+csl: utils/scientific-reports.csl
 header-includes:
@@
 
-While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images) [@mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
 Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
@@
 
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2018cognitive; @makowski2019phenomenal].
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as *simulation monitoring*) [@makowski2018cognitive; @makowski2019phenomenal].
 With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
@@
 This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory [outlined in @makowski2018cognitive; @makowski2019phenomenal], which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+Based on the embodied reality theory
+[@makowski2018cognitive; @makowski2019phenomenal],
+<!-- [outlined in @makowski2018cognitive; @makowski2019phenomenal], -->
+which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
@@
 
-In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/MaskedForReview**](https://github.com/RealityBending/FakeFace){.uri}.
+In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
 
@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* [24 items, @sibley2011] measuring 6 personality traits, the *SIAS-6* and the *SPS-6* [6 items each, @peters2012development] assessing social anxiety levels, the *FFNI-BF* [30 items, @jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS* [18 items, @freeman2021revised] measuring 2 dimensions related to paranoid thinking; and the *IUS-12* [12 items, @carleton2007fearing] measuring intolerance to uncertainty.
-Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness ("How attractive would you say you are?", @marcinkowska2021self) and the other measuring physical attractiveness ("How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive).
+In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* 
+(24 items) [@sibley2011] 
+<!-- [24 items, @sibley2011]  -->
+measuring 6 personality traits, the *SIAS-6* and the *SPS-6* 
+(6 items each) [@peters2012development]
+<!-- [6 items each, @peters2012development]  -->
+assessing social anxiety levels, the *FFNI-BF* 
+(30 items) [@jauk2022validation]
+<!-- [30 items, @jauk2022validation]  -->
+measuring 9 facets of narcissism; the *R-GPTS* 
+(18 items) [@freeman2021revised]
+<!-- [18 items, @freeman2021revised]  -->
+measuring 2 dimensions related to paranoid thinking; and the *IUS-12* 
+(12 items) [@carleton2007fearing]
+<!-- [12 items, @carleton2007fearing]  -->
+measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness 
+("How attractive would you say you are?") [@marcinkowska2021self]
+<!-- ["How attractive would you say you are?", @marcinkowska2021self] -->
+and the other measuring physical attractiveness 
+("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive]
+<!-- ["How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive].  -->
 Finally, we devised 5 items pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
-To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale [*GAAIS*, @schepman2020initial].
-This scale was presented after the social anxiety questionnaires.
-3 attention check questions were also embedded in the surveys.
+To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale
+(*GAAIS*) [@schepman2020initial].
+<!-- [*GAAIS*, @schepman2020initial].  -->
+This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.
 
-In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database (AMFD, [@chen2021broadening]) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
+In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database 
+(AMFD) [@chen2021broadening] 
+<!-- [AMFD, @chen2021broadening]  -->
+were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales.
@@
 It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [e.g., heart rate deceleration, @skora2022functional].
-
-<!-- even after adjusting for the effects of trustworthiness and familiarity; both characteristics that are evolutionarily advantageous [@hou2019survival; @little2011facial]. A -->
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers
+(e.g., heart rate deceleration) [@skora2022functional].
+<!-- [e.g., heart rate deceleration, @skora2022functional]. -->
 
@@
 Given prior evidence that faces presented as computer-generated were rated less trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a linear association to be more clearly present for both genders.
-One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females
+(explained evolutionarily as a compromise to their reproductive potential [@van2020sex]),
+<!-- [explained evolutionarily as a compromise to their reproductive potential, @van2020sex],  -->
+to which perceived facial trustworthiness relates [@hou2019survival].
 However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
@@
 This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters [@freeman2005psychology].
-
-<!-- In contrast, intolerance to uncertainty, a trait related to aversion towards unpredictable situations, was found to be negatively correlated to individuals' confidence in real judgements [@chen2016intolerance; @jensen2014intolerance].
-This is consistent with previous reports that uncertainty intolerance correlates with under-confidence in decision-making in ambiguous scenarios [@wei2021confidence; @jensen2014intolerance].
-Interestingly, no significant effect on individuals' perceptions of realness was observed despite uncertainty intolerance being commonly associated with enhanced threat appraisal [@zheng2022worry; @chen2016intolerance; @jensen2014intolerance].
-To this end, recent studies have attempted to disentangle the perception of threat from the experience of negative affect in ambiguous situations, conceptualising uncertainty intolerance as a response to unpredictability independent of threat altogether [@pepperdine2018disentangling; @milne2019review].
-Taking this into perspective with the positive relations found between paranoid traits and beliefs of reality, future studies could clarify the role of threat appraisal on simulation monitoring processes, and attempt to delineate the specific mechanisms involved.
--->
-
-<!-- In fact, the only trait that modulated the tendency to rate an image as fake or real was the social phobia score, whereby low values were associated with an increased tendency to judge faces as real.
-Social phobia being characterized as a heightened fear in social interaction contexts [@kolassa2006psychophysiological; @ran2017impact], the nature of the stimuli - pictures of faces - could play a role in this association.
-However, given the fact that neutral faces are perceived as more threatening by participants with high social phobia [@yoon2008interpreting; @staugaard2010threatening; @peschard2017overestimation], and thus likely more salient, we would have expected high social phobia tendencies to be associated with a bias towards reality judgement.
-This apparent contradiction could be explained through the lens of fictional reappraisal,  **TODO: can you double check that this last statement is correct?**.
--->
 
@@
 
+# Data Availability
+
+The datasets generated and/or analysed during the current study are available in the GitHub repository https://github.com/RealityBending/FakeFace
+
 # Funding
 
-This work was supported by **[masked for review]**
-<!-- This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
--->
+This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
 
@@
 
-**[masked for review]**
-<!-- We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials. -->
+We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
 

### 2022-11-10 submission/manuscript.tex
scirep

--- 2022-10-22 submission/manuscript.tex
@@
 The authors made the following contributions.
-Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Ngoi Zi Liang: Project administration, Resources, Writing -- review \& editing; Panagiotis Mavros: Supervision, Writing -- review \& editing; S.H.
+Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Data curation, Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Ngoi Zi Liang: Project administration, Resources, Writing -- review \& editing; Panagiotis Mavros: Supervision, Writing -- review \& editing; S.H.
 Annabel Chen: Project administration, Supervision, Writing -- review \& editing.
@@
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
+
+\textbf{Significance Statement.} Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
+Given the evolutionary importance of perceived attractiveness, we investigated if faces rated as more attractive would be more likely judged as real (vs ``fake'', i.e., artificially generated).
+We indeed found a gender-dependent role of attractiveness on reality judgements, as well as a global influence of personality traits such as narcissism.
+These results are discussed in the light of consciousness psychology and evolutionary science, and are relevant to AI-researchers and misinformation management agencies.
 }
@@
 For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
-Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
-This issue is central to what has been coined the ``post-truth era'' (Lewandowsky et al., 2017), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
-
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
+These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access\textsuperscript{1}.
+Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination\textsuperscript{2}.
+This issue is central to what has been coined the ``post-truth era''\textsuperscript{3}, in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
+
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images)\textsuperscript{4}, it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation\textsuperscript{1,5,6}.
 Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
 
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, Makowski, 2018; Makowski, Sperduti, et al., 2019).
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
-However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
-Chen et al., 2015).
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring})\textsuperscript{7,8}.
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy\textsuperscript{9,10}, people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation\textsuperscript{9--11}.
+However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult\textsuperscript{12,13}.
 Thus, in the absence of clear contextual information, what drives our beliefs of reality?
@@
 
-Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
-For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019), and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations (Britt et al., 2019).
-Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
+Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits\textsuperscript{14--16}.
+For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli\textsuperscript{17,18}, and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations\textsuperscript{19}.
+Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news\textsuperscript{16,20}.
 
 Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005).
-Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
-Additionally, other factors, such as the stimuli's perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in guiding our appraisal of a stimulus.
-
-AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
-Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real (Tucciarelli et al., 2020).
-Conversely, Liefooghe et al.
-(2022) reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
+For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment\textsuperscript{21,22}.
+Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation\textsuperscript{8,23}.
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief\textsuperscript{24,25}.
+Additionally, other factors, such as the stimuli's perceived self-relevance\textsuperscript{26,27}, as well as familiarity\textsuperscript{28}, could also play a role in guiding our appraisal of a stimulus.
+
+AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness\textsuperscript{29--32}.
+Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real\textsuperscript{5}.
+Conversely,\textsuperscript{33} reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
 Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
@@
 This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory (outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019), which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
-We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
+Based on the embodied reality theory\textsuperscript{7,8},
+which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness\textsuperscript{33--36}, and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6} (24 items, Sibley et al., 2011) measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6} (6 items each, Peters et al., 2012) assessing social anxiety levels, the \emph{FFNI-BF} (30 items, Jauk et al., 2022) measuring 9 facets of narcissism; the \emph{R-GPTS} (18 items, Freeman et al., 2021) measuring 2 dimensions related to paranoid thinking; and the \emph{IUS-12} (12 items, Carleton et al., 2007) measuring intolerance to uncertainty.
-Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness (``How attractive would you say you are?'', Marcinkowska et al.
-(2021)) and the other measuring physical attractiveness (``How would you rate your own physical attractiveness relative to the average'', Spielmann et al.
-(2020)).
+In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6}
+(24 items)\textsuperscript{37}
+measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6}
+(6 items each)\textsuperscript{38}
+assessing social anxiety levels, the \emph{FFNI-BF}
+(30 items)\textsuperscript{39}
+measuring 9 facets of narcissism; the \emph{R-GPTS}
+(18 items)\textsuperscript{40}
+measuring 2 dimensions related to paranoid thinking; and the \emph{IUS-12}
+(12 items)\textsuperscript{41}
+measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness
+(``How attractive would you say you are?'')\textsuperscript{42}
+and the other measuring physical attractiveness
+(``How would you rate your own physical attractiveness relative to the average'')\textsuperscript{43}
 Finally, we devised 5 items pertaining to expectations about AI-generated image technology (``I think current Artificial Intelligence algorithms can generate very realistic images'').
-To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale (\emph{GAAIS}, Schepman \& Rodway, 2020).
-This scale was presented after the social anxiety questionnaires.
-3 attention check questions were also embedded in the surveys.
-
-In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database (AMFD, (J.
-M.
-Chen et al., 2021)) were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
+To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale
+(\emph{GAAIS})\textsuperscript{44}.
+This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.
+
+In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database
+(AMFD)\textsuperscript{45}
+were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of \emph{Trustworthiness} (``I find this person trustworthy'') and \emph{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we assessed attractiveness using 2 visual analog scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects\textsuperscript{46,47}, we assessed attractiveness using 2 visual analog scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
 
@@
 This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with \emph{Fake} and \emph{Real} as the two extremes).
-The study was implemented using \emph{jsPsych} (De Leeuw, 2015), and the exact instructions are available in the experiment code.
+The study was implemented using \emph{jsPsych}\textsuperscript{48}, and the exact instructions are available in the experiment code.
 
@@
 
-One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data (Peer et al., 2022).
+One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data\textsuperscript{49}.
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 The points are the average per participant confidence for both types of judgements.
-Stars indicate significance (p < .001***, p < .01**, p < .05*)}\label{fig:unnamed-chunk-3}
+Stars indicate significance (p < .001***, p < .01**, p < .05*).}\label{fig:unnamed-chunk-3}
 \end{figure}
 
-The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski et al., 2020; Makowski, Ben-Shachar, et al., 2019).
+The analysis was carried out using \emph{R 4.2}\textsuperscript{50}, the \emph{tidyverse}\textsuperscript{51}, and the \emph{easystats} collection of packages\textsuperscript{52--56}.
 As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant (\(p <.01\)).
@@
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women\textsuperscript{57,58}.
 In fact, female participants were more confident in judging faces as fake only when they were rated very high or low on beauty, suggesting that physical beauty and attractiveness are not analogous in their effects on simulation monitoring decisions.
@@
 Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
-Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \& Ying, 2022).
+Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities\textsuperscript{57--59}.
 It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers (e.g., heart rate deceleration, Skora et al., 2022).
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging\textsuperscript{60,61} or physiological markers
+(e.g., heart rate deceleration)\textsuperscript{62}.
 
 Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
-Given prior evidence that faces presented as computer-generated were rated less trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such a linear association to be more clearly present for both genders.
-One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females (explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
+Given prior evidence that faces presented as computer-generated were rated less trustworthy\textsuperscript{30,33,63}, we expected such a linear association to be more clearly present for both genders.
+One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females
+(explained evolutionarily as a compromise to their reproductive potential\textsuperscript{64}),
+to which perceived facial trustworthiness relates\textsuperscript{65}.
 However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
@@
 Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females (Lewin \& Herlitz, 2002; Mishra et al., 2019; Sommer et al., 2013), as well as an overconfidence in face recall for males (Bailey, 2021; Herbst, 2020).
+Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females\textsuperscript{66--68}, as well as an overconfidence in face recall for males\textsuperscript{69,70}.
 However, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
@@
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012) - to be related to a lower confidence in simulation monitoring judgements.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion\textsuperscript{71,72} - to be related to a lower confidence in simulation monitoring judgements.
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
-This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
-
-Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
+This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking\textsuperscript{73,74}, and to be more vigilant and attentive to external stimuli\textsuperscript{75--77}.
+
+Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism\textsuperscript{78}, we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making\textsuperscript{79--82}.
 Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this relationship as related to a higher response assertiveness.
@@
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
-This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters (Freeman et al., 2005).
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat\textsuperscript{83--85}, it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
+This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters\textsuperscript{86}.
 
@@
 Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
-This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities (Said et al., 2022), hence permitting themselves to be more confident in their simulation monitoring decisions.
-In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (Said et al., 2022).
+This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities\textsuperscript{87}, hence permitting themselves to be more confident in their simulation monitoring decisions.
+In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications\textsuperscript{87}.
 
 On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
-Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness (Makowski et al., 2017; Sperduti et al., 2016).
+Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display\textsuperscript{88--90}.
+Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness\textsuperscript{22,26}.
 However, if that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
@@
 We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-We hope subsequent works to further our understanding of the factors driving the reality beliefs pertaining to ambiguous stimuli, an question becoming increasingly pertinent given the rapid technological advances.
+We believe that these findings provide the foundations to help us understand what drives reality beliefs in an increasingly reality-ambiguous world.
+
+\hypertarget{data-availability}{%
+\section{Data Availability}\label{data-availability}}
+
+The datasets generated and/or analysed during the current study are available in the GitHub repository \url{https://github.com/RealityBending/FakeFace}
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-nightingale2022}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Nightingale, S.
+J.
+\& Farid, H.
+\href{https://doi.org/10.1073/pnas.2120481119}{AI-synthesized faces are indistinguishable from real faces and more trustworthy}.
+\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2120481119 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Pantserev, K.
+The malicious use of AI-based deepfake technology as the new threat to psychological security and political stability.
+in 37--55 (2020).
+doi:\href{https://doi.org/10.1007/978-3-030-35746-7_3}{10.1007/978-3-030-35746-7\_3}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2017beyond}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Lewandowsky, S., Ecker, U.
+K.
+\& Cook, J.
+Beyond misinformation: Understanding and coping with the {`post-truth'} era.
+\emph{Journal of applied research in memory and cognition} \textbf{6}, 353--369 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcdonnell2010face}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{McDonnell, R. \& Breidt, M. Face reality: Investigating the uncanny valley for virtual faces. in \emph{ACM SIGGRAPH ASIA 2010 sketches} 1--2 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Tucciarelli, R., Vehar, N.
+\& Tsakiris, M.
+\emph{On the realness of people who do not exist: the social processing of artificial faces}.
+\url{https://osf.io/dnk9x} (2020) doi:\href{https://doi.org/10.31234/osf.io/dnk9x}{10.31234/osf.io/dnk9x}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moshel2022}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Moshel, M.
+L., Robinson, A.
+K., Carlson, T.
+A.
+\& Grootswagers, T.
+\href{https://doi.org/10.1016/j.visres.2022.108079}{Are you for real?
+Decoding realistic AI-generated faces from neural activity}.
+\emph{Vision Research} \textbf{199}, 108079 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2018cognitive}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Makowski, D. Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal. (Sorbonne Paris Cit{é}, 2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Makowski, D.
+\emph{et al.} Phenomenal, bodily and brain correlates of fictional reappraisal as an implicit emotion regulation strategy.
+\emph{Cognitive, Affective, \& Behavioral Neuroscience} \textbf{19}, 877--897 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-michael2021source}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Michael, R. B. \& Sanson, M. Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies} \textbf{11}, 119 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-susmann2021persuasion}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Susmann, M. W. \emph{et al.} Persuasion amidst a pandemic: Insights from the elaboration likelihood model. \emph{European Review of Social Psychology} 1--37 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-petty1986elaboration}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Petty, R. E. \& Cacioppo, J. T. The elaboration likelihood model of persuasion. in \emph{Communication and persuasion} 1--24 (Springer, 1986).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-berghel2018weaponizing}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Berghel, H. Weaponizing twitter litter: Abuse-forming networks and social media. \emph{Computer} \textbf{51}, 70--73 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Chen, Y., Conroy, N.
+K.
+\& Rubin, V.
+L.
+News in an online world: The need for an {`automatic crap detector'}.
+\emph{Proceedings of the Association for Information Science and Technology} \textbf{52}, 1--4 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Bryanov, K. \& Vziatysheva, V. Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS one} \textbf{16}, e0253717 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ecker2022psychological}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Ecker, U. K. \emph{et al.} The psychological drivers of misinformation belief and its resistance to correction. \emph{Nature Reviews Psychology} \textbf{1}, 13--29 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sindermann2020short}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Sindermann, C., Cooper, A. \& Montag, C. A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology} \textbf{36}, 44--48 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pehlivanoglu2021role}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Pehlivanoglu, D.
+\emph{et al.} The role of analytical reasoning and source credibility on the evaluation of real and fake full-length news articles.
+\emph{Cognitive research: principles and implications} \textbf{6}, 1--12 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pennycook2019lazy}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Pennycook, G.
+\& Rand, D.
+G.
+Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning.
+\emph{Cognition} \textbf{188}, 39--50 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Britt, M.
+A., Rouet, J.-F., Blaum, D.
+\& Millis, K.
+A reasoned approach to dealing with fake news.
+\emph{Policy Insights from the Behavioral and Brain Sciences} \textbf{6}, 94--101 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Piksa, M. \emph{et al.} Cognitive processes and personality traits underlying four phenotypes of susceptibility to (mis) information. \emph{Frontiers in psychiatry} 1142 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Sanchez-Vives, M. V. \& Slater, M. From presence to consciousness through virtual reality. \emph{Nature Reviews Neuroscience} \textbf{6}, 332--339 (2005).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2017being}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Makowski, D., Sperduti, M., Nicolas, S.
+\& Piolino, P.
+{`Being there'} and remembering it: Presence improves memory encoding.
+\emph{Consciousness and cognition} \textbf{53}, 194--202 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperduti2017distinctive}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Sperduti, M. \emph{et al.} The distinctive role of executive functions in implicit emotion regulation. \emph{Acta Psychologica} \textbf{173}, 13--20 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Martel, C., Pennycook, G. \& Rand, D. G. Reliance on emotion promotes belief in fake news. \emph{Cognitive research: principles and implications} \textbf{5}, 1--20 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Bago, B., Rosenzweig, L.
+R., Berinsky, A.
+J.
+\& Rand, D.
+G.
+Emotion may predict susceptibility to fake news but emotion regulation does not seem to help.
+\emph{Cognition and Emotion} 1--15 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperduti2016paradox}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Sperduti, M. \emph{et al.} The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance. \emph{Acta psychologica} \textbf{165}, 53--59 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Goldstein, T.
+R.
+The pleasure of unadulterated sadness: Experiencing sorrow in fiction, nonfiction, and" in person.".
+\emph{Psychology of Aesthetics, Creativity, and the Arts} \textbf{3}, 232 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-begg1992dissociation}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Begg, I.
+M., Anas, A.
+\& Farinacci, S.
+Dissociation of processes in belief: Source recollection, statement familiarity, and the illusion of truth.
+\emph{Journal of Experimental Psychology: General} \textbf{121}, 446 (1992).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Sobieraj, S.
+\& Krämer, N.
+C.
+What is beautiful in cyberspace?
+Communication with attractive avatars.
+in \emph{International conference on social computing and social media} 125--136 (Springer, 2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-balas2017}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Balas, B.
+\& Pacella, J.
+\href{https://doi.org/10.1016/j.chb.2017.08.045}{Trustworthiness perception is disrupted in artificial faces}.
+\emph{Computers in Human Behavior} \textbf{77}, (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tsikandilakis2019beauty}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Tsikandilakis, M., Bali, P.
+\& Chapman, P.
+Beauty is in the eye of the beholder: The appraisal of facial attractiveness and its relation to conscious awareness.
+\emph{Perception} \textbf{48}, 72--92 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Calbi, M.
+\emph{et al.} \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2017.01684}{How context influences our perception of emotional faces: A behavioral study on the kuleshov effect}.
+\emph{Frontiers in Psychology} \textbf{8}, (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Liefooghe, B. \emph{et al.} Faces merely labelled as artificial are trusted less. (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Bartosik, B., Wojcik, G.
+M., Brzezicka, A.
+\& Kawiak, A.
+Are you able to trust me?
+Analysis of the relationships between personality traits and the assessment of attractiveness and trust.
+\emph{Frontiers in Human Neuroscience} \textbf{15}, 685530 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Garrido, M.
+V.
+\& Prada, M.
+KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces.
+\emph{Frontiers in Psychology} \textbf{8}, 2181 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-little2011facial}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Little, A.
+C., Jones, B.
+C.
+\& DeBruine, L.
+M.
+Facial attractiveness: Evolutionary based research.
+\emph{Philosophical Transactions of the Royal Society B: Biological Sciences} \textbf{366}, 1638--1659 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Sibley, C.
+\emph{et al.} The mini-IPIP6: Validation and extension of a short measure of the big-six factors of personality in new zealand.
+\emph{New Zealand Journal of Psychology} \textbf{40}, 142--159 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{Peters, L., Sunderland, M., Andrews, G., Rapee, R.
+M.
+\& Mattick, R.
+P.
+Development of a short form social interaction anxiety (SIAS) and social phobia scale (SPS) using nonparametric item response theory: The SIAS-6 and the SPS-6.
+\emph{Psychological assessment} \textbf{24}, 66 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Jauk, E., Olaru, G., Schürch, E., Back, M.
+D.
+\& Morf, C.
+C.
+Validation of the german five-factor narcissism inventory and construction of a brief form using ant colony optimization.
+\emph{Assessment} 10731911221075761 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2021revised}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Freeman, D.
+\emph{et al.} The revised green et al., Paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
+\emph{Psychological Medicine} \textbf{51}, 244--253 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Carleton, R.
+N., Norton, M.
+P.
+J.
+\& Asmundson, G.
+J.
+Fearing the unknown: A short version of the intolerance of uncertainty scale.
+\emph{Journal of anxiety disorders} \textbf{21}, 105--117 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-marcinkowska2021self}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{Marcinkowska, U.
+M., Jones, B.
+C.
+\& Lee, A.
+J.
+Self-rated attractiveness predicts preferences for sexually dimorphic facial characteristics in a culturally diverse sample.
+\emph{Scientific Reports} \textbf{11}, 1--8 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-spielmann2020predictive}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Spielmann, S.
+S., Maxwell, J.
+A., MacDonald, G., Peragine, D.
+\& Impett, E.
+A.
+The predictive effects of fear of being single on physical attractiveness and less selective partner selection strategies.
+\emph{Journal of Social and Personal Relationships} \textbf{37}, 100--123 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schepman2020initial}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Schepman, A. \& Rodway, P. Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in human behavior reports} \textbf{1}, 100014 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021broadening}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Chen, J. M., Norman, J. B. \& Nam, Y. Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods} \textbf{53}, 371--389 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{Rhodes, G. \emph{et al.} The evolutionary psychology of facial beauty. \emph{Annual review of psychology} \textbf{57}, 199 (2006).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{Han, S.
+\emph{et al.} Beauty is in the eye of the beholder: The halo effect and generalization effect in the facial attractiveness evaluation.
+\emph{Acta Psychologica Sinica} \textbf{50}, 363 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{De Leeuw, J. R. jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior research methods} \textbf{47}, 1--12 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peer2022}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{Peer, E., Rothschild, D., Gordon, A., Evernden, Z.
+\& Damer, E.
+\href{https://doi.org/10.3758/s13428-021-01694-3}{Data quality of platforms and panels for online behavioral research}.
+\emph{Behavior Research Methods} \textbf{54}, 1643--1662 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{Wickham, H. \emph{et al.} \href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}. \emph{Journal of Open Source Software} \textbf{4}, 1686 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
+\CSLLeftMargin{52. }%
+\CSLRightInline{Lüdecke, D., Waggoner, P.
+\& Makowski, D.
+\href{https://doi.org/10.21105/joss.01412}{Insight: A unified interface to access information from model objects in {R}}.
+\emph{JOSS} \textbf{4}, 1412 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Makowski, D., Ben-Shachar, M.
+\& Lüdecke, D.
+\href{https://doi.org/10.21105/joss.01541}{{bayestestR}: Describing effects and their uncertainty, existence and significance within the {Bayesian} framework}.
+\emph{JOSS} \textbf{4}, 1541 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P.
+\& Makowski, D.
+\href{https://doi.org/10.21105/joss.03139}{{performance}: An {R} package for assessment, comparison and testing of statistical models}.
+\emph{JOSS} \textbf{6}, 3139 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-parametersArticle}{}}%
+\CSLLeftMargin{55. }%
+\CSLRightInline{Lüdecke, D., Ben-Shachar, M., Patil, I.
+\& Makowski, D.
+\href{https://doi.org/10.21105/joss.02445}{Extracting, computing and exploring the parameters of statistical models using {R}}.
+\emph{JOSS} \textbf{5}, 2445 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
+\CSLLeftMargin{56. }%
+\CSLRightInline{Makowski, D., Ben-Shachar, M., Patil, I.
+\& Lüdecke, D.
+\href{https://doi.org/10.21105/joss.02306}{Methods and algorithms for correlation analysis in {R}}.
+\emph{JOSS} \textbf{5}, 2306 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buunk2002age}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{Buunk, B.
+P., Dijkstra, P., Fetchenhauer, D.
+\& Kenrick, D.
+T.
+Age and gender differences in mate selection criteria for various involvement levels.
+\emph{Personal relationships} \textbf{9}, 271--278 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
+\CSLLeftMargin{58. }%
+\CSLRightInline{Qi, Y. \& Ying, J. Gender biases in the accuracy of facial judgments: Facial attractiveness and perceived socioeconomic status. \emph{Frontiers in Psychology} \textbf{13}, (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Fink, B., Neave, N., Manning, J.
+T.
+\& Grammer, K.
+Facial symmetry and judgements of attractiveness, health and personality.
+\emph{Personality and Individual differences} \textbf{41}, 491--499 (2006).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lou2015perceptual}{}}%
+\CSLLeftMargin{60. }%
+\CSLRightInline{Lou, B., Hsu, W.-Y.
+\& Sajda, P.
+Perceptual salience and reward both influence feedback-related neural activity arising from choice.
+\emph{Journal of Neuroscience} \textbf{35}, 13064--13075 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-indovina2007dissociation}{}}%
+\CSLLeftMargin{61. }%
+\CSLRightInline{Indovina, I. \& Macaluso, E. Dissociation of stimulus relevance and saliency factors during shifts of visuospatial attention. \emph{Cerebral Cortex} \textbf{17}, 1701--1711 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-skora2022functional}{}}%
+\CSLLeftMargin{62. }%
+\CSLRightInline{Skora, L., Livermore, J. \& Roelofs, K. The functional role of cardiac activity in perception and action. \emph{Neuroscience \& Biobehavioral Reviews} 104655 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hoogers2021effect}{}}%
+\CSLLeftMargin{63. }%
+\CSLRightInline{Hoogers, E. The effect of attitude towards computer generated faces on face perception. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2020sex}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Van Den Akker, O.
+R., Assen, M.
+A.
+van, Van Vugt, M.
+\& Wicherts, J.
+M.
+Sex differences in trust and trustworthiness: A meta-analysis of the trust game and the gift-exchange game.
+\emph{Journal of Economic Psychology} \textbf{81}, 102329 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hou2019survival}{}}%
+\CSLLeftMargin{65. }%
+\CSLRightInline{Hou, C.
+\& Liu, Z.
+The survival processing advantage of face: The memorization of the (un) trustworthy face contributes more to survival adaptation.
+\emph{Evolutionary Psychology} \textbf{17}, 1474704919839726 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mishra2019gender}{}}%
+\CSLLeftMargin{66. }%
+\CSLRightInline{Mishra, M. V. \emph{et al.} Gender differences in familiar face recognition and the influence of sociocultural gender inequality. \emph{Scientific reports} \textbf{9}, 1--12 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lewin2002sex}{}}%
+\CSLLeftMargin{67. }%
+\CSLRightInline{Lewin, C. \& Herlitz, A. Sex differences in face recognition---women's faces make the difference. \emph{Brain and cognition} \textbf{50}, 121--128 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sommer2013sex}{}}%
+\CSLLeftMargin{68. }%
+\CSLRightInline{Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A. \& Wilhelm, O. Sex differences in face cognition. \emph{Acta psychologica} \textbf{142}, 62--73 (2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bailey2021gender}{}}%
+\CSLLeftMargin{69. }%
+\CSLRightInline{Bailey, A. A gender in-group effect on facial recall. (University of Tasmania, 2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-herbst2020gender}{}}%
+\CSLLeftMargin{70. }%
+\CSLRightInline{Herbst, T.
+H.
+Gender differences in self-perception accuracy: The confidence gap and women leaders' underrepresentation in academia.
+\emph{SA Journal of Industrial Psychology} \textbf{46}, 1--8 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
+\CSLLeftMargin{71. }%
+\CSLRightInline{Levidi, M.
+D.
+C., McGrath, A., Kyriakoulis, P.
+\& Sulikowski, D.
+Understanding criminal decision-making: Links between honesty-humility, perceived risk and negative affect: Psychology, crime \& law.
+\emph{Psychology, Crime and Law} 1--29 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
+\CSLLeftMargin{72. }%
+\CSLRightInline{Weller, J.
+A.
+\& Thulin, E.
+W.
+Do honest people take fewer risks?
+Personality correlates of risk-taking to achieve gains and avoid losses in HEXACO space.
+\emph{Personality and individual differences} \textbf{53}, 923--926 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-littrell2020overconfidently}{}}%
+\CSLLeftMargin{73. }%
+\CSLRightInline{Littrell, S., Fugelsang, J.
+\& Risko, E.
+F.
+Overconfidently underthinking: Narcissism negatively predicts cognitive reflection.
+\emph{Thinking \& Reasoning} \textbf{26}, 352--380 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ahadzadeh2021social}{}}%
+\CSLLeftMargin{74. }%
+\CSLRightInline{Ahadzadeh, A.
+S., Ong, F.
+S.
+\& Wu, S.
+L.
+Social media skepticism and belief in conspiracy theories about COVID-19: The moderating role of the dark triad.
+\emph{Current Psychology} 1--13 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carolan2017searching}{}}%
+\CSLLeftMargin{75. }%
+\CSLRightInline{Carolan, P.
+L.
+Searching {`inaffectively'}: A behavioral, psychometric, and electroencephalographic investigation of psychopathic personality and visual-spatial attention.
+(Arts \& Social Sciences: Department of Psychology, 2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grapsas2020and}{}}%
+\CSLLeftMargin{76. }%
+\CSLRightInline{Grapsas, S., Brummelman, E., Back, M.
+D.
+\& Denissen, J.
+J.
+The {`why'} and {`how'} of narcissism: A process model of narcissistic status pursuit.
+\emph{Perspectives on Psychological Science} \textbf{15}, 150--172 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eddy2021self}{}}%
+\CSLLeftMargin{77. }%
+\CSLRightInline{Eddy, C. M. Self-serving social strategies: A systematic review of social cognition in narcissism. \emph{Current Psychology} 1--19 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hodson2018dark}{}}%
+\CSLLeftMargin{78. }%
+\CSLRightInline{Hodson, G. \emph{et al.} Is the dark triad common factor distinct from low honesty-humility? \emph{Journal of Research in Personality} \textbf{73}, 123--129 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-campbell2004narcissism}{}}%
+\CSLLeftMargin{79. }%
+\CSLRightInline{Campbell, W. K., Goodie, A. S. \& Foster, J. D. Narcissism, confidence, and risk attitude. \emph{Journal of behavioral decision making} \textbf{17}, 297--311 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
+\CSLLeftMargin{80. }%
+\CSLRightInline{Chatterjee, A. \& Pollock, T. G. Master of puppets: How narcissistic CEOs construct their professional worlds. \emph{Academy of Management Review} \textbf{42}, 703--725 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunell2017narcissism}{}}%
+\CSLLeftMargin{81. }%
+\CSLRightInline{Brunell, A. B. \& Buelow, M. T. Narcissism and performance on behavioral decision-making tasks. \emph{Journal of Behavioral Decision Making} \textbf{30}, 3--14 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-o2021grandiose}{}}%
+\CSLLeftMargin{82. }%
+\CSLRightInline{O'Reilly, C.
+A.
+\& Hall, N.
+Grandiose narcissists and decision making: Impulsive, overconfident, and skeptical of experts--but seldom in doubt.
+\emph{Personality and Individual Differences} \textbf{168}, 110280 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fornells2015people}{}}%
+\CSLLeftMargin{83. }%
+\CSLRightInline{Fornells-Ambrojo, M.
+\emph{et al.} How do people with persecutory delusions evaluate threat in a controlled social environment?
+A qualitative study using virtual reality.
+\emph{Behavioural and Cognitive Psychotherapy} \textbf{43}, 89--107 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2003can}{}}%
+\CSLLeftMargin{84. }%
+\CSLRightInline{Freeman, D. \emph{et al.} Can virtual reality be used to investigate persecutory ideation? \emph{The Journal of nervous and mental disease} \textbf{191}, 509--514 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
+\CSLLeftMargin{85. }%
+\CSLRightInline{King, A.
+\& Dudley, R.
+Paranoia, worry, cognitive avoidance and intolerance of uncertainty in a student population.
+\emph{Journal of Applied Psychology and Social Science} \textbf{3}, 70--89 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2005psychology}{}}%
+\CSLLeftMargin{86. }%
+\CSLRightInline{Freeman, D.
+\emph{et al.} The psychology of persecutory ideation II: A virtual reality experimental study.
+\emph{The Journal of nervous and mental disease} \textbf{193}, 309--315 (2005).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-said2022artificial}{}}%
+\CSLLeftMargin{87. }%
+\CSLRightInline{Said, N. \emph{et al.} An artificial intelligence perspective: How knowledge and confidence shape risk and opportunity perception. (2022).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-abraham2009reality}{}}%
-Abraham, A., \& Von Cramon, D.
+\CSLLeftMargin{88. }%
+\CSLRightInline{Abraham, A.
+\& Von Cramon, D.
 Y.
-(2009).
 Reality= relevance?
 Insights from spontaneous modulations of the brain's default network when telling apart reality from fiction.
-\emph{PloS One}, \emph{4}(3), e4741.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ahadzadeh2021social}{}}%
-Ahadzadeh, A. S., Ong, F. S., \& Wu, S. L. (2021). Social media skepticism and belief in conspiracy theories about COVID-19: The moderating role of the dark triad. \emph{Current Psychology}, 1--13.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
-Bago, B., Rosenzweig, L. R., Berinsky, A. J., \& Rand, D. G. (2022). Emotion may predict susceptibility to fake news but emotion regulation does not seem to help. \emph{Cognition and Emotion}, 1--15.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bailey2021gender}{}}%
-Bailey, A. (2021). \emph{A gender in-group effect on facial recall} {[}PhD thesis{]}. University of Tasmania.
-
-\leavevmode\vadjust pre{\hypertarget{ref-balas2017}{}}%
-Balas, B., \& Pacella, J. (2017). Trustworthiness perception is disrupted in artificial faces. \emph{Computers in Human Behavior}, \emph{77}. \url{https://doi.org/10.1016/j.chb.2017.08.045}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
-Bartosik, B., Wojcik, G.
-M., Brzezicka, A., \& Kawiak, A.
-(2021).
-Are you able to trust me?
-Analysis of the relationships between personality traits and the assessment of attractiveness and trust.
-\emph{Frontiers in Human Neuroscience}, \emph{15}, 685530.
-
-\leavevmode\vadjust pre{\hypertarget{ref-begg1992dissociation}{}}%
-Begg, I.
-M., Anas, A., \& Farinacci, S.
-(1992).
-Dissociation of processes in belief: Source recollection, statement familiarity, and the illusion of truth.
-\emph{Journal of Experimental Psychology: General}, \emph{121}(4), 446.
-
-\leavevmode\vadjust pre{\hypertarget{ref-berghel2018weaponizing}{}}%
-Berghel, H. (2018). Weaponizing twitter litter: Abuse-forming networks and social media. \emph{Computer}, \emph{51}(4), 70--73.
-
-\leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
-Britt, M. A., Rouet, J.-F., Blaum, D., \& Millis, K. (2019). A reasoned approach to dealing with fake news. \emph{Policy Insights from the Behavioral and Brain Sciences}, \emph{6}(1), 94--101.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brunell2017narcissism}{}}%
-Brunell, A. B., \& Buelow, M. T. (2017). Narcissism and performance on behavioral decision-making tasks. \emph{Journal of Behavioral Decision Making}, \emph{30}(1), 3--14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
-Bryanov, K., \& Vziatysheva, V. (2021). Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS One}, \emph{16}(6), e0253717.
-
-\leavevmode\vadjust pre{\hypertarget{ref-buunk2002age}{}}%
-Buunk, B.
-P., Dijkstra, P., Fetchenhauer, D., \& Kenrick, D.
-T.
-(2002).
-Age and gender differences in mate selection criteria for various involvement levels.
-\emph{Personal Relationships}, \emph{9}(3), 271--278.
-
-\leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
-Calbi, M., Heimann, K., Barratt, D., Siri, F., Umiltà, M.
-A., \& Gallese, V.
-(2017).
-How context influences our perception of emotional faces: A behavioral study on the kuleshov effect.
-\emph{Frontiers in Psychology}, \emph{8}.
-\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2017.01684}
-
-\leavevmode\vadjust pre{\hypertarget{ref-campbell2004narcissism}{}}%
-Campbell, W. K., Goodie, A. S., \& Foster, J. D. (2004). Narcissism, confidence, and risk attitude. \emph{Journal of Behavioral Decision Making}, \emph{17}(4), 297--311.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
-Carleton, R.
-N., Norton, M.
-P.
-J., \& Asmundson, G.
-J.
-(2007).
-Fearing the unknown: A short version of the intolerance of uncertainty scale.
-\emph{Journal of Anxiety Disorders}, \emph{21}(1), 105--117.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carolan2017searching}{}}%
-Carolan, P.
-L.
-(2017).
-\emph{Searching {``inaffectively''}: A behavioral, psychometric, and electroencephalographic investigation of psychopathic personality and visual-spatial attention} {[}PhD thesis{]}.
-Arts \& Social Sciences: Department of Psychology.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
-Chatterjee, A., \& Pollock, T. G. (2017). Master of puppets: How narcissistic CEOs construct their professional worlds. \emph{Academy of Management Review}, \emph{42}(4), 703--725.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021broadening}{}}%
-Chen, J. M., Norman, J. B., \& Nam, Y. (2021). Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods}, \emph{53}(1), 371--389.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
-Chen, Y., Conroy, N.
-K., \& Rubin, V.
-L.
-(2015).
-News in an online world: The need for an {``automatic crap detector.''} \emph{Proceedings of the Association for Information Science and Technology}, \emph{52}(1), 1--4.
-
-\leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
-De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecker2022psychological}{}}%
-Ecker, U.
-K., Lewandowsky, S., Cook, J., Schmid, P., Fazio, L.
-K., Brashier, N., Kendeou, P., Vraga, E.
-K., \& Amazeen, M.
-A.
-(2022).
-The psychological drivers of misinformation belief and its resistance to correction.
-\emph{Nature Reviews Psychology}, \emph{1}(1), 13--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eddy2021self}{}}%
-Eddy, C. M. (2021). Self-serving social strategies: A systematic review of social cognition in narcissism. \emph{Current Psychology}, 1--19.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
-Fink, B., Neave, N., Manning, J.
-T., \& Grammer, K.
-(2006).
-Facial symmetry and judgements of attractiveness, health and personality.
-\emph{Personality and Individual Differences}, \emph{41}(3), 491--499.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fornells2015people}{}}%
-Fornells-Ambrojo, M., Freeman, D., Slater, M., Swapp, D., Antley, A., \& Barker, C.
-(2015).
-How do people with persecutory delusions evaluate threat in a controlled social environment?
-A qualitative study using virtual reality.
-\emph{Behavioural and Cognitive Psychotherapy}, \emph{43}(1), 89--107.
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2005psychology}{}}%
-Freeman, D., Garety, P.
-A., Bebbington, P., Slater, M., Kuipers, E., Fowler, D., Green, C., Jordan, J., Ray, K., \& Dunn, G.
-(2005).
-The psychology of persecutory ideation II: A virtual reality experimental study.
-\emph{The Journal of Nervous and Mental Disease}, \emph{193}(5), 309--315.
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2021revised}{}}%
-Freeman, D., Loe, B.
-S., Kingdon, D., Startup, H., Molodynski, A., Rosebrock, L., Brown, P., Sheaves, B., Waite, F., \& Bird, J.
-C.
-(2021).
-The revised green et al., Paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
-\emph{Psychological Medicine}, \emph{51}(2), 244--253.
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2003can}{}}%
-Freeman, D., Slater, M., Bebbington, P.
-E., Garety, P.
-A., Kuipers, E., Fowler, D., Met, A., Read, C.
-M., Jordan, J., \& Vinayagamoorthy, V.
-(2003).
-Can virtual reality be used to investigate persecutory ideation?
-\emph{The Journal of Nervous and Mental Disease}, \emph{191}(8), 509--514.
-
-\leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
-Garrido, M. V., \& Prada, M. (2017). KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces. \emph{Frontiers in Psychology}, \emph{8}, 2181.
+\emph{PloS one} \textbf{4}, e4741 (2009).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gobbini2013prioritized}{}}%
-Gobbini, M.
-I., Gors, J.
-D., Halchenko, Y.
-O., Rogers, C., Guntupalli, J.
-S., Hughes, H., \& Cipolli, C.
-(2013).
-Prioritized detection of personally familiar faces.
-\emph{PloS One}, \emph{8}(6), e66620.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
-Goldstein, T.
-R.
-(2009).
-The pleasure of unadulterated sadness: Experiencing sorrow in fiction, nonfiction, and" in person.".
-\emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4), 232.
-
-\leavevmode\vadjust pre{\hypertarget{ref-grapsas2020and}{}}%
-Grapsas, S., Brummelman, E., Back, M.
-D., \& Denissen, J.
-J.
-(2020).
-The {``why''} and {``how''} of narcissism: A process model of narcissistic status pursuit.
-\emph{Perspectives on Psychological Science}, \emph{15}(1), 150--172.
-
-\leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
-Han, S., Li, Y., Liu, S., Xu, Q., Tan, Q., \& Zhang, L.
-(2018).
-Beauty is in the eye of the beholder: The halo effect and generalization effect in the facial attractiveness evaluation.
-\emph{Acta Psychologica Sinica}, \emph{50}(4), 363.
-
-\leavevmode\vadjust pre{\hypertarget{ref-herbst2020gender}{}}%
-Herbst, T.
-H.
-(2020).
-Gender differences in self-perception accuracy: The confidence gap and women leaders' underrepresentation in academia.
-\emph{SA Journal of Industrial Psychology}, \emph{46}(1), 1--8.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hodson2018dark}{}}%
-Hodson, G., Book, A., Visser, B.
-A., Volk, A.
-A., Ashton, M.
-C., \& Lee, K.
-(2018).
-Is the dark triad common factor distinct from low honesty-humility?
-\emph{Journal of Research in Personality}, \emph{73}, 123--129.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogers2021effect}{}}%
-Hoogers, E. (2021). \emph{The effect of attitude towards computer generated faces on face perception} {[}\{B.S.\} thesis{]}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hou2019survival}{}}%
-Hou, C., \& Liu, Z.
-(2019).
-The survival processing advantage of face: The memorization of the (un) trustworthy face contributes more to survival adaptation.
-\emph{Evolutionary Psychology}, \emph{17}(2), 1474704919839726.
-
-\leavevmode\vadjust pre{\hypertarget{ref-indovina2007dissociation}{}}%
-Indovina, I., \& Macaluso, E. (2007). Dissociation of stimulus relevance and saliency factors during shifts of visuospatial attention. \emph{Cerebral Cortex}, \emph{17}(7), 1701--1711.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
-Jauk, E., Olaru, G., Schürch, E., Back, M.
-D., \& Morf, C.
-C.
-(2022).
-Validation of the german five-factor narcissism inventory and construction of a brief form using ant colony optimization.
-\emph{Assessment}, 10731911221075761.
-
-\leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
-King, A., \& Dudley, R.
-(2017).
-Paranoia, worry, cognitive avoidance and intolerance of uncertainty in a student population.
-\emph{Journal of Applied Psychology and Social Science}, \emph{3}(2), 70--89.
-
-\leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
-Levidi, M.
-D.
-C., McGrath, A., Kyriakoulis, P., \& Sulikowski, D.
-(2022).
-Understanding criminal decision-making: Links between honesty-humility, perceived risk and negative affect: Psychology, crime \& law.
-\emph{Psychology, Crime and Law}, 1--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2017beyond}{}}%
-Lewandowsky, S., Ecker, U.
-K., \& Cook, J.
-(2017).
-Beyond misinformation: Understanding and coping with the {``post-truth''} era.
-\emph{Journal of Applied Research in Memory and Cognition}, \emph{6}(4), 353--369.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewin2002sex}{}}%
-Lewin, C., \& Herlitz, A. (2002). Sex differences in face recognition---women's faces make the difference. \emph{Brain and Cognition}, \emph{50}(1), 121--128.
-
-\leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
-Liefooghe, B., Oliveira, M., Leisten, L. M., Hoogers, E., Aarts, H., \& Hortensius, R. (2022). \emph{Faces merely labelled as artificial are trusted less}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-little2011facial}{}}%
-Little, A.
-C., Jones, B.
-C., \& DeBruine, L.
-M.
-(2011).
-Facial attractiveness: Evolutionary based research.
-\emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{366}(1571), 1638--1659.
-
-\leavevmode\vadjust pre{\hypertarget{ref-littrell2020overconfidently}{}}%
-Littrell, S., Fugelsang, J., \& Risko, E. F. (2020). Overconfidently underthinking: Narcissism negatively predicts cognitive reflection. \emph{Thinking \& Reasoning}, \emph{26}(3), 352--380.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lou2015perceptual}{}}%
-Lou, B., Hsu, W.-Y., \& Sajda, P.
-(2015).
-Perceptual salience and reward both influence feedback-related neural activity arising from choice.
-\emph{Journal of Neuroscience}, \emph{35}(38), 13064--13075.
-
-\leavevmode\vadjust pre{\hypertarget{ref-parametersArticle}{}}%
-Lüdecke, D., Ben-Shachar, M., Patil, I., \& Makowski, D.
-(2020).
-Extracting, computing and exploring the parameters of statistical models using {R}.
-\emph{Journal of Open Source Software}, \emph{5}(53), 2445.
-\url{https://doi.org/10.21105/joss.02445}
-
-\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
-Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., \& Makowski, D.
-(2021).
-{performance}: An {R} package for assessment, comparison and testing of statistical models.
-\emph{Journal of Open Source Software}, \emph{6}(60), 3139.
-\url{https://doi.org/10.21105/joss.03139}
-
-\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
-Lüdecke, D., Waggoner, P., \& Makowski, D.
-(2019).
-Insight: A unified interface to access information from model objects in {R}.
-\emph{Journal of Open Source Software}, \emph{4}(38), 1412.
-\url{https://doi.org/10.21105/joss.01412}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2018cognitive}{}}%
-Makowski, D. (2018). \emph{Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal} {[}PhD thesis{]}. Sorbonne Paris Cit{é}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%
-Makowski, D., Ben-Shachar, M., \& Lüdecke, D.
-(2019).
-{bayestestR}: Describing effects and their uncertainty, existence and significance within the {Bayesian} framework.
-\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
-\url{https://doi.org/10.21105/joss.01541}
-
-\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
-Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D.
-(2020).
-Methods and algorithms for correlation analysis in {R}.
-\emph{Journal of Open Source Software}, \emph{5}(51), 2306.
-\url{https://doi.org/10.21105/joss.02306}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2017being}{}}%
-Makowski, D., Sperduti, M., Nicolas, S., \& Piolino, P. (2017). {``Being there''} and remembering it: Presence improves memory encoding. \emph{Consciousness and Cognition}, \emph{53}, 194--202.
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
-Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
-(2019).
-Phenomenal, bodily and brain correlates of fictional reappraisal as an implicit emotion regulation strategy.
-\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 877--897.
-
-\leavevmode\vadjust pre{\hypertarget{ref-marcinkowska2021self}{}}%
-Marcinkowska, U.
-M., Jones, B.
-C., \& Lee, A.
-J.
-(2021).
-Self-rated attractiveness predicts preferences for sexually dimorphic facial characteristics in a culturally diverse sample.
-\emph{Scientific Reports}, \emph{11}(1), 1--8.
-
-\leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
-Martel, C., Pennycook, G., \& Rand, D. G. (2020). Reliance on emotion promotes belief in fake news. \emph{Cognitive Research: Principles and Implications}, \emph{5}(1), 1--20.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcdonnell2010face}{}}%
-McDonnell, R., \& Breidt, M. (2010). Face reality: Investigating the uncanny valley for virtual faces. In \emph{ACM SIGGRAPH ASIA 2010 sketches} (pp. 1--2).
-
-\leavevmode\vadjust pre{\hypertarget{ref-michael2021source}{}}%
-Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mishra2019gender}{}}%
-Mishra, M.
-V., Likitlersuang, J., B Wilmer, J., Cohan, S., Germine, L., \& DeGutis, J.
-M.
-(2019).
-Gender differences in familiar face recognition and the influence of sociocultural gender inequality.
-\emph{Scientific Reports}, \emph{9}(1), 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-moshel2022}{}}%
-Moshel, M.
-L., Robinson, A.
-K., Carlson, T.
-A., \& Grootswagers, T.
-(2022).
-Are you for real?
-Decoding realistic AI-generated faces from neural activity.
-\emph{Vision Research}, \emph{199}, 108079.
-\url{https://doi.org/10.1016/j.visres.2022.108079}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nightingale2022}{}}%
-Nightingale, S.
-J., \& Farid, H.
-(2022).
-AI-synthesized faces are indistinguishable from real faces and more trustworthy.
-\emph{Proceedings of the National Academy of Sciences}, \emph{119}(8), e2120481119.
-\url{https://doi.org/10.1073/pnas.2120481119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-o2021grandiose}{}}%
-O'Reilly, C.
-A., \& Hall, N.
-(2021).
-Grandiose narcissists and decision making: Impulsive, overconfident, and skeptical of experts--but seldom in doubt.
-\emph{Personality and Individual Differences}, \emph{168}, 110280.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
-Pantserev, K.
-(2020).
-\emph{The malicious use of AI-based deepfake technology as the new threat to psychological security and political stability} (pp.
-37--55).
-\url{https://doi.org/10.1007/978-3-030-35746-7_3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peer2022}{}}%
-Peer, E., Rothschild, D., Gordon, A., Evernden, Z., \& Damer, E.
-(2022).
-Data quality of platforms and panels for online behavioral research.
-\emph{Behavior Research Methods}, \emph{54}(4), 1643--1662.
-\url{https://doi.org/10.3758/s13428-021-01694-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pehlivanoglu2021role}{}}%
-Pehlivanoglu, D., Lin, T., Deceus, F., Heemskerk, A., Ebner, N.
-C., \& Cahill, B.
-S.
-(2021).
-The role of analytical reasoning and source credibility on the evaluation of real and fake full-length news articles.
-\emph{Cognitive Research: Principles and Implications}, \emph{6}(1), 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pennycook2019lazy}{}}%
-Pennycook, G., \& Rand, D. G. (2019). Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning. \emph{Cognition}, \emph{188}, 39--50.
-
-\leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
-Peters, L., Sunderland, M., Andrews, G., Rapee, R.
-M., \& Mattick, R.
-P.
-(2012).
-Development of a short form social interaction anxiety (SIAS) and social phobia scale (SPS) using nonparametric item response theory: The SIAS-6 and the SPS-6.
-\emph{Psychological Assessment}, \emph{24}(1), 66.
-
-\leavevmode\vadjust pre{\hypertarget{ref-petty1986elaboration}{}}%
-Petty, R. E., \& Cacioppo, J. T. (1986). The elaboration likelihood model of persuasion. In \emph{Communication and persuasion} (pp. 1--24). Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
-Piksa, M., Noworyta, K., Piasecki, J., Gwiazdzinski, P., Gundersen, A.
-B., Kunst, J., \& Rygula, R.
-(2022).
-Cognitive processes and personality traits underlying four phenotypes of susceptibility to (mis) information.
-\emph{Frontiers in Psychiatry}, 1142.
-
-\leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
-Qi, Y., \& Ying, J. (2022). Gender biases in the accuracy of facial judgments: Facial attractiveness and perceived socioeconomic status. \emph{Frontiers in Psychology}, \emph{13}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
-R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
-Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
-
-\leavevmode\vadjust pre{\hypertarget{ref-said2022artificial}{}}%
-Said, N., Potinteu, A.-E., Brich, I., Buder, J., Schumm, H., \& Huff, M. (2022). \emph{An artificial intelligence perspective: How knowledge and confidence shape risk and opportunity perception}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
-Sanchez-Vives, M. V., \& Slater, M. (2005). From presence to consciousness through virtual reality. \emph{Nature Reviews Neuroscience}, \emph{6}(4), 332--339.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schepman2020initial}{}}%
-Schepman, A., \& Rodway, P. (2020). Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in Human Behavior Reports}, \emph{1}, 100014.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
-Sibley, C., Luyten, N., Wolfman, M., Mobberley, A., Wootton, L.
-W., Hammond, M., Sengupta, N., Perry, R., West-Newman, T., Wilson, M., McLellan, L., Hoverd, W.
-J., \& Robertson, A.
-(2011).
-The mini-IPIP6: Validation and extension of a short measure of the big-six factors of personality in new zealand.
-\emph{New Zealand Journal of Psychology}, \emph{40}, 142--159.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sindermann2020short}{}}%
-Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology}, \emph{36}, 44--48.
-
-\leavevmode\vadjust pre{\hypertarget{ref-skora2022functional}{}}%
-Skora, L., Livermore, J., \& Roelofs, K. (2022). The functional role of cardiac activity in perception and action. \emph{Neuroscience \& Biobehavioral Reviews}, 104655.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
-Sobieraj, S., \& Krämer, N. C. (2014). What is beautiful in cyberspace? Communication with attractive avatars. \emph{International Conference on Social Computing and Social Media}, 125--136.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sommer2013sex}{}}%
-Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A., \& Wilhelm, O. (2013). Sex differences in face cognition. \emph{Acta Psychologica}, \emph{142}(1), 62--73.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sperduti2016paradox}{}}%
-Sperduti, M., Arcangeli, M., Makowski, D., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
-(2016).
-The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance.
-\emph{Acta Psychologica}, \emph{165}, 53--59.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sperduti2017distinctive}{}}%
-Sperduti, M., Makowski, D., Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
-(2017).
-The distinctive role of executive functions in implicit emotion regulation.
-\emph{Acta Psychologica}, \emph{173}, 13--20.
-
-\leavevmode\vadjust pre{\hypertarget{ref-spielmann2020predictive}{}}%
-Spielmann, S.
-S., Maxwell, J.
-A., MacDonald, G., Peragine, D., \& Impett, E.
-A.
-(2020).
-The predictive effects of fear of being single on physical attractiveness and less selective partner selection strategies.
-\emph{Journal of Social and Personal Relationships}, \emph{37}(1), 100--123.
-
-\leavevmode\vadjust pre{\hypertarget{ref-susmann2021persuasion}{}}%
-Susmann, M.
-W., Xu, M., Clark, J.
-K., Wallace, L.
-E., Blankenship, K.
-L., Philipp-Muller, A.
-Z., Luttrell, A., Wegener, D.
-T., \& Petty, R.
-E.
-(2021).
-Persuasion amidst a pandemic: Insights from the elaboration likelihood model.
-\emph{European Review of Social Psychology}, 1--37.
+\CSLLeftMargin{89. }%
+\CSLRightInline{Gobbini, M. I. \emph{et al.} Prioritized detection of personally familiar faces. \emph{PloS one} \textbf{8}, e66620 (2013).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-taylor2009neural}{}}%
-Taylor, M.
-J., Arsalidou, M., Bayless, S.
-J., Morris, D., Evans, J.
-W., \& Barbeau, E.
-J.
-(2009).
-Neural correlates of personally familiar faces: Parents, partner and own faces.
-\emph{Human Brain Mapping}, \emph{30}(7), 2008--2020.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tsikandilakis2019beauty}{}}%
-Tsikandilakis, M., Bali, P., \& Chapman, P.
-(2019).
-Beauty is in the eye of the beholder: The appraisal of facial attractiveness and its relation to conscious awareness.
-\emph{Perception}, \emph{48}(1), 72--92.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
-Tucciarelli, R., Vehar, N., \& Tsakiris, M. (2020). \emph{On the realness of people who do not exist: the social processing of artificial faces}. \url{https://doi.org/10.31234/osf.io/dnk9x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-van2020sex}{}}%
-Van Den Akker, O.
-R., Assen, M.
-A.
-van, Van Vugt, M., \& Wicherts, J.
-M.
-(2020).
-Sex differences in trust and trustworthiness: A meta-analysis of the trust game and the gift-exchange game.
-\emph{Journal of Economic Psychology}, \emph{81}, 102329.
-
-\leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
-Weller, J.
-A., \& Thulin, E.
-W.
-(2012).
-Do honest people take fewer risks?
-Personality correlates of risk-taking to achieve gains and avoid losses in HEXACO space.
-\emph{Personality and Individual Differences}, \emph{53}(7), 923--926.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
+\CSLLeftMargin{90. }%
+\CSLRightInline{Taylor, M. J. \emph{et al.} Neural correlates of personally familiar faces: Parents, partner and own faces. \emph{Human brain mapping} \textbf{30}, 2008--2020 (2009).}
 

### 2022-11-10 submission/manuscript.Rmd
add ethics statement

@@
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "4428"
+wordcount         : "4116"
 bibliography      : references.bib
@@
 ## Methods
+
+## Ethics Statement
+
+This study was approved by the NTU Institutional Review Board (NTU IRB-2022-187) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+All participants provided their informed consent prior to participation and were incentivized after completing the study.
 

### 2022-11-10 submission/manuscript.tex
add ethics statement

@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4428}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4116}
 \usepackage{lineno}
@@
 
+\hypertarget{ethics-statement}{%
+\subsection{Ethics Statement}\label{ethics-statement}}
+
+This study was approved by the NTU Institutional Review Board (NTU IRB-2022-187) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+All participants provided their informed consent prior to participation and were incentivized after completing the study.
+
 In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.

### 2022-11-11 submission/manuscript.Rmd
knit

@@
 keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
-wordcount         : "4116"
+wordcount         : "4088"
 bibliography      : references.bib
@@
 
-## Ethics Statement
+### Ethics Statement
 
@@
 
-In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
+<!-- In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
+-->
 

### 2022-11-11 submission/manuscript.tex
knit

@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4116}
+\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4088}
 \usepackage{lineno}
@@
 \hypertarget{ethics-statement}{%
-\subsection{Ethics Statement}\label{ethics-statement}}
+\subsubsection{Ethics Statement}\label{ethics-statement}}
 
@@
 All participants provided their informed consent prior to participation and were incentivized after completing the study.
-
-In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
 

### 2022-12-19 submission/manuscript.Rmd
revert citations style back to APA

@@
 output            : papaja::apa6_pdf
-csl: utils/scientific-reports.csl
+csl: utils/apa.csl
 header-includes:
@@
 
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images) [@mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
+While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
 Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
@@
 
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as *simulation monitoring*) [@makowski2018cognitive; @makowski2019phenomenal].
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2018cognitive; @makowski2019phenomenal].
 With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
@@
 Based on the embodied reality theory
-[@makowski2018cognitive; @makowski2019phenomenal],
-<!-- [outlined in @makowski2018cognitive; @makowski2019phenomenal], -->
+[outlined in @makowski2018cognitive; @makowski2019phenomenal],
 which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
@@
 In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* 
-(24 items) [@sibley2011] 
-<!-- [24 items, @sibley2011]  -->
+<!-- (24 items) [@sibley2011]  -->
+[24 items, @sibley2011]
 measuring 6 personality traits, the *SIAS-6* and the *SPS-6* 
-(6 items each) [@peters2012development]
-<!-- [6 items each, @peters2012development]  -->
+<!-- (6 items each) [@peters2012development] -->
+[6 items each, @peters2012development]
 assessing social anxiety levels, the *FFNI-BF* 
-(30 items) [@jauk2022validation]
-<!-- [30 items, @jauk2022validation]  -->
+<!-- (30 items) [@jauk2022validation] -->
+[30 items, @jauk2022validation]
 measuring 9 facets of narcissism; the *R-GPTS* 
-(18 items) [@freeman2021revised]
-<!-- [18 items, @freeman2021revised]  -->
+<!-- (18 items) [@freeman2021revised] -->
+[18 items, @freeman2021revised]
 measuring 2 dimensions related to paranoid thinking; and the *IUS-12* 
-(12 items) [@carleton2007fearing]
-<!-- [12 items, @carleton2007fearing]  -->
+<!-- (12 items) [@carleton2007fearing] -->
+[12 items, @carleton2007fearing]
 measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness 
-("How attractive would you say you are?") [@marcinkowska2021self]
-<!-- ["How attractive would you say you are?", @marcinkowska2021self] -->
+<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->
+["How attractive would you say you are?", @marcinkowska2021self]
 and the other measuring physical attractiveness 
-("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive]
-<!-- ["How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive].  -->
+<!-- ("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive] -->
+["How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive].
 Finally, we devised 5 items pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
 To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale
-(*GAAIS*) [@schepman2020initial].
-<!-- [*GAAIS*, @schepman2020initial].  -->
+<!-- (*GAAIS*) [@schepman2020initial]. -->
+[*GAAIS*, @schepman2020initial].
 This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.
@@
 In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database 
-(AMFD) [@chen2021broadening] 
-<!-- [AMFD, @chen2021broadening]  -->
+<!-- (AMFD) [@chen2021broadening]  -->
+[AMFD, @chen2021broadening]
 were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
@@
 However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers
-(e.g., heart rate deceleration) [@skora2022functional].
-<!-- [e.g., heart rate deceleration, @skora2022functional]. -->
+<!-- (e.g., heart rate deceleration) [@skora2022functional]. -->
+[e.g., heart rate deceleration, @skora2022functional].
 
@@
 One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females
-(explained evolutionarily as a compromise to their reproductive potential [@van2020sex]),
-<!-- [explained evolutionarily as a compromise to their reproductive potential, @van2020sex],  -->
+<!-- (explained evolutionarily as a compromise to their reproductive potential [@van2020sex]), -->
+[explained evolutionarily as a compromise to their reproductive potential, @van2020sex],
 to which perceived facial trustworthiness relates [@hou2019survival].

### 2022-12-19 submission/manuscript.tex
revert citations style back to APA

@@
 For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access\textsuperscript{1}.
-Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination\textsuperscript{2}.
-This issue is central to what has been coined the ``post-truth era''\textsuperscript{3}, in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
-
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images)\textsuperscript{4}, it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation\textsuperscript{1,5,6}.
+These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
+Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
+This issue is central to what has been coined the ``post-truth era'' (Lewandowsky et al., 2017), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
+
+While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
 Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
 
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring})\textsuperscript{7,8}.
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy\textsuperscript{9,10}, people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation\textsuperscript{9--11}.
-However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult\textsuperscript{12,13}.
+Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, Makowski, 2018; Makowski, Sperduti, et al., 2019).
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
+However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
+Chen et al., 2015).
 Thus, in the absence of clear contextual information, what drives our beliefs of reality?
@@
 
-Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits\textsuperscript{14--16}.
-For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli\textsuperscript{17,18}, and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations\textsuperscript{19}.
-Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news\textsuperscript{16,20}.
+Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
+For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019), and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations (Britt et al., 2019).
+Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
 
 Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment\textsuperscript{21,22}.
-Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation\textsuperscript{8,23}.
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief\textsuperscript{24,25}.
-Additionally, other factors, such as the stimuli's perceived self-relevance\textsuperscript{26,27}, as well as familiarity\textsuperscript{28}, could also play a role in guiding our appraisal of a stimulus.
-
-AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness\textsuperscript{29--32}.
-Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real\textsuperscript{5}.
-Conversely,\textsuperscript{33} reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
+For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005).
+Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
+Additionally, other factors, such as the stimuli's perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in guiding our appraisal of a stimulus.
+
+AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
+Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real (Tucciarelli et al., 2020).
+Conversely, Liefooghe et al.
+(2022) reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
 Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
@@
 This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory\textsuperscript{7,8},
+Based on the embodied reality theory
+(outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019),
 which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
-We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness\textsuperscript{33--36}, and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
+We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
@@
 In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6}
-(24 items)\textsuperscript{37}
+(24 items, Sibley et al., 2011)
 measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6}
-(6 items each)\textsuperscript{38}
+(6 items each, Peters et al., 2012)
 assessing social anxiety levels, the \emph{FFNI-BF}
-(30 items)\textsuperscript{39}
+(30 items, Jauk et al., 2022)
 measuring 9 facets of narcissism; the \emph{R-GPTS}
-(18 items)\textsuperscript{40}
+(18 items, Freeman et al., 2021)
 measuring 2 dimensions related to paranoid thinking; and the \emph{IUS-12}
-(12 items)\textsuperscript{41}
+(12 items, Carleton et al., 2007)
 measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness
-(``How attractive would you say you are?'')\textsuperscript{42}
+(``How attractive would you say you are?'' Marcinkowska et al., 2021)
 and the other measuring physical attractiveness
-(``How would you rate your own physical attractiveness relative to the average'')\textsuperscript{43}
+(``How would you rate your own physical attractiveness relative to the average,'' Spielmann et al., 2020).
 Finally, we devised 5 items pertaining to expectations about AI-generated image technology (``I think current Artificial Intelligence algorithms can generate very realistic images'').
 To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale
-(\emph{GAAIS})\textsuperscript{44}.
+(\emph{GAAIS}, Schepman \& Rodway, 2020).
 This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.
@@
 In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database
-(AMFD)\textsuperscript{45}
+(AMFD, J. M. Chen et al., 2021)
 were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
 After each stimulus presentation, ratings of \emph{Trustworthiness} (``I find this person trustworthy'') and \emph{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects\textsuperscript{46,47}, we assessed attractiveness using 2 visual analog scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
+Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we assessed attractiveness using 2 visual analog scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
 
@@
 This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with \emph{Fake} and \emph{Real} as the two extremes).
-The study was implemented using \emph{jsPsych}\textsuperscript{48}, and the exact instructions are available in the experiment code.
+The study was implemented using \emph{jsPsych} (De Leeuw, 2015), and the exact instructions are available in the experiment code.
 
@@
 
-One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data\textsuperscript{49}.
+One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data (Peer et al., 2022).
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-The analysis was carried out using \emph{R 4.2}\textsuperscript{50}, the \emph{tidyverse}\textsuperscript{51}, and the \emph{easystats} collection of packages\textsuperscript{52--56}.
+The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski et al., 2020; Makowski, Ben-Shachar, et al., 2019).
 As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant (\(p <.01\)).
@@
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women\textsuperscript{57,58}.
+The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
 In fact, female participants were more confident in judging faces as fake only when they were rated very high or low on beauty, suggesting that physical beauty and attractiveness are not analogous in their effects on simulation monitoring decisions.
@@
 Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
-Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities\textsuperscript{57--59}.
+Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \& Ying, 2022).
 It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging\textsuperscript{60,61} or physiological markers
-(e.g., heart rate deceleration)\textsuperscript{62}.
+However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers
+(e.g., heart rate deceleration, Skora et al., 2022).
 
 Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
-Given prior evidence that faces presented as computer-generated were rated less trustworthy\textsuperscript{30,33,63}, we expected such a linear association to be more clearly present for both genders.
+Given prior evidence that faces presented as computer-generated were rated less trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such a linear association to be more clearly present for both genders.
 One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females
-(explained evolutionarily as a compromise to their reproductive potential\textsuperscript{64}),
-to which perceived facial trustworthiness relates\textsuperscript{65}.
+(explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020),
+to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
 However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
@@
 Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females\textsuperscript{66--68}, as well as an overconfidence in face recall for males\textsuperscript{69,70}.
+Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females (Lewin \& Herlitz, 2002; Mishra et al., 2019; Sommer et al., 2013), as well as an overconfidence in face recall for males (Bailey, 2021; Herbst, 2020).
 However, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
@@
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion\textsuperscript{71,72} - to be related to a lower confidence in simulation monitoring judgements.
+Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012) - to be related to a lower confidence in simulation monitoring judgements.
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
-This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking\textsuperscript{73,74}, and to be more vigilant and attentive to external stimuli\textsuperscript{75--77}.
-
-Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism\textsuperscript{78}, we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making\textsuperscript{79--82}.
+This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
+
+Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
 Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this relationship as related to a higher response assertiveness.
@@
 Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat\textsuperscript{83--85}, it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
-This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters\textsuperscript{86}.
+Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
+This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters (Freeman et al., 2005).
 
@@
 Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
-This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities\textsuperscript{87}, hence permitting themselves to be more confident in their simulation monitoring decisions.
-In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications\textsuperscript{87}.
+This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities (Said et al., 2022), hence permitting themselves to be more confident in their simulation monitoring decisions.
+In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (Said et al., 2022).
 
 On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display\textsuperscript{88--90}.
-Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness\textsuperscript{22,26}.
+Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
+Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness (Makowski et al., 2017; Sperduti et al., 2016).
 However, if that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-nightingale2022}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{Nightingale, S.
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abraham2009reality}{}}%
+Abraham, A., \& Von Cramon, D.
+Y.
+(2009).
+Reality= relevance?
+Insights from spontaneous modulations of the brain's default network when telling apart reality from fiction.
+\emph{PloS One}, \emph{4}(3), e4741.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ahadzadeh2021social}{}}%
+Ahadzadeh, A. S., Ong, F. S., \& Wu, S. L. (2021). Social media skepticism and belief in conspiracy theories about COVID-19: The moderating role of the dark triad. \emph{Current Psychology}, 1--13.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
+Bago, B., Rosenzweig, L. R., Berinsky, A. J., \& Rand, D. G. (2022). Emotion may predict susceptibility to fake news but emotion regulation does not seem to help. \emph{Cognition and Emotion}, 1--15.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bailey2021gender}{}}%
+Bailey, A. (2021). \emph{A gender in-group effect on facial recall} {[}PhD thesis{]}. University of Tasmania.
+
+\leavevmode\vadjust pre{\hypertarget{ref-balas2017}{}}%
+Balas, B., \& Pacella, J. (2017). Trustworthiness perception is disrupted in artificial faces. \emph{Computers in Human Behavior}, \emph{77}. \url{https://doi.org/10.1016/j.chb.2017.08.045}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
+Bartosik, B., Wojcik, G.
+M., Brzezicka, A., \& Kawiak, A.
+(2021).
+Are you able to trust me?
+Analysis of the relationships between personality traits and the assessment of attractiveness and trust.
+\emph{Frontiers in Human Neuroscience}, \emph{15}, 685530.
+
+\leavevmode\vadjust pre{\hypertarget{ref-begg1992dissociation}{}}%
+Begg, I.
+M., Anas, A., \& Farinacci, S.
+(1992).
+Dissociation of processes in belief: Source recollection, statement familiarity, and the illusion of truth.
+\emph{Journal of Experimental Psychology: General}, \emph{121}(4), 446.
+
+\leavevmode\vadjust pre{\hypertarget{ref-berghel2018weaponizing}{}}%
+Berghel, H. (2018). Weaponizing twitter litter: Abuse-forming networks and social media. \emph{Computer}, \emph{51}(4), 70--73.
+
+\leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
+Britt, M. A., Rouet, J.-F., Blaum, D., \& Millis, K. (2019). A reasoned approach to dealing with fake news. \emph{Policy Insights from the Behavioral and Brain Sciences}, \emph{6}(1), 94--101.
+
+\leavevmode\vadjust pre{\hypertarget{ref-brunell2017narcissism}{}}%
+Brunell, A. B., \& Buelow, M. T. (2017). Narcissism and performance on behavioral decision-making tasks. \emph{Journal of Behavioral Decision Making}, \emph{30}(1), 3--14.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
+Bryanov, K., \& Vziatysheva, V. (2021). Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS One}, \emph{16}(6), e0253717.
+
+\leavevmode\vadjust pre{\hypertarget{ref-buunk2002age}{}}%
+Buunk, B.
+P., Dijkstra, P., Fetchenhauer, D., \& Kenrick, D.
+T.
+(2002).
+Age and gender differences in mate selection criteria for various involvement levels.
+\emph{Personal Relationships}, \emph{9}(3), 271--278.
+
+\leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
+Calbi, M., Heimann, K., Barratt, D., Siri, F., Umiltà, M.
+A., \& Gallese, V.
+(2017).
+How context influences our perception of emotional faces: A behavioral study on the kuleshov effect.
+\emph{Frontiers in Psychology}, \emph{8}.
+\url{https://www.frontiersin.org/articles/10.3389/fpsyg.2017.01684}
+
+\leavevmode\vadjust pre{\hypertarget{ref-campbell2004narcissism}{}}%
+Campbell, W. K., Goodie, A. S., \& Foster, J. D. (2004). Narcissism, confidence, and risk attitude. \emph{Journal of Behavioral Decision Making}, \emph{17}(4), 297--311.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
+Carleton, R.
+N., Norton, M.
+P.
+J., \& Asmundson, G.
 J.
-\& Farid, H.
-\href{https://doi.org/10.1073/pnas.2120481119}{AI-synthesized faces are indistinguishable from real faces and more trustworthy}.
-\emph{Proceedings of the National Academy of Sciences} \textbf{119}, e2120481119 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Pantserev, K.
-The malicious use of AI-based deepfake technology as the new threat to psychological security and political stability.
-in 37--55 (2020).
-doi:\href{https://doi.org/10.1007/978-3-030-35746-7_3}{10.1007/978-3-030-35746-7\_3}.}
+(2007).
+Fearing the unknown: A short version of the intolerance of uncertainty scale.
+\emph{Journal of Anxiety Disorders}, \emph{21}(1), 105--117.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carolan2017searching}{}}%
+Carolan, P.
+L.
+(2017).
+\emph{Searching {``inaffectively''}: A behavioral, psychometric, and electroencephalographic investigation of psychopathic personality and visual-spatial attention} {[}PhD thesis{]}.
+Arts \& Social Sciences: Department of Psychology.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
+Chatterjee, A., \& Pollock, T. G. (2017). Master of puppets: How narcissistic CEOs construct their professional worlds. \emph{Academy of Management Review}, \emph{42}(4), 703--725.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021broadening}{}}%
+Chen, J. M., Norman, J. B., \& Nam, Y. (2021). Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods}, \emph{53}(1), 371--389.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
+Chen, Y., Conroy, N.
+K., \& Rubin, V.
+L.
+(2015).
+News in an online world: The need for an {``automatic crap detector.''} \emph{Proceedings of the Association for Information Science and Technology}, \emph{52}(1), 1--4.
+
+\leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
+De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ecker2022psychological}{}}%
+Ecker, U.
+K., Lewandowsky, S., Cook, J., Schmid, P., Fazio, L.
+K., Brashier, N., Kendeou, P., Vraga, E.
+K., \& Amazeen, M.
+A.
+(2022).
+The psychological drivers of misinformation belief and its resistance to correction.
+\emph{Nature Reviews Psychology}, \emph{1}(1), 13--29.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eddy2021self}{}}%
+Eddy, C. M. (2021). Self-serving social strategies: A systematic review of social cognition in narcissism. \emph{Current Psychology}, 1--19.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
+Fink, B., Neave, N., Manning, J.
+T., \& Grammer, K.
+(2006).
+Facial symmetry and judgements of attractiveness, health and personality.
+\emph{Personality and Individual Differences}, \emph{41}(3), 491--499.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fornells2015people}{}}%
+Fornells-Ambrojo, M., Freeman, D., Slater, M., Swapp, D., Antley, A., \& Barker, C.
+(2015).
+How do people with persecutory delusions evaluate threat in a controlled social environment?
+A qualitative study using virtual reality.
+\emph{Behavioural and Cognitive Psychotherapy}, \emph{43}(1), 89--107.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2005psychology}{}}%
+Freeman, D., Garety, P.
+A., Bebbington, P., Slater, M., Kuipers, E., Fowler, D., Green, C., Jordan, J., Ray, K., \& Dunn, G.
+(2005).
+The psychology of persecutory ideation II: A virtual reality experimental study.
+\emph{The Journal of Nervous and Mental Disease}, \emph{193}(5), 309--315.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2021revised}{}}%
+Freeman, D., Loe, B.
+S., Kingdon, D., Startup, H., Molodynski, A., Rosebrock, L., Brown, P., Sheaves, B., Waite, F., \& Bird, J.
+C.
+(2021).
+The revised green et al., Paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
+\emph{Psychological Medicine}, \emph{51}(2), 244--253.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman2003can}{}}%
+Freeman, D., Slater, M., Bebbington, P.
+E., Garety, P.
+A., Kuipers, E., Fowler, D., Met, A., Read, C.
+M., Jordan, J., \& Vinayagamoorthy, V.
+(2003).
+Can virtual reality be used to investigate persecutory ideation?
+\emph{The Journal of Nervous and Mental Disease}, \emph{191}(8), 509--514.
+
+\leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
+Garrido, M. V., \& Prada, M. (2017). KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces. \emph{Frontiers in Psychology}, \emph{8}, 2181.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gobbini2013prioritized}{}}%
+Gobbini, M.
+I., Gors, J.
+D., Halchenko, Y.
+O., Rogers, C., Guntupalli, J.
+S., Hughes, H., \& Cipolli, C.
+(2013).
+Prioritized detection of personally familiar faces.
+\emph{PloS One}, \emph{8}(6), e66620.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
+Goldstein, T.
+R.
+(2009).
+The pleasure of unadulterated sadness: Experiencing sorrow in fiction, nonfiction, and" in person.".
+\emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4), 232.
+
+\leavevmode\vadjust pre{\hypertarget{ref-grapsas2020and}{}}%
+Grapsas, S., Brummelman, E., Back, M.
+D., \& Denissen, J.
+J.
+(2020).
+The {``why''} and {``how''} of narcissism: A process model of narcissistic status pursuit.
+\emph{Perspectives on Psychological Science}, \emph{15}(1), 150--172.
+
+\leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
+Han, S., Li, Y., Liu, S., Xu, Q., Tan, Q., \& Zhang, L.
+(2018).
+Beauty is in the eye of the beholder: The halo effect and generalization effect in the facial attractiveness evaluation.
+\emph{Acta Psychologica Sinica}, \emph{50}(4), 363.
+
+\leavevmode\vadjust pre{\hypertarget{ref-herbst2020gender}{}}%
+Herbst, T.
+H.
+(2020).
+Gender differences in self-perception accuracy: The confidence gap and women leaders' underrepresentation in academia.
+\emph{SA Journal of Industrial Psychology}, \emph{46}(1), 1--8.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hodson2018dark}{}}%
+Hodson, G., Book, A., Visser, B.
+A., Volk, A.
+A., Ashton, M.
+C., \& Lee, K.
+(2018).
+Is the dark triad common factor distinct from low honesty-humility?
+\emph{Journal of Research in Personality}, \emph{73}, 123--129.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hoogers2021effect}{}}%
+Hoogers, E. (2021). \emph{The effect of attitude towards computer generated faces on face perception} {[}\{B.S.\} thesis{]}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hou2019survival}{}}%
+Hou, C., \& Liu, Z.
+(2019).
+The survival processing advantage of face: The memorization of the (un) trustworthy face contributes more to survival adaptation.
+\emph{Evolutionary Psychology}, \emph{17}(2), 1474704919839726.
+
+\leavevmode\vadjust pre{\hypertarget{ref-indovina2007dissociation}{}}%
+Indovina, I., \& Macaluso, E. (2007). Dissociation of stimulus relevance and saliency factors during shifts of visuospatial attention. \emph{Cerebral Cortex}, \emph{17}(7), 1701--1711.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
+Jauk, E., Olaru, G., Schürch, E., Back, M.
+D., \& Morf, C.
+C.
+(2022).
+Validation of the german five-factor narcissism inventory and construction of a brief form using ant colony optimization.
+\emph{Assessment}, 10731911221075761.
+
+\leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
+King, A., \& Dudley, R.
+(2017).
+Paranoia, worry, cognitive avoidance and intolerance of uncertainty in a student population.
+\emph{Journal of Applied Psychology and Social Science}, \emph{3}(2), 70--89.
+
+\leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
+Levidi, M.
+D.
+C., McGrath, A., Kyriakoulis, P., \& Sulikowski, D.
+(2022).
+Understanding criminal decision-making: Links between honesty-humility, perceived risk and negative affect: Psychology, crime \& law.
+\emph{Psychology, Crime and Law}, 1--29.
 
 \leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2017beyond}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Lewandowsky, S., Ecker, U.
-K.
-\& Cook, J.
-Beyond misinformation: Understanding and coping with the {`post-truth'} era.
-\emph{Journal of applied research in memory and cognition} \textbf{6}, 353--369 (2017).}
+Lewandowsky, S., Ecker, U.
+K., \& Cook, J.
+(2017).
+Beyond misinformation: Understanding and coping with the {``post-truth''} era.
+\emph{Journal of Applied Research in Memory and Cognition}, \emph{6}(4), 353--369.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lewin2002sex}{}}%
+Lewin, C., \& Herlitz, A. (2002). Sex differences in face recognition---women's faces make the difference. \emph{Brain and Cognition}, \emph{50}(1), 121--128.
+
+\leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
+Liefooghe, B., Oliveira, M., Leisten, L. M., Hoogers, E., Aarts, H., \& Hortensius, R. (2022). \emph{Faces merely labelled as artificial are trusted less}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-little2011facial}{}}%
+Little, A.
+C., Jones, B.
+C., \& DeBruine, L.
+M.
+(2011).
+Facial attractiveness: Evolutionary based research.
+\emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{366}(1571), 1638--1659.
+
+\leavevmode\vadjust pre{\hypertarget{ref-littrell2020overconfidently}{}}%
+Littrell, S., Fugelsang, J., \& Risko, E. F. (2020). Overconfidently underthinking: Narcissism negatively predicts cognitive reflection. \emph{Thinking \& Reasoning}, \emph{26}(3), 352--380.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lou2015perceptual}{}}%
+Lou, B., Hsu, W.-Y., \& Sajda, P.
+(2015).
+Perceptual salience and reward both influence feedback-related neural activity arising from choice.
+\emph{Journal of Neuroscience}, \emph{35}(38), 13064--13075.
+
+\leavevmode\vadjust pre{\hypertarget{ref-parametersArticle}{}}%
+Lüdecke, D., Ben-Shachar, M., Patil, I., \& Makowski, D.
+(2020).
+Extracting, computing and exploring the parameters of statistical models using {R}.
+\emph{Journal of Open Source Software}, \emph{5}(53), 2445.
+\url{https://doi.org/10.21105/joss.02445}
+
+\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
+Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., \& Makowski, D.
+(2021).
+{performance}: An {R} package for assessment, comparison and testing of statistical models.
+\emph{Journal of Open Source Software}, \emph{6}(60), 3139.
+\url{https://doi.org/10.21105/joss.03139}
+
+\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
+Lüdecke, D., Waggoner, P., \& Makowski, D.
+(2019).
+Insight: A unified interface to access information from model objects in {R}.
+\emph{Journal of Open Source Software}, \emph{4}(38), 1412.
+\url{https://doi.org/10.21105/joss.01412}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2018cognitive}{}}%
+Makowski, D. (2018). \emph{Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal} {[}PhD thesis{]}. Sorbonne Paris Cit{é}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%
+Makowski, D., Ben-Shachar, M., \& Lüdecke, D.
+(2019).
+{bayestestR}: Describing effects and their uncertainty, existence and significance within the {Bayesian} framework.
+\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
+\url{https://doi.org/10.21105/joss.01541}
+
+\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
+Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D.
+(2020).
+Methods and algorithms for correlation analysis in {R}.
+\emph{Journal of Open Source Software}, \emph{5}(51), 2306.
+\url{https://doi.org/10.21105/joss.02306}
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2017being}{}}%
+Makowski, D., Sperduti, M., Nicolas, S., \& Piolino, P. (2017). {``Being there''} and remembering it: Presence improves memory encoding. \emph{Consciousness and Cognition}, \emph{53}, 194--202.
+
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
+Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
+(2019).
+Phenomenal, bodily and brain correlates of fictional reappraisal as an implicit emotion regulation strategy.
+\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 877--897.
+
+\leavevmode\vadjust pre{\hypertarget{ref-marcinkowska2021self}{}}%
+Marcinkowska, U.
+M., Jones, B.
+C., \& Lee, A.
+J.
+(2021).
+Self-rated attractiveness predicts preferences for sexually dimorphic facial characteristics in a culturally diverse sample.
+\emph{Scientific Reports}, \emph{11}(1), 1--8.
+
+\leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
+Martel, C., Pennycook, G., \& Rand, D. G. (2020). Reliance on emotion promotes belief in fake news. \emph{Cognitive Research: Principles and Implications}, \emph{5}(1), 1--20.
 
 \leavevmode\vadjust pre{\hypertarget{ref-mcdonnell2010face}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{McDonnell, R. \& Breidt, M. Face reality: Investigating the uncanny valley for virtual faces. in \emph{ACM SIGGRAPH ASIA 2010 sketches} 1--2 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Tucciarelli, R., Vehar, N.
-\& Tsakiris, M.
-\emph{On the realness of people who do not exist: the social processing of artificial faces}.
-\url{https://osf.io/dnk9x} (2020) doi:\href{https://doi.org/10.31234/osf.io/dnk9x}{10.31234/osf.io/dnk9x}.}
+McDonnell, R., \& Breidt, M. (2010). Face reality: Investigating the uncanny valley for virtual faces. In \emph{ACM SIGGRAPH ASIA 2010 sketches} (pp. 1--2).
+
+\leavevmode\vadjust pre{\hypertarget{ref-michael2021source}{}}%
+Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mishra2019gender}{}}%
+Mishra, M.
+V., Likitlersuang, J., B Wilmer, J., Cohan, S., Germine, L., \& DeGutis, J.
+M.
+(2019).
+Gender differences in familiar face recognition and the influence of sociocultural gender inequality.
+\emph{Scientific Reports}, \emph{9}(1), 1--12.
 
 \leavevmode\vadjust pre{\hypertarget{ref-moshel2022}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Moshel, M.
+Moshel, M.
 L., Robinson, A.
 K., Carlson, T.
+A., \& Grootswagers, T.
+(2022).
+Are you for real?
+Decoding realistic AI-generated faces from neural activity.
+\emph{Vision Research}, \emph{199}, 108079.
+\url{https://doi.org/10.1016/j.visres.2022.108079}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nightingale2022}{}}%
+Nightingale, S.
+J., \& Farid, H.
+(2022).
+AI-synthesized faces are indistinguishable from real faces and more trustworthy.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(8), e2120481119.
+\url{https://doi.org/10.1073/pnas.2120481119}
+
+\leavevmode\vadjust pre{\hypertarget{ref-o2021grandiose}{}}%
+O'Reilly, C.
+A., \& Hall, N.
+(2021).
+Grandiose narcissists and decision making: Impulsive, overconfident, and skeptical of experts--but seldom in doubt.
+\emph{Personality and Individual Differences}, \emph{168}, 110280.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
+Pantserev, K.
+(2020).
+\emph{The malicious use of AI-based deepfake technology as the new threat to psychological security and political stability} (pp.
+37--55).
+\url{https://doi.org/10.1007/978-3-030-35746-7_3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peer2022}{}}%
+Peer, E., Rothschild, D., Gordon, A., Evernden, Z., \& Damer, E.
+(2022).
+Data quality of platforms and panels for online behavioral research.
+\emph{Behavior Research Methods}, \emph{54}(4), 1643--1662.
+\url{https://doi.org/10.3758/s13428-021-01694-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pehlivanoglu2021role}{}}%
+Pehlivanoglu, D., Lin, T., Deceus, F., Heemskerk, A., Ebner, N.
+C., \& Cahill, B.
+S.
+(2021).
+The role of analytical reasoning and source credibility on the evaluation of real and fake full-length news articles.
+\emph{Cognitive Research: Principles and Implications}, \emph{6}(1), 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-pennycook2019lazy}{}}%
+Pennycook, G., \& Rand, D. G. (2019). Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning. \emph{Cognition}, \emph{188}, 39--50.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
+Peters, L., Sunderland, M., Andrews, G., Rapee, R.
+M., \& Mattick, R.
+P.
+(2012).
+Development of a short form social interaction anxiety (SIAS) and social phobia scale (SPS) using nonparametric item response theory: The SIAS-6 and the SPS-6.
+\emph{Psychological Assessment}, \emph{24}(1), 66.
+
+\leavevmode\vadjust pre{\hypertarget{ref-petty1986elaboration}{}}%
+Petty, R. E., \& Cacioppo, J. T. (1986). The elaboration likelihood model of persuasion. In \emph{Communication and persuasion} (pp. 1--24). Springer.
+
+\leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
+Piksa, M., Noworyta, K., Piasecki, J., Gwiazdzinski, P., Gundersen, A.
+B., Kunst, J., \& Rygula, R.
+(2022).
+Cognitive processes and personality traits underlying four phenotypes of susceptibility to (mis) information.
+\emph{Frontiers in Psychiatry}, 1142.
+
+\leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
+Qi, Y., \& Ying, J. (2022). Gender biases in the accuracy of facial judgments: Facial attractiveness and perceived socioeconomic status. \emph{Frontiers in Psychology}, \emph{13}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
+R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
+Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
+
+\leavevmode\vadjust pre{\hypertarget{ref-said2022artificial}{}}%
+Said, N., Potinteu, A.-E., Brich, I., Buder, J., Schumm, H., \& Huff, M. (2022). \emph{An artificial intelligence perspective: How knowledge and confidence shape risk and opportunity perception}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
+Sanchez-Vives, M. V., \& Slater, M. (2005). From presence to consciousness through virtual reality. \emph{Nature Reviews Neuroscience}, \emph{6}(4), 332--339.
+
+\leavevmode\vadjust pre{\hypertarget{ref-schepman2020initial}{}}%
+Schepman, A., \& Rodway, P. (2020). Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in Human Behavior Reports}, \emph{1}, 100014.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
+Sibley, C., Luyten, N., Wolfman, M., Mobberley, A., Wootton, L.
+W., Hammond, M., Sengupta, N., Perry, R., West-Newman, T., Wilson, M., McLellan, L., Hoverd, W.
+J., \& Robertson, A.
+(2011).
+The mini-IPIP6: Validation and extension of a short measure of the big-six factors of personality in new zealand.
+\emph{New Zealand Journal of Psychology}, \emph{40}, 142--159.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sindermann2020short}{}}%
+Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology}, \emph{36}, 44--48.
+
+\leavevmode\vadjust pre{\hypertarget{ref-skora2022functional}{}}%
+Skora, L., Livermore, J., \& Roelofs, K. (2022). The functional role of cardiac activity in perception and action. \emph{Neuroscience \& Biobehavioral Reviews}, 104655.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
+Sobieraj, S., \& Krämer, N. C. (2014). What is beautiful in cyberspace? Communication with attractive avatars. \emph{International Conference on Social Computing and Social Media}, 125--136.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sommer2013sex}{}}%
+Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A., \& Wilhelm, O. (2013). Sex differences in face cognition. \emph{Acta Psychologica}, \emph{142}(1), 62--73.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperduti2016paradox}{}}%
+Sperduti, M., Arcangeli, M., Makowski, D., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
+(2016).
+The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance.
+\emph{Acta Psychologica}, \emph{165}, 53--59.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sperduti2017distinctive}{}}%
+Sperduti, M., Makowski, D., Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
+(2017).
+The distinctive role of executive functions in implicit emotion regulation.
+\emph{Acta Psychologica}, \emph{173}, 13--20.
+
+\leavevmode\vadjust pre{\hypertarget{ref-spielmann2020predictive}{}}%
+Spielmann, S.
+S., Maxwell, J.
+A., MacDonald, G., Peragine, D., \& Impett, E.
 A.
-\& Grootswagers, T.
-\href{https://doi.org/10.1016/j.visres.2022.108079}{Are you for real?
-Decoding realistic AI-generated faces from neural activity}.
-\emph{Vision Research} \textbf{199}, 108079 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2018cognitive}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Makowski, D. Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal. (Sorbonne Paris Cit{é}, 2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Makowski, D.
-\emph{et al.} Phenomenal, bodily and brain correlates of fictional reappraisal as an implicit emotion regulation strategy.
-\emph{Cognitive, Affective, \& Behavioral Neuroscience} \textbf{19}, 877--897 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-michael2021source}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Michael, R. B. \& Sanson, M. Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies} \textbf{11}, 119 (2021).}
+(2020).
+The predictive effects of fear of being single on physical attractiveness and less selective partner selection strategies.
+\emph{Journal of Social and Personal Relationships}, \emph{37}(1), 100--123.
 
 \leavevmode\vadjust pre{\hypertarget{ref-susmann2021persuasion}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Susmann, M. W. \emph{et al.} Persuasion amidst a pandemic: Insights from the elaboration likelihood model. \emph{European Review of Social Psychology} 1--37 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-petty1986elaboration}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Petty, R. E. \& Cacioppo, J. T. The elaboration likelihood model of persuasion. in \emph{Communication and persuasion} 1--24 (Springer, 1986).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-berghel2018weaponizing}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Berghel, H. Weaponizing twitter litter: Abuse-forming networks and social media. \emph{Computer} \textbf{51}, 70--73 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Chen, Y., Conroy, N.
-K.
-\& Rubin, V.
-L.
-News in an online world: The need for an {`automatic crap detector'}.
-\emph{Proceedings of the Association for Information Science and Technology} \textbf{52}, 1--4 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Bryanov, K. \& Vziatysheva, V. Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS one} \textbf{16}, e0253717 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecker2022psychological}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Ecker, U. K. \emph{et al.} The psychological drivers of misinformation belief and its resistance to correction. \emph{Nature Reviews Psychology} \textbf{1}, 13--29 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sindermann2020short}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Sindermann, C., Cooper, A. \& Montag, C. A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology} \textbf{36}, 44--48 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pehlivanoglu2021role}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Pehlivanoglu, D.
-\emph{et al.} The role of analytical reasoning and source credibility on the evaluation of real and fake full-length news articles.
-\emph{Cognitive research: principles and implications} \textbf{6}, 1--12 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pennycook2019lazy}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Pennycook, G.
-\& Rand, D.
-G.
-Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning.
-\emph{Cognition} \textbf{188}, 39--50 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Britt, M.
-A., Rouet, J.-F., Blaum, D.
-\& Millis, K.
-A reasoned approach to dealing with fake news.
-\emph{Policy Insights from the Behavioral and Brain Sciences} \textbf{6}, 94--101 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Piksa, M. \emph{et al.} Cognitive processes and personality traits underlying four phenotypes of susceptibility to (mis) information. \emph{Frontiers in psychiatry} 1142 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Sanchez-Vives, M. V. \& Slater, M. From presence to consciousness through virtual reality. \emph{Nature Reviews Neuroscience} \textbf{6}, 332--339 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2017being}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Makowski, D., Sperduti, M., Nicolas, S.
-\& Piolino, P.
-{`Being there'} and remembering it: Presence improves memory encoding.
-\emph{Consciousness and cognition} \textbf{53}, 194--202 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sperduti2017distinctive}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Sperduti, M. \emph{et al.} The distinctive role of executive functions in implicit emotion regulation. \emph{Acta Psychologica} \textbf{173}, 13--20 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Martel, C., Pennycook, G. \& Rand, D. G. Reliance on emotion promotes belief in fake news. \emph{Cognitive research: principles and implications} \textbf{5}, 1--20 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Bago, B., Rosenzweig, L.
-R., Berinsky, A.
+Susmann, M.
+W., Xu, M., Clark, J.
+K., Wallace, L.
+E., Blankenship, K.
+L., Philipp-Muller, A.
+Z., Luttrell, A., Wegener, D.
+T., \& Petty, R.
+E.
+(2021).
+Persuasion amidst a pandemic: Insights from the elaboration likelihood model.
+\emph{European Review of Social Psychology}, 1--37.
+
+\leavevmode\vadjust pre{\hypertarget{ref-taylor2009neural}{}}%
+Taylor, M.
+J., Arsalidou, M., Bayless, S.
+J., Morris, D., Evans, J.
+W., \& Barbeau, E.
 J.
-\& Rand, D.
-G.
-Emotion may predict susceptibility to fake news but emotion regulation does not seem to help.
-\emph{Cognition and Emotion} 1--15 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sperduti2016paradox}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Sperduti, M. \emph{et al.} The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance. \emph{Acta psychologica} \textbf{165}, 53--59 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Goldstein, T.
-R.
-The pleasure of unadulterated sadness: Experiencing sorrow in fiction, nonfiction, and" in person.".
-\emph{Psychology of Aesthetics, Creativity, and the Arts} \textbf{3}, 232 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-begg1992dissociation}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Begg, I.
-M., Anas, A.
-\& Farinacci, S.
-Dissociation of processes in belief: Source recollection, statement familiarity, and the illusion of truth.
-\emph{Journal of Experimental Psychology: General} \textbf{121}, 446 (1992).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Sobieraj, S.
-\& Krämer, N.
-C.
-What is beautiful in cyberspace?
-Communication with attractive avatars.
-in \emph{International conference on social computing and social media} 125--136 (Springer, 2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-balas2017}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Balas, B.
-\& Pacella, J.
-\href{https://doi.org/10.1016/j.chb.2017.08.045}{Trustworthiness perception is disrupted in artificial faces}.
-\emph{Computers in Human Behavior} \textbf{77}, (2017).}
+(2009).
+Neural correlates of personally familiar faces: Parents, partner and own faces.
+\emph{Human Brain Mapping}, \emph{30}(7), 2008--2020.
 
 \leavevmode\vadjust pre{\hypertarget{ref-tsikandilakis2019beauty}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Tsikandilakis, M., Bali, P.
-\& Chapman, P.
+Tsikandilakis, M., Bali, P., \& Chapman, P.
+(2019).
 Beauty is in the eye of the beholder: The appraisal of facial attractiveness and its relation to conscious awareness.
-\emph{Perception} \textbf{48}, 72--92 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Calbi, M.
-\emph{et al.} \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2017.01684}{How context influences our perception of emotional faces: A behavioral study on the kuleshov effect}.
-\emph{Frontiers in Psychology} \textbf{8}, (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Liefooghe, B. \emph{et al.} Faces merely labelled as artificial are trusted less. (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Bartosik, B., Wojcik, G.
-M., Brzezicka, A.
-\& Kawiak, A.
-Are you able to trust me?
-Analysis of the relationships between personality traits and the assessment of attractiveness and trust.
-\emph{Frontiers in Human Neuroscience} \textbf{15}, 685530 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Garrido, M.
-V.
-\& Prada, M.
-KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces.
-\emph{Frontiers in Psychology} \textbf{8}, 2181 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-little2011facial}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Little, A.
-C., Jones, B.
-C.
-\& DeBruine, L.
-M.
-Facial attractiveness: Evolutionary based research.
-\emph{Philosophical Transactions of the Royal Society B: Biological Sciences} \textbf{366}, 1638--1659 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{Sibley, C.
-\emph{et al.} The mini-IPIP6: Validation and extension of a short measure of the big-six factors of personality in new zealand.
-\emph{New Zealand Journal of Psychology} \textbf{40}, 142--159 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{Peters, L., Sunderland, M., Andrews, G., Rapee, R.
-M.
-\& Mattick, R.
-P.
-Development of a short form social interaction anxiety (SIAS) and social phobia scale (SPS) using nonparametric item response theory: The SIAS-6 and the SPS-6.
-\emph{Psychological assessment} \textbf{24}, 66 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Jauk, E., Olaru, G., Schürch, E., Back, M.
-D.
-\& Morf, C.
-C.
-Validation of the german five-factor narcissism inventory and construction of a brief form using ant colony optimization.
-\emph{Assessment} 10731911221075761 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2021revised}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Freeman, D.
-\emph{et al.} The revised green et al., Paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
-\emph{Psychological Medicine} \textbf{51}, 244--253 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Carleton, R.
-N., Norton, M.
-P.
-J.
-\& Asmundson, G.
-J.
-Fearing the unknown: A short version of the intolerance of uncertainty scale.
-\emph{Journal of anxiety disorders} \textbf{21}, 105--117 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-marcinkowska2021self}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Marcinkowska, U.
-M., Jones, B.
-C.
-\& Lee, A.
-J.
-Self-rated attractiveness predicts preferences for sexually dimorphic facial characteristics in a culturally diverse sample.
-\emph{Scientific Reports} \textbf{11}, 1--8 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-spielmann2020predictive}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Spielmann, S.
-S., Maxwell, J.
-A., MacDonald, G., Peragine, D.
-\& Impett, E.
-A.
-The predictive effects of fear of being single on physical attractiveness and less selective partner selection strategies.
-\emph{Journal of Social and Personal Relationships} \textbf{37}, 100--123 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schepman2020initial}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Schepman, A. \& Rodway, P. Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in human behavior reports} \textbf{1}, 100014 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021broadening}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Chen, J. M., Norman, J. B. \& Nam, Y. Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods} \textbf{53}, 371--389 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Rhodes, G. \emph{et al.} The evolutionary psychology of facial beauty. \emph{Annual review of psychology} \textbf{57}, 199 (2006).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Han, S.
-\emph{et al.} Beauty is in the eye of the beholder: The halo effect and generalization effect in the facial attractiveness evaluation.
-\emph{Acta Psychologica Sinica} \textbf{50}, 363 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{De Leeuw, J. R. jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior research methods} \textbf{47}, 1--12 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peer2022}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Peer, E., Rothschild, D., Gordon, A., Evernden, Z.
-\& Damer, E.
-\href{https://doi.org/10.3758/s13428-021-01694-3}{Data quality of platforms and panels for online behavioral research}.
-\emph{Behavior Research Methods} \textbf{54}, 1643--1662 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Wickham, H. \emph{et al.} \href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}. \emph{Journal of Open Source Software} \textbf{4}, 1686 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Lüdecke, D., Waggoner, P.
-\& Makowski, D.
-\href{https://doi.org/10.21105/joss.01412}{Insight: A unified interface to access information from model objects in {R}}.
-\emph{JOSS} \textbf{4}, 1412 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Makowski, D., Ben-Shachar, M.
-\& Lüdecke, D.
-\href{https://doi.org/10.21105/joss.01541}{{bayestestR}: Describing effects and their uncertainty, existence and significance within the {Bayesian} framework}.
-\emph{JOSS} \textbf{4}, 1541 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P.
-\& Makowski, D.
-\href{https://doi.org/10.21105/joss.03139}{{performance}: An {R} package for assessment, comparison and testing of statistical models}.
-\emph{JOSS} \textbf{6}, 3139 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-parametersArticle}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Lüdecke, D., Ben-Shachar, M., Patil, I.
-\& Makowski, D.
-\href{https://doi.org/10.21105/joss.02445}{Extracting, computing and exploring the parameters of statistical models using {R}}.
-\emph{JOSS} \textbf{5}, 2445 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Makowski, D., Ben-Shachar, M., Patil, I.
-\& Lüdecke, D.
-\href{https://doi.org/10.21105/joss.02306}{Methods and algorithms for correlation analysis in {R}}.
-\emph{JOSS} \textbf{5}, 2306 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buunk2002age}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Buunk, B.
-P., Dijkstra, P., Fetchenhauer, D.
-\& Kenrick, D.
-T.
-Age and gender differences in mate selection criteria for various involvement levels.
-\emph{Personal relationships} \textbf{9}, 271--278 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Qi, Y. \& Ying, J. Gender biases in the accuracy of facial judgments: Facial attractiveness and perceived socioeconomic status. \emph{Frontiers in Psychology} \textbf{13}, (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Fink, B., Neave, N., Manning, J.
-T.
-\& Grammer, K.
-Facial symmetry and judgements of attractiveness, health and personality.
-\emph{Personality and Individual differences} \textbf{41}, 491--499 (2006).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lou2015perceptual}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Lou, B., Hsu, W.-Y.
-\& Sajda, P.
-Perceptual salience and reward both influence feedback-related neural activity arising from choice.
-\emph{Journal of Neuroscience} \textbf{35}, 13064--13075 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-indovina2007dissociation}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Indovina, I. \& Macaluso, E. Dissociation of stimulus relevance and saliency factors during shifts of visuospatial attention. \emph{Cerebral Cortex} \textbf{17}, 1701--1711 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-skora2022functional}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Skora, L., Livermore, J. \& Roelofs, K. The functional role of cardiac activity in perception and action. \emph{Neuroscience \& Biobehavioral Reviews} 104655 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogers2021effect}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Hoogers, E. The effect of attitude towards computer generated faces on face perception. (2021).}
+\emph{Perception}, \emph{48}(1), 72--92.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
+Tucciarelli, R., Vehar, N., \& Tsakiris, M. (2020). \emph{On the realness of people who do not exist: the social processing of artificial faces}. \url{https://doi.org/10.31234/osf.io/dnk9x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-van2020sex}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Van Den Akker, O.
+Van Den Akker, O.
 R., Assen, M.
 A.
-van, Van Vugt, M.
-\& Wicherts, J.
+van, Van Vugt, M., \& Wicherts, J.
 M.
+(2020).
 Sex differences in trust and trustworthiness: A meta-analysis of the trust game and the gift-exchange game.
-\emph{Journal of Economic Psychology} \textbf{81}, 102329 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hou2019survival}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Hou, C.
-\& Liu, Z.
-The survival processing advantage of face: The memorization of the (un) trustworthy face contributes more to survival adaptation.
-\emph{Evolutionary Psychology} \textbf{17}, 1474704919839726 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mishra2019gender}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Mishra, M. V. \emph{et al.} Gender differences in familiar face recognition and the influence of sociocultural gender inequality. \emph{Scientific reports} \textbf{9}, 1--12 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewin2002sex}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{Lewin, C. \& Herlitz, A. Sex differences in face recognition---women's faces make the difference. \emph{Brain and cognition} \textbf{50}, 121--128 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sommer2013sex}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A. \& Wilhelm, O. Sex differences in face cognition. \emph{Acta psychologica} \textbf{142}, 62--73 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bailey2021gender}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Bailey, A. A gender in-group effect on facial recall. (University of Tasmania, 2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-herbst2020gender}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{Herbst, T.
-H.
-Gender differences in self-perception accuracy: The confidence gap and women leaders' underrepresentation in academia.
-\emph{SA Journal of Industrial Psychology} \textbf{46}, 1--8 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Levidi, M.
-D.
-C., McGrath, A., Kyriakoulis, P.
-\& Sulikowski, D.
-Understanding criminal decision-making: Links between honesty-humility, perceived risk and negative affect: Psychology, crime \& law.
-\emph{Psychology, Crime and Law} 1--29 (2022).}
+\emph{Journal of Economic Psychology}, \emph{81}, 102329.
 
 \leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Weller, J.
-A.
-\& Thulin, E.
+Weller, J.
+A., \& Thulin, E.
 W.
+(2012).
 Do honest people take fewer risks?
 Personality correlates of risk-taking to achieve gains and avoid losses in HEXACO space.
-\emph{Personality and individual differences} \textbf{53}, 923--926 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-littrell2020overconfidently}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Littrell, S., Fugelsang, J.
-\& Risko, E.
-F.
-Overconfidently underthinking: Narcissism negatively predicts cognitive reflection.
-\emph{Thinking \& Reasoning} \textbf{26}, 352--380 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ahadzadeh2021social}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Ahadzadeh, A.
-S., Ong, F.
-S.
-\& Wu, S.
-L.
-Social media skepticism and belief in conspiracy theories about COVID-19: The moderating role of the dark triad.
-\emph{Current Psychology} 1--13 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carolan2017searching}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{Carolan, P.
-L.
-Searching {`inaffectively'}: A behavioral, psychometric, and electroencephalographic investigation of psychopathic personality and visual-spatial attention.
-(Arts \& Social Sciences: Department of Psychology, 2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grapsas2020and}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{Grapsas, S., Brummelman, E., Back, M.
-D.
-\& Denissen, J.
-J.
-The {`why'} and {`how'} of narcissism: A process model of narcissistic status pursuit.
-\emph{Perspectives on Psychological Science} \textbf{15}, 150--172 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-eddy2021self}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{Eddy, C. M. Self-serving social strategies: A systematic review of social cognition in narcissism. \emph{Current Psychology} 1--19 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hodson2018dark}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{Hodson, G. \emph{et al.} Is the dark triad common factor distinct from low honesty-humility? \emph{Journal of Research in Personality} \textbf{73}, 123--129 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-campbell2004narcissism}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{Campbell, W. K., Goodie, A. S. \& Foster, J. D. Narcissism, confidence, and risk attitude. \emph{Journal of behavioral decision making} \textbf{17}, 297--311 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{Chatterjee, A. \& Pollock, T. G. Master of puppets: How narcissistic CEOs construct their professional worlds. \emph{Academy of Management Review} \textbf{42}, 703--725 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brunell2017narcissism}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{Brunell, A. B. \& Buelow, M. T. Narcissism and performance on behavioral decision-making tasks. \emph{Journal of Behavioral Decision Making} \textbf{30}, 3--14 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-o2021grandiose}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{O'Reilly, C.
-A.
-\& Hall, N.
-Grandiose narcissists and decision making: Impulsive, overconfident, and skeptical of experts--but seldom in doubt.
-\emph{Personality and Individual Differences} \textbf{168}, 110280 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fornells2015people}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{Fornells-Ambrojo, M.
-\emph{et al.} How do people with persecutory delusions evaluate threat in a controlled social environment?
-A qualitative study using virtual reality.
-\emph{Behavioural and Cognitive Psychotherapy} \textbf{43}, 89--107 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2003can}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{Freeman, D. \emph{et al.} Can virtual reality be used to investigate persecutory ideation? \emph{The Journal of nervous and mental disease} \textbf{191}, 509--514 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{King, A.
-\& Dudley, R.
-Paranoia, worry, cognitive avoidance and intolerance of uncertainty in a student population.
-\emph{Journal of Applied Psychology and Social Science} \textbf{3}, 70--89 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2005psychology}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{Freeman, D.
-\emph{et al.} The psychology of persecutory ideation II: A virtual reality experimental study.
-\emph{The Journal of nervous and mental disease} \textbf{193}, 309--315 (2005).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-said2022artificial}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{Said, N. \emph{et al.} An artificial intelligence perspective: How knowledge and confidence shape risk and opportunity perception. (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-abraham2009reality}{}}%
-\CSLLeftMargin{88. }%
-\CSLRightInline{Abraham, A.
-\& Von Cramon, D.
-Y.
-Reality= relevance?
-Insights from spontaneous modulations of the brain's default network when telling apart reality from fiction.
-\emph{PloS one} \textbf{4}, e4741 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gobbini2013prioritized}{}}%
-\CSLLeftMargin{89. }%
-\CSLRightInline{Gobbini, M. I. \emph{et al.} Prioritized detection of personally familiar faces. \emph{PloS one} \textbf{8}, e66620 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-taylor2009neural}{}}%
-\CSLLeftMargin{90. }%
-\CSLRightInline{Taylor, M. J. \emph{et al.} Neural correlates of personally familiar faces: Parents, partner and own faces. \emph{Human brain mapping} \textbf{30}, 2008--2020 (2009).}
+\emph{Personality and Individual Differences}, \emph{53}(7), 923--926.
+
+\leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
+L., Miller, E., Bache, S.
+M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
+P., Spinu, V., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
 

### 2023-03-28 experiment/parameters.js
specify items from orignal scale

@@ -396,14 +396,14 @@ var IUS_dim = [
 
 var GAAIS = [
     "<b>I think current Artificial Intelligence algorithms can generate very realistic images</b><br>",
-    "<b>Organisations use Artificial Intelligence unethically</b><br>",
+    "<b>Organisations use Artificial Intelligence unethically</b><br>", //OG scale item 3
     "<b>I think videos generated by Artificial Intelligence are impossible to distinguish from real videos</b><br>",
-    "<b>I am interested in using artificially intelligent systems in my daily life</b><br>",
+    "<b>I am interested in using artificially intelligent systems in my daily life</b><br>", //OG scale item 7
     "<b>I think Computer-Generated Imagery (CGI) software is capable of perfectly imitating reality</b><br>",
-    "<b>I think Artificial Intelligence is dangerous</b><br>",
+    "<b>I think Artificial Intelligence is dangerous</b><br>", //OG scale item 10
     "<b>I think current Artificial Intelligence algorithms can generate very realistic videos</b><br>",
-    "<b>Artificial Intelligence is exciting</b><br>",
-    "<b>There are many beneficial applications of Artificial Intelligence</b><br>",
+    "<b>Artificial Intelligence is exciting</b><br>", // OG scale item 12
+    "<b>There are many beneficial applications of Artificial Intelligence</b><br>", //OG scale item 14
     "<b>Images of faces or people generated by Artificial Intelligence will contain errors</b><br>"
 ]
 

### 2023-03-28 submission/manuscript.Rmd
add reference

@@
 For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like "being there", as if the object of experience was real - when engaged in a fictional movie or a VR environment [@sanchez2005presence; @makowski2017being].
+Indeed, participants' self-reported emotional arousal were found to significantly predict the probability that they would perceive images as real [@azevedo2020body].
 Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
 In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion].
+In fact, photojournalistic images labelled fake were associated with greater surprise when they were highly arousing [@azevedo2020body].
 Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in guiding our appraisal of a stimulus.

### 2023-03-29 submission/manuscript.Rmd
update

--- 2022-12-19 submission/manuscript.Rmd
@@
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
-
-  **Significance Statement.** Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
-Given the evolutionary importance of perceived attractiveness, we investigated if faces rated as more attractive would be more likely judged as real (vs "fake", i.e., artificially generated).
-We indeed found a gender-dependent role of attractiveness on reality judgements, as well as a global influence of personality traits such as narcissism.
-These results are discussed in the light of consciousness psychology and evolutionary science, and are relevant to AI-researchers and misinformation management agencies.
 

### 2023-03-29 submission/manuscript.tex
update

@@
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
-
-\textbf{Significance Statement.} Computer-generated images of faces are likely to become objectively indistinguishable from real photos in the near future, creating important issues in the context of fake news and misinformation, as well as virtual reality developments.
-Given the evolutionary importance of perceived attractiveness, we investigated if faces rated as more attractive would be more likely judged as real (vs ``fake'', i.e., artificially generated).
-We indeed found a gender-dependent role of attractiveness on reality judgements, as well as a global influence of personality traits such as narcissism.
-These results are discussed in the light of consciousness psychology and evolutionary science, and are relevant to AI-researchers and misinformation management agencies.
 }

### 2023-04-03 analysis.Rmd
Add check against norms

--- 2022-10-13 analysis.Rmd
@@
   # More than 2 attention check fails
-  "611d03b822d4c8e041ea0c32_m0knb",
-  "5f0f0a2a8b2a480447f31b21_lqgpz",
+  "S113",
+  "S049",
   # Very short duration for questionnaire + low rating correlations (< 0.1)
-  "5eaef8702b68455d6e130595_ptsga",
-  "61356174c090b0083f131e01_asm81",
+  "S035",
+  "S117",
   # Prefered not answering to sexual orientation: further analysis impossible
-  "60eb34f117838a34a29a69d3_rxv85"
+  "S101"
 )
@@
   # 1 attention check failed
-  "5dc3485219ca0326027ce91f_37ho9",
-  "5c6414540821d30001046198_x9q7r",
-  "60dd7b03f1e72d38230df476_9yh9n",
-  "5962799cb752840001ca478b_jh4sl",
-  "5f44c23fbf2ddb80bcdf0edc_dnbny",
-  "5e80370d48b5f47170e30e5c_5w2gf"
+  "S027",
+  "S017",
+  "S097",
+  "S006",
+  "S055",
+  "S033"
 )
@@
   p <- df |>
-    ggplot(aes_string(x = var, y = "Real")) +
-    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+    ggplot(aes(x = .data[[var]], y = .data[["Real"]])) +
+    stat_density_2d(aes(fill = after_stat(density)), geom = "raster", contour = FALSE) +
     scale_fill_gradientn(colors = c("white", fill), guide = "none") +
@@
     geom_ribbon(data = y_real, aes(y = Predicted, group = Sex, fill = Sex, ymin = CI_low, ymax = CI_high), alpha = 1 / 3) +
-    geom_line(data = y_real, aes(y = Predicted, color = Sex), size=1) +
+    geom_line(data = y_real, aes(y = Predicted, color = Sex), linewidth=1) +
     # geom_ribbon(data = trend, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 1/6) +
@@
 rez_fa$p
+```
+
+### Cross-Validate with Normmative Scores
+
+```{r make_models_norms, message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width, cache=cache}
+rez_at_norm <- filter(df, Stimulus_Interest == TRUE) |> 
+  mutate(Norms_Attractive = normalize(Norms_Attractive)) |> 
+  make_model(
+    formula = "Sex / poly(Norms_Attractive, 2) + (1|Participant) + (1|Stimulus)",
+    var = "Norms_Attractive", fill = "#F44336"
+)
+
+rez_at_norm$p
+
+rez_tr_norm <- filter(df, Stimulus_Interest == TRUE) |> 
+  mutate(Norms_Trustworthy = normalize(Norms_Trustworthy)) |> 
+  make_model(
+    formula = "Sex / poly(Norms_Trustworthy, 2) + (1|Participant) + (1|Stimulus)",
+    var = "Norms_Trustworthy", fill = "#4CAF50"
+)
+
+rez_tr_norm$p
 ```

### 2023-04-03 submission/manuscript.Rmd
Add check against norms

@@
 
-keywords          : "attractiveness, simulation monitoring, fiction, deep fakes, sense of reality"
+keywords          : "attractiveness, AI-generated images, fiction, ffafke news, sense of reality"
 wordcount         : "4088"
@@
 
-While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation [@nightingale2022; @tucciarelli2020; @moshel2022].
-Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
+While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies or via recent algorithms such as GANs or diffusion models often include distortions or lack certain key details that makes them visually distinct from real images, @mcdonnell2010face; @corvi2022detection], it is fair to assume that these technical limitations will become negligible in the near future.
+This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos [@nightingale2022; @tucciarelli2020; @moshel2022].
+Such technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective "physical" characteristics, how can we form judgements regarding their nature?
 
@@
 With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
 Thus, in the absence of clear contextual information, what drives our beliefs of reality?
@@
 Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion].
-In fact, photojournalistic images labelled fake were associated with greater surprise when they were highly arousing [@azevedo2020body].
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion], and higher neurophysiological arousal was predictive of judging realistic images a real [@azevedo2020body].
 Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in guiding our appraisal of a stimulus.
@@
 Conversely, @liefooghe2022faces reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
-Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
+Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness contributes to the formation of reality beliefs - has received little attention to date.
 
@@
 
+All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
+
 ### Ethics Statement
@@
 All participants provided their informed consent prior to participation and were incentivized after completing the study.
-
-<!-- In line with open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
--->
 
@@
 
-One hundred and fifty participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022].
+Although the main part of the study relied on within-subject design (with 109 trials per participant), we also planned to do between-participants analyses, thus aiming at collecting a larger sample than traditionally used in experimental psychology (with budget availability as the main constraint).
+One hundred and fifty participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022; douglas2023data].
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-We excluded 5 participants that either failed 2 (\>= 66%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
+We excluded 5 participants that either failed 2 (\>= 66.6%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
 The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3% females, 51.0% males, 0.7% others).
@@
 
-The real-fake ratings (measured originally on a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
+The real-fake ratings (measured originally with a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
 The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\>= 0) as opposed to fake (\< 0).
@@
 
-### Manipulation Check
+<!-- ### Manipulation Check -->
 
@@
 Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
+
+A related issue is the possible contamination of the reality judgements by the prior explicit prompting
+
 Moreover, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.

### 2023-04-03 preprocessing.R

@@ -1,227 +1,0 @@
-unnest <- function(file, scale) {
-  data <- file |>
-    dplyr::filter(screen == scale) |>
-    dplyr::select(participant_id, response) |>
-    jsontools::json_unnest_wider(col = "response")
-  data
-}
-
-preprocess_raw <- function(file) {
-  data <- read.csv(file)
-
-  # Preprocess
-  if (!"end_screen" %in% data$screen) {
-    print(paste0("Warning: Incomplete data for ", file))
-    return(data.frame())
-  }
-
-  # Demographics
-  dem <- data[data$screen == "demographics" & !is.na(data$screen), "response"]
-
-  # Trials
-  block1 <- data[data$screen == "stimuli" & data$block_number == "1", ]
-  block2 <- data[data$screen == "stimuli" & data$block_number == "2", ]
-
-  answers <- unnest(data, "questionnaire")
-  realness_answers <- unnest(data, "perceived_realness")
-
-  # Realness Block
-  realness_df <- data.frame(
-    Block2_Trial = as.numeric(block2$trial_number),
-    Stimulus = gsub(".jgp", "", gsub("stimuli/AMFD/", "", block2$stimulus)),
-    Delay2 = as.numeric(block2$time_elapsed),
-    Real_RT = as.numeric(data[data$screen == "perceived_realness", "rt"]),
-    Real = datawizard::change_scale(realness_answers$perceived_realness,
-                                    to = c(0.0001, 0.9999), range = c(0, 1)
-    ),
-    Belief_Answer = datawizard::change_scale(realness_answers$perceived_realness,
-      to = c(-1, 1), range = c(0, 1)
-    ),
-    Belief = ifelse(realness_answers$perceived_realness >= 0.5, "Real", "Fake"),
-    Belief_Confidence = datawizard::change_scale(abs(datawizard::change_scale(realness_answers$perceived_realness,
-      to = c(-1, 1), range = c(0, 1)
-    )),
-    to = c(0.0001, 0.9999), range = c(0, 1)
-    )
-  )
-
-  # Info
-  info <- data[data$screen == "browser_info" & !is.na(data$screen), ]
-
-  df <- data.frame(
[…]

### 2023-04-10 submission/manuscript.Rmd
update

@@
 
-AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
+AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing [@dawel2021systematic], in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
 Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real [@tucciarelli2020].
@@
 
-This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory
-[outlined in @makowski2018cognitive; @makowski2019phenomenal],
-which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+AI-generated content, and in particular realistic images, is becoming commonplace and carries important risks for misinformation and black-mailing [@viola2023designed], emphasizing the need too understand the different components that come into play into the formation of reality beliefs.
+This exploratory study primarily aims at investigating the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the *affective reality theory*
+[outlined in @makowski2018cognitive; @makowski2019phenomenal, see **BLOGPOST**  for a summary],
+which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
@@
 
-Only one image file yielded a strong simulation monitoring bias (\> 85%), being classified as fake by 88.7% of participants.
+<!-- Only one image file yielded a strong simulation monitoring bias (\> 85%), being classified as fake by 88.7% of participants.
 This image was removed from further analysis, leaving 108 trials per participant.
+-->
 On average, across participants, 44% of images (95%\~CI [0.12, 0.64]) were judged as fake and 56% of images (95%\~CI [0.36, 0.84]) as real.
@@
 This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
+
+Note that we also tested as predictors the normative attractiveness and trustworthiness scores (i.e., the average values from the stimuli database validation), which showed a significant positive linear relationship between beliefs of reality and attractiveness, as well as  trustworthiness, only for males (see Supplementary Analysis for details).
 
@@
 
-A related issue is the possible contamination of the reality judgements by the prior explicit prompting
+A related issue is the effect of the reality judgements by the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
+Given this prior information given to participants, it seems like our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwaranted.
+After all,
 
-Moreover, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+In principle, a control condition without requiring a cover story with AI-generated images.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum.
+That said, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
+This can be studied by modulating this expectation in a controlled fashion (e.g., "most of the images *but a few* a real" vs.
+"most of the images *but a few* a fake") or inventing some implicit way of measuring reality belief that would not require the explicit introduction oof the concept of fake vs.
+real to participants.
+
+Moreover, although consistent in their directions across  models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
 Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.

### 2023-04-12 submission/manuscript.Rmd
update manu

@@
 
-keywords          : "attractiveness, AI-generated images, fiction, ffafke news, sense of reality"
-wordcount         : "4088"
+keywords          : "attractiveness, AI-generated images, fiction, fake news, sense of reality"
+wordcount         : "4970"
 bibliography      : references.bib
@@
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2018cognitive; @makowski2019phenomenal].
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., which journal was the information published in), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
 However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
@@
 Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion], and higher neurophysiological arousal was predictive of judging realistic images a real [@azevedo2020body].
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion], and higher neurophysiological arousal was predictive of judging realistic images as real [@azevedo2020body].
 Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in guiding our appraisal of a stimulus.
@@
 
-AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing [@dawel2021systematic], in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
+Due to their popularity as a target of CGI technology and the prospect offered with facial features that can be experimentally manipulated, AI-generated images of faces are increasingly used to study face processing [@dawel2021systematic], in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
 Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real [@tucciarelli2020].
@@
 
-AI-generated content, and in particular realistic images, is becoming commonplace and carries important risks for misinformation and black-mailing [@viola2023designed], emphasizing the need too understand the different components that come into play into the formation of reality beliefs.
+AI-generated content, in particular realistic images, is becoming commonplace and carries important risks for misinformation and black-mailing [@viola2023designed], emphasizing the need to understand the different components that come into play in the formation of reality beliefs.
 This exploratory study primarily aims at investigating the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
@@
 [outlined in @makowski2018cognitive; @makowski2019phenomenal, see **BLOGPOST**  for a summary],
-which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used as an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-This study aims beyond the investigation of the discriminative accuracy between "true" photos and "true" artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
+This study aims beyond the investigation of the discriminative accuracy between "true" photos and "true" artificially-generated images, focusing on the beliefs that a stimulus is real or fake independently of its true nature.
 
@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the *Mini-IPIP6* 
+In the first part of the study, participants answered a series of personality questionnaires presented in the order below. These include the *Mini-IPIP6* 
 <!-- (24 items) [@sibley2011]  -->
@@
 [6 items each, @peters2012development]
-assessing social anxiety levels, the *FFNI-BF* 
+assessing social anxiety levels, 5 items we devised pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images"), of which we mixed with 5 items from the general attitudes towards AI scale to lower the former's saliency and the possibility of it priming the subjects about the task,
+<!-- (*GAAIS*) [@schepman2020initial]. -->
+[*GAAIS*, @schepman2020initial]
+the *FFNI-BF* 
 <!-- (30 items) [@jauk2022validation] -->
@@
 ["How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive].
-Finally, we devised 5 items pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images").
-To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale
-<!-- (*GAAIS*) [@schepman2020initial]. -->
-[*GAAIS*, @schepman2020initial].
-This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.
+3 attention check questions were also embedded in the surveys.
 
@@
 
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender.
+Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with different patterns observed depending on the participant's gender.
 The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
@@
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
-It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
+It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of attractive faces for men, rendering them significantly more salient than unattractive faces, and in turn distorting the relationship with simulation monitoring.
 However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers
@@
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
-This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and to be more vigilant and attentive to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
+This is in line with recent research which found people with higher narcissism scores less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and to be more vigilant and attentive to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
 
@@
 
-A related issue is the effect of the reality judgements by the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
-Given this prior information given to participants, it seems like our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwaranted.
-After all,
-
-In principle, a control condition without requiring a cover story with AI-generated images.
+A related issue is the effect on reality judgement resulting from the explicit instruction in our cover story, which states that "about half of the faces were AI-generated and the other half real photos".
+Considering this prior information given to participants, our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwarranted.
+After all, in principle, a control condition should not have required a cover story with AI-generated images.
 However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum.
 That said, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
-This can be studied by modulating this expectation in a controlled fashion (e.g., "most of the images *but a few* a real" vs.
-"most of the images *but a few* a fake") or inventing some implicit way of measuring reality belief that would not require the explicit introduction oof the concept of fake vs.
+This can be studied by modulating this expectation in a controlled fashion (e.g., "most of the images *but a few* are real" vs.
+"most of the images *but a few* are fake") or inventing some implicit way of measuring reality belief that would not require the explicit introduction of the concept of fake vs.
 real to participants.

### 2023-04-12 submission/manuscript.tex
update manu

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
+  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
+  pdflang={en-EN},
+  pdfkeywords={attractiveness, AI-generated images, fiction, fake news, sense of reality},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 {}{\PatchFailed}
-\keywords{attractiveness, simulation monitoring, fiction, deep fakes, sense of reality\newline\indent Word count: 4088}
+\keywords{attractiveness, AI-generated images, fiction, fake news, sense of reality\newline\indent Word count: 4970}
 \usepackage{lineno}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
-  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
-  pdflang={en-EN},
-  pdfkeywords={attractiveness, simulation monitoring, fiction, deep fakes, sense of reality},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
-While not all simulations have achieved perfect realism (e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
-Such performance, however, leads to a new question: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgements regarding their nature?
+While not all simulations have achieved perfect realism (Corvi et al., 2022; e.g., Computer Generated Images - CGI in movies or via recent algorithms such as GANs or diffusion models often include distortions or lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future.
+This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
+Such technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective ``physical'' characteristics, how can we form judgements regarding their nature?
 
 Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, Makowski, 2018; Makowski, Sperduti, et al., 2019).
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., in what journal has information been published), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
-However, the automization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
+With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., which journal was the information published in), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
 Chen et al., 2015).
@@
 For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005).
+Indeed, participants' self-reported emotional arousal were found to significantly predict the probability that they would perceive images as real (Azevedo et al., 2020).
 Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020).
+In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020), and higher neurophysiological arousal was predictive of judging realistic images as real (Azevedo et al., 2020).
 Additionally, other factors, such as the stimuli's perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in guiding our appraisal of a stimulus.
 
-AI-generated images of faces, due to their popularity as a target of CGI technology and to the possibility of experimentally manipulating facial features, are increasingly used to study face processing in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
+Due to their popularity as a target of CGI technology and the prospect offered with facial features that can be experimentally manipulated, AI-generated images of faces are increasingly used to study face processing (Dawel et al., 2021), in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
 Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real (Tucciarelli et al., 2020).
@@
 (2022) reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
-Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness could drive simulation monitoring - has received little attention to date.
-
-This study primarily aims at exploring the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the embodied reality theory
-(outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019),
-which suggests that salient and emotional stimuli are perceived to be more real, we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness contributes to the formation of reality beliefs - has received little attention to date.
+
+AI-generated content, in particular realistic images, is becoming commonplace and carries important risks for misinformation and black-mailing (Viola \& Voto, 2023), emphasizing the need to understand the different components that come into play in the formation of reality beliefs.
+This exploratory study primarily aims at investigating the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
+Based on the \emph{affective reality theory}
+(outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019, see \textbf{BLOGPOST} for a summary),
+which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used as an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-This study aims beyond the investigation of the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
+This study aims beyond the investigation of the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images, focusing on the beliefs that a stimulus is real or fake independently of its true nature.
 
@@
 
+All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
+
 \hypertarget{ethics-statement}{%
@@
 
-In the first part of the study, participants answered a series of personality questionnaires, including the \emph{Mini-IPIP6}
+In the first part of the study, participants answered a series of personality questionnaires presented in the order below. These include the \emph{Mini-IPIP6}
 (24 items, Sibley et al., 2011)
@@
 (6 items each, Peters et al., 2012)
-assessing social anxiety levels, the \emph{FFNI-BF}
+assessing social anxiety levels, 5 items we devised pertaining to expectations about AI-generated image technology (``I think current Artificial Intelligence algorithms can generate very realistic images''), of which we mixed with 5 items from the general attitudes towards AI scale to lower the former's saliency and the possibility of it priming the subjects about the task,
+(\emph{GAAIS}, Schepman \& Rodway, 2020)
+the \emph{FFNI-BF}
 (30 items, Jauk et al., 2022)
@@
 (``How would you rate your own physical attractiveness relative to the average,'' Spielmann et al., 2020).
-Finally, we devised 5 items pertaining to expectations about AI-generated image technology (``I think current Artificial Intelligence algorithms can generate very realistic images'').
-To lower their saliency and the possibility of it priming the subjects about the task, we mixed these items with 5 items from the general attitudes towards AI scale
-(\emph{GAAIS}, Schepman \& Rodway, 2020).
-This scale was presented after the social anxiety questionnaires. 3 attention check questions were also embedded in the surveys.
+3 attention check questions were also embedded in the surveys.
 
@@
 
-One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data (Peer et al., 2022).
+Although the main part of the study relied on within-subject design (with 109 trials per participant), we also planned to do between-participants analyses, thus aiming at collecting a larger sample than traditionally used in experimental psychology (with budget availability as the main constraint).
+One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data {[}Peer et al.
+(2022); douglas2023data{]}.
 The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
@@
 
-We excluded 5 participants that either failed 2 (\textgreater= 66\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
+We excluded 5 participants that either failed 2 (\textgreater= 66.6\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
 The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: {[}19, 66{]}; Sex: 48.3\% females, 51.0\% males, 0.7\% others).
@@
 
-The real-fake ratings (measured originally on a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
+The real-fake ratings (measured originally with a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
 The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
@@
 
-\hypertarget{manipulation-check}{%
-\subsubsection{Manipulation Check}\label{manipulation-check}}
-
-Only one image file yielded a strong simulation monitoring bias (\textgreater{} 85\%), being classified as fake by 88.7\% of participants.
-This image was removed from further analysis, leaving 108 trials per participant.
 On average, across participants, 44\% of images (95\%\textasciitilde CI {[}0.12, 0.64{]}) were judged as fake and 56\% of images (95\%\textasciitilde CI {[}0.36, 0.84{]}) as real.
@@
 
+Note that we also tested as predictors the normative attractiveness and trustworthiness scores (i.e., the average values from the stimuli database validation), which showed a significant positive linear relationship between beliefs of reality and attractiveness, as well as trustworthiness, only for males (see Supplementary Analysis for details).
+
 \hypertarget{inter-individual-correlates-of-simulation-monitoring}{%
@@
 Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \& Ying, 2022).
-It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of men towards attractive faces, rendering them significantly more salient than unattractive faces, and in turn distorted the relationship with simulation monitoring.
+It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of attractive faces for men, rendering them significantly more salient than unattractive faces, and in turn distorting the relationship with simulation monitoring.
 However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers
@@
 Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
-This is in line with recent research which found people with narcissism to be less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
+This is in line with recent research which found people with higher narcissism scores less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
 
@@
 Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
-Moreover, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+
+A related issue is the effect on reality judgement resulting from the explicit instruction in our cover story, which states that ``about half of the faces were AI-generated and the other half real photos''.
+Considering this prior information given to participants, our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwarranted.
+After all, in principle, a control condition should not have required a cover story with AI-generated images.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum.
+That said, future studies should study the impact of these higher-order expectations on ratings (for instance, Tucciarelli et al., 2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces) as well as on the simulation monitoring process itself (i.e., the ``criterion'': would people form and distribute judgements differently).
+This can be studied by modulating this expectation in a controlled fashion (e.g., ``most of the images \emph{but a few} are real'' vs.~``most of the images \emph{but a few} are fake'') or inventing some implicit way of measuring reality belief that would not require the explicit introduction of the concept of fake vs.~real to participants.
+
+Moreover, although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
 Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-azevedo2020body}{}}%
+Azevedo, R., Tucciarelli, R., De Beuklaer, S., Ambroziak, K., Jones, I., \& Tsakiris, M. (2020). \emph{A body of evidence:`feeling in seeing'predicts realness judgments for photojournalistic images.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-corvi2022detection}{}}%
+Corvi, R., Cozzolino, D., Zingarini, G., Poggi, G., Nagano, K., \& Verdoliva, L. (2022). On the detection of synthetic images generated by diffusion models. \emph{arXiv Preprint arXiv:2211.00680}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dawel2021systematic}{}}%
+Dawel, A., Miller, E. J., Horsburgh, A., \& Ford, P. (2021). A systematic survey of face stimuli used in psychological research 2000--2020. \emph{Behavior Research Methods}, 1--13.
+
 \leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
-Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
+Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S.others.
 (2019).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
-Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
+Rhodes, G.others. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-viola2023designed}{}}%
+Viola, M., \& Voto, C. (2023). Designed to abuse? Deepfakes and the non-consensual diffusion of intimate images. \emph{Synthese}, \emph{201}(1), 1--20.
+
 \leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%

### 2023-04-12 analysis.Rmd
update
forgot to push -_-

@@
 
-df <- df |>
-  filter(!Stimulus %in% extreme_items$Stimulus)
+# df <- df |>
+#   filter(!Stimulus %in% extreme_items$Stimulus)
 
@@
   ggplot(aes(x = Score, y = Predicted)) +
-  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  stat_density_2d(aes(fill = after_stat(density)), geom = "raster", contour = FALSE) +
   # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
@@
   ggplot(aes(x = Delay, y = Real)) +
-  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
+  stat_density_2d(aes(fill = after_stat(density)), geom = "raster", contour = FALSE) +
   geom_hline(yintercept = 0.5, linetype = "dotted") +
@@
   display()
+```
+
+### Effect of Presentation Order
+
+```{r message=FALSE, warning=FALSE, cache=cache}
+model <- glmmTMB::glmmTMB(Belief ~ Block2_Trial + (1 | Participant) + (1 | Stimulus),
+  data = df,
+  family = "binomial"
+)
+pred <- estimate_relation(model, at = "Block2_Trial", length = 20)
+
+m_conf <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief / Block2_Trial + ((Belief / Block2_Trial) | Participant) + (1 | Stimulus),
+  data = df,
+  family = glmmTMB::beta_family()
+)
+y_conf <- estimate_relation(m_conf, at = c("Block2_Trial", "Belief"), length = 20)
+y_conf <- y_conf |>
+  mutate_at(c("Predicted", "CI_low", "CI_high"), function(x) ifelse(y_conf$Belief == "Real", datawizard::rescale(x, range = c(0, 1), to = c(0.5, 1)), datawizard::rescale(x, range = c(1, 0), to = c(0, 0.5))))
+
+df |>
+  ggplot(aes(x = Block2_Trial, y = Real)) +
+  stat_density_2d(aes(fill = after_stat(density)), geom = "raster", contour = FALSE) +
+  geom_hline(yintercept = 0.5, linetype = "dotted") +
+  # geom_ribbon(data=y_conf, aes(y=Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
+  geom_line(data = y_conf, aes(y = Predicted, group = Belief), linetype = "dashed", color = "red") +
+  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.3) +
+  geom_line(data = pred, aes(y = Predicted), color = "red") +
+  scale_fill_gradientn(colors = c("white", "#FF9800"), guide = "none") +
+  scale_x_continuous(expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
+  theme_modern() +
+  labs(title = "Effect of Presentation Order", x = "Minutes", y="Presentation Order") +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_blank(),
+    strip.placement = "outside",
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  ) +
+  ggside::geom_xsidedensity(fill = "#FF9800", color = "white") +
+  ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
+  ggside::theme_ggside_void() +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  ggside::ggside(collapse = "all")
+
+parameters::parameters(model, effects="fixed", exponentiate=TRUE) |> 
+  display(digits=4)
+parameters::parameters(m_conf, effects="fixed") |> 
+  display(digits=6)
 ```
@@
 
+parameters::parameters(rez_at_norm$model_belief, effects = "fixed", keep = "Attractive") |> 
+  display()
 rez_at_norm$p
@@
 
+parameters::parameters(rez_tr_norm$model_belief, effects = "fixed", keep = "Trustworthy") |> 
+  display()
 rez_tr_norm$p
@@
     ggplot(aes_string(x = var, y = "Real")) +
-    stat_density_2d(data=filter(df, Belief=="Real"), aes(fill = ..density..), geom = "raster", contour = FALSE, alpha=0.5) +
+    stat_density_2d(data=filter(df, Belief=="Real"), aes(fill = after_stat(density)), geom = "raster", contour = FALSE, alpha=0.5) +
     scale_fill_gradientn(colors = c("white", "#4CAF50"), guide = "none") +
     ggnewscale::new_scale_fill() +
-    stat_density_2d(data=filter(df, Belief=="Fake"), aes(fill = ..density..), geom = "raster", contour = FALSE, alpha=0.5) +
+    stat_density_2d(data=filter(df, Belief=="Fake"), aes(fill = after_stat(density)), geom = "raster", contour = FALSE, alpha=0.5) +
     scale_fill_gradientn(colors = c("white", "#F44336"), guide = "none") +

### 2023-04-12 submission/manuscript.Rmd
forgot to push -_-

--- 2023-04-10 submission/manuscript.Rmd
@@
 keywords          : "attractiveness, AI-generated images, fiction, ffafke news, sense of reality"
-wordcount         : "4088"
+wordcount         : "5223"
 bibliography      : references.bib
@@
 Based on the *affective reality theory*
-[outlined in @makowski2018cognitive; @makowski2019phenomenal, see **BLOGPOST**  for a summary],
+[outlined in @makowski2018cognitive; @makowski2019phenomenal, see @makowski2023affectivefor a summary],
 which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
@@
 We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were all images of real faces) were judged as fake in sufficient proportion to warrant their analysis.
-Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating).
+Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating), as well as that of the presentation order to check whether for habituation or learning effects.
 
@@
 -->
-On average, across participants, 44% of images (95%\~CI [0.12, 0.64]) were judged as fake and 56% of images (95%\~CI [0.36, 0.84]) as real.
+On average, across participants, 44% of images (95%\~CI [0.12, 0.64]) were judged as fake and 56% of images (95%\~CI [0.36, 0.88]) as real.
 An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.
 
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\%~CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$)
-
-<!-- There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\%~CI = [0.99, 1.00]$, $z = -2.27$, $p = .023$).
-There was also a significant negative effect on judgement confidence, but only in the real condition ($\beta = -0.005$, $95\%~CI = [-0.1, 0.0]$, $p = .023$).
--->
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\%~CI = [0.99, 1.00]$), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$).
+The presentation order also did not have have an effect on the belief ($OR = 1.00$, $95\%~CI = [1.00, 1.00]$) but was related to a decrease of confidence ($\beta_{real} = -0.003$, $95\%~CI = [-0.004, -0.002]$, $p < .001$; $\beta_{fake} = -0.002$, $95\%~CI = [-0.004, -0.0003]$, $p = .021$): items presented at the end of the session were judged with a similar bias but a decreased overall confidence.
 
@@
 
-A related issue is the effect of the reality judgements by the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
-Given this prior information given to participants, it seems like our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwaranted.
-After all,
+Another issue is the impact on reality judgements of the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
+Given this prior information given to participants, it migjt seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted: all it shows is that participants followed the instructions.
+First of all, even if that was the case, the fact that our beliefs of reality can be so easily re-programmed with basic instructions ad lead to high-confidence answers remains an interesting phenomenon.
+Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing a description of the dataset.
+The fact that no presentation order effect was found on reality beliefs gives credit to the assumption that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first items judged as real (the initial "true" belief of the participants), and later a hard bias towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfil the instructions).
 
-In principle, a control condition without requiring a cover story with AI-generated images.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum.
+That said, the potential confounding effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be welcome.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (asking them to discriminate real from fake without introducing the context and meaning of "fake" seems hardly feasible).
 That said, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
 This can be studied by modulating this expectation in a controlled fashion (e.g., "most of the images *but a few* a real" vs.
-"most of the images *but a few* a fake") or inventing some implicit way of measuring reality belief that would not require the explicit introduction oof the concept of fake vs.
+"most of the images *but a few* a fake") or inventing some implicit way of measuring reality belief that would not require the explicit introduction of the concept of fake vs.
 real to participants.
 
-Moreover, although consistent in their directions across  models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
 Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.

### 2023-04-12 submission/manuscript.Rmd

--- 2023-04-12 submission/manuscript.Rmd
@@
 keywords          : "attractiveness, AI-generated images, fiction, fake news, sense of reality"
-wordcount         : "4970"
+wordcount         : "5223"
 bibliography      : references.bib
@@
 Based on the *affective reality theory*
-[outlined in @makowski2018cognitive; @makowski2019phenomenal, see **BLOGPOST**  for a summary],
-which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used as an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+[outlined in @makowski2018cognitive; @makowski2019phenomenal, see @makowski2023affectivefor a summary],
+which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-This study aims beyond the investigation of the discriminative accuracy between "true" photos and "true" artificially-generated images, focusing on the beliefs that a stimulus is real or fake independently of its true nature.
+This study aims beyond the investigation of the discriminative accuracy between "true" photos and "true" artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 
-A related issue is the effect on reality judgement resulting from the explicit instruction in our cover story, which states that "about half of the faces were AI-generated and the other half real photos".
-Considering this prior information given to participants, our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwarranted.
-After all, in principle, a control condition should not have required a cover story with AI-generated images.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum.
+Another issue is the impact on reality judgements of the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
+Given this prior information given to participants, it migjt seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted: all it shows is that participants followed the instructions.
+First of all, even if that was the case, the fact that our beliefs of reality can be so easily re-programmed with basic instructions ad lead to high-confidence answers remains an interesting phenomenon.
+Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing a description of the dataset.
+The fact that no presentation order effect was found on reality beliefs gives credit to the assumption that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first items judged as real (the initial "true" belief of the participants), and later a hard bias towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfil the instructions).
+
+That said, the potential confounding effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be welcome.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (asking them to discriminate real from fake without introducing the context and meaning of "fake" seems hardly feasible).
 That said, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
@@
 
-Moreover, although consistent in their directions across  models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
 Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.

### 2023-04-12 submission/manuscript.tex
knit

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
-  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
-  pdflang={en-EN},
-  pdfkeywords={attractiveness, AI-generated images, fiction, fake news, sense of reality},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 {}{\PatchFailed}
-\keywords{attractiveness, AI-generated images, fiction, fake news, sense of reality\newline\indent Word count: 4970}
+\keywords{attractiveness, AI-generated images, fiction, fake news, sense of reality\newline\indent Word count: 5223}
 \usepackage{lineno}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
+  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
+  pdflang={en-EN},
+  pdfkeywords={attractiveness, AI-generated images, fiction, fake news, sense of reality},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 Based on the \emph{affective reality theory}
-(outlined in Makowski, 2018; Makowski, Sperduti, et al., 2019, see \textbf{BLOGPOST} for a summary),
-which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used as an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+(\textbf{makowski2023affectivefor?}),
+which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-This study aims beyond the investigation of the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images, focusing on the beliefs that a stimulus is real or fake independently of its true nature.
+This study aims beyond the investigation of the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 
-On average, across participants, 44\% of images (95\%\textasciitilde CI {[}0.12, 0.64{]}) were judged as fake and 56\% of images (95\%\textasciitilde CI {[}0.36, 0.84{]}) as real.
+On average, across participants, 44\% of images (95\%\textasciitilde CI {[}0.12, 0.64{]}) were judged as fake and 56\% of images (95\%\textasciitilde CI {[}0.36, 0.88{]}) as real.
 An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0\% for the participants and 9.6\% for the stimuli.
 
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality (\(OR = 1.00\), \(95\%~CI = [0.99, 1.00]\) ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real (\(\beta = -0.006\), \(95\%~CI = [-0.1, 0.002]\), \(p = .004\))
+While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality (\(OR = 1.00\), \(95\%~CI = [0.99, 1.00]\)), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real (\(\beta = -0.006\), \(95\%~CI = [-0.1, 0.002]\), \(p = .004\)).
+The presentation order also did not have have an effect on the belief (\(OR = 1.00\), \(95\%~CI = [1.00, 1.00]\)) but was related to a decrease of confidence (\(\beta_{real} = -0.003\), \(95\%~CI = [-0.004, -0.002]\), \(p < .001\); \(\beta_{fake} = -0.002\), \(95\%~CI = [-0.004, -0.0003]\), \(p = .021\)): items presented at the end of the session were judged with a similar bias but a decreased overall confidence.
 
@@
 
-A related issue is the effect on reality judgement resulting from the explicit instruction in our cover story, which states that ``about half of the faces were AI-generated and the other half real photos''.
-Considering this prior information given to participants, our enthusiasm that most people did indeed believe a high number of stimuli to be fake might be unwarranted.
-After all, in principle, a control condition should not have required a cover story with AI-generated images.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum.
+Another issue is the impact on reality judgements of the prior explicit instruction that ``about half of the faces were AI-generated and the other half real photos''.
+Given this prior information given to participants, it migjt seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted: all it shows is that participants followed the instructions.
+First of all, even if that was the case, the fact that our beliefs of reality can be so easily re-programmed with basic instructions ad lead to high-confidence answers remains an interesting phenomenon.
+Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing a description of the dataset.
+The fact that no presentation order effect was found on reality beliefs gives credit to the assumption that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first items judged as real (the initial ``true'' belief of the participants), and later a hard bias towards responding ``fake'' (as participants realize that all stimuli are of similar nature and that they have to ``make up'' for the prevalence of their ``real'' answers to fulfil the instructions).
+
+That said, the potential confounding effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be welcome.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (asking them to discriminate real from fake without introducing the context and meaning of ``fake'' seems hardly feasible).
 That said, future studies should study the impact of these higher-order expectations on ratings (for instance, Tucciarelli et al., 2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces) as well as on the simulation monitoring process itself (i.e., the ``criterion'': would people form and distribute judgements differently).
@@
 
-Moreover, although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
 Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
-Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S.others.
+Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
 (2019).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
-Rhodes, G.others. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
+Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
 

### 2023-04-13 submission/manuscript.Rmd
minor updates

@@
 keywords          : "attractiveness, AI-generated images, fiction, fake news, sense of reality"
-wordcount         : "5223"
+wordcount         : "5242"
 bibliography      : references.bib
@@
 This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos [@nightingale2022; @tucciarelli2020; @moshel2022].
-Such technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective "physical" characteristics, how can we form judgements regarding their nature?
+Such a technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective "physical" characteristics, how can we form judgements regarding their nature?
 
@@
 With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., which journal was the information published in), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult [@berghel2018weaponizing; @chen2015news].
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are often mass-shared with little context) makes this task progressively difficult [@berghel2018weaponizing; @chen2015news].
 Thus, in the absence of clear contextual information, what drives our beliefs of reality?
@@
 Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
-For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy], and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations [@britt2019reasoned].
+For instance, individuals with stronger analytical reasoning skills have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy], and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations [@britt2019reasoned].
 Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
@@
 Another issue is the impact on reality judgements of the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
-Given this prior information given to participants, it migjt seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted: all it shows is that participants followed the instructions.
-First of all, even if that was the case, the fact that our beliefs of reality can be so easily re-programmed with basic instructions ad lead to high-confidence answers remains an interesting phenomenon.
-Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing a description of the dataset.
-The fact that no presentation order effect was found on reality beliefs gives credit to the assumption that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first items judged as real (the initial "true" belief of the participants), and later a hard bias towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfil the instructions).
+Given this prior information given to participants, it might seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted, since it simply affirms participants followed the instructions.
+However, even if that was the case, the finding that our beliefs of reality can be so easily re-programmed with simple instructions and lead to high-confidence answers remains an interesting phenomenon.
+Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing them a description of the dataset.
+The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first few items judged as real (the initial "true" belief of the participants), and progressively a hard bias towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfill the expected proportion of responses given the instructions).
 
-That said, the potential confounding effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be welcome.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (asking them to discriminate real from fake without introducing the context and meaning of "fake" seems hardly feasible).
-That said, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
+That said, the potential demand effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be able to mitigate such confounds to some extent.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (simply instructing them to discriminate real from fake without providing some background information regarding the context and defining what is meant by "fake" seems hardly feasible).
+That being the case, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased, on average, the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
 This can be studied by modulating this expectation in a controlled fashion (e.g., "most of the images *but a few* are real" vs.

### 2023-04-13 submission/manuscript.tex
minor updates

@@
 {}{\PatchFailed}
-\keywords{attractiveness, AI-generated images, fiction, fake news, sense of reality\newline\indent Word count: 5223}
+\keywords{attractiveness, AI-generated images, fiction, fake news, sense of reality\newline\indent Word count: 5242}
 \usepackage{lineno}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
-  pdfauthor={Dominique Makowski1, An Shu Te1, Stephanie Kirk1, Ngoi Zi Liang1, Panagiotis Mavros2, \& S.H. Annabel Chen1, 3, 4, 5},
-  pdflang={en-EN},
-  pdfkeywords={attractiveness, AI-generated images, fiction, fake news, sense of reality},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
-Such technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective ``physical'' characteristics, how can we form judgements regarding their nature?
+Such a technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective ``physical'' characteristics, how can we form judgements regarding their nature?
 
@@
 With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., which journal was the information published in), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are mass-shared with little context) makes this task increasingly difficult (Berghel, 2018; Y.
+However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are often mass-shared with little context) makes this task progressively difficult (Berghel, 2018; Y.
 Chen et al., 2015).
@@
 Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
-For instance, individuals with stronger analytical reasoning have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019), and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations (Britt et al., 2019).
+For instance, individuals with stronger analytical reasoning skills have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019), and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations (Britt et al., 2019).
 Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
@@
 Another issue is the impact on reality judgements of the prior explicit instruction that ``about half of the faces were AI-generated and the other half real photos''.
-Given this prior information given to participants, it migjt seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted: all it shows is that participants followed the instructions.
-First of all, even if that was the case, the fact that our beliefs of reality can be so easily re-programmed with basic instructions ad lead to high-confidence answers remains an interesting phenomenon.
-Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing a description of the dataset.
-The fact that no presentation order effect was found on reality beliefs gives credit to the assumption that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first items judged as real (the initial ``true'' belief of the participants), and later a hard bias towards responding ``fake'' (as participants realize that all stimuli are of similar nature and that they have to ``make up'' for the prevalence of their ``real'' answers to fulfil the instructions).
-
-That said, the potential confounding effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be welcome.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (asking them to discriminate real from fake without introducing the context and meaning of ``fake'' seems hardly feasible).
-That said, future studies should study the impact of these higher-order expectations on ratings (for instance, Tucciarelli et al., 2020 found that merely mentioning that some faces were AI generated decreased on average the trustworthiness ratings for all faces) as well as on the simulation monitoring process itself (i.e., the ``criterion'': would people form and distribute judgements differently).
+Given this prior information given to participants, it might seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted, since it simply affirms participants followed the instructions.
+However, even if that was the case, the finding that our beliefs of reality can be so easily re-programmed with simple instructions and lead to high-confidence answers remains an interesting phenomenon.
+Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing them a description of the dataset.
+The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first few items judged as real (the initial ``true'' belief of the participants), and progressively a hard bias towards responding ``fake'' (as participants realize that all stimuli are of similar nature and that they have to ``make up'' for the prevalence of their ``real'' answers to fulfill the expected proportion of responses given the instructions).
+
+That said, the potential demand effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be able to mitigate such confounds to some extent.
+However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (simply instructing them to discriminate real from fake without providing some background information regarding the context and defining what is meant by ``fake'' seems hardly feasible).
+That being the case, future studies should study the impact of these higher-order expectations on ratings (for instance, Tucciarelli et al., 2020 found that merely mentioning that some faces were AI generated decreased, on average, the trustworthiness ratings for all faces) as well as on the simulation monitoring process itself (i.e., the ``criterion'': would people form and distribute judgements differently).
 This can be studied by modulating this expectation in a controlled fashion (e.g., ``most of the images \emph{but a few} are real'' vs.~``most of the images \emph{but a few} are fake'') or inventing some implicit way of measuring reality belief that would not require the explicit introduction of the concept of fake vs.~real to participants.

### 2023-09-12 analysis.Rmd
prepare for next sub

@@
   "S117",
-  # Prefered not answering to sexual orientation: further analysis impossible
+  # Preferred not answering to sexual orientation: further analysis impossible
   "S101"
@@
   group_by(Stimulus, Belief) |>
-  summarize(n = n() / length(unique(df$Participant))) |>
+  summarize(n = n() / length(unique(df$Participant)), .groups = "keep") |>
   pivot_wider(values_from = "n", names_from = "Belief") |>
@@
   arrange(Real) |>
-  filter(Real < 0.15 | Real > 0.85)
+  filter(Real < 0.2 | Real > 0.8) |> 
+  ungroup() |> 
+  mutate(Belief_Answer = c(-0.2, 0, 0, 0.2))
 
 p_item <- df |>
-  filter(Stimulus %in% extreme_items$Stimulus) |>
-  mutate(Stimulus = fct_relevel(Stimulus, as.character(extreme_items$Stimulus))) |>
+  group_by(Stimulus) |> 
+  mutate(Average_belief = mean(Belief_Answer)) |> 
+  ungroup() |> 
+  mutate(Stimulus = fct_reorder(Stimulus, Average_belief)) |>
+  # filter(Stimulus %in% extreme_items$Stimulus) |>
   ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
-  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
+  ggdist::stat_slab(scale = 4, slab_alpha = 2/3, normalize = "groups", color = "black", size=0.2) +
   geom_vline(xintercept = 0, linetype = "dotted") +
-  ggimage::geom_image(data = extreme_items, aes(image = File, x = 0, y = Stimulus), size = 0.1, by = "height") +
-  # scale_y_discrete(expand = c(0.5, 0.5)) +
+  ggimage::geom_image(data = extreme_items, aes(image = File, y = Stimulus), position = position_jitter(width = 0.2), size = 0.05, by = "height") +
+  scale_y_discrete(expand = c(0.1, 0.1)) +
   scale_x_continuous(
@@
   scale_fill_viridis_d(option = "inferno") +
-  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
+  labs(x = "Simulation Monitoring", y = "Items", title = "Distribution of Reality Judgments") +
   guides(fill = "none") +
@@
   theme(
-    # axis.text.y = element_blank(),
+    axis.text.y = element_blank(),
     plot.title = element_text(face = "bold", hjust = 0.5)
   )
-# p_item
+p_item
+
+extreme_items
 
@@
 #   filter(!Stimulus %in% extreme_items$Stimulus)
-
-extreme_items
 ```
@@
   ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
-  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups", color = "black", size = 0.1) +
+  ggdist::stat_slab(scale = 4, slab_alpha = 2/3, normalize = "groups", color = "black", size = 0.2) +
   geom_vline(xintercept = 0, linetype = "dotted") +
@@
 
-ggsave("figures/Figure2.png", width=fig.height * 1.8, height=fig.width * 1.5)
-```
-
-```{r message=FALSE, warning=FALSE, eval=FALSE}
-plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey", fillx = "purple") {
-  param <- cor_test(dfsub, x, y, bayesian = TRUE)
-
-  # Format stat output
-  r <- str_replace(str_remove(insight::format_value(param$rho), "^0+"), "^-0+", "-")
-  CI_low <- str_replace(str_remove(insight::format_value(param$CI_low), "^0+"), "^-0+", "-")
-  CI_high <- str_replace(str_remove(insight::format_value(param$CI_high), "^0+"), "^-0+", "-")
-
-  stat <- paste0("italic(r)~'= ", r, ", 95% CI [", CI_low, ", ", CI_high, "], BF'['10']~'", paste0(insight::format_bf(param$BF, name = "")), "'")
-
-  label <- data.frame(
-    x = min(dfsub[[x]], na.rm = TRUE),
-    y = max(dfsub[[y]], na.rm = TRUE),
-    label = stat
-  )
-
-  # Plot
-  dfsub |>
-    ggplot(aes_string(x = x, y = y)) +
-    geom_point2(
-      size = 3,
-      color = fillx,
-      # color = DVs[x],
-      alpha = 2 / 3
-    ) +
-    geom_smooth(method = "lm", color = "black", formula = "y ~ x", alpha = 0.3) +
-    labs(y = ylab, x = xlab) +
-    geom_label(data = label, aes(x = x, y = y), label = str2expression(label$label), hjust = 0, vjust = 1, size=rel(3.5)) +
-    theme_modern(axis.title.space = 5) +
-    ggside::geom_xsidedensity(fill = fillx, color = "white") +
-    ggside::geom_ysidedensity(fill = fill, color = "white") +
-    ggside::theme_ggside_void() +
-    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
-    ggside::scale_xsidey_continuous(expand = c(0, 0))
-}
-
-p1 <- plot_correlation(dfsub,
-  x = "IPIP6_HonestyHumility",
-  y = "Confidence_Real",
-  ylab = "Confidence that the stimulus is real",
-  xlab = "Honesty-Humility",
-  fillx = "#00BCD4",
-  fill = "#D81B60"
-) + 
-  scale_y_continuous(labels=scales::percent)
-
-p2 <- plot_correlation(dfsub,
-  y = "Confidence_Fake",
-  x = "AI_Enthusiasm",
-  ylab = "Confidence that the stimulus is fake",
-  xlab = "Enthusiasm about AI technology",
-  fillx = "#607D8B",
-  fill = "#3F51B5"
-) + 
-  scale_y_continuous(labels=scales::percent)
-
-p3 <- plot_correlation(dfsub,
-  y = "Confidence_Real",
-  x = "AI_Enthusiasm",
-  ylab = "Confidence that the stimulus is real",
-  xlab = "Enthusiasm about AI technology",
-  fillx = "#607D8B",
-  fill = "#D81B60"
-) + 
-  scale_y_continuous(labels=scales::percent)
-
-p4 <- plot_correlation(dfsub,
-  y = "Confidence_Real",
-  x = "FFNI_AcclaimSeeking",
-  ylab = "Confidence that the stimulus is real",
-  xlab = "Narcissism (Acclaim Seeking)",
-  fillx = "#FF9800",
-  fill = "#D81B60"
-) + 
-  scale_y_continuous(labels=scales::percent)
-
-p5 <- plot_correlation(dfsub,
-  y = "Confidence_Fake",
-  x = "FFNI_AcclaimSeeking",
-  ylab = "Confidence that the stimulus is fake",
-  xlab = "Narcissism (Acclaim Seeking)",
-  fillx = "#FF9800",
-  fill = "#3F51B5"
-) + 
-  scale_y_continuous(labels=scales::percent)
-
-p6 <- plot_correlation(dfsub,
-  y = "Confidence_Real",
-  x = "FFNI_GrandioseFantasies",
-  ylab = "Confidence that the stimulus is real",
-  xlab = "Narcissism (Grandiose Fantasies)",
-  fillx = "#FFC107",
-  fill = "#D81B60"
-) + 
-  scale_y_continuous(labels=scales::percent)
-
-fig <- wrap_elements(fig1a) /
-  wrap_elements(
-    ((p3 / p2) | (p1 / p6) | (p4 / p5)) + 
-  plot_annotation(title = "Personality Correlates of Simulation Monitoring", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
-  ) +
-  plot_layout(heights = c(1.1, 0.9))
-
-ggsave("figures/Figure2.png", width=fig.height * 1.8, height=fig.width * 1.5)
+ggsave("figures/Figure2.png", fig, width=fig.height * 1.8, height=fig.width * 1.5)
 ```

### 2023-09-12 submission/manuscript.Rmd
prepare for next sub

@@
       - "Writing – original draft"
-  - name          : "An Shu Te"
+  - name          : "An Shu Te"  # anshu.te@ntu.edu.sg
     affiliation   : "1"
@@
       - "Writing – original draft"
-  - name          : "Stephanie Kirk"
+  - name          : "Stephanie Kirk"  # stephanie.morgank@gmail.com
     affiliation   : "1"
@@
       - "Writing – original draft"
-  - name          : "Ngoi Zi Liang"
+  - name          : "Ngoi Zi Liang"  # ziliang.ngoi@ntu.edu.sg
     affiliation   : "1"
@@
       - "Writing – review & editing"
-  - name          : "Panagiotis Mavros"
+  - name          : "Panagiotis Mavros"  # panos.mavros@sec.ethz.ch 
     affiliation   : "2"
@@
       - "Writing – review & editing"
-  - name          : "S.H. Annabel Chen"
+  - name          : "S.H. Annabel Chen"  # AnnabelChen@ntu.edu.sg
     affiliation   : "1, 3, 4, 5"
@@
   - id            : "2"
-    institution   : "Singapore-ETH Centre, Future Cities Laboratory, Singapore"
+    institution   : "Department of Economics and Social Sciences, Télécom Paris, France"
   - id            : "3"
@@
 Based on the *affective reality theory*
-[outlined in @makowski2018cognitive; @makowski2019phenomenal, see @makowski2023affectivefor a summary],
+[outlined in @makowski2018cognitive; @makowski2019phenomenal, see @makowski2023affective for a summary],
 which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
@@
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-This study aims beyond the investigation of the discriminative accuracy between "true" photos and "true" artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
+Importantly, this study does investigate the discriminative accuracy between "true" photos and "true" artificially-generated images (which we consider more a technological issue than a psychological one), focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*.
-We took into account the gender of participants and stimuli by retaining the stimuli that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+The analysis focused on sexual-orientation relevant stimuli, i.e., on faces that were aligned with respect to the participants' sexual orientation (i.e., female faces for heterosexual males, male faces for homosexual males, etc.), and the models included the interaction with the participants' gender (as a sexual dimorphism has been reported in face appraisal processes).
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
@@
 This finding not only attests to the effectiveness of our instructions, but highlights the current levels of expectation regarding CGI technology.
-The strong impact of prior expectations and information on reality beliefs demonstrated here underlines the volatility of our sense of reality.
+The strong impact of prior expectations and information on reality beliefs underlines the volatility of our sense of reality.
 In fact, stimuli-related and participant-related characteristics accounted together for less than 20% of the beliefs variance, suggesting a large contribution of other subjective processes.
@@
 It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of attractive faces for men, rendering them significantly more salient than unattractive faces, and in turn distorting the relationship with simulation monitoring.
+<!-- However, it is also possible that this pattern occurred due to the stimuli range, by which the stimuli did not include sufficiently unattractive faces for males to be , by which   -->
 However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers
@@
 
-Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
-Given prior evidence that faces presented as computer-generated were rated less trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a linear association to be more clearly present for both genders.
-One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females
-<!-- (explained evolutionarily as a compromise to their reproductive potential [@van2020sex]), -->
-[explained evolutionarily as a compromise to their reproductive potential, @van2020sex],
-to which perceived facial trustworthiness relates [@hou2019survival].
-However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
+Our findings do not support the existence of a strong link between perceived trustworthiness and reality judgments.
+Given prior evidence that faces presented as computer-generated were rated less trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a linear association to be more clearly present.
+However, our results suggest a relationship with confidence ratings, especially for women, whereby faces judged with low and high trustworthiness are judged as real and fake with higher confidence.
+One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
+Future studies should clarify the role of trustworthiness both as a predictor and outcome of reality beliefs.
+
+<!-- However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
 Further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
+-->
 
@@
 Although the familiarity measure was not a "recognition" measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females [@mishra2019gender; @lewin2002sex; @sommer2013sex], as well as an overconfidence in face recall for males [@bailey2021gender; @herbst2020gender].
-However, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+However, it should be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest] - to be related to a lower confidence in simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking were associated with a higher number of faces judged as real.
 This is in line with recent research which found people with higher narcissism scores less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and to be more vigilant and attentive to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
@@
 
-Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
+Our findings suggest - though with low certainty - a potential positive link between paranoid ideation and the tendency to believe that the stimuli were real.
 Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
@@
 Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing them a description of the dataset.
-The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first few items judged as real (the initial "true" belief of the participants), and progressively a hard bias towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfill the expected proportion of responses given the instructions).
+The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern: for instance, the first few items judged as real (the initial "true" belief of the participants), and a bias would progressively appear towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfil the expected proportion of responses given the instructions).
 
@@
 
-Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial features measured in the study were not the key determinants of simulation monitoring.
+Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial appraisals measured in the study were not the key determinants of simulation monitoring.
 Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
@@
 Notably, we found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
-We also found that inter-individual traits, such as narcissistic acclaim-seeking and manipulativeness, as well as persecutory ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
+We also found that inter-individual traits, such as narcissistic acclaim-seeking, honesty-humility, and paranoid ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
 We believe that these findings provide the foundations to help us understand what drives reality beliefs in an increasingly reality-ambiguous world.

### 2023-10-10 submission/manuscript.tex
minor

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
+  pdfauthor={Dominique Makowski1, An Shu Te2, Stephanie Kirk2, Ngoi Zi Liang2, Panagiotis Mavros3, \& S.H. Annabel Chen2, 4, 5, 6},
+  pdflang={en-EN},
+  pdfkeywords={attractiveness, AI-generated images, fiction, fake news, sense of reality},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
 \title{\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}}
-\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{1}, Stephanie Kirk\textsuperscript{1}, Ngoi Zi Liang\textsuperscript{1}, Panagiotis Mavros\textsuperscript{2}, \& S.H.
-Annabel Chen\textsuperscript{1, 3, 4, 5}}
+\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{2}, Stephanie Kirk\textsuperscript{2}, Ngoi Zi Liang\textsuperscript{2}, Panagiotis Mavros\textsuperscript{3}, \& S.H.
+Annabel Chen\textsuperscript{2, 4, 5, 6}}
 \date{}
@@
 
-Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (\href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}).
+Correspondence concerning this article should be addressed to Dominique Makowski (\href{mailto:D.Makowski@sussex.ac.uk}{\nolinkurl{D.Makowski@sussex.ac.uk}}).
 
@@
 
-Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore.
-E-mail: \href{mailto:dom.makowski@gmail.com}{\nolinkurl{dom.makowski@gmail.com}}
+Correspondence concerning this article should be addressed to Dominique Makowski, School of Psychology, University of Sussex, Brighton.
+E-mail: \href{mailto:D.Makowski@sussex.ac.uk}{\nolinkurl{D.Makowski@sussex.ac.uk}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{2} Singapore-ETH Centre, Future Cities Laboratory, Singapore\\\textsuperscript{3} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{4} National Institute of Education, Singapore\\\textsuperscript{5} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} Department of Economics and Social Sciences, Télécom Paris, France\\\textsuperscript{4} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{5} National Institute of Education, Singapore\\\textsuperscript{6} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}
 
@@
 The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
-Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as ``fake''.
-Moreover, our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
+Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as ``fake'' (often with high confidence), with strong intra- and inter-individual variability.
+Our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
@@
 Based on the \emph{affective reality theory}
-(\textbf{makowski2023affectivefor?}),
+Makowski (2023),
 which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
@@
 Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-This study aims beyond the investigation of the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images, focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
+Importantly, this study does investigate the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images (which we consider more a technological issue than a psychological one), focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
 
@@
 Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables \emph{mutatis mutandis}.
-We took into account the gender of participants and stimuli by retaining the stimuli that were aligned with the participants' sexual preference (e.g., female faces for homosexual females, male faces for heterosexual females, and both for bisexual participants), and modeling the interaction with the participants' gender.
+The analysis focused on sexual-orientation relevant stimuli, i.e., on faces that were aligned with respect to the participants' sexual orientation (i.e., female faces for heterosexual males, male faces for homosexual males, etc.), and the models included the interaction with the participants' gender (as a sexual dimorphism has been reported in face appraisal processes).
 For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
@@
 
-The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2021, 2019, 2020; Makowski et al., 2020; Makowski, Ben-Shachar, et al., 2019).
+The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2019, 2020, 2021; Makowski, Ben-Shachar, et al., 2019; Makowski et al., 2020).
 As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant (\(p <.01\)).
@@
 This finding not only attests to the effectiveness of our instructions, but highlights the current levels of expectation regarding CGI technology.
-The strong impact of prior expectations and information on reality beliefs demonstrated here underlines the volatility of our sense of reality.
+The strong impact of prior expectations and information on reality beliefs underlines the volatility of our sense of reality.
 In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting a large contribution of other subjective processes.
@@
 
-Our results found a positive linear trend between trustworthiness and simulation monitoring for females only.
-Given prior evidence that faces presented as computer-generated were rated less trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such a linear association to be more clearly present for both genders.
-One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females
-(explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020),
-to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
-However, if that was the case, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real, leading to a quadratic relationship between trustworthiness and simulation monitoring instead.
-Further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.
+Our findings do not support the existence of a strong link between perceived trustworthiness and reality judgments.
+Given prior evidence that faces presented as computer-generated were rated less trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such a linear association to be more clearly present.
+However, our results suggest a relationship with confidence ratings, especially for women, whereby faces judged with low and high trustworthiness are judged as real and fake with higher confidence.
+One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females (explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
+Future studies should clarify the role of trustworthiness both as a predictor and outcome of reality beliefs.
 
@@
 Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females (Lewin \& Herlitz, 2002; Mishra et al., 2019; Sommer et al., 2013), as well as an overconfidence in face recall for males (Bailey, 2021; Herbst, 2020).
-However, it should be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
+However, it should be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
 As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
@@
 Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012) - to be related to a lower confidence in simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness were associated with a higher number of faces judged as real.
+Notably, greater narcissistic tendencies in dimensions such as acclaim seeking were associated with a higher number of faces judged as real.
 This is in line with recent research which found people with higher narcissism scores less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
@@
 
-Our findings suggest - though with weak significance - a positive link between paranoid ideation and the tendency to believe that the stimuli were real.
+Our findings suggest - though with low certainty - a potential positive link between paranoid ideation and the tendency to believe that the stimuli were real.
 Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
@@
 Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing them a description of the dataset.
-The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern, for instance the first few items judged as real (the initial ``true'' belief of the participants), and progressively a hard bias towards responding ``fake'' (as participants realize that all stimuli are of similar nature and that they have to ``make up'' for the prevalence of their ``real'' answers to fulfill the expected proportion of responses given the instructions).
+The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern: for instance, the first few items judged as real (the initial ``true'' belief of the participants), and a bias would progressively appear towards responding ``fake'' (as participants realize that all stimuli are of similar nature and that they have to ``make up'' for the prevalence of their ``real'' answers to fulfil the expected proportion of responses given the instructions).
 
@@
 (2021).
-The revised green et al., Paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
+The revised green et al., paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
 \emph{Psychological Medicine}, \emph{51}(2), 244--253.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-makowski2023affective}{}}%
+Makowski, D. (2023). How do we know what is real? The 'affective reality theory'. In \emph{Dr Dominique Makowski}. \url{https://dominiquemakowski.github.io/post/2023-04-11-affectivereality/}
+
 \leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%

### 2024-06-14 submission/manuscript.Rmd
add R1
@anafneves

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
-    email         : "dom.makowski@gmail.com"
+    address       : "School of Psychology, University of Sussex, Brighton"
+    email         : "D.Makowski@sussex.ac.uk"
     orcid         : 0000-0001-5375-9967
@@
   - name          : "An Shu Te"  # anshu.te@ntu.edu.sg
-    affiliation   : "1"
+    affiliation   : "2"
     orcid         : 0000-0001-8008-2824
@@
   - name          : "Stephanie Kirk"  # stephanie.morgank@gmail.com
-    affiliation   : "1"
+    affiliation   : "2"
     orcid         : 0000-0002-9312-5552
@@
   - name          : "Ngoi Zi Liang"  # ziliang.ngoi@ntu.edu.sg
-    affiliation   : "1"
+    affiliation   : "2"
     role:
@@
       - "Writing – review & editing"
-  - name          : "Panagiotis Mavros"  # panos.mavros@sec.ethz.ch 
-    affiliation   : "2"
+  - name          : "Panagiotis Mavros"  # panos.mavros@telecom-paris.fr
+    affiliation   : "3"
     orcid         : 0000-0002-1540-5516
@@
   - name          : "S.H. Annabel Chen"  # AnnabelChen@ntu.edu.sg
-    affiliation   : "1, 3, 4, 5"
+    affiliation   : "2, 4, 5, 6"
     orcid         : 0000-0002-1540-5516
@@
   - id            : "1"
+    institution   : "School of Psychology, University of Sussex, UK"
+  - id            : "2"
     institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
-  - id            : "2"
+  - id            : "3"
     institution   : "Department of Economics and Social Sciences, Télécom Paris, France"
-  - id            : "3"
+  - id            : "4"
     institution   : "LKC Medicine, Nanyang Technological University, Singapore"
-  - id            : "4"
+  - id            : "5"
     institution   : "National Institute of Education, Singapore"
-  - id            : "5"
+  - id            : "6"
     institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
 authornote: |
-  Correspondence concerning this article should be addressed to Dominique Makowski, HSS 04-18, 48 Nanyang Avenue, Singapore (dom.makowski@gmail.com).
+  Correspondence concerning this article should be addressed to Dominique Makowski (D.Makowski@sussex.ac.uk).
 abstract: |
@@
 The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
-Strikingly, despite all images being pictures of real faces from the same database, most participants rated a large portion of them as "fake".
-Moreover, our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
+Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as "fake" (often with high confidence), with strong intra- and inter-individual variability.
+Our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 csl: utils/apa.csl
@@
 
-All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
+All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at [**MASKED FOR REVIEW**]
+<!-- [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}. -->
 
@@
 
-This study was approved by the NTU Institutional Review Board (NTU IRB-2022-187) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
+This study was approved by the 
+<!-- NTU Institutional Review Board (NTU IRB-2022-187)  -->
+[**IRB NUMBER**]
+and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
 All participants provided their informed consent prior to participation and were incentivized after completing the study.
@@
 
-The datasets generated and/or analysed during the current study are available in the GitHub repository https://github.com/RealityBending/FakeFace
+The datasets generated and/or analysed during the current study are available in the GitHub repository 
+<!-- https://github.com/RealityBending/FakeFace -->
+[**MASKED FOR REVIEW**]
 
@@
 
-This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
+[**MASKED FOR REVIEW**]
+<!-- This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
+-->
 

### 2024-06-14 submission/new_manuscript/manuscript.qmd
new apaquarto manuscript

--- 2024-06-14 submission/manuscript.Rmd
@@
 ---
-title             : "**Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated**"
-shorttitle        : "Attractiveness and Reality"
+title: "Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated"
+# If blank, the running header is the title in upper case.
+shorttitle: "Attractiveness and Reality"
+# Set names and affiliations.
+# It is nice to specify everyone's orcid, if possible.
+# There can be only one corresponding author, but declaring one is optional.
 author:
+  - name: Dominique Makowski
+    corresponding: true
+    orcid: 0000-0001-5375-9967
+    email: D.Makowski@sussex.ac.uk
+    url: https://realitybending.github.io/
+    roles:
+      - Conceptualization
+      - Data curation
+      - Formal Analysis
+      - Funding acquisition
+      - Investigation
+      - Methodology
+      - Project administration
+      - Resources
+      - Software
+      - Supervision
+      - Validation
+      - Visualization
+      - Writing – original draft
+    affiliations:
+      - name: University of Sussex
+        department: School of Psychology
+  - name: An Shu Te
+    #corresponding: 
+    orcid: 0000-0002-9312-5552
+    role:
+      - Project administration
+      - Resources
+      - Writing – original draft
+    affiliations:
+      - name: Nanyang Technological University
+        department: School of Social Sciences
+  - name: Stephanie Kirk  # stephanie.morgank@gmail.com
+    orcid: 0000-0002-9312-5552
+    role:
+      - Project administration
+      - Resources
+      - Writing – original draft
+    affiliations:
+      - name: Nanyang Technological University
+        department: School of Social Sciences
+  - name: Ngoi Zi Liang  # ziliang.ngoi@ntu.edu.sg
+    #affiliation   : "2"
+    role:
+      - Project administration
+      - Resources
+      - Writing – review & editing
+    affiliations:
+      - name: Nanyang Technological University
+        department: School of Social Sciences
+  - name: Panagiotis Mavros  # panos.mavros@telecom-paris.fr
+    #affiliation   : "3"
+    orcid: 0000-0002-1540-5516
+    role:
+      - Supervision
+      - Writing – review & editing
+    affiliations:
+      - name:  Télécom Paris
+        department: Department of Economics and Social Sciences
+  - name: S.H. Annabel Chen  # AnnabelChen@ntu.edu.sg
+    role:
+      - Project administration
+      - Supervision
+      - Writing – review & editing
+    affiliations:
+      - name: University of Sussex
+        department: School of Psychology
+      - name: Nanyang Technological University
+        department: LKC Medicine
+      - name: National Institute of Education
+      - name: Nanyang Technological University
+        department:  Centre for Research and Development in Learning
 
-  - name          : "Dominique Makowski"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "School of Psychology, University of Sussex, Brighton"
-    email         : "D.Makowski@sussex.ac.uk"
-    orcid         : 0000-0001-5375-9967
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - "Conceptualization"
-      - "Data curation"
-      - "Formal Analysis"
-      - "Funding acquisition"
-      - "Investigation"
-      - "Methodology"
-      - "Project administration"
-      - "Resources"
-      - "Software"
-      - "Supervision"
-      - "Validation"
-      - "Visualization"
-      - "Writing – original draft"
-  - name          : "An Shu Te"  # anshu.te@ntu.edu.sg
-    affiliation   : "2"
-    orcid         : 0000-0001-8008-2824
-    role:
-      - "Data curation"
-      - "Project administration"
-      - "Resources"
-      - "Investigation"
-      - "Writing – original draft"
-  - name          : "Stephanie Kirk"  # stephanie.morgank@gmail.com
-    affiliation   : "2"
-    orcid         : 0000-0002-9312-5552
-    role:
-      - "Project administration"
-      - "Resources"
-      - "Writing – original draft"
-  - name          : "Ngoi Zi Liang"  # ziliang.ngoi@ntu.edu.sg
-    affiliation   : "2"
-    role:
-      - "Project administration"
-      - "Resources"
-      - "Writing – review & editing"
-  - name          : "Panagiotis Mavros"  # panos.mavros@telecom-paris.fr
-    affiliation   : "3"
-    orcid         : 0000-0002-1540-5516
-    role:
-      - "Supervision"
-      - "Writing – review & editing"
-  - name          : "S.H. Annabel Chen"  # AnnabelChen@ntu.edu.sg
-    affiliation   : "2, 4, 5, 6"
-    orcid         : 0000-0002-1540-5516
-    role:
-      - "Project administration"
-      - "Supervision"
-      - "Writing – review & editing"
-affiliation:
-
-  - id            : "1"
-    institution   : "School of Psychology, University of Sussex, UK"
-  - id            : "2"
-    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
-  - id            : "3"
-    institution   : "Department of Economics and Social Sciences, Télécom Paris, France"
-  - id            : "4"
-    institution   : "LKC Medicine, Nanyang Technological University, Singapore"
-  - id            : "5"
-    institution   : "National Institute of Education, Singapore"
-  - id            : "6"
-    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
-authornote: |
-  Correspondence concerning this article should be addressed to Dominique Makowski (D.Makowski@sussex.ac.uk).
-abstract: |
-  Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
+author-note:
+  status-changes: 
+    # Example: [Author name] is now at [affiliation].
+    affiliation-change: ~
+    # Example: [Author name] is deceased.
+    deceased: ~
+  # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
+  disclosures:
+    # Example: This study was registered at X (Identifier Y).
+    study-registration: ~
+    # Acknowledge and cite data/materials to be shared.
+    data-sharing: ~
+    # Example: This article is based on the dissertation completed by [citation].  
+    related-report: ~
+    # Example: [Author name] has been a paid consultant for Corporation X, which funded this study.
+    conflict-of-interest: ~
+    # Example: This study was supported by Grant [Grant Number] from [Funding Source].
+    financial-support: ~
+    # Example: The authors are grateful to [Person] for [Reason].
+    gratitude: ~
+    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
+    authorship-agreements: ~
+abstract: " Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
 In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
 The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
-Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as "fake" (often with high confidence), with strong intra- and inter-individual variability.
+Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as 'fake' (often with high confidence), with strong intra- and inter-individual variability.
 Our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
-We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
+We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation."
+# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
+keywords: [attractiveness, AI-generated images, fiction, fake news, sense of reality]
+# If true, tables and figures are mingled with the text instead of listed at the end of the document.
+floatsintext: true
+# Numbered lines (.pdf and .docx only)
+numbered-lines: true
+# File with references
+bibliography: references.bib
+# Suppress title page
+suppress-title-page: false
+# Masks references that appear in the masked-citations list
+mask: false
+# Language options. See https://quarto.org/docs/authoring/language.html
+lang: en
+language:
+  citation-last-author-separator: "and"
+  citation-masked-author: "Masked Citation"
+  citation-masked-date: "n.d."
+  citation-masked-title: "Masked Title"
+  title-block-author-note: "Author Note"
+  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
+  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
+  references-meta-analysis:
+format:
+  apaquarto-docx: default
+  apaquarto-html: default
+  apaquarto-pdf:
+    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
+    documentmode: man
+---
 
-keywords          : "attractiveness, AI-generated images, fiction, fake news, sense of reality"
-wordcount         : "5242"
-bibliography      : references.bib
-floatsintext      : yes
-linenumbers       : yes
-draft             : no
-mask              : yes
-figurelist        : yes
-tablelist         : no
-footnotelist      : no
-classoption       : "man"
-output            : papaja::apa6_word
-csl: utils/apa.csl
-header-includes:
-  - \usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
-editor_options:
-  chunk_output_type: console
----
+```{r}
+#| label: setup
+#| include: false
+library(conflicted)
+library(tidyverse)
+library(flextable)
+library(ftExtra)
+library(officer)
+library(knitr)
+
+conflicts_prefer(dplyr::filter, .quiet = TRUE)
+conflicts_prefer(flextable::separate_header, .quiet = TRUE)
+```
 
@@
 
-```{r message=FALSE, warning=FALSE, fig.cap="The decision to believe that an ambiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.", out.width="100%"}
-knitr::include_graphics("../figures/Figure1.png")
+```{r message=FALSE, warning=FALSE, fig.cap="Figure 1.
+The decision to believe that an ambiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.", out.width="100%"}
+knitr::include_graphics("../../figures/figure1.png")
 ```
@@
 
-```{r message=FALSE, warning=FALSE, fig.cap="Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
+```{r message=FALSE, warning=FALSE, fig.cap="Figure 2.
+Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
 fake (solid line) and 2) on the confidence associated with that judgement (dashed lines) depending on the sex.
@@
 Stars indicate significance (p < .001***, p < .01**, p < .05*).", out.width="100%"}
-knitr::include_graphics("../figures/Figure2.png")
+knitr::include_graphics("../../figures/Figure2.png")
 ```
@@
 <!-- https://github.com/RealityBending/FakeFace -->
-[**MASKED FOR REVIEW**]
 
-# Funding
-
-[**MASKED FOR REVIEW**]
-<!-- This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister’s Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
--->
-
-# Acknowledgments
-
-We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
-
-\newpage
+\pagebreak
 
@@
 
-::: {#refs custom-style="Bibliography"}
+<!-- References will auto-populate in the refs div below -->
+
+::: {#refs}
 :::

### 2024-06-18 submission/new_manuscript/manuscript.qmd
updated revision doc and manuscript doc

@@
 This exploratory study primarily aims at investigating the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the *affective reality theory*
-[outlined in @makowski2018cognitive; @makowski2019phenomenal, see @makowski2023affective for a summary],
-which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
+Based on the *affective reality theory* [@makowski2023affective], which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
 We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
@@
 
-All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at [**MASKED FOR REVIEW**]
-<!-- [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}. -->
+All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
 
-### Ethics Statement
-
-This study was approved by the 
-<!-- NTU Institutional Review Board (NTU IRB-2022-187)  -->
-[**IRB NUMBER**]
+**Ethics Statement.** 
+This study was approved by the NTU Institutional Review Board (NTU IRB-2022-187)
+<!-- [**IRB NUMBER**] -->
 and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
@@
 
-### Procedure
-
+**Procedure.** 
 In the first part of the study, participants answered a series of personality questionnaires presented in the order below. These include the *Mini-IPIP6*
@@
 
-### Participants
-
+**Participants.**
 Although the main part of the study relied on within-subject design (with 109 trials per participant), we also planned to do between-participants analyses, thus aiming at collecting a larger sample than traditionally used in experimental psychology (with budget availability as the main constraint).
@@
 
-### Data Analysis
-
+**Data Analysis.**
 The real-fake ratings (measured originally with a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
@@
 
-### Determinants of Simulation Monitoring
-
+**Determinants of Simulation Monitoring.**
 Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
@@
 
-### Inter-Individual Correlates of Simulation Monitoring
-
+**Inter-Individual Correlates of Simulation Monitoring.**
 The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\%~CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\%~CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
@@
 The datasets generated and/or analysed during the current study are available in the GitHub repository 
-<!-- https://github.com/RealityBending/FakeFace -->
+https://github.com/RealityBending/FakeFace
 

### 2024-07-02 submission/new_manuscript/manuscript.qmd
Soma changes to manuscript and revision doc

@@
 
-For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
+Advancements in technology have now made it possible to create near-perfect simulations that are indistinguishable from reality.
+These simulations are more affordable, faster to produce, and more accessible than at any other time in human history.
 These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
@@
 
-While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies or via recent algorithms such as GANs or diffusion models often include distortions or lack certain key details that makes them visually distinct from real images, @mcdonnell2010face; @corvi2022detection], it is fair to assume that these technical limitations will become negligible in the near future.
+While not all simulations have achieved perfect realism, such as Computer Generated Images (CGI) in movies or via recent algorithms such as GANs or diffusion model, which often include distortions or lack certain key details distinguishing them from real images  [@mcdonnell2010face; @corvi2022detection], it is fair to assume that these technical limitations will become negligible in the near future.
 This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos [@nightingale2022; @tucciarelli2020; @moshel2022].

### 2024-09-02 analysis.Rmd

@@
 library(brms)
+library(psych) # reliability analysis
+
+set.seed(33)
 
@@
 ```
+
+## Scales - Reliability analysis {.tabset}
+
+### IPIP
+
+```{r}
+#extraversion
+dplyr::select(df, starts_with("Extraversion_")) |>
+psych::alpha(check.keys = TRUE) # 0.82
+
+#Conscientiousness
+dplyr::select(df, starts_with("Conscientiousness_")) |>
+psych::alpha(check.keys = TRUE) # 0.73
+
+#Neuroticism 
+dplyr::select(df, starts_with("Neuroticism_")) |>
+psych::alpha(check.keys = TRUE) # 0.59
+
+#Openness
+dplyr::select(df, starts_with("Conscientiousness_")) |>
+psych::alpha(check.keys = TRUE) # 0.73
+
+#Honest-Humility
+dplyr::select(df, starts_with("HonestyHumility_")) |>
+psych::alpha(check.keys = TRUE) # 0.7
+
+#Agreableness 
+dplyr::select(df, starts_with("Agreeableness_")) |>
+psych::alpha(check.keys = TRUE) # 0.82
+
+```
+
+### SIAS-6 and SPS-6
+
+```{r}
+#SIAS- social interaction scale
+dplyr::select(df, starts_with("SIAS_")) |>
+psych::alpha(check.keys = TRUE) # 0.84
+
+#SPS - social phobia scale
+dplyr::select(df, starts_with("Social_Phobia_")) |>
+psych::alpha(check.keys = TRUE) # 0.87
+
+```
+
+### Expectations about AI technology and GAAIS
+
+<!-- Expectations about AI = items that did not said OG scale item from the parameters.js (GAAIS_1;3;5;7;10) -->
+
+```{r}
+
+#expectations about AI
+dplyr::select(df, AI_1_RealisticImages, AI_3_VideosReal, AI_5_ImitatingReality, AI_7_RealisticVideos, AI_10_FaceErrors) |>
+psych::alpha(check.keys = TRUE) # 0.61
+
+#GAAIS
+dplyr::select(df, AI_2_Unethical, AI_4_DailyLife, AI_6_Dangerous, AI_8_Exciting, AI_9_Applications) |>
+psych::alpha(check.keys = TRUE) # 0.74
+
+## positive GAAIS
+dplyr::select(df, AI_4_DailyLife, AI_8_Exciting, AI_9_Applications) |>
+psych::alpha(check.keys = TRUE) # 0.74
+
+## negtavive GAAIS
+dplyr::select(df, AI_2_Unethical, AI_6_Dangerous) |>
+psych::alpha(check.keys = TRUE) # 0.74
+
+```
+
+### FFNI-BF
+
+#### Low-order dimensions
+
+```{r}
+
+#acclaim seeking 
+dplyr::select(df, Acclaim_Seeking_1, Acclaim_Seeking_16) |>
+psych::alpha(check.keys = TRUE) # 0.68
+
+#authoritativeness
+dplyr::select(df, Authoritativeness_3, Authoritativeness_18) |>
+psych::alpha(check.keys = TRUE) # 0.77
+
+#grandiose fantasies
+dplyr::select(df, Grandiose_Fantasies_8, Grandiose_Fantasies_23) |>
+psych::alpha(check.keys = TRUE) # 0.8
+
+#Exhibition 
+dplyr::select(df, Exhibitionism_6, Exhibitionism_21) |>
+psych::alpha(check.keys = TRUE) # 0.65
+
+#Manipulativeness
+dplyr::select(df, Manipulativeness_11, Manipulativeness_26) |>
+psych::alpha(check.keys = TRUE) # 0.58
+
+#Exploitativeness
+dplyr::select(df, Exploitativeness_7, Exploitativeness_22) |>
+psych::alpha(check.keys = TRUE) # 0.74
+
+# Entitlement 
+dplyr::select(df, Entitlement_5, Entitlement_20) |>
+psych::alpha(check.keys = TRUE) # 0.8
+
+#  Lack of empathy
+dplyr::select(df, Lack_of_Empathy_10, Lack_of_Empathy_25) |>
+psych::alpha(check.keys = TRUE) # 0.68
+
+#Arrogance 
+dplyr::select(df, Arrogance_2, Arrogance_17) |>
+psych::alpha(check.keys = TRUE) # 0.59
+
+# Reactive Anger
+dplyr::select(df, Reactive_Anger_13, Reactive_Anger_28) |>
+psych::alpha(check.keys = TRUE) # 0.66
+
+# Distrut
+dplyr::select(df, Distrust_19, Distrust_4) |>
+psych::alpha(check.keys = TRUE) # 0.55
+
+# Thrill Seeking 
+dplyr::select(df, Thrill_Seeking_15, Thrill_Seeking_30) |>
+psych::alpha(check.keys = TRUE) # 0.77
+
+# Shame
+dplyr::select(df, Shame_14, Shame_29) |>
+psych::alpha(check.keys = TRUE) # 0.72
+
+# Indifference 
+dplyr::select(df, Indifference_9, Indifference_24) |>
+psych::alpha(check.keys = TRUE) # 0.63
+
+# Need for admiration
+dplyr::select(df, Need_for_Admiration_12, Need_for_Admiration_27) |>
+psych::alpha(check.keys = TRUE) # 0.57
+
+```
+
+#### High-order dimensions
+
+```{r}
+
+##agentic narcissism
+
+dplyr::select(df, Acclaim_Seeking_1, Acclaim_Seeking_16, Authoritativeness_3, Authoritativeness_18, Grandiose_Fantasies_8, Grandiose_Fantasies_23,  Exhibitionism_6, Exhibitionism_21) |>
+psych::alpha(check.keys = TRUE) #0.78
+
+#Antognistic Narcissism
+
+dplyr::select(df, Manipulativeness_11, Manipulativeness_26, Exploitativeness_7, Exploitativeness_22, Entitlement_5, Entitlement_20, Lack_of_Empathy_10, Lack_of_Empathy_25, Arrogance_2, Arrogance_17, Reactive_Anger_13, Reactive_Anger_28, Distrust_19, Distrust_4, Thrill_Seeking_15, Thrill_Seeking_30) |>
+psych::alpha(check.keys = TRUE) # 0.83
+
+# Neurotic Narcissism
+
+dplyr::select(df, Shame_14, Shame_29, Indifference_9, Indifference_24, Need_for_Admiration_12, Need_for_Admiration_27) |>
+psych::alpha(check.keys = TRUE) # 0.79
+
+```
+
+### R-GPTS
+
+```{r}
+# Reference
+dplyr::select(df, starts_with("Reference_")) |>
+psych::alpha(check.keys = TRUE) # 0.85
+
+#Prosecution 
+dplyr::select(df, starts_with("Persecution_")) |>
+psych::alpha(check.keys = TRUE) # 0.93
+
+```
+
+### IUS-12
+
+```{r}
+
+# Prospective anxiety 
+dplyr::select(df, starts_with("Prospective_Anxiety_")) |>
+psych::alpha(check.keys = TRUE) # 0.8
+
+#Inhibitory anxiety
+dplyr::select(df, starts_with("Inhibitory_Anxiety_")) |>
+psych::alpha(check.keys = TRUE) # 0.82
+
+```
+
+### Sel-rated attractiveness
+
+```{r}
+
+dplyr::select(df, self_rated_general_attractiveness, self_rated_physical_attractiveness) |>
+psych::alpha(check.keys = TRUE) # 0.94
+
+```
+
+:::
 
@@
 
-```{r make_models, message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width, cache=cache}
+```{r make_models, fig.height=fig.width, fig.width=fig.width, message=FALSE, warning=FALSE, cache=FALSE}
 rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),

### 2024-09-02 analysis.Rmd
Update analysis.Rmd

@@
 
+```{r message=FALSE, warning=FALSE}
+# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
+df |>
+  mutate(Stimulus = fct_relevel(Stimulus, df |>
+    group_by(Stimulus) |>
+    summarize(Belief_Answer = mean(Belief_Answer)) |>
+    ungroup() |>
+    arrange(Belief_Answer) |>
+    pull(Stimulus) |>
+    as.character())) |>
+  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
+  ggplot(aes(x = Belief_Answer, y = Stimulus, fill = Stimulus)) +
+  ggdist::stat_slab(scale = 4, slab_alpha = 2/3, normalize = "groups", color = "black", size = 0.2) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  scale_y_discrete(expand = c(0.02, 0)) +
+  scale_x_continuous(
+    limits = c(-1, 1),
+    expand = c(0, 0),
+    breaks = c(-0.95, 0, 0.95),
+    label = c("Fake", "", "Real")
+  ) +
+  scale_fill_viridis_d() +
+  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
+  guides(fill = "none") +
+  see::theme_modern() +
+  theme(
+    # axis.text.y = element_blank(),
+    plot.title = element_text(face = "bold", hjust = 0.5)
+  ) +
+  ggside::geom_xsidedensity(fill = "grey", color = "white") +
+  ggside::scale_xsidey_continuous(expand = c(0, 0))
+```
+
 ### Colinearity

### 2024-10-08 submission/new_manuscript/manuscript.qmd
changes to manuscript and R1

@@
 title: "Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated"
-# If blank, the running header is the title in upper case.
 shorttitle: "Attractiveness and Reality"
-# Set names and affiliations.
-# It is nice to specify everyone's orcid, if possible.
-# There can be only one corresponding author, but declaring one is optional.
 author:
@@
         department:  Centre for Research and Development in Learning
-
 author-note:
@@
     # Example: [Author name] is now at [affiliation].
-    affiliation-change: ~
+    affiliation-change: null
     # Example: [Author name] is deceased.
-    deceased: ~
+    deceased: null
   # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
   disclosures:
+    # Acknowledge and cite data/materials to be shared.
+    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
     # Example: This study was registered at X (Identifier Y).
-    study-registration: ~
-    # Acknowledge and cite data/materials to be shared.
-    data-sharing: ~
+    study-registration: null
+    data-sharing: null
     # Example: This article is based on the dissertation completed by [citation].  
-    related-report: ~
+    related-report: null
     # Example: [Author name] has been a paid consultant for Corporation X, which funded this study.
-    conflict-of-interest: ~
+    conflict-of-interest: null
     # Example: This study was supported by Grant [Grant Number] from [Funding Source].
-    financial-support: ~
+    financial-support: null
     # Example: The authors are grateful to [Person] for [Reason].
-    gratitude: ~
-    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
-    authorship-agreements: ~
+    gratitude: null
+    authorship-agreements: null
 abstract: " Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
@@
 We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation."
-# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
 keywords: [attractiveness, AI-generated images, fiction, fake news, sense of reality]
-# If true, tables and figures are mingled with the text instead of listed at the end of the document.
 floatsintext: true
-# Numbered lines (.pdf and .docx only)
 numbered-lines: true
-# File with references
 bibliography: references.bib
-# Suppress title page
 suppress-title-page: false
-# Masks references that appear in the masked-citations list
 mask: false
@@
     documentmode: man
+editor: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-Advancements in technology have now made it possible to create near-perfect simulations that are indistinguishable from reality.
-These simulations are more affordable, faster to produce, and more accessible than at any other time in human history.
-These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access [@nightingale2022].
-Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination [@pantserev2020].
-This issue is central to what has been coined the "post-truth era" [@lewandowsky2017beyond], in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
+Advancements in technology have now made it possible to create
+near-perfect simulations that are indistinguishable from reality. These
+simulations are more affordable, faster to produce, and more accessible
+than at any other time in human history. These artificial, yet realistic
+constructs permeate all areas of life through immersive works of
+fiction, deep fakes (real-like images and videos generated by deep
+learning algorithms), virtual and augmented reality (VR and AR),
+artificial beings (artificial intelligence "bots" with or without a
+physical form), fake news and skewed narratives, of which ground truth
+is often hard to access [@nightingale2022]. Such developments not only
+carry important consequences for the technological and entertainment
+sectors, but also for security and politics - for instance if used for
+propaganda and disinformation, recruitment into malevolent
+organizations, or religious indoctrination [@pantserev2020]. This issue
+is central to what has been coined the "post-truth era"
+[@lewandowsky2017beyond], in which the distinction (and lack thereof)
+between authentic and simulated objects will play a critical role.
 
@@
 
-While not all simulations have achieved perfect realism, such as Computer Generated Images (CGI) in movies or via recent algorithms such as GANs or diffusion model, which often include distortions or lack certain key details distinguishing them from real images  [@mcdonnell2010face; @corvi2022detection], it is fair to assume that these technical limitations will become negligible in the near future.
-This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos [@nightingale2022; @tucciarelli2020; @moshel2022].
-Such a technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective "physical" characteristics, how can we form judgements regarding their nature?
+While not all simulations have achieved perfect realism, such as
+Computer Generated Images (CGI) in movies or via recent algorithms such
+as GANs or diffusion model, which often include distortions or lack
+certain key details distinguishing them from real images
+[@mcdonnell2010face; @corvi2022detection], it is fair to assume that
+these technical limitations will become negligible in the near future.
+This is particularly true in the field of face generation, where
+face-generation algorithms are already able to create stimuli that are
+virtually indistinguishable from real photos [@nightingale2022;
+@tucciarelli2020; @moshel2022]. Such a technological feat, however,
+leads to a new question: if real and fake stimuli cannot be
+differentiated based on their objective "physical" characteristics, how
+can we form judgements regarding their nature?
 
@@
 
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality [a process henceforth referred to as *simulation monitoring*, @makowski2018cognitive; @makowski2019phenomenal].
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy [@michael2021source; @susmann2021persuasion], people tend to draw on peripheral contextual cues (**Figure 1**), such as the source of the stimulus (e.g., which journal was the information published in), and its credibility, authority and expertise, to help facilitate their evaluation [@petty1986elaboration; @susmann2021persuasion; @michael2021source].
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are often mass-shared with little context) makes this task progressively difficult [@berghel2018weaponizing; @chen2015news].
-Thus, in the absence of clear contextual information, what drives our beliefs of reality?
+Literature shows that the context surrounding a stimulus often plays an
+important role in the assessment of its reality [a process henceforth
+referred to as *simulation monitoring*, @makowski2018cognitive;
+@makowski2019phenomenal]. With the extensive search and processing of
+cues within ambiguous stimuli being an increasingly complex and
+cognitively effortful strategy [@michael2021source;
+@susmann2021persuasion], people tend to draw on peripheral contextual
+cues (**Figure 1**), such as the source of the stimulus (e.g., which
+journal was the information published in), and its credibility,
+authority and expertise, to help facilitate their evaluation
+[@petty1986elaboration; @susmann2021persuasion; @michael2021source].
+However, the atomization and decontextualization of information allowed
+by online social media (where text snippets or video excerpts are often
+mass-shared with little context) makes this task progressively difficult
+[@berghel2018weaponizing; @chen2015news]. Thus, in the absence of clear
+contextual information, what drives our beliefs of reality?
 
@@
 
-Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short].
-For instance, individuals with stronger analytical reasoning skills have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy], and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations [@britt2019reasoned].
-Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].
+Evidence suggests that inter-individual characteristics play a crucial
+role in simulation monitoring, with factors such as cognitive style,
+prior beliefs, and personality traits [@bryanov2021determinants;
+@ecker2022psychological; @sindermann2020short]. For instance,
+individuals with stronger analytical reasoning skills have been found to
+better discriminate real from fake stimuli [@pehlivanoglu2021role;
+@pennycook2019lazy], and prior knowledge or beliefs about the stimulus
+influences one's perception of it by biasing the attention deployment
+towards information that is in line with one's expectations
+[@britt2019reasoned]. Furthermore, dispositional traits, such as high
+levels of narcissism and low levels of openness and conscientiousness,
+have been associated with greater susceptibility to fake news
+[@piksa2022cognitive; @sindermann2020short]. **Interestingly, a recent
+review suggested that narcissism was related to a strong self-perceived
+ability at detecting lies [@turi2022tangled], which could translate to
+participants scoring high on narcissism providing more clear cut and
+confidence responses. Conversely, those high in honesty-humility tend to
+be more conservative in their judgments to ensure fairness
+[@liu2020honesty], likely resulting in lower confidence ratings.**
 
@@
 
-Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like "being there", as if the object of experience was real - when engaged in a fictional movie or a VR environment [@sanchez2005presence; @makowski2017being].
-Indeed, participants' self-reported emotional arousal were found to significantly predict the probability that they would perceive images as real [@azevedo2020body].
-Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive].
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion], and higher neurophysiological arousal was predictive of judging realistic images as real [@azevedo2020body].
-Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in guiding our appraisal of a stimulus.
+Beyond stimulus- and individual-related characteristics, evidence
+suggests that the interaction between the two (i.e., the subjective
+reaction associated with the experience of a given stimulus),
+contributes to simulation monitoring decisions. For instance, the
+intensity of experienced emotions have been shown to increase one's
+sense of presence - the extent to which one feels like "being there", as
+if the object of experience was real - when engaged in a fictional movie
+or a VR environment [@sanchez2005presence; @makowski2017being]. Indeed,
+participants' self-reported emotional arousal were found to
+significantly predict the probability that they would perceive images as
+real [@azevedo2020body]. Conversely, beliefs that emotional stimuli were
+fake (e.g., that emotional scenes were not authentic but instead
+involved actors and movie makeup) were found to result in emotion
+down-regulation [@makowski2019phenomenal; @sperduti2017distinctive]. In
+line with these findings, studies on susceptibility to fake news have
+also found heightened stimulus emotionality to be associated with
+greater belief [@martel2020reliance; @bago2022emotion], and higher
+neurophysiological arousal was predictive of judging realistic images as
+real [@azevedo2020body]. Additionally, other factors, such as the
+stimuli's perceived self-relevance [@sperduti2016paradox;
+@goldstein2009pleasure], as well as familiarity [@begg1992dissociation],
+could also play a role in guiding our appraisal of a stimulus.**For
+instance,** @miller2023 **reported that participants were more likely to
+mistakenly identify AI-generated faces as real because they perceived
+them as more familiar.**
 
-<!-- Attractiveness -->
+<!-- Attractiveness and trustworthiness  -->
 
-Due to their popularity as a target of CGI technology and the prospect offered with facial features that can be experimentally manipulated, AI-generated images of faces are increasingly used to study face processing [@dawel2021systematic], in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017].
-Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real [@tucciarelli2020].
-Conversely, @liefooghe2022faces reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
-Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness contributes to the formation of reality beliefs - has received little attention to date.
+Due to their popularity as a target of CGI technology and the prospect
+offered with facial features that can be experimentally manipulated,
+AI-generated images of faces are increasingly used to study face
+processing [@dawel2021systematic], in particular in relationship with
+saliency or emotions, as well as to other important components of face
+evaluation, such as trustworthiness or attractiveness
+[@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty;
+@calbi2017]. Interestingly, artificially created faces rated as more
+attractive (by an independent group of raters) were perceived as less
+real [@tucciarelli2020]. Conversely, @liefooghe2022faces reports that
+attractiveness ratings were significantly lower when participants who
+were told that the faces were AI-generated were compared to those who
+had no prior knowledge. **Similarly, when participants are informed that
+faces are AI-generated, the perceived artificiality leads to lower trust
+ratings [@wang2024], even when they are real faces
+[@liefooghe2022faces]. In contrast, when participants are unaware that
+the faces are AI-generated, trust ratings for these synthetic faces tend
+to increase [@nightingale2022]**. Whereas this line of evidence suggests
+that reality beliefs have an effect on face attractiveness and
+**trustworthiness** ratings, the opposite question - whether
+attractiveness **and trustworthiness contribute** to the formation of
+reality beliefs - has received little attention to date.
 
@@
 
-AI-generated content, in particular realistic images, is becoming commonplace and carries important risks for misinformation and black-mailing [@viola2023designed], emphasizing the need to understand the different components that come into play in the formation of reality beliefs.
-This exploratory study primarily aims at investigating the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the *affective reality theory* [@makowski2023affective], which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
-We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef; @little2011facial], and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
-Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-Importantly, this study does investigate the discriminative accuracy between "true" photos and "true" artificially-generated images (which we consider more a technological issue than a psychological one), focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
+AI-generated content, in particular realistic images, is becoming
+commonplace and carries important risks for misinformation and
+black-mailing [@viola2023designed], emphasizing the need to understand
+the different components that come into play in the formation of reality
+beliefs. This exploratory study primarily aims at investigating the
+effect of facial attractiveness on simulation monitoring, i.e., on the
+beliefs that an image is real or artificially generated. Based on the
+*affective reality theory* [@makowski2023affective], which suggests that
+salient and emotional stimuli are perceived to be more real (up to a
+point of reversal after which beliefs of fiction becomes used an emotion
+regulation strategy), we hypothesize a quadratic relationship between
+perceived realness and attractiveness: faces rated as highly attractive
+or unattractive will more likely be believed to be real. We expect a
+similar relationship with trustworthiness ratings given its
+well-established link with attractiveness [@liefooghe2022faces;
+@bartosik2021you; @garrido2017kdef; @little2011facial], and a positive
+relationship with familiarity (as more familiar faces would appear as
+more salient, self-relevant and anchored in reality). Additionally, we
+will further explore the link shared by dispositional traits, such as
+personality and attitude towards AI, with simulation monitoring
+tendencies. Importantly, this study does investigate the discriminative
+accuracy between "true" photos and "true" artificially-generated images
+(which we consider more a technological issue than a psychological one),
+focusing on the beliefs that a stimulus is real or fake, independently
+of its true nature.
 
@@
 
-All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
+All the material (preregistration, experiment demo, experiment code, raw
+data, analysis script with complementary figures and analyses, etc.) is
+available at
+[**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
 
-**Ethics Statement.** 
-This study was approved by the NTU Institutional Review Board (NTU IRB-2022-187)
-<!-- [**IRB NUMBER**] -->
-and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
-All participants provided their informed consent prior to participation and were incentivized after completing the study.
+**Ethics Statement.** This study was approved by the NTU Institutional
+Review Board (NTU IRB-2022-187) <!-- [**IRB NUMBER**] --> and all
+procedures performed were in accordance with the ethical standards of
+the institutional board and with the 1964 Helsinki Declaration. All
+participants provided their informed consent prior to participation and
+were incentivized after completing the study.
 
-**Procedure.** 
-In the first part of the study, participants answered a series of personality questionnaires presented in the order below. These include the *Mini-IPIP6*
-<!-- (24 items) [@sibley2011]  -->
-[24 items, @sibley2011]
-measuring 6 personality traits, the *SIAS-6* and the *SPS-6*
-<!-- (6 items each) [@peters2012development] -->
-[6 items each, @peters2012development]
-assessing social anxiety levels, 5 items we devised pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images"), of which we mixed with 5 items from the general attitudes towards AI scale to lower the former's saliency and the possibility of it priming the subjects about the task,
-<!-- (*GAAIS*) [@schepman2020initial]. -->
-[*GAAIS*, @schepman2020initial]
-the *FFNI-BF*
-<!-- (30 items) [@jauk2022validation] -->
-[30 items, @jauk2022validation]
-measuring 9 facets of narcissism; the *R-GPTS*
-<!-- (18 items) [@freeman2021revised] -->
-[18 items, @freeman2021revised]
-measuring 2 dimensions related to paranoid thinking; and the *IUS-12*
-<!-- (12 items) [@carleton2007fearing] -->
-[12 items, @carleton2007fearing]
-measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness
+**Procedure.** In the first part of the study, participants answered a
+series of personality questionnaires presented in the order below. These
+include the *Mini-IPIP6* <!-- (24 items) [@sibley2011]  --> [24 items,
+@sibley2011] measuring 6 personality traits, the *SIAS-6* and the
+*SPS-6* <!-- (6 items each) [@peters2012development] --> [6 items each,
+@peters2012development] assessing social anxiety levels, 5 items we
+devised pertaining to expectations about AI-generated image technology
+("I think current Artificial Intelligence algorithms can generate very
+realistic images"), **to potentially test and mitigate the potential
+effect of expectations/beliefs about AI.** **These items were** mixed
+with 5 items from the general attitudes towards AI scale to lower the
+former's saliency and the possibility of it priming the subjects about
+the task, <!-- (*GAAIS*) [@schepman2020initial]. --> [*GAAIS*,
+@schepman2020initial] the *FFNI-BF*
+<!-- (30 items) [@jauk2022validation] --> [30 items,
+@jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS*
+<!-- (18 items) [@freeman2021revised] --> [18 items,
+@freeman2021revised] measuring 2 dimensions related to paranoid
+thinking; and the *IUS-12* <!-- (12 items) [@carleton2007fearing] -->
+[12 items, @carleton2007fearing] measuring intolerance to uncertainty.
+Self-rated attractiveness was also assessed using 2 items - one
+measuring general attractiveness
 <!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->
-["How attractive would you say you are?", @marcinkowska2021self]
-and the other measuring physical attractiveness
+["How attractive would you say you are?", @marcinkowska2021self] and the
+other measuring physical attractiveness
 <!-- ("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive] -->
-["How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive].
-3 attention check questions were also embedded in the surveys.
+["How would you rate your own physical attractiveness relative to the
+average", @spielmann2020predictive]. 3 attention check questions were
+also embedded in the surveys.
 
-In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database
-<!-- (AMFD) [@chen2021broadening]  -->
-[AMFD, @chen2021broadening]
-were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
-After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 visual analog scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").
+In the second part of this study, images of neutral-expression faces
+from the validated American Multiracial Face Database
+<!-- (AMFD) [@chen2021broadening]  --> [AMFD, @chen2021broadening] were
+presented to the participants for 500ms each, in a randomized order,
+following a fixation cross display (750 ms). T**he decision to present
+the faces for 500 ms was based on pilot studies, which demonstrated that
+this duration provides a sufficient perceptual window for
+decision-making and aligns with previous research indicating stable
+judgment levels and increased confidence beyond this exposure time
+[@willis2006first].**
 
-In the last part of the study, participants were informed that "about half" of the images previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
-The same set of stimuli was displayed again for 500 ms in a new randomized order.
-This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with *Fake* and *Real* as the two extremes).
-The study was implemented using *jsPsych* [@de2015jspsych], and the exact instructions are available in the experiment code.
+**The AMFD is a recently validated database including a set of 110
+pictures of homogeneous quality featuring diverse faces (particularly in
+terms of ethnicity), each (except one) posing with either a neutral or
+smiling expression. We selected all 109 neutral images (89 women and 20
+men) to reduce the influence of confounding factors like affect. The
+AMFD primarily features racially ambiguous faces, representing multiple
+racial categories such as multiracial, Latinx, and white. The database
+includes 81 faces from individuals self-reporting two racial backgrounds
+and 29 from those with three or more racial backgrounds: 33%
+Asian/White, 22% Latinx/White, 11% Asian/Latinx, 6% White/Middle
+Eastern, 5% Black/White, and 5% Asian/Middle Eastern, with about 18%
+identifying as other racial backgrounds.**
 
-**Participants.**
-Although the main part of the study relied on within-subject design (with 109 trials per participant), we also planned to do between-participants analyses, thus aiming at collecting a larger sample than traditionally used in experimental psychology (with budget availability as the main constraint).
-One hundred and fifty participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022; douglas2023data].
-The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
-Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish.
-Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.
+After each stimulus presentation, ratings of *Trustworthiness* ("I find
+this person trustworthy") and *Familiarity* ("This person reminds me of
+someone I know") were collected using visual analog scales. Notably, as
+facial attractiveness is a multidimensional construct, encompassing
+evolutionary, sociocultural, biological as well as cognitive aspects
+[@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness
+using 2 visual analog scales, measuring general *Attractiveness* ("I
+find this person attractive") and physical *Beauty* ("This face is
+good-looking"). **This dual-scale approach aims to reflect two
+conceptually distinct dimensions: Attractiveness might capture personal,
+Self-relevant and subjective appeal, whereas Beauty might be related to
+a more “objective” decision based on aesthetic criteria that can be
+recognized independently of personal attraction. In other words, we
+wanted the experiment to be able to potentially capture scenarios where
+a face could be judged beautiful yet not, attractive and vice versa.**
 
-We excluded 5 participants that either failed 2 (\>= 66.6%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
-The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3% females, 51.0% males, 0.7% others).
+In the last part of the study, participants were informed that "about
+half" of the images previously seen were AI-generated (the instructions
+used a cover story explaining that the aim of the research was to
+validate a new face generation algorithm). The same set of stimuli was
+displayed again for 500 ms in a new randomized order. This time, after
+each display, participants were asked to express their belief regarding
+the nature of the stimulus using a visual analog scale (with *Fake* and
+*Real* as the two extremes). The study was implemented using *jsPsych*
+[@de2015jspsych], and the exact instructions are available in the
+experiment code.
 
-**Data Analysis.**
-The real-fake ratings (measured originally with a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\>= 0) as opposed to fake (\< 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using mixed beta regressions (suited for outcome variables expressed in percentages).
-The models included the participants and stimuli as random factors.
+**Participants.** Although the main part of the study relied on
+within-subject design (with 109 trials per participant), we also planned
+to do between-participants analyses, thus aiming at collecting a larger
+sample than traditionally used in experimental psychology (with budget
+availability as the main constraint). One hundred and fifty participants
+were recruited via *Prolific*, a crowd-sourcing platform recognized for
+providing high quality data [@peer2022; douglas2023data]. The only
+inclusion criterion was a fluent proficiency in English to ensure that
+the experiment instructions would be well-understood. Participants were
+incentivised with a reward of about \textsterling 7.5 for completing the
+study, which took about 45 minutes to finish. Demographic variables
+(age, gender, sexual orientation, education and ethnicity) were
+self-reported on a voluntary basis.
 
-We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were all images of real faces) were judged as fake in sufficient proportion to warrant their analysis.
-Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating), as well as that of the presentation order to check whether for habituation or learning effects.
+We excluded 5 participants that either failed 2 (\>= 66.6%) or more
+attention check questions, took an implausibly short time to finish the
+questionnaires or had incomplete responses. The final sample included
+145 participants (Mean age = 28.3, SD = 9.0, range: \[19, 66\]; Sex:
+48.3% females, 51.0% males, 0.7% others).
 
-The determinants of reality beliefs were modelled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (**Figure 2**).
-Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables *mutatis mutandis*.
-The analysis focused on sexual-orientation relevant stimuli, i.e., on faces that were aligned with respect to the participants' sexual orientation (i.e., female faces for heterosexual males, male faces for homosexual males, etc.), and the models included the interaction with the participants' gender (as a sexual dimorphism has been reported in face appraisal processes).
-For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
-Finally, we investigated the inter-individual correlates of simulation monitoring with similar models (but this time, for all items regardless of the participant's gender or sexual orientation) for each questionnaire, with all of the subscales as orthogonal predictors.
+**Data Analysis.** The real-fake ratings (measured originally with a
+\[-1, 1\] analog scale) were converted into two scores, corresponding to
+two conceptually distinct mechanisms: the dichotomous *belief* (real or
+fake, based on the sign of the rating) and the *confidence* (the
+rating's absolute value) associated with that belief. The former was
+analyzed using logistic mixed models, which modelled the probability of
+assigning a face to the real (\>= 0) as opposed to fake (\< 0). The
+latter, as well as the other face ratings (attractiveness, beauty,
+trustworthiness and familiarity), was modelled using mixed beta
+regressions (suited for outcome variables expressed in percentages). The
+models included the participants and stimuli as random factors.
+
+We started by investigating the effect of the procedure and instructions
+to check whether the stimuli (which were all images of real faces) were
+judged as fake in sufficient proportion to warrant their analysis.
+Additionally, we assessed the effect of the re-exposure delay, i.e., the
+time between the first presentation of the image (corresponding to the
+face ratings) and the second presentation (for the real-fake rating), as
+well as that of the presentation order to check whether for habituation
+or learning effects.
+
+The determinants of reality beliefs were modelled separately for
+attractiveness, beauty, trustworthiness, and familiarity, using second
+order raw polynomials coefficients to allow for possible quadratic
+relationships (**Figure 2**). Aside from attractiveness (conceptualized
+as a general construct), models for beauty, trustworthiness and
+familiarity were adjusted for the the two remaining variables *mutatis
+mutandis*. The analysis focused on sexual-orientation relevant stimuli,
+i.e., on faces that were aligned with respect to the participants'
+sexual orientation (i.e., female faces for heterosexual males, male
+faces for homosexual males, etc.), and the models included the
+interaction with the participants' gender (as a sexual dimorphism has
+been reported in face appraisal processes). For the attractiveness and
+beauty models, we then added the interaction with the reported
+self-attractiveness (the average of the two questions pertaining to it)
+to investigate its potential modulatory effect. Finally, we investigated
+the inter-individual correlates of simulation monitoring with similar
+models (but this time, for all items regardless of the participant's
+gender or sexual orientation) for each questionnaire, with all of the
+subscales as orthogonal predictors.
 
@@
 
-The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle].
-As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant ($p <.01$).
+The analysis was carried out using *R 4.2* [@RCoreTeam2022], the
+*tidyverse* [@wickham2019], and the *easystats* collection of packages
+[@insightArticle; @bayestestRArticle; @performanceArticle;
+@parametersArticle; @correlationArticle]. As all the details, scripts
+and complimentary analyses are open-access, we will focus in the
+manuscript on findings that are highly statistically significant
+($p <.01$).
 
@@
 -->
-On average, across participants, 44% of images (95%\~CI [0.12, 0.64]) were judged as fake and 56% of images (95%\~CI [0.36, 0.88]) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.
 
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\%~CI = [0.99, 1.00]$), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$).
-The presentation order also did not have have an effect on the belief ($OR = 1.00$, $95\%~CI = [1.00, 1.00]$) but was related to a decrease of confidence ($\beta_{real} = -0.003$, $95\%~CI = [-0.004, -0.002]$, $p < .001$; $\beta_{fake} = -0.002$, $95\%~CI = [-0.004, -0.0003]$, $p = .021$): items presented at the end of the session were judged with a similar bias but a decreased overall confidence.
+On average, across participants, 44% of images (95%\~CI \[0.12, 0.64\])
+were judged as fake and 56% of images (95%\~CI \[0.36, 0.88\]) as real.
+An intercept-only model with the participants and images as random
+factors showed that the Intraclass Correlation Coefficient (ICC), which
+can be interpreted as the proportion of variance explained by the random
+factors, was of 9.0% for the participants and 9.6% for the stimuli.
 
-**Determinants of Simulation Monitoring.**
-Attractiveness had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 16.57$, $95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a quadratic relationship for females ($\beta_{poly2} = 7.82$, $95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both non-attractive and attractive faces being judged as more real.
-Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real ($\beta_{poly2} = 4.30$, $95\%~CI = [0.97, 7.64]$, $z = 2.53$, $p = .011$) and as fake ($\beta_{poly2} = 5.23$, $95\%~CI = [0.
-86, 9.60]$, $z = 2.35$, $p = .019$) for females.
-For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake ($\beta_{poly2} = -9.92$, $95\%~CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$).
-There was no interaction with reported self-attractiveness.
+While the delay of stimulus re-exposure stimulus did not have a
+significant effect on participants' beliefs of reality ($OR = 1.00$,
+$95\%~CI = [0.99, 1.00]$), judgement confidence was found to be
+negatively associated with re-exposure delay when the faces were judged
+as real ($\beta = -0.006$, $95\%~CI = [-0.1, 0.002]$, $p = .004$). The
+presentation order also did not have have an effect on the belief
+($OR = 1.00$, $95\%~CI = [1.00, 1.00]$) but was related to a decrease of
+confidence ($\beta_{real} = -0.003$, $95\%~CI = [-0.004, -0.002]$,
+$p < .001$; $\beta_{fake} = -0.002$, $95\%~CI = [-0.004, -0.0003]$,
+$p = .021$): items presented at the end of the session were judged with
+a similar bias but a decreased overall confidence.
 
-Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 11.82$, $95\%~CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only.
-No effect on confidence was found, aside from a quadratic relationship in females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces ($\beta_{poly2} = 7.84$, $95\%~CI = [3.39, 12.29]$, $z = 3.46$, $p < .001$).
-There was no interaction with reported self-attractiveness.
+**Determinants of Simulation Monitoring.** Attractiveness had a
+significant positive and linear relationship ($R^2_{marginal}$ = 2.0%)
+with the belief that a stimulus was real ($\beta_{poly1} = 16.57$,
+$95\%~CI = [7.33, 25.82]$, $z = 3.51$, $p < .001$) for males, and a
+quadratic relationship for females ($\beta_{poly2} = 7.82$,
+$95\%~CI = [1.81, 13.84]$, $z = 2.55$, $p = .011$), with both
+non-attractive and attractive faces being judged as more real.
+Attractiveness was also found to have a significant positive and
+quadratic relationship with confidence in judging faces both as real
+($\beta_{poly2} = 4.30$, $95\%~CI = [0.97, 7.64]$, $z = 2.53$,
+$p = .011$) and as fake ($\beta_{poly2} = 5.23$,
+$95\%~CI = [0. 86, 9.60]$, $z = 2.35$, $p = .019$) for females. For
+males, however, a significant negative and quadratic relationship was
+found between attractiveness ratings and belief confidence only for
+faces judged as fake ($\beta_{poly2} = -9.92$,
+$95\%~CI = [-18.99, -0.86]$, $z = -2.15$, $p = .032$). There was no
+interaction with reported self-attractiveness.
 
-Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\%~CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
-No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\%~CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\%~CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.
+Beauty, adjusted for trustworthiness and familiarity, had a significant
+positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the
+belief that a stimulus was real ($\beta_{poly1} = 11.82$,
+$95\%~CI = [4.28, 20.21]$, $z = 2.76$, $p = .006$) for males only. No
+effect on confidence was found, aside from a quadratic relationship in
+females for faces judged as fake, suggesting that non-beautiful and
+highly beautiful faces were rated as fake with more confidence than
+average faces ($\beta_{poly2} = 7.84$, $95\%~CI = [3.39, 12.29]$,
+$z = 3.46$, $p < .001$). There was no interaction with reported
+self-attractiveness.
 
-We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%).
-However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only.
-This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
+Trustworthiness, adjusted for beauty and familiarity, had a
+predominantly positive and linear relationship ($R^2_{marginal}$ = 2.0%)
+with the belief that a stimulus was real ($\beta_{poly1} = 6.44$,
+$95\%~CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only.
+No effect on confidence was found for males, whereas a quadratic
+relationship was found for females for both faces judged as real
+($\beta_{poly2} = 6.14$, $95\%~CI = [2.13, 10.14]$, $z = 3.00$,
+$p = .003$) as well as fake ($\beta_{poly2} =6.12$,
+$95\%~CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that
+non-trustworthy and highly trustworthy faces were rated with more
+confidence than average faces.
 
-Note that we also tested as predictors the normative attractiveness and trustworthiness scores (i.e., the average values from the stimuli database validation), which showed a significant positive linear relationship between beliefs of reality and attractiveness, as well as  trustworthiness, only for males (see Supplementary Analysis for details).
+We did not find any significant relationships for familiarity adjusted
+for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%). However, a
+significant positive and linear relationship was found between
+familiarity and the confidence judgements of rating faces as real
+($\beta_{poly1} = 9.98$, $95\%~CI = [3.83, 16.13]$, $z = 3.18$,
+$p = .001$) whereas a negative linear relationship was found with those
+judged as fake ($\beta_{poly1} = -12.41$, $95\%~CI = [-20.27, -4.54]$,
+$z = -3.09$, $p = .002$) for males only. This hence suggests that males
+more confidently judge faces as real with when they are familiar, and as
+fake when they are unfamiliar.
 
-**Inter-Individual Correlates of Simulation Monitoring.**
-The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\%~CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\%~CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$).
+Note that we also tested as predictors the normative attractiveness and
+trustworthiness scores (i.e., the average values from the stimuli
+database validation), which showed a significant positive linear
+relationship between beliefs of reality and attractiveness, as well as
+trustworthiness, only for males (see Supplementary Analysis for
+details).
 
-Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\%~CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\%~CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$).
-Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgements with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).
+**Inter-Individual Correlates of Simulation Monitoring.** The models
+including the personality traits suggested that *Honesty-Humility* had a
+significant negative relationship with the confidence associated with
+real as well as fake judgements ($\beta_{real} = -1.62$,
+$95\%~CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$;
+$\beta_{fake} = -1.16$, $95\%~CI = [-2.09, -0.23]$, $z = -2.45$,
+$p = 0.014$).
 
-A positive trend was found in the relationship between the *Persecutory Ideation* dimension of paranoid thinking and the belief that the faces were real ($\beta = 1.87$, $95\%~CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$).
+Significant positive associations were found between the probability of
+judging faces as real and dimensions of narcissism such as *Acclaim
+Seeking* ($\beta = 2.24$, $95\%~CI = [1.17, 4.27]$, $z = 2.44$,
+$p = .015$), and *Manipulativeness* ($\beta = 0.47$,
+$95\%~CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$). Confidence
+judgements also shared significant links with narcissism through various
+facets, such as a positive relationship between the confidence for both
+real and fake judgements with *Acclaim Seeking* ($\beta_{real} = 1.65$,
+$95\%~CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$,
+$95\%~CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative
+relationship with *Authoritativeness* ($\beta_{real} = -1.57$,
+$95\%~CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$;
+$\beta_{fake} = -1.49$, $95\%~CI = [-2.50, -0.48]$, $z = -2.89$,
+$p = .004$).
 
-The *Prospective Anxiety* aspect of intolerance to uncertainty shared a negative trend in its association with confidence ratings ($\beta_{real} = 1.43$, $95\%~CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$; $\beta_{fake} = -0.91$, $95\%~CI = [-1.93, 0.11]$, $z = -1.75$, $p = .081$).
-No significant effect was found for social anxiety.
+A positive trend was found in the relationship between the *Persecutory
+Ideation* dimension of paranoid thinking and the belief that the faces
+were real ($\beta = 1.87$, $95\%~CI = [0.99, 3.54]$, $z = 1.93$,
+$p = .054$).
 
-Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgements ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).
+The *Prospective Anxiety* aspect of intolerance to uncertainty shared a
+negative trend in its association with confidence ratings
+($\beta_{real} = 1.43$, $95\%~CI = [0.10, 2.76]$, $z = 2.10$,
+$p = .036$; $\beta_{fake} = -0.91$, $95\%~CI = [-1.93, 0.11]$,
+$z = -1.75$, $p = .081$). No significant effect was found for social
+anxiety.
+
+Questions pertaining to the attitude towards AI were reduced to 3
+dimensions through factor analysis, labelled AI-Enthusiasm (loaded by
+items expressing interest and excitement in AI development and
+applications), AI-Realness (loaded by items expressing positive opinions
+on the ability of AI to create realistic material), and AI-Danger
+(loaded by items expressing concerns on the unethical misuse of AI
+technology). However, only AI-Enthusiasm displayed a significant
+positive relationship with the confidence in both real and fake
+judgements ($\beta_{real} = 0.21$, $95\%~CI = [0.02, 0.40]$, $z = 2.20$,
+$p = .028$; $\beta_{fake} = 0.31$, $95\%~CI = [0.12, 0.50]$,
+$z = -8.90$, $p < 0.001$).
 
@@
 
-This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that a stimulus was artificially generated.
-Most strikingly, despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding not only attests to the effectiveness of our instructions, but highlights the current levels of expectation regarding CGI technology.
-The strong impact of prior expectations and information on reality beliefs underlines the volatility of our sense of reality.
-In fact, stimuli-related and participant-related characteristics accounted together for less than 20% of the beliefs variance, suggesting a large contribution of other subjective processes.
+This study aimed at investigating the effect of facial ratings
+(attractiveness, beauty, trustworthiness and familiarity) on simulation
+monitoring, i.e., on the belief that a stimulus was artificially
+generated. Most strikingly, despite all the stimuli being real faces
+from the same database, all participants believed (to high degrees of
+confidence) that a significant proportion of them were fake. This
+finding not only attests to the effectiveness of our instructions, but
+highlights the current levels of expectation regarding CGI technology.
+The strong impact of prior expectations and information on reality
+beliefs underlines the volatility of our sense of reality. In fact,
+stimuli-related and participant-related characteristics accounted
+together for less than 20% of the beliefs variance, suggesting a large
+contribution of other subjective processes.
 
@@
 
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with different patterns observed depending on the participant's gender.
-The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender].
-In fact, female participants were more confident in judging faces as fake only when they were rated very high or low on beauty, suggesting that physical beauty and attractiveness are not analogous in their effects on simulation monitoring decisions.
+Although attractiveness did not seem to be the primary drive underlying
+simulation monitoring of face images, we do nonetheless report
+significant associations, with different patterns observed depending on
+the participant's gender. The quadratic relationship found for female
+participants is aligned with our hypothesis that salient faces (i.e.,
+rated as very attractive or very unattractive) are judged to be more
+real. The fact that this effect did not reach significance for beauty
+underlines that attractiveness judgement, and its role in simulation
+monitoring, is a multidimensional construct that cannot be reduced to
+physical facial attractiveness, in particular for women [@buunk2002age;
+@qi2022gender]. In fact, female participants were more confident in
+judging faces as fake only when they were rated very high or low on
+beauty, suggesting that physical beauty and attractiveness are not
+analogous in their effects on simulation monitoring decisions.
 
@@
 
-Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
-Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age].
-It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of attractive faces for men, rendering them significantly more salient than unattractive faces, and in turn distorting the relationship with simulation monitoring.
+Interestingly, we found a significant positive linear relationship in
+male participants for both attractiveness and beauty on simulation
+monitoring that we could interpret under an evolutionary lens.
+Specifically, males purportedly place more emphasis on facial
+attractiveness as a sign of reproductive potential, as compared with
+females, who tend to value characteristics signaling resource
+acquisition capabilities [@qi2022gender; @fink2006facial;
+@buunk2002age]. It is thus possible that the evolutionary weight
+associated with attractiveness skewed the perceived saliency of
+attractive faces for men, rendering them significantly more salient than
+unattractive faces, and in turn distorting the relationship with
+simulation monitoring.
 <!-- However, it is also possible that this pattern occurred due to the stimuli range, by which the stimuli did not include sufficiently unattractive faces for males to be , by which   -->
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers
-<!-- (e.g., heart rate deceleration) [@skora2022functional]. -->
-[e.g., heart rate deceleration, @skora2022functional].
+However, future studies should test this saliency-based hypothesis by
+measuring constructs closer to salience and its effects, for instance
+using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or
+physiological markers
+<!-- (e.g., heart rate deceleration) [@skora2022functional]. --> [e.g.,
+heart rate deceleration, @skora2022functional].
 
@@
 
-Our findings do not support the existence of a strong link between perceived trustworthiness and reality judgments.
-Given prior evidence that faces presented as computer-generated were rated less trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a linear association to be more clearly present.
-However, our results suggest a relationship with confidence ratings, especially for women, whereby faces judged with low and high trustworthiness are judged as real and fake with higher confidence.
-One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival].
-Future studies should clarify the role of trustworthiness both as a predictor and outcome of reality beliefs.
+Our findings do not support the existence of a strong link between
+perceived trustworthiness and reality judgments. Given prior evidence
+that faces presented as computer-generated were rated less trustworthy
+[@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such
+a linear association to be more clearly present. However, our results
+suggest a relationship with confidence ratings, especially for women,
+whereby faces judged with low and high trustworthiness are judged as
+real and fake with higher confidence. One of the underlying mechanisms
+that possibly contributed to this dimorphism could be the increased
+risk-taking aversion reported in females [explained evolutionarily as a
+compromise to their reproductive potential, @van2020sex], to which
+perceived facial trustworthiness relates [@hou2019survival]. Future
+studies should clarify the role of trustworthiness both as a predictor
+and outcome of reality beliefs.
 
@@
 
-Contrary to our hypothesis, we did not find familiarity to be significantly related to simulation monitoring decisions.
-Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-Although the familiarity measure was not a "recognition" measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females [@mishra2019gender; @lewin2002sex; @sommer2013sex], as well as an overconfidence in face recall for males [@bailey2021gender; @herbst2020gender].
-However, it should be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
+Contrary to our hypothesis, we did not find familiarity to be
+significantly related to simulation monitoring decisions. Interestingly,
+there were significant linear relationships between familiarity and
+confidence judgements for males only, where familiarity increased the
+confidence of reality beliefs. Although the familiarity measure was not
+a "recognition" measure, evidence from studies pertaining to the latter
+could be linked, reporting better face memory for females
+[@mishra2019gender; @lewin2002sex; @sommer2013sex], as well as an
+overconfidence in face recall for males [@bailey2021gender;
+@herbst2020gender]. However, it should be noted that the distribution of
+familiarity ratings was strongly skewed, and only a low number of
+pictures was rated as highly familiar. As such, future studies should
+clarify this point by experimentally manipulating familiarity, for
+instance by modulating the amount of exposure to items before querying
+the simulation monitoring judgements.
 
@@
 
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion [@levidi2022understanding; @weller2012honest] - to be related to a lower confidence in simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking were associated with a higher number of faces judged as real.
-This is in line with recent research which found people with higher narcissism scores less likely to engage in analytical reasoning strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social], and to be more vigilant and attentive to external stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
+Regarding the role of inter-individual characteristics in simulation
+monitoring tendencies, we found higher scores of honesty-humility - a
+trait related to an increased risk perception and aversion
+[@levidi2022understanding; @weller2012honest] - to be related to a lower
+confidence in simulation monitoring judgements. Notably, greater
+narcissistic tendencies in dimensions such as acclaim seeking were
+associated with a higher number of faces judged as real. This is in line
+with recent research which found people with higher narcissism scores
+less likely to engage in analytical reasoning strategies such as
+reflective thinking [@littrell2020overconfidently;
+@ahadzadeh2021social], and to be more vigilant and attentive to external
+stimuli [@carolan2017searching; @grapsas2020and; @eddy2021self].
 
-Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism [@hodson2018dark], we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making [@campbell2004narcissism; @chatterjee2017master; @brunell2017narcissism; @o2021grandiose].
-Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this relationship as related to a higher response assertiveness.
-Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
-Alternatively, participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
+Moreover, putting the significant positive links between narcissistic
+acclaim seeking and confidence judgements in perspective with the
+negative correlation between honesty-humility and narcissism
+[@hodson2018dark], we confirm previous evidence regarding the
+relationship between narcissistic grandiosity and over-confidence in
+decision-making [@campbell2004narcissism; @chatterjee2017master;
+@brunell2017narcissism; @o2021grandiose]. Although an inverse effect was
+found for the narcissistic facet of authoritativeness, we interpret this
+relationship as related to a higher response assertiveness. Taken
+together, these results suggest that participants with low humility and
+high recognition desires are more confident in their judgement regarding
+the real or fake nature of ambiguous stimuli. Alternatively,
+participants with opposite traits might perceive a higher risk in the
+decision-making process and its potential consequences (e.g., being seen
+as bad at the task at hand), resulting in more conservative confidence
+ratings.
 
@@
 
-Our findings suggest - though with low certainty - a potential positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat [@fornells2015people; @freeman2003can; @king2017paranoia], it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
-This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters [@freeman2005psychology].
+Our findings suggest - though with low certainty - a potential positive
+link between paranoid ideation and the tendency to believe that the
+stimuli were real. Given previous reports that people with higher levels
+of paranoia are more sensitive to cues of social threat
+[@fornells2015people; @freeman2003can; @king2017paranoia], it is
+plausible that paranoid traits confer greater saliency and emotionality
+to observed faces, hence increasing perceptions of its realness. This
+hypothesis, if confirmed by future studies, would be in line with
+previous findings that persecutory delusions are predicted by a greater
+sense of presence in VR environments populated with virtual characters
+[@freeman2005psychology].
 
@@
 
-Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
-Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
-Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
-This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions.
-In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@said2022artificial].
+Despite the ubiquity of AI, the literature pertaining to the influence
+of people's AI attitudes on simulation monitoring is scarce. Contrary to
+our expectations, we did not find evidence for the role of participants'
+expectations regarding the capabilities of AI technology (in terms of
+the realism of its productions). Instead, we found only one's enthusiasm
+about AI technology to be related to an increased confidence in
+simulation monitoring ratings. This could potentially be because
+participants with a highly positive attitude towards AI perceive
+themselves as having greater knowledge about AI and its capabilities
+[@said2022artificial], hence permitting themselves to be more confident
+in their simulation monitoring decisions. In fact, this result is in
+line with reports that AI attitudes interacts with people's perceived
+self-knowledge to influence their perception of the opportunities and
+risks accorded by AI applications [@said2022artificial].
 
@@
 
-On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display [@abraham2009reality; @gobbini2013prioritized; @taylor2009neural].
-Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness [@sperduti2016paradox; @makowski2017being].
-However, if that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
-Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
+On a methodological level, although the order of presentation of the
+facial images was randomized to reduce effects of adaptation,
+participants were more confident in their judgements for faces perceived
+as real following a shorter re-exposure delay. Such shorter durations
+could be associated with the faces being better remembered and appearing
+more familiar, thereby triggering self-referential and autobiographical
+memory processing during the repeated display [@abraham2009reality;
+@gobbini2013prioritized; @taylor2009neural]. Indeed, this finding is
+consistent with studies in which fictional stimuli that were associated
+with familiarity up-regulated emotions, biasing its salience and
+perceived realness [@sperduti2016paradox; @makowski2017being]. However,
+if that was the case, we would expect shorter re-exposure delays to
+impact the decision bias as well towards reality, rather than simply the
+confidence. Future studies should further investigate the modulatory
+effects of types and degrees of familiarity on perceived realness
+judgements.
 
@@
 
-Several limitations have to be noted.
-The current experimental paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements from influencing the other ratings).
-Although the effect of re-exposure delay was negligible, the potential bias induced by face familiarity (as compared to judging completely new items) cannot be discarded.
-Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
+Several limitations have to be noted. The current experimental paradigm
+required participants to judge the realness of faces they had prior
+exposure to (which was done to prevent reality judgements from
+influencing the other ratings). Although the effect of re-exposure delay
+was negligible, the potential bias induced by face familiarity (as
+compared to judging completely new items) cannot be discarded. Future
+studies could examine that by incorporating novel face images or
+increasing the duration of the re-exposure delay.
 
-Another issue is the impact on reality judgements of the prior explicit instruction that "about half of the faces were AI-generated and the other half real photos".
-Given this prior information given to participants, it might seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted, since it simply affirms participants followed the instructions.
-However, even if that was the case, the finding that our beliefs of reality can be so easily re-programmed with simple instructions and lead to high-confidence answers remains an interesting phenomenon.
-Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing them a description of the dataset.
-The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern: for instance, the first few items judged as real (the initial "true" belief of the participants), and a bias would progressively appear towards responding "fake" (as participants realize that all stimuli are of similar nature and that they have to "make up" for the prevalence of their "real" answers to fulfil the expected proportion of responses given the instructions).
+Another issue is the impact on reality judgements of the prior explicit
+instruction that "about half of the faces were AI-generated and the
+other half real photos". Given this prior information given to
+participants, it might seems like our enthusiasm pertaining to the
+finding that most people did indeed believe a high number of stimuli to
+be fake might be unwarranted, since it simply affirms participants
+followed the instructions. However, even if that was the case, the
+finding that our beliefs of reality can be so easily re-programmed with
+simple instructions and lead to high-confidence answers remains an
+interesting phenomenon. Moreover, it is to note that the paradigm did
+not instruct participants to balance their answers according to a
+certain distribution (e.g., 50-50), merely providing them a description
+of the dataset. The fact that no presentation order effect was found on
+reality beliefs suggests that participants did not try to actively
+distribute their responses to match the instructions, in which case we
+would have expected a different pattern: for instance, the first few
+items judged as real (the initial "true" belief of the participants),
+and a bias would progressively appear towards responding "fake" (as
+participants realize that all stimuli are of similar nature and that
+they have to "make up" for the prevalence of their "real" answers to
+fulfil the expected proportion of responses given the instructions).
 
-That said, the potential demand effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be able to mitigate such confounds to some extent.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (simply instructing them to discriminate real from fake without providing some background information regarding the context and defining what is meant by "fake" seems hardly feasible).
-That being the case, future studies should study the impact of these higher-order expectations on ratings [for instance, @tucciarelli2020 found that merely mentioning that some faces were AI generated decreased, on average, the trustworthiness ratings for all faces] as well as on the simulation monitoring process itself (i.e., the "criterion": would people form and distribute judgements differently).
-This can be studied by modulating this expectation in a controlled fashion (e.g., "most of the images *but a few* are real" vs.
-"most of the images *but a few* are fake") or inventing some implicit way of measuring reality belief that would not require the explicit introduction of the concept of fake vs.
-real to participants.
+That said, the potential demand effect of the instructions still exists,
+and a control condition without the cover story with AI-generated images
+would in-principle be able to mitigate such confounds to some extent.
+However, the distinction real/fake is hard to operationalize and
+introduce to participants in a vacuum (simply instructing them to
+discriminate real from fake without providing some background
+information regarding the context and defining what is meant by "fake"
+seems hardly feasible). That being the case, future studies should study
+the impact of these higher-order expectations on ratings [for instance,
+@tucciarelli2020 found that merely mentioning that some faces were AI
+generated decreased, on average, the trustworthiness ratings for all
+faces] as well as on the simulation monitoring process itself (i.e., the
+"criterion": would people form and distribute judgements differently).
+This can be studied by modulating this expectation in a controlled
+fashion (e.g., "most of the images *but a few* are real" vs. "most of
+the images *but a few* are fake") or inventing some implicit way of
+measuring reality belief that would not require the explicit
+introduction of the concept of fake vs. real to participants.
 
-Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial appraisals measured in the study were not the key determinants of simulation monitoring.
-Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
+Finally, it is important to note that although consistent in their
+directions across models and variables, the magnitude of the effects
+found in the study was relatively small, suggesting that the facial
+appraisals measured in the study were not the key determinants of
+simulation monitoring. Hence, beyond exploring new potential mechanisms,
+future studies should include a more thorough debriefing to try to
+capture what conscious strategies (if any) the participants used (e.g.,
+focusing on some features of the stimulus - like hair or eyes in the
+case of faces) to guide their reality beliefs.
 
@@
 
-In summary, the aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
-Notably, we found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
-We also found that inter-individual traits, such as narcissistic acclaim-seeking, honesty-humility, and paranoid ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-We believe that these findings provide the foundations to help us understand what drives reality beliefs in an increasingly reality-ambiguous world.
+In summary, the aim of the present study was to examine whether a subset
+of specific characteristics, in particular face attractiveness,
+significantly influences our simulation monitoring decisions. Notably,
+we found faces rated as attractive to be perceived as more real, with a
+possible sexual dimorphism affecting the shape of the relationship. We
+also found that inter-individual traits, such as narcissistic
+acclaim-seeking, honesty-humility, and paranoid ideation, were related
+to a systematic bias towards beliefs that the stimuli were real or fake.
+We believe that these findings provide the foundations to help us
+understand what drives reality beliefs in an increasingly
+reality-ambiguous world.
 
@@
 
-The datasets generated and/or analysed during the current study are available in the GitHub repository 
+The datasets generated and/or analysed during the current study are
+available in the GitHub repository
 https://github.com/RealityBending/FakeFace

### 2024-10-22 analysis.Rmd
changes made to new_manuscript

@@
 ```{r message=FALSE, warning=FALSE, cache=cache, fig.width=20, fig.height=20}
+
 p_att <- dfsub |>
   select(Participant, starts_with("Att")) |>
-  pivot_longer(-Participant) |>
+  tidyr::pivot_longer(-Participant) |>
   # mutate(name = str_remove(name, "Cor_")) |>
-  ggplot(aes(x = Participant, y = value)) +
+  ggplot2::ggplot(aes(x = Participant, y = value)) +
   geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
   scale_y_continuous(expand = c(0, 0)) +
-  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
-  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7")) +
+  scale_fill_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7", "#843c54","#03989e", "#588163")) +
+  scale_color_manual(values = c("black", "#2196F3", "#3F51B5", "#673AB7","#843c54","#03989e", "#588163")) +
   see::theme_modern() +
@@
   filter(!Participant %in% c(outliers))
+
 ```

### 2024-10-22 submission/new_manuscript/manuscript.qmd
changes made to new_manuscript

@@
 Advancements in technology have now made it possible to create
-near-perfect simulations that are indistinguishable from reality. These
-simulations are more affordable, faster to produce, and more accessible
-than at any other time in human history. These artificial, yet realistic
-constructs permeate all areas of life through immersive works of
-fiction, deep fakes (real-like images and videos generated by deep
-learning algorithms), virtual and augmented reality (VR and AR),
-artificial beings (artificial intelligence "bots" with or without a
-physical form), fake news and skewed narratives, of which ground truth
-is often hard to access [@nightingale2022]. Such developments not only
-carry important consequences for the technological and entertainment
-sectors, but also for security and politics - for instance if used for
-propaganda and disinformation, recruitment into malevolent
-organizations, or religious indoctrination [@pantserev2020]. This issue
-is central to what has been coined the "post-truth era"
+near-perfect simulations that are indistinguishable from reality with an
+ease, affordability and accessibility that are unprecedented in Human
+history.These artificial, yet realistic constructs permeate all areas of
+life through immersive works of fiction, deep fakes (real-like images
+and videos generated by deep learning algorithms), virtual and augmented
+reality (VR and AR), artificial beings (artificial intelligence "bots"
+with or without a physical form), fake news and skewed narratives, of
+which ground truth is often hard to access [@nightingale2022]. Such
+developments not only carry important consequences for the technological
+and entertainment sectors, but also for security and politics - for
+instance if used for propaganda and disinformation, recruitment into
+malevolent organizations, or religious indoctrination [@pantserev2020].
+This issue is central to what has been coined the "post-truth era"
 [@lewandowsky2017beyond], in which the distinction (and lack thereof)
@@
 
-Literature shows that the context surrounding a stimulus often plays an
+Literature shows that the context surrounding a stimulfus often plays an
 important role in the assessment of its reality [a process henceforth
@@
 beliefs that an image is real or artificially generated. Based on the
-*affective reality theory* [@makowski2023affective], which suggests that
-salient and emotional stimuli are perceived to be more real (up to a
-point of reversal after which beliefs of fiction becomes used an emotion
-regulation strategy), we hypothesize a quadratic relationship between
-perceived realness and attractiveness: faces rated as highly attractive
-or unattractive will more likely be believed to be real. We expect a
-similar relationship with trustworthiness ratings given its
-well-established link with attractiveness [@liefooghe2022faces;
-@bartosik2021you; @garrido2017kdef; @little2011facial], and a positive
-relationship with familiarity (as more familiar faces would appear as
-more salient, self-relevant and anchored in reality). Additionally, we
-will further explore the link shared by dispositional traits, such as
-personality and attitude towards AI, with simulation monitoring
-tendencies. Importantly, this study does investigate the discriminative
-accuracy between "true" photos and "true" artificially-generated images
-(which we consider more a technological issue than a psychological one),
-focusing on the beliefs that a stimulus is real or fake, independently
-of its true nature.
+*affective reality theory* [@makowski2023affective;
+@makowski2018cognitive], which suggests that salient and emotional
+stimuli are perceived to be more real (up to a point of reversal after
+which beliefs of fiction becomes used an emotion regulation strategy),
+we hypothesize a quadratic relationship between perceived realness and
+attractiveness: faces rated as highly attractive or unattractive will
+more likely be believed to be real. We expect a similar relationship
+with trustworthiness ratings given its well-established link with
+attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef;
+@little2011facial], and a positive relationship with familiarity (as
+more familiar faces would appear as more salient, self-relevant and
+anchored in reality). Additionally, we will further explore the link
+shared by dispositional traits, such as personality and attitude towards
+AI, with simulation monitoring tendencies. Importantly, this study does
+investigate the discriminative accuracy between "true" photos and "true"
+artificially-generated images (which we consider more a technological
+issue than a psychological one), focusing on the beliefs that a stimulus
+is real or fake, independently of its true. **In other words, the
+present study investigates the psychological process that leads to
+different *beliefs* of reality, rather than the discrimination between
+real faces and actual AI-generated ones, which largely depends on the
+technological quality of the AI-generation process.**
 
@@
 
-All the material (preregistration, experiment demo, experiment code, raw
+All the material (preregistration ***[FOOTNOTE: This approach diverges from the preregistration in several key ways.
+First, the phrasing of items was modified from "Assuming the face you saw was of a real individual, how..." to "I find this person..." A new attractiveness scale (i.e., Beauty) was introduced to capture a more objective measure of attraction.
+Finally, the data analysis method was altered from Bayesian Mixed Models due to computational limitations, as we were unable to run these models on a high-performance cluster.]***, experiment demo, experiment code, raw
 data, analysis script with complementary figures and analyses, etc.) is
@@
 average", @spielmann2020predictive]. 3 attention check questions were
-also embedded in the surveys.
+also embedded in the surveys. **All Cronbach's alpha values were within
+the acceptable to excellent range, except for the neuroticism subscale
+of the Mini-IPIP6 and the negative subscale of the GAAI, which were
+poor, and the Expectations about AI scale, which was questionable (Gliem
+& Gliem, 2003; see supplementary material for the details of the
+reliability analysis).**
 
@@
 attention check questions, took an implausibly short time to finish the
-questionnaires or had incomplete responses. The final sample included
-145 participants (Mean age = 28.3, SD = 9.0, range: \[19, 66\]; Sex:
-48.3% females, 51.0% males, 0.7% others).
+questionnaires or had incomplete responses. Out of the 5 participants
+excluded, 2 Participants were excluded because they failed 2 out of 3
+attention checks, 1 because they did not answer the sexual orientation
+question, which made further analysis impossible, and 2 had an abnormal
+low agreement (r \< 0.1) between the beauty and the attractiveness
+ratings (possibly indicating random responses as these two scales
+exhibited a higher correlation for the other participants).The final
+sample included 145 participants (Mean age = 28.3, SD = 9.0, range:
+\[19, 66\]; Sex:48.3% females, 51.0% males, 0.7% others).
 
@@
 regressions (suited for outcome variables expressed in percentages). The
-models included the participants and stimuli as random factors.
+models included the participants and stimuli as random **intercepts with
+no nested variables**.
 
@@
 gender or sexual orientation) for each questionnaire, with all of the
-subscales as orthogonal predictors.
+subscales as orthogonal predictors. \
 
@@
 influencing the other ratings). Although the effect of re-exposure delay
-was negligible, the potential bias induced by face familiarity (as
-compared to judging completely new items) cannot be discarded. Future
-studies could examine that by incorporating novel face images or
-increasing the duration of the re-exposure delay.
+was negligible, the potential bias induced by face familiarity, that is
+by re-presenting the same face stimuli twice, as compared to judging
+completely new items, cannot be discarded. Future studies could examine
+that by incorporating novel face images or increasing the duration of
+the re-exposure delay.
 
@@
 case of faces) to guide their reality beliefs.
+**Additionally, the role of specific facial features, like perceived dominance, warmth or gender, would be an interesting avenue to explore in future studies, in particular with paradigms directly manipulating these dimensions (for instance using AI to generate faces of different characteristics).**
 

### 2024-10-22 submission/new_manuscript/manuscript.tex
changes made to new_manuscript

--- 2023-10-10 submission/manuscript.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
 \documentclass[
-  man,floatsintext]{apa6}
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
+  man,
+  floatsintext,
+  longtable,
+  nolmodern,
+  notxfonts,
+  notimes,
+  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\usepackage[bidi=default]{babel}
+\babelprovide[main,import]{english}
+
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+
+\RequirePackage{longtable}
+% \setlength\LTleft{0pt}
+\RequirePackage{threeparttablex}
+
+% %
+
 \makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+	{-.5em}%
+	{\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
+	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+	{-\z@\relax}%
+	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
 \makeatother
-\usepackage{xcolor}
+
+\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float}
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.15}
+\renewcommand{\floatpagefraction}{0.7}
+
+\usepackage{tcolorbox}
+\tcbuselibrary{listings,theorems, breakable, skins}
+\usepackage{fontawesome5}
+
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
+\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}
+
+\newlength\Oldarrayrulewidth
+\newlength\Oldtabcolsep
+
+\usepackage{hyperref}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+
 \usepackage{graphicx}
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+
+\usepackage[nolongtablepatch]{lineno}
+\linenumbers
+
+\usepackage{newtx}
+
+\defaultfontfeatures{Scale=MatchLowercase}
+\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+
+\title{Too Beautiful to be Fake: Attractive Faces are Less Likely to be
+Judged as Artificially Generated}
+\shorttitle{Attractiveness and Reality}
+
+\usepackage{etoolbox}
+
+\authorsnames[{1},{2},{2},{2},{3},{1,4,5,6}]{Dominique Makowski,An Shu
+Te,Stephanie Kirk,Ngoi Zi Liang,Panagiotis Mavros,S.H. Annabel Chen}
+
+\authorsaffiliations{
+{School of Psychology, University of Sussex},{School of Social
+Sciences, Nanyang Technological University},{Department of Economics and
+Social Sciences, Télécom Paris},{LKC Medicine, Nanyang Technological
+University},{National Institute of Education},{Centre for Research and
+Development in Learning, Nanyang Technological University}}
+
+\leftheader{Makowski, Te, Kirk, Liang, Mavros and Chen}
+
+\abstract{Technological advances render the distinction between
+artificial (e.g., computer-generated faces) and real stimuli
+increasingly difficult, yet the factors driving our beliefs regarding
+the nature of ambiguous stimuli remain largely unknown. In this study,
+150 participants rated 109 pictures of faces on 4 characteristics
+(attractiveness, beauty, trustworthiness, familiarity). The stimuli were
+then presented again with the new information that some of them were
+AI-generated, and participants had to rate each image according to
+whether they believed them to be real or fake. Despite all images being
+pictures of real faces from the same database, most participants did
+indeed rate a large portion of them as `fake' (often with high
+confidence), with strong intra- and inter-individual variability. Our
+results suggest a gender-dependent role of attractiveness on reality
+judgements, with faces rated as more attractive being classified as more
+real. We also report links between reality beliefs tendencies and
+dispositional traits such as narcissism and paranoid ideation.}
+% 
+\keywords{attractiveness, AI-generated images, fiction, fake news, sense
+of reality}
+
+\authornote{\par{\addORCIDlink{Dominique
+Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
+Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Stephanie
+Kirk}{0000-0002-9312-5552}}\par{\addORCIDlink{Panagiotis
+Mavros}{0000-0002-1540-5516}}
+\par{ }
+\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
+Makowski:   Conceptualization, Data curation, Formal Analysis, Funding
+acquisition, Investigation, Methodology, Project
+administration, Resources, Software, Supervision, Validation, Visualization, Writing
+-- original draft; An Shu Te:   Project
+administration, Resources, Writing -- original draft; Stephanie
+Kirk:   Project administration, Resources, Writing -- original
+draft; Ngoi Zi Liang:   Project administration, Resources, Writing --
+review \& editing; Panagiotis Mavros:   Supervision, Writing -- review
+\& editing; S.H. Annabel Chen:   Project
+administration, Supervision, Writing -- review \& editing}
+\par{Correspondence concerning this article should be addressed
+to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
+}
+
 \makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
+\let\endoldlt\endlongtable
+\def\endlongtable{
+\hline
+\endoldlt
+}
+\makeatother
+
+\urlstyle{same}
+
+% From https://tex.stackexchange.com/a/645996/211326
+%%% apa7 doesn't want to add appendix section titles in the toc
+%%% let's make it do it
 \makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\xpatchcmd{\appendix}
+  {\par}
+  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
+  {}{}
 \makeatother
 
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
+\begin{document}
+
+\maketitle
+
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+
+\setlength\LTleft{0pt}
+
+\resetlinenumber[1]
+
+Advancements in technology have now made it possible to create
+near-perfect simulations that are indistinguishable from reality with an
+ease, affordability and accessibility that are unprecedented in Human
+history.These artificial, yet realistic constructs permeate all areas of
+life through immersive works of fiction, deep fakes (real-like images
+and videos generated by deep learning algorithms), virtual and augmented
+reality (VR and AR), artificial beings (artificial intelligence ``bots''
+with or without a physical form), fake news and skewed narratives, of
+which ground truth is often hard to access (Nightingale \& Farid, 2022).
+Such developments not only carry important consequences for the
+technological and entertainment sectors, but also for security and
+politics - for instance if used for propaganda and disinformation,
+recruitment into malevolent organizations, or religious indoctrination
+(Pantserev, 2020). This issue is central to what has been coined the
+``post-truth era'' (Lewandowsky et al., 2017), in which the distinction
+(and lack thereof) between authentic and simulated objects will play a
+critical role.
+
+While not all simulations have achieved perfect realism, such as
+Computer Generated Images (CGI) in movies or via recent algorithms such
+as GANs or diffusion model, which often include distortions or lack
+certain key details distinguishing them from real images (Corvi et al.,
+2022; McDonnell \& Breidt, 2010), it is fair to assume that these
+technical limitations will become negligible in the near future. This is
+particularly true in the field of face generation, where face-generation
+algorithms are already able to create stimuli that are virtually
+indistinguishable from real photos (Moshel et al., 2022; Nightingale \&
+Farid, 2022; Tucciarelli et al., 2020). Such a technological feat,
+however, leads to a new question: if real and fake stimuli cannot be
+differentiated based on their objective ``physical'' characteristics,
+how can we form judgements regarding their nature?
+
+Literature shows that the context surrounding a stimulfus often plays an
+important role in the assessment of its reality (a process henceforth
+referred to as \emph{simulation monitoring}, Makowski, 2018; Makowski,
+Sperduti, et al., 2019). With the extensive search and processing of
+cues within ambiguous stimuli being an increasingly complex and
+cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al.,
+2021), people tend to draw on peripheral contextual cues (\textbf{Figure
+1}), such as the source of the stimulus (e.g., which journal was the
+information published in), and its credibility, authority and expertise,
+to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \&
+Cacioppo, 1986; Susmann et al., 2021). However, the atomization and
+decontextualization of information allowed by online social media (where
+text snippets or video excerpts are often mass-shared with little
+context) makes this task progressively difficult (Berghel, 2018; Y. Chen
+et al., 2015). Thus, in the absence of clear contextual information,
+what drives our beliefs of reality?
+
+\begin{figure}[H]
+
+\caption{Figure 1. The decision to believe that an ambiguous stimulus
+(of any form, e.g., images, text, videos, environments, \ldots) is real
+or fake depends of individual characteristics (e.g., personality and
+cognitive styles), stimulus-related features (context, emotionality),
+and their interaction, which can manifest for instance in our bodily
+reaction.}
+
+{\centering \includegraphics[width=1\textwidth,height=\textheight]{../../figures/figure1.png}
+
 }
-{}{\PatchFailed}
-\keywords{attractiveness, AI-generated images, fiction, fake news, sense of reality\newline\indent Word count: 5242}
-\usepackage{lineno}
-
-\linenumbers
-\usepackage{csquotes}
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{figure}
-\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
-\renewcommand{\cftfigaftersnum}{.\space}
-\setlength{\cftfigindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cftfignumwidth}{Figure 10.\qquad}
-\usepackage[labelfont=bf, font={scriptsize, color=gray}]{caption}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated},
-  pdfauthor={Dominique Makowski1, An Shu Te2, Stephanie Kirk2, Ngoi Zi Liang2, Panagiotis Mavros3, \& S.H. Annabel Chen2, 4, 5, 6},
-  pdflang={en-EN},
-  pdfkeywords={attractiveness, AI-generated images, fiction, fake news, sense of reality},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-
-\title{\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}}
-\author{Dominique Makowski\textsuperscript{1}, An Shu Te\textsuperscript{2}, Stephanie Kirk\textsuperscript{2}, Ngoi Zi Liang\textsuperscript{2}, Panagiotis Mavros\textsuperscript{3}, \& S.H.
-Annabel Chen\textsuperscript{2, 4, 5, 6}}
-\date{}
-
-\shorttitle{Attractiveness and Reality}
-
-\authornote{
-
-Correspondence concerning this article should be addressed to Dominique Makowski (\href{mailto:D.Makowski@sussex.ac.uk}{\nolinkurl{D.Makowski@sussex.ac.uk}}).
-
-The authors made the following contributions.
-Dominique Makowski: Conceptualization, Data curation, Formal Analysis, Funding acquisition, Investigation, Methodology, Project administration, Resources, Software, Supervision, Validation, Visualization, Writing -- original draft; An Shu Te: Data curation, Project administration, Resources, Investigation, Writing -- original draft; Stephanie Kirk: Project administration, Resources, Writing -- original draft; Ngoi Zi Liang: Project administration, Resources, Writing -- review \& editing; Panagiotis Mavros: Supervision, Writing -- review \& editing; S.H.
-Annabel Chen: Project administration, Supervision, Writing -- review \& editing.
-
-Correspondence concerning this article should be addressed to Dominique Makowski, School of Psychology, University of Sussex, Brighton.
-E-mail: \href{mailto:D.Makowski@sussex.ac.uk}{\nolinkurl{D.Makowski@sussex.ac.uk}}
+
+\end{figure}%
+
+Evidence suggests that inter-individual characteristics play a crucial
+role in simulation monitoring, with factors such as cognitive style,
+prior beliefs, and personality traits (Bryanov \& Vziatysheva, 2021;
+Ecker et al., 2022; Sindermann et al., 2020). For instance, individuals
+with stronger analytical reasoning skills have been found to better
+discriminate real from fake stimuli (Pehlivanoglu et al., 2021;
+Pennycook \& Rand, 2019), and prior knowledge or beliefs about the
+stimulus influences one's perception of it by biasing the attention
+deployment towards information that is in line with one's expectations
+(Britt et al., 2019). Furthermore, dispositional traits, such as high
+levels of narcissism and low levels of openness and conscientiousness,
+have been associated with greater susceptibility to fake news (Piksa et
+al., 2022; Sindermann et al., 2020). \textbf{Interestingly, a recent
+review suggested that narcissism was related to a strong self-perceived
+ability at detecting lies (Turi et al., 2022), which could translate to
+participants scoring high on narcissism providing more clear cut and
+confidence responses. Conversely, those high in honesty-humility tend to
+be more conservative in their judgments to ensure fairness (Liu et al.,
+2020), likely resulting in lower confidence ratings.}
+
+Beyond stimulus- and individual-related characteristics, evidence
+suggests that the interaction between the two (i.e., the subjective
+reaction associated with the experience of a given stimulus),
+contributes to simulation monitoring decisions. For instance, the
+intensity of experienced emotions have been shown to increase one's
+sense of presence - the extent to which one feels like ``being there'',
+as if the object of experience was real - when engaged in a fictional
+movie or a VR environment (Makowski et al., 2017; Sanchez-Vives \&
+Slater, 2005). Indeed, participants' self-reported emotional arousal
+were found to significantly predict the probability that they would
+perceive images as real (Azevedo et al., 2020). Conversely, beliefs that
+emotional stimuli were fake (e.g., that emotional scenes were not
+authentic but instead involved actors and movie makeup) were found to
+result in emotion down-regulation (Makowski, Sperduti, et al., 2019;
+Sperduti et al., 2017). In line with these findings, studies on
+susceptibility to fake news have also found heightened stimulus
+emotionality to be associated with greater belief (Bago et al., 2022;
+Martel et al., 2020), and higher neurophysiological arousal was
+predictive of judging realistic images as real (Azevedo et al., 2020).
+Additionally, other factors, such as the stimuli's perceived
+self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as
+familiarity (Begg et al., 1992), could also play a role in guiding our
+appraisal of a stimulus.\textbf{For instance,} Miller et al. (2023)
+\textbf{reported that participants were more likely to mistakenly
+identify AI-generated faces as real because they perceived them as more
+familiar.}
+
+Due to their popularity as a target of CGI technology and the prospect
+offered with facial features that can be experimentally manipulated,
+AI-generated images of faces are increasingly used to study face
+processing (Dawel et al., 2021), in particular in relationship with
+saliency or emotions, as well as to other important components of face
+evaluation, such as trustworthiness or attractiveness (Balas \& Pacella,
+2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et
+al., 2019). Interestingly, artificially created faces rated as more
+attractive (by an independent group of raters) were perceived as less
+real (Tucciarelli et al., 2020). Conversely, Liefooghe et al. (2022)
+reports that attractiveness ratings were significantly lower when
+participants who were told that the faces were AI-generated were
+compared to those who had no prior knowledge. \textbf{Similarly, when
+participants are informed that faces are AI-generated, the perceived
+artificiality leads to lower trust ratings (Wang \& Nishida, 2024), even
+when they are real faces (Liefooghe et al., 2022). In contrast, when
+participants are unaware that the faces are AI-generated, trust ratings
+for these synthetic faces tend to increase (Nightingale \& Farid,
+2022)}. Whereas this line of evidence suggests that reality beliefs have
+an effect on face attractiveness and \textbf{trustworthiness} ratings,
+the opposite question - whether attractiveness \textbf{and
+trustworthiness contribute} to the formation of reality beliefs - has
+received little attention to date.
+
+AI-generated content, in particular realistic images, is becoming
+commonplace and carries important risks for misinformation and
+black-mailing (Viola \& Voto, 2023), emphasizing the need to understand
+the different components that come into play in the formation of reality
+beliefs. This exploratory study primarily aims at investigating the
+effect of facial attractiveness on simulation monitoring, i.e., on the
+beliefs that an image is real or artificially generated. Based on the
+\emph{affective reality theory} (Makowski, 2018, 2023), which suggests
+that salient and emotional stimuli are perceived to be more real (up to
+a point of reversal after which beliefs of fiction becomes used an
+emotion regulation strategy), we hypothesize a quadratic relationship
+between perceived realness and attractiveness: faces rated as highly
+attractive or unattractive will more likely be believed to be real. We
+expect a similar relationship with trustworthiness ratings given its
+well-established link with attractiveness (Bartosik et al., 2021;
+Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011),
+and a positive relationship with familiarity (as more familiar faces
+would appear as more salient, self-relevant and anchored in reality).
+Additionally, we will further explore the link shared by dispositional
+traits, such as personality and attitude towards AI, with simulation
+monitoring tendencies. Importantly, this study does investigate the
+discriminative accuracy between ``true'' photos and ``true''
+artificially-generated images (which we consider more a technological
+issue than a psychological one), focusing on the beliefs that a stimulus
+is real or fake, independently of its true. \textbf{In other words, the
+present study investigates the psychological process that leads to
+different \emph{beliefs} of reality, rather than the discrimination
+between real faces and actual AI-generated ones, which largely depends
+on the technological quality of the AI-generation process.}
+
+\subsection{Methods}\label{methods}
+
+All the material (preregistration \textbf{\emph{{[}FOOTNOTE: This
+approach diverges from the preregistration in several key ways. First,
+the phrasing of items was modified from ``Assuming the face you saw was
+of a real individual, how\ldots{}'' to ``I find this person\ldots{}'' A
+new attractiveness scale (i.e., Beauty) was introduced to capture a more
+objective measure of attraction. Finally, the data analysis method was
+altered from Bayesian Mixed Models due to computational limitations, as
+we were unable to run these models on a high-performance cluster.{]}}},
+experiment demo, experiment code, raw data, analysis script with
+complementary figures and analyses, etc.) is available at
+\href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
+
+\textbf{Ethics Statement.} This study was approved by the NTU
+Institutional Review Board (NTU IRB-2022-187) and all procedures
+performed were in accordance with the ethical standards of the
+institutional board and with the 1964 Helsinki Declaration. All
+participants provided their informed consent prior to participation and
+were incentivized after completing the study.
+
+\textbf{Procedure.} In the first part of the study, participants
+answered a series of personality questionnaires presented in the order
+below. These include the \emph{Mini-IPIP6} (24 items, Sibley et al.,
+2011) measuring 6 personality traits, the \emph{SIAS-6} and the
+\emph{SPS-6} (6 items each, Peters et al., 2012) assessing social
+anxiety levels, 5 items we devised pertaining to expectations about
+AI-generated image technology (``I think current Artificial Intelligence
+algorithms can generate very realistic images''), \textbf{to potentially
+test and mitigate the potential effect of expectations/beliefs about
+AI.} \textbf{These items were} mixed with 5 items from the general
+attitudes towards AI scale to lower the former's saliency and the
+possibility of it priming the subjects about the task, (\emph{GAAIS},
+Schepman \& Rodway, 2020) the \emph{FFNI-BF} (30 items, Jauk et al.,
+2022) measuring 9 facets of narcissism; the \emph{R-GPTS} (18 items,
+Freeman et al., 2021) measuring 2 dimensions related to paranoid
+thinking; and the \emph{IUS-12} (12 items, Carleton et al., 2007)
+measuring intolerance to uncertainty. Self-rated attractiveness was also
+assessed using 2 items - one measuring general attractiveness (``How
+attractive would you say you are?'' Marcinkowska et al., 2021) and the
+other measuring physical attractiveness (``How would you rate your own
+physical attractiveness relative to the average,'' Spielmann et al.,
+2020). 3 attention check questions were also embedded in the surveys.
+\textbf{All Cronbach's alpha values were within the acceptable to
+excellent range, except for the neuroticism subscale of the Mini-IPIP6
+and the negative subscale of the GAAI, which were poor, and the
+Expectations about AI scale, which was questionable (Gliem \& Gliem,
+2003; see supplementary material for the details of the reliability
+analysis).}
+
+In the second part of this study, images of neutral-expression faces
+from the validated American Multiracial Face Database (AMFD, J. M. Chen
+et al., 2021) were presented to the participants for 500ms each, in a
+randomized order, following a fixation cross display (750 ms).
+T\textbf{he decision to present the faces for 500 ms was based on pilot
+studies, which demonstrated that this duration provides a sufficient
+perceptual window for decision-making and aligns with previous research
+indicating stable judgment levels and increased confidence beyond this
+exposure time (Willis \& Todorov, 2006).}
+
+\textbf{The AMFD is a recently validated database including a set of 110
+pictures of homogeneous quality featuring diverse faces (particularly in
+terms of ethnicity), each (except one) posing with either a neutral or
+smiling expression. We selected all 109 neutral images (89 women and 20
+men) to reduce the influence of confounding factors like affect. The
+AMFD primarily features racially ambiguous faces, representing multiple
+racial categories such as multiracial, Latinx, and white. The database
+includes 81 faces from individuals self-reporting two racial backgrounds
+and 29 from those with three or more racial backgrounds: 33\%
+Asian/White, 22\% Latinx/White, 11\% Asian/Latinx, 6\% White/Middle
+Eastern, 5\% Black/White, and 5\% Asian/Middle Eastern, with about 18\%
+identifying as other racial backgrounds.}
+
+After each stimulus presentation, ratings of \emph{Trustworthiness} (``I
+find this person trustworthy'') and \emph{Familiarity} (``This person
+reminds me of someone I know'') were collected using visual analog
+scales. Notably, as facial attractiveness is a multidimensional
+construct, encompassing evolutionary, sociocultural, biological as well
+as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we
+assessed attractiveness using 2 visual analog scales, measuring general
+\emph{Attractiveness} (``I find this person attractive'') and physical
+\emph{Beauty} (``This face is good-looking''). \textbf{This dual-scale
+approach aims to reflect two conceptually distinct dimensions:
+Attractiveness might capture personal, Self-relevant and subjective
+appeal, whereas Beauty might be related to a more ``objective'' decision
+based on aesthetic criteria that can be recognized independently of
+personal attraction. In other words, we wanted the experiment to be able
+to potentially capture scenarios where a face could be judged beautiful
+yet not, attractive and vice versa.}
+
+In the last part of the study, participants were informed that ``about
+half'' of the images previously seen were AI-generated (the instructions
+used a cover story explaining that the aim of the research was to
+validate a new face generation algorithm). The same set of stimuli was
+displayed again for 500 ms in a new randomized order. This time, after
+each display, participants were asked to express their belief regarding
+the nature of the stimulus using a visual analog scale (with \emph{Fake}
+and \emph{Real} as the two extremes). The study was implemented using
+\emph{jsPsych} (De Leeuw, 2015), and the exact instructions are
+available in the experiment code.
+
+\textbf{Participants.} Although the main part of the study relied on
+within-subject design (with 109 trials per participant), we also planned
+to do between-participants analyses, thus aiming at collecting a larger
+sample than traditionally used in experimental psychology (with budget
+availability as the main constraint). One hundred and fifty participants
+were recruited via \emph{Prolific}, a crowd-sourcing platform recognized
+for providing high quality data {[}Peer et al. (2022);
+douglas2023data{]}. The only inclusion criterion was a fluent
+proficiency in English to ensure that the experiment instructions would
+be well-understood. Participants were incentivised with a reward of
+about \textsterling 7.5 for completing the study, which took about 45
+minutes to finish. Demographic variables (age, gender, sexual
+orientation, education and ethnicity) were self-reported on a voluntary
+basis.
+
+We excluded 5 participants that either failed 2 (\textgreater= 66.6\%)
+or more attention check questions, took an implausibly short time to
+finish the questionnaires or had incomplete responses. Out of the 5
+participants excluded, 2 Participants were excluded because they failed
+2 out of 3 attention checks, 1 because they did not answer the sexual
+orientation question, which made further analysis impossible, and 2 had
+an abnormal low agreement (r \textless{} 0.1) between the beauty and the
+attractiveness ratings (possibly indicating random responses as these
+two scales exhibited a higher correlation for the other
+participants).The final sample included 145 participants (Mean age =
+28.3, SD = 9.0, range: {[}19, 66{]}; Sex:48.3\% females, 51.0\% males,
+0.7\% others).
+
+\textbf{Data Analysis.} The real-fake ratings (measured originally with
+a {[}-1, 1{]} analog scale) were converted into two scores,
+corresponding to two conceptually distinct mechanisms: the dichotomous
+\emph{belief} (real or fake, based on the sign of the rating) and the
+\emph{confidence} (the rating's absolute value) associated with that
+belief. The former was analyzed using logistic mixed models, which
+modelled the probability of assigning a face to the real (\textgreater=
+0) as opposed to fake (\textless{} 0). The latter, as well as the other
+face ratings (attractiveness, beauty, trustworthiness and familiarity),
+was modelled using mixed beta regressions (suited for outcome variables
+expressed in percentages). The models included the participants and
+stimuli as random \textbf{intercepts with no nested variables}.
+
+We started by investigating the effect of the procedure and instructions
+to check whether the stimuli (which were all images of real faces) were
+judged as fake in sufficient proportion to warrant their analysis.
+Additionally, we assessed the effect of the re-exposure delay, i.e., the
+time between the first presentation of the image (corresponding to the
+face ratings) and the second presentation (for the real-fake rating), as
+well as that of the presentation order to check whether for habituation
+or learning effects.
+
+The determinants of reality beliefs were modelled separately for
+attractiveness, beauty, trustworthiness, and familiarity, using second
+order raw polynomials coefficients to allow for possible quadratic
+relationships (\textbf{Figure 2}). Aside from attractiveness
+(conceptualized as a general construct), models for beauty,
+trustworthiness and familiarity were adjusted for the the two remaining
+variables \emph{mutatis mutandis}. The analysis focused on
+sexual-orientation relevant stimuli, i.e., on faces that were aligned
+with respect to the participants' sexual orientation (i.e., female faces
+for heterosexual males, male faces for homosexual males, etc.), and the
+models included the interaction with the participants' gender (as a
+sexual dimorphism has been reported in face appraisal processes). For
+the attractiveness and beauty models, we then added the interaction with
+the reported self-attractiveness (the average of the two questions
+pertaining to it) to investigate its potential modulatory effect.
+Finally, we investigated the inter-individual correlates of simulation
+monitoring with similar models (but this time, for all items regardless
+of the participant's gender or sexual orientation) for each
+questionnaire, with all of the subscales as orthogonal predictors.\\
+
+\begin{figure}[H]
+
+\caption{Figure 2. Top part shows the efffect of face ratings on 1) the
+probability of judging a face as real vs.~fake (solid line) and 2) on
+the confidence associated with that judgement (dashed lines) depending
+on the sex. Bottom part shows the effect of personality traits on the
+belief (black line) and the confidence associated with it (colored
+lines). The points are the average per participant confidence for both
+types of judgements. Stars indicate significance (p \textless{}
+.001\emph{\textbf{, p \textless{} .01}, p \textless{} .05}).}
+
+{\centering \includegraphics[width=1\textwidth,height=\textheight]{../../figures/Figure2.png}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} School of Psychology, University of Sussex, UK\\\textsuperscript{2} School of Social Sciences, Nanyang Technological University, Singapore\\\textsuperscript{3} Department of Economics and Social Sciences, Télécom Paris, France\\\textsuperscript{4} LKC Medicine, Nanyang Technological University, Singapore\\\textsuperscript{5} National Institute of Education, Singapore\\\textsuperscript{6} Centre for Research and Development in Learning, Nanyang Technological University, Singapore}
-
-\abstract{%
-Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown.
-In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity).
-The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake.
-Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as ``fake'' (often with high confidence), with strong intra- and inter-individual variability.
-Our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real.
-We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation.
-}
-
-\begin{document}
-\maketitle
-
-For the first time in human history, technology has enabled the creation of near-perfect simulations indistinguishable from reality.
-These artificial, yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality (VR and AR), artificial beings (artificial intelligence ``bots'' with or without a physical form), fake news and skewed narratives, of which ground truth is often hard to access (Nightingale \& Farid, 2022).
-Such developments not only carry important consequences for the technological and entertainment sectors, but also for security and politics - for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination (Pantserev, 2020).
-This issue is central to what has been coined the ``post-truth era'' (Lewandowsky et al., 2017), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.
-
-While not all simulations have achieved perfect realism (Corvi et al., 2022; e.g., Computer Generated Images - CGI in movies or via recent algorithms such as GANs or diffusion models often include distortions or lack certain key details that makes them visually distinct from real images, McDonnell \& Breidt, 2010), it is fair to assume that these technical limitations will become negligible in the near future.
-This is particularly true in the field of face generation, where face-generation algorithms are already able to create stimuli that are virtually indistinguishable from real photos (Moshel et al., 2022; Nightingale \& Farid, 2022; Tucciarelli et al., 2020).
-Such a technological feat, however, leads to a new question: if real and fake stimuli cannot be differentiated based on their objective ``physical'' characteristics, how can we form judgements regarding their nature?
-
-Literature shows that the context surrounding a stimulus often plays an important role in the assessment of its reality (a process henceforth referred to as \emph{simulation monitoring}, Makowski, 2018; Makowski, Sperduti, et al., 2019).
-With the extensive search and processing of cues within ambiguous stimuli being an increasingly complex and cognitively effortful strategy (Michael \& Sanson, 2021; Susmann et al., 2021), people tend to draw on peripheral contextual cues (\textbf{Figure 1}), such as the source of the stimulus (e.g., which journal was the information published in), and its credibility, authority and expertise, to help facilitate their evaluation (Michael \& Sanson, 2021; Petty \& Cacioppo, 1986; Susmann et al., 2021).
-However, the atomization and decontextualization of information allowed by online social media (where text snippets or video excerpts are often mass-shared with little context) makes this task progressively difficult (Berghel, 2018; Y.
-Chen et al., 2015).
-Thus, in the absence of clear contextual information, what drives our beliefs of reality?
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{../figures/Figure1} \caption{The decision to believe that an ambiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.}\label{fig:unnamed-chunk-2}
-\end{figure}
-
-Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits (Bryanov \& Vziatysheva, 2021; Ecker et al., 2022; Sindermann et al., 2020).
-For instance, individuals with stronger analytical reasoning skills have been found to better discriminate real from fake stimuli (Pehlivanoglu et al., 2021; Pennycook \& Rand, 2019), and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations (Britt et al., 2019).
-Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news (Piksa et al., 2022; Sindermann et al., 2020).
-
-Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions.
-For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like ``being there'', as if the object of experience was real - when engaged in a fictional movie or a VR environment (Makowski et al., 2017; Sanchez-Vives \& Slater, 2005).
-Indeed, participants' self-reported emotional arousal were found to significantly predict the probability that they would perceive images as real (Azevedo et al., 2020).
-Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation (Makowski, Sperduti, et al., 2019; Sperduti et al., 2017).
-In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief (Bago et al., 2022; Martel et al., 2020), and higher neurophysiological arousal was predictive of judging realistic images as real (Azevedo et al., 2020).
-Additionally, other factors, such as the stimuli's perceived self-relevance (Goldstein, 2009; Sperduti et al., 2016), as well as familiarity (Begg et al., 1992), could also play a role in guiding our appraisal of a stimulus.
-
-Due to their popularity as a target of CGI technology and the prospect offered with facial features that can be experimentally manipulated, AI-generated images of faces are increasingly used to study face processing (Dawel et al., 2021), in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness (Balas \& Pacella, 2017; Calbi et al., 2017; Sobieraj \& Krämer, 2014; Tsikandilakis et al., 2019).
-Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real (Tucciarelli et al., 2020).
-Conversely, Liefooghe et al.
-(2022) reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge.
-Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness contributes to the formation of reality beliefs - has received little attention to date.
-
-AI-generated content, in particular realistic images, is becoming commonplace and carries important risks for misinformation and black-mailing (Viola \& Voto, 2023), emphasizing the need to understand the different components that come into play in the formation of reality beliefs.
-This exploratory study primarily aims at investigating the effect of facial attractiveness on simulation monitoring, i.e., on the beliefs that an image is real or artificially generated.
-Based on the \emph{affective reality theory}
-Makowski (2023),
-which suggests that salient and emotional stimuli are perceived to be more real (up to a point of reversal after which beliefs of fiction becomes used an emotion regulation strategy), we hypothesize a quadratic relationship between perceived realness and attractiveness: faces rated as highly attractive or unattractive will more likely be believed to be real.
-We expect a similar relationship with trustworthiness ratings given its well-established link with attractiveness (Bartosik et al., 2021; Garrido \& Prada, 2017; Liefooghe et al., 2022; Little et al., 2011), and a positive relationship with familiarity (as more familiar faces would appear as more salient, self-relevant and anchored in reality).
-Additionally, we will further explore the link shared by dispositional traits, such as personality and attitude towards AI, with simulation monitoring tendencies.
-Importantly, this study does investigate the discriminative accuracy between ``true'' photos and ``true'' artificially-generated images (which we consider more a technological issue than a psychological one), focusing on the beliefs that a stimulus is real or fake, independently of its true nature.
-
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
-
-All the material (preregistration, experiment demo, experiment code, raw data, analysis script with complementary figures and analyses, etc.) is available at \href{https://github.com/RealityBending/FakeFace}{\textbf{https://github.com/RealityBending/FakeFace}}.
-
-\hypertarget{ethics-statement}{%
-\subsubsection{Ethics Statement}\label{ethics-statement}}
-
-This study was approved by the NTU Institutional Review Board (NTU IRB-2022-187) and all procedures performed were in accordance with the ethical standards of the institutional board and with the 1964 Helsinki Declaration.
-All participants provided their informed consent prior to participation and were incentivized after completing the study.
-
-\hypertarget{procedure}{%
-\subsubsection{Procedure}\label{procedure}}
-
-In the first part of the study, participants answered a series of personality questionnaires presented in the order below. These include the \emph{Mini-IPIP6}
-(24 items, Sibley et al., 2011)
-measuring 6 personality traits, the \emph{SIAS-6} and the \emph{SPS-6}
-(6 items each, Peters et al., 2012)
-assessing social anxiety levels, 5 items we devised pertaining to expectations about AI-generated image technology (``I think current Artificial Intelligence algorithms can generate very realistic images''), of which we mixed with 5 items from the general attitudes towards AI scale to lower the former's saliency and the possibility of it priming the subjects about the task,
-(\emph{GAAIS}, Schepman \& Rodway, 2020)
-the \emph{FFNI-BF}
-(30 items, Jauk et al., 2022)
-measuring 9 facets of narcissism; the \emph{R-GPTS}
-(18 items, Freeman et al., 2021)
-measuring 2 dimensions related to paranoid thinking; and the \emph{IUS-12}
-(12 items, Carleton et al., 2007)
-measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness
-(``How attractive would you say you are?'' Marcinkowska et al., 2021)
-and the other measuring physical attractiveness
-(``How would you rate your own physical attractiveness relative to the average,'' Spielmann et al., 2020).
-3 attention check questions were also embedded in the surveys.
-
-In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database
-(AMFD, J. M. Chen et al., 2021)
-were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms).
-After each stimulus presentation, ratings of \emph{Trustworthiness} (``I find this person trustworthy'') and \emph{Familiarity} (``This person reminds me of someone I know'') were collected using visual analog scales.
-Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects (Han et al., 2018; Rhodes et al., 2006), we assessed attractiveness using 2 visual analog scales, measuring general \emph{Attractiveness} (``I find this person attractive'') and physical \emph{Beauty} (``This face is good-looking'').
-
-In the last part of the study, participants were informed that ``about half'' of the images previously seen were AI-generated (the instructions used a cover story explaining that the aim of the research was to validate a new face generation algorithm).
-The same set of stimuli was displayed again for 500 ms in a new randomized order.
-This time, after each display, participants were asked to express their belief regarding the nature of the stimulus using a visual analog scale (with \emph{Fake} and \emph{Real} as the two extremes).
-The study was implemented using \emph{jsPsych} (De Leeuw, 2015), and the exact instructions are available in the experiment code.
-
-\hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
-
-Although the main part of the study relied on within-subject design (with 109 trials per participant), we also planned to do between-participants analyses, thus aiming at collecting a larger sample than traditionally used in experimental psychology (with budget availability as the main constraint).
-One hundred and fifty participants were recruited via \emph{Prolific}, a crowd-sourcing platform recognized for providing high quality data {[}Peer et al.
-(2022); douglas2023data{]}.
-The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood.
-Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish.
-Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.
-
-We excluded 5 participants that either failed 2 (\textgreater= 66.6\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses.
-The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: {[}19, 66{]}; Sex: 48.3\% females, 51.0\% males, 0.7\% others).
-
-\hypertarget{data-analysis}{%
-\subsubsection{Data Analysis}\label{data-analysis}}
-
-The real-fake ratings (measured originally with a {[}-1, 1{]} analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous \emph{belief} (real or fake, based on the sign of the rating) and the \emph{confidence} (the rating's absolute value) associated with that belief.
-The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\textgreater= 0) as opposed to fake (\textless{} 0).
-The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using mixed beta regressions (suited for outcome variables expressed in percentages).
-The models included the participants and stimuli as random factors.
-
-We started by investigating the effect of the procedure and instructions to check whether the stimuli (which were all images of real faces) were judged as fake in sufficient proportion to warrant their analysis.
-Additionally, we assessed the effect of the re-exposure delay, i.e., the time between the first presentation of the image (corresponding to the face ratings) and the second presentation (for the real-fake rating), as well as that of the presentation order to check whether for habituation or learning effects.
-
-The determinants of reality beliefs were modelled separately for attractiveness, beauty, trustworthiness, and familiarity, using second order raw polynomials coefficients to allow for possible quadratic relationships (\textbf{Figure 2}).
-Aside from attractiveness (conceptualized as a general construct), models for beauty, trustworthiness and familiarity were adjusted for the the two remaining variables \emph{mutatis mutandis}.
-The analysis focused on sexual-orientation relevant stimuli, i.e., on faces that were aligned with respect to the participants' sexual orientation (i.e., female faces for heterosexual males, male faces for homosexual males, etc.), and the models included the interaction with the participants' gender (as a sexual dimorphism has been reported in face appraisal processes).
-For the attractiveness and beauty models, we then added the interaction with the reported self-attractiveness (the average of the two questions pertaining to it) to investigate its potential modulatory effect.
-Finally, we investigated the inter-individual correlates of simulation monitoring with similar models (but this time, for all items regardless of the participant's gender or sexual orientation) for each questionnaire, with all of the subscales as orthogonal predictors.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{../figures/Figure2} \caption{Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
-fake (solid line) and 2) on the confidence associated with that judgement (dashed lines) depending on the sex.
-Bottom part shows the effect of personality traits on the belief (black line) and the confidence associated with it (colored lines).
-The points are the average per participant confidence for both types of judgements.
-Stars indicate significance (p < .001***, p < .01**, p < .05*).}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the \emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats} collection of packages (Lüdecke et al., 2019, 2020, 2021; Makowski, Ben-Shachar, et al., 2019; Makowski et al., 2020).
-As all the details, scripts and complimentary analyses are open-access, we will focus in the manuscript on findings that are highly statistically significant (\(p <.01\)).
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-On average, across participants, 44\% of images (95\%\textasciitilde CI {[}0.12, 0.64{]}) were judged as fake and 56\% of images (95\%\textasciitilde CI {[}0.36, 0.88{]}) as real.
-An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0\% for the participants and 9.6\% for the stimuli.
-
-While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality (\(OR = 1.00\), \(95\%~CI = [0.99, 1.00]\)), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real (\(\beta = -0.006\), \(95\%~CI = [-0.1, 0.002]\), \(p = .004\)).
-The presentation order also did not have have an effect on the belief (\(OR = 1.00\), \(95\%~CI = [1.00, 1.00]\)) but was related to a decrease of confidence (\(\beta_{real} = -0.003\), \(95\%~CI = [-0.004, -0.002]\), \(p < .001\); \(\beta_{fake} = -0.002\), \(95\%~CI = [-0.004, -0.0003]\), \(p = .021\)): items presented at the end of the session were judged with a similar bias but a decreased overall confidence.
-
-\hypertarget{determinants-of-simulation-monitoring}{%
-\subsubsection{Determinants of Simulation Monitoring}\label{determinants-of-simulation-monitoring}}
-
-Attractiveness had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 16.57\), \(95\%~CI = [7.33, 25.82]\), \(z = 3.51\), \(p < .001\)) for males, and a quadratic relationship for females (\(\beta_{poly2} = 7.82\), \(95\%~CI = [1.81, 13.84]\), \(z = 2.55\), \(p = .011\)), with both non-attractive and attractive faces being judged as more real.
-Attractiveness was also found to have a significant positive and quadratic relationship with confidence in judging faces both as real (\(\beta_{poly2} = 4.30\), \(95\%~CI = [0.97, 7.64]\), \(z = 2.53\), \(p = .011\)) and as fake (\(\beta_{poly2} = 5.23\), \(95\%~CI = [0.
-86, 9.60]\), \(z = 2.35\), \(p = .019\)) for females.
-For males, however, a significant negative and quadratic relationship was found between attractiveness ratings and belief confidence only for faces judged as fake (\(\beta_{poly2} = -9.92\), \(95\%~CI = [-18.99, -0.86]\), \(z = -2.15\), \(p = .032\)).
-There was no interaction with reported self-attractiveness.
-
-Beauty, adjusted for trustworthiness and familiarity, had a significant positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 11.82\), \(95\%~CI = [4.28, 20.21]\), \(z = 2.76\), \(p = .006\)) for males only.
-No effect on confidence was found, aside from a quadratic relationship in females for faces judged as fake, suggesting that non-beautiful and highly beautiful faces were rated as fake with more confidence than average faces (\(\beta_{poly2} = 7.84\), \(95\%~CI = [3.39, 12.29]\), \(z = 3.46\), \(p < .001\)).
-There was no interaction with reported self-attractiveness.
-
-Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the belief that a stimulus was real (\(\beta_{poly1} = 6.44\), \(95\%~CI = [-0.11, 13.00]\), \(z = 1.93\), \(p = .0054\)) for females only.
-No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real (\(\beta_{poly2} = 6.14\), \(95\%~CI = [2.13, 10.14]\), \(z = 3.00\), \(p = .003\)) as well as fake (\(\beta_{poly2} =6.12\), \(95\%~CI = [1.49, 10.75]\), \(z = 2.59\), \(p = .001\)), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.
-
-We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness (\(R^2_{marginal}\) = 2.0\%).
-However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real (\(\beta_{poly1} = 9.98\), \(95\%~CI = [3.83, 16.13]\), \(z = 3.18\), \(p = .001\)) whereas a negative linear relationship was found with those judged as fake (\(\beta_{poly1} = -12.41\), \(95\%~CI = [-20.27, -4.54]\), \(z = -3.09\), \(p = .002\)) for males only.
-This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.
-
-Note that we also tested as predictors the normative attractiveness and trustworthiness scores (i.e., the average values from the stimuli database validation), which showed a significant positive linear relationship between beliefs of reality and attractiveness, as well as trustworthiness, only for males (see Supplementary Analysis for details).
-
-\hypertarget{inter-individual-correlates-of-simulation-monitoring}{%
-\subsubsection{Inter-Individual Correlates of Simulation Monitoring}\label{inter-individual-correlates-of-simulation-monitoring}}
-
-The models including the personality traits suggested that \emph{Honesty-Humility} had a significant negative relationship with the confidence associated with real as well as fake judgements (\(\beta_{real} = -1.62\), \(95\%~CI = [-2.55, -0.70]\), \(z = -3.43\), \(p < .001\); \(\beta_{fake} = -1.16\), \(95\%~CI = [-2.09, -0.23]\), \(z = -2.45\), \(p = 0.014\)).
-
-Significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as \emph{Acclaim Seeking} (\(\beta = 2.24\), \(95\%~CI = [1.17, 4.27]\), \(z = 2.44\), \(p = .015\)), and \emph{Manipulativeness} (\(\beta = 0.47\), \(95\%~CI = [0.25, 0.87]\), \(z = -2.4\), \(p = 0.017\)).
-Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgements with \emph{Acclaim Seeking} (\(\beta_{real} = 1.65\), \(95\%~CI = [0.59, 2.70]\), \(z = 3.07\), \(p =.002\); \(\beta_{fake} = 1.62\), \(95\%~CI = [0.56, 2.68]\), \(z = 3.00\), \(p = .003\)), and a negative relationship with \emph{Authoritativeness} (\(\beta_{real} = -1.57\), \(95\%~CI = [-2.58, -0.57]\), \(z = -3.08\), \(p = .002\); \(\beta_{fake} = -1.49\), \(95\%~CI = [-2.50, -0.48]\), \(z = -2.89\), \(p = .004\)).
-
-A positive trend was found in the relationship between the \emph{Persecutory Ideation} dimension of paranoid thinking and the belief that the faces were real (\(\beta = 1.87\), \(95\%~CI = [0.99, 3.54]\), \(z = 1.93\), \(p = .054\)).
-
-The \emph{Prospective Anxiety} aspect of intolerance to uncertainty shared a negative trend in its association with confidence ratings (\(\beta_{real} = 1.43\), \(95\%~CI = [0.10, 2.76]\), \(z = 2.10\), \(p = .036\); \(\beta_{fake} = -0.91\), \(95\%~CI = [-1.93, 0.11]\), \(z = -1.75\), \(p = .081\)).
-No significant effect was found for social anxiety.
-
-Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology).
-However, only AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgements (\(\beta_{real} = 0.21\), \(95\%~CI = [0.02, 0.40]\), \(z = 2.20\), \(p = .028\); \(\beta_{fake} = 0.31\), \(95\%~CI = [0.12, 0.50]\), \(z = -8.90\), \(p < 0.001\)).
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-This study aimed at investigating the effect of facial ratings (attractiveness, beauty, trustworthiness and familiarity) on simulation monitoring, i.e., on the belief that a stimulus was artificially generated.
-Most strikingly, despite all the stimuli being real faces from the same database, all participants believed (to high degrees of confidence) that a significant proportion of them were fake.
-This finding not only attests to the effectiveness of our instructions, but highlights the current levels of expectation regarding CGI technology.
-The strong impact of prior expectations and information on reality beliefs underlines the volatility of our sense of reality.
-In fact, stimuli-related and participant-related characteristics accounted together for less than 20\% of the beliefs variance, suggesting a large contribution of other subjective processes.
-
-Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with different patterns observed depending on the participant's gender.
-The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real.
-The fact that this effect did not reach significance for beauty underlines that attractiveness judgement, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women (Buunk et al., 2002; Qi \& Ying, 2022).
-In fact, female participants were more confident in judging faces as fake only when they were rated very high or low on beauty, suggesting that physical beauty and attractiveness are not analogous in their effects on simulation monitoring decisions.
-
-Interestingly, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring that we could interpret under an evolutionary lens.
-Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \& Ying, 2022).
-It is thus possible that the evolutionary weight associated with attractiveness skewed the perceived saliency of attractive faces for men, rendering them significantly more salient than unattractive faces, and in turn distorting the relationship with simulation monitoring.
-However, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al., 2015) or physiological markers
-(e.g., heart rate deceleration, Skora et al., 2022).
-
-Our findings do not support the existence of a strong link between perceived trustworthiness and reality judgments.
-Given prior evidence that faces presented as computer-generated were rated less trustworthy (Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we expected such a linear association to be more clearly present.
-However, our results suggest a relationship with confidence ratings, especially for women, whereby faces judged with low and high trustworthiness are judged as real and fake with higher confidence.
-One of the underlying mechanisms that possibly contributed to this dimorphism could be the increased risk-taking aversion reported in females (explained evolutionarily as a compromise to their reproductive potential, Van Den Akker et al., 2020), to which perceived facial trustworthiness relates (Hou \& Liu, 2019).
-Future studies should clarify the role of trustworthiness both as a predictor and outcome of reality beliefs.
-
-Contrary to our hypothesis, we did not find familiarity to be significantly related to simulation monitoring decisions.
-Interestingly, there were significant linear relationships between familiarity and confidence judgements for males only, where familiarity increased the confidence of reality beliefs.
-Although the familiarity measure was not a ``recognition'' measure, evidence from studies pertaining to the latter could be linked, reporting better face memory for females (Lewin \& Herlitz, 2002; Mishra et al., 2019; Sommer et al., 2013), as well as an overconfidence in face recall for males (Bailey, 2021; Herbst, 2020).
-However, it should be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar.
-As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgements.
-
-Regarding the role of inter-individual characteristics in simulation monitoring tendencies, we found higher scores of honesty-humility - a trait related to an increased risk perception and aversion (Levidi et al., 2022; Weller \& Thulin, 2012) - to be related to a lower confidence in simulation monitoring judgements.
-Notably, greater narcissistic tendencies in dimensions such as acclaim seeking were associated with a higher number of faces judged as real.
-This is in line with recent research which found people with higher narcissism scores less likely to engage in analytical reasoning strategies such as reflective thinking (Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et al., 2020).
-
-Moreover, putting the significant positive links between narcissistic acclaim seeking and confidence judgements in perspective with the negative correlation between honesty-humility and narcissism (Hodson et al., 2018), we confirm previous evidence regarding the relationship between narcissistic grandiosity and over-confidence in decision-making (Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock, 2017; O'Reilly \& Hall, 2021).
-Although an inverse effect was found for the narcissistic facet of authoritativeness, we interpret this relationship as related to a higher response assertiveness.
-Taken together, these results suggest that participants with low humility and high recognition desires are more confident in their judgement regarding the real or fake nature of ambiguous stimuli.
-Alternatively, participants with opposite traits might perceive a higher risk in the decision-making process and its potential consequences (e.g., being seen as bad at the task at hand), resulting in more conservative confidence ratings.
-
-Our findings suggest - though with low certainty - a potential positive link between paranoid ideation and the tendency to believe that the stimuli were real.
-Given previous reports that people with higher levels of paranoia are more sensitive to cues of social threat (Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley, 2017), it is plausible that paranoid traits confer greater saliency and emotionality to observed faces, hence increasing perceptions of its realness.
-This hypothesis, if confirmed by future studies, would be in line with previous findings that persecutory delusions are predicted by a greater sense of presence in VR environments populated with virtual characters (Freeman et al., 2005).
-
-Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce.
-Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions).
-Instead, we found only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings.
-This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities (Said et al., 2022), hence permitting themselves to be more confident in their simulation monitoring decisions.
-In fact, this result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications (Said et al., 2022).
-
-On a methodological level, although the order of presentation of the facial images was randomized to reduce effects of adaptation, participants were more confident in their judgements for faces perceived as real following a shorter re-exposure delay.
-Such shorter durations could be associated with the faces being better remembered and appearing more familiar, thereby triggering self-referential and autobiographical memory processing during the repeated display (Abraham \& Von Cramon, 2009; Gobbini et al., 2013; Taylor et al., 2009).
-Indeed, this finding is consistent with studies in which fictional stimuli that were associated with familiarity up-regulated emotions, biasing its salience and perceived realness (Makowski et al., 2017; Sperduti et al., 2016).
-However, if that was the case, we would expect shorter re-exposure delays to impact the decision bias as well towards reality, rather than simply the confidence.
-Future studies should further investigate the modulatory effects of types and degrees of familiarity on perceived realness judgements.
-
-Several limitations have to be noted.
-The current experimental paradigm required participants to judge the realness of faces they had prior exposure to (which was done to prevent reality judgements from influencing the other ratings).
-Although the effect of re-exposure delay was negligible, the potential bias induced by face familiarity (as compared to judging completely new items) cannot be discarded.
-Future studies could examine that by incorporating novel face images or increasing the duration of the re-exposure delay.
-
-Another issue is the impact on reality judgements of the prior explicit instruction that ``about half of the faces were AI-generated and the other half real photos''.
-Given this prior information given to participants, it might seems like our enthusiasm pertaining to the finding that most people did indeed believe a high number of stimuli to be fake might be unwarranted, since it simply affirms participants followed the instructions.
-However, even if that was the case, the finding that our beliefs of reality can be so easily re-programmed with simple instructions and lead to high-confidence answers remains an interesting phenomenon.
-Moreover, it is to note that the paradigm did not instruct participants to balance their answers according to a certain distribution (e.g., 50-50), merely providing them a description of the dataset.
-The fact that no presentation order effect was found on reality beliefs suggests that participants did not try to actively distribute their responses to match the instructions, in which case we would have expected a different pattern: for instance, the first few items judged as real (the initial ``true'' belief of the participants), and a bias would progressively appear towards responding ``fake'' (as participants realize that all stimuli are of similar nature and that they have to ``make up'' for the prevalence of their ``real'' answers to fulfil the expected proportion of responses given the instructions).
-
-That said, the potential demand effect of the instructions still exists, and a control condition without the cover story with AI-generated images would in-principle be able to mitigate such confounds to some extent.
-However, the distinction real/fake is hard to operationalize and introduce to participants in a vacuum (simply instructing them to discriminate real from fake without providing some background information regarding the context and defining what is meant by ``fake'' seems hardly feasible).
-That being the case, future studies should study the impact of these higher-order expectations on ratings (for instance, Tucciarelli et al., 2020 found that merely mentioning that some faces were AI generated decreased, on average, the trustworthiness ratings for all faces) as well as on the simulation monitoring process itself (i.e., the ``criterion'': would people form and distribute judgements differently).
-This can be studied by modulating this expectation in a controlled fashion (e.g., ``most of the images \emph{but a few} are real'' vs.~``most of the images \emph{but a few} are fake'') or inventing some implicit way of measuring reality belief that would not require the explicit introduction of the concept of fake vs.~real to participants.
-
-Finally, it is important to note that although consistent in their directions across models and variables, the magnitude of the effects found in the study was relatively small, suggesting that the facial appraisals measured in the study were not the key determinants of simulation monitoring.
-Hence, beyond exploring new potential mechanisms, future studies should include a more thorough debriefing to try to capture what conscious strategies (if any) the participants used (e.g., focusing on some features of the stimulus - like hair or eyes in the case of faces) to guide their reality beliefs.
-
-In summary, the aim of the present study was to examine whether a subset of specific characteristics, in particular face attractiveness, significantly influences our simulation monitoring decisions.
-Notably, we found faces rated as attractive to be perceived as more real, with a possible sexual dimorphism affecting the shape of the relationship.
-We also found that inter-individual traits, such as narcissistic acclaim-seeking, honesty-humility, and paranoid ideation, were related to a systematic bias towards beliefs that the stimuli were real or fake.
-We believe that these findings provide the foundations to help us understand what drives reality beliefs in an increasingly reality-ambiguous world.
-
-\hypertarget{data-availability}{%
-\section{Data Availability}\label{data-availability}}
-
-The datasets generated and/or analysed during the current study are available in the GitHub repository \url{https://github.com/RealityBending/FakeFace}
-
-\hypertarget{funding}{%
-\section{Funding}\label{funding}}
-
-This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM) and the Intra-CREATE Seed Collaboration Grant (NRF2021-ITS008-0010) from the National Research Foundation, Prime Minister's Office, Singapore, under its Campus for Research Excellence and Technological Enterprise (CREATE) programme (awarded to DM and PM).
-
-\hypertarget{acknowledgments}{%
-\section{Acknowledgments}\label{acknowledgments}}
-
-We would like to thank Taong Ren Qing Malcolm for his contribution to the selection of the materials.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
+\end{figure}%
+
+The analysis was carried out using \emph{R 4.2} (R Core Team, 2022), the
+\emph{tidyverse} (Wickham et al., 2019), and the \emph{easystats}
+collection of packages (Lüdecke et al., 2019, 2020, 2021; Makowski,
+Ben-Shachar, et al., 2019; Makowski et al., 2020). As all the details,
+scripts and complimentary analyses are open-access, we will focus in the
+manuscript on findings that are highly statistically significant
+(\(p <.01\)).
+
+\subsection{Results}\label{results}
+
+On average, across participants, 44\% of images (95\%\textasciitilde CI
+{[}0.12, 0.64{]}) were judged as fake and 56\% of images
+(95\%\textasciitilde CI {[}0.36, 0.88{]}) as real. An intercept-only
+model with the participants and images as random factors showed that the
+Intraclass Correlation Coefficient (ICC), which can be interpreted as
+the proportion of variance explained by the random factors, was of 9.0\%
+for the participants and 9.6\% for the stimuli.
+
+While the delay of stimulus re-exposure stimulus did not have a
+significant effect on participants' beliefs of reality (\(OR = 1.00\),
+\(95\%~CI = [0.99, 1.00]\)), judgement confidence was found to be
+negatively associated with re-exposure delay when the faces were judged
+as real (\(\beta = -0.006\), \(95\%~CI = [-0.1, 0.002]\), \(p = .004\)).
+The presentation order also did not have have an effect on the belief
+(\(OR = 1.00\), \(95\%~CI = [1.00, 1.00]\)) but was related to a
+decrease of confidence (\(\beta_{real} = -0.003\),
+\(95\%~CI = [-0.004, -0.002]\), \(p < .001\); \(\beta_{fake} = -0.002\),
+\(95\%~CI = [-0.004, -0.0003]\), \(p = .021\)): items presented at the
+end of the session were judged with a similar bias but a decreased
+overall confidence.
+
+\textbf{Determinants of Simulation Monitoring.} Attractiveness had a
+significant positive and linear relationship (\(R^2_{marginal}\) =
+2.0\%) with the belief that a stimulus was real
+(\(\beta_{poly1} = 16.57\), \(95\%~CI = [7.33, 25.82]\), \(z = 3.51\),
+\(p < .001\)) for males, and a quadratic relationship for females
+(\(\beta_{poly2} = 7.82\), \(95\%~CI = [1.81, 13.84]\), \(z = 2.55\),
+\(p = .011\)), with both non-attractive and attractive faces being
+judged as more real. Attractiveness was also found to have a significant
+positive and quadratic relationship with confidence in judging faces
+both as real (\(\beta_{poly2} = 4.30\), \(95\%~CI = [0.97, 7.64]\),
+\(z = 2.53\), \(p = .011\)) and as fake (\(\beta_{poly2} = 5.23\),
+\(95\%~CI = [0. 86, 9.60]\), \(z = 2.35\), \(p = .019\)) for females.
+For males, however, a significant negative and quadratic relationship
+was found between attractiveness ratings and belief confidence only for
+faces judged as fake (\(\beta_{poly2} = -9.92\),
+\(95\%~CI = [-18.99, -0.86]\), \(z = -2.15\), \(p = .032\)). There was
+no interaction with reported self-attractiveness.
+
+Beauty, adjusted for trustworthiness and familiarity, had a significant
+positive and linear relationship (\(R^2_{marginal}\) = 2.0\%) with the
+belief that a stimulus was real (\(\beta_{poly1} = 11.82\),
+\(95\%~CI = [4.28, 20.21]\), \(z = 2.76\), \(p = .006\)) for males only.
+No effect on confidence was found, aside from a quadratic relationship
+in females for faces judged as fake, suggesting that non-beautiful and
+highly beautiful faces were rated as fake with more confidence than
+average faces (\(\beta_{poly2} = 7.84\), \(95\%~CI = [3.39, 12.29]\),
+\(z = 3.46\), \(p < .001\)). There was no interaction with reported
+self-attractiveness.
+
+Trustworthiness, adjusted for beauty and familiarity, had a
+predominantly positive and linear relationship (\(R^2_{marginal}\) =
+2.0\%) with the belief that a stimulus was real
+(\(\beta_{poly1} = 6.44\), \(95\%~CI = [-0.11, 13.00]\), \(z = 1.93\),
+\(p = .0054\)) for females only. No effect on confidence was found for
+males, whereas a quadratic relationship was found for females for both
+faces judged as real (\(\beta_{poly2} = 6.14\),
+\(95\%~CI = [2.13, 10.14]\), \(z = 3.00\), \(p = .003\)) as well as fake
+(\(\beta_{poly2} =6.12\), \(95\%~CI = [1.49, 10.75]\), \(z = 2.59\),
+\(p = .001\)), suggesting that non-trustworthy and highly trustworthy
+faces were rated with more confidence than average faces.
+
+We did not find any significant relationships for familiarity adjusted
+for beauty and trustworthiness (\(R^2_{marginal}\) = 2.0\%). However, a
+significant positive and linear relationship was found between
+familiarity and the confidence judgements of rating faces as real
+(\(\beta_{poly1} = 9.98\), \(95\%~CI = [3.83, 16.13]\), \(z = 3.18\),
+\(p = .001\)) whereas a negative linear relationship was found with
+those judged as fake (\(\beta_{poly1} = -12.41\),
+\(95\%~CI = [-20.27, -4.54]\), \(z = -3.09\), \(p = .002\)) for males
+only. This hence suggests that males more confidently judge faces as
+real with when they are familiar, and as fake when they are unfamiliar.
+
+Note that we also tested as predictors the normative attractiveness and
+trustworthiness scores (i.e., the average values from the stimuli
+database validation), which showed a significant positive linear
+relationship between beliefs of reality and attractiveness, as well as
+trustworthiness, only for males (see Supplementary Analysis for
+details).
+
+\textbf{Inter-Individual Correlates of Simulation Monitoring.} The
+models including the personality traits suggested that
+\emph{Honesty-Humility} had a significant negative relationship with the
+confidence associated with real as well as fake judgements
+(\(\beta_{real} = -1.62\), \(95\%~CI = [-2.55, -0.70]\), \(z = -3.43\),
+\(p < .001\); \(\beta_{fake} = -1.16\), \(95\%~CI = [-2.09, -0.23]\),
+\(z = -2.45\), \(p = 0.014\)).
+
+Significant positive associations were found between the probability of
+judging faces as real and dimensions of narcissism such as \emph{Acclaim
+Seeking} (\(\beta = 2.24\), \(95\%~CI = [1.17, 4.27]\), \(z = 2.44\),
+\(p = .015\)), and \emph{Manipulativeness} (\(\beta = 0.47\),
+\(95\%~CI = [0.25, 0.87]\), \(z = -2.4\), \(p = 0.017\)). Confidence
+judgements also shared significant links with narcissism through various
+facets, such as a positive relationship between the confidence for both
+real and fake judgements with \emph{Acclaim Seeking}
+(\(\beta_{real} = 1.65\), \(95\%~CI = [0.59, 2.70]\), \(z = 3.07\),
+\(p =.002\); \(\beta_{fake} = 1.62\), \(95\%~CI = [0.56, 2.68]\),
+\(z = 3.00\), \(p = .003\)), and a negative relationship with
+\emph{Authoritativeness} (\(\beta_{real} = -1.57\),
+\(95\%~CI = [-2.58, -0.57]\), \(z = -3.08\), \(p = .002\);
+\(\beta_{fake} = -1.49\), \(95\%~CI = [-2.50, -0.48]\), \(z = -2.89\),
+\(p = .004\)).
+
+A positive trend was found in the relationship between the
+\emph{Persecutory Ideation} dimension of paranoid thinking and the
+belief that the faces were real (\(\beta = 1.87\),
+\(95\%~CI = [0.99, 3.54]\), \(z = 1.93\), \(p = .054\)).
+
+The \emph{Prospective Anxiety} aspect of intolerance to uncertainty
+shared a negative trend in its association with confidence ratings
+(\(\beta_{real} = 1.43\), \(95\%~CI = [0.10, 2.76]\), \(z = 2.10\),
+\(p = .036\); \(\beta_{fake} = -0.91\), \(95\%~CI = [-1.93, 0.11]\),
+\(z = -1.75\), \(p = .081\)). No significant effect was found for social
+anxiety.
+
+Questions pertaining to the attitude towards AI were reduced to 3
+dimensions through factor analysis, labelled AI-Enthusiasm (loaded by
+items expressing interest and excitement in AI development and
+applications), AI-Realness (loaded by items expressing positive opinions
+on the ability of AI to create realistic material), and AI-Danger
+(loaded by items expressing concerns on the unethical misuse of AI
+technology). However, only AI-Enthusiasm displayed a significant
+positive relationship with the confidence in both real and fake
+judgements (\(\beta_{real} = 0.21\), \(95\%~CI = [0.02, 0.40]\),
+\(z = 2.20\), \(p = .028\); \(\beta_{fake} = 0.31\),
+\(95\%~CI = [0.12, 0.50]\), \(z = -8.90\), \(p < 0.001\)).
+
+\subsection{Discussion}\label{discussion}
+
+This study aimed at investigating the effect of facial ratings
+(attractiveness, beauty, trustworthiness and familiarity) on simulation
+monitoring, i.e., on the belief that a stimulus was artificially
+generated. Most strikingly, despite all the stimuli being real faces
+from the same database, all participants believed (to high degrees of
+confidence) that a significant proportion of them were fake. This
+finding not only attests to the effectiveness of our instructions, but
+highlights the current levels of expectation regarding CGI technology.
+The strong impact of prior expectations and information on reality
+beliefs underlines the volatility of our sense of reality. In fact,
+stimuli-related and participant-related characteristics accounted
+together for less than 20\% of the beliefs variance, suggesting a large
+contribution of other subjective processes.
+
+Although attractiveness did not seem to be the primary drive underlying
+simulation monitoring of face images, we do nonetheless report
+significant associations, with different patterns observed depending on
+the participant's gender. The quadratic relationship found for female
+participants is aligned with our hypothesis that salient faces (i.e.,
+rated as very attractive or very unattractive) are judged to be more
+real. The fact that this effect did not reach significance for beauty
+underlines that attractiveness judgement, and its role in simulation
+monitoring, is a multidimensional construct that cannot be reduced to
+physical facial attractiveness, in particular for women (Buunk et al.,
+2002; Qi \& Ying, 2022). In fact, female participants were more
+confident in judging faces as fake only when they were rated very high
+or low on beauty, suggesting that physical beauty and attractiveness are
+not analogous in their effects on simulation monitoring decisions.
+
+Interestingly, we found a significant positive linear relationship in
+male participants for both attractiveness and beauty on simulation
+monitoring that we could interpret under an evolutionary lens.
+Specifically, males purportedly place more emphasis on facial
+attractiveness as a sign of reproductive potential, as compared with
+females, who tend to value characteristics signaling resource
+acquisition capabilities (Buunk et al., 2002; Fink et al., 2006; Qi \&
+Ying, 2022). It is thus possible that the evolutionary weight associated
+with attractiveness skewed the perceived saliency of attractive faces
+for men, rendering them significantly more salient than unattractive
+faces, and in turn distorting the relationship with simulation
+monitoring. However, future studies should test this saliency-based
+hypothesis by measuring constructs closer to salience and its effects,
+for instance using neuroimaging (Indovina \& Macaluso, 2007; Lou et al.,
+2015) or physiological markers (e.g., heart rate deceleration, Skora et
+al., 2022).
+
+Our findings do not support the existence of a strong link between
+perceived trustworthiness and reality judgments. Given prior evidence
+that faces presented as computer-generated were rated less trustworthy
+(Balas \& Pacella, 2017; Hoogers, 2021; Liefooghe et al., 2022), we
+expected such a linear association to be more clearly present. However,
+our results suggest a relationship with confidence ratings, especially
+for women, whereby faces judged with low and high trustworthiness are
+judged as real and fake with higher confidence. One of the underlying
+mechanisms that possibly contributed to this dimorphism could be the
+increased risk-taking aversion reported in females (explained
+evolutionarily as a compromise to their reproductive potential, Van Den
+Akker et al., 2020), to which perceived facial trustworthiness relates
+(Hou \& Liu, 2019). Future studies should clarify the role of
+trustworthiness both as a predictor and outcome of reality beliefs.
+
+Contrary to our hypothesis, we did not find familiarity to be
+significantly related to simulation monitoring decisions. Interestingly,
+there were significant linear relationships between familiarity and
+confidence judgements for males only, where familiarity increased the
+confidence of reality beliefs. Although the familiarity measure was not
+a ``recognition'' measure, evidence from studies pertaining to the
+latter could be linked, reporting better face memory for females (Lewin
+\& Herlitz, 2002; Mishra et al., 2019; Sommer et al., 2013), as well as
+an overconfidence in face recall for males (Bailey, 2021; Herbst, 2020).
+However, it should be noted that the distribution of familiarity ratings
+was strongly skewed, and only a low number of pictures was rated as
+highly familiar. As such, future studies should clarify this point by
+experimentally manipulating familiarity, for instance by modulating the
+amount of exposure to items before querying the simulation monitoring
+judgements.
+
+Regarding the role of inter-individual characteristics in simulation
+monitoring tendencies, we found higher scores of honesty-humility - a
+trait related to an increased risk perception and aversion (Levidi et
+al., 2022; Weller \& Thulin, 2012) - to be related to a lower confidence
+in simulation monitoring judgements. Notably, greater narcissistic
+tendencies in dimensions such as acclaim seeking were associated with a
+higher number of faces judged as real. This is in line with recent
+research which found people with higher narcissism scores less likely to
+engage in analytical reasoning strategies such as reflective thinking
+(Ahadzadeh et al., 2021; Littrell et al., 2020), and to be more vigilant
+and attentive to external stimuli (Carolan, 2017; Eddy, 2021; Grapsas et
+al., 2020).
+
+Moreover, putting the significant positive links between narcissistic
+acclaim seeking and confidence judgements in perspective with the
+negative correlation between honesty-humility and narcissism (Hodson et
+al., 2018), we confirm previous evidence regarding the relationship
+between narcissistic grandiosity and over-confidence in decision-making
+(Brunell \& Buelow, 2017; Campbell et al., 2004; Chatterjee \& Pollock,
+2017; O'Reilly \& Hall, 2021). Although an inverse effect was found for
+the narcissistic facet of authoritativeness, we interpret this
+relationship as related to a higher response assertiveness. Taken
+together, these results suggest that participants with low humility and
+high recognition desires are more confident in their judgement regarding
+the real or fake nature of ambiguous stimuli. Alternatively,
+participants with opposite traits might perceive a higher risk in the
+decision-making process and its potential consequences (e.g., being seen
+as bad at the task at hand), resulting in more conservative confidence
+ratings.
+
+Our findings suggest - though with low certainty - a potential positive
+link between paranoid ideation and the tendency to believe that the
+stimuli were real. Given previous reports that people with higher levels
+of paranoia are more sensitive to cues of social threat
+(Fornells-Ambrojo et al., 2015; Freeman et al., 2003; King \& Dudley,
+2017), it is plausible that paranoid traits confer greater saliency and
+emotionality to observed faces, hence increasing perceptions of its
+realness. This hypothesis, if confirmed by future studies, would be in
+line with previous findings that persecutory delusions are predicted by
+a greater sense of presence in VR environments populated with virtual
+characters (Freeman et al., 2005).
+
+Despite the ubiquity of AI, the literature pertaining to the influence
+of people's AI attitudes on simulation monitoring is scarce. Contrary to
+our expectations, we did not find evidence for the role of participants'
+expectations regarding the capabilities of AI technology (in terms of
+the realism of its productions). Instead, we found only one's enthusiasm
+about AI technology to be related to an increased confidence in
+simulation monitoring ratings. This could potentially be because
+participants with a highly positive attitude towards AI perceive
+themselves as having greater knowledge about AI and its capabilities
+(Said et al., 2022), hence permitting themselves to be more confident in
+their simulation monitoring decisions. In fact, this result is in line
+with reports that AI attitudes interacts with people's perceived
+self-knowledge to influence their perception of the opportunities and
+risks accorded by AI applications (Said et al., 2022).
+
+On a methodological level, although the order of presentation of the
+facial images was randomized to reduce effects of adaptation,
+participants were more confident in their judgements for faces perceived
+as real following a shorter re-exposure delay. Such shorter durations
+could be associated with the faces being better remembered and appearing
+more familiar, thereby triggering self-referential and autobiographical
+memory processing during the repeated display (Abraham \& Von Cramon,
+2009; Gobbini et al., 2013; Taylor et al., 2009). Indeed, this finding
+is consistent with studies in which fictional stimuli that were
+associated with familiarity up-regulated emotions, biasing its salience
+and perceived realness (Makowski et al., 2017; Sperduti et al., 2016).
+However, if that was the case, we would expect shorter re-exposure
+delays to impact the decision bias as well towards reality, rather than
+simply the confidence. Future studies should further investigate the
+modulatory effects of types and degrees of familiarity on perceived
+realness judgements.
+
+Several limitations have to be noted. The current experimental paradigm
+required participants to judge the realness of faces they had prior
+exposure to (which was done to prevent reality judgements from
+influencing the other ratings). Although the effect of re-exposure delay
+was negligible, the potential bias induced by face familiarity, that is
+by re-presenting the same face stimuli twice, as compared to judging
+completely new items, cannot be discarded. Future studies could examine
+that by incorporating novel face images or increasing the duration of
+the re-exposure delay.
+
+Another issue is the impact on reality judgements of the prior explicit
+instruction that ``about half of the faces were AI-generated and the
+other half real photos''. Given this prior information given to
+participants, it might seems like our enthusiasm pertaining to the
+finding that most people did indeed believe a high number of stimuli to
+be fake might be unwarranted, since it simply affirms participants
+followed the instructions. However, even if that was the case, the
+finding that our beliefs of reality can be so easily re-programmed with
+simple instructions and lead to high-confidence answers remains an
+interesting phenomenon. Moreover, it is to note that the paradigm did
+not instruct participants to balance their answers according to a
+certain distribution (e.g., 50-50), merely providing them a description
+of the dataset. The fact that no presentation order effect was found on
+reality beliefs suggests that participants did not try to actively
+distribute their responses to match the instructions, in which case we
+would have expected a different pattern: for instance, the first few
+items judged as real (the initial ``true'' belief of the participants),
+and a bias would progressively appear towards responding ``fake'' (as
+participants realize that all stimuli are of similar nature and that
+they have to ``make up'' for the prevalence of their ``real'' answers to
+fulfil the expected proportion of responses given the instructions).
+
+That said, the potential demand effect of the instructions still exists,
+and a control condition without the cover story with AI-generated images
+would in-principle be able to mitigate such confounds to some extent.
+However, the distinction real/fake is hard to operationalize and
+introduce to participants in a vacuum (simply instructing them to
+discriminate real from fake without providing some background
+information regarding the context and defining what is meant by ``fake''
+seems hardly feasible). That being the case, future studies should study
+the impact of these higher-order expectations on ratings (for instance,
+Tucciarelli et al., 2020 found that merely mentioning that some faces
+were AI generated decreased, on average, the trustworthiness ratings for
+all faces) as well as on the simulation monitoring process itself (i.e.,
+the ``criterion'': would people form and distribute judgements
+differently). This can be studied by modulating this expectation in a
+controlled fashion (e.g., ``most of the images \emph{but a few} are
+real'' vs.~``most of the images \emph{but a few} are fake'') or
+inventing some implicit way of measuring reality belief that would not
+require the explicit introduction of the concept of fake vs.~real to
+participants.
+
+Finally, it is important to note that although consistent in their
+directions across models and variables, the magnitude of the effects
+found in the study was relatively small, suggesting that the facial
+appraisals measured in the study were not the key determinants of
+simulation monitoring. Hence, beyond exploring new potential mechanisms,
+future studies should include a more thorough debriefing to try to
+capture what conscious strategies (if any) the participants used (e.g.,
+focusing on some features of the stimulus - like hair or eyes in the
+case of faces) to guide their reality beliefs. \textbf{Additionally, the
+role of specific facial features, like perceived dominance, warmth or
+gender, would be an interesting avenue to explore in future studies, in
+particular with paradigms directly manipulating these dimensions (for
+instance using AI to generate faces of different characteristics).}
+
+In summary, the aim of the present study was to examine whether a subset
+of specific characteristics, in particular face attractiveness,
+significantly influences our simulation monitoring decisions. Notably,
+we found faces rated as attractive to be perceived as more real, with a
+possible sexual dimorphism affecting the shape of the relationship. We
+also found that inter-individual traits, such as narcissistic
+acclaim-seeking, honesty-humility, and paranoid ideation, were related
+to a systematic bias towards beliefs that the stimuli were real or fake.
+We believe that these findings provide the foundations to help us
+understand what drives reality beliefs in an increasingly
+reality-ambiguous world.
+
+\section{Data Availability}\label{data-availability}
+
+The datasets generated and/or analysed during the current study are
+available in the GitHub repository
+https://github.com/RealityBending/FakeFace
+
+\pagebreak
+
+\section{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abraham2009reality}{}}%
-Abraham, A., \& Von Cramon, D.
-Y.
-(2009).
-Reality= relevance?
-Insights from spontaneous modulations of the brain's default network when telling apart reality from fiction.
-\emph{PloS One}, \emph{4}(3), e4741.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ahadzadeh2021social}{}}%
-Ahadzadeh, A. S., Ong, F. S., \& Wu, S. L. (2021). Social media skepticism and belief in conspiracy theories about COVID-19: The moderating role of the dark triad. \emph{Current Psychology}, 1--13.
-
-\leavevmode\vadjust pre{\hypertarget{ref-azevedo2020body}{}}%
-Azevedo, R., Tucciarelli, R., De Beuklaer, S., Ambroziak, K., Jones, I., \& Tsakiris, M. (2020). \emph{A body of evidence:`feeling in seeing'predicts realness judgments for photojournalistic images.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bago2022emotion}{}}%
-Bago, B., Rosenzweig, L. R., Berinsky, A. J., \& Rand, D. G. (2022). Emotion may predict susceptibility to fake news but emotion regulation does not seem to help. \emph{Cognition and Emotion}, 1--15.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bailey2021gender}{}}%
-Bailey, A. (2021). \emph{A gender in-group effect on facial recall} {[}PhD thesis{]}. University of Tasmania.
-
-\leavevmode\vadjust pre{\hypertarget{ref-balas2017}{}}%
-Balas, B., \& Pacella, J. (2017). Trustworthiness perception is disrupted in artificial faces. \emph{Computers in Human Behavior}, \emph{77}. \url{https://doi.org/10.1016/j.chb.2017.08.045}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bartosik2021you}{}}%
-Bartosik, B., Wojcik, G.
-M., Brzezicka, A., \& Kawiak, A.
-(2021).
-Are you able to trust me?
-Analysis of the relationships between personality traits and the assessment of attractiveness and trust.
-\emph{Frontiers in Human Neuroscience}, \emph{15}, 685530.
-
-\leavevmode\vadjust pre{\hypertarget{ref-begg1992dissociation}{}}%
-Begg, I.
-M., Anas, A., \& Farinacci, S.
-(1992).
-Dissociation of processes in belief: Source recollection, statement familiarity, and the illusion of truth.
-\emph{Journal of Experimental Psychology: General}, \emph{121}(4), 446.
-
-\leavevmode\vadjust pre{\hypertarget{ref-berghel2018weaponizing}{}}%
-Berghel, H. (2018). Weaponizing twitter litter: Abuse-forming networks and social media. \emph{Computer}, \emph{51}(4), 70--73.
-
-\leavevmode\vadjust pre{\hypertarget{ref-britt2019reasoned}{}}%
-Britt, M. A., Rouet, J.-F., Blaum, D., \& Millis, K. (2019). A reasoned approach to dealing with fake news. \emph{Policy Insights from the Behavioral and Brain Sciences}, \emph{6}(1), 94--101.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brunell2017narcissism}{}}%
-Brunell, A. B., \& Buelow, M. T. (2017). Narcissism and performance on behavioral decision-making tasks. \emph{Journal of Behavioral Decision Making}, \emph{30}(1), 3--14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bryanov2021determinants}{}}%
-Bryanov, K., \& Vziatysheva, V. (2021). Determinants of individuals' belief in fake news: A scoping review determinants of belief in fake news. \emph{PLoS One}, \emph{16}(6), e0253717.
-
-\leavevmode\vadjust pre{\hypertarget{ref-buunk2002age}{}}%
-Buunk, B.
-P., Dijkstra, P., Fetchenhauer, D., \& Kenrick, D.
-T.
-(2002).
-Age and gender differences in mate selection criteria for various involvement levels.
-\emph{Personal Relationships}, \emph{9}(3), 271--278.
-
-\leavevmode\vadjust pre{\hypertarget{ref-calbi2017}{}}%
-Calbi, M., Heimann, K., Barratt, D., Siri, F., Umiltà, M.
-A., \& Gallese, V.
-(2017).
-How context influences our perception of emotional faces: A behavioral study on the kuleshov effect.
-\emph{Frontiers in Psychology}, \emph{8}.
+\bibitem[\citeproctext]{ref-abraham2009reality}
+Abraham, A., \& Von Cramon, D. Y. (2009). Reality= relevance? Insights
+from spontaneous modulations of the brain's default network when telling
+apart reality from fiction. \emph{PloS One}, \emph{4}(3), e4741.
+
+\bibitem[\citeproctext]{ref-ahadzadeh2021social}
+Ahadzadeh, A. S., Ong, F. S., \& Wu, S. L. (2021). Social media
+skepticism and belief in conspiracy theories about COVID-19: The
+moderating role of the dark triad. \emph{Current Psychology}, 1--13.
+
+\bibitem[\citeproctext]{ref-azevedo2020body}
+Azevedo, R., Tucciarelli, R., De Beuklaer, S., Ambroziak, K., Jones, I.,
+\& Tsakiris, M. (2020). \emph{A body of evidence:`feeling in
+seeing'predicts realness judgments for photojournalistic images.}
+
+\bibitem[\citeproctext]{ref-bago2022emotion}
+Bago, B., Rosenzweig, L. R., Berinsky, A. J., \& Rand, D. G. (2022).
+Emotion may predict susceptibility to fake news but emotion regulation
+does not seem to help. \emph{Cognition and Emotion}, 1--15.
+
+\bibitem[\citeproctext]{ref-bailey2021gender}
+Bailey, A. (2021). \emph{A gender in-group effect on facial recall}
+{[}PhD thesis{]}. University of Tasmania.
+
+\bibitem[\citeproctext]{ref-balas2017}
+Balas, B., \& Pacella, J. (2017). Trustworthiness perception is
+disrupted in artificial faces. \emph{Computers in Human Behavior},
+\emph{77}. \url{https://doi.org/10.1016/j.chb.2017.08.045}
+
+\bibitem[\citeproctext]{ref-bartosik2021you}
+Bartosik, B., Wojcik, G. M., Brzezicka, A., \& Kawiak, A. (2021). Are
+you able to trust me? Analysis of the relationships between personality
+traits and the assessment of attractiveness and trust. \emph{Frontiers
+in Human Neuroscience}, \emph{15}, 685530.
+
+\bibitem[\citeproctext]{ref-begg1992dissociation}
+Begg, I. M., Anas, A., \& Farinacci, S. (1992). Dissociation of
+processes in belief: Source recollection, statement familiarity, and the
+illusion of truth. \emph{Journal of Experimental Psychology: General},
+\emph{121}(4), 446.
+
+\bibitem[\citeproctext]{ref-berghel2018weaponizing}
+Berghel, H. (2018). Weaponizing twitter litter: Abuse-forming networks
+and social media. \emph{Computer}, \emph{51}(4), 70--73.
+
+\bibitem[\citeproctext]{ref-britt2019reasoned}
+Britt, M. A., Rouet, J.-F., Blaum, D., \& Millis, K. (2019). A reasoned
+approach to dealing with fake news. \emph{Policy Insights from the
+Behavioral and Brain Sciences}, \emph{6}(1), 94--101.
+
+\bibitem[\citeproctext]{ref-brunell2017narcissism}
+Brunell, A. B., \& Buelow, M. T. (2017). Narcissism and performance on
+behavioral decision-making tasks. \emph{Journal of Behavioral Decision
+Making}, \emph{30}(1), 3--14.
+
+\bibitem[\citeproctext]{ref-bryanov2021determinants}
+Bryanov, K., \& Vziatysheva, V. (2021). Determinants of individuals'
+belief in fake news: A scoping review determinants of belief in fake
+news. \emph{PLoS One}, \emph{16}(6), e0253717.
+
+\bibitem[\citeproctext]{ref-buunk2002age}
+Buunk, B. P., Dijkstra, P., Fetchenhauer, D., \& Kenrick, D. T. (2002).
+Age and gender differences in mate selection criteria for various
+involvement levels. \emph{Personal Relationships}, \emph{9}(3),
+271--278.
+
+\bibitem[\citeproctext]{ref-calbi2017}
+Calbi, M., Heimann, K., Barratt, D., Siri, F., Umiltà, M. A., \&
+Gallese, V. (2017). How context influences our perception of emotional
+faces: A behavioral study on the kuleshov effect. \emph{Frontiers in
+Psychology}, \emph{8}.
 \url{https://www.frontiersin.org/articles/10.3389/fpsyg.2017.01684}
 
-\leavevmode\vadjust pre{\hypertarget{ref-campbell2004narcissism}{}}%
-Campbell, W. K., Goodie, A. S., \& Foster, J. D. (2004). Narcissism, confidence, and risk attitude. \emph{Journal of Behavioral Decision Making}, \emph{17}(4), 297--311.
-
-\leavevmode\vadjust pre{\hypertarget{ref-carleton2007fearing}{}}%
-Carleton, R.
-N., Norton, M.
-P.
-J., \& Asmundson, G.
-J.
-(2007).
-Fearing the unknown: A short version of the intolerance of uncertainty scale.
+\bibitem[\citeproctext]{ref-campbell2004narcissism}
+Campbell, W. K., Goodie, A. S., \& Foster, J. D. (2004). Narcissism,
+confidence, and risk attitude. \emph{Journal of Behavioral Decision
+Making}, \emph{17}(4), 297--311.
+
+\bibitem[\citeproctext]{ref-carleton2007fearing}
+Carleton, R. N., Norton, M. P. J., \& Asmundson, G. J. (2007). Fearing
+the unknown: A short version of the intolerance of uncertainty scale.
 \emph{Journal of Anxiety Disorders}, \emph{21}(1), 105--117.
 
-\leavevmode\vadjust pre{\hypertarget{ref-carolan2017searching}{}}%
-Carolan, P.
-L.
-(2017).
-\emph{Searching {``inaffectively''}: A behavioral, psychometric, and electroencephalographic investigation of psychopathic personality and visual-spatial attention} {[}PhD thesis{]}.
+\bibitem[\citeproctext]{ref-carolan2017searching}
+Carolan, P. L. (2017). \emph{Searching {``inaffectively''}: A
+behavioral, psychometric, and electroencephalographic investigation of
+psychopathic personality and visual-spatial attention} {[}PhD thesis{]}.
 Arts \& Social Sciences: Department of Psychology.
 
-\leavevmode\vadjust pre{\hypertarget{ref-chatterjee2017master}{}}%
-Chatterjee, A., \& Pollock, T. G. (2017). Master of puppets: How narcissistic CEOs construct their professional worlds. \emph{Academy of Management Review}, \emph{42}(4), 703--725.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021broadening}{}}%
-Chen, J. M., Norman, J. B., \& Nam, Y. (2021). Broadening the stimulus set: Introducing the american multiracial faces database. \emph{Behavior Research Methods}, \emph{53}(1), 371--389.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2015news}{}}%
-Chen, Y., Conroy, N.
-K., \& Rubin, V.
-L.
-(2015).
-News in an online world: The need for an {``automatic crap detector.''} \emph{Proceedings of the Association for Information Science and Technology}, \emph{52}(1), 1--4.
-
-\leavevmode\vadjust pre{\hypertarget{ref-corvi2022detection}{}}%
-Corvi, R., Cozzolino, D., Zingarini, G., Poggi, G., Nagano, K., \& Verdoliva, L. (2022). On the detection of synthetic images generated by diffusion models. \emph{arXiv Preprint arXiv:2211.00680}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dawel2021systematic}{}}%
-Dawel, A., Miller, E. J., Horsburgh, A., \& Ford, P. (2021). A systematic survey of face stimuli used in psychological research 2000--2020. \emph{Behavior Research Methods}, 1--13.
-
-\leavevmode\vadjust pre{\hypertarget{ref-de2015jspsych}{}}%
-De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a web browser. \emph{Behavior Research Methods}, \emph{47}(1), 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ecker2022psychological}{}}%
-Ecker, U.
-K., Lewandowsky, S., Cook, J., Schmid, P., Fazio, L.
-K., Brashier, N., Kendeou, P., Vraga, E.
-K., \& Amazeen, M.
-A.
-(2022).
-The psychological drivers of misinformation belief and its resistance to correction.
-\emph{Nature Reviews Psychology}, \emph{1}(1), 13--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eddy2021self}{}}%
-Eddy, C. M. (2021). Self-serving social strategies: A systematic review of social cognition in narcissism. \emph{Current Psychology}, 1--19.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fink2006facial}{}}%
-Fink, B., Neave, N., Manning, J.
-T., \& Grammer, K.
-(2006).
-Facial symmetry and judgements of attractiveness, health and personality.
+\bibitem[\citeproctext]{ref-chatterjee2017master}
+Chatterjee, A., \& Pollock, T. G. (2017). Master of puppets: How
+narcissistic CEOs construct their professional worlds. \emph{Academy of
+Management Review}, \emph{42}(4), 703--725.
+
+\bibitem[\citeproctext]{ref-chen2021broadening}
+Chen, J. M., Norman, J. B., \& Nam, Y. (2021). Broadening the stimulus
+set: Introducing the american multiracial faces database. \emph{Behavior
+Research Methods}, \emph{53}(1), 371--389.
+
+\bibitem[\citeproctext]{ref-chen2015news}
+Chen, Y., Conroy, N. K., \& Rubin, V. L. (2015). News in an online
+world: The need for an {``automatic crap detector.''} \emph{Proceedings
+of the Association for Information Science and Technology},
+\emph{52}(1), 1--4.
+
+\bibitem[\citeproctext]{ref-corvi2022detection}
+Corvi, R., Cozzolino, D., Zingarini, G., Poggi, G., Nagano, K., \&
+Verdoliva, L. (2022). On the detection of synthetic images generated by
+diffusion models. \emph{arXiv Preprint arXiv:2211.00680}.
+
+\bibitem[\citeproctext]{ref-dawel2021systematic}
+Dawel, A., Miller, E. J., Horsburgh, A., \& Ford, P. (2021). A
+systematic survey of face stimuli used in psychological research
+2000--2020. \emph{Behavior Research Methods}, 1--13.
+
+\bibitem[\citeproctext]{ref-de2015jspsych}
+De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
+behavioral experiments in a web browser. \emph{Behavior Research
+Methods}, \emph{47}(1), 1--12.
+
+\bibitem[\citeproctext]{ref-ecker2022psychological}
+Ecker, U. K., Lewandowsky, S., Cook, J., Schmid, P., Fazio, L. K.,
+Brashier, N., Kendeou, P., Vraga, E. K., \& Amazeen, M. A. (2022). The
+psychological drivers of misinformation belief and its resistance to
+correction. \emph{Nature Reviews Psychology}, \emph{1}(1), 13--29.
+
+\bibitem[\citeproctext]{ref-eddy2021self}
+Eddy, C. M. (2021). Self-serving social strategies: A systematic review
+of social cognition in narcissism. \emph{Current Psychology}, 1--19.
+
+\bibitem[\citeproctext]{ref-fink2006facial}
+Fink, B., Neave, N., Manning, J. T., \& Grammer, K. (2006). Facial
+symmetry and judgements of attractiveness, health and personality.
 \emph{Personality and Individual Differences}, \emph{41}(3), 491--499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-fornells2015people}{}}%
-Fornells-Ambrojo, M., Freeman, D., Slater, M., Swapp, D., Antley, A., \& Barker, C.
-(2015).
-How do people with persecutory delusions evaluate threat in a controlled social environment?
-A qualitative study using virtual reality.
-\emph{Behavioural and Cognitive Psychotherapy}, \emph{43}(1), 89--107.
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2005psychology}{}}%
-Freeman, D., Garety, P.
-A., Bebbington, P., Slater, M., Kuipers, E., Fowler, D., Green, C., Jordan, J., Ray, K., \& Dunn, G.
-(2005).
-The psychology of persecutory ideation II: A virtual reality experimental study.
-\emph{The Journal of Nervous and Mental Disease}, \emph{193}(5), 309--315.
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2021revised}{}}%
-Freeman, D., Loe, B.
-S., Kingdon, D., Startup, H., Molodynski, A., Rosebrock, L., Brown, P., Sheaves, B., Waite, F., \& Bird, J.
-C.
-(2021).
-The revised green et al., paranoid thoughts scale (r-GPTS): Psychometric properties, severity ranges, and clinical cut-offs.
-\emph{Psychological Medicine}, \emph{51}(2), 244--253.
-
-\leavevmode\vadjust pre{\hypertarget{ref-freeman2003can}{}}%
-Freeman, D., Slater, M., Bebbington, P.
-E., Garety, P.
-A., Kuipers, E., Fowler, D., Met, A., Read, C.
-M., Jordan, J., \& Vinayagamoorthy, V.
-(2003).
-Can virtual reality be used to investigate persecutory ideation?
-\emph{The Journal of Nervous and Mental Disease}, \emph{191}(8), 509--514.
-
-\leavevmode\vadjust pre{\hypertarget{ref-garrido2017kdef}{}}%
-Garrido, M. V., \& Prada, M. (2017). KDEF-PT: Valence, emotional intensity, familiarity and attractiveness ratings of angry, neutral, and happy faces. \emph{Frontiers in Psychology}, \emph{8}, 2181.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gobbini2013prioritized}{}}%
-Gobbini, M.
-I., Gors, J.
-D., Halchenko, Y.
-O., Rogers, C., Guntupalli, J.
-S., Hughes, H., \& Cipolli, C.
-(2013).
-Prioritized detection of personally familiar faces.
-\emph{PloS One}, \emph{8}(6), e66620.
-
-\leavevmode\vadjust pre{\hypertarget{ref-goldstein2009pleasure}{}}%
-Goldstein, T.
-R.
-(2009).
-The pleasure of unadulterated sadness: Experiencing sorrow in fiction, nonfiction, and" in person.".
-\emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4), 232.
-
-\leavevmode\vadjust pre{\hypertarget{ref-grapsas2020and}{}}%
-Grapsas, S., Brummelman, E., Back, M.
-D., \& Denissen, J.
-J.
-(2020).
-The {``why''} and {``how''} of narcissism: A process model of narcissistic status pursuit.
-\emph{Perspectives on Psychological Science}, \emph{15}(1), 150--172.
-
-\leavevmode\vadjust pre{\hypertarget{ref-han2018beauty}{}}%
-Han, S., Li, Y., Liu, S., Xu, Q., Tan, Q., \& Zhang, L.
-(2018).
-Beauty is in the eye of the beholder: The halo effect and generalization effect in the facial attractiveness evaluation.
-\emph{Acta Psychologica Sinica}, \emph{50}(4), 363.
-
-\leavevmode\vadjust pre{\hypertarget{ref-herbst2020gender}{}}%
-Herbst, T.
-H.
-(2020).
-Gender differences in self-perception accuracy: The confidence gap and women leaders' underrepresentation in academia.
+\bibitem[\citeproctext]{ref-fornells2015people}
+Fornells-Ambrojo, M., Freeman, D., Slater, M., Swapp, D., Antley, A., \&
+Barker, C. (2015). How do people with persecutory delusions evaluate
+threat in a controlled social environment? A qualitative study using
+virtual reality. \emph{Behavioural and Cognitive Psychotherapy},
+\emph{43}(1), 89--107.
+
+\bibitem[\citeproctext]{ref-freeman2005psychology}
+Freeman, D., Garety, P. A., Bebbington, P., Slater, M., Kuipers, E.,
+Fowler, D., Green, C., Jordan, J., Ray, K., \& Dunn, G. (2005). The
+psychology of persecutory ideation II: A virtual reality experimental
+study. \emph{The Journal of Nervous and Mental Disease}, \emph{193}(5),
+309--315.
+
+\bibitem[\citeproctext]{ref-freeman2021revised}
+Freeman, D., Loe, B. S., Kingdon, D., Startup, H., Molodynski, A.,
+Rosebrock, L., Brown, P., Sheaves, B., Waite, F., \& Bird, J. C. (2021).
+The revised green et al., paranoid thoughts scale (r-GPTS): Psychometric
+properties, severity ranges, and clinical cut-offs. \emph{Psychological
+Medicine}, \emph{51}(2), 244--253.
+
+\bibitem[\citeproctext]{ref-freeman2003can}
+Freeman, D., Slater, M., Bebbington, P. E., Garety, P. A., Kuipers, E.,
+Fowler, D., Met, A., Read, C. M., Jordan, J., \& Vinayagamoorthy, V.
+(2003). Can virtual reality be used to investigate persecutory ideation?
+\emph{The Journal of Nervous and Mental Disease}, \emph{191}(8),
+509--514.
+
+\bibitem[\citeproctext]{ref-garrido2017kdef}
+Garrido, M. V., \& Prada, M. (2017). KDEF-PT: Valence, emotional
+intensity, familiarity and attractiveness ratings of angry, neutral, and
+happy faces. \emph{Frontiers in Psychology}, \emph{8}, 2181.
+
+\bibitem[\citeproctext]{ref-gobbini2013prioritized}
+Gobbini, M. I., Gors, J. D., Halchenko, Y. O., Rogers, C., Guntupalli,
+J. S., Hughes, H., \& Cipolli, C. (2013). Prioritized detection of
+personally familiar faces. \emph{PloS One}, \emph{8}(6), e66620.
+
+\bibitem[\citeproctext]{ref-goldstein2009pleasure}
+Goldstein, T. R. (2009). The pleasure of unadulterated sadness:
+Experiencing sorrow in fiction, nonfiction, and" in person.".
+\emph{Psychology of Aesthetics, Creativity, and the Arts}, \emph{3}(4),
+232.
+
+\bibitem[\citeproctext]{ref-grapsas2020and}
+Grapsas, S., Brummelman, E., Back, M. D., \& Denissen, J. J. (2020). The
+{``why''} and {``how''} of narcissism: A process model of narcissistic
+status pursuit. \emph{Perspectives on Psychological Science},
+\emph{15}(1), 150--172.
+
+\bibitem[\citeproctext]{ref-han2018beauty}
+Han, S., Li, Y., Liu, S., Xu, Q., Tan, Q., \& Zhang, L. (2018). Beauty
+is in the eye of the beholder: The halo effect and generalization effect
+in the facial attractiveness evaluation. \emph{Acta Psychologica
+Sinica}, \emph{50}(4), 363.
+
+\bibitem[\citeproctext]{ref-herbst2020gender}
+Herbst, T. H. (2020). Gender differences in self-perception accuracy:
+The confidence gap and women leaders' underrepresentation in academia.
 \emph{SA Journal of Industrial Psychology}, \emph{46}(1), 1--8.
 
-\leavevmode\vadjust pre{\hypertarget{ref-hodson2018dark}{}}%
-Hodson, G., Book, A., Visser, B.
-A., Volk, A.
-A., Ashton, M.
-C., \& Lee, K.
-(2018).
-Is the dark triad common factor distinct from low honesty-humility?
-\emph{Journal of Research in Personality}, \emph{73}, 123--129.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoogers2021effect}{}}%
-Hoogers, E. (2021). \emph{The effect of attitude towards computer generated faces on face perception} {[}\{B.S.\} thesis{]}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hou2019survival}{}}%
-Hou, C., \& Liu, Z.
-(2019).
-The survival processing advantage of face: The memorization of the (un) trustworthy face contributes more to survival adaptation.
-\emph{Evolutionary Psychology}, \emph{17}(2), 1474704919839726.
-
-\leavevmode\vadjust pre{\hypertarget{ref-indovina2007dissociation}{}}%
-Indovina, I., \& Macaluso, E. (2007). Dissociation of stimulus relevance and saliency factors during shifts of visuospatial attention. \emph{Cerebral Cortex}, \emph{17}(7), 1701--1711.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jauk2022validation}{}}%
-Jauk, E., Olaru, G., Schürch, E., Back, M.
-D., \& Morf, C.
-C.
-(2022).
-Validation of the german five-factor narcissism inventory and construction of a brief form using ant colony optimization.
+\bibitem[\citeproctext]{ref-hodson2018dark}
+Hodson, G., Book, A., Visser, B. A., Volk, A. A., Ashton, M. C., \& Lee,
+K. (2018). Is the dark triad common factor distinct from low
+honesty-humility? \emph{Journal of Research in Personality}, \emph{73},
+123--129.
+
+\bibitem[\citeproctext]{ref-hoogers2021effect}
+Hoogers, E. (2021). \emph{The effect of attitude towards computer
+generated faces on face perception} {[}\{B.S.\} thesis{]}.
+
+\bibitem[\citeproctext]{ref-hou2019survival}
+Hou, C., \& Liu, Z. (2019). The survival processing advantage of face:
+The memorization of the (un) trustworthy face contributes more to
+survival adaptation. \emph{Evolutionary Psychology}, \emph{17}(2),
+1474704919839726.
+
+\bibitem[\citeproctext]{ref-indovina2007dissociation}
+Indovina, I., \& Macaluso, E. (2007). Dissociation of stimulus relevance
+and saliency factors during shifts of visuospatial attention.
+\emph{Cerebral Cortex}, \emph{17}(7), 1701--1711.
+
+\bibitem[\citeproctext]{ref-jauk2022validation}
+Jauk, E., Olaru, G., Schürch, E., Back, M. D., \& Morf, C. C. (2022).
+Validation of the german five-factor narcissism inventory and
+construction of a brief form using ant colony optimization.
 \emph{Assessment}, 10731911221075761.
 
-\leavevmode\vadjust pre{\hypertarget{ref-king2017paranoia}{}}%
-King, A., \& Dudley, R.
-(2017).
-Paranoia, worry, cognitive avoidance and intolerance of uncertainty in a student population.
-\emph{Journal of Applied Psychology and Social Science}, \emph{3}(2), 70--89.
-
-\leavevmode\vadjust pre{\hypertarget{ref-levidi2022understanding}{}}%
-Levidi, M.
-D.
-C., McGrath, A., Kyriakoulis, P., \& Sulikowski, D.
-(2022).
-Understanding criminal decision-making: Links between honesty-humility, perceived risk and negative affect: Psychology, crime \& law.
-\emph{Psychology, Crime and Law}, 1--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2017beyond}{}}%
-Lewandowsky, S., Ecker, U.
-K., \& Cook, J.
-(2017).
-Beyond misinformation: Understanding and coping with the {``post-truth''} era.
-\emph{Journal of Applied Research in Memory and Cognition}, \emph{6}(4), 353--369.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewin2002sex}{}}%
-Lewin, C., \& Herlitz, A. (2002). Sex differences in face recognition---women's faces make the difference. \emph{Brain and Cognition}, \emph{50}(1), 121--128.
-
-\leavevmode\vadjust pre{\hypertarget{ref-liefooghe2022faces}{}}%
-Liefooghe, B., Oliveira, M., Leisten, L. M., Hoogers, E., Aarts, H., \& Hortensius, R. (2022). \emph{Faces merely labelled as artificial are trusted less}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-little2011facial}{}}%
-Little, A.
-C., Jones, B.
-C., \& DeBruine, L.
-M.
-(2011).
-Facial attractiveness: Evolutionary based research.
-\emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{366}(1571), 1638--1659.
-
-\leavevmode\vadjust pre{\hypertarget{ref-littrell2020overconfidently}{}}%
-Littrell, S., Fugelsang, J., \& Risko, E. F. (2020). Overconfidently underthinking: Narcissism negatively predicts cognitive reflection. \emph{Thinking \& Reasoning}, \emph{26}(3), 352--380.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lou2015perceptual}{}}%
-Lou, B., Hsu, W.-Y., \& Sajda, P.
-(2015).
-Perceptual salience and reward both influence feedback-related neural activity arising from choice.
+\bibitem[\citeproctext]{ref-king2017paranoia}
+King, A., \& Dudley, R. (2017). Paranoia, worry, cognitive avoidance and
+intolerance of uncertainty in a student population. \emph{Journal of
+Applied Psychology and Social Science}, \emph{3}(2), 70--89.
+
+\bibitem[\citeproctext]{ref-levidi2022understanding}
+Levidi, M. D. C., McGrath, A., Kyriakoulis, P., \& Sulikowski, D.
+(2022). Understanding criminal decision-making: Links between
+honesty-humility, perceived risk and negative affect: Psychology, crime
+\& law. \emph{Psychology, Crime and Law}, 1--29.
+
+\bibitem[\citeproctext]{ref-lewandowsky2017beyond}
+Lewandowsky, S., Ecker, U. K., \& Cook, J. (2017). Beyond
+misinformation: Understanding and coping with the {``post-truth''} era.
+\emph{Journal of Applied Research in Memory and Cognition}, \emph{6}(4),
+353--369.
+
+\bibitem[\citeproctext]{ref-lewin2002sex}
+Lewin, C., \& Herlitz, A. (2002). Sex differences in face
+recognition---women's faces make the difference. \emph{Brain and
+Cognition}, \emph{50}(1), 121--128.
+
+\bibitem[\citeproctext]{ref-liefooghe2022faces}
+Liefooghe, B., Oliveira, M., Leisten, L. M., Hoogers, E., Aarts, H., \&
+Hortensius, R. (2022). \emph{Faces merely labelled as artificial are
+trusted less}.
+
+\bibitem[\citeproctext]{ref-little2011facial}
+Little, A. C., Jones, B. C., \& DeBruine, L. M. (2011). Facial
+attractiveness: Evolutionary based research. \emph{Philosophical
+Transactions of the Royal Society B: Biological Sciences},
+\emph{366}(1571), 1638--1659.
+
+\bibitem[\citeproctext]{ref-littrell2020overconfidently}
+Littrell, S., Fugelsang, J., \& Risko, E. F. (2020). Overconfidently
+underthinking: Narcissism negatively predicts cognitive reflection.
+\emph{Thinking \& Reasoning}, \emph{26}(3), 352--380.
+
+\bibitem[\citeproctext]{ref-liu2020honesty}
+Liu, J., Zettler, I., \& Hilbig, B. E. (2020). Honesty-humility.
+\emph{Encyclopedia of Personality and Individual Differences},
+1996--2004.
+
+\bibitem[\citeproctext]{ref-lou2015perceptual}
+Lou, B., Hsu, W.-Y., \& Sajda, P. (2015). Perceptual salience and reward
+both influence feedback-related neural activity arising from choice.
 \emph{Journal of Neuroscience}, \emph{35}(38), 13064--13075.
 
-\leavevmode\vadjust pre{\hypertarget{ref-parametersArticle}{}}%
-Lüdecke, D., Ben-Shachar, M., Patil, I., \& Makowski, D.
-(2020).
-Extracting, computing and exploring the parameters of statistical models using {R}.
-\emph{Journal of Open Source Software}, \emph{5}(53), 2445.
+\bibitem[\citeproctext]{ref-parametersArticle}
+Lüdecke, D., Ben-Shachar, M., Patil, I., \& Makowski, D. (2020).
+Extracting, computing and exploring the parameters of statistical models
+using {R}. \emph{Journal of Open Source Software}, \emph{5}(53), 2445.
 \url{https://doi.org/10.21105/joss.02445}
 
-\leavevmode\vadjust pre{\hypertarget{ref-performanceArticle}{}}%
+\bibitem[\citeproctext]{ref-performanceArticle}
 Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., \& Makowski, D.
-(2021).
-{performance}: An {R} package for assessment, comparison and testing of statistical models.
-\emph{Journal of Open Source Software}, \emph{6}(60), 3139.
-\url{https://doi.org/10.21105/joss.03139}
-
-\leavevmode\vadjust pre{\hypertarget{ref-insightArticle}{}}%
-Lüdecke, D., Waggoner, P., \& Makowski, D.
-(2019).
-Insight: A unified interface to access information from model objects in {R}.
-\emph{Journal of Open Source Software}, \emph{4}(38), 1412.
+(2021). {performance}: An {R} package for assessment, comparison and
+testing of statistical models. \emph{Journal of Open Source Software},
+\emph{6}(60), 3139. \url{https://doi.org/10.21105/joss.03139}
+
+\bibitem[\citeproctext]{ref-insightArticle}
+Lüdecke, D., Waggoner, P., \& Makowski, D. (2019). Insight: A unified
+interface to access information from model objects in {R}. \emph{Journal
+of Open Source Software}, \emph{4}(38), 1412.
 \url{https://doi.org/10.21105/joss.01412}
 
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2018cognitive}{}}%
-Makowski, D. (2018). \emph{Cognitive neuropsychology of implicit emotion regulation through fictional reappraisal} {[}PhD thesis{]}. Sorbonne Paris Cit{é}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2023affective}{}}%
-Makowski, D. (2023). How do we know what is real? The 'affective reality theory'. In \emph{Dr Dominique Makowski}. \url{https://dominiquemakowski.github.io/post/2023-04-11-affectivereality/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bayestestRArticle}{}}%
-Makowski, D., Ben-Shachar, M., \& Lüdecke, D.
-(2019).
-{bayestestR}: Describing effects and their uncertainty, existence and significance within the {Bayesian} framework.
-\emph{Journal of Open Source Software}, \emph{4}(40), 1541.
-\url{https://doi.org/10.21105/joss.01541}
-
-\leavevmode\vadjust pre{\hypertarget{ref-correlationArticle}{}}%
-Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D.
-(2020).
-Methods and algorithms for correlation analysis in {R}.
-\emph{Journal of Open Source Software}, \emph{5}(51), 2306.
+\bibitem[\citeproctext]{ref-makowski2018cognitive}
+Makowski, D. (2018). \emph{Cognitive neuropsychology of implicit emotion
+regulation through fictional reappraisal} {[}PhD thesis{]}. Sorbonne
+Paris Cit{é}.
+
+\bibitem[\citeproctext]{ref-makowski2023affective}
+Makowski, D. (2023). How do we know what is real? The 'affective reality
+theory'. In \emph{Dr Dominique Makowski}.
+\url{https://dominiquemakowski.github.io/post/2023-04-11-affectivereality/}
+
+\bibitem[\citeproctext]{ref-bayestestRArticle}
+Makowski, D., Ben-Shachar, M., \& Lüdecke, D. (2019). {bayestestR}:
+Describing effects and their uncertainty, existence and significance
+within the {Bayesian} framework. \emph{Journal of Open Source Software},
+\emph{4}(40), 1541. \url{https://doi.org/10.21105/joss.01541}
+
+\bibitem[\citeproctext]{ref-correlationArticle}
+Makowski, D., Ben-Shachar, M., Patil, I., \& Lüdecke, D. (2020). Methods
+and algorithms for correlation analysis in {R}. \emph{Journal of Open
+Source Software}, \emph{5}(51), 2306.
 \url{https://doi.org/10.21105/joss.02306}
 
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2017being}{}}%
-Makowski, D., Sperduti, M., Nicolas, S., \& Piolino, P. (2017). {``Being there''} and remembering it: Presence improves memory encoding. \emph{Consciousness and Cognition}, \emph{53}, 194--202.
-
-\leavevmode\vadjust pre{\hypertarget{ref-makowski2019phenomenal}{}}%
-Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
-(2019).
-Phenomenal, bodily and brain correlates of fictional reappraisal as an implicit emotion regulation strategy.
-\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 877--897.
-
-\leavevmode\vadjust pre{\hypertarget{ref-marcinkowska2021self}{}}%
-Marcinkowska, U.
-M., Jones, B.
-C., \& Lee, A.
-J.
-(2021).
-Self-rated attractiveness predicts preferences for sexually dimorphic facial characteristics in a culturally diverse sample.
-\emph{Scientific Reports}, \emph{11}(1), 1--8.
-
-\leavevmode\vadjust pre{\hypertarget{ref-martel2020reliance}{}}%
-Martel, C., Pennycook, G., \& Rand, D. G. (2020). Reliance on emotion promotes belief in fake news. \emph{Cognitive Research: Principles and Implications}, \emph{5}(1), 1--20.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcdonnell2010face}{}}%
-McDonnell, R., \& Breidt, M. (2010). Face reality: Investigating the uncanny valley for virtual faces. In \emph{ACM SIGGRAPH ASIA 2010 sketches} (pp. 1--2).
-
-\leavevmode\vadjust pre{\hypertarget{ref-michael2021source}{}}%
-Michael, R. B., \& Sanson, M. (2021). Source information affects interpretations of the news across multiple age groups in the united states. \emph{Societies}, \emph{11}(4), 119.
-
-\leavevmode\vadjust pre{\hypertarget{ref-mishra2019gender}{}}%
-Mishra, M.
-V., Likitlersuang, J., B Wilmer, J., Cohan, S., Germine, L., \& DeGutis, J.
-M.
-(2019).
-Gender differences in familiar face recognition and the influence of sociocultural gender inequality.
+\bibitem[\citeproctext]{ref-makowski2017being}
+Makowski, D., Sperduti, M., Nicolas, S., \& Piolino, P. (2017). {``Being
+there''} and remembering it: Presence improves memory encoding.
+\emph{Consciousness and Cognition}, \emph{53}, 194--202.
+
+\bibitem[\citeproctext]{ref-makowski2019phenomenal}
+Makowski, D., Sperduti, M., Pelletier, J., Blondé, P., La Corte, V.,
+Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., et al.
+(2019). Phenomenal, bodily and brain correlates of fictional reappraisal
+as an implicit emotion regulation strategy. \emph{Cognitive, Affective,
+\& Behavioral Neuroscience}, \emph{19}(4), 877--897.
+
+\bibitem[\citeproctext]{ref-marcinkowska2021self}
+Marcinkowska, U. M., Jones, B. C., \& Lee, A. J. (2021). Self-rated
+attractiveness predicts preferences for sexually dimorphic facial
+characteristics in a culturally diverse sample. \emph{Scientific
+Reports}, \emph{11}(1), 1--8.
+
+\bibitem[\citeproctext]{ref-martel2020reliance}
+Martel, C., Pennycook, G., \& Rand, D. G. (2020). Reliance on emotion
+promotes belief in fake news. \emph{Cognitive Research: Principles and
+Implications}, \emph{5}(1), 1--20.
+
+\bibitem[\citeproctext]{ref-mcdonnell2010face}
+McDonnell, R., \& Breidt, M. (2010). Face reality: Investigating the
+uncanny valley for virtual faces. In \emph{ACM SIGGRAPH ASIA 2010
+sketches} (pp. 1--2).
+
+\bibitem[\citeproctext]{ref-michael2021source}
+Michael, R. B., \& Sanson, M. (2021). Source information affects
+interpretations of the news across multiple age groups in the united
+states. \emph{Societies}, \emph{11}(4), 119.
+
+\bibitem[\citeproctext]{ref-miller2023}
+Miller, E. J., Steward, B. A., Witkower, Z., Sutherland, C. A.,
+Krumhuber, E. G., \& Dawel, A. (2023). AI hyperrealism: Why AI faces are
+perceived as more real than human ones. \emph{Psychological Science},
+\emph{34}(12), 1390--1403.
+
+\bibitem[\citeproctext]{ref-mishra2019gender}
+Mishra, M. V., Likitlersuang, J., B Wilmer, J., Cohan, S., Germine, L.,
+\& DeGutis, J. M. (2019). Gender differences in familiar face
+recognition and the influence of sociocultural gender inequality.
 \emph{Scientific Reports}, \emph{9}(1), 1--12.
 
-\leavevmode\vadjust pre{\hypertarget{ref-moshel2022}{}}%
-Moshel, M.
-L., Robinson, A.
-K., Carlson, T.
-A., \& Grootswagers, T.
-(2022).
-Are you for real?
-Decoding realistic AI-generated faces from neural activity.
-\emph{Vision Research}, \emph{199}, 108079.
+\bibitem[\citeproctext]{ref-moshel2022}
+Moshel, M. L., Robinson, A. K., Carlson, T. A., \& Grootswagers, T.
+(2022). Are you for real? Decoding realistic AI-generated faces from
+neural activity. \emph{Vision Research}, \emph{199}, 108079.
 \url{https://doi.org/10.1016/j.visres.2022.108079}
 
-\leavevmode\vadjust pre{\hypertarget{ref-nightingale2022}{}}%
-Nightingale, S.
-J., \& Farid, H.
-(2022).
-AI-synthesized faces are indistinguishable from real faces and more trustworthy.
-\emph{Proceedings of the National Academy of Sciences}, \emph{119}(8), e2120481119.
-\url{https://doi.org/10.1073/pnas.2120481119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-o2021grandiose}{}}%
-O'Reilly, C.
-A., \& Hall, N.
-(2021).
-Grandiose narcissists and decision making: Impulsive, overconfident, and skeptical of experts--but seldom in doubt.
-\emph{Personality and Individual Differences}, \emph{168}, 110280.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pantserev2020}{}}%
-Pantserev, K.
-(2020).
-\emph{The malicious use of AI-based deepfake technology as the new threat to psychological security and political stability} (pp.
-37--55).
+\bibitem[\citeproctext]{ref-nightingale2022}
+Nightingale, S. J., \& Farid, H. (2022). AI-synthesized faces are
+indistinguishable from real faces and more trustworthy.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(8),
+e2120481119. \url{https://doi.org/10.1073/pnas.2120481119}
+
+\bibitem[\citeproctext]{ref-o2021grandiose}
+O'Reilly, C. A., \& Hall, N. (2021). Grandiose narcissists and decision
+making: Impulsive, overconfident, and skeptical of experts--but seldom
+in doubt. \emph{Personality and Individual Differences}, \emph{168},
+110280.
+
+\bibitem[\citeproctext]{ref-pantserev2020}
+Pantserev, K. (2020). \emph{The malicious use of AI-based deepfake
+technology as the new threat to psychological security and political
+stability} (pp. 37--55).
 \url{https://doi.org/10.1007/978-3-030-35746-7_3}
 
-\leavevmode\vadjust pre{\hypertarget{ref-peer2022}{}}%
-Peer, E., Rothschild, D., Gordon, A., Evernden, Z., \& Damer, E.
-(2022).
+\bibitem[\citeproctext]{ref-peer2022}
+Peer, E., Rothschild, D., Gordon, A., Evernden, Z., \& Damer, E. (2022).
 Data quality of platforms and panels for online behavioral research.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pehlivanoglu2021role}{}}%
-Pehlivanoglu, D., Lin, T., Deceus, F., Heemskerk, A., Ebner, N.
-C., \& Cahill, B.
-S.
-(2021).
-The role of analytical reasoning and source credibility on the evaluation of real and fake full-length news articles.
-\emph{Cognitive Research: Principles and Implications}, \emph{6}(1), 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pennycook2019lazy}{}}%
-Pennycook, G., \& Rand, D. G. (2019). Lazy, not biased: Susceptibility to partisan fake news is better explained by lack of reasoning than by motivated reasoning. \emph{Cognition}, \emph{188}, 39--50.
-
-\leavevmode\vadjust pre{\hypertarget{ref-peters2012development}{}}%
-Peters, L., Sunderland, M., Andrews, G., Rapee, R.
-M., \& Mattick, R.
-P.
-(2012).
-Development of a short form social interaction anxiety (SIAS) and social phobia scale (SPS) using nonparametric item response theory: The SIAS-6 and the SPS-6.
-\emph{Psychological Assessment}, \emph{24}(1), 66.
-
-\leavevmode\vadjust pre{\hypertarget{ref-petty1986elaboration}{}}%
-Petty, R. E., \& Cacioppo, J. T. (1986). The elaboration likelihood model of persuasion. In \emph{Communication and persuasion} (pp. 1--24). Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-piksa2022cognitive}{}}%
+\bibitem[\citeproctext]{ref-pehlivanoglu2021role}
+Pehlivanoglu, D., Lin, T., Deceus, F., Heemskerk, A., Ebner, N. C., \&
+Cahill, B. S. (2021). The role of analytical reasoning and source
+credibility on the evaluation of real and fake full-length news
+articles. \emph{Cognitive Research: Principles and Implications},
+\emph{6}(1), 1--12.
+
+\bibitem[\citeproctext]{ref-pennycook2019lazy}
+Pennycook, G., \& Rand, D. G. (2019). Lazy, not biased: Susceptibility
+to partisan fake news is better explained by lack of reasoning than by
+motivated reasoning. \emph{Cognition}, \emph{188}, 39--50.
+
+\bibitem[\citeproctext]{ref-peters2012development}
+Peters, L., Sunderland, M., Andrews, G., Rapee, R. M., \& Mattick, R. P.
+(2012). Development of a short form social interaction anxiety (SIAS)
+and social phobia scale (SPS) using nonparametric item response theory:
+The SIAS-6 and the SPS-6. \emph{Psychological Assessment}, \emph{24}(1),
+66.
+
+\bibitem[\citeproctext]{ref-petty1986elaboration}
+Petty, R. E., \& Cacioppo, J. T. (1986). The elaboration likelihood
+model of persuasion. In \emph{Communication and persuasion} (pp. 1--24).
+Springer.
+
+\bibitem[\citeproctext]{ref-piksa2022cognitive}
 Piksa, M., Noworyta, K., Piasecki, J., Gwiazdzinski, P., Gundersen, A.
-B., Kunst, J., \& Rygula, R.
-(2022).
-Cognitive processes and personality traits underlying four phenotypes of susceptibility to (mis) information.
-\emph{Frontiers in Psychiatry}, 1142.
-
-\leavevmode\vadjust pre{\hypertarget{ref-qi2022gender}{}}%
-Qi, Y., \& Ying, J. (2022). Gender biases in the accuracy of facial judgments: Facial attractiveness and perceived socioeconomic status. \emph{Frontiers in Psychology}, \emph{13}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
-R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rhodes2006evolutionary}{}}%
-Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty. \emph{Annual Review of Psychology}, \emph{57}, 199.
-
-\leavevmode\vadjust pre{\hypertarget{ref-said2022artificial}{}}%
-Said, N., Potinteu, A.-E., Brich, I., Buder, J., Schumm, H., \& Huff, M. (2022). \emph{An artificial intelligence perspective: How knowledge and confidence shape risk and opportunity perception}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanchez2005presence}{}}%
-Sanchez-Vives, M. V., \& Slater, M. (2005). From presence to consciousness through virtual reality. \emph{Nature Reviews Neuroscience}, \emph{6}(4), 332--339.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schepman2020initial}{}}%
-Schepman, A., \& Rodway, P. (2020). Initial validation of the general attitudes towards artificial intelligence scale. \emph{Computers in Human Behavior Reports}, \emph{1}, 100014.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sibley2011}{}}%
-Sibley, C., Luyten, N., Wolfman, M., Mobberley, A., Wootton, L.
-W., Hammond, M., Sengupta, N., Perry, R., West-Newman, T., Wilson, M., McLellan, L., Hoverd, W.
-J., \& Robertson, A.
-(2011).
-The mini-IPIP6: Validation and extension of a short measure of the big-six factors of personality in new zealand.
-\emph{New Zealand Journal of Psychology}, \emph{40}, 142--159.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sindermann2020short}{}}%
-Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on susceptibility to falling for fake political news. \emph{Current Opinion in Psychology}, \emph{36}, 44--48.
-
-\leavevmode\vadjust pre{\hypertarget{ref-skora2022functional}{}}%
-Skora, L., Livermore, J., \& Roelofs, K. (2022). The functional role of cardiac activity in perception and action. \emph{Neuroscience \& Biobehavioral Reviews}, 104655.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sobieraj2014beautiful}{}}%
-Sobieraj, S., \& Krämer, N. C. (2014). What is beautiful in cyberspace? Communication with attractive avatars. \emph{International Conference on Social Computing and Social Media}, 125--136.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sommer2013sex}{}}%
-Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A., \& Wilhelm, O. (2013). Sex differences in face cognition. \emph{Acta Psychologica}, \emph{142}(1), 62--73.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sperduti2016paradox}{}}%
-Sperduti, M., Arcangeli, M., Makowski, D., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
-(2016).
-The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance.
-\emph{Acta Psychologica}, \emph{165}, 53--59.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sperduti2017distinctive}{}}%
-Sperduti, M., Makowski, D., Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P.
-(2017).
-The distinctive role of executive functions in implicit emotion regulation.
+B., Kunst, J., \& Rygula, R. (2022). Cognitive processes and personality
+traits underlying four phenotypes of susceptibility to (mis)
+information. \emph{Frontiers in Psychiatry}, 1142.
+
+\bibitem[\citeproctext]{ref-qi2022gender}
+Qi, Y., \& Ying, J. (2022). Gender biases in the accuracy of facial
+judgments: Facial attractiveness and perceived socioeconomic status.
+\emph{Frontiers in Psychology}, \emph{13}.
+
+\bibitem[\citeproctext]{ref-RCoreTeam2022}
+R Core Team. (2022). \emph{R: A language and environment for statistical
+computing}. R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}
+
+\bibitem[\citeproctext]{ref-rhodes2006evolutionary}
+Rhodes, G. et al. (2006). The evolutionary psychology of facial beauty.
+\emph{Annual Review of Psychology}, \emph{57}, 199.
+
+\bibitem[\citeproctext]{ref-said2022artificial}
+Said, N., Potinteu, A.-E., Brich, I., Buder, J., Schumm, H., \& Huff, M.
+(2022). \emph{An artificial intelligence perspective: How knowledge and
+confidence shape risk and opportunity perception}.
+
+\bibitem[\citeproctext]{ref-sanchez2005presence}
+Sanchez-Vives, M. V., \& Slater, M. (2005). From presence to
+consciousness through virtual reality. \emph{Nature Reviews
+Neuroscience}, \emph{6}(4), 332--339.
+
+\bibitem[\citeproctext]{ref-schepman2020initial}
+Schepman, A., \& Rodway, P. (2020). Initial validation of the general
+attitudes towards artificial intelligence scale. \emph{Computers in
+Human Behavior Reports}, \emph{1}, 100014.
+
+\bibitem[\citeproctext]{ref-sibley2011}
+Sibley, C., Luyten, N., Wolfman, M., Mobberley, A., Wootton, L. W.,
+Hammond, M., Sengupta, N., Perry, R., West-Newman, T., Wilson, M.,
+McLellan, L., Hoverd, W. J., \& Robertson, A. (2011). The mini-IPIP6:
+Validation and extension of a short measure of the big-six factors of
+personality in new zealand. \emph{New Zealand Journal of Psychology},
+\emph{40}, 142--159.
+
+\bibitem[\citeproctext]{ref-sindermann2020short}
+Sindermann, C., Cooper, A., \& Montag, C. (2020). A short review on
+susceptibility to falling for fake political news. \emph{Current Opinion
+in Psychology}, \emph{36}, 44--48.
+
+\bibitem[\citeproctext]{ref-skora2022functional}
+Skora, L., Livermore, J., \& Roelofs, K. (2022). The functional role of
+cardiac activity in perception and action. \emph{Neuroscience \&
+Biobehavioral Reviews}, 104655.
+
+\bibitem[\citeproctext]{ref-sobieraj2014beautiful}
+Sobieraj, S., \& Krämer, N. C. (2014). What is beautiful in cyberspace?
+Communication with attractive avatars. \emph{International Conference on
+Social Computing and Social Media}, 125--136.
+
+\bibitem[\citeproctext]{ref-sommer2013sex}
+Sommer, W., Hildebrandt, A., Kunina-Habenicht, O., Schacht, A., \&
+Wilhelm, O. (2013). Sex differences in face cognition. \emph{Acta
+Psychologica}, \emph{142}(1), 62--73.
+
+\bibitem[\citeproctext]{ref-sperduti2016paradox}
+Sperduti, M., Arcangeli, M., Makowski, D., Wantzen, P., Zalla, T.,
+Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P. (2016). The
+paradox of fiction: Emotional response toward fiction and the modulatory
+role of self-relevance. \emph{Acta Psychologica}, \emph{165}, 53--59.
+
+\bibitem[\citeproctext]{ref-sperduti2017distinctive}
+Sperduti, M., Makowski, D., Arcangeli, M., Wantzen, P., Zalla, T.,
+Lemaire, S., Dokic, J., Pelletier, J., \& Piolino, P. (2017). The
+distinctive role of executive functions in implicit emotion regulation.
 \emph{Acta Psychologica}, \emph{173}, 13--20.
 
-\leavevmode\vadjust pre{\hypertarget{ref-spielmann2020predictive}{}}%
-Spielmann, S.
-S., Maxwell, J.
-A., MacDonald, G., Peragine, D., \& Impett, E.
-A.
-(2020).
-The predictive effects of fear of being single on physical attractiveness and less selective partner selection strategies.
-\emph{Journal of Social and Personal Relationships}, \emph{37}(1), 100--123.
-
-\leavevmode\vadjust pre{\hypertarget{ref-susmann2021persuasion}{}}%
-Susmann, M.
-W., Xu, M., Clark, J.
-K., Wallace, L.
-E., Blankenship, K.
-L., Philipp-Muller, A.
-Z., Luttrell, A., Wegener, D.
-T., \& Petty, R.
-E.
-(2021).
-Persuasion amidst a pandemic: Insights from the elaboration likelihood model.
-\emph{European Review of Social Psychology}, 1--37.
-
-\leavevmode\vadjust pre{\hypertarget{ref-taylor2009neural}{}}%
-Taylor, M.
-J., Arsalidou, M., Bayless, S.
-J., Morris, D., Evans, J.
-W., \& Barbeau, E.
-J.
-(2009).
-Neural correlates of personally familiar faces: Parents, partner and own faces.
-\emph{Human Brain Mapping}, \emph{30}(7), 2008--2020.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tsikandilakis2019beauty}{}}%
-Tsikandilakis, M., Bali, P., \& Chapman, P.
-(2019).
-Beauty is in the eye of the beholder: The appraisal of facial attractiveness and its relation to conscious awareness.
-\emph{Perception}, \emph{48}(1), 72--92.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tucciarelli2020}{}}%
-Tucciarelli, R., Vehar, N., \& Tsakiris, M. (2020). \emph{On the realness of people who do not exist: the social processing of artificial faces}. \url{https://doi.org/10.31234/osf.io/dnk9x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-van2020sex}{}}%
-Van Den Akker, O.
-R., Assen, M.
-A.
-van, Van Vugt, M., \& Wicherts, J.
-M.
-(2020).
-Sex differences in trust and trustworthiness: A meta-analysis of the trust game and the gift-exchange game.
-\emph{Journal of Economic Psychology}, \emph{81}, 102329.
-
-\leavevmode\vadjust pre{\hypertarget{ref-viola2023designed}{}}%
-Viola, M., \& Voto, C. (2023). Designed to abuse? Deepfakes and the non-consensual diffusion of intimate images. \emph{Synthese}, \emph{201}(1), 1--20.
-
-\leavevmode\vadjust pre{\hypertarget{ref-weller2012honest}{}}%
-Weller, J.
-A., \& Thulin, E.
-W.
-(2012).
-Do honest people take fewer risks?
-Personality correlates of risk-taking to achieve gains and avoid losses in HEXACO space.
-\emph{Personality and Individual Differences}, \emph{53}(7), 923--926.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wickham2019}{}}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
+\bibitem[\citeproctext]{ref-spielmann2020predictive}
+Spielmann, S. S., Maxwell, J. A., MacDonald, G., Peragine, D., \&
+Impett, E. A. (2020). The predictive effects of fear of being single on
+physical attractiveness and less selective partner selection strategies.
+\emph{Journal of Social and Personal Relationships}, \emph{37}(1),
+100--123.
+
+\bibitem[\citeproctext]{ref-susmann2021persuasion}
+Susmann, M. W., Xu, M., Clark, J. K., Wallace, L. E., Blankenship, K.
+L., Philipp-Muller, A. Z., Luttrell, A., Wegener, D. T., \& Petty, R. E.
+(2021). Persuasion amidst a pandemic: Insights from the elaboration
+likelihood model. \emph{European Review of Social Psychology}, 1--37.
+
+\bibitem[\citeproctext]{ref-taylor2009neural}
+Taylor, M. J., Arsalidou, M., Bayless, S. J., Morris, D., Evans, J. W.,
+\& Barbeau, E. J. (2009). Neural correlates of personally familiar
+faces: Parents, partner and own faces. \emph{Human Brain Mapping},
+\emph{30}(7), 2008--2020.
+
+\bibitem[\citeproctext]{ref-tsikandilakis2019beauty}
+Tsikandilakis, M., Bali, P., \& Chapman, P. (2019). Beauty is in the eye
+of the beholder: The appraisal of facial attractiveness and its relation
+to conscious awareness. \emph{Perception}, \emph{48}(1), 72--92.
+
+\bibitem[\citeproctext]{ref-tucciarelli2020}
+Tucciarelli, R., Vehar, N., \& Tsakiris, M. (2020). \emph{On the
+realness of people who do not exist: the social processing of artificial
+faces}. \url{https://doi.org/10.31234/osf.io/dnk9x}
+
+\bibitem[\citeproctext]{ref-turi2022tangled}
+Turi, A., Rebeleș, M.-R., \& Visu-Petra, L. (2022). The tangled webs
+they weave: A scoping review of deception detection and production in
+relation to dark triad traits. \emph{Acta Psychologica}, \emph{226},
+103574.
+
+\bibitem[\citeproctext]{ref-van2020sex}
+Van Den Akker, O. R., Assen, M. A. van, Van Vugt, M., \& Wicherts, J. M.
+(2020). Sex differences in trust and trustworthiness: A meta-analysis of
+the trust game and the gift-exchange game. \emph{Journal of Economic
+Psychology}, \emph{81}, 102329.
+
+\bibitem[\citeproctext]{ref-viola2023designed}
+Viola, M., \& Voto, C. (2023). Designed to abuse? Deepfakes and the
+non-consensual diffusion of intimate images. \emph{Synthese},
+\emph{201}(1), 1--20.
+
+\bibitem[\citeproctext]{ref-wang2024}
+Wang, J., \& Nishida, S. (2024). Artificiality is perceptually
+associated with trustworthiness but not attractiveness in AI-synthesized
+faces. \emph{人工知能学会全国大会論文集 第 38 回 (2024)},
+3Xin241--3Xin241.
+
+\bibitem[\citeproctext]{ref-weller2012honest}
+Weller, J. A., \& Thulin, E. W. (2012). Do honest people take fewer
+risks? Personality correlates of risk-taking to achieve gains and avoid
+losses in HEXACO space. \emph{Personality and Individual Differences},
+\emph{53}(7), 923--926.
+
+\bibitem[\citeproctext]{ref-wickham2019}
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D.,
+François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M.,
+Pedersen, T. L., Miller, E., Bache, S. M., Müller, K., Ooms, J.,
+Robinson, D., Seidel, D. P., Spinu, V., \ldots{} Yutani, H. (2019).
+Welcome to the {tidyverse}. \emph{Journal of Open Source Software},
+\emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}
+
+\bibitem[\citeproctext]{ref-willis2006first}
+Willis, J., \& Todorov, A. (2006). First impressions: Making up your
+mind after a 100-ms exposure to a face. \emph{Psychological Science},
+\emph{17}(7), 592--598.
 
@@
 
-\clearpage
-\renewcommand{\listfigurename}{Figure captions}
-
 \end{document}

### 2024-10-23 submission/new_manuscript/manuscript.qmd
revision completed

@@
         department: School of Social Sciences
+  - name: Ana Neves  
+    orcid: 0009-0006-0020-7599
+    role:
+      - Data curation
+      - Formal Analysis
+      - Writing – review & editing
+    affiliations:
+      - name: University of Sussex
+        department: School of Psychology     
   - name: Stephanie Kirk  # stephanie.morgank@gmail.com
@@
 
-Advancements in technology have now made it possible to create
-near-perfect simulations that are indistinguishable from reality with an
-ease, affordability and accessibility that are unprecedented in Human
-history.These artificial, yet realistic constructs permeate all areas of
+**Advancements in technology have now made it possible to create near-perfect simulations that are indistinguishable from reality with an ease, affordability and accessibility that are unprecedented in Human history**.These artificial, yet realistic constructs permeate all areas of
 life through immersive works of fiction, deep fakes (real-like images
@@
 
-While not all simulations have achieved perfect realism, such as
-Computer Generated Images (CGI) in movies or via recent algorithms such
-as GANs or diffusion model, which often include distortions or lack
-certain key details distinguishing them from real images
-[@mcdonnell2010face; @corvi2022detection], it is fair to assume that
-these technical limitations will become negligible in the near future.
+**While not all simulations have achieved perfect realism, such as Computer Generated Images (CGI) in movies or via recent algorithms such as GANs or diffusion model, which often include distortions or lack certain key details distinguishing them from real images [@mcdonnell2010face; @corvi2022detection], it is fair to assume that these technical limitations will become negligible in the near future.**
 This is particularly true in the field of face generation, where
@@
 effect of facial attractiveness on simulation monitoring, i.e., on the
-beliefs that an image is real or artificially generated. Based on the
-*affective reality theory* [@makowski2023affective;
-@makowski2018cognitive], which suggests that salient and emotional
-stimuli are perceived to be more real (up to a point of reversal after
-which beliefs of fiction becomes used an emotion regulation strategy),
-we hypothesize a quadratic relationship between perceived realness and
-attractiveness: faces rated as highly attractive or unattractive will
-more likely be believed to be real. We expect a similar relationship
-with trustworthiness ratings given its well-established link with
-attractiveness [@liefooghe2022faces; @bartosik2021you; @garrido2017kdef;
-@little2011facial], and a positive relationship with familiarity (as
-more familiar faces would appear as more salient, self-relevant and
-anchored in reality). Additionally, we will further explore the link
-shared by dispositional traits, such as personality and attitude towards
-AI, with simulation monitoring tendencies. Importantly, this study does
-investigate the discriminative accuracy between "true" photos and "true"
-artificially-generated images (which we consider more a technological
-issue than a psychological one), focusing on the beliefs that a stimulus
-is real or fake, independently of its true. **In other words, the
-present study investigates the psychological process that leads to
-different *beliefs* of reality, rather than the discrimination between
-real faces and actual AI-generated ones, which largely depends on the
-technological quality of the AI-generation process.**
+beliefs that an image is real or artificially generated.
+**The affective reality theory [@makowski2023affective; @makowski2018cognitive] posits that the default tendency is to believe that experiences are real, with emotional and bodily reactions playing a pivotal role in reinforcing or challenging this belief.
+According to the theory, there is a quadratic (inverse U-shaped) relationship between affect and reality judgments: stimuli that elicit mild to moderate emotional and/or bodily reactions tend to enhance the perception of realness, increasing confidence in reality.
+However, when emotional or bodily responses become too intense or overwhelming, the default belief shifts towards non-reality beliefs as an emotion regulation mechanism.
+In other words, extreme emotional reactions can potentially trigger beliefs of reality denial (“it cannot be real”) as a protective mechanism to help individuals cope with distress.
+The present experiment can be put in relation with the first part of this proposal - that of a positive relationship between embodied or emotional reactions and appraisals of reality.
+Following this hypothesis, faces rated as either highly attractive or unattractive - and eliciting stronger reactions - would likely be judged as real**.
+**We expect a similar pattern with trustworthiness, where faces judged as highly trustworthy or untrustworthy will be more likely to be perceived as real.
+Finally, we anticipate a positive relationship between familiarity and perceived realness, as familiar faces tend to be judged as more real [@miller2023].** Additionally, we will further explore the
+link shared by dispositional traits, such as personality and attitude
+towards AI, with simulation monitoring tendencies. Importantly, this
+study does investigate the discriminative accuracy between "true" photos
+and "true" artificially-generated images (which we consider more a
+technological issue than a psychological one), focusing on the beliefs
+that a stimulus is real or fake, independently of its true. **In other
+words, the present study investigates the psychological process that
+leads to different *beliefs* of reality, rather than the discrimination
+between real faces and actual AI-generated ones, which largely depends
+on the technological quality of the AI-generation process.**
 
@@
 
-All the material (preregistration ***[FOOTNOTE: This approach diverges from the preregistration in several key ways.
-First, the phrasing of items was modified from "Assuming the face you saw was of a real individual, how..." to "I find this person..." A new attractiveness scale (i.e., Beauty) was introduced to capture a more objective measure of attraction.
-Finally, the data analysis method was altered from Bayesian Mixed Models due to computational limitations, as we were unable to run these models on a high-performance cluster.]***, experiment demo, experiment code, raw
-data, analysis script with complementary figures and analyses, etc.) is
-available at
+All the material (preregistration ***\[FOOTNOTE: This approach diverges
+from the preregistration in several key ways. First, the phrasing of
+items was modified from "Assuming the face you saw was of a real
+individual, how..." to "I find this person..." A new attractiveness
+scale (i.e., Beauty) was introduced to capture a more objective measure
+of attraction. Finally, the data analysis method was altered from
+Bayesian Mixed Models due to computational limitations, as we were
+unable to run these models on a high-performance cluster.\]***,
+experiment demo, experiment code, raw data, analysis script with
+complementary figures and analyses, etc.) is available at
 [**https://github.com/RealityBending/FakeFace**](https://github.com/RealityBending/FakeFace){.uri}.
@@
 attention check questions, took an implausibly short time to finish the
-questionnaires or had incomplete responses. Out of the 5 participants
-excluded, 2 Participants were excluded because they failed 2 out of 3
-attention checks, 1 because they did not answer the sexual orientation
-question, which made further analysis impossible, and 2 had an abnormal
-low agreement (r \< 0.1) between the beauty and the attractiveness
-ratings (possibly indicating random responses as these two scales
-exhibited a higher correlation for the other participants).The final
+questionnaires or had incomplete responses.
+**Out of the 5 participants excluded, 2 participants were excluded because they failed 2 out of 3 attention checks, 1 because they did not answer the sexual orientation question, which made further analysis impossible, and 2 had an abnormal low agreement (r \< 0.1) between the beauty and the attractiveness ratings (possibly indicating random responses as these two scales exhibited a higher correlation for the other participants)**.The final
 sample included 145 participants (Mean age = 28.3, SD = 9.0, range:
@@
 gender or sexual orientation) for each questionnaire, with all of the
-subscales as orthogonal predictors. \
+subscales as orthogonal predictors.\
 
@@
 influencing the other ratings). Although the effect of re-exposure delay
-was negligible, the potential bias induced by face familiarity, that is
-by re-presenting the same face stimuli twice, as compared to judging
-completely new items, cannot be discarded. Future studies could examine
+was negligible, the potential bias induced by face familiarity, **that is by re-presenting the same face stimuli twice**, as compared to judging completely new items, cannot be discarded.
+Future studies could examine
 that by incorporating novel face images or increasing the duration of
@@
 simple instructions and lead to high-confidence answers remains an
-interesting phenomenon. Moreover, it is to note that the paradigm did
-not instruct participants to balance their answers according to a
-certain distribution (e.g., 50-50), merely providing them a description
-of the dataset. The fact that no presentation order effect was found on
+interesting phenomenon.
+**Moreover, it is to note that the paradigm did not explicitly instruct participants to balance their answers according to a certain distribution (e.g., 50-50) - merely providing them a description of the dataset (but participants could, and in some cases did, deviate substantially from the information provided).** The fact that no presentation order effect was found on
 reality beliefs suggests that participants did not try to actively
@@
 focusing on some features of the stimulus - like hair or eyes in the
-case of faces) to guide their reality beliefs.
-**Additionally, the role of specific facial features, like perceived dominance, warmth or gender, would be an interesting avenue to explore in future studies, in particular with paradigms directly manipulating these dimensions (for instance using AI to generate faces of different characteristics).**
+case of faces) to guide their reality beliefs. **Additionally, the role
+of specific facial features, like perceived dominance, warmth or gender,
+would be an interesting avenue to explore in future studies, in
+particular with paradigms directly manipulating these dimensions (for
+instance using AI to generate faces of different characteristics).**
 

### 2024-10-23 submission/R2/manuscript-Academ-7C8RB54.qmd
clean manuscript

--- 2024-10-23 submission/new_manuscript/manuscript.qmd
@@
 suppress-title-page: false
-mask: false
+mask: true
 # Language options. See https://quarto.org/docs/authoring/language.html
@@
 @goldstein2009pleasure], as well as familiarity [@begg1992dissociation],
-could also play a role in guiding our appraisal of a stimulus.**For
+could also play a role in guiding our appraisal of a stimulus. **For
 instance,** @miller2023 **reported that participants were more likely to
@@
 measuring general attractiveness
-<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->
-["How attractive would you say you are?", @marcinkowska2021self] and the
+<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->["How attractive would you say you are?", @marcinkowska2021self] and the
 other measuring physical attractiveness
@@
 In the second part of this study, images of neutral-expression faces
-from the validated American Multiracial Face Database
-<!-- (AMFD) [@chen2021broadening]  --> [AMFD, @chen2021broadening] were
+from the validated American Multiracial Face Database <!-- (AMFD) [@chen2021broadening]  -->[AMFD, @chen2021broadening] were
 presented to the participants for 500ms each, in a randomized order,

### 2024-12-06 submission/R2/manuscript.qmd
submission
R3 prep

--- 2024-10-23 submission/new_manuscript/manuscript.qmd
@@
 
-**Advancements in technology have now made it possible to create near-perfect simulations that are indistinguishable from reality with an ease, affordability and accessibility that are unprecedented in Human history**.These artificial, yet realistic constructs permeate all areas of
-life through immersive works of fiction, deep fakes (real-like images
+**Advancements in technology have now made it possible to create
+near-perfect simulations that are indistinguishable from reality with an
+ease, affordability and accessibility that are unprecedented in Human
+history**. These artificial, yet realistic constructs permeate all areas
+of life through immersive works of fiction, deep fakes (real-like images
 and videos generated by deep learning algorithms), virtual and augmented
@@
 
-**While not all simulations have achieved perfect realism, such as Computer Generated Images (CGI) in movies or via recent algorithms such as GANs or diffusion model, which often include distortions or lack certain key details distinguishing them from real images [@mcdonnell2010face; @corvi2022detection], it is fair to assume that these technical limitations will become negligible in the near future.**
+**While not all simulations have achieved perfect realism, such as
+Computer Generated Images (CGI) in movies or via recent algorithms such
+as GANs or diffusion model, which often include distortions or lack
+certain key details distinguishing them from real images
+[@mcdonnell2010face; @corvi2022detection], it is fair to assume that
+these technical limitations will become negligible in the near future.**
 This is particularly true in the field of face generation, where
@@
 
-Literature shows that the context surrounding a stimulfus often plays an
+Literature shows that the context surrounding a stimulus often plays an
 important role in the assessment of its reality [a process henceforth
@@
 effect of facial attractiveness on simulation monitoring, i.e., on the
-beliefs that an image is real or artificially generated.
-**The affective reality theory [@makowski2023affective; @makowski2018cognitive] posits that the default tendency is to believe that experiences are real, with emotional and bodily reactions playing a pivotal role in reinforcing or challenging this belief.
-According to the theory, there is a quadratic (inverse U-shaped) relationship between affect and reality judgments: stimuli that elicit mild to moderate emotional and/or bodily reactions tend to enhance the perception of realness, increasing confidence in reality.
-However, when emotional or bodily responses become too intense or overwhelming, the default belief shifts towards non-reality beliefs as an emotion regulation mechanism.
-In other words, extreme emotional reactions can potentially trigger beliefs of reality denial (“it cannot be real”) as a protective mechanism to help individuals cope with distress.
-The present experiment can be put in relation with the first part of this proposal - that of a positive relationship between embodied or emotional reactions and appraisals of reality.
-Following this hypothesis, faces rated as either highly attractive or unattractive - and eliciting stronger reactions - would likely be judged as real**.
-**We expect a similar pattern with trustworthiness, where faces judged as highly trustworthy or untrustworthy will be more likely to be perceived as real.
-Finally, we anticipate a positive relationship between familiarity and perceived realness, as familiar faces tend to be judged as more real [@miller2023].** Additionally, we will further explore the
-link shared by dispositional traits, such as personality and attitude
-towards AI, with simulation monitoring tendencies. Importantly, this
-study does investigate the discriminative accuracy between "true" photos
-and "true" artificially-generated images (which we consider more a
-technological issue than a psychological one), focusing on the beliefs
+beliefs that an image is real or artificially generated. **The affective
+reality theory [@makowski2023affective; @makowski2018cognitive] posits
+that the default tendency is to believe that experiences are real, with
+emotional and bodily reactions playing a pivotal role in reinforcing or
+challenging this belief. According to the theory, there is a quadratic
+(inverse U-shaped) relationship between affect and reality judgments:
+stimuli that elicit mild to moderate emotional and/or bodily reactions
+tend to enhance the perception of realness, increasing confidence in
+reality. However, when emotional or bodily responses become too intense
+or overwhelming, the default belief shifts towards non-reality beliefs
+as an emotion regulation mechanism. In other words, extreme emotional
+reactions can potentially trigger beliefs of reality denial (“it cannot
+be real”) as a protective mechanism to help individuals cope with
+distress. The present experiment can be put in relation with the first
+part of this proposal - that of a positive relationship between embodied
+or emotional reactions and appraisals of reality. Following this
+hypothesis, faces rated as either highly attractive or unattractive -
+and eliciting stronger reactions - would likely be judged as real**.
+**We expect a similar pattern with trustworthiness, where faces judged
+as highly trustworthy or untrustworthy will be more likely to be
+perceived as real. Finally, we anticipate a positive relationship
+between familiarity and perceived realness, as familiar faces tend to be
+judged as more real [@miller2023].** Additionally, we will further
+explore the link shared by dispositional traits, such as personality and
+attitude towards AI, with simulation monitoring tendencies. Importantly,
+this study does investigate the discriminative accuracy between "true"
+photos and "true" artificially-generated images (which we consider more
+a technological issue than a psychological one), focusing on the beliefs
 that a stimulus is real or fake, independently of its true. **In other
@@
 **Ethics Statement.** This study was approved by the NTU Institutional
-Review Board (NTU IRB-2022-187) <!-- [**IRB NUMBER**] --> and all
+Review Board (NTU IRB-2022-187) <!-- [**IRB NUMBER**] -->and all
 procedures performed were in accordance with the ethical standards of
@@
 measuring general attractiveness
-<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->
-["How attractive would you say you are?", @marcinkowska2021self] and the
-other measuring physical attractiveness
-<!-- ("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive] -->
+<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->["How
+attractive would you say you are?", @marcinkowska2021self] and the other
+measuring physical
+attractiveness<!-- ("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive] -->
 ["How would you rate your own physical attractiveness relative to the
@@
 from the validated American Multiracial Face Database
-<!-- (AMFD) [@chen2021broadening]  --> [AMFD, @chen2021broadening] were
+<!-- (AMFD) [@chen2021broadening]  -->[AMFD, @chen2021broadening] were
 presented to the participants for 500ms each, in a randomized order,
@@
 the experiment instructions would be well-understood. Participants were
-incentivised with a reward of about \textsterling 7.5 for completing the
-study, which took about 45 minutes to finish. Demographic variables
-(age, gender, sexual orientation, education and ethnicity) were
-self-reported on a voluntary basis.
+incentivised with a reward of about £ 7.5 for completing the study,
+which took about 45 minutes to finish. Demographic variables (age,
+gender, sexual orientation, education and ethnicity) were self-reported
+on a voluntar
 
@@
 attention check questions, took an implausibly short time to finish the
-questionnaires or had incomplete responses.
-**Out of the 5 participants excluded, 2 participants were excluded because they failed 2 out of 3 attention checks, 1 because they did not answer the sexual orientation question, which made further analysis impossible, and 2 had an abnormal low agreement (r \< 0.1) between the beauty and the attractiveness ratings (possibly indicating random responses as these two scales exhibited a higher correlation for the other participants)**.The final
+questionnaires or had incomplete responses. **Out of the 5 participants
+excluded, 2 participants were excluded because they failed 2 out of 3
+attention checks, 1 because they did not answer the sexual orientation
+question, which made further analysis impossible, and 2 had an abnormal
+low agreement (r \< 0.1) between the beauty and the attractiveness
+ratings (possibly indicating random responses as these two scales
+exhibited a higher correlation for the other participants)**.The final
 sample included 145 participants (Mean age = 28.3, SD = 9.0, range:
@@
 as a general construct), models for beauty, trustworthiness and
-familiarity were adjusted for the the two remaining variables *mutatis
+familiarity were adjusted for the two remaining variables *mutatis
 mutandis*. The analysis focused on sexual-orientation relevant stimuli,
@@
 ```{r message=FALSE, warning=FALSE, fig.cap="Figure 2.
-Top part shows the efffect of face ratings on 1) the probability of judging a face as real vs.
+Top part shows the effect of face ratings on 1) the probability of judging a face as real vs.
 fake (solid line) and 2) on the confidence associated with that judgement (dashed lines) depending on the sex.
@@
 physiological markers
-<!-- (e.g., heart rate deceleration) [@skora2022functional]. --> [e.g.,
+<!-- (e.g., heart rate deceleration) [@skora2022functional]. -->[e.g.,
 heart rate deceleration, @skora2022functional].
@@
 influencing the other ratings). Although the effect of re-exposure delay
-was negligible, the potential bias induced by face familiarity, **that is by re-presenting the same face stimuli twice**, as compared to judging completely new items, cannot be discarded.
-Future studies could examine
-that by incorporating novel face images or increasing the duration of
-the re-exposure delay.
+was negligible, the potential bias induced by face familiarity, **that
+is by re-presenting the same face stimuli twice**, as compared to
+judging completely new items, cannot be discarded. Future studies could
+examine that by incorporating novel face images or increasing the
+duration of the re-exposure delay.
 
@@
 other half real photos". Given this prior information given to
-participants, it might seems like our enthusiasm pertaining to the
+participants, it might seem like our enthusiasm pertaining to the
 finding that most people did indeed believe a high number of stimuli to
@@
 simple instructions and lead to high-confidence answers remains an
-interesting phenomenon.
-**Moreover, it is to note that the paradigm did not explicitly instruct participants to balance their answers according to a certain distribution (e.g., 50-50) - merely providing them a description of the dataset (but participants could, and in some cases did, deviate substantially from the information provided).** The fact that no presentation order effect was found on
-reality beliefs suggests that participants did not try to actively
-distribute their responses to match the instructions, in which case we
-would have expected a different pattern: for instance, the first few
-items judged as real (the initial "true" belief of the participants),
-and a bias would progressively appear towards responding "fake" (as
-participants realize that all stimuli are of similar nature and that
-they have to "make up" for the prevalence of their "real" answers to
-fulfil the expected proportion of responses given the instructions).
+interesting phenomenon. **Moreover, it is to note that the paradigm did
+not explicitly instruct participants to balance their answers according
+to a certain distribution (e.g., 50-50) - merely providing them a
+description of the dataset (but participants could, and in some cases
+did, deviate substantially from the information provided).** The fact
+that no presentation order effect was found on reality beliefs suggests
+that participants did not try to actively distribute their responses to
+match the instructions, in which case we would have expected a different
+pattern: for instance, the first few items judged as real (the initial
+"true" belief of the participants), and a bias would progressively
+appear towards responding "fake" (as participants realize that all
+stimuli are of similar nature and that they have to "make up" for the
+prevalence of their "real" answers to fulfil the expected proportion of
+responses given the instructions).
 
@@
 
-# Data Availability
+## Data Availability
 
@@
 
+## Funding
+
+This work was supported by the Presidential Postdoctoral Fellowship Grant (NTU-PPF-2020-10014) from Nanyang Technological University (awarded to DM).
+
 \pagebreak
 
-# References
+## References
 

### 2024-12-06 submission/R2/manuscript.qmd
changes to manuscript

@@
 
-**Advancements in technology have now made it possible to create
+Advancements in technology have now made it possible to create
 near-perfect simulations that are indistinguishable from reality with an
 ease, affordability and accessibility that are unprecedented in Human
-history**. These artificial, yet realistic constructs permeate all areas
+history. These artificial, yet realistic constructs permeate all areas
 of life through immersive works of fiction, deep fakes (real-like images
@@
 
-**While not all simulations have achieved perfect realism, such as
+While not all simulations have achieved perfect realism, such as
 Computer Generated Images (CGI) in movies or via recent algorithms such
@@
 [@mcdonnell2010face; @corvi2022detection], it is fair to assume that
-these technical limitations will become negligible in the near future.**
+these technical limitations will become negligible in the near future.
 This is particularly true in the field of face generation, where
@@
 important role in the assessment of its reality [a process henceforth
-referred to as *simulation monitoring*, @makowski2018cognitive;
+referred to as simulation monitoring, @makowski2018cognitive;
 @makowski2019phenomenal]. With the extensive search and processing of
@@
 have been associated with greater susceptibility to fake news
-[@piksa2022cognitive; @sindermann2020short]. **Interestingly, a recent
+[@piksa2022cognitive; @sindermann2020short]. Interestingly, a recent
 review suggested that narcissism was related to a strong self-perceived
@@
 be more conservative in their judgments to ensure fairness
-[@liu2020honesty], likely resulting in lower confidence ratings.**
+[@liu2020honesty], likely resulting in lower confidence ratings.
 
@@
 @goldstein2009pleasure], as well as familiarity [@begg1992dissociation],
-could also play a role in guiding our appraisal of a stimulus. **For
-instance,** @miller2023 **reported that participants were more likely to
+could also play a role in guiding our appraisal of a stimulus. For
+instance, @miller2023 reported that participants were more likely to
 mistakenly identify AI-generated faces as real because they perceived
-them as more familiar.**
+them as more familiar.
 
@@
 were told that the faces were AI-generated were compared to those who
-had no prior knowledge. **Similarly, when participants are informed that
+had no prior knowledge. Similarly, when participants are informed that
 faces are AI-generated, the perceived artificiality leads to lower trust
@@
 the faces are AI-generated, trust ratings for these synthetic faces tend
-to increase [@nightingale2022]**. Whereas this line of evidence suggests
+to increase [@nightingale2022]. Whereas this line of evidence suggests
 that reality beliefs have an effect on face attractiveness and
-**trustworthiness** ratings, the opposite question - whether
-attractiveness **and trustworthiness contribute** to the formation of
+trustworthiness ratings, the opposite question - whether
+attractiveness and trustworthiness contribute to the formation of
 reality beliefs - has received little attention to date.
@@
 effect of facial attractiveness on simulation monitoring, i.e., on the
-beliefs that an image is real or artificially generated. **The affective
+beliefs that an image is real or artificially generated. The affective
 reality theory [@makowski2023affective; @makowski2018cognitive] posits
@@
 hypothesis, faces rated as either highly attractive or unattractive -
-and eliciting stronger reactions - would likely be judged as real**.
-**We expect a similar pattern with trustworthiness, where faces judged
+and eliciting stronger reactions - would likely be judged as real.
+We expect a similar pattern with trustworthiness, where faces judged
 as highly trustworthy or untrustworthy will be more likely to be
@@
 between familiarity and perceived realness, as familiar faces tend to be
-judged as more real [@miller2023].** Additionally, we will further
+judged as more real [@miller2023]. Additionally, we will further
 explore the link shared by dispositional traits, such as personality and
@@
 a technological issue than a psychological one), focusing on the beliefs
-that a stimulus is real or fake, independently of its true. **In other
+that a stimulus is real or fake, independently of its true. In other
 words, the present study investigates the psychological process that
-leads to different *beliefs* of reality, rather than the discrimination
+leads to different beliefs of reality, rather than the discrimination
 between real faces and actual AI-generated ones, which largely depends
-on the technological quality of the AI-generation process.**
+on the technological quality of the AI-generation process.
 
@@
 ("I think current Artificial Intelligence algorithms can generate very
-realistic images"), **to potentially test and mitigate the potential
-effect of expectations/beliefs about AI.** **These items were** mixed
+realistic images"), to potentially test and mitigate the potential
+effect of expectations/beliefs about AI.These items were mixed
 with 5 items from the general attitudes towards AI scale to lower the
@@
 average", @spielmann2020predictive]. 3 attention check questions were
-also embedded in the surveys. **All Cronbach's alpha values were within
+also embedded in the surveys. All Cronbach's alpha values were within
 the acceptable to excellent range, except for the neuroticism subscale
@@
 & Gliem, 2003; see supplementary material for the details of the
-reliability analysis).**
+reliability analysis).
 
@@
 presented to the participants for 500ms each, in a randomized order,
-following a fixation cross display (750 ms). T**he decision to present
+following a fixation cross display (750 ms). The decision to present
 the faces for 500 ms was based on pilot studies, which demonstrated that
@@
 judgment levels and increased confidence beyond this exposure time
-[@willis2006first].**
+[@willis2006first].
 
-**The AMFD is a recently validated database including a set of 110
+The AMFD is a recently validated database including a set of 110
 pictures of homogeneous quality featuring diverse faces (particularly in
@@
 Eastern, 5% Black/White, and 5% Asian/Middle Eastern, with about 18%
-identifying as other racial backgrounds.**
+identifying as other racial backgrounds.
 
@@
 find this person attractive") and physical *Beauty* ("This face is
-good-looking"). **This dual-scale approach aims to reflect two
+good-looking"). This dual-scale approach aims to reflect two
 conceptually distinct dimensions: Attractiveness might capture personal,
@@
 wanted the experiment to be able to potentially capture scenarios where
-a face could be judged beautiful yet not, attractive and vice versa.**
+a face could be judged beautiful yet not, attractive and vice versa.
 
@@
 gender, sexual orientation, education and ethnicity) were self-reported
-on a voluntar
+on a voluntary basis.
 
@@
 attention check questions, took an implausibly short time to finish the
-questionnaires or had incomplete responses. **Out of the 5 participants
+questionnaires or had incomplete responses. Out of the 5 participants
 excluded, 2 participants were excluded because they failed 2 out of 3
@@
 ratings (possibly indicating random responses as these two scales
-exhibited a higher correlation for the other participants)**.The final
+exhibited a higher correlation for the other participants).The final
 sample included 145 participants (Mean age = 28.3, SD = 9.0, range:
@@
 models included the participants and stimuli as random **intercepts with
-no nested variables**.
+no nested variables.
 
@@
 as a general construct), models for beauty, trustworthiness and
-familiarity were adjusted for the two remaining variables *mutatis
-mutandis*. The analysis focused on sexual-orientation relevant stimuli,
+familiarity were adjusted for the two remaining variables *mutatis mutandis*. The analysis focused on sexual-orientation relevant stimuli,
 i.e., on faces that were aligned with respect to the participants'
@@
 gender or sexual orientation) for each questionnaire, with all of the
-subscales as orthogonal predictors.\
+subscales as orthogonal predictors.
 
@@
 The points are the average per participant confidence for both types of judgements.
-Stars indicate significance (p < .001***, p < .01**, p < .05*).", out.width="100%"}
+Stars indicate significance (p < .001\\*\\*\\*, p < .01\\*\\*, p < .05\\*).", out.width="100%"}
 knitr::include_graphics("../../figures/Figure2.png")
@@
 influencing the other ratings). Although the effect of re-exposure delay
-was negligible, the potential bias induced by face familiarity, **that
-is by re-presenting the same face stimuli twice**, as compared to
+was negligible, the potential bias induced by face familiarity, that
+is by re-presenting the same face stimuli twice, as compared to
 judging completely new items, cannot be discarded. Future studies could
@@
 simple instructions and lead to high-confidence answers remains an
-interesting phenomenon. **Moreover, it is to note that the paradigm did
+interesting phenomenon. Moreover, it is to note that the paradigm did
 not explicitly instruct participants to balance their answers according
@@
 description of the dataset (but participants could, and in some cases
-did, deviate substantially from the information provided).** The fact
+did, deviate substantially from the information provided). The fact
 that no presentation order effect was found on reality beliefs suggests
@@
 stimuli are of similar nature and that they have to "make up" for the
-prevalence of their "real" answers to fulfil the expected proportion of
+prevalence of their "real" answers to fulfill the expected proportion of
 responses given the instructions).
@@
 focusing on some features of the stimulus - like hair or eyes in the
-case of faces) to guide their reality beliefs. **Additionally, the role
+case of faces) to guide their reality beliefs. Additionally, the role
 of specific facial features, like perceived dominance, warmth or gender,
@@
 particular with paradigms directly manipulating these dimensions (for
-instance using AI to generate faces of different characteristics).**
+instance using AI to generate faces of different characteristics).
 
